### 2021-12-17 paper/manuscript.Rmd
initial setup

---
title: "Measuring individual differences in the understanding of gaze cues"
author: "Julia Prein"
date: "12/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

# Methods
## Participants
## Procedure
## Data analysis

# Results

# Discussion

# References

# Acknowledgements

# Author Contributions

### 2021-12-17 paper/manuscript.Rmd
use papaja template

@@
 ---
-title: "Measuring individual differences in the understanding of gaze cues"
-author: "Julia Prein"
-date: "12/17/2021"
-output: pdf_document
+title             : "Measuring individual differences in the understanding of gaze cues"
+shorttitle        : "Gaze cue understanding"
+
+author: 
+  - name          : "Julia Prein"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
+    email         : "julia_prein@eva.mpg.de"
+
+  - name          : "Manuel Bohn"
+    affiliation   : "1"
+
+  - name          : "Luke Maurits"
+    affiliation   : "1"
+
+  - name          : "Steven Kalinke"
+    affiliation   : "1"
+
+  - name          : "Daniel M. Haun"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "social cognition, individual differences, gaze cues, psychometrics"
+wordcount         : "X"
+
+bibliography      : ["r-references.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup, include = FALSE}
+library("papaja")
+r_refs("r-references.bib")
 ```
 
-# Introduction
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
 
 # Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
 ## Participants
+
+## Material
+
 ## Procedure
+
 ## Data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
 
@@
 
+\newpage
+
 # References
 
-# Acknowledgements
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
-# Author Contributions
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2021-12-17 paper/manuscript.tex
use papaja template

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\title{Measuring individual differences in the understanding of gaze cues}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Measuring individual differences in the understanding of gaze cues},
  pdfauthor={Julia Prein1, Manuel Bohn1, Luke Maurits1, Steven Kalinke1, \& Daniel M. Haun1},
  pdflang={en-EN},
  pdfkeywords={social cognition, individual differences, gaze cues, psychometrics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Gaze cue understanding}
\keywords{social cognition, individual differences, gaze cues, psychometrics\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany. E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\end{CSLReferences}

\endgroup

\end{document}

### 2021-12-18 paper/manuscript.Rmd
change title and add idea for opener

@@
 ---
-title             : "Measuring individual differences in the understanding of gaze cues"
+title             : "Measuring individual differences in the understanding of gaze cues across the lifespan"
 shorttitle        : "Gaze cue understanding"
@@
 
+Idea for an opener :)
+
+Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+For example ...
+.
+
 # Methods

### 2021-12-21 paper/manuscript.Rmd
add first sentences for methods

@@
 abstract: |
+  There must be an abstract of no more than 250 words.
   One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
@@
 ## Material
+Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+The code is open-source (https://github.com/ccp-eva/gafo-demo) 
+and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
 
-## Procedure
+The web-app generates two files: 
+(1) a text file (JSON) containing click responses, 
+and (2) a video file (webm) of the participant's webcam recording.
+Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+
+The web-app was programmed in Vanilla JavaScript, HTML and CSS. 
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's viewport without loss of quality,
+while keepiong the aspect ratio and relative object positions.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all 
+composite parts of the scene (e.g., pupil of the agent).
+
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used 
+to animate the movement of single SVG elements.
+
+Study instructions were pre-recorded and, therefore, constant across participants. 
+No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+
+## Procedure (from pre-reg)
+An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. 
+A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. 
+The target then falls to the ground. 
+The agent’s gaze follows the movement of the target, 
+that is, the pupils of the agent move in a way that their center aligns with the center of the target. 
+Participants are then asked to locate the target’s position on the screen.
+
+Visual access to the target’s true location is manipulated by a hedge. 
+Participants either have full, partial, or no visual access to the true target location. 
+When partial or no information about the target location is accessible, 
+participants are expected to use the agent’s gaze as a cue.
+
+There are two different versions of partial and no visual access trials. 
+For families that use a tablet with touchscreen, 
+the target lands behind a hedge (i.e., hedge version). 
+Children are then asked to click directly on the hedge to indicate where the target is.
+For families that use a computer without touchscreen, the balloon falls into a box. 
+Children are then asked to point to the box containing the target. 
+Caregivers then act as the "digital finger" of their children and click on the indicated box.
+
+The dependent variable depends on the study version: 
+For the hedge version, our dependent variable is continuous. 
+Here, the dependent variable is imprecision, 
+which is defined as the absolute difference between the true x coordinate of the target 
+and the x coordinate of the participant’s click on the screen. 
+For the box version, we use our categorical outcome (i.e., which box was clicked) 
+to calculate the proportion of correct responses.
+
+There are three different trial types, 
+depending on the visual access to the target flight and end location. 
+In touch training trials, participants have full visual access to the target flight 
+and the target's end location. 
+In familiarization trials, participants have visual access to the target flight 
+but not to the target's end location. 
+In the hedge version, the target's end location is covered by a hedge. 
+In the box version, the target flies into a box and is therefore not visible anymore. 
+In test trials, participants have no visual access to the target flight 
+nor the end location. 
+In both versions, the target flight is covered by a hedge. 
+In the hedge version, the hedge then shrinks to cover the target's end location. 
+In the box version, the hedge shrinks completely. 
+The boxes then hide the target's end location.
+
+Depending on the participant's device, 
+participants have to indicate their estimated target location directly on the hedge 
+(i.e., hedge version) or in one of five boxes (i.e., box version).
+
+Participants receive 19 trials with one touch training, two familiarization trials, 
+and 16 test trials. 
+The first trial of each type comprises a voice-over description of the presented events. 
+Touch and familiarization trials, as well as voice-over trials, will not be included in the analysis. 
+Therefore, we will conduct our analysis with 15 test trials.
+
+Target locations are generated as follows. 
+For the hedge version, the full width of the screen is divided into ten bins. 
+Exact coordinates within each bin are randomly generated. 
+For the box version, the target randomly lands in one out of five boxes. 
+Each bin/box occurs equally often. 
+The same bin/box can occur only twice in a row.
 
@@
 # Discussion
+
+# Declarations
+## Open practices statement
+The web application (https://ccp-odc.eva.mpg.de/gafo-demo/) described here is open source (https://github.com/ccp-eva/gafo-demo).
+The datasets generated during and/or analysed during the current study are available
+in the [gazecues-methods] repository, (https://github.com/jprein/gazecues-methods).
+All experiments were preregistered (https://osf.io/zjhsc/).
+
+## Funding 
+This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number). 
+We thank all the children and parents who participated in the study.
+
+## Conflicts of interest 
+The authors declare that they have no conflict of interest.
+
+## Ethics approval
+
+## Consent to participate
+Informed consent was obtained from all individual participants included in the study or their legal guardians.
+
+## Consent for publication
+
+## Open access
+
+## Authors' contributions 
+optional: please review the submission guidelines from the
+journal whether statements are mandatory
 

### 2021-12-21 paper/manuscript.tex
add first sentences for methods

@@
   man,floatsintext]{apa6}
-\title{Measuring individual differences in the understanding of gaze cues}
+\title{Measuring individual differences in the understanding of gaze cues across the lifespan}
 \author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
@@
 \hypersetup{
-  pdftitle={Measuring individual differences in the understanding of gaze cues},
+  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
   pdfauthor={Julia Prein1, Manuel Bohn1, Luke Maurits1, Steven Kalinke1, \& Daniel M. Haun1},
@@
 \abstract{
+There must be an abstract of no more than 250 words.
 One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
@@
 
+Idea for an opener :)
+
+Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+For example \ldots{} .
+
 \hypertarget{methods}{%
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+The code is open-source (\url{https://github.com/ccp-eva/gafo-demo})
+and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+
+The web-app generates two files:
+(1) a text file (JSON) containing click responses,
+and (2) a video file (webm) of the participant's webcam recording.
+Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+
+The web-app was programmed in Vanilla JavaScript, HTML and CSS.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's viewport without loss of quality,
+while keepiong the aspect ratio and relative object positions.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all
+composite parts of the scene (e.g., pupil of the agent).
+
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used
+to animate the movement of single SVG elements.
+
+Study instructions were pre-recorded and, therefore, constant across participants.
+No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+
+\hypertarget{procedure-from-pre-reg}{%
+\subsection{Procedure (from pre-reg)}\label{procedure-from-pre-reg}}
+
+An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
+A balloon (i.e., target; blue, green, yellow, or red) is located in front of them.
+The target then falls to the ground.
+The agent's gaze follows the movement of the target,
+that is, the pupils of the agent move in a way that their center aligns with the center of the target.
+Participants are then asked to locate the target's position on the screen.
+
+Visual access to the target's true location is manipulated by a hedge.
+Participants either have full, partial, or no visual access to the true target location.
+When partial or no information about the target location is accessible,
+participants are expected to use the agent's gaze as a cue.
+
+There are two different versions of partial and no visual access trials.
+For families that use a tablet with touchscreen,
+the target lands behind a hedge (i.e., hedge version).
+Children are then asked to click directly on the hedge to indicate where the target is.
+For families that use a computer without touchscreen, the balloon falls into a box.
+Children are then asked to point to the box containing the target.
+Caregivers then act as the ``digital finger'' of their children and click on the indicated box.
+
+The dependent variable depends on the study version:
+For the hedge version, our dependent variable is continuous.
+Here, the dependent variable is imprecision,
+which is defined as the absolute difference between the true x coordinate of the target
+and the x coordinate of the participant's click on the screen.
+For the box version, we use our categorical outcome (i.e., which box was clicked)
+to calculate the proportion of correct responses.
+
+There are three different trial types,
+depending on the visual access to the target flight and end location.
+In touch training trials, participants have full visual access to the target flight
+and the target's end location.
+In familiarization trials, participants have visual access to the target flight
+but not to the target's end location.
+In the hedge version, the target's end location is covered by a hedge.
+In the box version, the target flies into a box and is therefore not visible anymore.
+In test trials, participants have no visual access to the target flight
+nor the end location.
+In both versions, the target flight is covered by a hedge.
+In the hedge version, the hedge then shrinks to cover the target's end location.
+In the box version, the hedge shrinks completely.
+The boxes then hide the target's end location.
+
+Depending on the participant's device,
+participants have to indicate their estimated target location directly on the hedge
+(i.e., hedge version) or in one of five boxes (i.e., box version).
+
+Participants receive 19 trials with one touch training, two familiarization trials,
+and 16 test trials.
+The first trial of each type comprises a voice-over description of the presented events.
+Touch and familiarization trials, as well as voice-over trials, will not be included in the analysis.
+Therefore, we will conduct our analysis with 15 test trials.
+
+Target locations are generated as follows.
+For the hedge version, the full width of the screen is divided into ten bins.
+Exact coordinates within each bin are randomly generated.
+For the box version, the target randomly lands in one out of five boxes.
+Each bin/box occurs equally often.
+The same bin/box can occur only twice in a row.
 
@@
 \section{Discussion}\label{discussion}}
+
+\hypertarget{declarations}{%
+\section{Declarations}\label{declarations}}
+
+\hypertarget{open-practices-statement}{%
+\subsection{Open practices statement}\label{open-practices-statement}}
+
+The web application (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) described here is open source (\url{https://github.com/ccp-eva/gafo-demo}).
+The datasets generated during and/or analysed during the current study are available
+in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
+All experiments were preregistered (\url{https://osf.io/zjhsc/}).
+
+\hypertarget{funding}{%
+\subsection{Funding}\label{funding}}
+
+This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
+We thank all the children and parents who participated in the study.
+
+\hypertarget{conflicts-of-interest}{%
+\subsection{Conflicts of interest}\label{conflicts-of-interest}}
+
+The authors declare that they have no conflict of interest.
+
+\hypertarget{ethics-approval}{%
+\subsection{Ethics approval}\label{ethics-approval}}
+
+\hypertarget{consent-to-participate}{%
+\subsection{Consent to participate}\label{consent-to-participate}}
+
+Informed consent was obtained from all individual participants included in the study or their legal guardians.
+
+\hypertarget{consent-for-publication}{%
+\subsection{Consent for publication}\label{consent-for-publication}}
+
+\hypertarget{open-access}{%
+\subsection{Open access}\label{open-access}}
+
+\hypertarget{authors-contributions}{%
+\subsection{Authors' contributions}\label{authors-contributions}}
+
+optional: please review the submission guidelines from the
+journal whether statements are mandatory
 

### 2022-01-05 paper/manuscript.Rmd
start writing prolific supplement

@@
 \endgroup
+
+\newpage
+
+# Supplements
+
+## Adult sample
+
+### Recruitment
+We recruited participants using the online participant recruitment service 
+*Prolific* from the University of Oxford. 
+*Prolific*'s subject pool consists of a mostly European and US-american sample 
+although subjects from all over the world are included.
+
+The recruitment platform realises ethical payment of participants, 
+which requires researchers to pay participants a fixed minimum wage  
+of £5.00 (around US$6.50 or €6.00) per hour.
+We decided to pay all participants the same fixed fee which was in relation 
+to the estimated average time taken to complete the task.
+
+*Prolific* distributed our study link to potential participants, 
+while the hosting of the online study was done by local servers in the
+Max Planck Institute for Evolutionary Anthropology, Leipzig. 
+Therefore, study data was saved only on our internal servers, 
+while *Prolific* provided demographic information of the participants.
+
+Participants' *Prolific* ID was forwarded to our study website using URL parameters.
+This way, we could match participant demographic data to our study data. 
+The same technique was used to confirm study completion: 
+we redirected participants from our study website back to the *Prolific* website 
+using URL parameters.
+
+We used *Prolific*'s inbuilt prescreening filter to include 
+only participants who were fluent in English
+and could therefore properly understand our written and oral study instructions.
+
+### Study 1 - Validation hedge version
+We recruited participants online by advertising the study on *Prolific*.
+
+50 adults participated in the study. 
+One additional subject returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+Data collection took place in May 2021.
+
+Participants were compensated with £1.25 for completing the study. 
+We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
+In average, participants took 05:56min to complete the study.
+
+Participants were required to complete the study on a tablet or desktop. 
+Participation on mobile devices was disabled 
+since the display would be too small and would harm click precision.
+It was indicated that the study required audio sound.
+
+We stored *Prolific*'s internal demographic information, 
+while not asking for additional personal information.
+
+After clicking the study title, participants were directed to our online study website.
+...
+
+### Study 2 - Validation box version
+As in study 1, we recruited participants on *Prolific*, and employed the same methodology. 
+However, this time participants were presented with the box version of the task.
+We showed eight boxes in which the target could land.
+
+50 adults participated in the study. 
+One additional subject returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+Data collection took place in June 2021.
+
+Participants were compensated with £1.00 for completing the study. 
+We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
+In average, participants took 04:43min to complete the study.
+
+### Study 3 - Reliability hedge version
+In addition to the beforementioned prescreening settings, we used a whitelist.
+
+whitelist screener: 
+"When the researcher uses a whitelist, 
+only participants with IDs entered into the whitelist are invited to participate in a study. 
+This allows gathering information from the same subjects at different points in time."
+
+### Study 4 - Reliability box version
+As in study 3, we recruited participants on *Prolific*, and employed the same methodology. 
+However, this time participants were presented with the box version of the task.
+As in study 2, we employed eight boxes in which the target could land.

### 2022-01-05 paper/manuscript.tex
start writing prolific supplement

@@
 
+\newpage
+
+\hypertarget{supplements}{%
+\section{Supplements}\label{supplements}}
+
+\hypertarget{adult-sample}{%
+\subsection{Adult sample}\label{adult-sample}}
+
+\hypertarget{recruitment}{%
+\subsubsection{Recruitment}\label{recruitment}}
+
+We recruited participants using the online participant recruitment service
+\emph{Prolific} from the University of Oxford.
+\emph{Prolific}'s subject pool consists of a mostly European and US-american sample
+although subjects from all over the world are included.
+
+The recruitment platform realises ethical payment of participants,
+which requires researchers to pay participants a fixed minimum wage\\
+of £5.00 (around US\$6.50 or €6.00) per hour.
+We decided to pay all participants the same fixed fee which was in relation
+to the estimated average time taken to complete the task.
+
+\emph{Prolific} distributed our study link to potential participants,
+while the hosting of the online study was done by local servers in the
+Max Planck Institute for Evolutionary Anthropology, Leipzig.
+Therefore, study data was saved only on our internal servers,
+while \emph{Prolific} provided demographic information of the participants.
+
+Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
+This way, we could match participant demographic data to our study data.
+The same technique was used to confirm study completion:
+we redirected participants from our study website back to the \emph{Prolific} website
+using URL parameters.
+
+We used \emph{Prolific}'s inbuilt prescreening filter to include
+only participants who were fluent in English
+and could therefore properly understand our written and oral study instructions.
+
+\hypertarget{study-1---validation-hedge-version}{%
+\subsubsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}
+
+We recruited participants online by advertising the study on \emph{Prolific}.
+
+50 adults participated in the study.
+One additional subject returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+Data collection took place in May 2021.
+
+Participants were compensated with £1.25 for completing the study.
+We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
+In average, participants took 05:56min to complete the study.
+
+Participants were required to complete the study on a tablet or desktop.
+Participation on mobile devices was disabled
+since the display would be too small and would harm click precision.
+It was indicated that the study required audio sound.
+
+We stored \emph{Prolific}'s internal demographic information,
+while not asking for additional personal information.
+
+After clicking the study title, participants were directed to our online study website.
+\ldots{}
+
+\hypertarget{study-2---validation-box-version}{%
+\subsubsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}
+
+As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
+However, this time participants were presented with the box version of the task.
+We showed eight boxes in which the target could land.
+
+50 adults participated in the study.
+One additional subject returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+Data collection took place in June 2021.
+
+Participants were compensated with £1.00 for completing the study.
+We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
+In average, participants took 04:43min to complete the study.
+
+\hypertarget{study-3---reliability-hedge-version}{%
+\subsubsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}
+
+In addition to the beforementioned prescreening settings, we used a whitelist.
+
+whitelist screener:
+``When the researcher uses a whitelist,
+only participants with IDs entered into the whitelist are invited to participate in a study.
+This allows gathering information from the same subjects at different points in time.''
+
+\hypertarget{study-4---reliability-box-version}{%
+\subsubsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}
+
+As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
+However, this time participants were presented with the box version of the task.
+As in study 2, we employed eight boxes in which the target could land.
+
 \end{document}

### 2022-01-10 paper/manuscript.Rmd
supplements: add details for prolific reli testing

@@
 ### Study 1 - Validation hedge version
+Study 1 was pre-registered: https://osf.io/r3bhn. 
 We recruited participants online by advertising the study on *Prolific*.
@@
 ### Study 3 - Reliability hedge version
+Study 3 and study 4 were pre-registered: https://osf.io/nu62m.
+In order to assess the test-retest reliability, 
+we tested the same participants twice with a delay of two weeks.
+
 In addition to the beforementioned prescreening settings, we used a whitelist.
+*Prolific* has a so-called *custom allowlist prescreening filter* 
+where one can enter the *Prolific* IDs of participants who completed a previous study. 
+Only these subjects are then invited to participate in a study. 
+This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.
 
-whitelist screener: 
-"When the researcher uses a whitelist, 
-only participants with IDs entered into the whitelist are invited to participate in a study. 
-This allows gathering information from the same subjects at different points in time."
+In a first round, 60 participants took part on the first testday. 
+Additional two subjects returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+The maximum time is calculated by *Prolific*, based on the estimated average completion time. 
+For this study, the maximum time amounted to 41 minutes. 
+For the first testday, participants were compensated with £1.25. 
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
+In average, participants took 07:11min to complete the first part.
+
+Of the 60 participants that completed testday 1, 41 subjects finished testday 2. 
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Participants were compensated with £1.50 for completing the second part of the study. 
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
+In average, participants took 06:36min to complete the second part of the study.
+
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, 
+we reran the first testday with additional 50 participants. 
+Additional seven subjects returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.25 for completing the first part of the study 
+(estimated average completion time 9 minutes, estimated hourly rate of £8.33). 
+In average, participants took 06:51min to complete the first part.
+
+Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2. 
+Again, participants were compensated with £1.50 for completing the second part of the study. 
+(estimated average completion time 9 minutes, estimated hourly rate of £10).
+In average, participants took 06:26min to complete the second part of the study.
 
@@
 As in study 2, we employed eight boxes in which the target could land.
+
+In a first round, 60 participants took part on the first testday. 
+Additional five subjects returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+For the first testday, participants were compensated with £1.25. 
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
+In average, participants took 07:33min to complete the first part.
+
+Of the 60 participants that completed testday 1, 41 subjects finished testday 2. 
+Participants were compensated with £1.50 for completing the second part of the study. 
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
+In average, participants took 07:50min to complete the second part of the study.
+
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, 
+we reran the first testday with additional 50 participants. 
+Additional eight subjects returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.25 for completing the first part of the study 
+(estimated average completion time 9 minutes, estimated hourly rate of £8.33). 
+In average, participants took 07:37min to complete the first part.
+
+Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2. 
+Additional three subjects returned their submission,
+i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.50 for completing the second part of the study. 
+(estimated average completion time 9 minutes, estimated hourly rate of £10).
+In average, participants took 06:30min to complete the second part of the study.
+
+## Child sample
+### Study 1 - Validation Remote and in-person
+https://osf.io/snju6
+
+### Study 2 - Reliability in-person 
+https://osf.io/xqm73

### 2022-02-14 paper/manuscript.Rmd
revise method section, add sample description child vali inperson

@@
   - id            : "1"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
 
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
 
@@
 
+# Introduction 
 Idea for an opener :)
@@
 Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
-The code is open-source (https://github.com/ccp-eva/gafo-demo) 
-and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
+The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
 
-The web-app generates two files: 
-(1) a text file (JSON) containing click responses, 
-and (2) a video file (webm) of the participant's webcam recording.
+The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
 Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
 
-The web-app was programmed in Vanilla JavaScript, HTML and CSS. 
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality,
-while keepiong the aspect ratio and relative object positions.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all 
-composite parts of the scene (e.g., pupil of the agent).
+This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
 
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used 
-to animate the movement of single SVG elements.
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
 
-Study instructions were pre-recorded and, therefore, constant across participants. 
-No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+## Procedure
+In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
 
-## Procedure (from pre-reg)
+## Stimuli
 An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
@@
 The target then falls to the ground.
-The agent’s gaze follows the movement of the target, 
-that is, the pupils of the agent move in a way that their center aligns with the center of the target. 
-Participants are then asked to locate the target’s position on the screen.
+The agent’s gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+Participants were then asked to locate the target’s position on the screen.
 
-Visual access to the target’s true location is manipulated by a hedge. 
-Participants either have full, partial, or no visual access to the true target location. 
-When partial or no information about the target location is accessible, 
-participants are expected to use the agent’s gaze as a cue.
+There are three different trial types, depending on the visual access to the target flight and end location.
+In *touch training* trials, participants have *full visual access* to the target flight and the target's end location.
+In *familiarization trials*, participants have *partial visual access*: they witness the target flight but cannot see the target's end location.
+In *test trials*, participants have *no visual access* to the target flight nor the end location.
+When partial or no information about the target location is accessible,  participants are expected to use the agent’s gaze as a cue.
 
-There are two different versions of partial and no visual access trials. 
-For families that use a tablet with touchscreen, 
-the target lands behind a hedge (i.e., hedge version). 
-Children are then asked to click directly on the hedge to indicate where the target is.
-For families that use a computer without touchscreen, the balloon falls into a box. 
-Children are then asked to point to the box containing the target. 
-Caregivers then act as the "digital finger" of their children and click on the indicated box.
-
-The dependent variable depends on the study version: 
-For the hedge version, our dependent variable is continuous. 
-Here, the dependent variable is imprecision, 
-which is defined as the absolute difference between the true x coordinate of the target 
-and the x coordinate of the participant’s click on the screen. 
-For the box version, we use our categorical outcome (i.e., which box was clicked) 
-to calculate the proportion of correct responses.
-
-There are three different trial types, 
-depending on the visual access to the target flight and end location. 
-In touch training trials, participants have full visual access to the target flight 
-and the target's end location. 
-In familiarization trials, participants have visual access to the target flight 
-but not to the target's end location. 
-In the hedge version, the target's end location is covered by a hedge. 
-In the box version, the target flies into a box and is therefore not visible anymore. 
-In test trials, participants have no visual access to the target flight 
-nor the end location. 
-In both versions, the target flight is covered by a hedge. 
+There are two different versions of partial and no visual access trials: participants have to indicate their estimated target location directly on the hedge (i.e., hedge version) or in one of five/eight boxes (i.e., box version).
+In test trials, the target flight is always covered by a hedge.
 In the hedge version, the hedge then shrinks to cover the target's end location.
@@
 
-Depending on the participant's device, 
-participants have to indicate their estimated target location directly on the hedge 
-(i.e., hedge version) or in one of five boxes (i.e., box version).
+To keep participants engaged and interested, the presentation of events was accompanied by cartoon-like sounds.
+Each trial started with an eye-blinking sound, while pupils and iris were enlarged and changed in opacity for 0.3 sec.
+The landing of the target was accompanied by a tapping sound.
+After the response was registered, a short plop sound played and a small orange circle confirmed the participants' location choice.
+Once the target landed, the instructor's voice asked "Where is the balloon?".
+If no response was registered, an audio prompt reminded the participant to respond and click on the balloon/the hedge/a box.
 
-Participants receive 19 trials with one touch training, two familiarization trials, 
+Study instructions were pre-recorded and constant across participants.
+No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+Participants received 19 trials with one touch training, two familiarization trials,
 and 16 test trials.
-The first trial of each type comprises a voice-over description of the presented events. 
-Touch and familiarization trials, as well as voice-over trials, will not be included in the analysis. 
-Therefore, we will conduct our analysis with 15 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+Touch and familiarization trials, as well as voice-over trials, were not included in the analysis.
+Therefore, we conducted our analyses with 15 test trials.
 
-Target locations are generated as follows. 
-For the hedge version, the full width of the screen is divided into ten bins. 
-Exact coordinates within each bin are randomly generated. 
-For the box version, the target randomly lands in one out of five boxes. 
-Each bin/box occurs equally often. 
-The same bin/box can occur only twice in a row.
+### Dependent variable
+The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant’s click on the screen.
+For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+
+### Remote datacollection
+Depending on the participant's device, the website automatically presents the hedge or box version of the study.
+For families that use a tablet with touchscreen, the hedge version is shown.
+Here, children can directly click on the screen themselves to indicate where the target is.
+For families that use a computer without touchscreen, the website presents the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
+In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
+
+### Randomization
+All agents and target colors appeared equally often and could not be repeated in more than two consecutive trials.
+The randomization of the target end location depended on the study version.
+In the hedge version, the full width of the screen was divided into ten bins.
+Exact coordinates within each bin were randomly generated.
+In the box version, the target randomly landed in one of the boxes.
+Each bin/box occurred equally often.
+The same bin/box could only occur twice in a row.
 
@@
 The web application (https://ccp-odc.eva.mpg.de/gafo-demo/) described here is open source (https://github.com/ccp-eva/gafo-demo).
-The datasets generated during and/or analysed during the current study are available
-in the [gazecues-methods] repository, (https://github.com/jprein/gazecues-methods).
+The datasets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (https://github.com/jprein/gazecues-methods).
 All experiments were preregistered (https://osf.io/zjhsc/).
@@
 ## Authors' contributions 
-optional: please review the submission guidelines from the
-journal whether statements are mandatory
+optional: please review the submission guidelines from the journal whether statements are mandatory
 
@@
 ### Recruitment
-We recruited participants using the online participant recruitment service 
-*Prolific* from the University of Oxford. 
-*Prolific*'s subject pool consists of a mostly European and US-american sample 
-although subjects from all over the world are included.
-
-The recruitment platform realises ethical payment of participants, 
-which requires researchers to pay participants a fixed minimum wage  
-of £5.00 (around US$6.50 or €6.00) per hour.
-We decided to pay all participants the same fixed fee which was in relation 
-to the estimated average time taken to complete the task.
-
-*Prolific* distributed our study link to potential participants, 
-while the hosting of the online study was done by local servers in the
-Max Planck Institute for Evolutionary Anthropology, Leipzig. 
-Therefore, study data was saved only on our internal servers, 
-while *Prolific* provided demographic information of the participants.
-
+We recruited participants using the online participant recruitment service *Prolific* from the University of Oxford.
+*Prolific*'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
+The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US$6.50 or €6.00) per hour.
+We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
+*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
+Therefore, study data was saved only on our internal servers, while *Prolific* provided demographic information of the participants.
 Participants' *Prolific* ID was forwarded to our study website using URL parameters.
 This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion: 
-we redirected participants from our study website back to the *Prolific* website 
-using URL parameters.
-
-We used *Prolific*'s inbuilt prescreening filter to include 
-only participants who were fluent in English
-and could therefore properly understand our written and oral study instructions.
+The same technique was used to confirm study completion: we redirected participants from our study website back to the *Prolific* website using URL parameters.
+We used *Prolific*'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
 
 ### Study 1 - Validation hedge version
-Study 1 was pre-registered: https://osf.io/r3bhn. 
+The aim of Study 1 was to validate the hedge version of our balloon finding task.
+The pre-registration can be found here: https://osf.io/r3bhn.
 We recruited participants online by advertising the study on *Prolific*.
@@
 50 adults participated in the study.
-One additional subject returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 Data collection took place in May 2021.
@@
 
-Participants were required to complete the study on a tablet or desktop. 
-Participation on mobile devices was disabled 
-since the display would be too small and would harm click precision.
+Participants were required to complete the study on a tablet or desktop.Participation on mobile devices was disabled since the display would be too small and would harm click precision.
 It was indicated that the study required audio sound.
@@
 As in study 1, we recruited participants on *Prolific*, and employed the same methodology.
-However, this time participants were presented with the box version of the task.
-We showed eight boxes in which the target could land.
+However, this time we focussed on validating the box version of the task in an adult sample.
+Participants were presented with eight boxes in which the target could land.
 
 50 adults participated in the study.
-One additional subject returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 Data collection took place in June 2021.
@@
 ### Study 3 - Reliability hedge version
-Study 3 and study 4 were pre-registered: https://osf.io/nu62m.
-In order to assess the test-retest reliability, 
-we tested the same participants twice with a delay of two weeks.
+In study 3 and 4, we assessed the test-retest reliability of our balloon-finding task in an adult sample.
+The pre-registration can be found here: https://osf.io/nu62m.
+We tested the same participants twice with a delay of two weeks.
+The testing conditions were as specified in Study 1 and 2.
+However, the target locations as well as the succession of animals and target colors was randomized once.
+Each participant then received the same fixed randomized order of target location, animal, and target color.
+Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.
 
 In addition to the beforementioned prescreening settings, we used a whitelist.
-*Prolific* has a so-called *custom allowlist prescreening filter* 
-where one can enter the *Prolific* IDs of participants who completed a previous study. 
+*Prolific* has a so-called *custom allowlist prescreening filter* where one can enter the *Prolific* IDs of participants who completed a previous study.
 Only these subjects are then invited to participate in a study.
@@
 In a first round, 60 participants took part on the first testday.
-Additional two subjects returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
@@
 
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, 
-we reran the first testday with additional 50 participants. 
-Additional seven subjects returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
+Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study 
-(estimated average completion time 9 minutes, estimated hourly rate of £8.33). 
+Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
 In average, participants took 06:51min to complete the first part.
@@
 Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
-Again, participants were compensated with £1.50 for completing the second part of the study. 
-(estimated average completion time 9 minutes, estimated hourly rate of £10).
+Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
 In average, participants took 06:26min to complete the second part of the study.
@@
 However, this time participants were presented with the box version of the task.
+Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
 As in study 2, we employed eight boxes in which the target could land.
@@
 In a first round, 60 participants took part on the first testday.
-Additional five subjects returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 For the first testday, participants were compensated with £1.25.
@@
 
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, 
-we reran the first testday with additional 50 participants. 
-Additional eight subjects returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
+Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study 
-(estimated average completion time 9 minutes, estimated hourly rate of £8.33). 
+Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
 In average, participants took 07:37min to complete the first part.
@@
 Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
-Additional three subjects returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.50 for completing the second part of the study. 
-(estimated average completion time 9 minutes, estimated hourly rate of £10).
+Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
 In average, participants took 06:30min to complete the second part of the study.
@@
 ## Child sample
+```{r}
+library(tidyverse)
+testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
+    studyversion = factor(studyversion, levels = c("hedge", "box")), 
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "adults")), 
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
+  )
+
+kids_vali <- testtrials %>% 
+  filter(ageInYears < 6 & studytype == "vali")
+
+kids_vali_inperson_sample <- kids_vali %>%
+  filter(datacollection == "in-person - supervised") %>% 
+  group_by(ageInYears) %>%
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
+    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
+    minAgeInMonths = min(ageInMonths, na.rm = T),
+    maxAgeInMonths = max(ageInMonths, na.rm = T),
+  )
+
+# kids_vali %>% 
+#   filter(datacollection == "in-person - supervised") %>% 
+#   group_by(ageInYears, gender) %>% 
+#   summarise(
+#     n = length(unique(subjID))
+#   )
+```
+
 ### Study 1 - Validation Remote and in-person
-https://osf.io/snju6
+The validation of our task in a in-person and remote child sample can be found here: https://osf.io/snju6. 
+We chose to have at least 20 data points per cell (i.e.
+unique combination of data collection mode, study version, and age-group).
+Across the two data collection modes, a total of `r kids_vali %>% select(subjID) %>% n_distinct()` children participated.
+Participants received a small gift as thank you for their participation in the study.
+
+For our in-person supervised testing sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+For our remote unsupervised testing sample, families were recruited on a voluntary basis via email from the database of the Max Planck Institute for Evolutionary Anthropology.
+Children in both sub samples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+Written informed consent was obtained from at least one caregiver prior to testing. 
+TODO: how to phrase for kiga testing?
+
+Our in-person supervised testing sample involved `r kids_vali %>% filter(datacollection == "in-person - supervised") %>% select(subjID) %>% n_distinct()` children, including `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(nTotal)` 3-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(maxAgeInMonths)`, 22 girls), `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(nTotal)` 4-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(maxAgeInMonths)`, 19 girls), and `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(nTotal)` 5-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(maxAgeInMonths)`, 22 girls).
 

### 2022-02-14 paper/manuscript.tex
revise method section, add sample description child vali inperson

@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
 Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}
 
@@
 
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
 Idea for an opener :)
@@
 Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
-The code is open-source (\url{https://github.com/ccp-eva/gafo-demo})
-and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
 
-The web-app generates two files:
-(1) a text file (JSON) containing click responses,
-and (2) a video file (webm) of the participant's webcam recording.
+The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
 Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
 
-The web-app was programmed in Vanilla JavaScript, HTML and CSS.
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality,
-while keepiong the aspect ratio and relative object positions.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all
-composite parts of the scene (e.g., pupil of the agent).
+This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
 
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used
-to animate the movement of single SVG elements.
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
 
-Study instructions were pre-recorded and, therefore, constant across participants.
-No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-\hypertarget{procedure-from-pre-reg}{%
-\subsection{Procedure (from pre-reg)}\label{procedure-from-pre-reg}}
+In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+
+\hypertarget{stimuli}{%
+\subsection{Stimuli}\label{stimuli}}
 
@@
 The target then falls to the ground.
-The agent's gaze follows the movement of the target,
-that is, the pupils of the agent move in a way that their center aligns with the center of the target.
-Participants are then asked to locate the target's position on the screen.
+The agent's gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+Participants were then asked to locate the target's position on the screen.
 
-Visual access to the target's true location is manipulated by a hedge.
-Participants either have full, partial, or no visual access to the true target location.
-When partial or no information about the target location is accessible,
-participants are expected to use the agent's gaze as a cue.
+There are three different trial types, depending on the visual access to the target flight and end location.
+In \emph{touch training} trials, participants have \emph{full visual access} to the target flight and the target's end location.
+In \emph{familiarization trials}, participants have \emph{partial visual access}: they witness the target flight but cannot see the target's end location.
+In \emph{test trials}, participants have \emph{no visual access} to the target flight nor the end location.
+When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.
 
-There are two different versions of partial and no visual access trials.
-For families that use a tablet with touchscreen,
-the target lands behind a hedge (i.e., hedge version).
-Children are then asked to click directly on the hedge to indicate where the target is.
-For families that use a computer without touchscreen, the balloon falls into a box.
-Children are then asked to point to the box containing the target.
-Caregivers then act as the ``digital finger'' of their children and click on the indicated box.
-
-The dependent variable depends on the study version:
-For the hedge version, our dependent variable is continuous.
-Here, the dependent variable is imprecision,
-which is defined as the absolute difference between the true x coordinate of the target
-and the x coordinate of the participant's click on the screen.
-For the box version, we use our categorical outcome (i.e., which box was clicked)
-to calculate the proportion of correct responses.
-
-There are three different trial types,
-depending on the visual access to the target flight and end location.
-In touch training trials, participants have full visual access to the target flight
-and the target's end location.
-In familiarization trials, participants have visual access to the target flight
-but not to the target's end location.
-In the hedge version, the target's end location is covered by a hedge.
-In the box version, the target flies into a box and is therefore not visible anymore.
-In test trials, participants have no visual access to the target flight
-nor the end location.
-In both versions, the target flight is covered by a hedge.
+There are two different versions of partial and no visual access trials: participants have to indicate their estimated target location directly on the hedge (i.e., hedge version) or in one of five/eight boxes (i.e., box version).
+In test trials, the target flight is always covered by a hedge.
 In the hedge version, the hedge then shrinks to cover the target's end location.
@@
 
-Depending on the participant's device,
-participants have to indicate their estimated target location directly on the hedge
-(i.e., hedge version) or in one of five boxes (i.e., box version).
+To keep participants engaged and interested, the presentation of events was accompanied by cartoon-like sounds.
+Each trial started with an eye-blinking sound, while pupils and iris were enlarged and changed in opacity for 0.3 sec.~The landing of the target was accompanied by a tapping sound.
+After the response was registered, a short plop sound played and a small orange circle confirmed the participants' location choice.
+Once the target landed, the instructor's voice asked ``Where is the balloon?'' If no response was registered, an audio prompt reminded the participant to respond and click on the balloon/the hedge/a box.
 
-Participants receive 19 trials with one touch training, two familiarization trials,
+Study instructions were pre-recorded and constant across participants.
+No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
+Participants received 19 trials with one touch training, two familiarization trials,
 and 16 test trials.
-The first trial of each type comprises a voice-over description of the presented events.
-Touch and familiarization trials, as well as voice-over trials, will not be included in the analysis.
-Therefore, we will conduct our analysis with 15 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+Touch and familiarization trials, as well as voice-over trials, were not included in the analysis.
+Therefore, we conducted our analyses with 15 test trials.
 
-Target locations are generated as follows.
-For the hedge version, the full width of the screen is divided into ten bins.
-Exact coordinates within each bin are randomly generated.
-For the box version, the target randomly lands in one out of five boxes.
-Each bin/box occurs equally often.
-The same bin/box can occur only twice in a row.
+\hypertarget{dependent-variable}{%
+\subsubsection{Dependent variable}\label{dependent-variable}}
+
+The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant's click on the screen.
+For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+
+\hypertarget{remote-datacollection}{%
+\subsubsection{Remote datacollection}\label{remote-datacollection}}
+
+Depending on the participant's device, the website automatically presents the hedge or box version of the study.
+For families that use a tablet with touchscreen, the hedge version is shown.
+Here, children can directly click on the screen themselves to indicate where the target is.
+For families that use a computer without touchscreen, the website presents the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
+In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
+
+\hypertarget{randomization}{%
+\subsubsection{Randomization}\label{randomization}}
+
+All agents and target colors appeared equally often and could not be repeated in more than two consecutive trials.
+The randomization of the target end location depended on the study version.
+In the hedge version, the full width of the screen was divided into ten bins.
+Exact coordinates within each bin were randomly generated.
+In the box version, the target randomly landed in one of the boxes.
+Each bin/box occurred equally often.
+The same bin/box could only occur twice in a row.
 
@@
 The web application (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) described here is open source (\url{https://github.com/ccp-eva/gafo-demo}).
-The datasets generated during and/or analysed during the current study are available
-in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
+The datasets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
 All experiments were preregistered (\url{https://osf.io/zjhsc/}).
@@
 
-optional: please review the submission guidelines from the
-journal whether statements are mandatory
+optional: please review the submission guidelines from the journal whether statements are mandatory
 
@@
 
-We recruited participants using the online participant recruitment service
-\emph{Prolific} from the University of Oxford.
-\emph{Prolific}'s subject pool consists of a mostly European and US-american sample
-although subjects from all over the world are included.
-
-The recruitment platform realises ethical payment of participants,
-which requires researchers to pay participants a fixed minimum wage\\
-of £5.00 (around US\$6.50 or €6.00) per hour.
-We decided to pay all participants the same fixed fee which was in relation
-to the estimated average time taken to complete the task.
-
-\emph{Prolific} distributed our study link to potential participants,
-while the hosting of the online study was done by local servers in the
-Max Planck Institute for Evolutionary Anthropology, Leipzig.
-Therefore, study data was saved only on our internal servers,
-while \emph{Prolific} provided demographic information of the participants.
-
+We recruited participants using the online participant recruitment service \emph{Prolific} from the University of Oxford.
+\emph{Prolific}'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
+The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
+We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
+\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
+Therefore, study data was saved only on our internal servers, while \emph{Prolific} provided demographic information of the participants.
 Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
 This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion:
-we redirected participants from our study website back to the \emph{Prolific} website
-using URL parameters.
-
-We used \emph{Prolific}'s inbuilt prescreening filter to include
-only participants who were fluent in English
-and could therefore properly understand our written and oral study instructions.
+The same technique was used to confirm study completion: we redirected participants from our study website back to the \emph{Prolific} website using URL parameters.
+We used \emph{Prolific}'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
 
@@
 
+The aim of Study 1 was to validate the hedge version of our balloon finding task.
+The pre-registration can be found here: \url{https://osf.io/r3bhn}.
 We recruited participants online by advertising the study on \emph{Prolific}.
@@
 
-Participants were required to complete the study on a tablet or desktop.
-Participation on mobile devices was disabled
-since the display would be too small and would harm click precision.
+Participants were required to complete the study on a tablet or desktop.Participation on mobile devices was disabled since the display would be too small and would harm click precision.
 It was indicated that the study required audio sound.
@@
 As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
-However, this time participants were presented with the box version of the task.
-We showed eight boxes in which the target could land.
+However, this time we focussed on validating the box version of the task in an adult sample.
+Participants were presented with eight boxes in which the target could land.
 
 50 adults participated in the study.
-One additional subject returned their submission,
-i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
 Data collection took place in June 2021.
@@
 
+In study 3 and 4, we assessed the test-retest reliability of our balloon-finding task in an adult sample.
+The pre-registration can be found here: \url{https://osf.io/nu62m}.
+We tested the same participants twice with a delay of two weeks.
+The testing conditions were as specified in Study 1 and 2.
+However, the target locations as well as the succession of animals and target colors was randomized once.
+Each participant then received the same fixed randomized order of target location, animal, and target color.
+Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.
+
 In addition to the beforementioned prescreening settings, we used a whitelist.
+\emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
+Only these subjects are then invited to participate in a study.
+This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.
 
-whitelist screener:
-``When the researcher uses a whitelist,
-only participants with IDs entered into the whitelist are invited to participate in a study.
-This allows gathering information from the same subjects at different points in time.''
+In a first round, 60 participants took part on the first testday.
+Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+The maximum time is calculated by \emph{Prolific}, based on the estimated average completion time.
+For this study, the maximum time amounted to 41 minutes.
+For the first testday, participants were compensated with £1.25.
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
+In average, participants took 07:11min to complete the first part.
+
+Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Participants were compensated with £1.50 for completing the second part of the study.
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
+In average, participants took 06:36min to complete the second part of the study.
+
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
+Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
+Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
+In average, participants took 06:51min to complete the first part.
+
+Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
+Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
+In average, participants took 06:26min to complete the second part of the study.
 
@@
 However, this time participants were presented with the box version of the task.
+Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
 As in study 2, we employed eight boxes in which the target could land.
 
+In a first round, 60 participants took part on the first testday.
+Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
+For the first testday, participants were compensated with £1.25.
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
+In average, participants took 07:33min to complete the first part.
+
+Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
+Participants were compensated with £1.50 for completing the second part of the study.
+We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
+In average, participants took 07:50min to complete the second part of the study.
+
+Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
+Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
+In average, participants took 07:37min to complete the first part.
+
+Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
+Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
+One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
+Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
+In average, participants took 06:30min to complete the second part of the study.
+
+\hypertarget{child-sample}{%
+\subsection{Child sample}\label{child-sample}}
+
+\hypertarget{study-1---validation-remote-and-in-person}{%
+\subsubsection{Study 1 - Validation Remote and in-person}\label{study-1---validation-remote-and-in-person}}
+
+The validation of our task in a in-person and remote child sample can be found here: \url{https://osf.io/snju6}.
+We chose to have at least 20 data points per cell (i.e.~unique combination of data collection mode, study version, and age-group).
+Across the two data collection modes, a total of 267 children participated.
+Participants received a small gift as thank you for their participation in the study.
+
+For our in-person supervised testing sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+For our remote unsupervised testing sample, families were recruited on a voluntary basis via email from the database of the Max Planck Institute for Evolutionary Anthropology.
+Children in both sub samples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+Written informed consent was obtained from at least one caregiver prior to testing.
+TODO: how to phrase for kiga testing?
+
+Our in-person supervised testing sample involved 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.6 months, SD = 3.1, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).
+
+\hypertarget{study-2---reliability-in-person}{%
+\subsubsection{Study 2 - Reliability in-person}\label{study-2---reliability-in-person}}
+
+\url{https://osf.io/xqm73}
+
 \end{document}

### 2022-02-18 paper/manuscript.Rmd
create rough paper structure

@@
 
+\newpage
+
+# -- POSSIBLE ROUGH STRUCTURE -- 
+# intro
+## individual differences in dev psy
+- reliable tasks: need variation, more trials
+
+## exisiting tasks for social cognition
+- wellman
+
+## current goal
+- standardized, easy to use, continuous
+
+# methods (let's see whether we want this generic heading...)
+## design of our task
+- training trials (touch & fam together, click on visible balloon / visible target flight, voice over trials)
+- test trials
+- flexible: two versions, can also use discrete
+- face value
+
+- stimulus timing
+
+## implementation / development
+- JS, HTML, CSS
+- parcel?!
+- SVG: scalable
+- webapp: portable across devices, flexible, no hard system requirements
+- response collection: file format, variables saved (click responses)
+
+## data processing
+- workflow for collecting data
+- pipeline? downloading server data into r, coverting coordinate systems
+
+# does our task induce variation?
+## participants: kiga & prolific vali
+## procedure 
+## results
+- for hedge & box
+- sanity check: developmental trajectory
+- remote testing: online child sample as side note
+
+# do we capture variation reliably?
+## participants: relikiga & prolific reli
+## results: 
+- internal consistency?
+- test-retest
+
+# exploratory: external validity
+## participants: subsample kiga & relikiga with questionnaire data
+## results: 
+- peer exposure (box & hedge combined?)
+
+# discussion
+## limitations
+## future development / extending the task
+# conclusion
+
+\newpage
 # Introduction 
@@
 
+- individual differences in developmental psychology
+- reliable tasks, variation needed, more trials
+- existing tasks for social cognition: wellman
+- goal of the current project
+
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-## Participants
-
-## Material
-Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
-The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
-
-The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
-
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
-
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
-
-## Procedure
-In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+## Design of our balloon finding task
+- training trials (summarize touch & fam & voice over)
+- test trials in detail
+- two versions: continuous & discrete, flexible to use
 
 ## Stimuli
+# TODO: cartoon style stimuli. engaging and for children and adults alike
+
 An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
@@
 
+# TODO: phrasing training trials
 There are three different trial types, depending on the visual access to the target flight and end location.
@@
 
-### Dependent variable
-The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant’s click on the screen.
-For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
-
-### Remote datacollection
-Depending on the participant's device, the website automatically presents the hedge or box version of the study.
-For families that use a tablet with touchscreen, the hedge version is shown.
-Here, children can directly click on the screen themselves to indicate where the target is.
-For families that use a computer without touchscreen, the website presents the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
-In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
 ### Randomization
@@
 
-## Data analysis
+### Dependent variable
+The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant’s click on the screen.
+For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+
+## Implementation
+- Parcel?
+- benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
+- response collection: file formats, information we save
+
+Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
+
+The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
+
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
+
+## Data processing
+- workflow server to R, converting coordinate systems
 We used `r cite_r("r-references.bib")` for all our analyses.
 
-# Results
+# Does the balloon finding task induce variation?
+## Participants: kiga & prolific vali
+## Procedure
+## Results
+- for hedge & box
+- sanity check: developmental trajectory
+- remote testing: online child sample as side note
+
+# Can we capture variation reliably?
+## Participants: religa kiga & prolific reli
+## Procedure: 14 ± 3 days
+- what is different compared to variation? nr of trials, fixed order
+## Results
+- internal consistency
+- test-retest
+
+# Exploring the external validity of our task
+## Participants: subset kiga & relikiga that filled out questionnaires
+## Results
+- peer exposure (hedge & box combined?)
 
 # Discussion
+## Limitations
+## Future development / extending the task
+
+# Conclusion
 
@@
 
+## Procedure Remote Testing
+In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+
+Depending on the participant's device, the website automatically presents the hedge or box version of the study.
+For families that use a tablet with touchscreen, the hedge version is shown.
+Here, children can directly click on the screen themselves to indicate where the target is.
+For families that use a computer without touchscreen, the website presents the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
+In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
+
 Our in-person supervised testing sample involved `r kids_vali %>% filter(datacollection == "in-person - supervised") %>% select(subjID) %>% n_distinct()` children, including `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(nTotal)` 3-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(maxAgeInMonths)`, 22 girls), `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(nTotal)` 4-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(maxAgeInMonths)`, 19 girls), and `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(nTotal)` 5-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(maxAgeInMonths)`, 22 girls).

### 2022-02-18 paper/manuscript.tex
create rough paper structure

@@
 
+\newpage
+
+\hypertarget{possible-rough-structure}{%
+\section{-- POSSIBLE ROUGH STRUCTURE --}\label{possible-rough-structure}}
+
+\hypertarget{intro}{%
+\section{intro}\label{intro}}
+
+\hypertarget{individual-differences-in-dev-psy}{%
+\subsection{individual differences in dev psy}\label{individual-differences-in-dev-psy}}
+
+\begin{itemize}
+\tightlist
+\item
+  reliable tasks: need variation, more trials
+\end{itemize}
+
+\hypertarget{exisiting-tasks-for-social-cognition}{%
+\subsection{exisiting tasks for social cognition}\label{exisiting-tasks-for-social-cognition}}
+
+\begin{itemize}
+\tightlist
+\item
+  wellman
+\end{itemize}
+
+\hypertarget{current-goal}{%
+\subsection{current goal}\label{current-goal}}
+
+\begin{itemize}
+\tightlist
+\item
+  standardized, easy to use, continuous
+\end{itemize}
+
+\hypertarget{methods-lets-see-whether-we-want-this-generic-heading}{%
+\section{methods (let's see whether we want this generic heading\ldots)}\label{methods-lets-see-whether-we-want-this-generic-heading}}
+
+\hypertarget{design-of-our-task}{%
+\subsection{design of our task}\label{design-of-our-task}}
+
+\begin{itemize}
+\item
+  training trials (touch \& fam together, click on visible balloon / visible target flight, voice over trials)
+\item
+  test trials
+\item
+  flexible: two versions, can also use discrete
+\item
+  face value
+\item
+  stimulus timing
+\end{itemize}
+
+\hypertarget{implementation-development}{%
+\subsection{implementation / development}\label{implementation-development}}
+
+\begin{itemize}
+\tightlist
+\item
+  JS, HTML, CSS
+\item
+  parcel?!
+\item
+  SVG: scalable
+\item
+  webapp: portable across devices, flexible, no hard system requirements
+\item
+  response collection: file format, variables saved (click responses)
+\end{itemize}
+
+\hypertarget{data-processing}{%
+\subsection{data processing}\label{data-processing}}
+
+\begin{itemize}
+\tightlist
+\item
+  workflow for collecting data
+\item
+  pipeline? downloading server data into r, coverting coordinate systems
+\end{itemize}
+
+\hypertarget{does-our-task-induce-variation}{%
+\section{does our task induce variation?}\label{does-our-task-induce-variation}}
+
+\hypertarget{participants-kiga-prolific-vali}{%
+\subsection{participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali}}
+
+\hypertarget{procedure}{%
+\subsection{procedure}\label{procedure}}
+
+\hypertarget{results}{%
+\subsection{results}\label{results}}
+
+\begin{itemize}
+\tightlist
+\item
+  for hedge \& box
+\item
+  sanity check: developmental trajectory
+\item
+  remote testing: online child sample as side note
+\end{itemize}
+
+\hypertarget{do-we-capture-variation-reliably}{%
+\section{do we capture variation reliably?}\label{do-we-capture-variation-reliably}}
+
+\hypertarget{participants-relikiga-prolific-reli}{%
+\subsection{participants: relikiga \& prolific reli}\label{participants-relikiga-prolific-reli}}
+
+\hypertarget{results-1}{%
+\subsection{results:}\label{results-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  internal consistency?
+\item
+  test-retest
+\end{itemize}
+
+\hypertarget{exploratory-external-validity}{%
+\section{exploratory: external validity}\label{exploratory-external-validity}}
+
+\hypertarget{participants-subsample-kiga-relikiga-with-questionnaire-data}{%
+\subsection{participants: subsample kiga \& relikiga with questionnaire data}\label{participants-subsample-kiga-relikiga-with-questionnaire-data}}
+
+\hypertarget{results-2}{%
+\subsection{results:}\label{results-2}}
+
+\begin{itemize}
+\tightlist
+\item
+  peer exposure (box \& hedge combined?)
+\end{itemize}
+
+\hypertarget{discussion}{%
+\section{discussion}\label{discussion}}
+
+\hypertarget{limitations}{%
+\subsection{limitations}\label{limitations}}
+
+\hypertarget{future-development-extending-the-task}{%
+\subsection{future development / extending the task}\label{future-development-extending-the-task}}
+
+\hypertarget{conclusion}{%
+\section{conclusion}\label{conclusion}}
+
+\newpage
+
 \hypertarget{introduction}{%
@@
 
+\begin{itemize}
+\tightlist
+\item
+  individual differences in developmental psychology
+\item
+  reliable tasks, variation needed, more trials
+\item
+  existing tasks for social cognition: wellman
+\item
+  goal of the current project
+\end{itemize}
+
 \hypertarget{methods}{%
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+\hypertarget{design-of-our-balloon-finding-task}{%
+\subsection{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
-
-Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
-The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
-
-The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
-
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
-
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+\begin{itemize}
+\tightlist
+\item
+  training trials (summarize touch \& fam \& voice over)
+\item
+  test trials in detail
+\item
+  two versions: continuous \& discrete, flexible to use
+\end{itemize}
 
@@
 \subsection{Stimuli}\label{stimuli}}
+
+\hypertarget{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}{%
+\section{TODO: cartoon style stimuli. engaging and for children and adults alike}\label{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}}
 
@@
 Participants were then asked to locate the target's position on the screen.
+
+\hypertarget{todo-phrasing-training-trials}{%
+\section{TODO: phrasing training trials}\label{todo-phrasing-training-trials}}
 
@@
 
-\hypertarget{dependent-variable}{%
-\subsubsection{Dependent variable}\label{dependent-variable}}
-
-The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant's click on the screen.
-For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
-
-\hypertarget{remote-datacollection}{%
-\subsubsection{Remote datacollection}\label{remote-datacollection}}
-
-Depending on the participant's device, the website automatically presents the hedge or box version of the study.
-For families that use a tablet with touchscreen, the hedge version is shown.
-Here, children can directly click on the screen themselves to indicate where the target is.
-For families that use a computer without touchscreen, the website presents the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
-In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
 \hypertarget{randomization}{%
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\hypertarget{dependent-variable}{%
+\subsubsection{Dependent variable}\label{dependent-variable}}
 
+The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant's click on the screen.
+For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+
+\hypertarget{implementation}{%
+\subsection{Implementation}\label{implementation}}
+
+\begin{itemize}
+\tightlist
+\item
+  Parcel?
+\item
+  benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
+\item
+  response collection: file formats, information we save
+\end{itemize}
+
+Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+
+The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
+
+The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
+
+\hypertarget{data-processing-1}{%
+\subsection{Data processing}\label{data-processing-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  workflow server to R, converting coordinate systems
   We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
+\end{itemize}
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{does-the-balloon-finding-task-induce-variation}{%
+\section{Does the balloon finding task induce variation?}\label{does-the-balloon-finding-task-induce-variation}}
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{participants-kiga-prolific-vali-1}{%
+\subsection{Participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali-1}}
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
+\hypertarget{results-3}{%
+\subsection{Results}\label{results-3}}
+
+\begin{itemize}
+\tightlist
+\item
+  for hedge \& box
+\item
+  sanity check: developmental trajectory
+\item
+  remote testing: online child sample as side note
+\end{itemize}
+
+\hypertarget{can-we-capture-variation-reliably}{%
+\section{Can we capture variation reliably?}\label{can-we-capture-variation-reliably}}
+
+\hypertarget{participants-religa-kiga-prolific-reli}{%
+\subsection{Participants: religa kiga \& prolific reli}\label{participants-religa-kiga-prolific-reli}}
+
+\hypertarget{procedure-14-3-days}{%
+\subsection{Procedure: 14 ± 3 days}\label{procedure-14-3-days}}
+
+\begin{itemize}
+\tightlist
+\item
+  what is different compared to variation? nr of trials, fixed order
+  \#\# Results
+\item
+  internal consistency
+\item
+  test-retest
+\end{itemize}
+
+\hypertarget{exploring-the-external-validity-of-our-task}{%
+\section{Exploring the external validity of our task}\label{exploring-the-external-validity-of-our-task}}
+
+\hypertarget{participants-subset-kiga-relikiga-that-filled-out-questionnaires}{%
+\subsection{Participants: subset kiga \& relikiga that filled out questionnaires}\label{participants-subset-kiga-relikiga-that-filled-out-questionnaires}}
+
+\hypertarget{results-4}{%
+\subsection{Results}\label{results-4}}
+
+\begin{itemize}
+\tightlist
+\item
+  peer exposure (hedge \& box combined?)
+\end{itemize}
+
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
+
+\hypertarget{limitations-1}{%
+\subsection{Limitations}\label{limitations-1}}
+
+\hypertarget{future-development-extending-the-task-1}{%
+\subsection{Future development / extending the task}\label{future-development-extending-the-task-1}}
+
+\hypertarget{conclusion-1}{%
+\section{Conclusion}\label{conclusion-1}}
 
@@
 
+\hypertarget{procedure-remote-testing}{%
+\subsection{Procedure Remote Testing}\label{procedure-remote-testing}}
+
+In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+
+Depending on the participant's device, the website automatically presents the hedge or box version of the study.
+For families that use a tablet with touchscreen, the hedge version is shown.
+Here, children can directly click on the screen themselves to indicate where the target is.
+For families that use a computer without touchscreen, the website presents the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
+In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
+
 Our in-person supervised testing sample involved 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.6 months, SD = 3.1, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).

### 2022-02-18 paper/manuscript.Rmd
revise task design section

@@
 
-# Methods
-## Design of our balloon finding task
-- training trials (summarize touch & fam & voice over)
-- test trials in detail
-- two versions: continuous & discrete, flexible to use
+# Design of our balloon finding task
 
 ## Stimuli
-# TODO: cartoon style stimuli. engaging and for children and adults alike
-
+Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike.
 An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
@@
 The target then falls to the ground.
-The agent’s gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
-Participants were then asked to locate the target’s position on the screen.
+At all times, the agent’s gaze tracks the movement of the target.
+That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+Participants are then asked to locate the target’s position on the screen.
 
-# TODO: phrasing training trials
-There are three different trial types, depending on the visual access to the target flight and end location.
-In *touch training* trials, participants have *full visual access* to the target flight and the target's end location.
-In *familiarization trials*, participants have *partial visual access*: they witness the target flight but cannot see the target's end location.
-In *test trials*, participants have *no visual access* to the target flight nor the end location.
-When partial or no information about the target location is accessible,  participants are expected to use the agent’s gaze as a cue.
+To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like sounds.
+Each trial starts with an eye-blinking sound, while pupils and iris get slightly enlarged and change in opacity for 0.3 sec.
+The landing of the target is accompanied by a tapping sound.
+Once the target landed, the instructor's voice asks "Where is the balloon?".
+After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
+If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
 
-There are two different versions of partial and no visual access trials: participants have to indicate their estimated target location directly on the hedge (i.e., hedge version) or in one of five/eight boxes (i.e., box version).
-In test trials, the target flight is always covered by a hedge.
-In the hedge version, the hedge then shrinks to cover the target's end location.
-In the box version, the hedge shrinks completely.
-The boxes then hide the target's end location.
+## Trials
+Before participants advance to the test trials, there are four training trials.
+In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
+In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location.
+They are then asked to click on the invisible balloon, i.e., the location where they saw the target land.
+In test trials, participants have no visual access to the target flight nor the end location.
+Participants are expected to use the agent’s gaze as a cue to locate the target.
+The first trial of each type comprises a voice-over description of the presented events.
+After these four training and audio guided trials, participants receive 15 test trials.
+The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes testing time.
 
-To keep participants engaged and interested, the presentation of events was accompanied by cartoon-like sounds.
-Each trial started with an eye-blinking sound, while pupils and iris were enlarged and changed in opacity for 0.3 sec.
-The landing of the target was accompanied by a tapping sound.
-After the response was registered, a short plop sound played and a small orange circle confirmed the participants' location choice.
-Once the target landed, the instructor's voice asked "Where is the balloon?".
-If no response was registered, an audio prompt reminded the participant to respond and click on the balloon/the hedge/a box.
+## Study versions
+We designed two study versions which can be chosen according to the researchers' need: there is a continuous *hedge* version and a discrete *box* version.
+The versions use the same first training trial and then differ in the two consecutive training trials and the test trials.
+In the *hedge* version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant’s click.
+In the *box* version, participants are asked to click on a box that hides the target.
+Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
+Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+Note that in the test trials of both study versions, the target flight is covered by a hedge.
+In the *hedge* version, the hedge then shrinks to a minimum height required to cover the target's end location.
+In the *box* version, the hedge shrinks completely.
+The boxes then hide the target's final destination.
 
-Study instructions were pre-recorded and constant across participants.
-No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
-Participants received 19 trials with one touch training, two familiarization trials,
-and 16 test trials.
-The first trial of each type comprised a voice-over description of the presented events.
-Touch and familiarization trials, as well as voice-over trials, were not included in the analysis.
-Therefore, we conducted our analyses with 15 test trials.
-
-### Randomization
-All agents and target colors appeared equally often and could not be repeated in more than two consecutive trials.
-The randomization of the target end location depended on the study version.
-In the hedge version, the full width of the screen was divided into ten bins.
-Exact coordinates within each bin were randomly generated.
-In the box version, the target randomly landed in one of the boxes.
-Each bin/box occurred equally often.
-The same bin/box could only occur twice in a row.
-
-### Dependent variable
-The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant’s click on the screen.
-For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+## Randomization
+All agents and target colors appear equally often and are not repeated in more than two consecutive trials.
+The randomization of the target end location depends on the study version.
+In the *hedge* version, the full width of the screen is divided into ten bins.
+Exact coordinates within each bin are then randomly generated.
+In the *box* version, the target randomly lands in one of the boxes.
+As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.
 
 ## Implementation
-- Parcel?
-- benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
-- response collection: file formats, information we save
-
-Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+Our balloon finding task is presented as an interactive web-app.
+This way, the task is portable across devices and web browsers and does not require any installation.
+A great advantage of online testing is that our testing procedure is standardized across participants.
+Study instructions were pre-recorded and no interaction with the experimenter is necessary during the study.
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
 
-The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
+For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
+For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used. 
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
+This is needed for precisely calculating exact pupil and target locations and sizes.
+Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
+The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements.
 
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
-
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
+The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany.
+Data got automatically collected and safely stored on these in-house servers.
+If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
 

### 2022-02-18 paper/manuscript.tex
revise task design section

@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
 \hypertarget{design-of-our-balloon-finding-task}{%
-\subsection{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}
-
-\begin{itemize}
-\tightlist
-\item
-  training trials (summarize touch \& fam \& voice over)
-\item
-  test trials in detail
-\item
-  two versions: continuous \& discrete, flexible to use
-\end{itemize}
+\section{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}
 
@@
 
-\hypertarget{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}{%
-\section{TODO: cartoon style stimuli. engaging and for children and adults alike}\label{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}}
-
+Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike.
 An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
@@
 The target then falls to the ground.
-The agent's gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
-Participants were then asked to locate the target's position on the screen.
+At all times, the agent's gaze tracks the movement of the target.
+That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+Participants are then asked to locate the target's position on the screen.
 
-\hypertarget{todo-phrasing-training-trials}{%
-\section{TODO: phrasing training trials}\label{todo-phrasing-training-trials}}
+To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like sounds.
+Each trial starts with an eye-blinking sound, while pupils and iris get slightly enlarged and change in opacity for 0.3 sec.~The landing of the target is accompanied by a tapping sound.
+Once the target landed, the instructor's voice asks ``Where is the balloon?'' After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
+If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
 
-There are three different trial types, depending on the visual access to the target flight and end location.
-In \emph{touch training} trials, participants have \emph{full visual access} to the target flight and the target's end location.
-In \emph{familiarization trials}, participants have \emph{partial visual access}: they witness the target flight but cannot see the target's end location.
-In \emph{test trials}, participants have \emph{no visual access} to the target flight nor the end location.
-When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.
+\hypertarget{trials}{%
+\subsection{Trials}\label{trials}}
 
-There are two different versions of partial and no visual access trials: participants have to indicate their estimated target location directly on the hedge (i.e., hedge version) or in one of five/eight boxes (i.e., box version).
-In test trials, the target flight is always covered by a hedge.
-In the hedge version, the hedge then shrinks to cover the target's end location.
-In the box version, the hedge shrinks completely.
-The boxes then hide the target's end location.
+Before participants advance to the test trials, there are four training trials.
+In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
+In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location.
+They are then asked to click on the invisible balloon, i.e., the location where they saw the target land.
+In test trials, participants have no visual access to the target flight nor the end location.
+Participants are expected to use the agent's gaze as a cue to locate the target.
+The first trial of each type comprises a voice-over description of the presented events.
+After these four training and audio guided trials, participants receive 15 test trials.
+The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes testing time.
 
-To keep participants engaged and interested, the presentation of events was accompanied by cartoon-like sounds.
-Each trial started with an eye-blinking sound, while pupils and iris were enlarged and changed in opacity for 0.3 sec.~The landing of the target was accompanied by a tapping sound.
-After the response was registered, a short plop sound played and a small orange circle confirmed the participants' location choice.
-Once the target landed, the instructor's voice asked ``Where is the balloon?'' If no response was registered, an audio prompt reminded the participant to respond and click on the balloon/the hedge/a box.
+\hypertarget{study-versions}{%
+\subsection{Study versions}\label{study-versions}}
 
-Study instructions were pre-recorded and constant across participants.
-No interaction with the experimenter was necessary and children needed minimal assistance from their caregivers.
-Participants received 19 trials with one touch training, two familiarization trials,
-and 16 test trials.
-The first trial of each type comprised a voice-over description of the presented events.
-Touch and familiarization trials, as well as voice-over trials, were not included in the analysis.
-Therefore, we conducted our analyses with 15 test trials.
+We designed two study versions which can be chosen according to the researchers' need: there is a continuous \emph{hedge} version and a discrete \emph{box} version.
+The versions use the same first training trial and then differ in the two consecutive training trials and the test trials.
+In the \emph{hedge} version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version).
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant's click.
+In the \emph{box} version, participants are asked to click on a box that hides the target.
+Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
+Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+Note that in the test trials of both study versions, the target flight is covered by a hedge.
+In the \emph{hedge} version, the hedge then shrinks to a minimum height required to cover the target's end location.
+In the \emph{box} version, the hedge shrinks completely.
+The boxes then hide the target's final destination.
 
 \hypertarget{randomization}{%
-\subsubsection{Randomization}\label{randomization}}
+\subsection{Randomization}\label{randomization}}
 
-All agents and target colors appeared equally often and could not be repeated in more than two consecutive trials.
-The randomization of the target end location depended on the study version.
-In the hedge version, the full width of the screen was divided into ten bins.
-Exact coordinates within each bin were randomly generated.
-In the box version, the target randomly landed in one of the boxes.
-Each bin/box occurred equally often.
-The same bin/box could only occur twice in a row.
-
-\hypertarget{dependent-variable}{%
-\subsubsection{Dependent variable}\label{dependent-variable}}
-
-The dependent variable depends on the study version: for the hedge version, our dependent variable is continuous.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the true x coordinate of the target and the x coordinate of the participant's click on the screen.
-For the box version, we use our categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
+All agents and target colors appear equally often and are not repeated in more than two consecutive trials.
+The randomization of the target end location depends on the study version.
+In the \emph{hedge} version, the full width of the screen is divided into ten bins.
+Exact coordinates within each bin are then randomly generated.
+In the \emph{box} version, the target randomly lands in one of the boxes.
+As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Parcel?
-\item
-  benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
-\item
-  response collection: file formats, information we save
-\end{itemize}
-
-Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser.
+Our balloon finding task is presented as an interactive web-app.
+This way, the task is portable across devices and web browsers and does not require any installation.
+A great advantage of online testing is that our testing procedure is standardized across participants.
+Study instructions were pre-recorded and no interaction with the experimenter is necessary during the study.
 The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
 
-The web-app generates two files: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-Data gets automatically collected and safely stored on local servers located in Leipzig, Germany.
+The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP.
+For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
+For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
+This is needed for precisely calculating exact pupil and target locations and sizes.
+Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
+The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements.
 
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5 and CSS.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to precisely control and calculate the size and position of all composite parts of the scene (e.g., pupil of the agent).
-
-The GreenSock Animation Platform (GSAP; TODO insert citation) library was used to animate the movement of single SVG elements.
+The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany.
+Data got automatically collected and safely stored on these in-house servers.
+If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
 

### 2022-02-21 paper/manuscript.Rmd
add setup pictures

@@
 That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+While the distance of the target's flight depends on the final location, the target moves at a constant speed.
 Participants are then asked to locate the target’s position on the screen.
 
-To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like sounds.
-Each trial starts with an eye-blinking sound, while pupils and iris get slightly enlarged and change in opacity for 0.3 sec.
+To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
+Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec.
 The landing of the target is accompanied by a tapping sound.
@@
 ## Trials
-Before participants advance to the test trials, there are four training trials.
+Before participants advance to the test trials, we present four training trials.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 The first trial of each type comprises a voice-over description of the presented events.
+The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script).
 After these four training and audio guided trials, participants receive 15 test trials.
-The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes testing time.
+The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.
 
@@
 We designed two study versions which can be chosen according to the researchers' need: there is a continuous *hedge* version and a discrete *box* version.
-The versions use the same first training trial and then differ in the two consecutive training trials and the test trials.
+Both versions use the same first training trial and then differ in the consecutive training and test trials.
 In the *hedge* version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
@@
 The boxes then hide the target's final destination.
+(ref:figlab1) **Study versions of the balloon finding task**.
+(a) Screenshots from the continuous *hedge* version of the task.
+(b) Screenshots from the discrete *box* version of the task.
+(i) The agent stands in a window with the target in front of them.
+(ii) A hedge grows and covers the target.
+(iii) The target falls to a random location on the ground / into a box.
+The agent's eyes track the movement of the target.
+
+```{r fig1, fig.show = "hold", out.width = "100%", fig.align = "default", fig.cap = "(ref:figlab1)",}
+# {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
+knitr::include_graphics(c("../figures/gafo_hedge.png", "../figures/gafo_boxes.png"))
+```
 
@@
 Our balloon finding task is presented as an interactive web-app.
-This way, the task is portable across devices and web browsers and does not require any installation.
+The task is portable across devices and web browsers and does not require any installation.
 A great advantage of online testing is that our testing procedure is standardized across participants.
-Study instructions were pre-recorded and no interaction with the experimenter is necessary during the study.
+By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study.
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
@@
 If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
+
+(ref:figlab2) **Infrastructure for online testing**.
+With our new infrastructure, subjects aged 3 – 99+ can participate.
+Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
+Our task is presented as a website that works across devices.
+The scripts for the website and recorded data are stored on secure local servers.
+```{r fig2, out.width="100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/infrastructure.png")
+```
 
@@
 
+```{r}
+# test papajas apa tables
+apa_table(kids_vali_inperson_sample, 
+          caption = "Child sample", 
+          note = "in-person supervised testing", 
+          # align = c("l", "r", "c"), 
+          escape = FALSE, 
+          row.names = TRUE, 
+          placement = "h")
+```
+
 ### Study 2 - Reliability in-person 
 https://osf.io/xqm73
+
+# Instructions and voice over descriptions
+This is the content of our voice recordings. Children listen to this during the game.
+
+|     |     |     |     |     |
+| --- | --- | --- | --- | --- |
+| **Nr** | **Timeline** | **German** | **English** | **Filename** |
+| **1** | **welcome** | Hallo!
+Schön, dass du da bist.
+Wir spielen jetzt das Ballon-Spiel!
+Siehst du die Tiere auf dem Bild da?
+Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen.
+Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
+| Hello!
+Great that you’re here.
+We’ll now play a balloon game.
+Can you see the animals in the picture over there?
+We want to play together with the animals using the balloon.
+We’ll now talk you through exactly what will happen.
+| welcome.mp3 |
+| **2** | **touch** | Schau mal, da steht ein Tier im Fenster.
+Und siehst du den Ballon da?
+Der Ballon fällt immer runter und landet auf dem Boden.
+Und du musst ihn dann finden.
+Das Tier hilft Dir und schaut immer den Ballon an.
+| Look, an animal is standing in the window.
+And can you see the balloon over there?
+The balloon always falls down and lands on the ground.
+And you have to find it!
+The animal helps you and always looks at the balloon.
+| touch-1.mp3 |
+| **3** |     | Wo ist der Ballon? Drück auf den Ballon! | Where is the balloon? Click on the balloon! | prompt-touch-long.mp3 |
+| **4** | **fam - HEDGE** | Klasse, das war super!
+Jetzt spielen wir weiter.
+Siehst du wieder das Tier und den Ballon da?
+Der Ballon fällt wieder runter.
+Diesmal fällt er hinter eine Hecke.
+Du musst ihn wieder finden.
+Das Tier hilft dir und schaut immer den Ballon an.
+| Perfect, that was great!
+Now, we’ll continue playing.
+Can you see the animal and the balloon again?
+The balloon will fall down again.
+This time, it will fall behind a hedge.
+And you have to find it!
+The animal helps you and looks at the balloon.
+| fam-hedge-1.mp3 |
+| **5** |     | Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. | Where is the balloon? On the hedge, click where the balloon is. | prompt-hedge-long.mp3 |
+| **6** | **fam - BOX** | Klasse, das war super!
+Jetzt spielen wir weiter.
+Siehst du wieder das Tier und den Ballon da?
+Der Ballon fällt wieder runter.
+Diesmal fällt er in eine Kiste.
+<br>Du musst ihn wieder finden.
+Das Tier hilft dir und schaut immer den Ballon an.
+| Perfect, that was great!
+Now, we’ll continue playing.
+Can you see the animal and the balloon again?
+The balloon falls down again.
+This time, it falls into a box.
+And you have to find it!
+The animal helps you and looks at the balloon.
+| fam-box-1.mp3 |
+| **7** |     | Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. | Where is the balloon? Click on the box with the balloon. | prompt-box-long.mp3 |
+| **8** | **test - HEDGE** | Klasse , das hast du toll gemacht!
+Nun spielen wir weiter.
+Da sind wieder der Ballon, das Tier und die Hecke.
+Die Hecke wächst jetzt hoch.
+| Nice, good job!
+Now, we’ll continue playing.
+There is the balloon, the animal and the hedge.
+The hedge is growing a bit now.
+| test-hedge-1.mp3 |
+| **9** |     | Der Ballon ist nun hinter der Hecke.
+Du kannst das nicht sehen - das Tier aber!
+Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
+Denk dran - das Tier schaut immer den Ballon an.
+| The balloon is behind the hedge now.
+You can’t see it - but the animal can!
+The balloon falls to the ground and you have to find it.
+Remember - the animal always looks at the balloon!
+| test-hedge-2.mp3 |
+| **10** |     | Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. | Now, the hedge is shrinking. On the hedge, click where the balloon is. | test-hedge-3.mp3 |
+| **11** | **test - BOX** | Klasse , das hast du toll gemacht!
+Nun spielen wir weiter.
+Da sind wieder der Ballon, das Tier und die Kisten.
+Jetzt wächst eine Hecke hoch.
+| Nice, good job!
+Now, we’ll continue playing.
+There is the balloon and the animal.
+Now, a hedge is growing.
+| test-box-1.mp3 |
+| **12** |     | Der Ballon ist nun hinter der Hecke.
+Du kannst das nicht sehen - das Tier aber!
+Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
+Denk dran - das Tier schaut immer den Ballon an.
+| The balloon is behind the hedge now.
+You can’t see it - but the animal can!
+The balloon falls into a box and you have to find it.
+Remember - the animal always looks at the balloon!
+| test-box-2.mp3 |
+| **13** |     | Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. | Now, the hedge is shrinking. Click on the box with the balloon. | test-box-3.mp3 |
+| **14** | **goodbye** | Geschafft!
+Die Tiere sind schon ganz glücklich vom Spielen!
+Vielen Dank für deine Hilfe!
+Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf | The animals are super happy after playing.
+Thanks a lot for your help!
+See you soon and goodbye from the pig, monkey and sheep | goodbye.mp3 |
+| **15** | **general prompt** | Wo ist der Ballon? | Where is the balloon? | prompt-general.mp3 |
+| **16** | **touch - no response** | Drück auf den Ballon! | Click on the balloon! | prompt-touch.mp3 |
+| **17** | **hedge - no response** | Drücke auf die Hecke - wo der Ballon ist! | On the hedge, click where the balloon is! | prompt-hedge.mp3 |
+| **18** | **box - no response** | Drücke auf die Kiste mit dem Ballon! | Click on the box with the balloon! | prompt-box.mp3 |
+| **19** | **landing sound of balloon** | \-  | \-  | balloon-lands.mp3 |
+| **20** | **sound of blinking eyes** | \-  | \-  | blink.mp3 |
+| **21** | **sound for target click** | \-  | \-  | positive-feedback.mp3 |

### 2022-02-21 paper/manuscript.tex
add setup pictures

@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+While the distance of the target's flight depends on the final location, the target moves at a constant speed.
 Participants are then asked to locate the target's position on the screen.
 
-To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like sounds.
-Each trial starts with an eye-blinking sound, while pupils and iris get slightly enlarged and change in opacity for 0.3 sec.~The landing of the target is accompanied by a tapping sound.
+To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
+Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.~The landing of the target is accompanied by a tapping sound.
 Once the target landed, the instructor's voice asks ``Where is the balloon?'' After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
@@
 
-Before participants advance to the test trials, there are four training trials.
+Before participants advance to the test trials, we present four training trials.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 We designed two study versions which can be chosen according to the researchers' need: there is a continuous \emph{hedge} version and a discrete \emph{box} version.
-The versions use the same first training trial and then differ in the two consecutive training trials and the test trials.
+Both versions use the same first training trial and then differ in the consecutive training and test trials.
 In the \emph{hedge} version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version).
@@
 The boxes then hide the target's final destination.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../figures/gafo_hedge} \includegraphics[width=1\linewidth]{../figures/gafo_boxes} \caption{\textbf{Study versions of the balloon finding task}.
+(a) Screenshots from the continuous \emph{hedge} version of the task.
+(b) Screenshots from the discrete \emph{box} version of the task.
+(i) The agent stands in a window with the target in front of them.
+(ii) A hedge grows and covers the target.
+(iii) The target falls to a random location on the ground / into a box.
+The agent's eyes track the movement of the target.}\label{fig:fig1}
+\end{figure}
 
@@
 Our balloon finding task is presented as an interactive web-app.
-This way, the task is portable across devices and web browsers and does not require any installation.
+The task is portable across devices and web browsers and does not require any installation.
 A great advantage of online testing is that our testing procedure is standardized across participants.
-Study instructions were pre-recorded and no interaction with the experimenter is necessary during the study.
+By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study.
 The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
@@
 If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/infrastructure}
+
+}
+
+\caption{\textbf{Infrastructure for online testing}.
+With our new infrastructure, subjects aged 3 -- 99+ can participate.
+Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
+Our task is presented as a website that works across devices.
+The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
+\end{figure}
 
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-2}Child sample}
+
+\begin{tabular}{llllll}
+\toprule
+ageInYears & \multicolumn{1}{c}{nTotal} & \multicolumn{1}{c}{meanAgeInMonths} & \multicolumn{1}{c}{sdAgeInMonths} & \multicolumn{1}{c}{minAgeInMonths} & \multicolumn{1}{c}{maxAgeInMonths}\\
+\midrule
+3.00 & 40 & 41.45 & 3.85 & 36.00 & 47.00\\
+4.00 & 40 & 54.60 & 3.10 & 48.00 & 59.00\\
+5.00 & 40 & 66.95 & 3.39 & 60.00 & 71.00\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} in-person supervised testing}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{study-2---reliability-in-person}{%
@@
 
+\hypertarget{instructions-and-voice-over-descriptions}{%
+\section{Instructions and voice over descriptions}\label{instructions-and-voice-over-descriptions}}
+
+This is the content of our voice recordings. Children listen to this during the game.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}@{}}
+\toprule
+\endhead
+\textbf{Nr} & \textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
+\textbf{1} & \textbf{welcome} & Hallo!
+Schön, dass du da bist.
+Wir spielen jetzt das Ballon-Spiel!
+Siehst du die Tiere auf dem Bild da?
+Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen.
+Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
+& Hello!
+Great that you're here.
+We'll now play a balloon game.
+Can you see the animals in the picture over there?
+We want to play together with the animals using the balloon.
+We'll now talk you through exactly what will happen.
+& welcome.mp3 \\
+\textbf{2} & \textbf{touch} & Schau mal, da steht ein Tier im Fenster.
+Und siehst du den Ballon da?
+Der Ballon fällt immer runter und landet auf dem Boden.
+Und du musst ihn dann finden.
+Das Tier hilft Dir und schaut immer den Ballon an.
+& Look, an animal is standing in the window.
+And can you see the balloon over there?
+The balloon always falls down and lands on the ground.
+And you have to find it!
+The animal helps you and always looks at the balloon.
+& touch-1.mp3 \\
+\textbf{3} & & Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
+\textbf{4} & \textbf{fam - HEDGE} & Klasse, das war super!
+Jetzt spielen wir weiter.
+Siehst du wieder das Tier und den Ballon da?
+Der Ballon fällt wieder runter.
+Diesmal fällt er hinter eine Hecke.
+Du musst ihn wieder finden.
+Das Tier hilft dir und schaut immer den Ballon an.
+& Perfect, that was great!
+Now, we'll continue playing.
+Can you see the animal and the balloon again?
+The balloon will fall down again.
+This time, it will fall behind a hedge.
+And you have to find it!
+The animal helps you and looks at the balloon.
+& fam-hedge-1.mp3 \\
+\textbf{5} & & Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
+\textbf{6} & \textbf{fam - BOX} & Klasse, das war super!
+Jetzt spielen wir weiter.
+Siehst du wieder das Tier und den Ballon da?
+Der Ballon fällt wieder runter.
+Diesmal fällt er in eine Kiste.
+Du musst ihn wieder finden.
+Das Tier hilft dir und schaut immer den Ballon an.
+& Perfect, that was great!
+Now, we'll continue playing.
+Can you see the animal and the balloon again?
+The balloon falls down again.
+This time, it falls into a box.
+And you have to find it!
+The animal helps you and looks at the balloon.
+& fam-box-1.mp3 \\
+\textbf{7} & & Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
+\textbf{8} & \textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
+Nun spielen wir weiter.
+Da sind wieder der Ballon, das Tier und die Hecke.
+Die Hecke wächst jetzt hoch.
+& Nice, good job!
+Now, we'll continue playing.
+There is the balloon, the animal and the hedge.
+The hedge is growing a bit now.
+& test-hedge-1.mp3 \\
+\textbf{9} & & Der Ballon ist nun hinter der Hecke.
+Du kannst das nicht sehen - das Tier aber!
+Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
+Denk dran - das Tier schaut immer den Ballon an.
+& The balloon is behind the hedge now.
+You can't see it - but the animal can!
+The balloon falls to the ground and you have to find it.
+Remember - the animal always looks at the balloon!
+& test-hedge-2.mp3 \\
+\textbf{10} & & Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
+\textbf{11} & \textbf{test - BOX} & Klasse , das hast du toll gemacht!
+Nun spielen wir weiter.
+Da sind wieder der Ballon, das Tier und die Kisten.
+Jetzt wächst eine Hecke hoch.
+& Nice, good job!
+Now, we'll continue playing.
+There is the balloon and the animal.
+Now, a hedge is growing.
+& test-box-1.mp3 \\
+\textbf{12} & & Der Ballon ist nun hinter der Hecke.
+Du kannst das nicht sehen - das Tier aber!
+Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
+Denk dran - das Tier schaut immer den Ballon an.
+& The balloon is behind the hedge now.
+You can't see it - but the animal can!
+The balloon falls into a box and you have to find it.
+Remember - the animal always looks at the balloon!
+& test-box-2.mp3 \\
+\textbf{13} & & Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
+\textbf{14} & \textbf{goodbye} & Geschafft!
+Die Tiere sind schon ganz glücklich vom Spielen!
+Vielen Dank für deine Hilfe!
+Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf & The animals are super happy after playing.
+Thanks a lot for your help!
+See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
+\textbf{15} & \textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
+\textbf{16} & \textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
+\textbf{17} & \textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
+\textbf{18} & \textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
+\textbf{19} & \textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
+\textbf{20} & \textbf{sound of blinking eyes} & - & - & blink.mp3 \\
+\textbf{21} & \textbf{sound for target click} & - & - & positive-feedback.mp3 \\
+\bottomrule
+\end{longtable}
+
 \end{document}

### 2022-02-21 paper/manuscript.Rmd
add participant sections

@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+```{r load_data}
+library(tidyverse)
+testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
+    studyversion = factor(studyversion, levels = c("hedge", "box")), 
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "adults")), 
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
+  )
 ```
@@
 The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements. 
+We use URL parameters to capture the participant's ID, language and study version.
 
@@
 We used `r cite_r("r-references.bib")` for all our analyses.
+For child samples, we uploaded safety copies of the already collected responses after the fourth test trial.
+In cases where children want to stop participation earlier, no responses get lost.
+All test trials without voice over description are included in our analyses.
 
 # Does the balloon finding task induce variation?
-## Participants: kiga & prolific vali
+```{r vali_sample}
+vali <- testtrials %>% 
+  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
+
+vali_kids <- vali %>%
+  filter(ageInYears < 6) %>% 
+  group_by(datacollection, ageInYears) %>%
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
+    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
+    minAgeInMonths = min(ageInMonths, na.rm = T),
+    maxAgeInMonths = max(ageInMonths, na.rm = T),
+  )
+
+vali_kids_gender <- vali %>% 
+  filter(ageInYears < 6) %>% 
+  group_by(datacollection, ageInYears) %>%
+  filter(gender == "f") %>% 
+  summarise(
+    nFemales = length(unique(subjID))
+  )
+
+vali_kids <- vali_kids %>% 
+  left_join(vali_kids_gender, by = c("datacollection", "ageInYears"))
+
+vali_adults <- vali %>%
+  filter(ageInYears == 18) %>% 
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+  )
+
+vali_adults_gender <- vali %>% 
+  filter(ageInYears == 18 & gender == "f") %>% 
+  summarise(
+    nFemales = length(unique(subjID))
+  )
+
+vali_adults <- vali_adults %>% 
+  full_join(vali_adults_gender, by = character())
+```
+## Participants
+Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
+The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample).
+Participants were equally distributed across the two study versions.
+
+For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+Children in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+The child sample consisted of 
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
+and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls). 
+Children received a small thank-you gift for their participation in the study.
+
+In addition, we recruited adult participants by advertising the study on *Prolific*.
+*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
+Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
+For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
+*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+
 ## Procedure
+All participants received 15 test trials that were displayed as described above.
+In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.
+
 ## Results
@@
 
+To assess whether we would gain similar results in a remote, unsupervised testing context with children, we recruited an additional online sample of `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
+and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). 
+Families were recruited on a voluntary basis via email from the institute internal database. 
+In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+Depending on the participant's device, the website automatically presented the hedge or box version of the study.
+For families that used a tablet with touchscreen, the hedge version was shown.
+Here, children could directly click on the touchscreen themselves to indicate where the target is.
+For families that used a computer without touchscreen, the website presented the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
+
 # Can we capture variation reliably?
-## Participants: religa kiga & prolific reli
-## Procedure: 14 ± 3 days
-- what is different compared to variation? nr of trials, fixed order
+```{r reli_sample}
+reli <- testtrials %>% 
+  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli)
+
+reli_kids <- reli %>%
+  filter(ageInYears < 6) %>% 
+  group_by(datacollection, ageInYears) %>%
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
+    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
+    minAgeInMonths = min(ageInMonths, na.rm = T),
+    maxAgeInMonths = max(ageInMonths, na.rm = T),
+  )
+
+reli_kids_gender <- reli %>% 
+  filter(ageInYears < 6) %>% 
+  group_by(datacollection, ageInYears) %>%
+  filter(gender == "f") %>% 
+  summarise(
+    nFemales = length(unique(subjID))
+  )
+
+reli_kids <- reli_kids %>% 
+  left_join(reli_kids_gender, by = c("datacollection", "ageInYears"))
+
+reli_adults <- reli %>%
+  filter(ageInYears == 18) %>% 
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+  )
+
+reli_adults_gender <- reli %>% 
+  filter(ageInYears == 18 & gender == "f") %>% 
+  summarise(
+    nFemales = length(unique(subjID))
+  )
+
+reli_adults <- reli_adults %>% 
+  full_join(reli_adults_gender, by = character())
+```
+## Participants
+Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable.
+The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
+
+For our child sample, we again went to kindergartens in Leipzig and surroundings.
+The child sample consisted of 
+`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
+`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
+SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
+range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
+- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
+`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
+`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
+SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
+range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
+- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
+`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
+and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
+SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
+range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
+- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
+`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).
+
+The adult sample was again recruited over *Prolific* and consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
+
+## Procedure
+The procedure was as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
+The target locations as well as the succession of animals and target colors was randomized once.
+Each participant then received this fixed randomized order of target location, animal, and target color.
+The child sample received 15 test trials.
+In the hedge version, each bin occurred once, making up ten of the test trials.
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc).
+In the box version, we ensured that each of the five boxes occurred exactly three times.
+For the remaining training trials, we repeated a fixed order of four random bins/boxes.
+Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
+Adults in the box version received 32 test trials with each of the eight boxes occurring exactly four times.
+
 ## Results
@@
 # Exploring the external validity of our task
-## Participants: subset kiga & relikiga that filled out questionnaires
+```{r peerexposure_sample}
+pe <- testtrials %>% 
+  filter(ageInYears < 6) %>% 
+  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, targetCentralityX) %>%
+  # so that all models run with same nr of subjects
+  drop_na()
+
+pe_sample <- pe %>%
+  group_by(ageInYears) %>%
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
+    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
+    minAgeInMonths = min(ageInMonths, na.rm = T),
+    maxAgeInMonths = max(ageInMonths, na.rm = T),
+  )
+
+pe_gender <- pe %>% 
+  group_by(ageInYears) %>%
+  filter(gender == "f") %>% 
+  summarise(
+    nFemales = length(unique(subjID))
+  )
+
+pe_sample <- pe_sample %>% 
+  left_join(pe_gender, by = c("ageInYears"))
+```
+
+## Participants
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire.
+Our sample consisted of
+`r sum(pe_sample$nTotal)` children, including 
+`r sum(pe_sample$nTotal[pe_sample$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "3"])` months, 
+SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "3"])`, 
+range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "3"])`
+- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "3"])`, 
+`r sum(pe_sample$nFemales[pe_sample$ageInYears == "3"])` girls),
+`r sum(pe_sample$nTotal[pe_sample$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "4"])` months, 
+SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "4"])`, 
+range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "4"])`
+- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "4"])`, 
+`r sum(pe_sample$nFemales[pe_sample$ageInYears == "4"])` girls),
+and `r sum(pe_sample$nTotal[pe_sample$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "5"])` months, 
+SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "5"])`, 
+range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "5"])`
+- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "5"])`, 
+`r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).
+
 ## Results
@@
 Data collection took place in May 2021.
-
 Participants were compensated with £1.25 for completing the study.
@@
 In average, participants took 05:56min to complete the study.
-
-Participants were required to complete the study on a tablet or desktop.Participation on mobile devices was disabled since the display would be too small and would harm click precision.
+Participants were required to complete the study on a tablet or desktop.
+Participation on mobile devices was disabled since the display would be too small and would harm click precision.
 It was indicated that the study required audio sound.
 
-We stored *Prolific*'s internal demographic information, 
-while not asking for additional personal information.
-
-After clicking the study title, participants were directed to our online study website.
-...
+We stored *Prolific*'s internal demographic information, while not asking for additional personal information.
 
@@
 Participants were presented with eight boxes in which the target could land.
-
 50 adults participated in the study.
@@
 Data collection took place in June 2021.
-
 Participants were compensated with £1.00 for completing the study.
@@
 ## Child sample
-```{r}
-library(tidyverse)
-testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-    studyversion = factor(studyversion, levels = c("hedge", "box")), 
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "adults")), 
-    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
-  )
-
-kids_vali <- testtrials %>% 
-  filter(ageInYears < 6 & studytype == "vali")
-
-kids_vali_inperson_sample <- kids_vali %>%
-  filter(datacollection == "in-person - supervised") %>% 
-  group_by(ageInYears) %>%
-  summarise(
-    nTotal = n_distinct(subjID), 
-    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
-    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
-    minAgeInMonths = min(ageInMonths, na.rm = T),
-    maxAgeInMonths = max(ageInMonths, na.rm = T),
-  )
-
-# kids_vali %>% 
-#   filter(datacollection == "in-person - supervised") %>% 
-#   group_by(ageInYears, gender) %>% 
-#   summarise(
-#     n = length(unique(subjID))
-#   )
-```
-
 ### Study 1 - Validation Remote and in-person
@@
 unique combination of data collection mode, study version, and age-group).
-Across the two data collection modes, a total of `r kids_vali %>% select(subjID) %>% n_distinct()` children participated.
+Across the two data collection modes, a total of ...
+children participated.
 Participants received a small gift as thank you for their participation in the study.
@@
 In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
-Our in-person supervised testing sample involved `r kids_vali %>% filter(datacollection == "in-person - supervised") %>% select(subjID) %>% n_distinct()` children, including `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(nTotal)` 3-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(maxAgeInMonths)`, 22 girls), `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(nTotal)` 4-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(maxAgeInMonths)`, 19 girls), and `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(nTotal)` 5-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(maxAgeInMonths)`, 22 girls).
-
-```{r}
-# test papajas apa tables
-apa_table(kids_vali_inperson_sample, 
-          caption = "Child sample", 
-          note = "in-person supervised testing", 
-          # align = c("l", "r", "c"), 
-          escape = FALSE, 
-          row.names = TRUE, 
-          placement = "h")
-```
 

### 2022-02-21 paper/manuscript.tex
add participant sections

@@
 The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements.
+We use URL parameters to capture the participant's ID, language and study version.
 
@@
   We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
+  For child samples, we uploaded safety copies of the already collected responses after the fourth test trial.
+In cases where children want to stop participation earlier, no responses get lost.
+All test trials without voice over description are included in our analyses.
 \end{itemize}
@@
 
-\hypertarget{participants-kiga-prolific-vali-1}{%
-\subsection{Participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali-1}}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
+The pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and here: \url{https://osf.io/r3bhn} (adult sample).
+Participants were equally distributed across the two study versions.
+
+For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+Children in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+The child sample consisted of
+120 children, including
+40 3-year-olds
+(mean = 41.45 months,
+SD = 3.85,
+range = 36
+- 47,
+22 girls),
+40 4-year-olds
+(mean = 54.60 months,
+SD = 3.10,
+range = 48
+- 59,
+19 girls),
+and 40 5-year-olds
+(mean = 66.95 months,
+SD = 3.39,
+range = 60
+- 71,
+22 girls).
+Children received a small thank-you gift for their participation in the study.
+
+In addition, we recruited adult participants by advertising the study on \emph{Prolific}.
+\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
+Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
+For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
+\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
 
@@
 \subsection{Procedure}\label{procedure-1}}
+
+All participants received 15 test trials that were displayed as described above.
+In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.
 
@@
 
+To assess whether we would gain similar results in a remote, unsupervised testing context with children, we recruited an additional online sample of 147 children, including
+45 3-year-olds
+(mean = 42.62 months,
+SD = 3.35,
+range = 36
+- 47,
+14 girls),
+47 4-year-olds
+(mean = 52.64 months,
+SD = 3.40,
+range = 48
+- 59,
+25 girls),
+and 55 5-year-olds
+(mean = 65.11 months,
+SD = 3.77,
+range = 60
+- 71,
+27 girls).
+Families were recruited on a voluntary basis via email from the institute internal database.
+In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+After completion, families received a little crafting / coloring sheet as a small thank-you gift.
+Depending on the participant's device, the website automatically presented the hedge or box version of the study.
+For families that used a tablet with touchscreen, the hedge version was shown.
+Here, children could directly click on the touchscreen themselves to indicate where the target is.
+For families that used a computer without touchscreen, the website presented the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen.
+Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
+
 \hypertarget{can-we-capture-variation-reliably}{%
@@
 
-\hypertarget{participants-religa-kiga-prolific-reli}{%
-\subsection{Participants: religa kiga \& prolific reli}\label{participants-religa-kiga-prolific-reli}}
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
 
-\hypertarget{procedure-14-3-days}{%
-\subsection{Procedure: 14 ± 3 days}\label{procedure-14-3-days}}
+Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable.
+The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
+
+For our child sample, we again went to kindergartens in Leipzig and surroundings.
+The child sample consisted of
+87 children, including
+19 3-year-olds
+(mean = 42.57 months,
+SD = 3.32,
+range = 38
+- 47,
+9 girls),
+38 4-year-olds
+(mean = 53.77 months,
+SD = 3.16,
+range = 48
+- 59,
+19 girls),
+and 30 5-year-olds
+(mean = 66.10 months,
+SD = 3.43,
+range = 61
+- 71,
+16 girls).
+
+The adult sample was again recruited over \emph{Prolific} and consisted of 136 English-speakers with an average age of 25.74 years (SD = 8.11, range = 18 - 71, 87 females).
+
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
+
+The procedure was as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days.
+The target locations as well as the succession of animals and target colors was randomized once.
+Each participant then received this fixed randomized order of target location, animal, and target color.
+The child sample received 15 test trials.
+In the hedge version, each bin occurred once, making up ten of the test trials.
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 \& 2, bin 3 \& 4, etc).
+In the box version, we ensured that each of the five boxes occurred exactly three times.
+For the remaining training trials, we repeated a fixed order of four random bins/boxes.
+Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
+Adults in the box version received 32 test trials with each of the eight boxes occurring exactly four times.
+
+\hypertarget{results-4}{%
+\subsection{Results}\label{results-4}}
 
@@
 \tightlist
-\item
-  what is different compared to variation? nr of trials, fixed order
-  \#\# Results
 \item
@@
 
-\hypertarget{participants-subset-kiga-relikiga-that-filled-out-questionnaires}{%
-\subsection{Participants: subset kiga \& relikiga that filled out questionnaires}\label{participants-subset-kiga-relikiga-that-filled-out-questionnaires}}
+\hypertarget{participants-2}{%
+\subsection{Participants}\label{participants-2}}
 
-\hypertarget{results-4}{%
-\subsection{Results}\label{results-4}}
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire.
+Our sample consisted of
+130 children, including
+39 3-year-olds
+(mean = 43.02 months,
+SD = 3.26,
+range = 37
+- 47,
+20 girls),
+44 4-year-olds
+(mean = 54.43 months,
+SD = 2.77,
+range = 48
+- 59,
+26 girls),
+and 47 5-year-olds
+(mean = 66.19 months,
+SD = 3.56,
+range = 60
+- 71,
+23 girls).
+
+\hypertarget{results-5}{%
+\subsection{Results}\label{results-5}}
 
@@
 In average, participants took 05:56min to complete the study.
-
-Participants were required to complete the study on a tablet or desktop.Participation on mobile devices was disabled since the display would be too small and would harm click precision.
+Participants were required to complete the study on a tablet or desktop.
+Participation on mobile devices was disabled since the display would be too small and would harm click precision.
 It was indicated that the study required audio sound.
 
-We stored \emph{Prolific}'s internal demographic information,
-while not asking for additional personal information.
-
-After clicking the study title, participants were directed to our online study website.
-\ldots{}
+We stored \emph{Prolific}'s internal demographic information, while not asking for additional personal information.
 
@@
 We chose to have at least 20 data points per cell (i.e.~unique combination of data collection mode, study version, and age-group).
-Across the two data collection modes, a total of 267 children participated.
+Across the two data collection modes, a total of \ldots{} children participated.
 Participants received a small gift as thank you for their participation in the study.
@@
 In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
-Our in-person supervised testing sample involved 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.6 months, SD = 3.1, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-2}Child sample}
-
-\begin{tabular}{llllll}
-\toprule
-ageInYears & \multicolumn{1}{c}{nTotal} & \multicolumn{1}{c}{meanAgeInMonths} & \multicolumn{1}{c}{sdAgeInMonths} & \multicolumn{1}{c}{minAgeInMonths} & \multicolumn{1}{c}{maxAgeInMonths}\\
-\midrule
-3.00 & 40 & 41.45 & 3.85 & 36.00 & 47.00\\
-4.00 & 40 & 54.60 & 3.10 & 48.00 & 59.00\\
-5.00 & 40 & 66.95 & 3.39 & 60.00 & 71.00\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} in-person supervised testing}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
 

### 2022-02-23 paper/manuscript.Rmd
add the first plots for interind variation

@@
 library(tidyverse)
+library(brms)
 testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target’s position on the screen.
+Participants are then asked to locate the target’s destination: they respond by touching or clicking onto position on the screen.
 
@@
 ## Trials
-Before participants advance to the test trials, we present four training trials.
+Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 A great advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study.
+By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
@@
 If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
+For child samples, we upload safety copies of the already collected responses after the fourth test trial.
+In cases where children want to stop participation earlier, no responses get lost.
 
 (ref:figlab2) **Infrastructure for online testing**.
-With our new infrastructure, subjects aged 3 – 99+ can participate.
+(i) With our new infrastructure, subjects aged 3 – 99+ can participate.
 Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
-Our task is presented as a website that works across devices.
-The scripts for the website and recorded data are stored on secure local servers.
+(ii) Our task is presented as a website that works across devices.
+(iii) The scripts for the website and recorded data are stored on secure local servers.
 ```{r fig2, out.width="100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
@@
 ## Data processing
-- workflow server to R, converting coordinate systems
-We used `r cite_r("r-references.bib")` for all our analyses.
-For child samples, we uploaded safety copies of the already collected responses after the fourth test trial.
-In cases where children want to stop participation earlier, no responses get lost.
+We used `r cite_r("r-references.bib")` for all our analyses. Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses. 
 All test trials without voice over description are included in our analyses.
@@
 # Does the balloon finding task induce variation?
+Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
+The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample).
+Participants were equally distributed across the two study versions.
+The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+Data was collected between May 2021 and XXX 2022.
+
 ```{r vali_sample}
@@
 ## Participants
-Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
-The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample).
-Participants were equally distributed across the two study versions.
-
 For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
@@
 ## Procedure
+Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
 All participants received 15 test trials that were displayed as described above.
@@
 ## Results
-- for hedge & box
 - sanity check: developmental trajectory
 - remote testing: online child sample as side note
+
+We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
+
+(ref:figlab3) **Interindividual variation**. 
+The regression line shows the developmental trajectory (with 95% CI) of children's performance by age. 
+Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
+(a) Variation in the hedge version.
+Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
+(b) Variation in the box version.
+Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
+The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).
+Dotted line shows level of performance expected by chance for the adult sample (12.5%, i.e., 1 out of 8 boxes).
+
+```{r fig3, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab3)"}
+# {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
+knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+```
+
+TODO: For investigating the internal consistency of our task, we split the test trials into halves...
+
+(ref:figlab4) **Internal consistency**. 
+```{r fig4, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab4)"}
+# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+```
 
@@
 
+(ref:figlab5) **Comparing data collection modes**.
+
+```{r fig5, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab5)"}
+# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+```
+
+## Discussion
+Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+With increasing age, participants got more and more precise in locating the target.
+We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds.
+Internal consistency indicated that the measured variation was systematic.
+These results hold for both the continuous hedge version as well as the discrete box version of the task.
+Furthermore, we found comparable results for an unsupervised remote child sample.
+This underlines how flexibly our new task can be used.
+
 # Can we capture variation reliably?
+Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
+For this aim, we assessed the test-retest reliability by testing the same individual twice.
+The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
+Participants were equally distributed across the two study versions.
+The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+Data was collected between XXX 2021 and XXX 2022.
+
 ```{r reli_sample}
@@
 ## Participants
-Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable.
-The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
-
 For our child sample, we again went to kindergartens in Leipzig and surroundings.
@@
 # Exploring the external validity of our task
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. 
 ```{r peerexposure_sample}
@@
 ## Participants
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire.
-Our sample consisted of
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. Our sample consisted of 
 `r sum(pe_sample$nTotal)` children, including 

### 2022-02-23 paper/manuscript.tex
add the first plots for interind variation

@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target's position on the screen.
+Participants are then asked to locate the target's destination: they respond by touching or clicking onto position on the screen.
 
@@
 
-Before participants advance to the test trials, we present four training trials.
+Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 A great advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study.
+By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
 The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
@@
 If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
+For child samples, we upload safety copies of the already collected responses after the fourth test trial.
+In cases where children want to stop participation earlier, no responses get lost.
 
@@
 \caption{\textbf{Infrastructure for online testing}.
-With our new infrastructure, subjects aged 3 -- 99+ can participate.
+(i) With our new infrastructure, subjects aged 3 -- 99+ can participate.
 Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
-Our task is presented as a website that works across devices.
-The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
+(ii) Our task is presented as a website that works across devices.
+(iii) The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
 \end{figure}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  workflow server to R, converting coordinate systems
-  We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
-  For child samples, we uploaded safety copies of the already collected responses after the fourth test trial.
-In cases where children want to stop participation earlier, no responses get lost.
+We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{ggpubr} {[}Version 0.4.0; Kassambara (2020){]}, \emph{ggthemes} {[}Version 4.2.4; Arnold (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.6; Müller and Wickham (2021){]}, \emph{tidyboot} {[}Version 0.1.1; Braginsky and Yurovsky (2018){]}, \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
+(2019){]}, \emph{viridis} {[}Version 0.6.1; Garnier et al.
+(2021a); Garnier et al.
+(2021b){]}, and \emph{viridisLite} {[}Version 0.4.0; Garnier et al.
+(2021b){]} for all our analyses.
+Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
 All test trials without voice over description are included in our analyses.
-\end{itemize}
 
@@
 Participants were equally distributed across the two study versions.
+The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+Data was collected between May 2021 and XXX 2022.
 
@@
 
+Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
 All participants received 15 test trials that were displayed as described above.
@@
 \item
-  for hedge \& box
-\item
   sanity check: developmental trajectory
@@
 \end{itemize}
+
+We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
+
+\begin{figure}
+\includegraphics[width=0.49\linewidth]{../figures/gafo_hedge_variation} \includegraphics[width=0.49\linewidth]{../figures/gafo_box_variation} \caption{\textbf{Interindividual variation}.
+The regression line shows the developmental trajectory (with 95\% CI) of children's performance by age.
+Colored diamonds show means by age in years (with 95\% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
+(a) Variation in the hedge version.
+Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
+(b) Variation in the box version.
+Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
+The straight line shows level of performance expected by chance for the child sample (20\%, i.e., 1 out of 5 boxes).
+Dotted line shows level of performance expected by chance for the adult sample (12.5\%, i.e., 1 out of 8 boxes).}\label{fig:fig3}
+\end{figure}
+
+TODO: For investigating the internal consistency of our task, we split the test trials into halves\ldots{}
 
@@
 
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
+
+Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+With increasing age, participants got more and more precise in locating the target.
+We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds.
+Internal consistency indicated that the measured variation was systematic.
+These results hold for both the continuous hedge version as well as the discrete box version of the task.
+Furthermore, we found comparable results for an unsupervised remote child sample.
+This underlines how flexibly our new task can be used.
+
 \hypertarget{can-we-capture-variation-reliably}{%
 \section{Can we capture variation reliably?}\label{can-we-capture-variation-reliably}}
+
+Based on the results of Study 1, we wanted to further investigate the reliability of our measure. We analyzed the test-retest reliability by testing the same individual twice.
 
@@
 
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
+\hypertarget{discussion-2}{%
+\section{Discussion}\label{discussion-2}}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
+Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyboot}{}}%
+Braginsky, M., \& Yurovsky, D. (2018). \emph{Tidyboot: Tidyverse-compatible bootstrapping}. Retrieved from \url{https://CRAN.R-project.org/package=tidyboot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-brms_a}{}}%
+Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-brms_b}{}}%
+Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_b}{}}%
+Eddelbuettel, D., \& Balamuta, J.
+J.
+(2018).
+{Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}.
+\emph{The American Statistician}, \emph{72}(1), 28--36.
+\url{https://doi.org/10.1080/00031305.2017.1375990}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_a}{}}%
+Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggpubr}{}}%
+Kassambara, A. (2020). \emph{Ggpubr: 'ggplot2' based publication ready plots}. Retrieved from \url{https://CRAN.R-project.org/package=ggpubr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 

### 2022-02-23 stats/analysis.Rmd
add some more setup stuff
add the first plots for interind variation

--- 2021-12-17 paper/manuscript.Rmd
@@
 ---
-title: "Measuring individual differences in the understanding of gaze cues"
+title: "Stats"
 author: "Julia Prein"
@@
 
-# Introduction
+```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
+library(tidyverse)
+library(viridis) # color scales
+library(ggpubr)
+library(tidyboot)
+library(ggthemes)
+library(brms)
 
-# Methods
-## Participants
-## Procedure
-## Data analysis
+options(scipen = 999)
+theme_set(theme_classic())
+```
 
-# Results
+```{r load_data}
+testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
+    studyversion = factor(studyversion, levels = c("hedge", "box")), 
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "adults")), 
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
+  )
+```
 
-# Discussion
+```{r vali_data}
+vali <- testtrials %>% 
+  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
+```
 
-# References
+```{r}
+variationHedgeKids <- vali %>% 
+  filter(studyversion == "hedge" & sample == "kids" & datacollection == "in-person - supervised") %>% 
+  group_by(ageInYears, ageInMonths, subjID) %>%
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE) %>% 
+  group_by(ageInYears) %>% 
+  arrange(desc(mean), .by_group = TRUE) %>% 
+  mutate(
+    subjID = as_factor(subjID), 
+    ageInYears = as_factor(ageInYears)
+  )
 
-# Acknowledgements
+variationHedgeAdultsInd <- vali %>% 
+  filter(sample == "adults" & studyversion == "hedge") %>% 
+  group_by(ageInYears, subjID) %>%
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
 
-# Author Contributions
+variationHedgeAdults <- vali %>% 
+  filter(sample == "adults" & studyversion == "hedge") %>% 
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
+
+ggplot(data = variationHedgeKids, aes(x = ageInMonths, y = mean/160)) +
+  geom_pointrange(aes(ymin = ci_lower/160, ymax = ci_upper/160), position = position_jitter(width = 0.5), size = .25, colour = "darkgrey") +
+  geom_smooth(method = "glm", color = "#006c66", alpha = 0.2) +
+  labs(x = "Age in months", y = "Average imprecision in target width") + 
+  geom_point(data = variationHedgeAdults, aes(x = 78, y = mean/160), color = "#006c66", size = 1) + 
+  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) +
+  geom_errorbar(data = variationHedgeAdults, aes(x = 78, ymin = ci_lower/160, ymax = ci_upper/160), width = 0.2, color = "#006c66") +
+  scale_x_continuous(breaks = seq(36, 78, 6), labels = c(paste0(seq(36, 72, 6)), expression(paste("Adults ",italic("(N"), "= 50)"))))
+
+ggsave("../figures/gafo_hedge_variationAgeMonths.png", width = 6, height = 4)
+```
+
+```{r}
+vali %>% 
+  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  group_by(ageInYears) %>% 
+  summarise(n = n_distinct(subjID))
+
+variationHedgeAgegroups <- vali %>% 
+  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  group_by(ageInYears) %>%
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
+
+variationHedgeAgegroupsInd <- vali %>% 
+  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  group_by(ageInYears, subjID) %>%
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
+
+ggplot() +
+  geom_jitter(data = variationHedgeAgegroupsInd, aes(x = as.factor(ageInYears), y = mean/160), alpha = .8, width = 0.1, height = 0, col = "grey") + 
+  geom_pointrange(data = variationHedgeAgegroups, aes(x = as.factor(ageInYears), y = mean/160, ymin = ci_lower/160, ymax = ci_upper/160), 
+    size = 0.8, pch = 18) +
+  labs(x = "Age", y = "Average imprecision in target width") + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
+  scale_x_discrete(breaks = c(3, 4, 5, 18), labels = c(expression(paste("3-year-olds ",italic("(N"), "= 20)")), expression(paste("4-year-olds ",italic("(N"), "= 20)")), expression(paste("5-year-olds ",italic("(N"), "= 20)")), expression(paste("Adults ",italic("(N"), "= 50)"))))
+
+ggsave("../figures/gafo_hedge_variationAgegroup.png", width = 6, height = 4)
+```
+
+```{r variation_hedge}
+variationHedgeInd <- vali %>% 
+  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  mutate(
+    ageInYearsExact = ageInMonths/12
+  ) %>% 
+  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
+  summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))
+
+variationHedge <- variationHedgeInd %>%
+  group_by(sample, ageInYears) %>%
+  tidyboot_mean(column = mean)
+
+## without color
+# ggplot() +
+#   # child data
+#   geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "#006c66", alpha = 0.2) +
+#   geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean), alpha = .25) +
+#   geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) + 
+# 
+#   # adult data
+#   geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+#   geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
+#   labs(x = "Age in years", y = "Average imprecision in target width") + 
+#   scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
+#   scale_x_continuous(breaks = c(3.5, 4.5, 5.5, 6.5), labels = c(expression(paste("3-year-olds ",italic("(n"), "= 20)")), expression(paste("4-year-olds ",italic("(n"), "= 20)")), expression(paste("5-year-olds ",italic("(n"), "= 20)")), expression(paste("Adults ",italic("(n"), "= 50)"))))
+
+## with color
+ggplot() +
+  # child data
+  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
+  geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+
+  # adult data
+  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
+  labs(x = "Age in years", y = "Average imprecision in target width", color = "Age group") + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.11, 0.18))
+
+ggsave("../figures/gafo_hedge_variation.png", width = 6, height = 4)
+```
+
+```{r variation_box}
+variationBoxInd <- vali %>% 
+  filter(studyversion == "box" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  mutate(
+    ageInYearsExact = ageInMonths/12
+  ) %>% 
+  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
+  summarise(mean = mean(correctBox, na.rm = TRUE))
+
+variationBox <- variationBoxInd %>%
+  group_by(sample, ageInYears) %>%
+  tidyboot_mean(column = mean)
+
+ggplot() +
+  # chance level
+  geom_hline(aes(yintercept = 0.2), lty = 1) + 
+  geom_hline(aes(yintercept = 0.125), lty = 2) +
+
+  # child data
+  geom_smooth(data = variationBoxInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
+  geom_point(data = variationBoxInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
+  geom_pointrange(data = variationBox %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+
+  # adult data
+  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
+  labs(x = "Age in years", y = "Proportion correct", color = "Age group") + 
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.11, 0.85))
+
+ggsave("../figures/gafo_box_variation.png", width = 6, height = 4)
+```

### 2022-02-25 stats/analysis.Rmd
play around with ICC for between vs within person variation

@@
 
-```{r}
-variationHedgeKids <- vali %>% 
-  filter(studyversion == "hedge" & sample == "kids" & datacollection == "in-person - supervised") %>% 
-  group_by(ageInYears, ageInMonths, subjID) %>%
-  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE) %>% 
-  group_by(ageInYears) %>% 
-  arrange(desc(mean), .by_group = TRUE) %>% 
-  mutate(
-    subjID = as_factor(subjID), 
-    ageInYears = as_factor(ageInYears)
-  )
-
-variationHedgeAdultsInd <- vali %>% 
-  filter(sample == "adults" & studyversion == "hedge") %>% 
-  group_by(ageInYears, subjID) %>%
-  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
-
-variationHedgeAdults <- vali %>% 
-  filter(sample == "adults" & studyversion == "hedge") %>% 
-  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
-
-ggplot(data = variationHedgeKids, aes(x = ageInMonths, y = mean/160)) +
-  geom_pointrange(aes(ymin = ci_lower/160, ymax = ci_upper/160), position = position_jitter(width = 0.5), size = .25, colour = "darkgrey") +
-  geom_smooth(method = "glm", color = "#006c66", alpha = 0.2) +
-  labs(x = "Age in months", y = "Average imprecision in target width") + 
-  geom_point(data = variationHedgeAdults, aes(x = 78, y = mean/160), color = "#006c66", size = 1) + 
-  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) +
-  geom_errorbar(data = variationHedgeAdults, aes(x = 78, ymin = ci_lower/160, ymax = ci_upper/160), width = 0.2, color = "#006c66") +
-  scale_x_continuous(breaks = seq(36, 78, 6), labels = c(paste0(seq(36, 72, 6)), expression(paste("Adults ",italic("(N"), "= 50)"))))
-
-ggsave("../figures/gafo_hedge_variationAgeMonths.png", width = 6, height = 4)
-```
-
-```{r}
-vali %>% 
-  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
-  group_by(ageInYears) %>% 
-  summarise(n = n_distinct(subjID))
-
-variationHedgeAgegroups <- vali %>% 
-  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
-  group_by(ageInYears) %>%
-  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
-
-variationHedgeAgegroupsInd <- vali %>% 
-  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
-  group_by(ageInYears, subjID) %>%
-  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)
-
-ggplot() +
-  geom_jitter(data = variationHedgeAgegroupsInd, aes(x = as.factor(ageInYears), y = mean/160), alpha = .8, width = 0.1, height = 0, col = "grey") + 
-  geom_pointrange(data = variationHedgeAgegroups, aes(x = as.factor(ageInYears), y = mean/160, ymin = ci_lower/160, ymax = ci_upper/160), 
-    size = 0.8, pch = 18) +
-  labs(x = "Age", y = "Average imprecision in target width") + 
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
-  scale_x_discrete(breaks = c(3, 4, 5, 18), labels = c(expression(paste("3-year-olds ",italic("(N"), "= 20)")), expression(paste("4-year-olds ",italic("(N"), "= 20)")), expression(paste("5-year-olds ",italic("(N"), "= 20)")), expression(paste("Adults ",italic("(N"), "= 50)"))))
-
-ggsave("../figures/gafo_hedge_variationAgegroup.png", width = 6, height = 4)
-```
-
 ```{r variation_hedge}
@@
   mutate(
-    ageInYearsExact = ageInMonths/12
+    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
+    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
   ) %>% 
-  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
+  group_by(sample, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>%
   summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))
@@
   mutate(
-    ageInYearsExact = ageInMonths/12
+    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
+    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
   ) %>% 
-  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
+  group_by(sample, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>% 
   summarise(mean = mean(correctBox, na.rm = TRUE))
@@
 ```
+
+```{r}
+# ICC
+# no simple ICC function for brms models. use lmer instead
+library(lme4)
+library(sjstats)
+
+hedgeMdata <- vali %>% 
+  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
+  mutate(
+    imprecision = abs(clickDistFromTargetCenterX), 
+    bin = case_when(
+                      targetPosition == 5 | targetPosition == 6 ~ 1, 
+                      targetPosition == 4 | targetPosition == 7 ~ 2, 
+                      targetPosition == 3 | targetPosition == 8 ~ 3, 
+                      targetPosition == 2 | targetPosition == 9 ~ 4,                       
+                      targetPosition == 1 | targetPosition == 10 ~ 5), 
+    trial = scale(trialNr, center = TRUE, scale = TRUE)[,1],
+    pos = scale(targetCentralityX, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, imprecision, bin, pos, trial)
+
+hedgeID <- lmer(imprecision ~ (1 | subjID), data = hedgeMdata)
+sjstats::icc(hedgeID) # 37% is attributable to between-person variation, 63% is attributable to within-person variation.
+
+hedgeIDBin <- lmer(imprecision ~ (bin | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDBin) # 50% is attributable to between-person variation, 50% is attributable to within-person variation.
+
+hedgeIDBinRE <- lmer(imprecision ~ (bin | subjID) + (1 | bin), data = hedgeMdata)
+sjstats::icc(hedgeIDBinRE) # 53.1% is attributable to between-person variation
+
+hedgeIDBinF <- lmer(imprecision ~ bin + (bin | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDBinF) # Adjusted ICC: 0.550, Conditional ICC: 0.470
+
+hedgeIDPos <- lmer(imprecision ~ (pos | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDPos) # Adjusted ICC: 0.593, Conditional ICC: 0.593
+
+hedgeIDPosF <- lmer(imprecision ~ pos + (pos | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDPosF) # Adjusted ICC: 0.550, Conditional ICC: 0.465
+
+hedgeIDPosTrial <- lmer(imprecision ~ pos + (pos + trial | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDPosTrial) # Adjusted ICC: 0.556, Conditional ICC: 0.469
+
+hedgeIDPosTrialF <- lmer(imprecision ~ pos + trial + (pos + trial | subjID), data = hedgeMdata)
+sjstats::icc(hedgeIDPosTrialF) # Adjusted ICC: 0.559, Conditional ICC: 0.473
+
+# => der wert steigt, je besser wir within erklären 
+# => Target position ist wichtig, trial weniger
+
+# icc() calculates an adjusted and conditional ICC, which both take all sources of uncertainty (i.e.
+of all random effects) into account.
+While the adjusted ICC only relates to the random effects, the conditional ICC also takes the fixed effects variances into account (see Nakagawa et al.
+2017).
+# (1 | subjID) + (1 | targetBin) # symmetrisch, binned
+# (targetBin | subjID) + (1 | targetBin) # symmetrisch, binned. targetBin kann variieren zwischen IDs
+# fixed kein pooling, unterschiedliche levels frei geschätzt. RE pooling, shrinkage
+
+# targetCentrality + (targetCentrality | ID) # linear & symmetrisch, metrisch. als abweichung von mean
+# nicht als RE, dann wärs gaussian process
+
+# split into between and within subjects component
+hedgeICCdata %>% 
+  mutate(
+    meanOverall = mean(imprecision, na.rm = TRUE), 
+    meanCentered =  imprecision - meanOverall, # subtract grand mean from the raw scores 
+  ) %>% 
+  group_by(subjID) %>% 
+  mutate(
+    imprecisionB = mean(meanCentered, na.rm = TRUE), # between-subjects mean from this grand mean centered variable
+    imprecisionW = meanCentered - imprecisionB, # within-subjects mean using this between-subject mean
+  ) 
+```
+
+```{r}
+
+```

### 2022-02-25 paper/manuscript.Rmd
add plots for datacollection mode comparison

@@
 ```{r fig5, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab5)"}
-# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+knitr::include_graphics(c("../figures/gafo_hedge_remote.png", "../figures/gafo_box_remote.png"))
 ```

### 2022-02-25 stats/analysis.Rmd
add plots for datacollection mode comparison

--- 2021-12-17 paper/manuscript.Rmd
@@
 
-# Introduction
+```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
+library(tidyverse)
+library(viridis) # color scales
+library(ggpubr)
+library(tidyboot)
+library(ggthemes)
+library(brms)
 
-# Methods
-## Participants
-## Procedure
-## Data analysis
+options(scipen = 999)
+theme_set(theme_classic())
+```
 
-# Results
+```{r load_data}
+testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
+    studyversion = factor(studyversion, levels = c("hedge", "box")), 
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "adults")), 
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
+  )
+```
 
-# Discussion
+```{r vali_data}
+vali <- testtrials %>% 
+  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
+```
 
-# References
+```{r variation_hedge_preparateData}
+variationHedgeInd <- vali %>% 
+  filter(studyversion == "hedge") %>% 
+  mutate(
+    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
+    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
+  ) %>% 
+  group_by(sample, datacollection, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>%
+  summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))
 
-# Acknowledgements
+variationHedge <- variationHedgeInd %>%
+  group_by(sample, datacollection, ageInYears) %>%
+  tidyboot_mean(column = mean)
+```
 
-# Author Contributions
+```{r variation_hedge}
+## variation without remote kids
+ggplot() +
+  # child data
+  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
+  geom_point(data = variationHedgeInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+
+  # adult data
+  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
+  labs(x = "Age in years", y = "Average imprecision in target width", color = "Age group") + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.11, 0.18))
+
+ggsave("../figures/gafo_hedge_variation.png", width = 6, height = 4)
+```
+
+```{r variation_hedge_remote}
+# with remote sample
+ggplot() +
+  # child data
+  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean, group = datacollection, col = datacollection), method = "glm", alpha = 0.2, size = 0.5) + 
+  geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = datacollection), alpha = .25) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = datacollection), size = 0.8, pch = 18, position=position_dodge(width = 0.1)) +
+  scale_color_manual(values = c("#00b1ea", "#29485d"), labels = c("in-person - supervised", "remote - unsupervised")) +
+
+  # adult data
+  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width", color = "Data collection mode") + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.85, 0.88))
+
+ggsave("../figures/gafo_hedge_remote.png", width = 6, height = 4)
+```
+
+```{r variation_box_prepareData}
+variationBoxInd <- vali %>% 
+  filter(studyversion == "box") %>% 
+  mutate(
+    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
+    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
+  ) %>% 
+  group_by(sample, datacollection, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>% 
+  summarise(mean = mean(correctBox, na.rm = TRUE))
+
+variationBox <- variationBoxInd %>%
+  group_by(sample, datacollection, ageInYears) %>%
+  tidyboot_mean(column = mean)
+```
+
+```{r variation_box} 
+ggplot() +
+  # chance level
+  geom_hline(aes(yintercept = 0.2), lty = 1) + 
+  geom_hline(aes(yintercept = 0.125), lty = 2) +
+
+  # child data
+  geom_smooth(data = variationBoxInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
+  geom_point(data = variationBoxInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
+  geom_pointrange(data = variationBox %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+
+  # adult data
+  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
+  labs(x = "Age in years", y = "Proportion correct", color = "Age group") + 
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.11, 0.85))
+
+ggsave("../figures/gafo_box_variation.png", width = 6, height = 4)
+```
+
+```{r variation_box_remote}
+# with remote sample
+ggplot() +
+  # chance level
+  geom_hline(aes(yintercept = 0.2), lty = 1) + 
+  geom_hline(aes(yintercept = 0.125), lty = 2) +
+
+  # child data
+  geom_smooth(data = variationBoxInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean, group = datacollection, col = datacollection), method = "glm", alpha = 0.2, size = 0.5) +
+  geom_point(data = variationBoxInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = datacollection), alpha = .25) +
+  geom_pointrange(data = variationBox %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = datacollection), size = 0.8, pch = 18, position=position_dodge(width = 0.1)) +
+  scale_color_manual(values = c("#00b1ea", "#29485d"), labels = c("in-person - supervised", "remote - unsupervised")) +
+
+  # adult data
+  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width", color = "Data collection mode") + 
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position = c(0.17, 0.9))
+
+ggsave("../figures/gafo_box_remote.png", width = 6, height = 4)
+```

### 2022-02-25 paper/manuscript.Rmd
add splithalf reli (i.e. internal consistency) data

@@
 (b) Screenshots from the discrete *box* version of the task.
+Number of boxes (min.
+1; max.
+8) as potential hiding locations can be set individually.
 (i) The agent stands in a window with the target in front of them.
@@
 # {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
-knitr::include_graphics(c("../figures/gafo_hedge.png", "../figures/gafo_boxes.png"))
+knitr::include_graphics(c("../figures/gafo_hedge_procedure.png", "../figures/gafo_box_procedure.png"))
 ```
@@
 - sanity check: developmental trajectory
-- remote testing: online child sample as side note
 
+### Interindividual variation
 We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
@@
 
-TODO: For investigating the internal consistency of our task, we split the test trials into halves...
+### Internal consistency
+```{r variation_splithalf}
+splithalf <- readRDS(file = "../stats/gafo-splithalf.rds") 
+```
+
+TODO: cite splithalfr package
+We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable.
+As a first step, we investigated the internal consistency.
+In the hedge version, we found a splithalf reliability of
+`r splithalf$hedge_odd_even` (95%CI [`r splithalf$hedge_odd_even_ci_lower`;`r splithalf$hedge_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
+`r splithalf$hedge_first_second` (95%CI [`r splithalf$hedge_first_second_ci_lower`;`r splithalf$hedge_first_second_ci_upper`]) when splitting trials in the first and second test halves. 
+For the box version, we found a splithalf reliability of 
+`r splithalf$box_odd_even` (95%CI [`r splithalf$box_odd_even_ci_lower`;`r splithalf$box_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
+`r splithalf$box_first_second` (95%CI [`r splithalf$box_first_second_ci_lower`;`r splithalf$box_first_second_ci_upper`]) when splitting trials in the first and second test halves.
 
@@
 ```{r fig4, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab4)"}
-# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+knitr::include_graphics(c("../figures/gafo_hedge_intCon.png", "../figures/gafo_box_intCon.png"))
 ```
 
-To assess whether we would gain similar results in a remote, unsupervised testing context with children, we recruited an additional online sample of `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
+### Remote data collection
+Since our task is implemented in a way that no experimenter interaction is necessary, data can also be collected without supervision. 
+To assess whether we would gain similar results in a remote testing context, we recruited an additional online sample of `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
 `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
@@
 Families were recruited on a voluntary basis via email from the institute internal database.
+Every child received a personalized link and families could participate at any time or location they wanted.
 In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
@@
 They were asked to enable the sound and seat their child centrally in front of their device.
-Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
 Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+We stressed that caregivers should not help their children and that all kinds of child behavior were interesting to us.
 Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
@@
 
+As Figure 5 shows, our remotely collected data closely resembled the data from the kindergarten sample.
+We found a minor difference in that children that participate remotely are slightly more precise.
+This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
+It is conceivable that caregivers were especially prone to help with the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
+
 (ref:figlab5) **Comparing data collection modes**. 
-
+The regression line shows the developmental trajectory (with 95% CI) of children's performance by age, separated by data collection mode. 
+Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
+(a) Variation in the hedge version split by data collection mode.
+Performance is measured as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
+(b) Variation in the box version split by data collection mode.
+Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
+The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).
 ```{r fig5, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab5)"}
@@
 These results hold for both the continuous hedge version as well as the discrete box version of the task.
-Furthermore, we found comparable results for an unsupervised remote child sample.
+Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
 This underlines how flexibly our new task can be used.
@@
 ## Participants
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. Our sample consisted of 
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This ub sample consisted of 
 `r sum(pe_sample$nTotal)` children, including 
@@
 `r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).
+
+## Procedure
+Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire (print out / online questionnaire).
+We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
 

### 2022-02-25 stats/analysis.Rmd
add splithalf reli (i.e. internal consistency) data

@@
 ```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
-library(tidyverse)
-library(viridis) # color scales
+library(tidyverse) # data handling etc.
+library(viridis) # color scales, plotting...
 library(ggpubr)
-library(tidyboot)
 library(ggthemes)
-library(brms)
+library(tidyboot) # for bootstrap CIs
+library(brms) # modeling
+library(splithalfr) # reliability
 
@@
   # adult data
-  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+  # geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  # geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
 
@@
   geom_hline(aes(yintercept = 0.2), lty = 1) + 
-  geom_hline(aes(yintercept = 0.125), lty = 2) +
+  # geom_hline(aes(yintercept = 0.125), lty = 2) +
 
@@
   # adult data
-  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+  # geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
+  # geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
 
@@
 ```
+
+```{r variation_hedge_intCon}
+# check for kids that did not have at least 2 trials in each target position
+# not happening for hedge version! since 10 bins but only 15 test trials
+
+hedge_intCon_data <- vali %>% 
+  filter(studyversion == "hedge" & sample == "kids" & datacollection == "in-person - supervised") 
+  # mutate(trialsPerPos = n()) %>% 
+  # filter(trialsPerPos >= 2)
+
+hedge_intCon <- hedge_intCon_data %>% 
+  group_by(subjID, targetPosition) %>% 
+  mutate(
+    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
+  ) %>% 
+  group_by(subjID, testhalf) %>%
+  tidyboot_mean(col = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
+
+hedge_intCon <- hedge_intCon %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, testhalf) %>%
+  pivot_wider(
+    names_from = testhalf,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+hedge_intCon %>% psych::describe()
+
+hedge_intCon %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_point(alpha = .5) + 
+  geom_errorbarh(aes(xmin = ci_lower_even_trials, xmax = ci_upper_odd_trials), alpha = 0.3, col = "darkgrey") + 
+  geom_errorbar(aes(ymin = ci_lower_even_trials, ymax = ci_upper_odd_trials), alpha = 0.3, col = "darkgrey") +
+  # stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) +
+  geom_smooth(method = "lm", color = "#006c66", alpha = 0.25) +
+  geom_abline(intercept = 0, slope = 1, color = "darkgrey", linetype = "longdash") +
+  scale_x_continuous(breaks = seq(0, 7, 1)) +
+  scale_y_continuous(breaks = seq(0, 7, 1)) +
+  labs(x = "Average imprecision in target width in even trials", y = "Average imprecision in target width in odd trials")
+
+ggsave("../figures/gafo_hedge_intCon.png", width = 6, height = 4)
+```
+
+```{r hedge_splithalfr}
+fn_score_hedge <- function(ds) {
+  return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
+}
+
+### ODD EVEN
+split_scores_hedge_odd_even <- by_split(
+  hedge_intCon_data,
+  hedge_intCon_data$subjID,
+  fn_score_hedge,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_odd_even <- split_coefs(split_scores_hedge_odd_even, cor)
+hedge_odd_even_ci  <- split_ci(split_scores_hedge_odd_even, cor)
+
+save_splithalf <- tibble(hedge_odd_even)
+
+### FIRST SECOND
+split_scores_hedge_first_second <- by_split(
+  hedge_intCon_data,
+  hedge_intCon_data$subjID,
+  fn_score_hedge,
+  replications = 1,
+  method = c("first_second"),
+)
+
+hedge_first_second <- split_coefs(split_scores_hedge_first_second, cor)
+hedge_first_second_ci <- split_ci(split_scores_hedge_first_second, cor)
+
+save_splithalf <- save_splithalf %>% 
+  mutate(
+    # add confidence interval of coefficients (bca: bias-corrected and accelerated bootstrap confidence intervals)
+    hedge_odd_even_ci_lower = hedge_odd_even_ci$lims["0.025","bca"],
+    hedge_odd_even_ci_upper = hedge_odd_even_ci$lims["0.975","bca"],
+
+    # same for splitting according to first / second test half
+    hedge_first_second = hedge_first_second, 
+    hedge_first_second_ci_lower = hedge_first_second_ci$lims["0.025","bca"],
+    hedge_first_second_ci_upper = hedge_first_second_ci$lims["0.975","bca"],
+  )
+```
+
+```{r variation_box_intCon}
+box_intCon_excluded <- vali %>% 
+  filter(studyversion == "box" & sample == "kids" & datacollection == "in-person - supervised") %>% 
+  group_by(subjID, targetPosition) %>% 
+  summarise(trialsPerPos = n()) %>% 
+  filter(trialsPerPos < 2)
+
+box_intCon_excluded %>% 
+  select(subjID) %>% 
+  summarise(n = n_distinct(subjID))
+
+box_intCon_data <- vali %>% 
+  filter(studyversion == "box" & sample == "kids" & datacollection == "in-person - supervised" & subjID != "gk1-103")
+
+box_intCon <- box_intCon_data %>% 
+  mutate(
+    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
+  ) %>% 
+  group_by(subjID, testhalf) %>%
+  tidyboot_mean(col = correctBox, na.rm = TRUE)
+
+box_intCon <- box_intCon %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, testhalf) %>%
+  pivot_wider(
+    names_from = testhalf,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+box_intCon %>% psych::describe()
+
+box_intCon %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_point(alpha = .5) + 
+  geom_errorbarh(aes(xmin = ci_lower_even_trials, xmax = ci_upper_odd_trials), alpha = 0.3, col = "darkgrey") + 
+  geom_errorbar(aes(ymin = ci_lower_even_trials, ymax = ci_upper_odd_trials), alpha = 0.3, col = "darkgrey") +
+  # stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) +
+  geom_smooth(method = "lm", color = "#006c66", alpha = 0.25) +
+  geom_abline(intercept = 0, slope = 1, color = "darkgrey", linetype = "longdash") +
+  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
+  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
+  labs(x = "Average imprecision in target width in even trials", y = "Average imprecision in target width in odd trials")
+
+ggsave("../figures/gafo_box_intCon.png", width = 6, height = 4)
+```
+
+```{r box_splithalfr}
+fn_score_box <- function(ds) {
+  return(mean(ds$correctBox, na.rm = TRUE))
+}
+
+### ODD EVEN
+split_scores_box_odd_even <- by_split(
+  box_intCon_data,
+  box_intCon_data$subjID,
+  fn_score_box,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+box_odd_even = split_coefs(split_scores_box_odd_even, cor)
+box_odd_even_ci = split_ci(split_scores_box_odd_even, cor)
+
+### FIRST SECOND
+split_scores_box_first_second <- by_split(
+  box_intCon_data,
+  box_intCon_data$subjID,
+  fn_score_box,
+  replications = 1,
+  method = c("first_second"),
+)
+
+box_first_second = split_coefs(split_scores_box_first_second, cor)
+box_first_second_ci = split_ci(split_scores_box_first_second, cor)
+
+save_splithalf <- save_splithalf %>% 
+  mutate(
+    # add splitting according to odd / even test half
+    box_odd_even = box_odd_even, 
+    box_odd_even_ci_lower = box_odd_even_ci$lims["0.025","bca"],
+    box_odd_even_ci_upper = box_odd_even_ci$lims["0.975","bca"],
+
+    # same for splitting according to first / second test half
+    box_first_second = box_first_second, 
+    box_first_second_ci_lower = box_first_second_ci$lims["0.025","bca"],
+    box_first_second_ci_upper = box_first_second_ci$lims["0.975","bca"],
+  )
+```
+
+```{r save_splithalfr}
+save_splithalf
+
+write.csv(save_splithalf, "gafo-splithalf.csv", quote = F, row.names = F)
+saveRDS(save_splithalf, file = "gafo-splithalf.rds")
+```

### 2022-03-18 stats/analysis.Rmd
create one big plot

--- 2022-02-25 stats/analysis.Rmd
@@
 ```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
-library(tidyverse)
-library(viridis) # color scales
+library(tidyverse) # data handling etc.
+library(viridis) # col scales, plotting...
 library(ggpubr)
-library(tidyboot)
 library(ggthemes)
-library(brms)
+library(tidyboot) # for bootstrap CIs
+library(brms) # modeling
+library(splithalfr) # reliability
 
@@
 ```
+
+# VARIATION
 
@@
 
-```{r variation_hedge}
-## variation without remote kids
-ggplot() +
+```{r variation_hedge_plot}
+hedge_variation_plot <- ggplot() +
   # child data
-  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
-  geom_point(data = variationHedgeInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
-  geom_pointrange(data = variationHedge %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  geom_smooth(
+    data = variationHedgeInd %>% filter(sample == "kids"),  
+    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
+    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
+  ) +
+
+  geom_point(
+    data = variationHedgeInd %>% filter(sample == "kids"), 
+    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
+  ) +
+
+  geom_pointrange(
+    data = variationHedge %>% filter(sample == "kids"), 
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+  ) +
+
   scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+  scale_shape_manual(values = c(16, 18)) + 
+  scale_alpha_discrete(range = c(1, 0.4)) + 
+  scale_linetype_manual(values = c("solid", "dashed")) +
 
   # adult data
-  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
-  labs(x = "Age in years", y = "Average imprecision in target width", color = "Age group") + 
+  geom_jitter(
+    data = variationHedgeInd %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
+  ) +
+
+  geom_pointrange(
+    data = variationHedge %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
+    size = 0.8,
+  ) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
   scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
   scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +
-  theme(legend.position = c(0.11, 0.18))
 
-ggsave("../figures/gafo_hedge_variation.png", width = 6, height = 4)
-```
+  # theme(legend.text = element_text(size = 7),
+  #       legend.key.size = unit(0.4, "cm"), 
+  #       legend.direction = "vertical", 
+  #       legend.position = c(0.89, 0.8), 
+  #       legend.spacing.y = unit(0.25, 'cm'))
 
-```{r variation_hedge_remote}
-# with remote sample
-ggplot() +
-  # child data
-  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean, group = datacollection, col = datacollection), method = "glm", alpha = 0.2, size = 0.5) + 
-  geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = datacollection), alpha = .25) +
-  geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = datacollection), size = 0.8, pch = 18, position=position_dodge(width = 0.1)) +
-  scale_color_manual(values = c("#00b1ea", "#29485d"), labels = c("in-person - supervised", "remote - unsupervised")) +
+  theme(legend.text = element_text(size = 8),
+        legend.key.size = unit(0.4, "cm"), 
+        legend.direction = "vertical", 
+        legend.box = "horizontal",
+        legend.position = c(0.72, 0.85), 
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black")
+        )
 
-  # adult data
-  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+hedge_variation_plot
 
-  labs(x = "Age in years", y = "Average imprecision in target width", color = "Data collection mode") + 
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
-  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
-  theme(legend.position = c(0.85, 0.88))
-
-ggsave("../figures/gafo_hedge_remote.png", width = 6, height = 4)
+ggsave("../figures/gafo_hedge_variation.png", width = 7, height = 4)
 ```
@@
 
-```{r variation_box} 
-ggplot() +
+```{r variation_box_plot}
+# with remote sample
+box_variation_plot <- ggplot() +
   # chance level
-  geom_hline(aes(yintercept = 0.2), lty = 1) + 
-  geom_hline(aes(yintercept = 0.125), lty = 2) +
+  geom_segment(aes(x = 3.0, y = 0.2, xend = 6.2, yend = 0.2), lty = "dotted") + 
+  geom_segment(aes(x = 6.25, y = 0.125, xend = 6.75, yend = 0.125), lty = "dotted") +
 
   # child data
-  geom_smooth(data = variationBoxInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
-  geom_point(data = variationBoxInd %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
-  geom_pointrange(data = variationBox %>% filter(sample == "kids" & datacollection == "in-person - supervised"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) +
+  geom_smooth(
+    data = variationBoxInd %>% filter(sample == "kids"),  
+    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
+    method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey",
+  ) +
+
+  geom_point(
+    data = variationBoxInd %>% filter(sample == "kids"), 
+    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
+  ) +
+
+  geom_pointrange(
+    data = variationBox %>% filter(sample == "kids"), 
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+  ) +
+
   scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+  scale_shape_manual(values = c(16, 18)) + 
+  scale_alpha_discrete(range = c(1, 0.4)) + 
+  scale_linetype_manual(values = c("solid", "dashed")) +
 
   # adult data
-  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
-  labs(x = "Age in years", y = "Proportion correct", color = "Age group") + 
+  geom_jitter(
+    data = variationBoxInd %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
+  ) +
+
+  geom_pointrange(
+    data = variationBox %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
+    size = 0.8,
+  ) +
+
+  labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
   scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
-  theme(legend.position = c(0.11, 0.85))
+  theme(legend.position="none")
 
-ggsave("../figures/gafo_box_variation.png", width = 6, height = 4)
+box_variation_plot
+
+ggsave("../figures/gafo_box_variation.png", width = 5, height = 4)
 ```
 
-```{r variation_box_remote}
-# with remote sample
-ggplot() +
-  # chance level
-  geom_hline(aes(yintercept = 0.2), lty = 1) + 
-  geom_hline(aes(yintercept = 0.125), lty = 2) +
+# RELI
 
-  # child data
-  geom_smooth(data = variationBoxInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean, group = datacollection, col = datacollection), method = "glm", alpha = 0.2, size = 0.5) +
-  geom_point(data = variationBoxInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = datacollection), alpha = .25) +
-  geom_pointrange(data = variationBox %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = datacollection), size = 0.8, pch = 18, position=position_dodge(width = 0.1)) +
-  scale_color_manual(values = c("#00b1ea", "#29485d"), labels = c("in-person - supervised", "remote - unsupervised")) +
+```{r reli_data}
+reli <- testtrials %>% 
+  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli == TRUE)
 
-  # adult data
-  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
-  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +
+reli %>%
+  group_by(subjID) %>%
+  slice(1) %>%
+  ungroup() %>% 
+  select(ageInYears, studyversion) %>%
+  ftable()
+```
 
-  labs(x = "Age in years", y = "Average imprecision in target width", color = "Data collection mode") + 
+```{r intCon_hedge_data}
+# take data of first reli day for internal consistency
+hedge_intCon <- reli %>% 
+  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
+  # group_by(subjID, targetPosition, sample) %>% 
+  mutate(
+    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
+  ) %>% 
+  group_by(subjID, testhalf, sample) %>%
+  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
+
+hedge_intCon <- hedge_intCon %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, testhalf) %>%
+  pivot_wider(
+    names_from = testhalf,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+psych::describeBy(hedge_intCon, hedge_intCon$sample)
+```
+
+```{r intCon_hedge_kids}
+hedge_intCon_kids <- hedge_intCon %>% 
+  filter(sample == "kids") %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "#006c66", size = 0.7) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
+  labs(x = "Even trials", y = "Odd trials")
+
+hedge_intCon_kids
+
+ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
+```
+
+```{r intCon_hedge_adults}
+hedge_intCon_adults <- hedge_intCon %>% 
+  filter(sample == "adults") %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
+  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
+  labs(x = "Even trials", y = "Odd trials")
+
+hedge_intCon_adults
+
+ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
+```
+
+```{r splithalfr_hedge}
+# fn_score_hedge <- function(ds) {
+#   return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
+# }
+# 
+# ### ODD EVEN
+# split_scores_hedge_odd_even <- by_split(
+#   hedge_intCon_data,
+#   hedge_intCon_data$subjID,
+#   fn_score_hedge,
+#   replications = 1,
+#   method = c("odd_even"),
+# )
+# 
+# hedge_odd_even <- split_coefs(split_scores_hedge_odd_even, cor)
+# hedge_odd_even_ci  <- split_ci(split_scores_hedge_odd_even, cor)
+# 
+# save_splithalf <- tibble(hedge_odd_even)
+# 
+# ### FIRST SECOND
+# split_scores_hedge_first_second <- by_split(
+#   hedge_intCon_data,
+#   hedge_intCon_data$subjID,
+#   fn_score_hedge,
+#   replications = 1,
+#   method = c("first_second"),
+# )
+# 
+# hedge_first_second <- split_coefs(split_scores_hedge_first_second, cor)
+# hedge_first_second_ci <- split_ci(split_scores_hedge_first_second, cor)
+# 
+# save_splithalf <- save_splithalf %>% 
+#   mutate(
+#     # add confidence interval of coefficients (bca: bias-corrected and accelerated bootstrap confidence intervals)
+#     hedge_odd_even_ci_lower = hedge_odd_even_ci$lims["0.025","bca"],
+#     hedge_odd_even_ci_upper = hedge_odd_even_ci$lims["0.975","bca"],
+#     
+#     # same for splitting according to first / second test half
+#     hedge_first_second = hedge_first_second, 
+#     hedge_first_second_ci_lower = hedge_first_second_ci$lims["0.025","bca"],
+#     hedge_first_second_ci_upper = hedge_first_second_ci$lims["0.975","bca"],
+#   )
+```
+
+```{r intCon_box_data}
+# take data of first reli day for internal consistency
+box_intCon <- reli %>% 
+  filter(studyversion == "box" & reliday == "reliday1") %>% 
+  mutate(
+    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
+  ) %>% 
+  group_by(subjID, testhalf, sample) %>%
+  tidyboot_mean(column = correctBox, na.rm = TRUE)
+
+box_intCon <- box_intCon %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, testhalf) %>%
+  pivot_wider(
+    names_from = testhalf,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+psych::describeBy(box_intCon, box_intCon$sample)
+```
+
+```{r intCon_box_kids}
+box_intCon_kids <- box_intCon %>% 
+  filter(sample == "kids") %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "#006c66", size = 0.7) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
+  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
+  labs(x = "Even trials", y = "Odd trials")
+
+box_intCon_kids
+
+ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
+```
+
+```{r intCon_box_adults}
+box_intCon_adults <- box_intCon %>% 
+  filter(sample == "adults") %>% 
+  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
-  theme(legend.position = c(0.17, 0.9))
+  labs(x = "Even trials", y = "Odd trials")
 
-ggsave("../figures/gafo_box_remote.png", width = 6, height = 4)
+box_intCon_adults
+
+ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
 ```
+
+```{r box_splithalfr}
+# fn_score_box <- function(ds) {
+#   return(mean(ds$correctBox, na.rm = TRUE))
+# }
+# 
+# ### ODD EVEN
+# split_scores_box_odd_even <- by_split(
+#   box_intCon_data,
+#   box_intCon_data$subjID,
+#   fn_score_box,
+#   replications = 1,
+#   method = c("odd_even"),
+# )
+# 
+# box_odd_even = split_coefs(split_scores_box_odd_even, cor)
+# box_odd_even_ci = split_ci(split_scores_box_odd_even, cor)
+#   
+# ### FIRST SECOND
+# split_scores_box_first_second <- by_split(
+#   box_intCon_data,
+#   box_intCon_data$subjID,
+#   fn_score_box,
+#   replications = 1,
+#   method = c("first_second"),
+# )
+# 
+# box_first_second = split_coefs(split_scores_box_first_second, cor)
+# box_first_second_ci = split_ci(split_scores_box_first_second, cor)
+# 
+# save_splithalf <- save_splithalf %>% 
+#   mutate(
+#     # add splitting according to odd / even test half
+#     box_odd_even = box_odd_even, 
+#     box_odd_even_ci_lower = box_odd_even_ci$lims["0.025","bca"],
+#     box_odd_even_ci_upper = box_odd_even_ci$lims["0.975","bca"],
+#     
+#     # same for splitting according to first / second test half
+#     box_first_second = box_first_second, 
+#     box_first_second_ci_lower = box_first_second_ci$lims["0.025","bca"],
+#     box_first_second_ci_upper = box_first_second_ci$lims["0.975","bca"],
+#   )
+```
+
+```{r save_splithalfr}
+# save_splithalf
+# 
+# write.csv(save_splithalf, "gafo-splithalf.csv", quote = F, row.names = F)
+# saveRDS(save_splithalf, file = "gafo-splithalf.rds")
+```
+
+```{r retest_hedge_data}
+# take data of first reli day for internal consistency
+hedge_retest <- reli %>% 
+  filter(studyversion == "hedge") %>% 
+  group_by(subjID, reliday, sample) %>% 
+  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
+
+hedge_retest <- hedge_retest %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, reliday) %>%
+  pivot_wider(
+    names_from = reliday,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+psych::describeBy(hedge_retest, hedge_retest$sample)
+
+# exclude 1 outlier
+hedge_retest <- hedge_retest %>% 
+  filter(mean_reliday1 < mean(mean_reliday1) + 3*sd(mean_reliday1), mean_reliday1 > mean(mean_reliday1) - 3*sd(mean_reliday1), 
+         mean_reliday2 < mean(mean_reliday2) + 3*sd(mean_reliday2), mean_reliday2 > mean(mean_reliday2) - 3*sd(mean_reliday2))
+```
+
+```{r retest_hedge_kids}
+hedge_retest_kids <- hedge_retest %>% 
+  filter(sample == "kids") %>% 
+  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "#006c66", size = 0.7) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  labs(x = "Testday 1", y = "Testday 2")
+
+hedge_retest_kids
+
+ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
+```
+
+```{r retest_hedge_adults}
+hedge_retest_adults <- hedge_retest %>% 
+  filter(sample == "adults") %>% 
+  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
+  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
+  labs(x = "Testday 1", y = "Testday 2")
+
+hedge_retest_adults
+
+ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+```
+
+```{r retest_box_data}
+# take data of first reli day for internal consistency
+box_retest <- reli %>% 
+  filter(studyversion == "box") %>% 
+  group_by(subjID, reliday, sample) %>% 
+  tidyboot_mean(column = correctBox, na.rm = TRUE)
+
+box_retest <- box_retest %>% 
+  select(-c(n, empirical_stat)) %>% 
+  group_by(subjID, reliday) %>%
+  pivot_wider(
+    names_from = reliday,
+    values_from = c(mean, ci_lower, ci_upper)
+  ) %>%
+  ungroup()
+
+# summary
+psych::describeBy(box_retest, box_retest$sample)
+```
+```{r retest_box_kids}
+box_retest_kids <- box_retest %>% 
+  filter(sample == "kids") %>% 
+  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "#006c66", size = 0.7) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  labs(x = "Testday 1", y = "Testday 2")
+
+box_retest_kids
+
+ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
+```
+
+```{r retest_box_adults}
+box_retest_adults <- box_retest %>% 
+  filter(sample == "adults") %>% 
+  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
+  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
+  geom_point(col = "darkgrey", size = 1.2, shape = 18, alpha = 0.5) + 
+  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+  labs(x = "Testday 1", y = "Testday 2")
+
+box_retest_adults
+
+ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+```
+
+```{r arrange_plots}
+ggarrange(
+
+  ggarrange(hedge_variation_plot,
+            NULL,
+            ggarrange(
+              hedge_intCon_kids, 
+              hedge_intCon_adults,
+              hedge_retest_kids, 
+              hedge_retest_adults, 
+              nrow = 2, 
+              ncol = 2, 
+              labels = c("B", "C", "D", "E")
+            ),
+
+            # hedge: space between vari and reli
+            nrow = 1, widths = c(1.2, 0.06, 1),
+            labels = c("A", "", "")
+  ),
+
+  NULL,
+
+  ggarrange(box_variation_plot,
+            NULL,
+            ggarrange(
+              box_intCon_kids,
+              box_intCon_adults,
+              box_retest_kids,
+              box_retest_adults,
+              nrow = 2, 
+              ncol = 2,
+              labels = c("G", "H", "I", "J")
+            ),
+
+            # box: space between vari and reli
+            nrow = 1, widths = c(1.2, 0.06, 1),
+            labels = c("F", "", "")
+  ),
+
+  # space between hedge & box
+  nrow = 3, heights = c(1.2, 0.1, 1.2)
+)
+
+ggsave("../figures/gafo_results.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+```

### 2022-03-18 stats/analysis.Rmd
for corr plots: color according to age group

@@
 ```{r variation_hedge_plot}
+tmp <- variationHedgeInd
+
+variationHedgeInd <- variationHedgeInd %>% 
+  mutate(
+    ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18"))
+  )
+
 hedge_variation_plot <- ggplot() +
@@
 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+  # scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
   scale_shape_manual(values = c(16, 18)) + 
@@
     data = variationHedgeInd %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
+    aes(x = 6.5, y = mean, col = as.factor(ageInYears), shape = datacollection), alpha = 0.8, width = .05, height = .01,  
   ) +
@@
 
-  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
+  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
   scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
@@
   filter(studyversion == "hedge" & reliday == "reliday1") %>% 
-  # group_by(subjID, targetPosition, sample) %>% 
   mutate(
@@
   ) %>% 
-  group_by(subjID, testhalf, sample) %>%
+  group_by(subjID, testhalf, sample, ageInYears) %>%
   tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
@@
   geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
-  geom_point(col = "#006c66", size = 0.7) + 
+  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
@@
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 2, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(limits = c(0, 2), breaks = seq(0, 2, 0.5)) +
@@
   ) %>% 
-  group_by(subjID, testhalf, sample) %>%
+  group_by(subjID, testhalf, sample, ageInYears) %>%
   tidyboot_mean(column = correctBox, na.rm = TRUE)
@@
   geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
-  geom_point(col = "#006c66", size = 0.7) + 
+  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(breaks = seq(0, 1, 0.2)) +
@@
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
@@
   filter(studyversion == "hedge") %>% 
-  group_by(subjID, reliday, sample) %>% 
+  group_by(subjID, reliday, sample, ageInYears) %>% 
   tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
@@
   geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
-  geom_point(col = "#006c66", size = 0.7) + 
+  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
@@
   filter(studyversion == "box") %>% 
-  group_by(subjID, reliday, sample) %>% 
+  group_by(subjID, reliday, sample, ageInYears) %>% 
   tidyboot_mean(column = correctBox, na.rm = TRUE)
@@
   geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
-  geom_point(col = "#006c66", size = 0.7) + 
+  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") + 
+  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
   scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +

### 2022-03-18 stats/analysis.Rmd
correct col of adult points

@@
 vali <- testtrials %>% 
-  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
+  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18)) %>% 
+  mutate(ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18")))
 ```
@@
 ```{r variation_hedge_plot}
-tmp <- variationHedgeInd
-
-variationHedgeInd <- variationHedgeInd %>% 
-  mutate(
-    ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18"))
-  )
-
 hedge_variation_plot <- ggplot() +
@@
     data = variationHedgeInd %>% filter(sample == "kids"), 
-    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
+    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
   ) +
@@
     data = variationHedge %>% filter(sample == "kids"), 
-    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
   ) +
 
-  # scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
   scale_shape_manual(values = c(16, 18)) + 
@@
     data = variationHedgeInd %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, col = as.factor(ageInYears), shape = datacollection), alpha = 0.8, width = .05, height = .01,  
+    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
   ) +
@@
   scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +
-
-  # theme(legend.text = element_text(size = 7),
-  #       legend.key.size = unit(0.4, "cm"), 
-  #       legend.direction = "vertical", 
-  #       legend.position = c(0.89, 0.8), 
-  #       legend.spacing.y = unit(0.25, 'cm'))
 
@@
     data = variationBoxInd %>% filter(sample == "kids"), 
-    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
+    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
   ) +
@@
     data = variationBox %>% filter(sample == "kids"), 
-    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
   ) +
 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
   scale_shape_manual(values = c(16, 18)) + 
@@
     data = variationBoxInd %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
+    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
   ) +
@@
   labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
@@
 reli <- testtrials %>% 
-  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli == TRUE)
+  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli == TRUE) %>% 
+  mutate(ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18")))
 
@@
   geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
-  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
+  geom_point(aes(col = ageInYears), size = 0.7) + 
   scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +

### 2022-03-18 paper/manuscript.Rmd
add revised plots

@@
 output            : papaja::apa6_pdf
+
+header-includes:
+  - \usepackage{setspace}
+  - \captionsetup[figure]{font={stretch=1}}
 ---
@@
 The boxes then hide the target's final destination.
-(ref:figlab1) **Study versions of the balloon finding task**.
-(a) Screenshots from the continuous *hedge* version of the task.
-(b) Screenshots from the discrete *box* version of the task.
-Number of boxes (min.
-1; max.
-8) as potential hiding locations can be set individually.
+
+(ref:figlab1) **Study setup**. 
+(a) Infrastructure for online testing.
+(i) Subjects aged 3 – 99+ can participate.
+Data collection can take place anywhere: at home, in kindergartens or research institutes.
+(ii) The task is presented as a website that works across devices.
+(iii) The scripts for the website and the recorded data are stored on secure local servers.
+(b) Continuous *hedge* version of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
 (ii) A hedge grows and covers the target.
-(iii) The target falls to a random location on the ground / into a box.
+(iii) The target falls to a random location on the ground.
 The agent's eyes track the movement of the target.
+(c) Discrete *box* version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.
 
-```{r fig1, fig.show = "hold", out.width = "100%", fig.align = "default", fig.cap = "(ref:figlab1)",}
-# {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
-knitr::include_graphics(c("../figures/gafo_hedge_procedure.png", "../figures/gafo_box_procedure.png"))
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/gafo_procedure.jpg")
 ```
@@
 In cases where children want to stop participation earlier, no responses get lost.
-
-(ref:figlab2) **Infrastructure for online testing**.
-(i) With our new infrastructure, subjects aged 3 – 99+ can participate.
-Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
-(ii) Our task is presented as a website that works across devices.
-(iii) The scripts for the website and recorded data are stored on secure local servers.
-```{r fig2, out.width="100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics("../figures/infrastructure.png")
-```
 
@@
 
-(ref:figlab3) **Interindividual variation**. 
-The regression line shows the developmental trajectory (with 95% CI) of children's performance by age. 
-Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
-(a) Variation in the hedge version.
-Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
+(ref:figlab2) **Measuring interindividual variation**. 
+(a) Developmental trajectory in continuous *hedge* version.
+Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
 The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
-(b) Variation in the box version.
+(b) Internal consistency (odd-even split) in hedge child sample.
+(c) Internal consistency in hedge adult sample.
+(d) Test-retest reliability in hedge child sample.
+(e) Test-retest reliability in hedge adult sample.
+(f) Developmental trajectory in discrete *box* version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
-The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).
-Dotted line shows level of performance expected by chance for the adult sample (12.5%, i.e., 1 out of 8 boxes).
+Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
+(g) Internal consistency (odd-even split) in box child sample.
+(h) Internal consistency in box adult sample.
+(i) Test-retest reliability in box child sample.
+(j) Test-retest reliability in box adult sample.
+Regression lines with 95% CI show product-moment-correlations with Pearson's correlation coefficient r. 
+Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
+Small data points show the mean performance for each subject.
+Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
+Color of data points represent each age group (binned by year).
 
-```{r fig3, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab3)"}
-# {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
-knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics(c("../figures/gafo_results.png"))
 ```
@@
 `r splithalf$box_first_second` (95%CI [`r splithalf$box_first_second_ci_lower`;`r splithalf$box_first_second_ci_upper`]) when splitting trials in the first and second test halves.
-
-(ref:figlab4) **Internal consistency**. 
-```{r fig4, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics(c("../figures/gafo_hedge_intCon.png", "../figures/gafo_box_intCon.png"))
-```
 
@@
 The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).
-```{r fig5, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab5)"}
-knitr::include_graphics(c("../figures/gafo_hedge_remote.png", "../figures/gafo_box_remote.png"))
-```
 

### 2022-03-18 paper/manuscript.tex
add revised plots

@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
-\title{Measuring individual differences in the understanding of gaze cues across the lifespan}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 
@@
 \makeatother
-\shorttitle{Gaze cue understanding}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{social cognition, individual differences, gaze cues, psychometrics\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
+\usepackage{setspace}
+\captionsetup[figure]{font={stretch=1}}
 \ifLuaTeX
@@
 
+\title{Measuring individual differences in the understanding of gaze cues across the lifespan}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
+\date{}
+
+\shorttitle{Gaze cue understanding}
+
 \authornote{
@@
 
-\abstract{
+\abstract{%
 There must be an abstract of no more than 250 words.
@@
 Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.~The landing of the target is accompanied by a tapping sound.
-Once the target landed, the instructor's voice asks ``Where is the balloon?'' After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
+Once the target landed, the instructor's voice asks ``Where is the balloon?''.
+After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
 If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figures/gafo_hedge} \includegraphics[width=1\linewidth]{../figures/gafo_boxes} \caption{\textbf{Study versions of the balloon finding task}.
-(a) Screenshots from the continuous \emph{hedge} version of the task.
-(b) Screenshots from the discrete \emph{box} version of the task.
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gafo_procedure}
+
+}
+
+\caption{\textbf{Study setup}.
+(a) Infrastructure for online testing.
+(i) Subjects aged 3 -- 99+ can participate.
+Data collection can take place anywhere: at home, in kindergartens or research institutes.
+(ii) The task is presented as a website that works across devices.
+(iii) The scripts for the website and the recorded data are stored on secure local servers.
+(b) Continuous \emph{hedge} version of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
 (ii) A hedge grows and covers the target.
-(iii) The target falls to a random location on the ground / into a box.
-The agent's eyes track the movement of the target.}\label{fig:fig1}
+(iii) The target falls to a random location on the ground.
+The agent's eyes track the movement of the target.
+(c) Discrete \emph{box} version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.}\label{fig:fig1}
 \end{figure}
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/infrastructure}
-
-}
-
-\caption{\textbf{Infrastructure for online testing}.
-(i) With our new infrastructure, subjects aged 3 -- 99+ can participate.
-Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes.
-(ii) Our task is presented as a website that works across devices.
-(iii) The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
-\end{figure}
-
 \hypertarget{data-processing-1}{%
@@
 
-We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{ggpubr} {[}Version 0.4.0; Kassambara (2020){]}, \emph{ggthemes} {[}Version 4.2.4; Arnold (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.6; Müller and Wickham (2021){]}, \emph{tidyboot} {[}Version 0.1.1; Braginsky and Yurovsky (2018){]}, \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
-(2019){]}, \emph{viridis} {[}Version 0.6.1; Garnier et al.
-(2021a); Garnier et al.
-(2021b){]}, and \emph{viridisLite} {[}Version 0.4.0; Garnier et al.
-(2021b){]} for all our analyses.
+We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{brms} (Version 2.15.0; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.6; Eddelbuettel \& François, 2011), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{splithalfr} (Version 2.1.1; Thomas, Dylan, Reinout, \& Jaap, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyboot} (Version 0.1.1; Braginsky \& Yurovsky, 2018), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.1; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses.
 Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
@@
 \section{Does the balloon finding task induce variation?}\label{does-the-balloon-finding-task-induce-variation}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
 
@@
 Data was collected between May 2021 and XXX 2022.
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
   sanity check: developmental trajectory
-\item
-  remote testing: online child sample as side note
 \end{itemize}
 
+\hypertarget{interindividual-variation}{%
+\subsubsection{Interindividual variation}\label{interindividual-variation}}
+
 We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
@@
 \begin{figure}
-\includegraphics[width=0.49\linewidth]{../figures/gafo_hedge_variation} \includegraphics[width=0.49\linewidth]{../figures/gafo_box_variation} \caption{\textbf{Interindividual variation}.
-The regression line shows the developmental trajectory (with 95\% CI) of children's performance by age.
-Colored diamonds show means by age in years (with 95\% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
-(a) Variation in the hedge version.
-Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gafo_results}
+
+}
+
+\caption{\textbf{Measuring interindividual variation}.
+(a) Developmental trajectory in continuous \emph{hedge} version.
+Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
 The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
-(b) Variation in the box version.
+(b) Internal consistency (odd-even split) in hedge child sample.
+(c) Internal consistency in hedge adult sample.
+(d) Test-retest reliability in hedge child sample.
+(e) Test-retest reliability in hedge adult sample.
+(f) Developmental trajectory in discrete \emph{box} version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
-The straight line shows level of performance expected by chance for the child sample (20\%, i.e., 1 out of 5 boxes).
-Dotted line shows level of performance expected by chance for the adult sample (12.5\%, i.e., 1 out of 8 boxes).}\label{fig:fig3}
+Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
+(g) Internal consistency (odd-even split) in box child sample.
+(h) Internal consistency in box adult sample.
+(i) Test-retest reliability in box child sample.
+(j) Test-retest reliability in box adult sample.
+Regression lines with 95\% CI show product-moment-correlations with Pearson's correlation coefficient r.
+Large data points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
+Small data points show the mean performance for each subject.
+Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
+Color of data points represent each age group (binned by year).}\label{fig:fig2}
 \end{figure}
 
-TODO: For investigating the internal consistency of our task, we split the test trials into halves\ldots{}
-
-To assess whether we would gain similar results in a remote, unsupervised testing context with children, we recruited an additional online sample of 147 children, including
+\hypertarget{internal-consistency}{%
+\subsubsection{Internal consistency}\label{internal-consistency}}
+
+TODO: cite splithalfr package
+We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable.
+As a first step, we investigated the internal consistency.
+In the hedge version, we found a splithalf reliability of
+0.72 (95\%CI {[}0.60;0.82{]}) when applying an odd-even split, and splithalf reliability of
+0.71 (95\%CI {[}0.51;0.81{]}) when splitting trials in the first and second test halves.
+For the box version, we found a splithalf reliability of
+0.55 (95\%CI {[}0.35;0.69{]}) when applying an odd-even split, and splithalf reliability of
+0.79 (95\%CI {[}0.64;0.86{]}) when splitting trials in the first and second test halves.
+
+\hypertarget{remote-data-collection}{%
+\subsubsection{Remote data collection}\label{remote-data-collection}}
+
+Since our task is implemented in a way that no experimenter interaction is necessary, data can also be collected without supervision.
+To assess whether we would gain similar results in a remote testing context, we recruited an additional online sample of 147 children, including
 45 3-year-olds
@@
 Families were recruited on a voluntary basis via email from the institute internal database.
+Every child received a personalized link and families could participate at any time or location they wanted.
 In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
@@
 
+As Figure 5 shows, our remotely collected data closely resembled the data from the kindergarten sample.
+We found a minor difference in that children that participate remotely are slightly more precise.
+This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
+It is conceivable that caregivers were especially prone to help with the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
+
 \hypertarget{discussion-1}{%
@@
 
-Based on the results of Study 1, we wanted to further investigate the reliability of our measure. We analyzed the test-retest reliability by testing the same individual twice.
+Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
+For this aim, we assessed the test-retest reliability by testing the same individual twice.
+The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
+Participants were equally distributed across the two study versions.
+The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+Data was collected between XXX 2021 and XXX 2022.
 
@@
 
-Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable.
-The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
-
 For our child sample, we again went to kindergartens in Leipzig and surroundings.
 The child sample consisted of
-87 children, including
-19 3-year-olds
-(mean = 42.57 months,
-SD = 3.32,
+93 children, including
+24 3-year-olds
+(mean = 42.49 months,
+SD = 2.99,
 range = 38
 - 47,
-9 girls),
+13 girls),
 38 4-year-olds
@@
 19 girls),
-and 30 5-year-olds
-(mean = 66.10 months,
-SD = 3.43,
+and 31 5-year-olds
+(mean = 66 months,
+SD = 3.42,
 range = 61
 - 71,
-16 girls).
+17 girls).
 
@@
 
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+
 \hypertarget{participants-2}{%
@@
 
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire.
-Our sample consisted of
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This ub sample consisted of
 130 children, including
@@
 (mean = 43.02 months,
-SD = 3.26,
+SD = 3.20,
 range = 37
@@
 and 47 5-year-olds
-(mean = 66.19 months,
-SD = 3.56,
+(mean = 66.13 months,
+SD = 3.55,
 range = 60
@@
 23 girls).
+
+\hypertarget{procedure-3}{%
+\subsection{Procedure}\label{procedure-3}}
+
+Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire (print out / online questionnaire).
+We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
 
@@
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
 
@@
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-splithalfr}{}}%
+Thomas, P., Dylan, M., Reinout, W., \& Jaap, M.
+(2021).
+Methods to split cognitive task data for estimating split-half reliability: A comprehensive review and systematic assessment.
+\emph{Psychonomic Bulletin \& Review}, 1--11.
+\url{https://doi.org/10.3758/s13423-021-01948-3}
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.20}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
 \toprule

### 2022-03-18 stats/analysis.Rmd
clean up plots

@@
 
+## Internal consistency
 ```{r intCon_hedge_data}
@@
 
+## Test-retest reliability
+
 ```{r retest_hedge_data}
@@
 
+# Save plots
+
 ```{r arrange_plots}
@@
             # hedge: space between vari and reli
-            nrow = 1, widths = c(1.2, 0.06, 1),
+            nrow = 1, widths = c(1, 0.06, 1),
             labels = c("A", "", "")
@@
             # box: space between vari and reli
-            nrow = 1, widths = c(1.2, 0.06, 1),
+            nrow = 1, widths = c(1, 0.06, 1),
             labels = c("F", "", "")

### 2022-03-21 stats/analysis.Rmd
add splithalf analysis on first reliday

@@
 
-```{r splithalfr_hedge}
-# fn_score_hedge <- function(ds) {
-#   return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
-# }
-# 
-# ### ODD EVEN
-# split_scores_hedge_odd_even <- by_split(
-#   hedge_intCon_data,
-#   hedge_intCon_data$subjID,
-#   fn_score_hedge,
-#   replications = 1,
-#   method = c("odd_even"),
-# )
-# 
-# hedge_odd_even <- split_coefs(split_scores_hedge_odd_even, cor)
-# hedge_odd_even_ci  <- split_ci(split_scores_hedge_odd_even, cor)
-# 
-# save_splithalf <- tibble(hedge_odd_even)
-# 
-# ### FIRST SECOND
-# split_scores_hedge_first_second <- by_split(
-#   hedge_intCon_data,
-#   hedge_intCon_data$subjID,
-#   fn_score_hedge,
-#   replications = 1,
-#   method = c("first_second"),
-# )
-# 
-# hedge_first_second <- split_coefs(split_scores_hedge_first_second, cor)
-# hedge_first_second_ci <- split_ci(split_scores_hedge_first_second, cor)
-# 
-# save_splithalf <- save_splithalf %>% 
-#   mutate(
-#     # add confidence interval of coefficients (bca: bias-corrected and accelerated bootstrap confidence intervals)
-#     hedge_odd_even_ci_lower = hedge_odd_even_ci$lims["0.025","bca"],
-#     hedge_odd_even_ci_upper = hedge_odd_even_ci$lims["0.975","bca"],
-#     
-#     # same for splitting according to first / second test half
-#     hedge_first_second = hedge_first_second, 
-#     hedge_first_second_ci_lower = hedge_first_second_ci$lims["0.025","bca"],
-#     hedge_first_second_ci_upper = hedge_first_second_ci$lims["0.975","bca"],
-#   )
-```
-
 ```{r intCon_box_data}
@@
 
-```{r box_splithalfr}
-# fn_score_box <- function(ds) {
-#   return(mean(ds$correctBox, na.rm = TRUE))
-# }
-# 
-# ### ODD EVEN
-# split_scores_box_odd_even <- by_split(
-#   box_intCon_data,
-#   box_intCon_data$subjID,
-#   fn_score_box,
-#   replications = 1,
-#   method = c("odd_even"),
-# )
-# 
-# box_odd_even = split_coefs(split_scores_box_odd_even, cor)
-# box_odd_even_ci = split_ci(split_scores_box_odd_even, cor)
-#   
-# ### FIRST SECOND
-# split_scores_box_first_second <- by_split(
-#   box_intCon_data,
-#   box_intCon_data$subjID,
-#   fn_score_box,
-#   replications = 1,
-#   method = c("first_second"),
-# )
-# 
-# box_first_second = split_coefs(split_scores_box_first_second, cor)
-# box_first_second_ci = split_ci(split_scores_box_first_second, cor)
-# 
-# save_splithalf <- save_splithalf %>% 
-#   mutate(
-#     # add splitting according to odd / even test half
-#     box_odd_even = box_odd_even, 
-#     box_odd_even_ci_lower = box_odd_even_ci$lims["0.025","bca"],
-#     box_odd_even_ci_upper = box_odd_even_ci$lims["0.975","bca"],
-#     
-#     # same for splitting according to first / second test half
-#     box_first_second = box_first_second, 
-#     box_first_second_ci_lower = box_first_second_ci$lims["0.025","bca"],
-#     box_first_second_ci_upper = box_first_second_ci$lims["0.975","bca"],
-#   )
+```{r splithalfr_hedge_kids}
+fn_score_hedge <- function(ds) {
+  return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
+}
+
+hedge_intCon_data <- reli %>% 
+  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
+  mutate(
+    # summarize bins, so that 9 + 10 = bin 5
+    # bin = ceiling(as.numeric(targetPosition)/2)
+
+    # summarize so that 1 + 10 = bin 5
+    symmetricBin = case_when(targetPosition == "5" | targetPosition == "6" ~ 1, 
+                             targetPosition == "4" | targetPosition == "7" ~ 2,
+                             targetPosition == "3" | targetPosition == "8" ~ 3, 
+                             targetPosition == "2" | targetPosition == "9" ~ 4,
+                             targetPosition == "1" | targetPosition == "10"~ 5, 
+                       )
+  )
+
+# random split
+splitscores_hedge_random_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
+hedge_random_kids_ci  <- split_ci(splitscores_hedge_random_kids, cor)
+
+# create dataframe to save data
+splithalf_data <- tibble(
+                    studyversion = "hedge", 
+                    sample = "kids", 
+                    split = "random", 
+                    stratification = "none", 
+                    mean = hedge_random_kids, 
+                    CI_lower = hedge_random_kids_ci$lims["0.025","bca"], 
+                    CI_upper = hedge_random_kids_ci$lims["0.975","bca"])
+
+# random split with stratification by target position
+splitscores_hedge_randomStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+hedge_randomStrat_kids <- split_coefs(splitscores_hedge_randomStrat_kids, cor)
+hedge_randomStrat_kids_ci <- split_ci(splitscores_hedge_randomStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "kids", 
+                                        split = "random",
+                                        stratification = "target position",
+                                        mean = hedge_randomStrat_kids, 
+                                        CI_lower = hedge_randomStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_randomStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split
+splitscores_hedge_oddeven_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
+hedge_oddeven_kids_ci  <- split_ci(splitscores_hedge_oddeven_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "kids", 
+                                        split = "odd even", 
+                                        stratification = "none", 
+                                        mean = hedge_oddeven_kids, 
+                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split with stratification by target position
+splitscores_hedge_oddevenStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
+hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "kids", 
+                                        split = "odd even",
+                                        stratification = "target position",
+                                        mean = hedge_oddevenStrat_kids, 
+                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split
+splitscores_hedge_firstsecond_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("first_second"),
+)
+
+hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
+hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "kids", 
+                                        split = "first second", 
+                                        stratification = "none",                                        
+                                        mean = hedge_firstsecond_kids, 
+                                        CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split with stratification by target position
+splitscores_hedge_firstsecondStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
+hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "kids", 
+                                        split = "first second",
+                                        stratification = "target position",
+                                        mean = hedge_firstsecondStrat_kids, 
+                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
 ```
 
-```{r save_splithalfr}
-# save_splithalf
-# 
-# write.csv(save_splithalf, "gafo-splithalf.csv", quote = F, row.names = F)
-# saveRDS(save_splithalf, file = "gafo-splithalf.rds")
+```{r splithalfr_hedge_adults}
+# random split
+splitscores_hedge_random_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+hedge_random_adults <- split_coefs(splitscores_hedge_random_adults, cor)
+hedge_random_adults_ci  <- split_ci(splitscores_hedge_random_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "random", 
+                                        stratification = "none", 
+                                        mean = hedge_random_adults, 
+                                        CI_lower = hedge_random_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_random_adults_ci$lims["0.975","bca"]
+                                      )
+
+# random split with stratification by target position
+splitscores_hedge_randomStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+hedge_randomStrat_adults <- split_coefs(splitscores_hedge_randomStrat_adults, cor)
+hedge_randomStrat_adults_ci <- split_ci(splitscores_hedge_randomStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "random",
+                                        stratification = "target position",
+                                        mean = hedge_randomStrat_adults, 
+                                        CI_lower = hedge_randomStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_randomStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split
+splitscores_hedge_oddeven_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
+hedge_oddeven_adults_ci  <- split_ci(splitscores_hedge_oddeven_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "odd even", 
+                                        stratification = "none", 
+                                        mean = hedge_oddeven_adults, 
+                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split with stratification by target position
+splitscores_hedge_oddevenStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
+hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "odd even",
+                                        stratification = "target position",
+                                        mean = hedge_oddevenStrat_adults, 
+                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split
+splitscores_hedge_firstsecond_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 1,
+  method = c("first_second"),
+)
+
+hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
+hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "first second", 
+                                        stratification = "none",                                        
+                                        mean = hedge_firstsecond_adults, 
+                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split with stratification by target position
+splitscores_hedge_firstsecondStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
+  replications = 1,
+  method = c("odd_even"),
+)
+
+hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
+hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "hedge", 
+                                        sample = "adults", 
+                                        split = "first second",
+                                        stratification = "target position",
+                                        mean = hedge_firstsecondStrat_adults, 
+                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_kids}
+fn_score_box <- function(ds) {
+  return(mean(ds$correctBox, na.rm = TRUE))
+}
+
+box_intCon_data <- reli %>% 
+  filter(studyversion == "box" & reliday == "reliday1")
+
+box_intCon_data %>% 
+  group_by(subjID, targetPosition) %>% 
+  summarise(n = n()) %>% 
+  filter(n < 2)
+
+# random split
+splitscores_box_random_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+box_random_kids <- split_coefs(splitscores_box_random_kids, cor)
+box_random_kids_ci  <- split_ci(splitscores_box_random_kids, cor)
+
+# create dataframe to save data
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "random", 
+                                        stratification = "none", 
+                                        mean = box_random_kids, 
+                                        CI_lower = box_random_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_random_kids_ci$lims["0.975","bca"])
+
+# random split with stratification by target position
+splitscores_box_randomStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  careful = FALSE, 
+)
+
+box_randomStrat_kids <- split_coefs(splitscores_box_randomStrat_kids, cor)
+box_randomStrat_kids_ci <- split_ci(splitscores_box_randomStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "random",
+                                        stratification = "target position",
+                                        mean = box_randomStrat_kids, 
+                                        CI_lower = box_randomStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_randomStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split
+splitscores_box_oddeven_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
+box_oddeven_kids_ci  <- split_ci(splitscores_box_oddeven_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "odd even", 
+                                        stratification = "none", 
+                                        mean = box_oddeven_kids, 
+                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split with stratification by target position
+splitscores_box_oddevenStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
+  replications = 1,
+  method = c("odd_even"),
+  careful = FALSE
+)
+
+box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
+box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "odd even",
+                                        stratification = "target position",
+                                        mean = box_oddevenStrat_kids, 
+                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split
+splitscores_box_firstsecond_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("first_second"),
+)
+
+box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
+box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "first second", 
+                                        stratification = "none",                                        
+                                        mean = box_firstsecond_kids, 
+                                        CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split with stratification by target position
+splitscores_box_firstsecondStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
+  replications = 1,
+  method = c("odd_even"),
+  careful = FALSE,
+)
+
+box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
+box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "kids", 
+                                        split = "first second",
+                                        stratification = "target position",
+                                        mean = box_firstsecondStrat_kids, 
+                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_adults}
+# random split
+splitscores_box_random_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+)
+
+box_random_adults <- split_coefs(splitscores_box_random_adults, cor)
+box_random_adults_ci  <- split_ci(splitscores_box_random_adults, cor)
+
+# create dataframe to save data
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "random", 
+                                        stratification = "none", 
+                                        mean = box_random_adults, 
+                                        CI_lower = box_random_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_random_adults_ci$lims["0.975","bca"]
+                                      )
+
+# random split with stratification by target position
+splitscores_box_randomStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
+  replications = 1,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  careful = FALSE,
+)
+
+box_randomStrat_adults <- split_coefs(splitscores_box_randomStrat_adults, cor)
+box_randomStrat_adults_ci <- split_ci(splitscores_box_randomStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "random",
+                                        stratification = "target position",
+                                        mean = box_randomStrat_adults, 
+                                        CI_lower = box_randomStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_randomStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split
+splitscores_box_oddeven_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("odd_even"),
+)
+
+box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
+box_oddeven_adults_ci  <- split_ci(splitscores_box_oddeven_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "odd even", 
+                                        stratification = "none", 
+                                        mean = box_oddeven_adults, 
+                                        CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd even split with stratification by target position
+splitscores_box_oddevenStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
+  replications = 1,
+  method = c("odd_even"),
+  careful = FALSE,
+)
+
+box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
+box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "odd even",
+                                        stratification = "target position",
+                                        mean = box_oddevenStrat_adults, 
+                                        CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split
+splitscores_box_firstsecond_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 1,
+  method = c("first_second"),
+)
+
+box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
+box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "first second", 
+                                        stratification = "none",                                        
+                                        mean = box_firstsecond_adults, 
+                                        CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first second testhalves split with stratification by target position
+splitscores_box_firstsecondStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
+  replications = 1,
+  method = c("odd_even"),
+  careful = FALSE,
+)
+
+box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
+box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        studyversion = "box", 
+                                        sample = "adults", 
+                                        split = "first second",
+                                        stratification = "target position",
+                                        mean = box_firstsecondStrat_adults, 
+                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalf_plot}
+splithalf_data %>% 
+  mutate(sample = fct_rev(sample)) %>%
+  unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
+  mutate(samplegroup = fct_rev(samplegroup)) %>%
+  unite("method", c(split, stratification), sep = ", ", remove = FALSE) %>% 
+  ggplot(aes(x = method, y = mean, color = sample, group = studyversion)) + 
+    geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
+    geom_point(position = position_dodge(0.1), size = 3) +
+    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+    scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
+    labs(x = "Splitting & stratification method", y = "") +
+    coord_flip() + 
+    facet_wrap(~ samplegroup) + 
+    theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
+
+ggsave("../figures/gafo_splithalf.png", width = 6, height = 4, scale = 1.4)
+```
+
+```{r splithalf_table}
+knitr::kable(splithalf_data)
+```
+
+```{r save_splithalf_data}
+write.csv(splithalf_data, "gafo-splithalf.csv", quote = F, row.names = F)
+saveRDS(splithalf_data, file = "gafo-splithalf.rds")
 ```

### 2022-03-21 paper/manuscript.Rmd
minor clean up

@@
 
-\newpage
-
-# -- POSSIBLE ROUGH STRUCTURE -- 
-# intro
-## individual differences in dev psy
-- reliable tasks: need variation, more trials
-
-## exisiting tasks for social cognition
-- wellman
-
-## current goal
-- standardized, easy to use, continuous
-
-# methods (let's see whether we want this generic heading...)
-## design of our task
-- training trials (touch & fam together, click on visible balloon / visible target flight, voice over trials)
-- test trials
-- flexible: two versions, can also use discrete
-- face value
-
-- stimulus timing
-
-## implementation / development
-- JS, HTML, CSS
-- parcel?!
-- SVG: scalable
-- webapp: portable across devices, flexible, no hard system requirements
-- response collection: file format, variables saved (click responses)
-
-## data processing
-- workflow for collecting data
-- pipeline? downloading server data into r, coverting coordinate systems
-
-# does our task induce variation?
-## participants: kiga & prolific vali
-## procedure 
-## results
-- for hedge & box
-- sanity check: developmental trajectory
-- remote testing: online child sample as side note
-
-# do we capture variation reliably?
-## participants: relikiga & prolific reli
-## results: 
-- internal consistency?
-- test-retest
-
-# exploratory: external validity
-## participants: subsample kiga & relikiga with questionnaire data
-## results: 
-- peer exposure (box & hedge combined?)
-
-# discussion
-## limitations
-## future development / extending the task
-# conclusion
-
-\newpage
 # Introduction 
@@
 
-- individual differences in developmental psychology
+- individual differences in developmental psychology:
 - reliable tasks, variation needed, more trials
 - existing tasks for social cognition: wellman
-- goal of the current project
+- goal of the current project: standardized, easy to use continuous methods
 
 # Design of our balloon finding task
+- face value of task (or maybe in intro already?)
 
@@
 The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
-For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
-For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used. 
+We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 ## Results
-- sanity check: developmental trajectory
-
-### Interindividual variation
-We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
-
 (ref:figlab2) **Measuring interindividual variation**. 
@@
 
-### Internal consistency
-```{r variation_splithalf}
-splithalf <- readRDS(file = "../stats/gafo-splithalf.rds") 
-```
-
-TODO: cite splithalfr package
-We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable.
-As a first step, we investigated the internal consistency.
-In the hedge version, we found a splithalf reliability of
-`r splithalf$hedge_odd_even` (95%CI [`r splithalf$hedge_odd_even_ci_lower`;`r splithalf$hedge_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
-`r splithalf$hedge_first_second` (95%CI [`r splithalf$hedge_first_second_ci_lower`;`r splithalf$hedge_first_second_ci_upper`]) when splitting trials in the first and second test halves. 
-For the box version, we found a splithalf reliability of 
-`r splithalf$box_odd_even` (95%CI [`r splithalf$box_odd_even_ci_lower`;`r splithalf$box_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
-`r splithalf$box_first_second` (95%CI [`r splithalf$box_first_second_ci_lower`;`r splithalf$box_first_second_ci_upper`]) when splitting trials in the first and second test halves.
+We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance.
+In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F).
+By the end of their sixth year of life, children come close to the adult's proficiency level.
+We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.
 
@@
 
-As Figure 5 shows, our remotely collected data closely resembled the data from the kindergarten sample.
+As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample.
 We found a minor difference in that children that participate remotely are slightly more precise.
@@
 
-(ref:figlab5) **Comparing data collection modes**. 
-The regression line shows the developmental trajectory (with 95% CI) of children's performance by age, separated by data collection mode. 
-Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
-(a) Variation in the hedge version split by data collection mode.
-Performance is measured as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click.
-The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
-(b) Variation in the box version split by data collection mode.
-Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
-The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).
-
 ## Discussion
@@
 With increasing age, participants got more and more precise in locating the target.
-We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds.
-Internal consistency indicated that the measured variation was systematic.
-These results hold for both the continuous hedge version as well as the discrete box version of the task.
+We found inter-individual variation in across all age groups.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
-For this aim, we assessed the test-retest reliability by testing the same individual twice.
+For this aim, we assessed the internal consistency and test-retest reliability.
 The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
@@
 - test-retest
+
+```{r splithalf}
+splithalf <- readRDS(file = "../stats/gafo-splithalf.rds")
+```
+
+For estimating the internal consistency, we analyzed the raw performance per subject of the first test day. 
+Our main analysis focuses on an odd-even split on our data.  
+In the hedge version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2B), and an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2C).
+In the box version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2G), and an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2H).
+
+A recent paper by [TODO: insert citation splithalfr paper] presents new techniques to analyze internal consistency. 
+The modern statistical approach of stratification allows for a better representation of the data and experimental structure. 
+To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position.
+As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates.
+As might be expected, we found higher coefficients for the samples with higher variation, i.e. for our continuous hedge version of the task.
+
+```{r}
+knitr::kable(splithalf, col.names = c("study version", "age group", "splitting method", "stratification", "mean estimate", "lower 95%CI", "upper 95%CI"))
+```
+
+Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
+
+## Discussion
 

### 2022-03-21 paper/manuscript.tex
minor clean up

@@
 
-\newpage
-
-\hypertarget{possible-rough-structure}{%
-\section{-- POSSIBLE ROUGH STRUCTURE --}\label{possible-rough-structure}}
-
-\hypertarget{intro}{%
-\section{intro}\label{intro}}
-
-\hypertarget{individual-differences-in-dev-psy}{%
-\subsection{individual differences in dev psy}\label{individual-differences-in-dev-psy}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Idea for an opener :)
+
+Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+For example \ldots{} .
 
@@
 \item
-  reliable tasks: need variation, more trials
-\end{itemize}
-
-\hypertarget{exisiting-tasks-for-social-cognition}{%
-\subsection{exisiting tasks for social cognition}\label{exisiting-tasks-for-social-cognition}}
-
-\begin{itemize}
-\tightlist
-\item
-  wellman
-\end{itemize}
-
-\hypertarget{current-goal}{%
-\subsection{current goal}\label{current-goal}}
-
-\begin{itemize}
-\tightlist
-\item
-  standardized, easy to use, continuous
-\end{itemize}
-
-\hypertarget{methods-lets-see-whether-we-want-this-generic-heading}{%
-\section{methods (let's see whether we want this generic heading\ldots)}\label{methods-lets-see-whether-we-want-this-generic-heading}}
-
-\hypertarget{design-of-our-task}{%
-\subsection{design of our task}\label{design-of-our-task}}
-
-\begin{itemize}
-\item
-  training trials (touch \& fam together, click on visible balloon / visible target flight, voice over trials)
-\item
-  test trials
-\item
-  flexible: two versions, can also use discrete
-\item
-  face value
-\item
-  stimulus timing
-\end{itemize}
-
-\hypertarget{implementation-development}{%
-\subsection{implementation / development}\label{implementation-development}}
-
-\begin{itemize}
-\tightlist
-\item
-  JS, HTML, CSS
-\item
-  parcel?!
-\item
-  SVG: scalable
-\item
-  webapp: portable across devices, flexible, no hard system requirements
-\item
-  response collection: file format, variables saved (click responses)
-\end{itemize}
-
-\hypertarget{data-processing}{%
-\subsection{data processing}\label{data-processing}}
-
-\begin{itemize}
-\tightlist
-\item
-  workflow for collecting data
-\item
-  pipeline? downloading server data into r, coverting coordinate systems
-\end{itemize}
-
-\hypertarget{does-our-task-induce-variation}{%
-\section{does our task induce variation?}\label{does-our-task-induce-variation}}
-
-\hypertarget{participants-kiga-prolific-vali}{%
-\subsection{participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali}}
-
-\hypertarget{procedure}{%
-\subsection{procedure}\label{procedure}}
-
-\hypertarget{results}{%
-\subsection{results}\label{results}}
-
-\begin{itemize}
-\tightlist
-\item
-  for hedge \& box
-\item
-  sanity check: developmental trajectory
-\item
-  remote testing: online child sample as side note
-\end{itemize}
-
-\hypertarget{do-we-capture-variation-reliably}{%
-\section{do we capture variation reliably?}\label{do-we-capture-variation-reliably}}
-
-\hypertarget{participants-relikiga-prolific-reli}{%
-\subsection{participants: relikiga \& prolific reli}\label{participants-relikiga-prolific-reli}}
-
-\hypertarget{results-1}{%
-\subsection{results:}\label{results-1}}
-
-\begin{itemize}
-\tightlist
-\item
-  internal consistency?
-\item
-  test-retest
-\end{itemize}
-
-\hypertarget{exploratory-external-validity}{%
-\section{exploratory: external validity}\label{exploratory-external-validity}}
-
-\hypertarget{participants-subsample-kiga-relikiga-with-questionnaire-data}{%
-\subsection{participants: subsample kiga \& relikiga with questionnaire data}\label{participants-subsample-kiga-relikiga-with-questionnaire-data}}
-
-\hypertarget{results-2}{%
-\subsection{results:}\label{results-2}}
-
-\begin{itemize}
-\tightlist
-\item
-  peer exposure (box \& hedge combined?)
-\end{itemize}
-
-\hypertarget{discussion}{%
-\section{discussion}\label{discussion}}
-
-\hypertarget{limitations}{%
-\subsection{limitations}\label{limitations}}
-
-\hypertarget{future-development-extending-the-task}{%
-\subsection{future development / extending the task}\label{future-development-extending-the-task}}
-
-\hypertarget{conclusion}{%
-\section{conclusion}\label{conclusion}}
-
-\newpage
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Idea for an opener :)
-
-Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-For example \ldots{} .
-
-\begin{itemize}
-\tightlist
-\item
-  individual differences in developmental psychology
+  individual differences in developmental psychology:
 \item
@@
 \item
-  goal of the current project
+  goal of the current project: standardized, easy to use continuous methods
 \end{itemize}
@@
 \section{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}
+
+\begin{itemize}
+\tightlist
+\item
+  face value of task (or maybe in intro already?)
+\end{itemize}
 
@@
 The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP.
-For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
-For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used.
+We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 
-\hypertarget{data-processing-1}{%
-\subsection{Data processing}\label{data-processing-1}}
+\hypertarget{data-processing}{%
+\subsection{Data processing}\label{data-processing}}
 
@@
 
-\hypertarget{procedure-1}{%
-\subsection{Procedure}\label{procedure-1}}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 
-\hypertarget{results-3}{%
-\subsection{Results}\label{results-3}}
-
-\begin{itemize}
-\tightlist
-\item
-  sanity check: developmental trajectory
-\end{itemize}
-
-\hypertarget{interindividual-variation}{%
-\subsubsection{Interindividual variation}\label{interindividual-variation}}
-
-We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
@@
 
-\hypertarget{internal-consistency}{%
-\subsubsection{Internal consistency}\label{internal-consistency}}
-
-TODO: cite splithalfr package
-We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable.
-As a first step, we investigated the internal consistency.
-In the hedge version, we found a splithalf reliability of
-0.72 (95\%CI {[}0.60;0.82{]}) when applying an odd-even split, and splithalf reliability of
-0.71 (95\%CI {[}0.51;0.81{]}) when splitting trials in the first and second test halves.
-For the box version, we found a splithalf reliability of
-0.55 (95\%CI {[}0.35;0.69{]}) when applying an odd-even split, and splithalf reliability of
-0.79 (95\%CI {[}0.64;0.86{]}) when splitting trials in the first and second test halves.
+We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance.
+In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F).
+By the end of their sixth year of life, children come close to the adult's proficiency level.
+We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.
 
@@
 
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
@@
 Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
-For this aim, we assessed the test-retest reliability by testing the same individual twice.
+For this aim, we assessed the internal consistency and test-retest reliability.
 The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
@@
 
-\hypertarget{procedure-2}{%
-\subsection{Procedure}\label{procedure-2}}
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
 
@@
 
-\hypertarget{results-4}{%
-\subsection{Results}\label{results-4}}
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 \end{itemize}
+
+For estimating the internal consistency, we analyzed the raw performance per subject of the first test day.
+Our main analysis focuses on an odd-even split on our data.\\
+In the hedge version, odd-even splitting yielded an estimate of 0.86 for the child sample (see Figure 2B), and an estimate of 0.77 for the adult sample (see Figure 2C).
+In the box version, odd-even splitting yielded an estimate of 0.55 for the child sample (see Figure 2G), and an estimate of 0.76 for the adult sample (see Figure 2H).
+
+A recent paper by {[}TODO: insert citation splithalfr paper{]} presents new techniques to analyze internal consistency.
+The modern statistical approach of stratification allows for a better representation of the data and experimental structure.
+To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position.
+As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates.
+As might be expected, we found higher coefficients for the samples with higher variation, i.e.~for our continuous hedge version of the task.
+
+\begin{tabular}{l|l|l|l|r|r|r}
+\hline
+study version & age group & splitting method & stratification & mean estimate & lower 95\%CI & upper 95\%CI\\
+\hline
+hedge & kids & random & none & 0.8043888 & 0.6920419 & 0.9164789\\
+\hline
+hedge & kids & random & target position & 0.9476184 & 0.8969928 & 0.9755679\\
+\hline
+hedge & kids & odd even & none & 0.8594840 & 0.7205078 & 0.9093440\\
+\hline
+hedge & kids & odd even & target position & 0.8024165 & 0.5332674 & 0.9298445\\
+\hline
+hedge & kids & first second & none & 0.8181923 & 0.6947852 & 0.9381469\\
+\hline
+hedge & kids & first second & target position & 0.8024165 & 0.5203456 & 0.9246955\\
+\hline
+hedge & adults & random & none & 0.8653142 & 0.7987080 & 0.9165413\\
+\hline
+hedge & adults & random & target position & 0.9239187 & 0.8751052 & 0.9518373\\
+\hline
+hedge & adults & odd even & none & 0.7686066 & 0.5965930 & 0.8631549\\
+\hline
+hedge & adults & odd even & target position & 0.8024056 & 0.6640335 & 0.8818732\\
+\hline
+hedge & adults & first second & none & 0.6752549 & 0.5261556 & 0.7964930\\
+\hline
+hedge & adults & first second & target position & 0.8024056 & 0.6561634 & 0.8822399\\
+\hline
+box & kids & random & none & 0.7660606 & 0.5458261 & 0.8598990\\
+\hline
+box & kids & random & target position & 0.9088431 & 0.8521932 & 0.9424099\\
+\hline
+box & kids & odd even & none & 0.5483231 & 0.3375113 & 0.6922869\\
+\hline
+box & kids & odd even & target position & 0.6137607 & 0.3960722 & 0.7393150\\
+\hline
+box & kids & first second & none & 0.5022750 & 0.2369860 & 0.6633424\\
+\hline
+box & kids & first second & target position & 0.6137607 & 0.3772301 & 0.7354956\\
+\hline
+box & adults & random & none & 0.8004204 & 0.6814629 & 0.8755589\\
+\hline
+box & adults & random & target position & 0.8657569 & 0.7669845 & 0.9221076\\
+\hline
+box & adults & odd even & none & 0.7597443 & 0.6424789 & 0.8387192\\
+\hline
+box & adults & odd even & target position & 0.6673433 & 0.4851349 & 0.7846746\\
+\hline
+box & adults & first second & none & 0.6685946 & 0.4850376 & 0.7642744\\
+\hline
+box & adults & first second & target position & 0.6673433 & 0.4845532 & 0.7820390\\
+\hline
+\end{tabular}
+
+Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
+
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
 
@@
 
-\hypertarget{procedure-3}{%
-\subsection{Procedure}\label{procedure-3}}
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
 
@@
 
-\hypertarget{results-5}{%
-\subsection{Results}\label{results-5}}
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
 
@@
 
-\hypertarget{limitations-1}{%
-\subsection{Limitations}\label{limitations-1}}
-
-\hypertarget{future-development-extending-the-task-1}{%
-\subsection{Future development / extending the task}\label{future-development-extending-the-task-1}}
-
-\hypertarget{conclusion-1}{%
-\section{Conclusion}\label{conclusion-1}}
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+\hypertarget{future-development-extending-the-task}{%
+\subsection{Future development / extending the task}\label{future-development-extending-the-task}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 

### 2022-03-22 stats/analysis.Rmd
create clickDistInBalloons and symmetricPosition as overall variables. add age model in variation section, add age corrected retest model

@@
     sample = factor(sample, levels = c("kids", "adults")), 
-    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
+
+    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
+    # the smaller the value, the more central the position
+    symmetricPosition = case_when(
+                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
+                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
+                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
+                                  targetPosition == "2" | targetPosition == "9" ~ 4,
+                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
+                       ),
+
+    # distance between target and click in balloon widths (balloon width is 160 SVG units)
+    clickDistInBalloons = clickDistInBalloons,
   )
@@
   group_by(sample, datacollection, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>%
-  summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))
+  summarise(mean = mean(clickDistInBalloons, na.rm = TRUE))
 
@@
 ggsave("../figures/gafo_hedge_variation.png", width = 7, height = 4)
+```
+
+```{r age_hedge_model}
+mDataAgeHedge <- vali %>% 
+  filter(studyversion == "hedge" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)
+
+mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
+                    data = mDataAgeHedge,
+                    family = lognormal(),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4)
 ```
@@
 
+```{r age_box_model}
+# define data
+mDataAgeBox <- vali %>% 
+  filter(studyversion == "box" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, datacollection, symmetricPosition, targetPosition, correctBox)
+
+mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
+                    data = mDataAgeBox,
+                    family = bernoulli(link = "logit"),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4)
+```
+
 # RELI
@@
   group_by(subjID, testhalf, sample, ageInYears) %>%
-  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
+  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)
 
@@
 fn_score_hedge <- function(ds) {
-  return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
+  return(mean(clickDistInBalloons, na.rm = TRUE))
 }
@@
 hedge_intCon_data <- reli %>% 
-  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
-  mutate(
-    # summarize bins, so that 9 + 10 = bin 5
-    # bin = ceiling(as.numeric(targetPosition)/2)
-
-    # summarize so that 1 + 10 = bin 5
-    symmetricBin = case_when(targetPosition == "5" | targetPosition == "6" ~ 1, 
-                             targetPosition == "4" | targetPosition == "7" ~ 2,
-                             targetPosition == "3" | targetPosition == "8" ~ 3, 
-                             targetPosition == "2" | targetPosition == "9" ~ 4,
-                             targetPosition == "1" | targetPosition == "10"~ 5, 
-                       )
-  )
+  filter(studyversion == "hedge" & reliday == "reliday1")
 
@@
   fn_score_hedge,
-  replications = 1,
+  replications = 10000,
   method = c("random"),
@@
   fn_score_hedge,
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
-  replications = 1,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+  replications = 10000,
   method = c("random"),
@@
   fn_score_hedge,
-  replications = 1,
+  replications = 10000,
   method = c("odd_even"),
@@
   fn_score_hedge,
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
-  replications = 1,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+  replications = 10000,
   method = c("odd_even"),
@@
   fn_score_hedge,
-  replications = 1,
+  replications = 10000,
   method = c("first_second"),
@@
   fn_score_hedge,
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
-  replications = 1,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+  replications = 10000,
   method = c("random"),
@@
   fn_score_hedge,
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
-  replications = 1,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+  replications = 10000,
   method = c("odd_even"),
@@
   fn_score_box,
-  replications = 1,
+  replications = 10000,
   method = c("random"),
@@
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 1,
+  replications = 10000,
   method = c("random"),
@@
   fn_score_box,
-  replications = 1,
+  replications = 10000,
   method = c("odd_even"),
@@
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 1,
+  replications = 10000,
   method = c("odd_even"),
@@
   fn_score_box,
-  replications = 1,
+  replications = 10000,
   method = c("first_second"),
@@
   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 1,
+  replications = 10000,
   method = c("random"),
@@
   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 1,
+  replications = 10000,
   method = c("odd_even"),
@@
   group_by(subjID, reliday, sample, ageInYears) %>% 
-  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)
+  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)
 
@@
 ```
+
 ```{r retest_box_kids}
@@
 
+```{r retest_hedge_model}
+# define data
+mDataRetestHedge <- reli %>% 
+  filter(studyversion == "hedge" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, reliday, clickDistInBalloons)
+
+# run model
+mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
+                              data   = mDataRetestHedge, 
+                              family = lognormal(), 
+                              warmup = 1000, 
+                              iter   = 3000, 
+                              chains = 4, 
+                              inits  = "random",
+                              cores  = 4)
+```
+
+```{r retest_box_model}
+# define data
+mDataRetestBox <- reli %>% 
+  filter(studyversion == "box" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, reliday, correctBox)
+
+# run model
+mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
+                              data   = mDataRetestBox, 
+                              family = bernoulli(link = "logit"),
+                              warmup = 1000, 
+                              iter   = 3000, 
+                              chains = 4, 
+                              inits  = "random",
+                              cores  = 4)
+```
+
 # Save plots
@@
 ```
+
+```{r save_model_output}
+# mcor <- model_cor %>%
+#     mutate(task = recode(task,
+#                     `mutual_exclusivity` = "Mutual Exclusivity",
+#                     `informativeness` = "Informativeness Inference (1)",
+#                     `simple_inf` = "Informativeness Inference (2)",
+#                     `preference` = "Speaker Preference",
+#                     `novelty` = "Discourse Novelty",
+#                     `card_sorting` = "Card Sorting",
+#                     `discourse_continuity` = "Discourse Continuity",
+#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
+#                     `match_to_sample` = "Relational Match-to-sample"),
+#            term = task, 
+#            mcor = Estimate, 
+#            mcor_lci = `l-95% CI`, 
+#            mcor_uci = `u-95% CI`)%>%
+#   select(study, term, task, mcor, mcor_lci, mcor_uci)
+
+# saveRDS(mcor, "model_results.rds")
+```

### 2022-03-22 paper/manuscript.Rmd
add age model

@@
 ``` 
+```{r}
+mAgeHedge <- readRDS(file = "../stats/mAgeHedge.rds") 
+mAgeBox <- readRDS(file = "../stats/mAgeBox.rds") 
+```
+
+We assessed the effect of data collection mode and age (in months, z-transformed) in a Bayesian generalized linear mixed model with target position and subject ID as random effects.
+In the hedge version, the estimate of age was `r fixef(mAgeHedge)["age", "Estimate"]` ([`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]; with remote unsupervised data collection as the reference category).
+In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` ([`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]; remote unsupervised data collection as reference category).
 

### 2022-03-22 paper/manuscript.tex
add age model

@@
 \end{figure}
+
+We assessed the effect of data collection mode and age (in months, z-transformed) in a Bayesian generalized linear mixed model with target position and subject ID as random effects.
+In the hedge version, the estimate of age is -0.33 ({[}-0.42; -0.23{]}) and of data collection mode is -0.32 ({[}-0.50; -0.14{]}, with remote unsupervised data collection as the reference category).
+In the box version, the estimate of age is 0.64 ({[}0.41; 0.88{]}) and of data collection mode is 1.16 ({[}0.73; 1.61{]}, with remote unsupervised data collection as the reference category).
 

### 2022-03-23 stats/analysis.Rmd
fix calculation clickDistInBalloons
play around with nr of replications splithalfr

@@
     # distance between target and click in balloon widths (balloon width is 160 SVG units)
-    clickDistInBalloons = clickDistInBalloons,
+    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
   )
@@
   fn_score_hedge,
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
@@
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
@@
   fn_score_hedge,
-  replications = 10000,
+  replications = 1,
   method = c("first_second"),
@@
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
@@
   fn_score_box,
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
@@
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
-  careful = FALSE
+  # careful = FALSE
 )
@@
   fn_score_box,
-  replications = 10000,
+  replications = 1,
   method = c("first_second"),
@@
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
-  careful = FALSE,
+  # careful = FALSE,
 )
@@
   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 10000,
+  replications = 1,
   method = c("odd_even"),
-  careful = FALSE,
+  # careful = FALSE,
 )

### 2022-03-23 paper/manuscript.Rmd
add proper splithalf section, change order in variation section

--- 2022-03-21 paper/manuscript.Rmd
@@
 For example ...
-.
 
-- individual differences in developmental psychology:
-- reliable tasks, variation needed, more trials
-- existing tasks for social cognition: wellman
+- why is social cognition important
+- what methods are currently been used?: wellman
+- what are common issues? 
+- what to aim at. individual differences in developmental psychology
+- what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
 - goal of the current project: standardized, easy to use continuous methods
+
+"Recently, it was suggested that a range of cognitive tasks may reliably measure group differences but not individual differences (Hedge et al., 2018).
+As cognitive tests are commonly used to make inferences about individuals, it seems a worthwhile pursuit to improve the reliability with which individual differences are assessed using these tests.
+To judge the success of such pursuits, accurate estimates of reliability are required." (Pronk, Molenaar, Wiers and Murre, 2021, p.
+1)
+"Firstly, reliability is not only a function of task and population sample but also of scoring algorithms." (Pronk, Molenaar, Wiers and Murre, 2021, p. 9)
+"Hence, we conclude that for the datasets included in our reanalysis, cognitive tasks may well have been able to measure individual differences, but that these differences may be relatively unstable over time (Kopp et al., 2021).
+In practice, this may make cognitive tasks suitable for cross-sectional research of individual differences, but not for longitudinal research." (Pronk, Molenaar, Wiers and Murre, 2021, p.
+10)
 
@@
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
-
 The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
@@
 We use URL parameters to capture the participant's ID, language and study version. 
-
 The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
@@
 ## Procedure
-Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
+Children were tested in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study. Adult participated remotely without supervision.
+
 All participants received 15 test trials that were displayed as described above.
-In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.
+In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.
 
@@
 ``` 
+```{r agemodels}
+mAgeHedge <- readRDS(file = "../stats/mAgeHedge.rds") 
+mAgeBox <- readRDS(file = "../stats/mAgeBox.rds") 
+```
 
-We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance.
-In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F).
-By the end of their sixth year of life, children come close to the adult's proficiency level.
-We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.
+We captured a developmental trajectory of gaze cue understanding: with increasing age, participants got more and more accurate in locating the target.
+In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+By the end of their sixth year of life, children came close to the adult's proficiency level.
+We found interindividual variation across study versions and age groups: some three-year-olds were more precise in their responses than some five-year-olds.
 
@@
 `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). 
-Families were recruited on a voluntary basis via email from the institute internal database.
+Families were recruited on a voluntary basis via email from the institute's internal database.
 Every child received a personalized link and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
 Then, caregivers were informed about data security and were asked for their informed consent.
@@
 Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-We stressed that caregivers should not help their children and that all kinds of child behavior were interesting to us.
+We stressed that caregivers should not help their children.
 Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-After completion, families received a little crafting / coloring sheet as a small thank-you gift.
 Depending on the participant's device, the website automatically presented the hedge or box version of the study.
@@
 We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
+Therefore, we asked children to point to the screen, while caregivers were  asked to act as the "digital finger" of their children and click on the indicated box.
 
 As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample.
-We found a minor difference in that children that participate remotely are slightly more precise.
+We found a minor difference in that children that participate remotely were slightly more precise.
 This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
@@
 
+To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with remote unsupervised data collection as the reference category), and target position and subject ID as random effects.
+In the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` ([`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` ([`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]; remote unsupervised data collection as reference category).
+
 ## Discussion
@@
 With increasing age, participants got more and more precise in locating the target.
-We found inter-individual variation in across all age groups.
+We found inter-individual variation across all age groups.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 # Can we capture variation reliably?
-Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
-For this aim, we assessed the internal consistency and test-retest reliability.
+As a next step we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
 The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
@@
 ## Procedure
-The procedure was as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
-The target locations as well as the succession of animals and target colors was randomized once.
-Each participant then received this fixed randomized order of target location, animal, and target color.
+We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
+The target locations as well as the succession of animals and target colors was randomized once and then held constant across participants.
 The child sample received 15 test trials.
@@
 ## Results
-- internal consistency
-- test-retest
 
@@
 
-For estimating the internal consistency, we analyzed the raw performance per subject of the first test day. 
-Our main analysis focuses on an odd-even split on our data.  
-In the hedge version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2B), and an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2C).
-In the box version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2G), and an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2H).
+As a first step for estimating the reliability of our task, we focused on the internal consistency by calculating splithalf reliability coefficients.
+Trials were split into two equally big parts and the performance scores per part were correlated against each other.
+We used the raw performance per subject of the first test day.
+Traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients are shown in Figure 2 B, C, G and H.
 
-A recent paper by [TODO: insert citation splithalfr paper] presents new techniques to analyze internal consistency. 
-The modern statistical approach of stratification allows for a better representation of the data and experimental structure. 
-To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position.
-As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates.
-As might be expected, we found higher coefficients for the samples with higher variation, i.e. for our continuous hedge version of the task.
+As a recent paper by Pronk, Molenaar, Wiers and Murre (2021; TODO insert citation) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+In the hedge version, reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
+In the box version, reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
+Similarly to the results of Pronk, Molenaar, Wiers and Murre (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
+As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
 
-```{r}
-knitr::kable(splithalf, col.names = c("study version", "age group", "splitting method", "stratification", "mean estimate", "lower 95%CI", "upper 95%CI"))
+(ref:figlab3) **Internal Consisteny**. 
+Reliability coefficients per splitting method, stratification level, study version and age group. Error bars show the 95% confidence intervals of the coefficient estimates. 
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gafo_splithalf.png")
 ``` 
-
+## Discussion
 Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
-
-## Discussion
 

### 2022-03-23 paper/manuscript.tex
add proper splithalf section, change order in variation section

--- 2022-03-21 paper/manuscript.tex
@@
 Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-For example \ldots{} .
+For example \ldots{}
 
@@
 \item
-  individual differences in developmental psychology:
+  why is social cognition important
 \item
-  reliable tasks, variation needed, more trials
+  what methods are currently been used?: wellman
 \item
-  existing tasks for social cognition: wellman
+  what are common issues?
+\item
+  what to aim at. individual differences in developmental psychology
+\item
+  what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
 \item
@@
 The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
-
 The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP.
@@
 We use URL parameters to capture the participant's ID, language and study version.
-
 The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
@@
 
-Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
+Children were tested in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study. Adult participated remotely without supervision.
+
 All participants received 15 test trials that were displayed as described above.
-In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.
+In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.
 
@@
 
-We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance.
-In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F).
-By the end of their sixth year of life, children come close to the adult's proficiency level.
-We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.
+We captured a developmental trajectory of gaze cue understanding: with increasing age, participants got more and more accurate in locating the target.
+In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+By the end of their sixth year of life, children came close to the adult's proficiency level.
+We found interindividual variation across study versions and age groups: some three-year-olds were more precise in their responses than some five-year-olds.
 
@@
 27 girls).
-Families were recruited on a voluntary basis via email from the institute internal database.
+Families were recruited on a voluntary basis via email from the institute's internal database.
 Every child received a personalized link and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+In the beginning of the online study, families were invited to enter our ``virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
 Then, caregivers were informed about data security and were asked for their informed consent.
@@
 We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
+Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.
 
 As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample.
-We found a minor difference in that children that participate remotely are slightly more precise.
+We found a minor difference in that children that participate remotely were slightly more precise.
 This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
@@
 
+To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with remote unsupervised data collection as the reference category), and target position and subject ID as random effects.
+In the hedge version, we found an estimate of age of -0.33 ({[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 ({[}-0.50; -0.14{]}).
+In the box version, the estimate of age was 0.64 ({[}0.41; 0.88{]}) and the estimate of data collection mode was 1.16 ({[}0.73; 1.61{]}; remote unsupervised data collection as reference category).
+
 \hypertarget{discussion}{%
@@
 
-Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable.
-For this aim, we assessed the internal consistency and test-retest reliability.
+As a next step we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
 The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
@@
 
-The procedure was as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days.
-The target locations as well as the succession of animals and target colors was randomized once.
-Each participant then received this fixed randomized order of target location, animal, and target color.
+We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days.
+The target locations as well as the succession of animals and target colors was randomized once and then held constant across participants.
 The child sample received 15 test trials.
@@
 
-\begin{itemize}
-\tightlist
-\item
-  internal consistency
-\item
-  test-retest
-\end{itemize}
-
-For estimating the internal consistency, we analyzed the raw performance per subject of the first test day.
-Our main analysis focuses on an odd-even split on our data.\\
-In the hedge version, odd-even splitting yielded an estimate of 0.86 for the child sample (see Figure 2B), and an estimate of 0.77 for the adult sample (see Figure 2C).
-In the box version, odd-even splitting yielded an estimate of 0.55 for the child sample (see Figure 2G), and an estimate of 0.76 for the adult sample (see Figure 2H).
-
-A recent paper by {[}TODO: insert citation splithalfr paper{]} presents new techniques to analyze internal consistency.
-The modern statistical approach of stratification allows for a better representation of the data and experimental structure.
-To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position.
-As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates.
-As might be expected, we found higher coefficients for the samples with higher variation, i.e.~for our continuous hedge version of the task.
-
-\begin{tabular}{l|l|l|l|r|r|r}
-\hline
-study version & age group & splitting method & stratification & mean estimate & lower 95\%CI & upper 95\%CI\\
-\hline
-hedge & kids & random & none & 0.8043888 & 0.6920419 & 0.9164789\\
-\hline
-hedge & kids & random & target position & 0.9476184 & 0.8969928 & 0.9755679\\
-\hline
-hedge & kids & odd even & none & 0.8594840 & 0.7205078 & 0.9093440\\
-\hline
-hedge & kids & odd even & target position & 0.8024165 & 0.5332674 & 0.9298445\\
-\hline
-hedge & kids & first second & none & 0.8181923 & 0.6947852 & 0.9381469\\
-\hline
-hedge & kids & first second & target position & 0.8024165 & 0.5203456 & 0.9246955\\
-\hline
-hedge & adults & random & none & 0.8653142 & 0.7987080 & 0.9165413\\
-\hline
-hedge & adults & random & target position & 0.9239187 & 0.8751052 & 0.9518373\\
-\hline
-hedge & adults & odd even & none & 0.7686066 & 0.5965930 & 0.8631549\\
-\hline
-hedge & adults & odd even & target position & 0.8024056 & 0.6640335 & 0.8818732\\
-\hline
-hedge & adults & first second & none & 0.6752549 & 0.5261556 & 0.7964930\\
-\hline
-hedge & adults & first second & target position & 0.8024056 & 0.6561634 & 0.8822399\\
-\hline
-box & kids & random & none & 0.7660606 & 0.5458261 & 0.8598990\\
-\hline
-box & kids & random & target position & 0.9088431 & 0.8521932 & 0.9424099\\
-\hline
-box & kids & odd even & none & 0.5483231 & 0.3375113 & 0.6922869\\
-\hline
-box & kids & odd even & target position & 0.6137607 & 0.3960722 & 0.7393150\\
-\hline
-box & kids & first second & none & 0.5022750 & 0.2369860 & 0.6633424\\
-\hline
-box & kids & first second & target position & 0.6137607 & 0.3772301 & 0.7354956\\
-\hline
-box & adults & random & none & 0.8004204 & 0.6814629 & 0.8755589\\
-\hline
-box & adults & random & target position & 0.8657569 & 0.7669845 & 0.9221076\\
-\hline
-box & adults & odd even & none & 0.7597443 & 0.6424789 & 0.8387192\\
-\hline
-box & adults & odd even & target position & 0.6673433 & 0.4851349 & 0.7846746\\
-\hline
-box & adults & first second & none & 0.6685946 & 0.4850376 & 0.7642744\\
-\hline
-box & adults & first second & target position & 0.6673433 & 0.4845532 & 0.7820390\\
-\hline
-\end{tabular}
-
-Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
+As a first step for estimating the reliability of our task, we focused on the internal consistency by calculating splithalf reliability coefficients.
+Trials were split into two equally big parts and the performance scores per part were correlated against each other.
+We used the raw performance per subject of the first test day.
+Traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients are shown in Figure 2 B, C, G and H.
+
+As a recent paper by Pronk, Molenaar, Wiers and Murre (2021; TODO insert citation) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+In the hedge version, reliability coefficients ranged from 0.57 to 0.87. In the box version, reliability coefficients ranged from 0.43 to 0.76.
+Similarly to the results of Pronk, Molenaar, Wiers and Murre (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
+As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gafo_splithalf}
+
+}
+
+\caption{\textbf{Internal Consisteny}.
+Reliability coefficients per splitting method, stratification level, study version and age group. Error bars show the 95\% confidence intervals of the coefficient estimates.}\label{fig:fig3}
+\end{figure}
 
@@
 \subsection{Discussion}\label{discussion-1}}
+
+Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
 

### 2022-03-23 stats/analysis.Rmd
add proper splithalf section, change order in variation section

@@
 fn_score_hedge <- function(ds) {
-  return(mean(clickDistInBalloons, na.rm = TRUE))
+  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
 }
@@
 
-# random split
-splitscores_hedge_random_kids <- by_split(
+# first-second half split
+splitscores_hedge_firstsecond_kids <- by_split(
   hedge_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_hedge,
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
-hedge_random_kids_ci  <- split_ci(splitscores_hedge_random_kids, cor)
-
-# create dataframe to save data
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
+hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
+
 splithalf_data <- tibble(
-                    studyversion = "hedge", 
-                    sample = "kids", 
-                    split = "random", 
-                    stratification = "none", 
-                    mean = hedge_random_kids, 
-                    CI_lower = hedge_random_kids_ci$lims["0.025","bca"], 
-                    CI_upper = hedge_random_kids_ci$lims["0.975","bca"])
-
-# random split with stratification by target position
-splitscores_hedge_randomStrat_kids <- by_split(
+                          sample = "kids", 
+                          studyversion = "hedge", 
+                          method = "first-second", 
+                          stratification = "none",                                        
+                          coefficient = hedge_firstsecond_kids, 
+                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
+                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
+                        )
+
+# first-second half stratified by target position
+splitscores_hedge_firstsecondStrat_kids <- by_split(
   hedge_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_hedge,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F, 
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-hedge_randomStrat_kids <- split_coefs(splitscores_hedge_randomStrat_kids, cor)
-hedge_randomStrat_kids_ci <- split_ci(splitscores_hedge_randomStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "kids", 
-                                        split = "random",
-                                        stratification = "target position",
-                                        mean = hedge_randomStrat_kids, 
-                                        CI_lower = hedge_randomStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_randomStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd even split
+)
+
+hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
+hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = hedge_firstsecondStrat_kids,
+                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split
 splitscores_hedge_oddeven_kids <- by_split(
@@
   fn_score_hedge,
-  replications = 1,
   method = c("odd_even"),
+  ncores = 1,
+  verbose = F
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "kids", 
-                                        split = "odd even", 
-                                        stratification = "none", 
-                                        mean = hedge_oddeven_kids, 
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = hedge_oddeven_kids,
                                         CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
@@
 
-# odd even split with stratification by target position
+# odd-even split stratified by target position
 splitscores_hedge_oddevenStrat_kids <- by_split(
@@
   fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F, 
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-  replications = 1,
-  method = c("odd_even"),
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "kids", 
-                                        split = "odd even",
-                                        stratification = "target position",
-                                        mean = hedge_oddevenStrat_kids, 
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = hedge_oddevenStrat_kids,
                                         CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
@@
 
-# first second testhalves split
-splitscores_hedge_firstsecond_kids <- by_split(
+# permutated splitting (random sampling without replacement)
+splitscores_hedge_permutated_kids <- by_split(
   hedge_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_hedge,
-  replications = 1,
-  method = c("first_second"),
-)
-
-hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
-hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "kids", 
-                                        split = "first second", 
-                                        stratification = "none",                                        
-                                        mean = hedge_firstsecond_kids, 
-                                        CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
-                                      )
-
-# first second testhalves split with stratification by target position
-splitscores_hedge_firstsecondStrat_kids <- by_split(
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+)
+
+hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
+hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = hedge_permutated_kids,
+                                        CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
+                                      )
+
+# permutated splitting stratified by target position
+splitscores_hedge_permutatedStrat_kids <- by_split(
   hedge_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-  replications = 1,
-  method = c("odd_even"),
-)
-
-hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
-hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "kids", 
-                                        split = "first second",
-                                        stratification = "target position",
-                                        mean = hedge_firstsecondStrat_kids, 
-                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
+)
+
+hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
+hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = hedge_permutatedStrat_kids,
+                                        CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo (sampling with replacement)
+splitscores_hedge_montecarlo_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+)
+
+hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
+hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = hedge_montecarlo_kids,
+                                        CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo stratified by target position
+splitscores_hedge_montecarloStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
+hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "hedge", 
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = hedge_montecarloStrat_kids,
+                                        CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
                                       )
@@
 ```{r splithalfr_hedge_adults}
-# random split
-splitscores_hedge_random_adults <- by_split(
+# first-second half split
+splitscores_hedge_firstsecond_adults <- by_split(
   hedge_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_hedge,
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-hedge_random_adults <- split_coefs(splitscores_hedge_random_adults, cor)
-hedge_random_adults_ci  <- split_ci(splitscores_hedge_random_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "random", 
-                                        stratification = "none", 
-                                        mean = hedge_random_adults, 
-                                        CI_lower = hedge_random_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_random_adults_ci$lims["0.975","bca"]
-                                      )
-
-# random split with stratification by target position
-splitscores_hedge_randomStrat_adults <- by_split(
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
+hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                              sample = "adults", 
+                                              studyversion = "hedge", 
+                                              method = "first-second", 
+                                              stratification = "none",                                        
+                                              coefficient = hedge_firstsecond_adults, 
+                                              CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
+                                              CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
+                                            )
+
+# first-second half stratified by target position
+splitscores_hedge_firstsecondStrat_adults <- by_split(
   hedge_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_hedge,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F, 
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-hedge_randomStrat_adults <- split_coefs(splitscores_hedge_randomStrat_adults, cor)
-hedge_randomStrat_adults_ci <- split_ci(splitscores_hedge_randomStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "random",
-                                        stratification = "target position",
-                                        mean = hedge_randomStrat_adults, 
-                                        CI_lower = hedge_randomStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_randomStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd even split
+)
+
+hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
+hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = hedge_firstsecondStrat_adults,
+                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split
 splitscores_hedge_oddeven_adults <- by_split(
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "odd even", 
-                                        stratification = "none", 
-                                        mean = hedge_oddeven_adults, 
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = hedge_oddeven_adults,
                                         CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
@@
 
-# odd even split with stratification by target position
+# odd-even split stratified by target position
 splitscores_hedge_oddevenStrat_adults <- by_split(
@@
   fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F, 
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-  replications = 1,
-  method = c("odd_even"),
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "odd even",
-                                        stratification = "target position",
-                                        mean = hedge_oddevenStrat_adults, 
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = hedge_oddevenStrat_adults,
                                         CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
@@
 
-# first second testhalves split
-splitscores_hedge_firstsecond_adults <- by_split(
+# permutated splitting (random sampling without replacement)
+splitscores_hedge_permutated_adults <- by_split(
   hedge_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_hedge,
-  replications = 1,
-  method = c("first_second"),
-)
-
-hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
-hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "first second", 
-                                        stratification = "none",                                        
-                                        mean = hedge_firstsecond_adults, 
-                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
-                                      )
-
-# first second testhalves split with stratification by target position
-splitscores_hedge_firstsecondStrat_adults <- by_split(
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+)
+
+hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
+hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = hedge_permutated_adults,
+                                        CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
+                                      )
+
+# permutated splitting stratified by target position
+splitscores_hedge_permutatedStrat_adults <- by_split(
   hedge_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-  replications = 1,
-  method = c("odd_even"),
-)
-
-hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
-hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "hedge", 
-                                        sample = "adults", 
-                                        split = "first second",
-                                        stratification = "target position",
-                                        mean = hedge_firstsecondStrat_adults, 
-                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
+)
+
+hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
+hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = hedge_permutatedStrat_adults,
+                                        CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo (sampling with replacement)
+splitscores_hedge_montecarlo_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+)
+
+hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
+hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = hedge_montecarlo_adults,
+                                        CI_lower = hedge_montecarlo_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_montecarlo_adults_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo stratified by target position
+splitscores_hedge_montecarloStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
+hedge_montecarloStrat_adults_ci <- split_ci(splitscores_hedge_montecarloStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "hedge", 
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = hedge_montecarloStrat_adults,
+                                        CI_lower = hedge_montecarloStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = hedge_montecarloStrat_adults_ci$lims["0.975","bca"]
                                       )
@@
 
-box_intCon_data %>% 
-  group_by(subjID, targetPosition) %>% 
-  summarise(n = n()) %>% 
-  filter(n < 2)
-
-# random split
-splitscores_box_random_kids <- by_split(
+# first-second half split
+splitscores_box_firstsecond_kids <- by_split(
   box_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_box,
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-box_random_kids <- split_coefs(splitscores_box_random_kids, cor)
-box_random_kids_ci  <- split_ci(splitscores_box_random_kids, cor)
-
-# create dataframe to save data
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "random", 
-                                        stratification = "none", 
-                                        mean = box_random_kids, 
-                                        CI_lower = box_random_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_random_kids_ci$lims["0.975","bca"])
-
-# random split with stratification by target position
-splitscores_box_randomStrat_kids <- by_split(
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
+box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                              sample = "kids", 
+                                              studyversion = "box", 
+                                              method = "first-second", 
+                                              stratification = "none",                                        
+                                              coefficient = box_firstsecond_kids, 
+                                              CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
+                                              CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
+                                            )
+
+# first-second half stratified by target position
+splitscores_box_firstsecondStrat_kids <- by_split(
   box_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-  careful = FALSE, 
-)
-
-box_randomStrat_kids <- split_coefs(splitscores_box_randomStrat_kids, cor)
-box_randomStrat_kids_ci <- split_ci(splitscores_box_randomStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "random",
-                                        stratification = "target position",
-                                        mean = box_randomStrat_kids, 
-                                        CI_lower = box_randomStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_randomStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd even split
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F, 
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
+box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = box_firstsecondStrat_kids,
+                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split
 splitscores_box_oddeven_kids <- by_split(
@@
   fn_score_box,
-  replications = 1,
   method = c("odd_even"),
+  ncores = 1,
+  verbose = F
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "odd even", 
-                                        stratification = "none", 
-                                        mean = box_oddeven_kids, 
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = box_oddeven_kids,
                                         CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
@@
 
-# odd even split with stratification by target position
+# odd-even split stratified by target position
 splitscores_box_oddevenStrat_kids <- by_split(
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 1,
   method = c("odd_even"),
-  # careful = FALSE
+  ncores = 1,
+  verbose = F, 
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "odd even",
-                                        stratification = "target position",
-                                        mean = box_oddevenStrat_kids, 
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = box_oddevenStrat_kids,
                                         CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
@@
 
-# first second testhalves split
-splitscores_box_firstsecond_kids <- by_split(
+# permutated splitting (random sampling without replacement)
+splitscores_box_permutated_kids <- by_split(
   box_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_box,
-  replications = 1,
-  method = c("first_second"),
-)
-
-box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
-box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "first second", 
-                                        stratification = "none",                                        
-                                        mean = box_firstsecond_kids, 
-                                        CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
-                                      )
-
-# first second testhalves split with stratification by target position
-splitscores_box_firstsecondStrat_kids <- by_split(
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+)
+
+box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
+box_permutated_kids_ci <- split_ci(splitscores_box_permutated_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = box_permutated_kids,
+                                        CI_lower = box_permutated_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_permutated_kids_ci$lims["0.975","bca"]
+                                      )
+
+# permutated splitting stratified by target position
+splitscores_box_permutatedStrat_kids <- by_split(
   box_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
-  replications = 1,
-  method = c("odd_even"),
-  # careful = FALSE,
-)
-
-box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
-box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "kids", 
-                                        split = "first second",
-                                        stratification = "target position",
-                                        mean = box_firstsecondStrat_kids, 
-                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
+box_permutatedStrat_kids_ci <- split_ci(splitscores_box_permutatedStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = box_permutatedStrat_kids,
+                                        CI_lower = box_permutatedStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_permutatedStrat_kids_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo (sampling with replacement)
+splitscores_box_montecarlo_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+)
+
+box_montecarlo_kids <- split_coefs(splitscores_box_montecarlo_kids, cor)
+box_montecarlo_kids_ci <- split_ci(splitscores_box_montecarlo_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = box_montecarlo_kids,
+                                        CI_lower = box_montecarlo_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_montecarlo_kids_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo stratified by target position
+splitscores_box_montecarloStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_montecarloStrat_kids <- split_coefs(splitscores_box_montecarloStrat_kids, cor)
+box_montecarloStrat_kids_ci <- split_ci(splitscores_box_montecarloStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids", 
+                                        studyversion = "box", 
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = box_montecarloStrat_kids,
+                                        CI_lower = box_montecarloStrat_kids_ci$lims["0.025","bca"], 
+                                        CI_upper = box_montecarloStrat_kids_ci$lims["0.975","bca"]
                                       )
@@
 ```{r splithalfr_box_adults}
-# random split
-splitscores_box_random_adults <- by_split(
+# first-second half split
+splitscores_box_firstsecond_adults <- by_split(
   box_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_box,
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-)
-
-box_random_adults <- split_coefs(splitscores_box_random_adults, cor)
-box_random_adults_ci  <- split_ci(splitscores_box_random_adults, cor)
-
-# create dataframe to save data
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "random", 
-                                        stratification = "none", 
-                                        mean = box_random_adults, 
-                                        CI_lower = box_random_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_random_adults_ci$lims["0.975","bca"]
-                                      )
-
-# random split with stratification by target position
-splitscores_box_randomStrat_adults <- by_split(
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
+box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                              sample = "adults", 
+                                              studyversion = "box", 
+                                              method = "first-second", 
+                                              stratification = "none",                                        
+                                              coefficient = box_firstsecond_adults, 
+                                              CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
+                                              CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
+                                            )
+
+# first-second half stratified by target position
+splitscores_box_firstsecondStrat_adults <- by_split(
   box_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 10000,
-  method = c("random"),
-  replace = TRUE,
-  split_p = 1,
-  careful = FALSE,
-)
-
-box_randomStrat_adults <- split_coefs(splitscores_box_randomStrat_adults, cor)
-box_randomStrat_adults_ci <- split_ci(splitscores_box_randomStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "random",
-                                        stratification = "target position",
-                                        mean = box_randomStrat_adults, 
-                                        CI_lower = box_randomStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_randomStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd even split
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F, 
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
+box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = box_firstsecondStrat_adults,
+                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split
 splitscores_box_oddeven_adults <- by_split(
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "odd even", 
-                                        stratification = "none", 
-                                        mean = box_oddeven_adults, 
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = box_oddeven_adults,
                                         CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
@@
 
-# odd even split with stratification by target position
+# odd-even split stratified by target position
 splitscores_box_oddevenStrat_adults <- by_split(
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 1,
   method = c("odd_even"),
-  # careful = FALSE,
+  ncores = 1,
+  verbose = F, 
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
 )
@@
 splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "odd even",
-                                        stratification = "target position",
-                                        mean = box_oddevenStrat_adults, 
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = box_oddevenStrat_adults,
                                         CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
@@
 
-# first second testhalves split
-splitscores_box_firstsecond_adults <- by_split(
+# permutated splitting (random sampling without replacement)
+splitscores_box_permutated_adults <- by_split(
   box_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_box,
-  replications = 1,
-  method = c("first_second"),
-)
-
-box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
-box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "first second", 
-                                        stratification = "none",                                        
-                                        mean = box_firstsecond_adults, 
-                                        CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
-                                      )
-
-# first second testhalves split with stratification by target position
-splitscores_box_firstsecondStrat_adults <- by_split(
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+)
+
+box_permutated_adults <- split_coefs(splitscores_box_permutated_adults, cor)
+box_permutated_adults_ci <- split_ci(splitscores_box_permutated_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = box_permutated_adults,
+                                        CI_lower = box_permutated_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_permutated_adults_ci$lims["0.975","bca"]
+                                      )
+
+# permutated splitting stratified by target position
+splitscores_box_permutatedStrat_adults <- by_split(
   box_intCon_data %>% filter(sample == "adults"),
@@
   fn_score_box,
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
-  replications = 1,
-  method = c("odd_even"),
-  # careful = FALSE,
-)
-
-box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
-box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        studyversion = "box", 
-                                        sample = "adults", 
-                                        split = "first second",
-                                        stratification = "target position",
-                                        mean = box_firstsecondStrat_adults, 
-                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_permutatedStrat_adults <- split_coefs(splitscores_box_permutatedStrat_adults, cor)
+box_permutatedStrat_adults_ci <- split_ci(splitscores_box_permutatedStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = box_permutatedStrat_adults,
+                                        CI_lower = box_permutatedStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_permutatedStrat_adults_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo (sampling with replacement)
+splitscores_box_montecarlo_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+)
+
+box_montecarlo_adults <- split_coefs(splitscores_box_montecarlo_adults, cor)
+box_montecarlo_adults_ci <- split_ci(splitscores_box_montecarlo_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = box_montecarlo_adults,
+                                        CI_lower = box_montecarlo_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_montecarlo_adults_ci$lims["0.975","bca"]
+                                      )
+
+# monte carlo stratified by target position
+splitscores_box_montecarloStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("random"),
+  ncores = 1,
+  verbose = F, 
+  replications = 1,
+  replace = TRUE,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_montecarloStrat_adults <- split_coefs(splitscores_box_montecarloStrat_adults, cor)
+box_montecarloStrat_adults_ci <- split_ci(splitscores_box_montecarloStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults", 
+                                        studyversion = "box", 
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = box_montecarloStrat_adults,
+                                        CI_lower = box_montecarloStrat_adults_ci$lims["0.025","bca"], 
+                                        CI_upper = box_montecarloStrat_adults_ci$lims["0.975","bca"]
                                       )
@@
 splithalf_data %>% 
-  mutate(sample = fct_rev(sample)) %>%
+  mutate(
+    sample = fct_rev(sample), 
+  ) %>%
   unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
   mutate(samplegroup = fct_rev(samplegroup)) %>%
-  unite("method", c(split, stratification), sep = ", ", remove = FALSE) %>% 
-  ggplot(aes(x = method, y = mean, color = sample, group = studyversion)) + 
+  unite("methodStrat", c(method, stratification), sep = " - ", remove = FALSE) %>% 
+  mutate(
+    methodStrat = factor(methodStrat, levels = c("first-second - none", "first-second - target position", "odd-even - none", "odd-even - target position", "permutated - none", "permutated - target position", "Monte Carlo - none", "Monte Carlo - target position")) %>% fct_rev(),
+  ) %>%  
+  ggplot(aes(x = methodStrat, y = coefficient, color = sample, group = studyversion)) + 
     geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
@@
     coord_flip() + 
-    facet_wrap(~ samplegroup) + 
+    facet_wrap(~ samplegroup, nrow = 1) + 
     theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
 
-ggsave("../figures/gafo_splithalf.png", width = 6, height = 4, scale = 1.4)
+ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
 ```

### 2022-04-01 paper/manuscript.Rmd
clean refs, reorder remote testing, add webcam analysis

@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["../../references.bib"]
 
@@
 library("papaja")
-r_refs("r-references.bib")
+# r_refs("r-references.bib")
 ```
@@
 10)
+
+Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1–13. https://doi.org/10.1038/s44159-022-00037-z:
+"The way humans view agents, be it others or themselves, differs radically from the way humans view the rest of the world.
+This difference is because agents feel, perceive and think.
+Agents see the world from their own subjective perspective and they rationally plan, form intentions and act accordingly.
+This way of seeing others as rational subjects with individual perspectives on the world is termed theory of mind (ToM)." (p.
+1)
+"ToM also has specific real-life consequences.
+First, the development of ToM competence goes along with general measures of children’s peer social skills in early and middle childhood.
+(...) Second, ToM specifically predicts communicative competence.
+(...) Third, ToM competence is related to the quality of peer relationships: children with more advanced ToM are rated as more likeable and popular among their peers.
+Fourth, children who are more proficient at ToM tasks tend to act more prosocially, including comforting, sharing or helping other individuals.
+Finally, preschool ToM competence predicts achievement in primary school, a relationship that is possibly mediated by social competence, in that preschool ToM abilities enable subsequent social competence development, which in turn contributes to school achievement." (p.
+2)
+"Evidence for an emerging understanding of perception at 9 months of age comes from various sources.
+For example, children begin to follow the gaze of other agents in systematic and differential ways: they follow an agent’s head turn only when the agent can actually see (has their eyes open rather than closed, or wears a transparent rather than an opaque blindfold)." (p.
+2)
+Developmental determinants: executive function, language ("that" complementations), social (SES, siblings, mind-minded parents)
+Implicit tasks: "A third class of implicit ToM tasks is interaction tasks, in which participants are involved in a communicative or cooperative interaction with another agent.
+This agent forms a mental state (such as a true or false belief regarding the contents of a box) and experimenters measure whether participants spontaneously take the agent’s belief into account in their interaction with the agent (for instance by helping or by interpreting the agent’s communicative acts accordingly)" (p.
+9)
+=> reliable & valid tasks to assess coherent development of social-cognitive functions
 
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements. 
+The GreenSock Animation Platform (GSAP; @greensock2022gsap) library was used to animate the movement of single SVG elements. 
 We use URL parameters to capture the participant's ID, language and study version. 
@@
 ## Data processing
-We used `r cite_r("r-references.bib")` for all our analyses. Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses. 
+We used `r R.version$version.string` [@rcoreteam2022language], and the packages *splithalfr* [@pronk2021methods] and *brms* [@burkner2017brms; @burkner2018advanced] for all our analyses.
+Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
 All test trials without voice over description are included in our analyses.
@@
 # Does the balloon finding task induce variation?
-Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
+Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample.
+Furthermore, we were interested in how the data collection mode influences responses.
+To analyze how the in-person collected data compares to data that gets collected in a online without supervision, we collected a remote child and adult sample.
+
 The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample).
@@
 The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between May 2021 and XXX 2022.
+Data was collected between May and October 2021.
 
@@
 ## Participants
-For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-Children in our sample grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
-The child sample consisted of 
+We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
+In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+The in-person child sample consisted of
 `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
@@
 `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).
-Children received a small thank-you gift for their participation in the study.
 
-In addition, we recruited adult participants by advertising the study on *Prolific*.
+For our remote child sample, we recruited families on a voluntary basis via email from the institute's internal database.
+Our remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
+`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
+and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
+SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
+range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
+- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
+`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
+Children in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+
+In addition, we recruited a remote adult sample by advertising the study on *Prolific*.
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 ## Procedure
-Children were tested in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study. Adult participated remotely without supervision.
+Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
+Children in the remote sample received a personalized link to the study websites and families could participate at any time or location they wanted.
+In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+We stressed that caregivers should not help their children.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Depending on the participant's device, the website automatically presented the hedge or box version of the study.
+For families that used a tablet with touchscreen, the hedge version was shown.
+Here, children could directly click on the touchscreen themselves to indicate where the target is.
+For families that used a computer without touchscreen, the website presented the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen, while caregivers were  asked to act as the "digital finger" of their children and click on the indicated box.
+
+Our adult sample participated remotely without supervision.
 
@@
 
-### Remote data collection
-Since our task is implemented in a way that no experimenter interaction is necessary, data can also be collected without supervision. 
-To assess whether we would gain similar results in a remote testing context, we recruited an additional online sample of `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
-and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). 
-Families were recruited on a voluntary basis via email from the institute's internal database.
-Every child received a personalized link and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Depending on the participant's device, the website automatically presented the hedge or box version of the study.
-For families that used a tablet with touchscreen, the hedge version was shown.
-Here, children could directly click on the touchscreen themselves to indicate where the target is.
-For families that used a computer without touchscreen, the website presented the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen, while caregivers were  asked to act as the "digital finger" of their children and click on the indicated box.
+As Figure 2 A and F show, our remotely collected data resembled the data from the kindergarten sample. 
+To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with in-person supervised data collection as the reference category), and target position and subject ID as random effects.
+In the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+Note that the effect of data collection appears to be present, but confidence intervals are wide.
 
-As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample.
-We found a minor difference in that children that participate remotely were slightly more precise.
+Our GLMM analysis, therefore, corroborated the effects of age and data collection mode that we already identified by visual inspection. 
+We found evidence that responses of children participating remotely were slightly more precise.
 This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
-It is conceivable that caregivers were especially prone to help with the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
+It is conceivable that caregivers were especially prone to influence the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^p]
 
-To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with remote unsupervised data collection as the reference category), and target position and subject ID as random effects.
-In the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` ([`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
-In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` ([`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]; remote unsupervised data collection as reference category).
+[^p]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
+We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
+A trial was defined as the time between two eye blinking sounds.
+We transcribed all utterances by parents and children and counted the words uttered by each.
+We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
+In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial. 
+We ran exploratory analyses .
+Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
+Our null model explained the the response behavior by age, while including random effects for subject and target position.
+We compared this null model to models including the number of words utterred by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes.
+Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
+On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+On a subject level, the effect reversed - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+Additionally, number of repeated testquestions displayed a negative estimate on the subject level: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+[TODO:] In all cases, however, standard errors of the WAIC score differences where greater than the ELPD difference scores themselves.
+Similarly, 95% CI of the model estimates included zero and were rather wide.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
 
@@
 With increasing age, participants got more and more precise in locating the target.
-We found inter-individual variation across all age groups.
+We found interindividual variation across all age groups.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between XXX 2021 and XXX 2022.
+Data was collected between July 2021 and April 2022.
 
@@
 
-As a recent paper by Pronk, Molenaar, Wiers and Murre (2021; TODO insert citation) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+As a recent paper by @pronk2021methods suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 In the box version, reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
-Similarly to the results of Pronk, Molenaar, Wiers and Murre (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+Similarly to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
 In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
@@
 ## Participants
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This ub sample consisted of 
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of 
 `r sum(pe_sample$nTotal)` children, including 
@@
 For our remote unsupervised testing sample, families were recruited on a voluntary basis via email from the database of the Max Planck Institute for Evolutionary Anthropology.
-Children in both sub samples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
+Children in both subsamples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
 Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

### 2022-04-01 paper/manuscript.tex
clean refs, reorder remote testing, add webcam analysis

@@
 
+``Recently, it was suggested that a range of cognitive tasks may reliably measure group differences but not individual differences (Hedge et al., 2018).
+As cognitive tests are commonly used to make inferences about individuals, it seems a worthwhile pursuit to improve the reliability with which individual differences are assessed using these tests.
+To judge the success of such pursuits, accurate estimates of reliability are required.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~1)
+``Firstly, reliability is not only a function of task and population sample but also of scoring algorithms.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~9)
+``Hence, we conclude that for the datasets included in our reanalysis, cognitive tasks may well have been able to measure individual differences, but that these differences may be relatively unstable over time (Kopp et al., 2021).
+In practice, this may make cognitive tasks suitable for cross-sectional research of individual differences, but not for longitudinal research.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~10)
+
+Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}:
+``The way humans view agents, be it others or themselves, differs radically from the way humans view the rest of the world.
+This difference is because agents feel, perceive and think.
+Agents see the world from their own subjective perspective and they rationally plan, form intentions and act accordingly.
+This way of seeing others as rational subjects with individual perspectives on the world is termed theory of mind (ToM).'' (p.~1)
+``ToM also has specific real-life consequences.
+First, the development of ToM competence goes along with general measures of children's peer social skills in early and middle childhood.
+(\ldots) Second, ToM specifically predicts communicative competence.
+(\ldots) Third, ToM competence is related to the quality of peer relationships: children with more advanced ToM are rated as more likeable and popular among their peers.
+Fourth, children who are more proficient at ToM tasks tend to act more prosocially, including comforting, sharing or helping other individuals.
+Finally, preschool ToM competence predicts achievement in primary school, a relationship that is possibly mediated by social competence, in that preschool ToM abilities enable subsequent social competence development, which in turn contributes to school achievement.'' (p.~2)
+``Evidence for an emerging understanding of perception at 9 months of age comes from various sources.
+For example, children begin to follow the gaze of other agents in systematic and differential ways: they follow an agent's head turn only when the agent can actually see (has their eyes open rather than closed, or wears a transparent rather than an opaque blindfold).'' (p.~2)
+Developmental determinants: executive function, language (``that'' complementations), social (SES, siblings, mind-minded parents)
+Implicit tasks: ``A third class of implicit ToM tasks is interaction tasks, in which participants are involved in a communicative or cooperative interaction with another agent.
+This agent forms a mental state (such as a true or false belief regarding the contents of a box) and experimenters measure whether participants spontaneously take the agent's belief into account in their interaction with the agent (for instance by helping or by interpreting the agent's communicative acts accordingly)'' (p.~9)
+=\textgreater{} reliable \& valid tasks to assess coherent development of social-cognitive functions
+
 \hypertarget{design-of-our-balloon-finding-task}{%
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements.
+The GreenSock Animation Platform (GSAP; Greensock (2022)) library was used to animate the movement of single SVG elements.
 We use URL parameters to capture the participant's ID, language and study version.
@@
 
-We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{brms} (Version 2.15.0; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.6; Eddelbuettel \& François, 2011), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{splithalfr} (Version 2.1.1; Thomas, Dylan, Reinout, \& Jaap, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyboot} (Version 0.1.1; Braginsky \& Yurovsky, 2018), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.1; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses.
+We used R version 4.1.3 (2022-03-10) (R Core Team, 2022), and the packages \emph{splithalfr} (Pronk, Molenaar, Wiers, \& Murre, 2021) and \emph{brms} (Bürkner, 2017, 2018) for all our analyses.
 Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
@@
 
-Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample.
+Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample.
+Furthermore, we were interested in how the data collection mode influences responses.
+To analyze how the in-person collected data compares to data that gets collected in a online without supervision, we collected a remote child and adult sample.
+
 The pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and here: \url{https://osf.io/r3bhn} (adult sample).
@@
 
-For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-Children in our sample grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
-The child sample consisted of
+We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
+In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
+The in-person child sample consisted of
 120 children, including
@@
 22 girls).
-Children received a small thank-you gift for their participation in the study.
-
-In addition, we recruited adult participants by advertising the study on \emph{Prolific}.
+
+For our remote child sample, we recruited families on a voluntary basis via email from the institute's internal database. Our remote child sample included 147 children, including
+45 3-year-olds
+(mean = 42.62 months,
+SD = 3.35,
+range = 36
+- 47,
+14 girls),
+47 4-year-olds
+(mean = 52.64 months,
+SD = 3.40,
+range = 48
+- 59,
+25 girls),
+and 55 5-year-olds
+(mean = 65.11 months,
+SD = 3.77,
+range = 60
+- 71,
+27 girls).
+Children in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+
+In addition, we recruited a remote adult sample by advertising the study on \emph{Prolific}.
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 
-Children were tested in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study. Adult participated remotely without supervision.
+Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
+Children in the remote sample received a personalized link to the study websites and families could participate at any time or location they wanted.
+In the beginning of the online study, families were invited to enter our ``virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Then, caregivers were informed about data security and were asked for their informed consent.
+They were asked to enable the sound and seat their child centrally in front of their device.
+Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+We stressed that caregivers should not help their children.
+Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Depending on the participant's device, the website automatically presented the hedge or box version of the study.
+For families that used a tablet with touchscreen, the hedge version was shown.
+Here, children could directly click on the touchscreen themselves to indicate where the target is.
+For families that used a computer without touchscreen, the website presented the box version of the task.
+We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.
+
+Our adult sample participated remotely without supervision.
 
@@
 
-\hypertarget{remote-data-collection}{%
-\subsubsection{Remote data collection}\label{remote-data-collection}}
-
-Since our task is implemented in a way that no experimenter interaction is necessary, data can also be collected without supervision.
-To assess whether we would gain similar results in a remote testing context, we recruited an additional online sample of 147 children, including
-45 3-year-olds
-(mean = 42.62 months,
-SD = 3.35,
-range = 36
-- 47,
-14 girls),
-47 4-year-olds
-(mean = 52.64 months,
-SD = 3.40,
-range = 48
-- 59,
-25 girls),
-and 55 5-year-olds
-(mean = 65.11 months,
-SD = 3.77,
-range = 60
-- 71,
-27 girls).
-Families were recruited on a voluntary basis via email from the institute's internal database.
-Every child received a personalized link and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter our ``virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Depending on the participant's device, the website automatically presented the hedge or box version of the study.
-For families that used a tablet with touchscreen, the hedge version was shown.
-Here, children could directly click on the touchscreen themselves to indicate where the target is.
-For families that used a computer without touchscreen, the website presented the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.
-
-As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample.
-We found a minor difference in that children that participate remotely were slightly more precise.
+As Figure 2 A and F show, our remotely collected data resembled the data from the kindergarten sample.
+To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with in-person supervised data collection as the reference category), and target position and subject ID as random effects.
+In the hedge version, we found an estimate of age of -0.33 (95\% CI {[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 (95\% CI {[}-0.50; -0.14{]}).
+In the box version, the estimate of age was 0.64 (95\% CI {[}0.41; 0.88{]}) and the estimate of data collection mode was 1.16 (95\% CI {[}0.73; 1.61{]}).
+Note that the effect of data collection appears to be present, but confidence intervals are wide.
+
+Our GLMM analysis, therefore, corroborated the effects of age and data collection mode that we already identified by visual inspection.
+We found evidence that responses of children participating remotely were slightly more precise.
 This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
-It is conceivable that caregivers were especially prone to help with the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
-
-To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with remote unsupervised data collection as the reference category), and target position and subject ID as random effects.
-In the hedge version, we found an estimate of age of -0.33 ({[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 ({[}-0.50; -0.14{]}).
-In the box version, the estimate of age was 0.64 ({[}0.41; 0.88{]}) and the estimate of data collection mode was 1.16 ({[}0.73; 1.61{]}; remote unsupervised data collection as reference category).
+It is conceivable that caregivers were especially prone to influence the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.\footnote{In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
+We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
+  A trial was defined as the time between two eye blinking sounds.
+We transcribed all utterances by parents and children and counted the words uttered by each.
+We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
+  In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
+  We ran exploratory analyses .
+Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
+Our null model explained the the response behavior by age, while including random effects for subject and target position.
+We compared this null model to models including the number of words utterred by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes.
+Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
+  On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+On a subject level, the effect reversed - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+Additionally, number of repeated testquestions displayed a negative estimate on the subject level: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+{[}TODO:{]} In all cases, however, standard errors of the WAIC score differences where greater than the ELPD difference scores themselves.
+Similarly, 95\% CI of the model estimates included zero and were rather wide.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.}
 
@@
 
-As a recent paper by Pronk, Molenaar, Wiers and Murre (2021; TODO insert citation) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+As a recent paper by Pronk et al.
+(2021) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 In the hedge version, reliability coefficients ranged from 0.57 to 0.87. In the box version, reliability coefficients ranged from 0.43 to 0.76.
-Similarly to the results of Pronk, Molenaar, Wiers and Murre (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+Similarly to the results of Pronk et al.
+(2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
 In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
@@
 
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This ub sample consisted of
+For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
 130 children, including
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
-Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
-Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyboot}{}}%
-Braginsky, M., \& Yurovsky, D. (2018). \emph{Tidyboot: Tidyverse-compatible bootstrapping}. Retrieved from \url{https://CRAN.R-project.org/package=tidyboot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-brms_a}{}}%
-Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-brms_b}{}}%
-Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_b}{}}%
-Eddelbuettel, D., \& Balamuta, J.
-J.
-(2018).
-{Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}.
-\emph{The American Statistician}, \emph{72}(1), 28--36.
-\url{https://doi.org/10.1080/00031305.2017.1375990}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_a}{}}%
-Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggpubr}{}}%
-Kassambara, A. (2020). \emph{Ggpubr: 'ggplot2' based publication ready plots}. Retrieved from \url{https://CRAN.R-project.org/package=ggpubr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-splithalfr}{}}%
-Thomas, P., Dylan, M., Reinout, W., \& Jaap, M.
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
+Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1). \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2018advanced}{}}%
+Bürkner, P.-C. (2018). Advanced {Bayesian Multilevel Modeling} with the {R Package} brms. \emph{The R Journal}, \emph{10}(1), 395. \url{https://doi.org/10.32614/RJ-2018-017}
+
+\leavevmode\vadjust pre{\hypertarget{ref-greensock2022gsap}{}}%
+Greensock. (2022). \emph{{GSAP} ({GreenSock Animation Platform})}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pronk2021methods}{}}%
+Pronk, T., Molenaar, D., Wiers, R.
+W., \& Murre, J.
 (2021).
-Methods to split cognitive task data for estimating split-half reliability: A comprehensive review and systematic assessment.
-\emph{Psychonomic Bulletin \& Review}, 1--11.
+Methods to split cognitive task data for estimating split-half reliability: {A} comprehensive review and systematic assessment.
+\emph{Psychonomic Bulletin \& Review}.
 \url{https://doi.org/10.3758/s13423-021-01948-3}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
-Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+\leavevmode\vadjust pre{\hypertarget{ref-rcoreteam2022language}{}}%
+R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.
 

### 2022-04-06 paper/manuscript.Rmd
create saves folder, add webcam coding script

@@
 
-## Data processing
-We used `r R.version$version.string` [@rcoreteam2022language], and the packages *splithalfr* [@pronk2021methods] and *brms* [@burkner2017brms; @burkner2018advanced] for all our analyses.
-Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
-All test trials without voice over description are included in our analyses.
-
 # Does the balloon finding task induce variation?
@@
 Furthermore, we were interested in how the data collection mode influences responses.
-To analyze how the in-person collected data compares to data that gets collected in a online without supervision, we collected a remote child and adult sample.
 
@@
 
+## Analysis
+All test trials without voice over description were included in our analyses.
+We ran all analyses in `r R.version$version.string` [@rcoreteam2022language]. 
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+
+To estimate the developmental trajectory of gaze cue understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
+Here, `targetPosition` refers to the absolute bin/box of the target, while `symmetricPosition` refers to the distance from the stimulus center (i.e., smaller value meaning more central target position).
+We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
+
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a lognormal distribution.
+For the box version, the model predicted correct responses (0/1) using a Bernoulli distribution with a logit link function.
+We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
+
 ## Results
@@
 (j) Test-retest reliability in box adult sample.
-Regression lines with 95% CI show product-moment-correlations with Pearson's correlation coefficient r. 
+Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r.* 
 Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
 Small data points show the mean performance for each subject.
-Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
+Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
 Color of data points represent each age group (binned by year).
@@
 ```{r agemodels}
-mAgeHedge <- readRDS(file = "../stats/mAgeHedge.rds") 
-mAgeBox <- readRDS(file = "../stats/mAgeBox.rds") 
+mAgeHedge <- readRDS(file = "../saves/mAgeHedge.rds") 
+mAgeBox <- readRDS(file = "../saves/mAgeBox.rds") 
 ```
@@
 In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+Most participants in the box version performed above chance level.
 By the end of their sixth year of life, children came close to the adult's proficiency level.
-We found interindividual variation across study versions and age groups: some three-year-olds were more precise in their responses than some five-year-olds.
+We found interindividual variation across study versions and age groups.
+For instance, this can be seen in that some three-year-olds were more precise in their responses than some five-year-olds.
 
-As Figure 2 A and F show, our remotely collected data resembled the data from the kindergarten sample. 
-To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with in-person supervised data collection as the reference category), and target position and subject ID as random effects.
-In the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
-In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]).
-Note that the effect of data collection appears to be present, but confidence intervals are wide.
-
-Our GLMM analysis, therefore, corroborated the effects of age and data collection mode that we already identified by visual inspection. 
+As Figure 2 A and F show, our remotely collected child data resembled the data from the kindergarten sample. 
 We found evidence that responses of children participating remotely were slightly more precise.
@@
 It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^p]
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^fn1]
 
-[^p]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
+[^fn1]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-A trial was defined as the time between two eye blinking sounds.
-We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
-In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial. 
-We ran exploratory analyses .
-Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
-Our null model explained the the response behavior by age, while including random effects for subject and target position.
-We compared this null model to models including the number of words utterred by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes.
-Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
-On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-On a subject level, the effect reversed - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-Additionally, number of repeated testquestions displayed a negative estimate on the subject level: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
-[TODO:] In all cases, however, standard errors of the WAIC score differences where greater than the ELPD difference scores themselves.
-Similarly, 95% CI of the model estimates included zero and were rather wide.
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
+Based on our model comparison, we conclude that there is no clear evidence of a stable effect of parental interference.
+See Supplements for further detail.
+
+Our GLMM analysis corroborated the effects of age and data collection mode that we already identified by visual inspection: in the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+Note that the effect of data collection appears to be present, but confidence intervals are wide.
 
@@
 # Can we capture variation reliably?
-As a next step we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable (i.e.,
+systematically order individuals in the same way).
 For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
@@
 ## Participants
-For our child sample, we again went to kindergartens in Leipzig and surroundings.
+For our child sample, we went to kindergartens in Leipzig and surroundings.
 The child sample consisted of 
@@
 
-The adult sample was again recruited over *Prolific* and consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
+The adult sample was recruited over *Prolific* and consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
 
@@
 We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
-The target locations as well as the succession of animals and target colors was randomized once and then held constant across participants.
+The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
 The child sample received 15 test trials.
@@
 
+## Analysis
+We assessed reliability in two ways. 
+First, we focused on the internal consistency by calculating splithalf reliability coefficients.
+For each subject, trials were split into odd and even and performance scores per part were correlated against each other using *Pearson* correlation coefficients.
+We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices.
+As a recent paper by @pronk2021methods suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+Analyses were run using the function `by_split`from the `splithalfr` package [@pronk2021methods].
+Second, we assessed the test-retest reliability.
+We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using *Pearson* correlation coefficients.
+Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach.
+We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
+For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
+The model computes a correlation between the participant specific estimates for each test day.
+This can be interpreted as the test-retest reliability.
+By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
+Most importantly, the model allows us to get an age-independent estimate for reliability.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.
+
 ## Results
-
 ```{r splithalf}
-splithalf <- readRDS(file = "../stats/gafo-splithalf.rds")
+splithalf <- readRDS(file = "../saves/gafo-splithalf.rds")
 ```
 
-As a first step for estimating the reliability of our task, we focused on the internal consistency by calculating splithalf reliability coefficients.
-Trials were split into two equally big parts and the performance scores per part were correlated against each other.
-We used the raw performance per subject of the first test day.
-Traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients are shown in Figure 2 B, C, G and H.
+We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
 
-As a recent paper by @pronk2021methods suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
-To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
-First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-In the hedge version, reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
-In the box version, reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
+For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure 2 B, C, G and H.
+
+Figure 3 compares splithalf reliability coefficients by splitting and stratification method, following @pronk2021methods.
+In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
+In the box version, splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
 Similarly to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
@@
 
-(ref:figlab3) **Internal Consisteny**. 
-Reliability coefficients per splitting method, stratification level, study version and age group. Error bars show the 95% confidence intervals of the coefficient estimates. 
+(ref:figlab3) **Internal Consistency**. 
+Reliability coefficients per splitting method, stratification level, study version and age group.
+Error bars show the 95% confidence intervals of the coefficient estimates, calculated with the function `by_split` from the `splithalfr` package [@pronk2021methods].
 ```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
@@
 ``` 
+```{r retestmodels}
+mRetestHedge <- readRDS(file = "../saves/mRetestHedge.rds") 
+mRetestBox <- readRDS(file = "../saves/mRetestBox.rds") 
+```
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure 2 D, E, I and J.[^fn2]
+
+[^fn2]: In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
+The performance of the mentioned child lay 3 standard deviations above the mean on both test days.
+Including the child yielded a *Pearson* correlation coefficient of *r* = 0.87.
+
+Taking age into account in our GLMM based approach yielded similar results.
+The age-independent retest reliability estimate in the hedge version amounted to `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the box version of the task, the age-independent correlation between participant specific test day estimates was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+The results suggest that our novel balloon finding task did capture individual differences beyond general cognitive maturation processes.
+This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the driving force acccounting for individual differences.
+
 ## Discussion
-Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
+Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
 
@@
 
+## Analysis
+We compared models using WAIC (widely applicable information criterion) scores and weights.
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+
 ## Results
@@
 # Supplements
+## Child sample
+### Webcam coding
+Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
+This difference was especially prominent in younger participants in the box version of the task.
+It is conceivable that caregivers were especially prone to influence the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
+In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
+We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
+A trial was defined as the time between two eye blinking sounds.
+We transcribed all utterances by parents and children and counted the words uttered by each.
+We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
+In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial. 
+We conducted a model comparison to estimate the effects of parental interference.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.
+We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
+Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
+Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
+We compared models using WAIC (widely applicable information criterion) scores and weights.
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+In all cases, however, ELPD difference scores were smaller than their standard errors.
+Similarly, 95% CI of the model estimates included zero and were rather wide.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
+
+```{r webcam_coding}
+webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds")
+
+knitr::kable(webcam_models)
+```
 
 ## Adult sample
-
 ### Recruitment
@@
 
-## Child sample
-### Study 1 - Validation Remote and in-person
-The validation of our task in a in-person and remote child sample can be found here: https://osf.io/snju6. 
-We chose to have at least 20 data points per cell (i.e.
-unique combination of data collection mode, study version, and age-group).
-Across the two data collection modes, a total of ...
-children participated.
-Participants received a small gift as thank you for their participation in the study.
+# Instructions and voice over descriptions
+This is the content of our audio recordings that were played as instructions and during voice over trials.
 
-For our in-person supervised testing sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-For our remote unsupervised testing sample, families were recruited on a voluntary basis via email from the database of the Max Planck Institute for Evolutionary Anthropology.
-Children in both subsamples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
-Written informed consent was obtained from at least one caregiver prior to testing. 
-TODO: how to phrase for kiga testing?
-
-## Procedure Remote Testing
-In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
-
-Depending on the participant's device, the website automatically presents the hedge or box version of the study.
-For families that use a tablet with touchscreen, the hedge version is shown.
-Here, children can directly click on the screen themselves to indicate where the target is.
-For families that use a computer without touchscreen, the website presents the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.
-In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
-### Study 2 - Reliability in-person 
-https://osf.io/xqm73
-
-# Instructions and voice over descriptions
-This is the content of our voice recordings. Children listen to this during the game.
-
-|     |     |     |     |     |
-| --- | --- | --- | --- | --- |
-| **Nr** | **Timeline** | **German** | **English** | **Filename** |
-| **1** | **welcome** | Hallo!
+|     |     |     |     |
+| --- | --- | --- | --- |
+| **Timeline** | **German** | **English** | **Filename** |
+| **welcome** | Hallo!
 Schön, dass du da bist.
@@
 | welcome.mp3 |
-| **2** | **touch** | Schau mal, da steht ein Tier im Fenster.
+| **touch** | Schau mal, da steht ein Tier im Fenster.
 Und siehst du den Ballon da?
@@
 | touch-1.mp3 |
-| **3** |     | Wo ist der Ballon? Drück auf den Ballon! | Where is the balloon? Click on the balloon! | prompt-touch-long.mp3 |
-| **4** | **fam - HEDGE** | Klasse, das war super!
+|     | Wo ist der Ballon? Drück auf den Ballon! | Where is the balloon? Click on the balloon! | prompt-touch-long.mp3 |
+| **fam - HEDGE** | Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 | fam-hedge-1.mp3 |
-| **5** |     | Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. | Where is the balloon? On the hedge, click where the balloon is. | prompt-hedge-long.mp3 |
-| **6** | **fam - BOX** | Klasse, das war super!
+|     | Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. | Where is the balloon? On the hedge, click where the balloon is. | prompt-hedge-long.mp3 |
+| **fam - BOX** | Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 | fam-box-1.mp3 |
-| **7** |     | Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. | Where is the balloon? Click on the box with the balloon. | prompt-box-long.mp3 |
-| **8** | **test - HEDGE** | Klasse , das hast du toll gemacht!
+|     | Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. | Where is the balloon? Click on the box with the balloon. | prompt-box-long.mp3 |
+| **test - HEDGE** | Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 | test-hedge-1.mp3 |
-| **9** |     | Der Ballon ist nun hinter der Hecke.
-Du kannst das nicht sehen - das Tier aber!
+|     | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
@@
 | test-hedge-2.mp3 |
-| **10** |     | Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. | Now, the hedge is shrinking. On the hedge, click where the balloon is. | test-hedge-3.mp3 |
-| **11** | **test - BOX** | Klasse , das hast du toll gemacht!
+|     | Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. | Now, the hedge is shrinking. On the hedge, click where the balloon is. | test-hedge-3.mp3 |
+| **test - BOX** | Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 | test-box-1.mp3 |
-| **12** |     | Der Ballon ist nun hinter der Hecke.
-Du kannst das nicht sehen - das Tier aber!
+|     | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
@@
 | test-box-2.mp3 |
-| **13** |     | Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. | Now, the hedge is shrinking. Click on the box with the balloon. | test-box-3.mp3 |
-| **14** | **goodbye** | Geschafft!
+|     | Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. | Now, the hedge is shrinking. Click on the box with the balloon. | test-box-3.mp3 |
+| **goodbye** | Geschafft!
 Die Tiere sind schon ganz glücklich vom Spielen!
@@
 See you soon and goodbye from the pig, monkey and sheep | goodbye.mp3 |
-| **15** | **general prompt** | Wo ist der Ballon? | Where is the balloon? | prompt-general.mp3 |
-| **16** | **touch - no response** | Drück auf den Ballon! | Click on the balloon! | prompt-touch.mp3 |
-| **17** | **hedge - no response** | Drücke auf die Hecke - wo der Ballon ist! | On the hedge, click where the balloon is! | prompt-hedge.mp3 |
-| **18** | **box - no response** | Drücke auf die Kiste mit dem Ballon! | Click on the box with the balloon! | prompt-box.mp3 |
-| **19** | **landing sound of balloon** | \-  | \-  | balloon-lands.mp3 |
-| **20** | **sound of blinking eyes** | \-  | \-  | blink.mp3 |
-| **21** | **sound for target click** | \-  | \-  | positive-feedback.mp3 |
+| **general prompt** | Wo ist der Ballon? | Where is the balloon? | prompt-general.mp3 |
+| **touch - no response** | Drück auf den Ballon! | Click on the balloon! | prompt-touch.mp3 |
+| **hedge - no response** | Drücke auf die Hecke - wo der Ballon ist! | On the hedge, click where the balloon is! | prompt-hedge.mp3 |
+| **box - no response** | Drücke auf die Kiste mit dem Ballon! | Click on the box with the balloon! | prompt-box.mp3 |
+| **landing sound of balloon** | \-  | \-  | balloon-lands.mp3 |
+| **sound of blinking eyes** | \-  | \-  | blink.mp3 |
+| **sound for target click** | \-  | \-  | positive-feedback.mp3 |

### 2022-04-06 paper/manuscript.tex
create saves folder, add webcam coding script

@@
 
-\hypertarget{data-processing}{%
-\subsection{Data processing}\label{data-processing}}
-
-We used R version 4.1.3 (2022-03-10) (R Core Team, 2022), and the packages \emph{splithalfr} (Pronk, Molenaar, Wiers, \& Murre, 2021) and \emph{brms} (Bürkner, 2017, 2018) for all our analyses.
-Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
-All test trials without voice over description are included in our analyses.
-
 \hypertarget{does-the-balloon-finding-task-induce-variation}{%
@@
 
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+All test trials without voice over description were included in our analyses.
+We ran all analyses in R version 4.1.3 (2022-03-10) (R Core Team, 2022).
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
+
+To estimate the developmental trajectory of gaze cue understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
+Here, \texttt{targetPosition} refers to the absolute bin/box of the target, while \texttt{symmetricPosition} refers to the distance from the stimulus center (i.e., smaller value meaning more central target position).
+We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
+
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a lognormal distribution.
+For the box version, the model predicted correct responses (0/1) using a Bernoulli distribution with a logit link function.
+We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
+
 \hypertarget{results}{%
@@
 (j) Test-retest reliability in box adult sample.
-Regression lines with 95\% CI show product-moment-correlations with Pearson's correlation coefficient r.
+Regression lines with 95\% CI show product-moment-correlations with \emph{Pearson}'s correlation coefficient \emph{r.}
 Large data points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
 Small data points show the mean performance for each subject.
-Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
+Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
 Color of data points represent each age group (binned by year).}\label{fig:fig2}
@@
 In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+Most participants in the box version performed above chance level.
 By the end of their sixth year of life, children came close to the adult's proficiency level.
-We found interindividual variation across study versions and age groups: some three-year-olds were more precise in their responses than some five-year-olds.
-
-As Figure 2 A and F show, our remotely collected data resembled the data from the kindergarten sample.
-To quantify the effect sizes, we formulated a Bayesian generalized linear mixed model with age (in months, z-transformed) and data collection mode (with in-person supervised data collection as the reference category), and target position and subject ID as random effects.
-In the hedge version, we found an estimate of age of -0.33 (95\% CI {[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 (95\% CI {[}-0.50; -0.14{]}).
-In the box version, the estimate of age was 0.64 (95\% CI {[}0.41; 0.88{]}) and the estimate of data collection mode was 1.16 (95\% CI {[}0.73; 1.61{]}).
-Note that the effect of data collection appears to be present, but confidence intervals are wide.
-
-Our GLMM analysis, therefore, corroborated the effects of age and data collection mode that we already identified by visual inspection.
+We found interindividual variation across study versions and age groups.
+For instance, this can be seen in that some three-year-olds were more precise in their responses than some five-year-olds.
+
+As Figure 2 A and F show, our remotely collected child data resembled the data from the kindergarten sample.
 We found evidence that responses of children participating remotely were slightly more precise.
@@
 In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.\footnote{In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
+We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-  A trial was defined as the time between two eye blinking sounds.
-We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
-  In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
-  We ran exploratory analyses .
-Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
-Our null model explained the the response behavior by age, while including random effects for subject and target position.
-We compared this null model to models including the number of words utterred by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes.
-Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
-  On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-On a subject level, the effect reversed - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-Additionally, number of repeated testquestions displayed a negative estimate on the subject level: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
-{[}TODO:{]} In all cases, however, standard errors of the WAIC score differences where greater than the ELPD difference scores themselves.
-Similarly, 95\% CI of the model estimates included zero and were rather wide.
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.}
+Based on our model comparison, we conclude that there is no clear evidence of a stable effect of parental interference.
+See Supplements for further detail.}
+
+Our GLMM analysis corroborated the effects of age and data collection mode that we already identified by visual inspection: in the hedge version, we found an estimate of age of -0.33 (95\% CI {[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 (95\% CI {[}-0.50; -0.14{]}).
+In the box version, the estimate of age was 0.64 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode was 1.16 (95\% CI {[}0.72; 1.61{]}).
+Note that the effect of data collection appears to be present, but confidence intervals are wide.
 
@@
 
-As a next step we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable (i.e.,
+systematically order individuals in the same way).
 For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
@@
 
-For our child sample, we again went to kindergartens in Leipzig and surroundings.
+For our child sample, we went to kindergartens in Leipzig and surroundings.
 The child sample consisted of
@@
 
-The adult sample was again recruited over \emph{Prolific} and consisted of 136 English-speakers with an average age of 25.74 years (SD = 8.11, range = 18 - 71, 87 females).
+The adult sample was recruited over \emph{Prolific} and consisted of 136 English-speakers with an average age of 25.74 years (SD = 8.11, range = 18 - 71, 87 females).
 
@@
 We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days.
-The target locations as well as the succession of animals and target colors was randomized once and then held constant across participants.
+The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
 The child sample received 15 test trials.
@@
 
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
+
+We assessed reliability in two ways.
+First, we focused on the internal consistency by calculating splithalf reliability coefficients.
+For each subject, trials were split into odd and even and performance scores per part were correlated against each other using \emph{Pearson} correlation coefficients.
+We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices.
+As a recent paper by Pronk, Molenaar, Wiers, and Murre (2021) suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+Analyses were run using the function \texttt{by\_split}from the \texttt{splithalfr} package (Pronk et al., 2021).
+Second, we assessed the test-retest reliability.
+We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using \emph{Pearson} correlation coefficients.
+Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach.
+We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
+For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
+The model computes a correlation between the participant specific estimates for each test day.
+This can be interpreted as the test-retest reliability.
+By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
+Most importantly, the model allows us to get an age-independent estimate for reliability.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.
+
 \hypertarget{results-1}{%
@@
 
-As a first step for estimating the reliability of our task, we focused on the internal consistency by calculating splithalf reliability coefficients.
-Trials were split into two equally big parts and the performance scores per part were correlated against each other.
-We used the raw performance per subject of the first test day.
-Traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients are shown in Figure 2 B, C, G and H.
-
-As a recent paper by Pronk et al.
-(2021) suggested, there are various, more sophisticated split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
-To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
-First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-In the hedge version, reliability coefficients ranged from 0.57 to 0.87. In the box version, reliability coefficients ranged from 0.43 to 0.76.
+We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
+
+For the internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure 2 B, C, G and H.
+
+Figure 3 compares splithalf reliability coefficients by splitting and stratification method, following Pronk et al. (2021).
+In the hedge version, the splithalf reliability coefficients ranged from 0.61 to 0.92. In the box version, splithalf reliability coefficients ranged from 0.40 to 0.87.
 Similarly to the results of Pronk et al.
@@
 
-\caption{\textbf{Internal Consisteny}.
-Reliability coefficients per splitting method, stratification level, study version and age group. Error bars show the 95\% confidence intervals of the coefficient estimates.}\label{fig:fig3}
+\caption{\textbf{Internal Consistency}.
+Reliability coefficients per splitting method, stratification level, study version and age group.
+Error bars show the 95\% confidence intervals of the coefficient estimates, calculated with the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).}\label{fig:fig3}
 \end{figure}
+
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure 2 D, E, I and J.\footnote{In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
+The performance of the mentioned child lay 3 standard deviations above the mean on both test days.
+Including the child yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.87.}
+
+Taking age into account in our GLMM based approach yielded similar results. The age-independent retest reliability estimate in the hedge version amounted to 0.88 (95\% CI {[}0.61;1.00{]}).
+In the box version of the task, the age-independent correlation between participant specific test day estimates was 0.89 (95\% CI {[}0.63;1.00{]}).
+The results suggest that our novel balloon finding task did capture individual differences beyond general cognitive maturation processes.
+This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the driving force acccounting for individual differences.
 
@@
 
-Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.
+Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
 
@@
 
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
+
+We compared models using WAIC (widely applicable information criterion) scores and weights.
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+
 \hypertarget{results-2}{%
@@
 \section{Supplements}\label{supplements}}
+
+\hypertarget{child-sample}{%
+\subsection{Child sample}\label{child-sample}}
+
+\hypertarget{webcam-coding}{%
+\subsubsection{Webcam coding}\label{webcam-coding}}
+
+Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
+This difference was especially prominent in younger participants in the box version of the task.
+It is conceivable that caregivers were especially prone to influence the behavior of younger children.
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
+In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
+We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
+A trial was defined as the time between two eye blinking sounds.
+We transcribed all utterances by parents and children and counted the words uttered by each.
+We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
+In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
+We conducted a model comparison to estimate the effects of parental interference.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.
+We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
+Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
+Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
+We compared models using WAIC (widely applicable information criterion) scores and weights.
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+In all cases, however, ELPD difference scores were smaller than their standard errors.
+Similarly, 95\% CI of the model estimates included zero and were rather wide.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
+
+\begin{tabular}{l|r|r|r|r}
+\hline
+model & waic & waic\_weight & elpd\_diff & se\_diff\\
+\hline
+mPerTrialVerificationChoice & 263.24183 & 0.6469352 & 0.0000000 & 0.000000\\
+\hline
+mPerTrialNull & 263.74712 & 0.3530572 & -0.2526455 & 1.202097\\
+\hline
+mPerTrialPI & 264.34608 & 0.0000048 & -0.5521261 & 0.978696\\
+\hline
+mPerTrialRepeatedTestquestion & 265.43452 & 0.0000011 & -1.0963445 & 1.272427\\
+\hline
+mPerTrialHintsEyes & 265.67182 & 0.0000014 & -1.2149955 & 1.255888\\
+\hline
+mPerTrialParentSpeech & 266.45389 & 0.0000003 & -1.6060301 & 1.211500\\
+\hline
+mPerSubjectRepeatedTestquestion & 83.52517 & 0.7033000 & 0.0000000 & 0.000000\\
+\hline
+mPerSubjectPI & 88.25288 & 0.0000019 & -2.3638570 & 3.596520\\
+\hline
+mPerSubjectNull & 89.25650 & 0.0000003 & -2.8656662 & 3.608723\\
+\hline
+mPerSubjectVerificationChoice & 89.85833 & 0.2966959 & -3.1665822 & 4.484388\\
+\hline
+mPerSubjectParentSpeech & 90.44632 & 0.0000018 & -3.4605795 & 4.204938\\
+\hline
+mPerSubjectHintsEyes & 92.76122 & 0.0000001 & -4.6180264 & 3.773420\\
+\hline
+\end{tabular}
 
@@
 
-\hypertarget{child-sample}{%
-\subsection{Child sample}\label{child-sample}}
-
-\hypertarget{study-1---validation-remote-and-in-person}{%
-\subsubsection{Study 1 - Validation Remote and in-person}\label{study-1---validation-remote-and-in-person}}
-
-The validation of our task in a in-person and remote child sample can be found here: \url{https://osf.io/snju6}.
-We chose to have at least 20 data points per cell (i.e.~unique combination of data collection mode, study version, and age-group).
-Across the two data collection modes, a total of \ldots{} children participated.
-Participants received a small gift as thank you for their participation in the study.
-
-For our in-person supervised testing sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-For our remote unsupervised testing sample, families were recruited on a voluntary basis via email from the database of the Max Planck Institute for Evolutionary Anthropology.
-Children in both subsamples live in Leipzig, Germany or surrounding areas and grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
-Written informed consent was obtained from at least one caregiver prior to testing.
-TODO: how to phrase for kiga testing?
-
-\hypertarget{procedure-remote-testing}{%
-\subsection{Procedure Remote Testing}\label{procedure-remote-testing}}
-
-In the beginning of the online study, families were invited to enter ``our virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
-Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.
-
-Depending on the participant's device, the website automatically presents the hedge or box version of the study.
-For families that use a tablet with touchscreen, the hedge version is shown.
-Here, children can directly click on the screen themselves to indicate where the target is.
-For families that use a computer without touchscreen, the website presents the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
-Therefore, we asked children to point to the screen.
-Caregivers were then asked to act as the ``digital finger'' of their children and click on the indicated box.
-In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.
-
-\hypertarget{study-2---reliability-in-person}{%
-\subsubsection{Study 2 - Reliability in-person}\label{study-2---reliability-in-person}}
-
-\url{https://osf.io/xqm73}
-
 \hypertarget{instructions-and-voice-over-descriptions}{%
@@
 
-This is the content of our voice recordings. Children listen to this during the game.
+This is the content of our audio recordings that were played as instructions and during voice over trials.
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
 \toprule
 \endhead
-\textbf{Nr} & \textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
-\textbf{1} & \textbf{welcome} & Hallo!
+\textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
+\textbf{welcome} & Hallo!
 Schön, dass du da bist.
@@
 & welcome.mp3 \\
-\textbf{2} & \textbf{touch} & Schau mal, da steht ein Tier im Fenster.
+\textbf{touch} & Schau mal, da steht ein Tier im Fenster.
 Und siehst du den Ballon da?
@@
 & touch-1.mp3 \\
-\textbf{3} & & Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
-\textbf{4} & \textbf{fam - HEDGE} & Klasse, das war super!
+& Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
+\textbf{fam - HEDGE} & Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 & fam-hedge-1.mp3 \\
-\textbf{5} & & Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
-\textbf{6} & \textbf{fam - BOX} & Klasse, das war super!
+& Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
+\textbf{fam - BOX} & Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 & fam-box-1.mp3 \\
-\textbf{7} & & Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
-\textbf{8} & \textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
+& Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
+\textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 & test-hedge-1.mp3 \\
-\textbf{9} & & Der Ballon ist nun hinter der Hecke.
-Du kannst das nicht sehen - das Tier aber!
+& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
@@
 & test-hedge-2.mp3 \\
-\textbf{10} & & Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
-\textbf{11} & \textbf{test - BOX} & Klasse , das hast du toll gemacht!
+& Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
+\textbf{test - BOX} & Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 & test-box-1.mp3 \\
-\textbf{12} & & Der Ballon ist nun hinter der Hecke.
-Du kannst das nicht sehen - das Tier aber!
+& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
@@
 & test-box-2.mp3 \\
-\textbf{13} & & Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
-\textbf{14} & \textbf{goodbye} & Geschafft!
+& Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
+\textbf{goodbye} & Geschafft!
 Die Tiere sind schon ganz glücklich vom Spielen!
@@
 See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
-\textbf{15} & \textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
-\textbf{16} & \textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
-\textbf{17} & \textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
-\textbf{18} & \textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
-\textbf{19} & \textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
-\textbf{20} & \textbf{sound of blinking eyes} & - & - & blink.mp3 \\
-\textbf{21} & \textbf{sound for target click} & - & - & positive-feedback.mp3 \\
+\textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
+\textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
+\textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
+\textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
+\textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
+\textbf{sound of blinking eyes} & - & - & blink.mp3 \\
+\textbf{sound for target click} & - & - & positive-feedback.mp3 \\
 \bottomrule

### 2022-04-06 stats/analysis.Rmd
create saves folder, add webcam coding script

@@
                     cores  = 4)
+
+write.csv(mAgeHedge, "../saves/mAgeHedge.csv", quote = F, row.names = F)
+saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")
 ```
@@
                     cores  = 4)
+
+write.csv(mAgeBox, "../saves/mAgeBox.csv", quote = F, row.names = F)
+saveRDS(mAgeBox, "../saves/mAgeBox.rds")
 ```
@@
 ```{r save_splithalf_data}
-write.csv(splithalf_data, "gafo-splithalf.csv", quote = F, row.names = F)
-saveRDS(splithalf_data, file = "gafo-splithalf.rds")
+write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
+saveRDS(splithalf_data, file = "../saves/gafo-splithalf.rds")
 ```
@@
 psych::describeBy(hedge_retest, hedge_retest$sample)
+
+# calculate at which values we would start seing data as outliers
+hedge_retest %>% 
+  summarize(
+    lower_reliday1 = mean(mean_reliday1) - 3*sd(mean_reliday1), 
+    upper_reliday1 = mean(mean_reliday1) + 3*sd(mean_reliday1),
+    lower_reliday2 = mean(mean_reliday2) - 3*sd(mean_reliday2),
+    upper_reliday2 = mean(mean_reliday2) + 3*sd(mean_reliday2),
+  )
+
+# check how many there are
+hedge_retest %>% 
+  filter(mean_reliday1 >= mean(mean_reliday1) + 3*sd(mean_reliday1) | 
+         mean_reliday1 <= mean(mean_reliday1) - 3*sd(mean_reliday1) |
+         mean_reliday2 >= mean(mean_reliday2) + 3*sd(mean_reliday2) |
+         mean_reliday2 <= mean(mean_reliday2) - 3*sd(mean_reliday2))
 
@@
   stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
-  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  scale_x_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
+  scale_y_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
   labs(x = "Testday 1", y = "Testday 2")
@@
 ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+```
+
+```{r retest_hedge_model}
+# define data
+mDataRetestHedge <- reli %>% 
+  filter(studyversion == "hedge" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, reliday, clickDistInBalloons)
+
+# run model
+mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
+                              data   = mDataRetestHedge, 
+                              family = lognormal(), 
+                              warmup = 1000, 
+                              iter   = 3000, 
+                              chains = 4, 
+                              inits  = "random",
+                              cores  = 4)
+
+write.csv(mRetestHedge, "../saves/mRetestHedge.csv", quote = F, row.names = F)
+saveRDS(mRetestHedge, "../saves/mRetestHedge.rds")
 ```
@@
 
-```{r retest_hedge_model}
-# define data
-mDataRetestHedge <- reli %>% 
-  filter(studyversion == "hedge" & sample == "kids") %>% 
-  mutate(
-    # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
-  ) %>% 
-  select(subjID, age, reliday, clickDistInBalloons)
-
-# run model
-mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
-                              data   = mDataRetestHedge, 
-                              family = lognormal(), 
-                              warmup = 1000, 
-                              iter   = 3000, 
-                              chains = 4, 
-                              inits  = "random",
-                              cores  = 4)
-```
-
 ```{r retest_box_model}
@@
                               cores  = 4)
+
+write.csv(mRetestBox, "../saves/mRetestBox.csv", quote = F, row.names = F)
+saveRDS(mRetestBox, "../saves/mRetestBox.rds")
 ```
@@
 ```
-
-```{r save_model_output}
-# mcor <- model_cor %>%
-#     mutate(task = recode(task,
-#                     `mutual_exclusivity` = "Mutual Exclusivity",
-#                     `informativeness` = "Informativeness Inference (1)",
-#                     `simple_inf` = "Informativeness Inference (2)",
-#                     `preference` = "Speaker Preference",
-#                     `novelty` = "Discourse Novelty",
-#                     `card_sorting` = "Card Sorting",
-#                     `discourse_continuity` = "Discourse Continuity",
-#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
-#                     `match_to_sample` = "Relational Match-to-sample"),
-#            term = task, 
-#            mcor = Estimate, 
-#            mcor_lci = `l-95% CI`, 
-#            mcor_uci = `u-95% CI`)%>%
-#   select(study, term, task, mcor, mcor_lci, mcor_uci)
-
-# saveRDS(mcor, "model_results.rds")
-```

### 2022-04-06 stats/supplements_webcamcoding.Rmd
create saves folder, add webcam coding script

---
title: "supplements_webcamcoding"
author: "Julia Prein"
date: '2022-04-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(brms)
library(ggridges)

options(scipen = 999)
theme_set(theme_classic())
```

```{r load_data}
webcam_data <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & webcam == TRUE & ageInYears == 3) %>% 
  group_by(subjID) %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("box1", "box2", "box3", "box4", "box5")), 
    proportionCorrectBox = mean(correctBox, na.rm = TRUE),
  )
```

### VISUAL EXPLORATION

```{r webcam_exploring}
### nrRepeatedTestquestion
webcam_data %>% 
  group_by(subjID) %>% 
  mutate(repeatedTestquestion = mean(nrRepeatedTestquestion, na.rm = TRUE)) %>% 
  ggplot(., aes(x = repeatedTestquestion, y = proportionCorrectBox)) + 
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))

### nrHintsEyes
webcam_data %>% 
  group_by(subjID) %>% 
  mutate(hintsEyes = mean(nrHintsEyes, na.rm = TRUE)) %>% 
  ggplot(., aes(x = hintsEyes, y = proportionCorrectBox)) + 
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))

### nrVerificationChoice
webcam_data %>% 
  group_by(subjID) %>% 
  mutate(verificationChoice = mean(nrVerificationChoice, na.rm = TRUE)) %>% 
  ggplot(., aes(x = verificationChoice, y = proportionCorrectBox)) + 
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))

### nrParentSpeech
webcam_data %>% 
  group_by(subjID) %>% 
  mutate(parentSpeech = mean(nrParentSpeech, na.rm = TRUE)) %>% 
  ggplot(., aes(x = parentSpeech, y = proportionCorrectBox)) + 
  geom_point(col = "#006c66", size = 0.7) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))
```

### MODELS ON TRIAL LEVEL

```{r webcam_perTrial_datapreparation}
# prepare data
mData <- webcam_data %>% 
  ungroup() %>% 
  mutate(
    correct = as.numeric(correctBox),

    # centered around minimum
    age = ageInMonths - min(ageInMonths),

    # centered around mean
    trial = scale(trialNr, center = TRUE, scale = FALSE), 
    repeatedTestquestion = scale(nrRepeatedTestquestion, center = TRUE, scale = FALSE),
    verificationChoice = scale(nrVerificationChoice, center = TRUE, scale = FALSE),
    hintsEyes = scale(nrHintsEyes, center = TRUE, scale = FALSE),
    nrParentSpeech = replace_na(nrParentSpeech, 0), 
    parentSpeech = scale(nrParentSpeech, center = TRUE, scale = FALSE),

    # calculating index
    parentalInterference = -(repeatedTestquestion) + -(verificationChoice) + hintsEyes,

    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    pi = scale(parentalInterference, scale = TRUE, center = TRUE), 
  ) %>% 
  select(trial, subjID, correct, targetPosition, age, parentalInterference, pi, repeatedTestquestion, verificationChoice, hintsEyes, parentSpeech)

```

```{r webcam_perTrial_models}
# originally: 
# brm(correct ~ age + (trial + targetPosition | subjID) + (age | targetPosition)
# age + person effect + trial effect
# simplified the model, since not a lot of data / info to estimate all the parameters. 
# therefore, remove trial & targetposition

mPerTrialNull <- brm(correct ~ age + (1 | subjID) + (1 | targetPosition), 
                              data   = mData, 
                              family = bernoulli(link = "logit"), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

# we decided to build an index since we're rather interested in the additive effect of the parameters; general parental inference
# we don't want to know what happens if we e.g. set repeatedQuestion & verfication to zero how does hintsEyes influence correct

# index: repeated testquestion & verification choice tend to lean into negative effect, 
# hints eyes rather positive. therefore -, - + for summing up
mPerTrialPI <- update(mPerTrialNull,
                      newdata = mData,
                      formula = correct ~ age + pi + (1 | subjID) + (1 | targetPosition), 
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerTrialRepeatedTestquestion <- update(mPerTrialNull,
                      newdata = mData,
                      formula = correct ~ age + repeatedTestquestion + (1 | subjID) + (1 | targetPosition), 
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerTrialVerificationChoice <- update(mPerTrialNull,
                      newdata = mData,
                      formula = correct ~ age + verificationChoice + (1 | subjID) + (1 | targetPosition), 
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerTrialHintsEyes <- update(mPerTrialNull,
                      newdata = mData,
                      formula = correct ~ age + hintsEyes + (1 | subjID) + (1 | targetPosition), 
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerTrialParentSpeech <- update(mPerTrialNull,
                      newdata = mData,
                      formula = correct ~ age + parentSpeech + (1 | subjID) + (1 | targetPosition), 
                      family = bernoulli(link = "logit"),
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)
```

```{r webcam_perTrial_comparisons}
mPerTrialNull <- add_criterion(mPerTrialNull, "waic")
mPerTrialPI <- add_criterion(mPerTrialPI, "waic")
mPerTrialRepeatedTestquestion <- add_criterion(mPerTrialRepeatedTestquestion, "waic")
mPerTrialVerificationChoice <- add_criterion(mPerTrialVerificationChoice, "waic")
mPerTrialHintsEyes <- add_criterion(mPerTrialHintsEyes, "waic")
mPerTrialParentSpeech <- add_criterion(mPerTrialParentSpeech, "waic")

mPerTrialComparison <- loo_compare(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic")

mPerTrialComparison <- as_tibble(mPerTrialComparison, rownames = "model")
write.csv(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.csv", quote = F, row.names = F)
saveRDS(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.rds")

mPerTrialComparisonWeights <- as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic"), rownames = "model")
write.csv(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.csv", quote = F, row.names = F)
saveRDS(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.rds")
```

```{r webcam_perTrial_plot}
postSamplesPerTrial <- bind_rows(
  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
  posterior_samples(mPerTrialPI, pars = "pi") %>% mutate(model = "mPerTrialPI") %>% rename(estimate = b_pi), 
  posterior_samples(mPerTrialRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerTrialRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
  posterior_samples(mPerTrialVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerTrialVerificationChoice") %>% rename(estimate = b_verificationChoice), 
  posterior_samples(mPerTrialHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerTrialHintsEyes") %>% rename(estimate = b_hintsEyes), 
  posterior_samples(mPerTrialParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerTrialParentSpeech") %>% rename(estimate = b_parentSpeech), 
)

postSamplesPerTrial <- postSamplesPerTrial %>% 
  mutate(
        model = factor(model, levels = c("mPerTrialParentSpeech", "mPerTrialHintsEyes", "mPerTrialVerificationChoice", "mPerTrialRepeatedTestquestion", "mPerTrialPI")),
  )

ggplot(postSamplesPerTrial, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") +
  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, by = 0.5))

ggsave("../figures/supplements-webcamcoding-mPerTrialComparison-posteriorsample.png")
```

### MODELS ON SUBJECT LEVEL

```{r webcam_perSubject_datapreparation}
mDataSubj <- webcam_data %>% 
  group_by(subjID) %>% 
  mutate(
    trials = n(),
    correctTrials = sum(correctBox), 
    repeatedTestquestion = sum(nrRepeatedTestquestion), 
    verificationChoice = sum(nrVerificationChoice), 
    hintsEyes = sum(nrHintsEyes), 
    parentalInterference = -(repeatedTestquestion) + verificationChoice + -(hintsEyes),
    nrParentSpeech = replace_na(nrParentSpeech, 0), 
    parentSpeech = sum(nrParentSpeech), 
  ) %>% 
  slice(1) %>% 
  # for scaling we need ungrouped data!
  ungroup() %>% 
  mutate(
    age = ageInMonths - mean(ageInMonths), 
    pi = scale(parentalInterference, scale = TRUE, center = TRUE), 
  ) %>% 
  select(subjID, correctTrials, trials, age, repeatedTestquestion, verificationChoice, hintsEyes, parentSpeech, pi)
```

```{r webcam_perSubject_models}
mPerSubjectNull <- brm(correctTrials |  trials(trials) ~ age, 
                              data   = mDataSubj, 
                              family = binomial(link = "logit"), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)

mPerSubjectPI <- update(mPerSubjectNull,
                      newdata = mDataSubj,
                      formula = correctTrials |  trials(trials) ~ age + pi, 
                      family = binomial(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerSubjectRepeatedTestquestion <- update(mPerSubjectNull,
                      newdata = mDataSubj,
                      formula = correctTrials |  trials(trials) ~ age + repeatedTestquestion, 
                      family = binomial(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerSubjectVerificationChoice <- update(mPerSubjectNull,
                      newdata = mDataSubj,
                      formula = correctTrials |  trials(trials) ~ age + verificationChoice, 
                      family = binomial(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerSubjectHintsEyes <- update(mPerSubjectNull,
                      newdata = mDataSubj,
                      formula = correctTrials |  trials(trials) ~ age + hintsEyes, 
                      family = binomial(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)

mPerSubjectParentSpeech <- update(mPerSubjectNull,
                      newdata = mDataSubj,
                      formula = correctTrials |  trials(trials) ~ age + parentSpeech, 
                      family = binomial(link = "logit"), 
                      warmup = 1000, 
                      iter   = 3000, 
                      chains = 4, 
                      inits  = "random",
                      cores  = 4)
```

```{r webcam_perTrial_comparisons}
mPerSubjectNull <- add_criterion(mPerSubjectNull, "waic")
mPerSubjectPI <- add_criterion(mPerSubjectPI, "waic")
mPerSubjectRepeatedTestquestion <- add_criterion(mPerSubjectRepeatedTestquestion, "waic")
mPerSubjectVerificationChoice <- add_criterion(mPerSubjectVerificationChoice, "waic")
mPerSubjectHintsEyes <- add_criterion(mPerSubjectHintsEyes, "waic")
mPerSubjectParentSpeech <- add_criterion(mPerSubjectParentSpeech, "waic")

mPerSubjectComparison <- loo_compare(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic")

mPerSubjectComparison <- as_tibble(mPerSubjectComparison, rownames = "model")
write.csv(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.csv", quote = F, row.names = F)
saveRDS(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.rds")

mPerSubjectComparisonWeights <- as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic"), rownames = "model")
write.csv(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.csv", quote = F, row.names = F)
saveRDS(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.rds")
```

```{r webcam_perTrial_plot}
postSamplesPerSubject <- bind_rows(
  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
  posterior_samples(mPerSubjectPI, pars = "pi") %>% mutate(model = "mPerSubjectPI") %>% rename(estimate = b_pi), 
  posterior_samples(mPerSubjectRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerSubjectRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
  posterior_samples(mPerSubjectVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerSubjectVerificationChoice") %>% rename(estimate = b_verificationChoice), 
  posterior_samples(mPerSubjectHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerSubjectHintsEyes") %>% rename(estimate = b_hintsEyes), 
  posterior_samples(mPerSubjectParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerSubjectParentSpeech") %>% rename(estimate = b_parentSpeech), 
)

postSamplesPerSubject <- postSamplesPerSubject %>% 
  mutate(
        model = factor(model, levels = c("mPerSubjectParentSpeech", "mPerSubjectHintsEyes", "mPerSubjectVerificationChoice", "mPerSubjectRepeatedTestquestion", "mPerSubjectPI")),
  )

ggplot(postSamplesPerSubject, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none")

ggsave("../figures/supplements-webcamcoding-mPerSubjectComparison-posteriorsample.png")
```

```{r overall_save}
overall_resuls <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
  select(model, waic, value, elpd_diff, se_diff) %>% 
  rename(waic_weight = value)

write.csv(overall_resuls, "../saves/supplements-webcamcoding-resuls.csv", quote = F, row.names = F)
saveRDS(overall_resuls, "../saves/supplements-webcamcoding-results.rds")
```

### 2022-04-07 paper/manuscript.Rmd
add external validity analysis

@@
 ```
+
 ```{r retestmodels}
@@
 Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. 
-```{r peerexposure_sample}
-pe <- testtrials %>% 
+```{r extvali_sample}
+extvali <- testtrials %>% 
   filter(ageInYears < 6) %>%
-  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, targetCentralityX) %>%
+  mutate(
+        symmetricPosition = case_when(
+                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
+                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
+                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
+                                  targetPosition == "2" | targetPosition == "9" ~ 4,
+                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
+                       ), 
+  ) %>% 
+  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>%
+  group_by(subjID) %>% 
   # so that all models run with same nr of subjects
@@
 
-pe_sample <- pe %>%
+extvali_sample <- extvali %>%
   group_by(ageInYears) %>%
@@
 
-pe_gender <- pe %>% 
+extvali_gender <- extvali %>% 
   group_by(ageInYears) %>%
@@
 
-pe_sample <- pe_sample %>% 
-  left_join(pe_gender, by = c("ageInYears"))
+extvali_sample <- extvali_sample %>% 
+  left_join(extvali_gender, by = c("ageInYears"))
 ```
@@
 For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of 
-`r sum(pe_sample$nTotal)` children, including 
-`r sum(pe_sample$nTotal[pe_sample$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "3"])` months, 
-SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "3"])`, 
-range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "3"])`
-- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "3"])`, 
-`r sum(pe_sample$nFemales[pe_sample$ageInYears == "3"])` girls),
-`r sum(pe_sample$nTotal[pe_sample$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "4"])` months, 
-SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "4"])`, 
-range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "4"])`
-- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "4"])`, 
-`r sum(pe_sample$nFemales[pe_sample$ageInYears == "4"])` girls),
-and `r sum(pe_sample$nTotal[pe_sample$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "5"])` months, 
-SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "5"])`, 
-range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "5"])`
-- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "5"])`, 
-`r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).
+`r sum(extvali_sample$nTotal)` children, including 
+`r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "3"])` 3-year-olds 
+(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "3"])` months, 
+SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "3"])`, 
+range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "3"])`
+- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "3"])`, 
+`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "3"])` girls),
+`r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "4"])` 4-year-olds 
+(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "4"])` months, 
+SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "4"])`, 
+range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "4"])`
+- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "4"])`, 
+`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "4"])` girls),
+and `r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "5"])` 5-year-olds 
+(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "5"])` months, 
+SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "5"])`, 
+range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "5"])`
+- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "5"])`, 
+`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "5"])` girls).
 
@@
 ## Analysis
-We compared models using WAIC (widely applicable information criterion) scores and weights.
+To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
+The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
+Therefore, our null model closely resembled the structure from our first analysis (section *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
+In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+For the target position, we summarized the two adjacent bins into one imaginary box.
+For the click responses, we created imaginary box boundaries around the target's landing position and assessed whether the participant's response fell into this imaginary box.
+Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
+For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subjects entered childcare.
+In addition, we calculated three index scores.
+First, we calculated a sibling variety score according to @peterson2000kindred.
+Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements).
+Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed).
+We compared the models using WAIC (widely applicable information criterion) scores and weights.
 As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
@@
 ## Results
-- peer exposure (hedge & box combined?)
+[TODO] All effects except when a child entered childcare positively influence performance. 
+The effect sizes are all small and 95% CIs mostly include zero.
+It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.
+
+(ref:figlab4) **External validity of the balloon finding task**. 
+[TODO] WAIC scores and weights can be found in the Supplements section. 
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/extvali-posteriorsample.png")
+```
 
@@
 knitr::kable(webcam_models)
+```
+
+### Appendix to external validity section
+#### Scoring of sibling variety scores
+For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature. 
+First, we followed the approach by @peterson2000kindred.
+Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+
+Second, we implemented the sibling variety score by @cassidy2005theory.
+The authors adjusted the original score of @peterson2000kindred in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+Twins with additional siblings scored depending on the age and number of their siblings.
+
+The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
+However, teenage siblings might provide opportunities for interesting discussions [@peterson2000kindred].
+
+#### WAIC scores and weights of the model comparison
+As can be seen, ELPD difference scores are smaller than their respective standard errors.
+WAIC scores between models don't differ substantially.
+All effects except when a child entered childcare positively influence performance.
+```{r extvali_results}
+extvali_models <- readRDS(file = "../saves/extvali-results.rds")
+knitr::kable(extvali_models)
 ```

### 2022-04-07 paper/manuscript.tex
add external validity analysis

@@
 
-We compared models using WAIC (widely applicable information criterion) scores and weights.
+To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
+The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
+Therefore, our null model closely resembled the structure from our first analysis (section \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
+In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+For the target position, we summarized the two adjacent bins into one imaginary box.
+For the click responses, we created imaginary box boundaries around the target's landing position and assessed whether the participant's response fell into this imaginary box.
+Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
+For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subjects entered childcare.
+In addition, we calculated three index scores.
+First, we calculated a sibling variety score according to Peterson (2000).
+Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements).
+Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed).
+We compared the models using WAIC (widely applicable information criterion) scores and weights.
 As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
@@
 
-\begin{itemize}
-\tightlist
-\item
-  peer exposure (hedge \& box combined?)
-\end{itemize}
+{[}TODO{]} All effects except when a child entered childcare positively influence performance.
+The effect sizes are all small and 95\% CIs mostly include zero.
+It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/extvali-posteriorsample}
+
+}
+
+\caption{\textbf{External validity of the balloon finding task}.
+{[}TODO{]} WAIC scores and weights can be found in the Supplements section.}\label{fig:fig4}
+\end{figure}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
+Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106.
+
 \leavevmode\vadjust pre{\hypertarget{ref-greensock2022gsap}{}}%
 Greensock. (2022). \emph{{GSAP} ({GreenSock Animation Platform})}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
+Peterson, C.
+C.
+(2000).
+Kindred spirits: {Influences} of siblings' perspectives on theory of mind.
+\emph{Cognitive Development}, \emph{15}(4), 435--455.
+\url{https://doi.org/10.1016/S0885-2014(01)00040-5}
 
@@
 mPerSubjectHintsEyes & 92.76122 & 0.0000001 & -4.6180264 & 3.773420\\
+\hline
+\end{tabular}
+
+\hypertarget{appendix-to-external-validity-section}{%
+\subsubsection{Appendix to external validity section}\label{appendix-to-external-validity-section}}
+
+\hypertarget{scoring-of-sibling-variety-scores}{%
+\paragraph{Scoring of sibling variety scores}\label{scoring-of-sibling-variety-scores}}
+
+For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
+First, we followed the approach by Peterson (2000).
+Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+
+Second, we implemented the sibling variety score by Cassidy et al.
+(2005).
+The authors adjusted the original score of Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+Twins with additional siblings scored depending on the age and number of their siblings.
+
+The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
+However, teenage siblings might provide opportunities for interesting discussions (Peterson, 2000).
+
+\hypertarget{waic-scores-and-weights-of-the-model-comparison}{%
+\paragraph{WAIC scores and weights of the model comparison}\label{waic-scores-and-weights-of-the-model-comparison}}
+
+As can be seen, ELPD difference scores are smaller than their respective standard errors.
+WAIC scores between models don't differ substantially.
+All effects except when a child entered childcare positively influence performance.
+
+\begin{tabular}{l|r|r|r|r}
+\hline
+model & waic & waic\_weight & elpd\_diff & se\_diff\\
+\hline
+PE & 2391.092 & 0.4516270 & 0.0000000 & 0.0000000\\
+\hline
+siblingsVarietyScoreP & 2391.433 & 0.2009621 & -0.1703600 & 1.1084142\\
+\hline
+siblingsVarietyScoreW & 2391.612 & 0.0489847 & -0.2602340 & 1.1033051\\
+\hline
+hhSibs & 2391.654 & 0.0932701 & -0.2809574 & 0.9592453\\
+\hline
+null & 2391.963 & 0.0003588 & -0.4355391 & 1.3235267\\
+\hline
+ccAge & 2392.770 & 0.2047406 & -0.8390844 & 1.7165235\\
+\hline
+sibsChildAged & 2393.059 & 0.0000352 & -0.9836425 & 1.0349722\\
+\hline
+ccHours & 2393.156 & 0.0000134 & -1.0320103 & 1.0784916\\
+\hline
+hhTotal & 2393.647 & 0.0000082 & -1.2775838 & 0.9703247\\
 \hline

### 2022-04-07 stats/analysis.Rmd
add external validity analysis

@@
 library(ggpubr)
+library(ggridges)
 library(ggthemes)
@@
 ```
+
+# EXTERNAL VALIDITY
+
+```{r extvali_prepareData}
+mDataExtvali <- testtrials %>% 
+  filter(ageInYears < 6) %>% 
+  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>%
+  group_by(subjID) %>% 
+  # so that all models run with same nr of subjects
+  drop_na() %>% 
+  ungroup() %>% 
+  mutate(
+    # centered around minimum
+    hhSibs = siblingsNr, 
+    sibsChildAged = siblingsChildAged,
+
+    # centered around mean
+    trial = scale(trialNr, center = TRUE, scale = FALSE)[,1],
+    ccAge = scale(childcareAge, center = TRUE, scale = FALSE)[,1],
+    ccHours = scale(childcareHours, center = TRUE, scale = FALSE)[,1],
+    hhTotal = scale(householdTotal, center = TRUE, scale = FALSE)[,1],
+
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE)[,1],
+    pe = scale(peerExposure, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(datacollection, studyversion, subjID, trial, age, targetPosition, symmetricPosition, correctBox, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>%
+  mutate_if(is.character, as.factor)
+
+n_distinct(extvali$subjID)
+```
+
+```{r extvali_nullmodel}
+mExtvalinull <- brm(correctBox ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                    data = mDataExtvali,
+                    family = bernoulli(link = "logit"),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4)
+```
+
+```{r extvali_fullmodels}
+mExtvaliccAge <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ ccAge + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"),
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvaliccHours <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ ccHours + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvalihhTotal <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ hhTotal + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvalihhSibs <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ hhSibs + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvalisibsChildAged <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ sibsChildAged + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvalisiblingsVarietyScoreP <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ siblingsVarietyScoreP + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvalisiblingsVarietyScoreW <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ siblingsVarietyScoreW + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+
+mExtvaliPE <- update(mExtvalinull,
+                      newdata = mDataExtvali,
+                      formula = correctBox ~ pe + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
+                      family = bernoulli(link = "logit"), 
+                      warmup = 1000, 
+                      iter   = 3000, 
+                      chains = 4, 
+                      inits  = "random",
+                      cores  = 4)
+```
+
+```{r extvali_modelcomparisons}
+mExtvalinull <- add_criterion(mExtvalinull, "waic")
+mExtvaliccAge <- add_criterion(mExtvaliccAge, "waic")
+mExtvaliccHours <- add_criterion(mExtvaliccHours, "waic")
+mExtvalihhTotal <- add_criterion(mExtvalihhTotal, "waic")
+mExtvalihhSibs <- add_criterion(mExtvalihhSibs, "waic")
+mExtvalisibsChildAged <- add_criterion(mExtvalisibsChildAged, "waic")
+mExtvalisiblingsVarietyScoreP <- add_criterion(mExtvalisiblingsVarietyScoreP, "waic")
+mExtvalisiblingsVarietyScoreW <- add_criterion(mExtvalisiblingsVarietyScoreW, "waic")
+mExtvaliPE <- add_criterion(mExtvaliPE, "waic")
+
+mExtvaliComparison <- as_tibble(loo_compare(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")
+
+mExtvaliComparison
+
+mExtvaliComparisonWeights <- as_tibble(model_weights(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")
+
+mExtvaliComparisonWeights %>% arrange(-value)
+
+extvaliModelorder <- mExtvaliComparisonWeights %>% arrange(value) %>%  pull(model)
+```
+
+```{r extvali_plot}
+extvaliPostSamples <- bind_rows(
+  posterior_samples(mExtvaliccAge, pars = "b_ccAge") %>% mutate(model = "mExtvaliccAge") %>% rename(estimate = b_ccAge), 
+  posterior_samples(mExtvaliccHours, pars = "b_ccHours") %>% mutate(model = "mExtvaliccHours") %>% rename(estimate = b_ccHours), 
+  posterior_samples(mExtvalihhTotal, pars = "b_hhTotal") %>% mutate(model = "mExtvalihhTotal") %>% rename(estimate = b_hhTotal), 
+  posterior_samples(mExtvalihhSibs, pars = "b_hhSibs") %>% mutate(model = "mExtvalihhSibs") %>% rename(estimate = b_hhSibs),
+  posterior_samples(mExtvalisibsChildAged, pars = "b_sibsChildAged") %>% mutate(model = "mExtvalisibsChildAged") %>% rename(estimate = b_sibsChildAged),
+  posterior_samples(mExtvalisiblingsVarietyScoreP, pars = "b_siblingsVarietyScoreP") %>% mutate(model = "mExtvalisiblingsVarietyScoreP") %>% rename(estimate = b_siblingsVarietyScoreP),
+  posterior_samples(mExtvalisiblingsVarietyScoreW, pars = "b_siblingsVarietyScoreW") %>% mutate(model = "mExtvalisiblingsVarietyScoreW") %>% rename(estimate = b_siblingsVarietyScoreW),
+  posterior_samples(mExtvaliPE, pars = "b_pe") %>% mutate(model = "mExtvaliPE") %>% rename(estimate = b_pe)
+) %>% 
+  mutate(
+    model = factor(model, levels = extvaliModelorder) %>% str_remove(., "mExtvali"), 
+  )
+
+write.csv(extvali_results, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
+saveRDS(extvali_results, "../saves/extvali-posteriorsamples.rds")
+
+ggplot(extvaliPostSamples, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
+  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE, 
+    quantiles = c(0.025, 0.975)
+  ) +	
+  scale_fill_manual(values = c("#006c66", "NA", "#006c66"), guide = "none")
+
+ggsave("../figures/extvali-posteriorsample.png")
+```
+
+```{r extvali_save}
+extvali_results <- mExtvaliComparison %>%
+  left_join(mExtvaliComparisonWeights) %>%
+  select(model, waic, value, elpd_diff, se_diff) %>%
+  rename(waic_weight = value) %>% 
+  mutate(
+    model = str_remove(model, "mExtvali")
+  )
+
+write.csv(extvali_results, "../saves/extvali-results.csv", quote = F, row.names = F)
+saveRDS(extvali_results, "../saves/extvali-results.rds")
+```

### 2022-04-07 stats/supplements_webcamcoding.Rmd
add external validity analysis

@@
 ```{r overall_save}
-overall_resuls <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
+overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
   left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
@@
 
-write.csv(overall_resuls, "../saves/supplements-webcamcoding-resuls.csv", quote = F, row.names = F)
-saveRDS(overall_resuls, "../saves/supplements-webcamcoding-results.rds")
+write.csv(overall_results, "../saves/supplements-webcamcoding-results.csv", quote = F, row.names = F)
+saveRDS(overall_results, "../saves/supplements-webcamcoding-results.rds")
 ```

### 2022-04-08 paper/manuscript.Rmd
review ext vali section

@@
 ## Study versions
-We designed two study versions which can be chosen according to the researchers' need: there is a continuous *hedge* version and a discrete *box* version.
+We designed two study versions which can be chosen according to the researchers' need: there is a continuous hedge version and a discrete box version.
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
-In the *hedge* version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
+In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
 Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant’s click.
-In the *box* version, participants are asked to click on a box that hides the target.
+In the box version, participants are asked to click on a box that hides the target.
 Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
@@
 Note that in the test trials of both study versions, the target flight is covered by a hedge.
-In the *hedge* version, the hedge then shrinks to a minimum height required to cover the target's end location.
-In the *box* version, the hedge shrinks completely.
+In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
+In the box version, the hedge shrinks completely.
 The boxes then hide the target's final destination.
@@
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(b) Continuous *hedge* version of the balloon finding task.
+(b) Continuous hedge version of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(c) Discrete *box* version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.
+(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.
 
@@
 The randomization of the target end location depends on the study version.
-In the *hedge* version, the full width of the screen is divided into ten bins.
+In the hedge version, the full width of the screen is divided into ten bins.
 Exact coordinates within each bin are then randomly generated.
-In the *box* version, the target randomly lands in one of the boxes.
+In the box version, the target randomly lands in one of the boxes.
 As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.
@@
 (ref:figlab2) **Measuring interindividual variation**. 
-(a) Developmental trajectory in continuous *hedge* version.
+(a) Developmental trajectory in continuous hedge version.
 Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
@@
 (e) Test-retest reliability in hedge adult sample.
-(f) Developmental trajectory in discrete *box* version.
+(f) Developmental trajectory in discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
@@
 ```
+
 ```{r agemodels}
@@
 First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-Analyses were run using the function `by_split`from the `splithalfr` package [@pronk2021methods].
+Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2021methods].
 Second, we assessed the test-retest reliability.
@@
 Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+
 ```{r extvali_sample}
@@
 In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
-For the target position, we summarized the two adjacent bins into one imaginary box.
-For the click responses, we created imaginary box boundaries around the target's landing position and assessed whether the participant's response fell into this imaginary box.
+For the target position, we categorized two adjacent bins as one imaginary box.
+To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
 Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
-For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subjects entered childcare.
+For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
 In addition, we calculated three index scores.
@@
 Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements).
-Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed).
+Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
 We compared the models using WAIC (widely applicable information criterion) scores and weights.
@@
 ## Results
-[TODO] All effects except when a child entered childcare positively influence performance. 
-The effect sizes are all small and 95% CIs mostly include zero.
-It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.
+```{r extvali_winningmodel}
+mExtvaliPE <- readRDS(file = "../saves/extvali-mExtvaliPE.rds") 
+```
+
+The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy.
+Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
+The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
+For example, for our winning model, we found an estimate of
+`r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
+with the estimates of age being `r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version `r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
+Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.
 
 (ref:figlab4) **External validity of the balloon finding task**. 
-[TODO] WAIC scores and weights can be found in the Supplements section. 
+Factors of children's social surroundings and their influence on the probability of responding correctly.
+Models are ordered according to their WAIC scores, with the uppermost winning the model comparison.
+The graph shows the estimated density curves of a model's predictor coefficient.
+Red tails display the 2.5% and 97.5% quantiles, respectively.
+
 ```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
@@
 
+## Discussion
+Factors of children's social surrounding influenced their gaze cue understanding performance only slightly.
+Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.
+
 # Discussion
+We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike.
+Our results suggest that the measured variation is systematic during the course of the same and different test days.
+Impressively, the ability that our task measures related to factors in children's everyday life experience.
+
 ## Limitations
@@
 All effects except when a child entered childcare positively influence performance.
+
 ```{r extvali_results}

### 2022-04-08 paper/manuscript.tex
review ext vali section

@@
 Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements).
-Third, based on our own data exploration we calculated the amount of peer exposure as the number of siblings and the average hours spent in childcare (all z-transformed).
+Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
 We compared the models using WAIC (widely applicable information criterion) scores and weights.
@@
 
-{[}TODO{]} All effects except when a child entered childcare positively influence performance.
-The effect sizes are all small and 95\% CIs mostly include zero.
-It is remarkable, however, that we were able to detect a relationship between a fundamental social-cognitive ability and very distant, real life demographics.
+The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy.
+Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
+The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
+For example, for our winning model, we found an estimate of
+0.18 (95\% CI {[}-0.01; 0.36{]}),
+with the estimates of age being 0.59 (95\% CI {[}0.40; 0.79{]}), data collection mode being 0.93 (95\% CI {[}0.54; 1.34{]}), and study version 1.84 (95\% CI {[}0.14; 3.47{]}).
+Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.
 
@@
 \caption{\textbf{External validity of the balloon finding task}.
-{[}TODO{]} WAIC scores and weights can be found in the Supplements section.}\label{fig:fig4}
+Factors of children's social surroundings and their influence on the probability of responding correctly.
+Models are ordered according to their WAIC scores, with the uppermost winning the model comparison.
+The graph shows the estimated density curves of a model's predictor coefficients.
+Red tails display the 2.5\% and 97.5\% quantiles, respectively.}\label{fig:fig4}
 \end{figure}
@@
 \hypertarget{discussion-2}{%
-\section{Discussion}\label{discussion-2}}
+\subsection{Discussion}\label{discussion-2}}
+
+Factors of children's social surrounding influenced their gaze cue understanding performance only slightly.
+Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.
+
+\hypertarget{discussion-3}{%
+\section{Discussion}\label{discussion-3}}
+
+We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike.
+Our results suggest that the measured variation is systematic during the course of the same and different test days.
+Impressively, the ability that our task measures related to factors in children's everyday life experience.
 
@@
 \hline
-PE & 2391.092 & 0.4516270 & 0.0000000 & 0.0000000\\
-\hline
-siblingsVarietyScoreP & 2391.433 & 0.2009621 & -0.1703600 & 1.1084142\\
-\hline
-siblingsVarietyScoreW & 2391.612 & 0.0489847 & -0.2602340 & 1.1033051\\
-\hline
-hhSibs & 2391.654 & 0.0932701 & -0.2809574 & 0.9592453\\
-\hline
-null & 2391.963 & 0.0003588 & -0.4355391 & 1.3235267\\
-\hline
-ccAge & 2392.770 & 0.2047406 & -0.8390844 & 1.7165235\\
-\hline
-sibsChildAged & 2393.059 & 0.0000352 & -0.9836425 & 1.0349722\\
-\hline
-ccHours & 2393.156 & 0.0000134 & -1.0320103 & 1.0784916\\
-\hline
-hhTotal & 2393.647 & 0.0000082 & -1.2775838 & 0.9703247\\
+PE & 2390.222 & 0.5405439 & 0.0000000 & 0.0000000\\
+\hline
+siblingsVarietyScoreP & 2390.429 & 0.3408146 & -0.1032133 & 1.0951621\\
+\hline
+ccHours & 2391.667 & 0.0001320 & -0.7222674 & 1.0449378\\
+\hline
+hhTotal & 2391.965 & 0.0001205 & -0.8716164 & 0.9255789\\
+\hline
+hhSibs & 2392.245 & 0.0000189 & -1.0114203 & 0.9762202\\
+\hline
+sibsChildAged & 2392.407 & 0.0000134 & -1.0924575 & 1.0418509\\
+\hline
+ccAge & 2392.445 & 0.1182920 & -1.1114913 & 1.6858011\\
+\hline
+null & 2392.618 & 0.0000583 & -1.1978484 & 1.2901087\\
+\hline
+siblingsVarietyScoreW & 2392.952 & 0.0000064 & -1.3648559 & 1.0877168\\
 \hline

### 2022-04-08 stats/analysis.Rmd
review ext vali section

@@
 
-n_distinct(extvali$subjID)
+n_distinct(mDataExtvali$subjID)
 ```
@@
 extvaliModelorder <- mExtvaliComparisonWeights %>% arrange(value) %>%  pull(model)
+```
+
+```{r extvali_savemodels}
+write.csv(mExtvalinull, "../saves/extvali-mExtvalinull.csv", quote = F, row.names = F)
+saveRDS(mExtvalinull, "../saves/extvali-mExtvalinull.rds")
+
+write.csv(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.csv", quote = F, row.names = F)
+saveRDS(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.rds")
+
+write.csv(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.csv", quote = F, row.names = F)
+saveRDS(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.rds")
+
+write.csv(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.csv", quote = F, row.names = F)
+saveRDS(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.rds")
+
+write.csv(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.csv", quote = F, row.names = F)
+saveRDS(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.rds")
+
+write.csv(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.csv", quote = F, row.names = F)
+saveRDS(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.rds")
+
+write.csv(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.csv", quote = F, row.names = F)
+saveRDS(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.rds")
+
+write.csv(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.csv", quote = F, row.names = F)
+saveRDS(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.rds")
+
+write.csv(mExtvaliPE, "../saves/extvali-mExtvaliPE.csv", quote = F, row.names = F)
+saveRDS(mExtvaliPE, "../saves/extvali-mExtvaliPE.rds")
 ```
@@
   mutate(
-    model = factor(model, levels = extvaliModelorder) %>% str_remove(., "mExtvali"), 
-  )
-
-write.csv(extvali_results, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
-saveRDS(extvali_results, "../saves/extvali-posteriorsamples.rds")
+    model = factor(model, levels = extvaliModelorder, labels = c("sibling variety score (Cassidy et al., 2005)", "number of children in household aged 1-12", "number of children in household aged 0-18", "null model", "number of household members", "average hours spent in childcare per day", "age of childcare entry", "sibling variety score (Peterson, 2000)", "peer exposure index"))
+  )
+
+write.csv(extvaliPostSamples, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
+saveRDS(extvaliPostSamples, "../saves/extvali-posteriorsamples.rds")
 
@@
   ) +	
-  scale_fill_manual(values = c("#006c66", "NA", "#006c66"), guide = "none")
-
-ggsave("../figures/extvali-posteriorsample.png")
+  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") + 
+  scale_x_continuous(limits = c(-0.25, 0.75)) + 
+  ylab("")
+
+ggsave("../figures/extvali-posteriorsample.png", width = 6, height = 3)
 ```

### 2022-04-11 paper/manuscript.Rmd
edit methods section, add abstract first draft

@@
 abstract: |
-  There must be an abstract of no more than 250 words.
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  In order to explain and predict the behavior of agents, we use social cognition: we represent and reason about other’s perspectives, knowledge, intentions, beliefs and preferences.
+Traditional measures of social cognition (e.g., false belief change-of-location tasks), however, often lack satisfactory psychometric properties: they are not designed to capture variation *between* children and rely on low trial numbers, dichotomous measures, and group averages.
+This has profound implications on what these studies can show.
+Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
+   To approach this issue, we designed a balloon finding task to study social cognition in young children and adults.
+We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding – the ability to locate and use the attentional focus of an agent.
+Our interactive web interface works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+The implemented spatial layout allows for discrete as well as continuous measures of participants’ click imprecision and is easily adoptable to different study needs.
+  Here we show that our task induces inter-individual differences in a child (N = XXX) and adult (N = XXX) sample.
+Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
+High internal consistency and test-test reliability estimates underline that the capured variation is systematic.
+Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real life social surrounding.
+Taken together, this work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
 
@@
 ## Stimuli
-Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike.
-An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
+Our newly implemented task features an online game where children or adults are asked to search for a balloon.
+The events proceed as follows.
+An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
 A balloon (i.e., target; blue, green, yellow, or red) is located in front of them.
@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target’s destination: they respond by touching or clicking onto position on the screen.
+Participants are then asked to locate the target’s destination: they respond by touching or clicking onto a position on the screen.
+Visual access to the target’s true location is manipulated by a hedge.
+Participants either have full, partial, or no visual access to the true target location.
+When partial or no information about the target location is accessible, participants are expected to use the agent’s gaze as a cue.
 
@@
 Once the target landed, the instructor's voice asks "Where is the balloon?".
-After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
+For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
 If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 ## Trials
-Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen.
+Trials differ in the amount of visual access that participants have to the final target position.
+Before the test trials start, we present four training trials during which participants familiarize themselves with selecting positions on the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 ## Study versions
-We designed two study versions which can be chosen according to the researchers' need: there is a continuous hedge version and a discrete box version.
+We designed two study versions which can be chosen according to the researchers' need.
+The study versions differ in the final hiding place of the target and, consequently, on the outcome measure: there is a continuous hedge version and a discrete box version.
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
 In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant’s click.
-In the box version, participants are asked to click on a box that hides the target.
-Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant’s click.
+In the discrete study version, the target lands in a box and participants are asked to click on the  box that hides the target.
+Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
 Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
@@
 The agent's eyes track the movement of the target.
-(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.
+(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
 
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform (GSAP; @greensock2022gsap) library was used to animate the movement of single SVG elements. 
+The GreenSock Animation Platform [GSAP; @greensock2022gsap] library was used to animate the movement of single SVG elements. 
 We use URL parameters to capture the participant's ID, language and study version. 
@@
 
-For our remote child sample, we recruited families on a voluntary basis via email from the institute's internal database.
-Our remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
+For our remote child sample, we recruited families on a voluntary basis via email from our institute's internal database.
+The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
 `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
@@
 Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
-Children in the remote sample received a personalized link to the study websites and families could participate at any time or location they wanted.
+
+Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
 In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
@@
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
-Here, `targetPosition` refers to the absolute bin/box of the target, while `symmetricPosition` refers to the distance from the stimulus center (i.e., smaller value meaning more central target position).
+Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
 We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
@@
 ## Discussion
-Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+Our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
 With increasing age, participants got more and more precise in locating the target.
@@
 The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (section *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
+Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
 In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
@@
 The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
-For example, for our winning model, we found an estimate of
+For example, for our winning model, we found a peer exposure estimate of
 `r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
@@
 ## Discussion
-Factors of children's social surrounding influenced their gaze cue understanding performance only slightly.
-Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.
+We found small evidence that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effect sizes are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
 
@@
 Our results suggest that the measured variation is systematic during the course of the same and different test days.
-Impressively, the ability that our task measures related to factors in children's everyday life experience.
+Impressively, gaze cue understanding as measured by our task related to factors in children's everyday life experience.
 

### 2022-04-11 paper/manuscript.tex
edit methods section, add abstract first draft

@@
 \abstract{%
-There must be an abstract of no more than 250 words.
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+In order to explain and predict the behavior of agents, we use social cognition: we represent and reason about other's perspectives, knowledge, intentions, beliefs and preferences.
+Traditional measures of social cognition (e.g., false belief change-of-location tasks), however, often lack satisfactory psychometric properties: they are not designed to capture variation \emph{between} children and rely on low trial numbers, dichotomous measures, and group averages.
+This has profound implications on what these studies can show.
+Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
+To approach this issue, we designed a balloon finding task to study social cognition in young children and adults.
+We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding -- the ability to locate and use the attentional focus of an agent.
+Our interactive web interface works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+The implemented spatial layout allows for discrete as well as continuous measures of participants' click imprecision and is easily adoptable to different study needs.
+Here we show that our task induces inter-individual differences in a child (N = XXX) and adult (N = XXX) sample.
+Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
+High internal consistency and test-test reliability estimates underline that the capured variation is systematic.
+Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real life social surrounding.
+Taken together, this work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
 }
@@
 
-Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike.
-An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window.
+Our newly implemented task features an online game where children or adults are asked to search for a balloon.
+The events proceed as follows.
+An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
 A balloon (i.e., target; blue, green, yellow, or red) is located in front of them.
@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target's destination: they respond by touching or clicking onto position on the screen.
+Participants are then asked to locate the target's destination: they respond by touching or clicking onto a position on the screen.
+Visual access to the target's true location is manipulated by a hedge.
+Participants either have full, partial, or no visual access to the true target location.
+When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.
 
@@
 Once the target landed, the instructor's voice asks ``Where is the balloon?''.
-After the response is registered, a short plop sound plays and a small orange circle confirms the participants' location choice.
+For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
 If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 
-Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen.
+Trials differ in the amount of visual access that participants have to the final target position.
+Before the test trials start, we present four training trials during which participants familiarize themselves with selecting positions on the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 
-We designed two study versions which can be chosen according to the researchers' need: there is a continuous \emph{hedge} version and a discrete \emph{box} version.
+We designed two study versions which can be chosen according to the researchers' need.
+The study versions differ in the final hiding place of the target and, consequently, on the outcome measure: there is a continuous hedge version and a discrete box version.
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
-In the \emph{hedge} version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version).
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the target's true x coordinate and the x coordinate of the participant's click.
-In the \emph{box} version, participants are asked to click on a box that hides the target.
-Researchers have the choice of how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
+In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version).
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
+In the discrete study version, the target lands in a box and participants are asked to click on the box that hides the target.
+Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
 Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
 Note that in the test trials of both study versions, the target flight is covered by a hedge.
-In the \emph{hedge} version, the hedge then shrinks to a minimum height required to cover the target's end location.
-In the \emph{box} version, the hedge shrinks completely.
+In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
+In the box version, the hedge shrinks completely.
 The boxes then hide the target's final destination.
@@
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(b) Continuous \emph{hedge} version of the balloon finding task.
+(b) Continuous hedge version of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(c) Discrete \emph{box} version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set individually.}\label{fig:fig1}
+(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
 \end{figure}
@@
 The randomization of the target end location depends on the study version.
-In the \emph{hedge} version, the full width of the screen is divided into ten bins.
+In the hedge version, the full width of the screen is divided into ten bins.
 Exact coordinates within each bin are then randomly generated.
-In the \emph{box} version, the target randomly lands in one of the boxes.
+In the box version, the target randomly lands in one of the boxes.
 As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform (GSAP; Greensock (2022)) library was used to animate the movement of single SVG elements.
+The GreenSock Animation Platform {[}GSAP; Greensock (2022){]} library was used to animate the movement of single SVG elements.
 We use URL parameters to capture the participant's ID, language and study version.
@@
 
-For our remote child sample, we recruited families on a voluntary basis via email from the institute's internal database. Our remote child sample included 147 children, including
+For our remote child sample, we recruited families on a voluntary basis via email from our institute's internal database. The remote child sample included 147 children, including
 45 3-year-olds
@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
+Participants consisted of 50, 50, 50, and 50 English-speakers with an average age of 31.92, 31.92, 30.76, and 30.76 years (SD = 12.15, 12.15, 9.12, and 9.12, range = 18, 18, 19, and 19 - 63, 63, 59, and 59, 36, 28, 36, and 28 females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
-Children in the remote sample received a personalized link to the study websites and families could participate at any time or location they wanted.
+
+Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
 In the beginning of the online study, families were invited to enter our ``virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
@@
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
-Here, \texttt{targetPosition} refers to the absolute bin/box of the target, while \texttt{symmetricPosition} refers to the distance from the stimulus center (i.e., smaller value meaning more central target position).
+Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
 We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
@@
 \caption{\textbf{Measuring interindividual variation}.
-(a) Developmental trajectory in continuous \emph{hedge} version.
+(a) Developmental trajectory in continuous hedge version.
 Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
@@
 (e) Test-retest reliability in hedge adult sample.
-(f) Developmental trajectory in discrete \emph{box} version.
+(f) Developmental trajectory in discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
@@
 
-Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+Our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
 With increasing age, participants got more and more precise in locating the target.
@@
 The child sample consisted of
-93 children, including
-24 3-year-olds
-(mean = 42.49 months,
-SD = 2.99,
+106 children, including
+35 3-year-olds
+(mean = 42.57 months,
+SD = 2.98,
 range = 38
 - 47,
-13 girls),
+17 girls),
 38 4-year-olds
@@
 19 girls),
-and 31 5-year-olds
-(mean = 66 months,
-SD = 3.42,
+and 33 5-year-olds
+(mean = 66.12 months,
+SD = 3.36,
 range = 61
@@
 
-The adult sample was recruited over \emph{Prolific} and consisted of 136 English-speakers with an average age of 25.74 years (SD = 8.11, range = 18 - 71, 87 females).
+The adult sample was recruited over \emph{Prolific} and consisted of 70, 70, 66, and 66 English-speakers with an average age of 25.43, 25.43, 26.05, and 26.05 years (SD = 6.43, 6.43, 9.44, and 9.44, range = 18, 18, 18, and 18 - 51, 51, 71, and 71, 45, 42, 45, and 42 females).
 
@@
 First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-Analyses were run using the function \texttt{by\_split}from the \texttt{splithalfr} package (Pronk et al., 2021).
+Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).
 Second, we assessed the test-retest reliability.
@@
 For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
-130 children, including
-39 3-year-olds
-(mean = 43.02 months,
-SD = 3.20,
+136 children, including
+41 3-year-olds
+(mean = 43.17 months,
+SD = 3.13,
 range = 37
@@
 20 girls),
-44 4-year-olds
+46 4-year-olds
 (mean = 54.43 months,
-SD = 2.77,
+SD = 2.76,
 range = 48
@@
 26 girls),
-and 47 5-year-olds
-(mean = 66.13 months,
-SD = 3.55,
+and 49 5-year-olds
+(mean = 66.25 months,
+SD = 3.47,
 range = 60
@@
 The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (section \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
+Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
 In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
@@
 The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
-For example, for our winning model, we found an estimate of
+For example, for our winning model, we found a peer exposure estimate of
 0.18 (95\% CI {[}-0.01; 0.36{]}),
@@
 Models are ordered according to their WAIC scores, with the uppermost winning the model comparison.
-The graph shows the estimated density curves of a model's predictor coefficients.
+The graph shows the estimated density curves of a model's predictor coefficient.
 Red tails display the 2.5\% and 97.5\% quantiles, respectively.}\label{fig:fig4}
@@
 
-Factors of children's social surrounding influenced their gaze cue understanding performance only slightly.
-Nevertheless, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables at all.
+We found small evidence that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effect sizes are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
 

### 2022-04-12 paper/manuscript.Rmd
switch to apa_table, less complicated way to count gender in sample characteristics

@@
   group_by(datacollection, ageInYears) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
   summarise(
@@
     maxAgeInMonths = max(ageInMonths, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
   )
-
-vali_kids_gender <- vali %>% 
-  filter(ageInYears < 6) %>% 
-  group_by(datacollection, ageInYears) %>%
-  filter(gender == "f") %>% 
-  summarise(
-    nFemales = length(unique(subjID))
-  )
-
-vali_kids <- vali_kids %>% 
-  left_join(vali_kids_gender, by = c("datacollection", "ageInYears"))
 
@@
   filter(ageInYears == 18) %>% 
+  mutate(
+    gender = ifelse(is.na(gender), 0, paste(gender)), 
+    female = ifelse(gender == "f", 1, 0),
+  ) %>% 
   summarise(
@@
     maxAge = max(age, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
   )
-
-vali_adults_gender <- vali %>% 
-  filter(ageInYears == 18 & gender == "f") %>% 
-  summarise(
-    nFemales = length(unique(subjID))
-  )
-
-vali_adults <- vali_adults %>% 
-  full_join(vali_adults_gender, by = character())
 ```
@@
     maxAgeInMonths = max(ageInMonths, na.rm = T),
+    nFemales = ceiling(sum(female/30)), # 15 test trials * 2
   )
-
-reli_kids_gender <- reli %>% 
-  filter(ageInYears < 6) %>% 
-  group_by(datacollection, ageInYears) %>%
-  filter(gender == "f") %>% 
-  summarise(
-    nFemales = length(unique(subjID))
-  )
-
-reli_kids <- reli_kids %>% 
-  left_join(reli_kids_gender, by = c("datacollection", "ageInYears"))
 
@@
     maxAge = max(age, na.rm = T),
+    nFemales = sum(female),
+  ) %>% 
+  mutate(
+    nFemales = ifelse(studyversion == "hedge", nFemales/60, nFemales/64), # test trials * 2
+    nFemales = ceiling(nFemales)
   )
-
-reli_adults_gender <- reli %>% 
-  filter(ageInYears == 18 & gender == "f") %>% 
-  summarise(
-    nFemales = length(unique(subjID))
-  )
-
-reli_adults <- reli_adults %>% 
-  full_join(reli_adults_gender, by = character())
 ```
@@
   group_by(ageInYears) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
   summarise(
@@
     maxAgeInMonths = max(ageInMonths, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
   )
-
-extvali_gender <- extvali %>% 
-  group_by(ageInYears) %>%
-  filter(gender == "f") %>% 
-  summarise(
-    nFemales = length(unique(subjID))
-  )
-
-extvali_sample <- extvali_sample %>% 
-  left_join(extvali_gender, by = c("ageInYears"))
 ```
@@
 In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95% CI of the model estimates included zero and were rather wide.
+Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
 Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
 
-```{r webcam_coding}
-webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds")
-
-knitr::kable(webcam_models)
+```{r webcam_table, results = "asis"}
+webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
+  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
+  mutate_if(is.numeric, round, 2)
+
+papaja::apa_table(
+  webcam_models, 
+  caption = "Model comparison for exploratory webcam coding of parental interference", 
+  note = "All models included random intercepts for participant and target position.", 
+  escape = T
+)
 ```
@@
 As can be seen, ELPD difference scores are smaller than their respective standard errors.
-WAIC scores between models don't differ substantially.
+WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}).
 All effects except when a child entered childcare positively influence performance.
 
-```{r extvali_results}
-extvali_models <- readRDS(file = "../saves/extvali-results.rds")
-knitr::kable(extvali_models)
+```{r extvali_table, results = "asis"}
+extvali_models <- readRDS(file = "../saves/extvali-results.rds") %>% 
+  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
+  mutate_if(is.numeric, round, 2)
+
+papaja::apa_table(
+  webcam_models, 
+  caption = "Model comparison for influences of children's social surrounding", 
+  note = "All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants", 
+  escape = T
+)
 ```

### 2022-04-12 paper/manuscript.tex
switch to apa_table, less complicated way to count gender in sample characteristics

@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of 50, 50, 50, and 50 English-speakers with an average age of 31.92, 31.92, 30.76, and 30.76 years (SD = 12.15, 12.15, 9.12, and 9.12, range = 18, 18, 19, and 19 - 63, 63, 59, and 59, 36, 28, 36, and 28 females).
+Participants consisted of 50 and 50 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 - 59,
-19 girls),
+20 girls),
 and 33 5-year-olds
@@
 
-The adult sample was recruited over \emph{Prolific} and consisted of 70, 70, 66, and 66 English-speakers with an average age of 25.43, 25.43, 26.05, and 26.05 years (SD = 6.43, 6.43, 9.44, and 9.44, range = 18, 18, 18, and 18 - 51, 51, 71, and 71, 45, 42, 45, and 42 females).
+The adult sample was recruited over \emph{Prolific} and consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).
 
@@
 - 47,
-20 girls),
+23 girls),
 46 4-year-olds
@@
 - 59,
-26 girls),
+34 girls),
 and 49 5-year-olds
@@
 - 71,
-23 girls).
+27 girls).
 
@@
 In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95\% CI of the model estimates included zero and were rather wide.
+Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
 Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
 
-\begin{tabular}{l|r|r|r|r}
-\hline
-model & waic & waic\_weight & elpd\_diff & se\_diff\\
-\hline
-mPerTrialVerificationChoice & 263.24183 & 0.6469352 & 0.0000000 & 0.000000\\
-\hline
-mPerTrialNull & 263.74712 & 0.3530572 & -0.2526455 & 1.202097\\
-\hline
-mPerTrialPI & 264.34608 & 0.0000048 & -0.5521261 & 0.978696\\
-\hline
-mPerTrialRepeatedTestquestion & 265.43452 & 0.0000011 & -1.0963445 & 1.272427\\
-\hline
-mPerTrialHintsEyes & 265.67182 & 0.0000014 & -1.2149955 & 1.255888\\
-\hline
-mPerTrialParentSpeech & 266.45389 & 0.0000003 & -1.6060301 & 1.211500\\
-\hline
-mPerSubjectRepeatedTestquestion & 83.52517 & 0.7033000 & 0.0000000 & 0.000000\\
-\hline
-mPerSubjectPI & 88.25288 & 0.0000019 & -2.3638570 & 3.596520\\
-\hline
-mPerSubjectNull & 89.25650 & 0.0000003 & -2.8656662 & 3.608723\\
-\hline
-mPerSubjectVerificationChoice & 89.85833 & 0.2966959 & -3.1665822 & 4.484388\\
-\hline
-mPerSubjectParentSpeech & 90.44632 & 0.0000018 & -3.4605795 & 4.204938\\
-\hline
-mPerSubjectHintsEyes & 92.76122 & 0.0000001 & -4.6180264 & 3.773420\\
-\hline
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
+
+\begin{tabular}{lllll}
+\toprule
+model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
+\midrule
+mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
+mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
+mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
+mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
+mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
+mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
+mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
+mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
+mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
+mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
+mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
+mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
+\bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 As can be seen, ELPD difference scores are smaller than their respective standard errors.
-WAIC scores between models don't differ substantially.
+WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}).
 All effects except when a child entered childcare positively influence performance.
 
-\begin{tabular}{l|r|r|r|r}
-\hline
-model & waic & waic\_weight & elpd\_diff & se\_diff\\
-\hline
-PE & 2390.222 & 0.5405439 & 0.0000000 & 0.0000000\\
-\hline
-siblingsVarietyScoreP & 2390.429 & 0.3408146 & -0.1032133 & 1.0951621\\
-\hline
-ccHours & 2391.667 & 0.0001320 & -0.7222674 & 1.0449378\\
-\hline
-hhTotal & 2391.965 & 0.0001205 & -0.8716164 & 0.9255789\\
-\hline
-hhSibs & 2392.245 & 0.0000189 & -1.0114203 & 0.9762202\\
-\hline
-sibsChildAged & 2392.407 & 0.0000134 & -1.0924575 & 1.0418509\\
-\hline
-ccAge & 2392.445 & 0.1182920 & -1.1114913 & 1.6858011\\
-\hline
-null & 2392.618 & 0.0000583 & -1.1978484 & 1.2901087\\
-\hline
-siblingsVarietyScoreW & 2392.952 & 0.0000064 & -1.3648559 & 1.0877168\\
-\hline
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:extvali_table}Model comparison for influences of children's social surrounding}
+
+\begin{tabular}{lllll}
+\toprule
+model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
+\midrule
+mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
+mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
+mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
+mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
+mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
+mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
+mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
+mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
+mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
+mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
+mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
+mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
+\bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2022-04-13 paper/manuscript.Rmd

@@
 
-# Design of our balloon finding task
+# Task design
 - face value of task (or maybe in intro already?)
@@
 Our newly implemented task features an online game where children or adults are asked to search for a balloon.
-The events proceed as follows.
+The events proceed as follows (see Figure \@ref(fig:fig1)B and C).
 An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target’s destination: they respond by touching or clicking onto a position on the screen.
+Participants are then asked to locate the target: they respond by touching or clicking on the screen.
 Visual access to the target’s true location is manipulated by a hedge.
@@
 For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
-If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
+If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
 
@@
 Trials differ in the amount of visual access that participants have to the final target position.
-Before the test trials start, we present four training trials during which participants familiarize themselves with selecting positions on the screen.
+Before the test trials start, participants complete four training trials during which they familiarize themselves with clicking the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
-In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location.
-They are then asked to click on the invisible balloon, i.e., the location where they saw the target land.
-In test trials, participants have no visual access to the target flight nor the end location.
+In the second and third training trials, participants have partial access: they witness the target flight but cannot see the target's end location.
+They are then asked to click on the hidden balloon, i.e., the location where they saw the target land.
+In test trials, participants have no visual access to the target flight or the end location.
 Participants are expected to use the agent’s gaze as a cue to locate the target.
@@
 The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script).
-After these four training and audio guided trials, participants receive 15 test trials.
-The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.
+After the four training trials, participants receive 15 test trials.
+The complete sequence of four training trials and 15 test trials can be easily completed within 5-10 minutes.
 
 ## Study versions
-We designed two study versions which can be chosen according to the researchers' need.
-The study versions differ in the final hiding place of the target and, consequently, on the outcome measure: there is a continuous hedge version and a discrete box version.
+We designed two study versions which differ in the final hiding place of the target and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
-In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
+In the hedge version, participants have to indicate their estimated target location directly on a hedge.
 Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant’s click.
-In the discrete study version, the target lands in a box and participants are asked to click on the  box that hides the target.
+In the box version, the target lands in a box and participants are asked to click on the  box that hides the target.
 Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
 Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
-Note that in the test trials of both study versions, the target flight is covered by a hedge.
+Note that in the test trials of both versions, the target flight is covered by a hedge.
 In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
 In the box version, the hedge shrinks completely.
-The boxes then hide the target's final destination.
+The boxes then hide the target's final destination (see Figure \@ref(fig:fig1)B and C).
 
 (ref:figlab1) **Study setup**. 
-(a) Infrastructure for online testing.
+(A) Infrastructure for online testing.
 (i) Subjects aged 3 – 99+ can participate.
-Data collection can take place anywhere: at home, in kindergartens or research institutes.
+Data collection can take place anywhere: online, in kindergartens or research labs.
 (ii) The task is presented as a website that works across devices.
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(b) Continuous hedge version of the balloon finding task.
+(B) Hedge version (continuous) of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
+(C) Box version (discrete) of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
 
@@
 
-## Implementation
+## Implementation [m: das vll zuerst - vor der Beschreibung der versionen]
 Our balloon finding task is presented as an interactive web-app.
 The task is portable across devices and web browsers and does not require any installation.
-A great advantage of online testing is that our testing procedure is standardized across participants.
+An advantage of online testing is that our testing procedure is standardized across participants.
 By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
-We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
+
+The web-app was programmed in `JavaScript` (ECMAScript 2015, i.e., ES6), `HTML5`, `CSS` and `PHP`.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform [GSAP; @greensock2022gsap] library was used to animate the movement of single SVG elements. 
-We use URL parameters to capture the participant's ID, language and study version. 
 The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany.
-Data got automatically collected and safely stored on these in-house servers.
-If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
-For child samples, we upload safety copies of the already collected responses after the fourth test trial.
-In cases where children want to stop participation earlier, no responses get lost.
-
-# Does the balloon finding task induce variation?
+These files can either be sent to a server or downloaded to the local device.
+
+# Individual differences
 Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample.
@@
 
-The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample).
+Methods, sample size and analysis were pre-registered: https://osf.io/snju6 (child sample) and https://osf.io/r3bhn (adult sample).
 Participants were equally distributed across the two study versions.
@@
 We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
-In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-The in-person child sample consisted of
+In-person testing with children took place in kindergartens in Leipzig, Germany. The in-person child sample consisted of 
 `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
@@
 
-For our remote child sample, we recruited families on a voluntary basis via email from our institute's internal database.
+For our remote child sample, we recruited families via an internal database.
 The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
@@
 
-In addition, we recruited a remote adult sample by advertising the study on *Prolific*.
+Adults were recruited via *Prolific*.
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
-*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
 
 ## Procedure
-Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
-
+Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
 Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
@@
 
-Our adult sample participated remotely without supervision.
-
-All participants received 15 test trials that were displayed as described above.
+All participants received 15 test trials.
 In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.
@@
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a lognormal distribution.
-For the box version, the model predicted correct responses (0/1) using a Bernoulli distribution with a logit link function.
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
+For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
 We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
@@
 (ref:figlab2) **Measuring interindividual variation**. 
-(a) Developmental trajectory in continuous hedge version.
+(A) Developmental trajectory in continuous hedge version.
 Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
 The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
-(b) Internal consistency (odd-even split) in hedge child sample.
-(c) Internal consistency in hedge adult sample.
-(d) Test-retest reliability in hedge child sample.
-(e) Test-retest reliability in hedge adult sample.
-(f) Developmental trajectory in discrete box version.
+(B) Internal consistency (odd-even split) in hedge child sample.
+(C) Internal consistency in hedge adult sample.
+(D) Test-retest reliability in hedge child sample.
+(E) Test-retest reliability in hedge adult sample.
+(F) Developmental trajectory in discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
 Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
-(g) Internal consistency (odd-even split) in box child sample.
-(h) Internal consistency in box adult sample.
-(i) Test-retest reliability in box child sample.
-(j) Test-retest reliability in box adult sample.
-Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r.* 
-Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
-Small data points show the mean performance for each subject.
-Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
-Color of data points represent each age group (binned by year).
+(G) Internal consistency (odd-even split) in box child sample.
+(H) Internal consistency in box adult sample.
+(I) Test-retest reliability in box child sample.
+(J) Test-retest reliability in box adult sample.
+Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r*.
+[m: die regressions linie ist ein smoothed mean based on liner model - guck einfach mal ?geom_smooth]
+Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
+Small points show the mean performance for each subject.
+Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection.
+Color of data points denotes age group.
 
@@
 
-We captured a developmental trajectory of gaze cue understanding: with increasing age, participants got more and more accurate in locating the target.
-In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
+In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure 2 A and F [m: siehe oben wie man auf die figures verweist]).
 Most participants in the box version performed above chance level.
 By the end of their sixth year of life, children came close to the adult's proficiency level.
-We found interindividual variation across study versions and age groups.
-For instance, this can be seen in that some three-year-olds were more precise in their responses than some five-year-olds.
+Most impoertantly, however, we found subtantial interindividual variation across study versions and age groups.
+For example, some three-year-olds were more precise in their responses than some five-year-olds [m: jetzt noch was zu den erwachsenene - sagen ,dass da auch variation ist; weniger als bei den kindern, but still].
 
@@
 
-Our GLMM analysis corroborated the effects of age and data collection mode that we already identified by visual inspection: in the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]).
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, we the estimates for age of ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were reliably different from zero [m: so würde ich alle estiamtes berichten.
+also sagen ob positive oder negative und ob veschieden von 0 oder nicht].
 In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]).
-Note that the effect of data collection appears to be present, but confidence intervals are wide.
+Note that the effect of data collection appears to be present, but confidence intervals are wide [m: das präziser - positive effect, but nor reliably different from 0 oder so].
 
 ## Discussion
-Our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+Our task induced interintidivudal variation in both adults and children.
 With increasing age, participants got more and more precise in locating the target.
-We found interindividual variation across all age groups.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
-This underlines how flexibly our new task can be used.
-
-# Can we capture variation reliably?
-As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable (i.e.,
-systematically order individuals in the same way).
-For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
-The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).
+This illustrates the flexibility of the task.
+
+# Internal consistency and retest reliability
+
+As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+We assessed internal consistency (split-half reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: )https://osf.io/xqm73 (child sample),  https://osf.io/nu62m (adult sample)).
 Participants were equally distributed across the two study versions.
@@
 ## Participants
-For our child sample, we went to kindergartens in Leipzig and surroundings.
-The child sample consisted of 
+Participants were recruited in the same way as in the previous study. The child sample consisted of 
 `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
@@
 
-The adult sample was recruited over *Prolific* and consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
+The adult sample consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
 
 ## Procedure
-We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
+We applied the same procedure as in the first study, with the following differences.
+Participants completed the study twice, with a delay of 14 ± 3 days.
 The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
@@
 First, we focused on the internal consistency by calculating splithalf reliability coefficients.
-For each subject, trials were split into odd and even and performance scores per part were correlated against each other using *Pearson* correlation coefficients.
-We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices.
-As a recent paper by @pronk2021methods suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using *Pearson* coefficients.
+For this, we used the data of the first test day.
+Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+@pronk2021methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2021methods].
+
 Second, we assessed the test-retest reliability.
-We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using *Pearson* correlation coefficients.
-Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach.
+We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
+Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [m: hier noch das paper zitieren].
 We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
@@
 Most importantly, the model allows us to get an age-independent estimate for reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen.
+also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum; also maturation ist sehr loaded - einfach domain general cognitive development].
 
@@
 We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
-
 For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure 2 B, C, G and H.
-
-Figure 3 compares splithalf reliability coefficients by splitting and stratification method, following @pronk2021methods.
+Figure 3 compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
 In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
@@
 [^fn2]: In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
-The performance of the mentioned child lay 3 standard deviations above the mean on both test days.
+The performance of the mentioned child was 3 standard deviations above the mean on both test days.
 Including the child yielded a *Pearson* correlation coefficient of *r* = 0.87.
 
-Taking age into account in our GLMM based approach yielded similar results.
-The age-independent retest reliability estimate in the hedge version amounted to `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
-In the box version of the task, the age-independent correlation between participant specific test day estimates was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
-The results suggest that our novel balloon finding task did capture individual differences beyond general cognitive maturation processes.
-This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the driving force acccounting for individual differences.
+The age-corrected, GLMM based retest reliabilities for children yielded similar results.
+In hedge version it was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the box version it was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
 
 ## Discussion
-Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
-
-# Exploring the external validity of our task
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+Our results indicated that the measured variation was systematic.
+As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
+For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
+This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
+
+# Validity
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment [m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden.
+Daher sehen wir das als indikator für validität, wenn wir das auch finden.]
 
@@
 ## Procedure
-Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire (print out / online questionnaire).
+Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire.
 We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
@@
 To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
-Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
-For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
+Across the two study versions, we could consequently model the participant's correct response (0/1) using a `Bernoulli` distribution with a logit link function.
+For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
 In addition, we calculated three index scores.
@@
 Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
-We compared the models using WAIC (widely applicable information criterion) scores and weights.
+We compared the models using WAIC (widely applicable information criterion) scores and weights [m: cite MCElreath dafür].
 As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
@@
 The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
-For example, for our winning model, we found a peer exposure estimate of
+For example, for our winning model, we found a peer exposure estimate of [m: hier bitte auch immer beta = notation machen]
 `r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
 with the estimates of age being `r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version `r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
-Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze.
-The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.
+Nevertheless, a general pattern emerges: exposure to a more vairable social environment positively influenced children's gaze cue understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow [m: na na ..
+ich dachte wir messen gaze cue *understanding*] the agent's gaze.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
+
+[m: figure 4 gefällt mir noch nciht so gut - vll kannst du noch point estimates und Cis mit reinmachen.
+so wie bei den gafo-clt merge plots.
+Die sind hier: https://github.com/ccp-eva/vocab/blob/main/analysis/clt_gafo_merge.Rmd, Zeile 114]
 
@@
 ## Discussion
-We found small evidence that factors of children's social surrounding influenced their gaze cue understanding.
-Even though the effect sizes are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
+In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables [m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen].
 
@@
 In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
+Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
+We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
 In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial. 
@@
 WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
 In all cases, however, ELPD difference scores were smaller than their standard errors.
 Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis [m: naja, ich würde sagen, dass der effekt nicht sonderlich groß ist, aber wen dann kommt er so zustande wie oben erklärt.
+Wir wollen ja weg von effekt da vs.
+nciht da].
 

### 2022-04-28 paper/manuscript.Rmd
new fig4, fix ccAge calculation error, incorporate some of M feedback

@@
 
+## Implementation
+Our balloon finding task is presented as an interactive web app.
+The task is portable across devices and web browsers and does not require any installation.
+An advantage of online testing is that our testing procedure is standardized across participants.
+By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
+The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
+
+The web app was programmed in `JavaScript`, `HTML5`, `CSS` and `PHP`.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
+This is needed for precisely calculating exact pupil and target locations and sizes.
+Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
+The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+These files can either be sent to a server or downloaded to the local device.
+
 ## Stimuli
@@
 
-## Implementation [m: das vll zuerst - vor der Beschreibung der versionen]
-Our balloon finding task is presented as an interactive web-app.
-The task is portable across devices and web browsers and does not require any installation.
-An advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
-The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
-
-The web-app was programmed in `JavaScript` (ECMAScript 2015, i.e., ES6), `HTML5`, `CSS` and `PHP`.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
-This is needed for precisely calculating exact pupil and target locations and sizes.
-Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-These files can either be sent to a server or downloaded to the local device.
-
 # Individual differences
-Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample.
+Our first aim was to assess whether our balloon finding task induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode influences responses.
@@
 ## Results
-(ref:figlab2) **Measuring interindividual variation**. 
+(ref:figlab2) **Measuring inter-individual variation**. 
 (A) Developmental trajectory in continuous hedge version.
@@
 (J) Test-retest reliability in box adult sample.
-Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r*.
-[m: die regressions linie ist ein smoothed mean based on liner model - guck einfach mal ?geom_smooth]
+Regression lines with 95% CI as smoothed mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
 Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
@@
 We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure 2 A and F [m: siehe oben wie man auf die figures verweist]).
+In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
 Most participants in the box version performed above chance level.
 By the end of their sixth year of life, children came close to the adult's proficiency level.
-Most impoertantly, however, we found subtantial interindividual variation across study versions and age groups.
-For example, some three-year-olds were more precise in their responses than some five-year-olds [m: jetzt noch was zu den erwachsenene - sagen ,dass da auch variation ist; weniger als bei den kindern, but still].
-
-As Figure 2 A and F show, our remotely collected child data resembled the data from the kindergarten sample. 
+Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
+For example, some three-year-olds were more precise in their responses than some five-year-olds.
+Even though variation is smaller, we even find inter-individual differences in the adult sample.
+
+As Figure \@ref(fig:fig2)A and F show, our remotely collected child data resembled the data from the kindergarten sample. 
 We found evidence that responses of children participating remotely were slightly more precise.
@@
 
-Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, we the estimates for age of ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were reliably different from zero [m: so würde ich alle estiamtes berichten.
-also sagen ob positive oder negative und ob veschieden von 0 oder nicht].
-In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]).
-Note that the effect of data collection appears to be present, but confidence intervals are wide [m: das präziser - positive effect, but nor reliably different from 0 oder so].
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were negative and reliably different from zero.
+In the box version, the estimate of age ($\beta$ =`r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode  ($\beta$ = `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]) were positive and reliably different from zero.
+Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
 
 ## Discussion
-Our task induced interintidivudal variation in both adults and children.
+Our task induced inter-individual variation in both adults and children.
 With increasing age, participants got more and more precise in locating the target.
@@
 We assessed internal consistency (split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: )https://osf.io/xqm73 (child sample),  https://osf.io/nu62m (adult sample)).
+Data collection and analysis were pre-registered (can be found here: https://osf.io/xqm73 for child sample, and https://osf.io/nu62m adult sample).
 Participants were equally distributed across the two study versions.
@@
 We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
-Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [m: hier noch das paper zitieren].
+Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics].
 We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
@@
 This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen.
-also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum; also maturation ist sehr loaded - einfach domain general cognitive development].
+also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum].
 
@@
 We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
-For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure 2 B, C, G and H.
-Figure 3 compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
+For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G and H.
+Figure \@ref(fig:fig3) compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
 In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
@@
 ```
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure 2 D, E, I and J.[^fn2]
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^fn2]
 
@@
 For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
-This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
+This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
 
@@
 Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
-We compared the models using WAIC (widely applicable information criterion) scores and weights [m: cite MCElreath dafür].
+We compared the models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2020statistical].
 As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
@@
 The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
-For example, for our winning model, we found a peer exposure estimate of [m: hier bitte auch immer beta = notation machen]
+For example, for our winning model, we found a peer exposure estimate of $\beta$ =
 `r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
-with the estimates of age being `r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version `r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
-Nevertheless, a general pattern emerges: exposure to a more vairable social environment positively influenced children's gaze cue understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow [m: na na ..
-ich dachte wir messen gaze cue *understanding*] the agent's gaze.
+with the estimates of age being $\beta$ =`r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being $\beta$ =`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version $\beta$ =`r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
 The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
-
-[m: figure 4 gefällt mir noch nciht so gut - vll kannst du noch point estimates und Cis mit reinmachen.
-so wie bei den gafo-clt merge plots.
-Die sind hier: https://github.com/ccp-eva/vocab/blob/main/analysis/clt_gafo_merge.Rmd, Zeile 114]
 
@@
 ```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/extvali-posteriorsample.png")
+knitr::include_graphics("../figures/extvali_results.png")
 ```

### 2022-04-28 paper/manuscript.tex
new fig4, fix ccAge calculation error, incorporate some of M feedback

@@
 
-\hypertarget{design-of-our-balloon-finding-task}{%
-\section{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}
+\hypertarget{task-design}{%
+\section{Task design}\label{task-design}}
 
@@
 
+\hypertarget{implementation}{%
+\subsection{Implementation}\label{implementation}}
+
+Our balloon finding task is presented as an interactive web app.
+The task is portable across devices and web browsers and does not require any installation.
+An advantage of online testing is that our testing procedure is standardized across participants.
+By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
+The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+
+The web app was programmed in \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS} and \texttt{PHP}.
+For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
+This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
+Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
+This is needed for precisely calculating exact pupil and target locations and sizes.
+Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
+The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+These files can either be sent to a server or downloaded to the local device.
+
 \hypertarget{stimuli}{%
@@
 Our newly implemented task features an online game where children or adults are asked to search for a balloon.
-The events proceed as follows.
+The events proceed as follows (see Figure \ref{fig:fig1}B and C).
 An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
@@
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target's destination: they respond by touching or clicking onto a position on the screen.
+Participants are then asked to locate the target: they respond by touching or clicking on the screen.
 Visual access to the target's true location is manipulated by a hedge.
@@
 Trials differ in the amount of visual access that participants have to the final target position.
-Before the test trials start, we present four training trials during which participants familiarize themselves with selecting positions on the screen.
+Before the test trials start, participants complete four training trials during which they familiarize themselves with clicking the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
-In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location.
-They are then asked to click on the invisible balloon, i.e., the location where they saw the target land.
-In test trials, participants have no visual access to the target flight nor the end location.
+In the second and third training trials, participants have partial access: they witness the target flight but cannot see the target's end location.
+They are then asked to click on the hidden balloon, i.e., the location where they saw the target land.
+In test trials, participants have no visual access to the target flight or the end location.
 Participants are expected to use the agent's gaze as a cue to locate the target.
@@
 The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script).
-After these four training and audio guided trials, participants receive 15 test trials.
-The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.
+After the four training trials, participants receive 15 test trials.
+The complete sequence of four training trials and 15 test trials can be easily completed within 5-10 minutes.
 
@@
 
-We designed two study versions which can be chosen according to the researchers' need.
-The study versions differ in the final hiding place of the target and, consequently, on the outcome measure: there is a continuous hedge version and a discrete box version.
+We designed two study versions which differ in the final hiding place of the target and, consequently, on the outcome measure: a \emph{hedge version} (continuous) and a \emph{box version} (discrete).
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
-In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version).
+In the hedge version, participants have to indicate their estimated target location directly on a hedge.
 Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the discrete study version, the target lands in a box and participants are asked to click on the box that hides the target.
+In the box version, the target lands in a box and participants are asked to click on the box that hides the target.
 Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
 Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
-Note that in the test trials of both study versions, the target flight is covered by a hedge.
+Note that in the test trials of both versions, the target flight is covered by a hedge.
 In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
 In the box version, the hedge shrinks completely.
-The boxes then hide the target's final destination.
+The boxes then hide the target's final destination (see Figure \ref{fig:fig1}B and C).
 
@@
 \caption{\textbf{Study setup}.
-(a) Infrastructure for online testing.
+(A) Infrastructure for online testing.
 (i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: at home, in kindergartens or research institutes.
+Data collection can take place anywhere: online, in kindergartens or research labs.
 (ii) The task is presented as a website that works across devices.
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(b) Continuous hedge version of the balloon finding task.
+(B) Hedge version (continuous) of the balloon finding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
+(C) Box version (discrete) of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
 \end{figure}
@@
 
-\hypertarget{implementation}{%
-\subsection{Implementation}\label{implementation}}
-
-Our balloon finding task is presented as an interactive web-app.
-The task is portable across devices and web browsers and does not require any installation.
-A great advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
-The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
-The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP.
-We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
-This is needed for precisely calculating exact pupil and target locations and sizes.
-Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The GreenSock Animation Platform {[}GSAP; Greensock (2022){]} library was used to animate the movement of single SVG elements.
-We use URL parameters to capture the participant's ID, language and study version.
-The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany.
-Data got automatically collected and safely stored on these in-house servers.
-If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.
-For child samples, we upload safety copies of the already collected responses after the fourth test trial.
-In cases where children want to stop participation earlier, no responses get lost.
-
-\hypertarget{does-the-balloon-finding-task-induce-variation}{%
-\section{Does the balloon finding task induce variation?}\label{does-the-balloon-finding-task-induce-variation}}
-
-Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample.
+\hypertarget{individual-differences}{%
+\section{Individual differences}\label{individual-differences}}
+
+Our first aim was to assess whether our balloon finding task induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode influences responses.
 
-The pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and here: \url{https://osf.io/r3bhn} (adult sample).
+Methods, sample size and analysis were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
 Participants were equally distributed across the two study versions.
@@
 We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
-In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology.
-The in-person child sample consisted of
+In-person testing with children took place in kindergartens in Leipzig, Germany. The in-person child sample consisted of
 120 children, including
@@
 
-For our remote child sample, we recruited families on a voluntary basis via email from our institute's internal database. The remote child sample included 147 children, including
+For our remote child sample, we recruited families via an internal database. The remote child sample included 147 children, including
 45 3-year-olds
@@
 
-In addition, we recruited a remote adult sample by advertising the study on \emph{Prolific}.
+Adults were recruited via \emph{Prolific}.
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
-\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
 
@@
 
-Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.
-
+Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
 Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
@@
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a lognormal distribution.
-For the box version, the model predicted correct responses (0/1) using a Bernoulli distribution with a logit link function.
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
+For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
 We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
@@
 
-\caption{\textbf{Measuring interindividual variation}.
-(a) Developmental trajectory in continuous hedge version.
+\caption{\textbf{Measuring inter-individual variation}.
+(A) Developmental trajectory in continuous hedge version.
 Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
 The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
-(b) Internal consistency (odd-even split) in hedge child sample.
-(c) Internal consistency in hedge adult sample.
-(d) Test-retest reliability in hedge child sample.
-(e) Test-retest reliability in hedge adult sample.
-(f) Developmental trajectory in discrete box version.
+(B) Internal consistency (odd-even split) in hedge child sample.
+(C) Internal consistency in hedge adult sample.
+(D) Test-retest reliability in hedge child sample.
+(E) Test-retest reliability in hedge adult sample.
+(F) Developmental trajectory in discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
 Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
-(g) Internal consistency (odd-even split) in box child sample.
-(h) Internal consistency in box adult sample.
-(i) Test-retest reliability in box child sample.
-(j) Test-retest reliability in box adult sample.
-Regression lines with 95\% CI show product-moment-correlations with \emph{Pearson}'s correlation coefficient \emph{r.}
-Large data points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
-Small data points show the mean performance for each subject.
-Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection.
-Color of data points represent each age group (binned by year).}\label{fig:fig2}
+(G) Internal consistency (odd-even split) in box child sample.
+(H) Internal consistency in box adult sample.
+(I) Test-retest reliability in box child sample.
+(J) Test-retest reliability in box adult sample.
+Regression lines with 95\% CI as smoothed mean based on a linear model, with \emph{Pearson}'s correlation coefficient \emph{r}.
+Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
+Small points show the mean performance for each subject.
+Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection.
+Color of data points denotes age group.}\label{fig:fig2}
 \end{figure}
 
-We captured a developmental trajectory of gaze cue understanding: with increasing age, participants got more and more accurate in locating the target.
-In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F).
+We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
+In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
 Most participants in the box version performed above chance level.
 By the end of their sixth year of life, children came close to the adult's proficiency level.
-We found interindividual variation across study versions and age groups.
-For instance, this can be seen in that some three-year-olds were more precise in their responses than some five-year-olds.
-
-As Figure 2 A and F show, our remotely collected child data resembled the data from the kindergarten sample.
+Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
+For example, some three-year-olds were more precise in their responses than some five-year-olds.
+Even though variation is smaller, we even find inter-individual differences in the adult sample.
+
+As Figure \ref{fig:fig2}A and F show, our remotely collected child data resembled the data from the kindergarten sample.
 We found evidence that responses of children participating remotely were slightly more precise.
@@
 
-Our GLMM analysis corroborated the effects of age and data collection mode that we already identified by visual inspection: in the hedge version, we found an estimate of age of -0.33 (95\% CI {[}-0.42; -0.23{]}) and an estimate of data collection mode of -0.32 (95\% CI {[}-0.50; -0.14{]}).
-In the box version, the estimate of age was 0.64 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode was 1.16 (95\% CI {[}0.72; 1.61{]}).
-Note that the effect of data collection appears to be present, but confidence intervals are wide.
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.32; 95\% CI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CI {[}-0.49; -0.14{]}) were negative and reliably different from zero.
+In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CI {[}0.69; 1.57{]}) were positive and reliably different from zero.
+Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
 
@@
 
-Our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults.
+Our task induced inter-individual variation in both adults and children.
 With increasing age, participants got more and more precise in locating the target.
-We found interindividual variation across all age groups.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
-This underlines how flexibly our new task can be used.
-
-\hypertarget{can-we-capture-variation-reliably}{%
-\section{Can we capture variation reliably?}\label{can-we-capture-variation-reliably}}
-
-As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable (i.e.,
-systematically order individuals in the same way).
-For this aim, we assessed the internal consistency, as calculated by splithalf reliability, and the test-retest reliability.
-The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample).
+This illustrates the flexibility of the task.
+
+\hypertarget{internal-consistency-and-retest-reliability}{%
+\section{Internal consistency and retest reliability}\label{internal-consistency-and-retest-reliability}}
+
+As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+We assessed internal consistency (split-half reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for child sample, and \url{https://osf.io/nu62m} adult sample).
 Participants were equally distributed across the two study versions.
@@
 
-For our child sample, we went to kindergartens in Leipzig and surroundings.
-The child sample consisted of
+Participants were recruited in the same way as in the previous study. The child sample consisted of
 106 children, including
@@
 
-The adult sample was recruited over \emph{Prolific} and consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).
+The adult sample consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).
 
@@
 
-We applied the same procedure as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days.
+We applied the same procedure as in the first study, with the following differences.
+Participants completed the study twice, with a delay of 14 ± 3 days.
 The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
@@
 First, we focused on the internal consistency by calculating splithalf reliability coefficients.
-For each subject, trials were split into odd and even and performance scores per part were correlated against each other using \emph{Pearson} correlation coefficients.
-We took the data of the first test day and defined performance according to study version: in the hedge version, performance referred to the absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the proportion of correct choices.
-As a recent paper by Pronk, Molenaar, Wiers, and Murre (2021) suggested, there are various less well-known split-half methods that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using \emph{Pearson} coefficients.
+For this, we used the data of the first test day.
+Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).
+
 Second, we assessed the test-retest reliability.
-We calculated performance scores (depending on study version as described above) for each individual in each test session and correlated those using \emph{Pearson} correlation coefficients.
-Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach.
+We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
+Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
 We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
@@
 Most importantly, the model allows us to get an age-independent estimate for reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive maturation processes instead of study-specific inter-individual differences.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences {[}m: das noch bisschen konkreter machen.
+also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum{]}.
 
@@
 We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
-
-For the internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure 2 B, C, G and H.
-
-Figure 3 compares splithalf reliability coefficients by splitting and stratification method, following Pronk et al. (2021).
-In the hedge version, the splithalf reliability coefficients ranged from 0.61 to 0.92. In the box version, splithalf reliability coefficients ranged from 0.40 to 0.87.
+For the internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G and H.
+Figure \ref{fig:fig3} compares splithalf reliability coefficients by splitting and stratification method (Pronk et al., 2021).
+In the hedge version, the splithalf reliability coefficients ranged from 0.57 to 0.84. In the box version, splithalf reliability coefficients ranged from 0.49 to 0.76.
 Similarly to the results of Pronk et al.
@@
 
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure 2 D, E, I and J.\footnote{In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
-The performance of the mentioned child lay 3 standard deviations above the mean on both test days.
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
+The performance of the mentioned child was 3 standard deviations above the mean on both test days.
 Including the child yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.87.}
 
-Taking age into account in our GLMM based approach yielded similar results. The age-independent retest reliability estimate in the hedge version amounted to 0.88 (95\% CI {[}0.61;1.00{]}).
-In the box version of the task, the age-independent correlation between participant specific test day estimates was 0.89 (95\% CI {[}0.63;1.00{]}).
-The results suggest that our novel balloon finding task did capture individual differences beyond general cognitive maturation processes.
-This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the driving force acccounting for individual differences.
+The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.90 (95\% CI {[}0.68;1.00{]}).
+In the box version it was 0.92 (95\% CI {[}0.70;1.00{]}).
 
@@
 
-Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
-
-\hypertarget{exploring-the-external-validity-of-our-task}{%
-\section{Exploring the external validity of our task}\label{exploring-the-external-validity-of-our-task}}
-
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings.
+Our results indicated that the measured variation was systematic.
+As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
+For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
+This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
+
+\hypertarget{validity}{%
+\section{Validity}\label{validity}}
+
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment {[}m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden.
+Daher sehen wir das als indikator für validität, wenn wir das auch finden.{]}
 
@@
 For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
-136 children, including
-41 3-year-olds
-(mean = 43.17 months,
-SD = 3.13,
-range = 37
+137 children, including
+42 3-year-olds
+(mean = 43.04 months,
+SD = 3.25,
+range = 36
 - 47,
@@
 
-Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire (print out / online questionnaire).
+Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire.
 We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
@@
 To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
-Across the two study versions, we could consequently model the participant's correct response (0/1) using a Bernoulli distribution with a logit link function.
-For model comparisons, we respectively added the following predictors as fixed effects to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
+Across the two study versions, we could consequently model the participant's correct response (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
+For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
 In addition, we calculated three index scores.
@@
 Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
-We compared the models using WAIC (widely applicable information criterion) scores and weights.
+We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
 As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
@@
 The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
-For example, for our winning model, we found a peer exposure estimate of
-0.18 (95\% CI {[}-0.01; 0.36{]}),
-with the estimates of age being 0.59 (95\% CI {[}0.40; 0.79{]}), data collection mode being 0.93 (95\% CI {[}0.54; 1.34{]}), and study version 1.84 (95\% CI {[}0.14; 3.47{]}).
-Nevertheless, a general direction of effect can be seen: there seems to be small evidence that a social surrounding positively influenced children's gaze cue understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow the agent's gaze.
-The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the more likely children found the target.
+For example, for our winning model, we found a peer exposure estimate of \(\beta\) =
+0.17 (95\% CI {[}-0.03; 0.36{]}),
+with the estimates of age being \(\beta\) =0.57 (95\% CI {[}0.39; 0.77{]}), data collection mode being \(\beta\) =0.96 (95\% CI {[}0.55; 1.36{]}), and study version \(\beta\) =1.81 (95\% CI {[}0.20; 3.50{]}).
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/extvali-posteriorsample}
+{\centering \includegraphics[width=1\linewidth]{../figures/extvali_results}
 
@@
 
-We found small evidence that factors of children's social surrounding influenced their gaze cue understanding.
-Even though the effect sizes are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
+In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables {[}m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen{]}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-greensock2022gsap}{}}%
-Greensock. (2022). \emph{{GSAP} ({GreenSock Animation Platform})}.
+\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
+McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rouder2019psychometrics}{}}%
+Rouder, J.
+N., \& Haaf, J.
+M.
+(2019).
+A psychometrics of individual differences in experimental tasks.
+\emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
+\url{https://doi.org/10.3758/s13423-018-1558-y}
+
 \end{CSLReferences}
@@
 In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the incredible time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
+Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated testquestion by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
+We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
 In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
@@
 WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
+On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
+Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
+On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
 In all cases, however, ELPD difference scores were smaller than their standard errors.
 Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.
+Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis {[}m: naja, ich würde sagen, dass der effekt nicht sonderlich groß ist, aber wen dann kommt er so zustande wie oben erklärt.
+Wir wollen ja weg von effekt da vs.~nciht da{]}.
 

### 2022-04-28 stats/analysis.Rmd
new fig4, fix ccAge calculation error, incorporate some of M feedback

@@
 library(splithalfr) # reliability 
+library(tidybayes) # for stat_halfeye
+library(ggdist)
 
@@
 
-```{r extvali_plot}
-extvaliPostSamples <- bind_rows(
-  posterior_samples(mExtvaliccAge, pars = "b_ccAge") %>% mutate(model = "mExtvaliccAge") %>% rename(estimate = b_ccAge), 
-  posterior_samples(mExtvaliccHours, pars = "b_ccHours") %>% mutate(model = "mExtvaliccHours") %>% rename(estimate = b_ccHours), 
-  posterior_samples(mExtvalihhTotal, pars = "b_hhTotal") %>% mutate(model = "mExtvalihhTotal") %>% rename(estimate = b_hhTotal), 
-  posterior_samples(mExtvalihhSibs, pars = "b_hhSibs") %>% mutate(model = "mExtvalihhSibs") %>% rename(estimate = b_hhSibs),
-  posterior_samples(mExtvalisibsChildAged, pars = "b_sibsChildAged") %>% mutate(model = "mExtvalisibsChildAged") %>% rename(estimate = b_sibsChildAged),
-  posterior_samples(mExtvalisiblingsVarietyScoreP, pars = "b_siblingsVarietyScoreP") %>% mutate(model = "mExtvalisiblingsVarietyScoreP") %>% rename(estimate = b_siblingsVarietyScoreP),
-  posterior_samples(mExtvalisiblingsVarietyScoreW, pars = "b_siblingsVarietyScoreW") %>% mutate(model = "mExtvalisiblingsVarietyScoreW") %>% rename(estimate = b_siblingsVarietyScoreW),
-  posterior_samples(mExtvaliPE, pars = "b_pe") %>% mutate(model = "mExtvaliPE") %>% rename(estimate = b_pe)
-) %>% 
-  mutate(
-    model = factor(model, levels = extvaliModelorder, labels = c("sibling variety score (Cassidy et al., 2005)", "number of children in household aged 1-12", "number of children in household aged 0-18", "null model", "number of household members", "average hours spent in childcare per day", "age of childcare entry", "sibling variety score (Peterson, 2000)", "peer exposure index"))
-  )
-
-write.csv(extvaliPostSamples, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
-saveRDS(extvaliPostSamples, "../saves/extvali-posteriorsamples.rds")
-
-ggplot(extvaliPostSamples, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
-  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
-  stat_density_ridges(
-    geom = "density_ridges_gradient",
-    calc_ecdf = TRUE, 
-    quantiles = c(0.025, 0.975)
-  ) +	
-  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") + 
-  scale_x_continuous(limits = c(-0.25, 0.75)) + 
-  ylab("")
-
-ggsave("../figures/extvali-posteriorsample.png", width = 6, height = 3)
-```
-
 ```{r extvali_save}
@@
 ```
+
+```{r extvali_posteriordraws}
+extvali_draws <- bind_rows(
+  mExtvaliccAge %>% gather_draws(b_ccAge),
+  mExtvaliccHours %>% gather_draws(b_ccHours), 
+  mExtvalihhTotal %>% gather_draws(b_hhTotal), 
+  mExtvalihhSibs %>% gather_draws(b_hhSibs), 
+  mExtvalisibsChildAged %>% gather_draws(b_sibsChildAged), 
+  mExtvalisiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
+  mExtvalisiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
+  mExtvaliPE %>% gather_draws(b_pe)
+  ) %>% 
+  mutate(
+    Predictor = factor(.variable, 
+                       levels = c("b_hhSibs", 
+                                  "b_siblingsVarietyScoreP", 
+                                  "b_sibsChildAged", 
+                                  "b_hhTotal", 
+                                  "b_ccHours", 
+                                  "b_ccAge", 
+                                  "b_siblingsVarietyScoreW", 
+                                  "b_pe"), 
+                       labels = c("Number of children in household aged 0-18", 
+                                  "Sibling variety score (Peterson, 2000)", 
+                                  "Number of children in household aged 1-12", 
+                                  "Number of household members", 
+                                  "Average hours spent in childcare per day", 
+                                  "Age of childcare entry", 
+                                  "Sibling variety score (Cassidy et al., 2005)", 
+                                  "Peer exposure index")
+                       )  
+  )
+
+write.csv(extvali_draws, "../saves/extvali-draws.csv", quote = F, row.names = F)
+saveRDS(extvali_draws, "../saves/extvali-draws.rds")
+```
+
+```{r extvali_plot}
+ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+ tidybayes::stat_halfeye(alpha = .7, .width = c(.95, .80), scale = 3) +
+    labs(x = "Posterior estimate", y = "")+
+  guides(fill = "none")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  scale_fill_manual(values = c("grey","#85AD00")) +
+  xlim(-0.2, 0.6) +
+  theme_minimal()
+
+extvali_draws %>% 
+  filter(
+          Predictor == "Peer exposure index" ||
+          Predictor == "Sibling variety score (Cassidy et al., 2005)" ||
+          Predictor == "Number of children in household aged 0-18" ||
+          Predictor == "Average hours spent in childcare per day", 
+         ) %>% 
+  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+ tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y = "") +
+  guides(fill = "none")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  scale_fill_manual(values = c("grey","#85AD00")) +
+  scale_x_continuous(limits = c(-0.6, 1), breaks = seq(-0.5, 1, 0.25)) + 
+  theme_minimal()
+
+ggsave("../figures/extvali_results.png", width = 10, height = 6, scale = 0.7, bg = "white")
+```

### 2022-04-29 paper/manuscript.Rmd
edit extvali and webcam coding posterior draws

@@
 The graph shows the estimated density curves of a model's predictor coefficient.
-Red tails display the 2.5% and 97.5% quantiles, respectively.
+Only models performing better than our null model are included in the graph.
 
@@
 ### Webcam coding
+(ref:figlab5) **Model comparison for exploratory webcam coding of parental interference**. 
+Factors of parental interference and their influence on the probability of responding correctly.
+The graph shows the estimated density curves of a model's predictor coefficient.
+Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison.
+(A) Analysis on a trial-by-trial level.
+(B) Analysis on a subject level.
+
+```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
+knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
+```
+
 Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
@@
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^fn3]
+
+[^fn3]: Attentive readers might notice that we simplified the structure of random effects.
+Compared to our models in the *Individual differences* and *External Validity* sections, this model does not include the random slope for symmetric target position within participants.
+We decided to do so since we had limited amount of data from few participants.
+
 We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
@@
 Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis [m: naja, ich würde sagen, dass der effekt nicht sonderlich groß ist, aber wen dann kommt er so zustande wie oben erklärt.
-Wir wollen ja weg von effekt da vs.
-nciht da].
+Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
 
@@
 webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
+  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>% 
   mutate_if(is.numeric, round, 2)
@@
 extvali_models <- readRDS(file = "../saves/extvali-results.rds") %>% 
-  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
+  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>% 
   mutate_if(is.numeric, round, 2)
@@
 papaja::apa_table(
-  webcam_models, 
+  extvali_models, 
   caption = "Model comparison for influences of children's social surrounding", 

### 2022-04-29 paper/manuscript.tex
edit extvali and webcam coding posterior draws

@@
 For example, for our winning model, we found a peer exposure estimate of \(\beta\) =
-0.17 (95\% CI {[}-0.03; 0.36{]}),
-with the estimates of age being \(\beta\) =0.57 (95\% CI {[}0.39; 0.77{]}), data collection mode being \(\beta\) =0.96 (95\% CI {[}0.55; 1.36{]}), and study version \(\beta\) =1.81 (95\% CI {[}0.20; 3.50{]}).
+0.16 (95\% CI {[}-0.03; 0.36{]}),
+with the estimates of age being \(\beta\) =0.58 (95\% CI {[}0.39; 0.77{]}), data collection mode being \(\beta\) =0.96 (95\% CI {[}0.56; 1.37{]}), and study version \(\beta\) =1.84 (95\% CI {[}0.26; 3.56{]}).
 Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
@@
 The graph shows the estimated density curves of a model's predictor coefficient.
-Red tails display the 2.5\% and 97.5\% quantiles, respectively.}\label{fig:fig4}
+Only models performing better than our null model are included in the graph.}\label{fig:fig4}
 \end{figure}
@@
 \subsubsection{Webcam coding}\label{webcam-coding}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/supplements_webcamcoding_draws}
+
+}
+
+\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
+Factors of parental interference and their influence on the probability of responding correctly.
+The graph shows the estimated density curves of a model's predictor coefficient.
+Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison.
+(A) Analysis on a trial-by-trial level.
+(B) Analysis on a subject level.}\label{fig:fig5}
+\end{figure}
 
@@
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.\footnote{Attentive readers might notice that we simplified the structure of random effects.
+Compared to our models in the \emph{Individual differences} and \emph{External Validity} sections, this model does not include the random slope for symmetric target position within participants.
+We decided to do so since we had limited amount of data from few participants.}
+
 We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
@@
 Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis {[}m: naja, ich würde sagen, dass der effekt nicht sonderlich groß ist, aber wen dann kommt er so zustande wie oben erklärt.
-Wir wollen ja weg von effekt da vs.~nciht da{]}.
+Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
 
@@
 \toprule
-model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
+Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
 \midrule
-mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
-mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
-mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
-mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
-mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
-mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
-mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
-mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
-mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
-mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
-mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
-mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
+By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
+By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
+By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
+By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
+By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
+By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
+By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
+By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
+By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
+By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
+By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
+By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
 \bottomrule
@@
 \toprule
-model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
+Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
 \midrule
-mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
-mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
-mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
-mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
-mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
-mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
-mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
-mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
-mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
-mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
-mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
-mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
+Average hours spent in childcare per day & 2,540.05 & 0.57 & 0.00 & 0.00\\
+Sibling variety score (Peterson, 2000) & 2,540.60 & 0.28 & -0.28 & 1.06\\
+\# Children in household aged 0-18 & 2,540.95 & 0.15 & -0.45 & 1.12\\
+Peer exposure index & 2,541.06 & 0.00 & -0.50 & 0.92\\
+Sibling variety score (Cassidy et al., 2005) & 2,541.31 & 0.00 & -0.63 & 1.02\\
+\# Household members & 2,542.10 & 0.00 & -1.03 & 0.96\\
+Null model & 2,542.37 & 0.00 & -1.16 & 0.80\\
+Age of childcare entry & 2,542.48 & 0.00 & -1.21 & 1.35\\
+\# Children in household aged 1-12 & 2,542.54 & 0.00 & -1.24 & 0.94\\
 \bottomrule

### 2022-04-29 stats/analysis.Rmd
edit extvali and webcam coding posterior draws

@@
   select(model, waic, value, elpd_diff, se_diff) %>%
-  rename(waic_weight = value) %>% 
+  rename(
+    Predictor = model, 
+    WAIC = waic, 
+    Weight = value, 
+    ELPD = elpd_diff, 
+    SE = se_diff,
+  ) %>% 
   mutate(
-    model = str_remove(model, "mExtvali")
+    Predictor = recode(Predictor, 
+                   "mExtvaliPE" = "Peer exposure index", 
+                   "mExtvalisiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
+                   "mExtvalihhSibs" = "# Children in household aged 0-18", 
+                   "mExtvaliccHours" = "Average hours spent in childcare per day",
+                   "mExtvalinull" = "Null model", 
+                   "mExtvalihhTotal" = "# Household members",
+                   "mExtvaliccAge" = "Age of childcare entry", 
+                   "mExtvalisiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
+                   "mExtvalisibsChildAged" = "# Children in household aged 1-12",
+                   )
   )
@@
                                   "b_pe"), 
-                       labels = c("Number of children in household aged 0-18", 
+                       labels = c("# Children in household aged 0-18", 
                                   "Sibling variety score (Peterson, 2000)", 
-                                  "Number of children in household aged 1-12", 
-                                  "Number of household members", 
+                                  "# Children in household aged 1-12", 
+                                  "# Household members", 
                                   "Average hours spent in childcare per day", 

### 2022-04-29 stats/supplements_webcamcoding.Rmd
edit extvali and webcam coding posterior draws

@@
 library(ggridges)
+library(ggpubr)
+library(tidybayes)
 
@@
 # originally: 
-# brm(correct ~ age + (trial + targetPosition | subjID) + (age | targetPosition)
+# brm(correct ~ age + (symmetricPosition | subjID) + (1 | targetPosition)
 # age + person effect + trial effect
@@
 mPerTrialComparison <- as_tibble(mPerTrialComparison, rownames = "model")
-write.csv(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.csv", quote = F, row.names = F)
-saveRDS(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.rds")
 
 mPerTrialComparisonWeights <- as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic"), rownames = "model")
-write.csv(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.csv", quote = F, row.names = F)
-saveRDS(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.rds")
+```
+
+```{r webcam_perTrial_posteriordraws}
+perTrial_draws <- bind_rows(
+  mPerTrialPI %>% gather_draws(b_pi),
+  mPerTrialRepeatedTestquestion %>% gather_draws(b_repeatedTestquestion), 
+  mPerTrialVerificationChoice %>% gather_draws(b_verificationChoice), 
+  mPerTrialHintsEyes %>% gather_draws(b_hintsEyes), 
+  mPerTrialParentSpeech %>% gather_draws(b_parentSpeech), 
+  ) %>% 
+  mutate(
+    Predictor = factor(.variable, 
+                       levels = c("b_verificationChoice", 
+                                  "b_pi", 
+                                  "b_repeatedTestquestion", 
+                                  "b_parentSpeech", 
+                                  "b_hintsEyes"
+                       ), 
+                       labels = c("# Verification choice", 
+                                  "Parental interference index",
+                                  "# Repeated testquestion", 
+                                  "# Words uttered by caregiver", 
+                                  "# Hints towards eyes"
+                       )
+                )  
+  )
+
+write.csv(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.csv", quote = F, row.names = F)
+saveRDS(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.rds")
 ```
@@
 ```{r webcam_perTrial_plot}
-postSamplesPerTrial <- bind_rows(
-  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
-  posterior_samples(mPerTrialPI, pars = "pi") %>% mutate(model = "mPerTrialPI") %>% rename(estimate = b_pi), 
-  posterior_samples(mPerTrialRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerTrialRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
-  posterior_samples(mPerTrialVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerTrialVerificationChoice") %>% rename(estimate = b_verificationChoice), 
-  posterior_samples(mPerTrialHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerTrialHintsEyes") %>% rename(estimate = b_hintsEyes), 
-  posterior_samples(mPerTrialParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerTrialParentSpeech") %>% rename(estimate = b_parentSpeech), 
-)
+perTrial_plot <- perTrial_draws %>% 
+  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+ tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
+    labs(x = "Posterior estimate", y = "") +
+  guides(fill = "none")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  scale_fill_manual(values = c("grey","#85AD00")) +
+  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 0.5)) +
+  theme_minimal()
 
-postSamplesPerTrial <- postSamplesPerTrial %>% 
-  mutate(
-        model = factor(model, levels = c("mPerTrialParentSpeech", "mPerTrialHintsEyes", "mPerTrialVerificationChoice", "mPerTrialRepeatedTestquestion", "mPerTrialPI")),
-  )
+perTrial_plot
 
-ggplot(postSamplesPerTrial, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
-  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
-  stat_density_ridges(
-    geom = "density_ridges_gradient",
-    calc_ecdf = TRUE, 
-    quantiles = c(0.025, 0.975)
-  ) +	
-  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") +
-  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, by = 0.5))
-
-ggsave("../figures/supplements-webcamcoding-mPerTrialComparison-posteriorsample.png")
+ggsave("../figures/supplements_webcamcoding_perTrial.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```
@@
 
-```{r webcam_perTrial_comparisons}
+```{r webcam_perSubject_comparisons}
 mPerSubjectNull <- add_criterion(mPerSubjectNull, "waic")
@@
 mPerSubjectComparison <- as_tibble(mPerSubjectComparison, rownames = "model")
-write.csv(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.csv", quote = F, row.names = F)
-saveRDS(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.rds")
 
 mPerSubjectComparisonWeights <- as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic"), rownames = "model")
-write.csv(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.csv", quote = F, row.names = F)
-saveRDS(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.rds")
 ```
 
-```{r webcam_perTrial_plot}
-postSamplesPerSubject <- bind_rows(
-  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
-  posterior_samples(mPerSubjectPI, pars = "pi") %>% mutate(model = "mPerSubjectPI") %>% rename(estimate = b_pi), 
-  posterior_samples(mPerSubjectRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerSubjectRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
-  posterior_samples(mPerSubjectVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerSubjectVerificationChoice") %>% rename(estimate = b_verificationChoice), 
-  posterior_samples(mPerSubjectHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerSubjectHintsEyes") %>% rename(estimate = b_hintsEyes), 
-  posterior_samples(mPerSubjectParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerSubjectParentSpeech") %>% rename(estimate = b_parentSpeech), 
+```{r webcam_perSubject_posteriordraws}
+perSubject_draws <- bind_rows(
+  mPerSubjectPI %>% gather_draws(b_pi),
+  mPerSubjectRepeatedTestquestion %>% gather_draws(b_repeatedTestquestion), 
+  mPerSubjectVerificationChoice %>% gather_draws(b_verificationChoice), 
+  mPerSubjectHintsEyes %>% gather_draws(b_hintsEyes), 
+  mPerSubjectParentSpeech %>% gather_draws(b_parentSpeech), 
+  ) %>% 
+  mutate(
+    Predictor = factor(.variable, 
+                       levels = c("b_verificationChoice", 
+                                  "b_pi", 
+                                  "b_repeatedTestquestion", 
+                                  "b_parentSpeech", 
+                                  "b_hintsEyes"
+                       ), 
+                       labels = c("# Verification choice", 
+                                  "Parental interference index",
+                                  "# Repeated testquestion", 
+                                  "# Words uttered by caregiver", 
+                                  "# Hints towards eyes"
+                       )
+                )
   )
 
-postSamplesPerSubject <- postSamplesPerSubject %>% 
-  mutate(
-        model = factor(model, levels = c("mPerSubjectParentSpeech", "mPerSubjectHintsEyes", "mPerSubjectVerificationChoice", "mPerSubjectRepeatedTestquestion", "mPerSubjectPI")),
+write.csv(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.csv", quote = F, row.names = F)
+saveRDS(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.rds")
+```
+
+```{r webcam_perSubject_plot}
+perSubject_plot <- perSubject_draws %>% 
+  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+ tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 1.75) +
+    labs(x = "Posterior estimate", y = "") +
+  guides(fill = "none")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  scale_fill_manual(values = c("grey","#85AD00")) +
+  scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.25)) +
+  theme_minimal()
+
+perSubject_plot
+
+ggsave("../figures/supplements_webcamcoding_perSubject_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
+```
+
+```{r combined_plot}
+ggarrange(perTrial_draws %>% 
+            ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+            tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
+            labs(x = "Posterior estimate", y = "") +
+            guides(fill = "none")+
+            geom_vline(xintercept = 0, linetype = "dashed") +
+            scale_fill_manual(values = c("grey","#85AD00")) +
+            scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 1)) +
+            theme_minimal() + 
+            theme(panel.grid.minor.x = element_blank()),
+
+          ggarrange(
+            perSubject_draws %>% 
+              ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
+              tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 2) +
+              labs(x = "", y = "") +
+              guides(y = "none", fill = "none") +
+              geom_vline(xintercept = 0, linetype = "dashed") +
+              scale_fill_manual(values = c("grey","#85AD00")) +
+              scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.5)) +
+              theme_minimal(), 
+            NULL, 
+            nrow = 2, heights = c(1, 0.0001)
+          ),
+
+          nrow = 1, widths = c(1, 0.75),
+          labels = c("A", "B")
           )
 
-ggplot(postSamplesPerSubject, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
-  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
-  stat_density_ridges(
-    geom = "density_ridges_gradient",
-    calc_ecdf = TRUE, 
-    quantiles = c(0.025, 0.975)
-  ) +	
-  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none")
-
-ggsave("../figures/supplements-webcamcoding-mPerSubjectComparison-posteriorsample.png")
+ggsave("../figures/supplements_webcamcoding_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```
@@
   select(model, waic, value, elpd_diff, se_diff) %>% 
-  rename(waic_weight = value)
+  rename(
+    Predictor = model, 
+    WAIC = waic, 
+    Weight = value, 
+    ELPD = elpd_diff, 
+    SE = se_diff,
+  ) %>% 
+  mutate(
+    Predictor = recode(Predictor, 
+                   "mPerTrialVerificationChoice" = "By trial - # Verification choice", 
+                   "mPerTrialNull" = "By trial - Null model", 
+                   "mPerTrialPI" = "By trial - Parental interference index", 
+                   "mPerTrialRepeatedTestquestion" = "By trial - # Repeated testquestion", 
+                   "mPerTrialParentSpeech" = "By trial - # Words uttered by caregiver", 
+                   "mPerTrialHintsEyes" = "By trial - # Hints eyes", 
+                   "mPerSubjectRepeatedTestquestion" = "By subject - # Repeated testquestion", 
+                   "mPerSubjectPI" = "By subject - Parental interference index", 
+                   "mPerSubjectNull" = "By subject - Null model", 
+                   "mPerSubjectVerificationChoice" = "By subject - # Verification choice", 
+                   "mPerSubjectParentSpeech" = "By subject - # Words uttered by caregiver", 
+                   "mPerSubjectHintsEyes" = "By subject - # Hints eyes"
+                   )
+  )
+
+overall_results
 

### 2022-05-05 paper/manuscript.Rmd
starting the intro...

@@
 # Introduction 
-Idea for an opener :)
-
 Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-For example ...
+
+## Why is social cognition important?
+
+For example, a booming research area of comparative and developmental psychologists and philosophers has been *Social Cognition* and *Theory of Mind*.
+Although definitions vary, these umbrella terms are commonly used to describe the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences (TODO: cite).
+Children spend a large amount of time interacting with and learning from others in social contexts.
+A main research interest has, therefore, been when social-cognitive abilities emerge in children.
+Here, studies often tracked change on a group level and assessed at which average age children succeed in a task that relies on a given social-cognitive ability.
+
+## What methods are currently been used? What are common issues?
+In recent years, there has been a focus on replicability issues.
+These are especially prominent in developmental psychology since recruiting children and keeping them attentive and in a good mood requires a lot of effort and time.
+Often, this leads to small sample sizes or low numbers of trials per subject.
+Experimental paradigms often focus on dichotomous outcome variables and, therefore, high chance levels.
+In short, tasks were simply not designed to measure children’s abilities on an individual level. 
+This has profound implications on what these studies can show: poor reliability of measures on an individual level may conceal relations between different aspects of cognition and also obscure developmental change.
+We argue that a systematic individual differences perspective on social-cognitive development is needed.
+
+## An individual difference perspective
+
+However, if we are interested in the co-development of social-cognitive abilities and a child’s pace of mastering developmental milestones, we need to focus on individual differences in social cognition.
+To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).
+
+Few studies using traditional measures (e.g., false belief change-of-location tasks) address these issues.
+A recent paper by @hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies.
+The authors could show that this often does not emerge due to high measurement variance but rather low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+In a similar vein, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a certain cognitive test is suited to draw inferences about individuals.
+
+## Aim of the current project
+We want to make individual differences measurable, in a systematic and reliable way. One of our main goals is, therefore, to create a task that induces variation between children. 
+For getting precise person specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
+To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
+To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small.
+A standardized, easily accessible test procedure helps us to enable data collection at scale.
+Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's surrounding.
+
+---
 
@@
 - goal of the current project: standardized, easy to use continuous methods
-
-"Recently, it was suggested that a range of cognitive tasks may reliably measure group differences but not individual differences (Hedge et al., 2018).
-As cognitive tests are commonly used to make inferences about individuals, it seems a worthwhile pursuit to improve the reliability with which individual differences are assessed using these tests.
-To judge the success of such pursuits, accurate estimates of reliability are required." (Pronk, Molenaar, Wiers and Murre, 2021, p.
-1)
-"Firstly, reliability is not only a function of task and population sample but also of scoring algorithms." (Pronk, Molenaar, Wiers and Murre, 2021, p. 9)
-"Hence, we conclude that for the datasets included in our reanalysis, cognitive tasks may well have been able to measure individual differences, but that these differences may be relatively unstable over time (Kopp et al., 2021).
-In practice, this may make cognitive tasks suitable for cross-sectional research of individual differences, but not for longitudinal research." (Pronk, Molenaar, Wiers and Murre, 2021, p.
-10)
+- soc cog, gaze cue understanding small def (longer one dev paper)
 
@@
 # Task design
-- face value of task (or maybe in intro already?)
 
@@
 By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
-Most importantly, the model allows us to get an age-independent estimate for reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen.
-also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum].
+Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person specific estimates.
+Most importantly, the model includes age as a fixed effect.
+The correlation between the two person specific estimates is consequently the age-independent estimate for test-retest reliability.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
+A high correlation between our participant specific model estimates would speak for a high association between test days.
 

### 2022-05-13 paper/manuscript.Rmd
work on intro

@@
 Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-
-## Why is social cognition important?
-
-For example, a booming research area of comparative and developmental psychologists and philosophers has been *Social Cognition* and *Theory of Mind*.
-Although definitions vary, these umbrella terms are commonly used to describe the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences (TODO: cite).
-Children spend a large amount of time interacting with and learning from others in social contexts.
-A main research interest has, therefore, been when social-cognitive abilities emerge in children.
-Here, studies often tracked change on a group level and assessed at which average age children succeed in a task that relies on a given social-cognitive ability.
-
-## What methods are currently been used? What are common issues?
-In recent years, there has been a focus on replicability issues.
-These are especially prominent in developmental psychology since recruiting children and keeping them attentive and in a good mood requires a lot of effort and time.
-Often, this leads to small sample sizes or low numbers of trials per subject.
-Experimental paradigms often focus on dichotomous outcome variables and, therefore, high chance levels.
-In short, tasks were simply not designed to measure children’s abilities on an individual level. 
-This has profound implications on what these studies can show: poor reliability of measures on an individual level may conceal relations between different aspects of cognition and also obscure developmental change.
+Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities.
+Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.
+
+Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.
+
+With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability.
+However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.
+
+If we want to answer questions about the co-development of social-cognitive abilities and the individual’s pace of mastering developmental milestones, we need to take variation between children seriously – both methodologically and theoretically.
 We argue that a systematic individual differences perspective on social-cognitive development is needed.
 
-## An individual difference perspective
-
-However, if we are interested in the co-development of social-cognitive abilities and a child’s pace of mastering developmental milestones, we need to focus on individual differences in social cognition.
 To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).
 
-Few studies using traditional measures (e.g., false belief change-of-location tasks) address these issues.
 A recent paper by @hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies.
@@
 
-## Aim of the current project
-We want to make individual differences measurable, in a systematic and reliable way. One of our main goals is, therefore, to create a task that induces variation between children. 
-For getting precise person specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
+From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts.
+For example, @sodian2016understanding studied the relation between several social cognition measures.
+Against expectation, they could not find correlations between some theoretically connected constructs (e.g.
+implicit false belief  and moral false belief understanding).
+Interestingly, nearly all measured variables were associated with their verbal IQ test.
+This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed.
+Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.
+
+Our aim is, therefore, to make individual differences measurable in a systematic and reliable way.
+For getting precise person-specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
+One of our main goals is to create a task that induces variation between children.
 To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
+
 To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small.
+Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
 A standardized, easily accessible test procedure helps us to enable data collection at scale.
+
 Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's surrounding.
+Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.
+
+In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent.
+By acting as a 'front end ability' [@brooks2005development, p.
+535], following an agent's gaze provides insights into their intentions, thoughts, and feelings.
+In our definition, gaze cue understanding goes one step further by including the *acting* on the gaze-cued location.
+
+In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on.
+In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.
+
+By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., @brooks2005development).
+It is, however, unclear when and how children start to use these cues to guide their own active behavior.
 
@@
 
+---
+
 Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1–13. https://doi.org/10.1038/s44159-022-00037-z:
-"The way humans view agents, be it others or themselves, differs radically from the way humans view the rest of the world.
-This difference is because agents feel, perceive and think.
-Agents see the world from their own subjective perspective and they rationally plan, form intentions and act accordingly.
-This way of seeing others as rational subjects with individual perspectives on the world is termed theory of mind (ToM)." (p.
-1)
+
 "ToM also has specific real-life consequences.
@@
 (J) Test-retest reliability in box adult sample.
-Regression lines with 95% CI as smoothed mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
+Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
 Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
@@
 Our task induced inter-individual variation in both adults and children.
-With increasing age, participants got more and more precise in locating the target.
+We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
+The five-year-olds reached a proficiency level close to the adults' level.
+For neither study version nor age group did we find any floor or ceiling effects.
+The presentation as a tablet game kept children interest and motivated throughout the 15 test trials.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
-Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person specific estimates.
+Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates.
 Most importantly, the model includes age as a fixed effect.
-The correlation between the two person specific estimates is consequently the age-independent estimate for test-retest reliability.
+The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
 This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
@@
 ```{r webcam_table, results = "asis"}
-webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>% 
-  mutate_if(is.numeric, round, 2)
-
-papaja::apa_table(
-  webcam_models, 
-  caption = "Model comparison for exploratory webcam coding of parental interference", 
-  note = "All models included random intercepts for participant and target position.", 
-  escape = T
-)
+# webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
+#   mutate(across(c(WAIC, SE_WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>% 
+#   mutate_if(is.numeric, round, 2)
+#     
+# papaja::apa_table(
+#   webcam_models, 
+#   caption = "Model comparison for exploratory webcam coding of parental interference", 
+#   note = "All models included random intercepts for participant and target position.", 
+#   escape = T
+# )
 ```
@@
 extvali_models <- readRDS(file = "../saves/extvali-results.rds") %>% 
-  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>% 
+  mutate(across(c(WAIC, SE_WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>% 
   mutate_if(is.numeric, round, 2)

### 2022-05-13 paper/manuscript.tex
work on intro

@@
 
-Idea for an opener :)
-
 Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-For example \ldots{}
+Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities.
+Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.
+
+Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.
+
+With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability.
+However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.
+
+If we want to answer questions about the co-development of social-cognitive abilities and the individual's pace of mastering developmental milestones, we need to take variation between children seriously -- both methodologically and theoretically.
+We argue that a systematic individual differences perspective on social-cognitive development is needed.
+
+To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).
+
+A recent paper by Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
+The authors could show that this often does not emerge due to high measurement variance but rather low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+In a similar vein, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a certain cognitive test is suited to draw inferences about individuals.
+
+From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts.
+For example, Sodian et al.
+(2016) studied the relation between several social cognition measures.
+Against expectation, they could not find correlations between some theoretically connected constructs (e.g.~implicit false belief and moral false belief understanding).
+Interestingly, nearly all measured variables were associated with their verbal IQ test.
+This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed.
+Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.
+
+Our aim is, therefore, to make individual differences measurable in a systematic and reliable way.
+For getting precise person-specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
+One of our main goals is to create a task that induces variation between children.
+To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
+
+To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small.
+Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
+A standardized, easily accessible test procedure helps us to enable data collection at scale.
+
+Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.
+
+In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent.
+By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p.
+535), following an agent's gaze provides insights into their intentions, thoughts, and feelings.
+In our definition, gaze cue understanding goes one step further by including the \emph{acting} on the gaze-cued location.
+
+In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on.
+In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.
+
+By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., Brooks and Meltzoff (2005)).
+It is, however, unclear when and how children start to use these cues to guide their own active behavior.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
   goal of the current project: standardized, easy to use continuous methods
+\item
+  soc cog, gaze cue understanding small def (longer one dev paper)
 \end{itemize}
 
-``Recently, it was suggested that a range of cognitive tasks may reliably measure group differences but not individual differences (Hedge et al., 2018).
-As cognitive tests are commonly used to make inferences about individuals, it seems a worthwhile pursuit to improve the reliability with which individual differences are assessed using these tests.
-To judge the success of such pursuits, accurate estimates of reliability are required.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~1)
-``Firstly, reliability is not only a function of task and population sample but also of scoring algorithms.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~9)
-``Hence, we conclude that for the datasets included in our reanalysis, cognitive tasks may well have been able to measure individual differences, but that these differences may be relatively unstable over time (Kopp et al., 2021).
-In practice, this may make cognitive tasks suitable for cross-sectional research of individual differences, but not for longitudinal research.'' (Pronk, Molenaar, Wiers and Murre, 2021, p.~10)
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
 Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}:
-``The way humans view agents, be it others or themselves, differs radically from the way humans view the rest of the world.
-This difference is because agents feel, perceive and think.
-Agents see the world from their own subjective perspective and they rationally plan, form intentions and act accordingly.
-This way of seeing others as rational subjects with individual perspectives on the world is termed theory of mind (ToM).'' (p.~1)
+
 ``ToM also has specific real-life consequences.
@@
 \section{Task design}\label{task-design}}
-
-\begin{itemize}
-\tightlist
-\item
-  face value of task (or maybe in intro already?)
-\end{itemize}
 
@@
 All test trials without voice over description were included in our analyses.
-We ran all analyses in R version 4.1.3 (2022-03-10) (R Core Team, 2022).
+We ran all analyses in R version 4.2.0 (2022-04-22) (R Core Team, 2022).
 Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
@@
 (J) Test-retest reliability in box adult sample.
-Regression lines with 95\% CI as smoothed mean based on a linear model, with \emph{Pearson}'s correlation coefficient \emph{r}.
+Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
 Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+Pronk et al.
+(2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
-Most importantly, the model allows us to get an age-independent estimate for reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences {[}m: das noch bisschen konkreter machen.
-also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum{]}.
+Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates.
+Most importantly, the model includes age as a fixed effect.
+The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
+This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
+A high correlation between our participant specific model estimates would speak for a high association between test days.
 
@@
 For example, for our winning model, we found a peer exposure estimate of \(\beta\) =
-0.16 (95\% CI {[}-0.03; 0.36{]}),
-with the estimates of age being \(\beta\) =0.58 (95\% CI {[}0.39; 0.77{]}), data collection mode being \(\beta\) =0.96 (95\% CI {[}0.56; 1.37{]}), and study version \(\beta\) =1.84 (95\% CI {[}0.26; 3.56{]}).
+0.17 (95\% CI {[}-0.03; 0.36{]}),
+with the estimates of age being \(\beta\) =0.57 (95\% CI {[}0.38; 0.77{]}), data collection mode being \(\beta\) =0.95 (95\% CI {[}0.56; 1.35{]}), and study version \(\beta\) =1.87 (95\% CI {[}0.25; 3.59{]}).
 Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
+Brooks, R., \& Meltzoff, A.
+N.
+(2005).
+The development of gaze following and its relation to language.
+\emph{Developmental Science}, \emph{8}(6), 535--543.
+\url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
@@
 Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hedge2018reliability}{}}%
+Hedge, C., Powell, G., \& Sumner, P.
+(2018).
+The reliability paradox: {Why} robust cognitive tasks do not produce reliable individual differences.
+\emph{Behavior Research Methods}, \emph{50}(3), 1166--1186.
+\url{https://doi.org/10.3758/s13428-017-0935-1}
 
@@
 \url{https://doi.org/10.3758/s13423-018-1558-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
+Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A.
+(2016).
+Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}.
+\emph{Child Development}, \emph{87}(4), 1221--1232.
+\url{https://doi.org/10.1111/cdev.12533}
 
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
-
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
-\midrule
-By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
-By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
-By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
-By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
-By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
-By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
-By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
-By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
-By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
-By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
-By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
-By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \hypertarget{appendix-to-external-validity-section}{%
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllll}
 \toprule
-Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
+Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{SE\_WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD\_DIFF} & \multicolumn{1}{c}{SE\_ELPD\_DIFF}\\
 \midrule
-Average hours spent in childcare per day & 2,540.05 & 0.57 & 0.00 & 0.00\\
-Sibling variety score (Peterson, 2000) & 2,540.60 & 0.28 & -0.28 & 1.06\\
-\# Children in household aged 0-18 & 2,540.95 & 0.15 & -0.45 & 1.12\\
-Peer exposure index & 2,541.06 & 0.00 & -0.50 & 0.92\\
-Sibling variety score (Cassidy et al., 2005) & 2,541.31 & 0.00 & -0.63 & 1.02\\
-\# Household members & 2,542.10 & 0.00 & -1.03 & 0.96\\
-Null model & 2,542.37 & 0.00 & -1.16 & 0.80\\
-Age of childcare entry & 2,542.48 & 0.00 & -1.21 & 1.35\\
-\# Children in household aged 1-12 & 2,542.54 & 0.00 & -1.24 & 0.94\\
+Average hours spent in childcare per day & 2,540.39 & 52.23 & 0.54 & 0.00 & 0.00\\
+Peer exposure index & 2,541.00 & 52.22 & 0.28 & -0.30 & 0.92\\
+\# Children in household aged 0-18 & 2,541.65 & 52.30 & 0.02 & -0.63 & 1.09\\
+Sibling variety score (Cassidy et al., 2005) & 2,541.76 & 52.33 & 0.01 & -0.68 & 1.05\\
+Sibling variety score (Peterson, 2000) & 2,541.80 & 52.38 & 0.02 & -0.71 & 1.10\\
+Age of childcare entry & 2,542.19 & 52.38 & 0.12 & -0.90 & 1.32\\
+\# Children in household aged 1-12 & 2,542.26 & 52.34 & 0.00 & -0.94 & 0.92\\
+Null model & 2,542.58 & 52.26 & 0.00 & -1.09 & 0.79\\
+\# Household members & 2,543.46 & 52.36 & 0.00 & -1.54 & 0.97\\
 \bottomrule

### 2022-05-20 paper/manuscript.Rmd
minor editing in intro & vali section

@@
 
+Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+
 # Introduction 
-Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities.
-Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.
-
-Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.
-
-With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability.
-However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.
-
-If we want to answer questions about the co-development of social-cognitive abilities and the individual’s pace of mastering developmental milestones, we need to take variation between children seriously – both methodologically and theoretically.
-We argue that a systematic individual differences perspective on social-cognitive development is needed.
-
-To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).
+Social cognition – representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior – is among the best-studied phenomena in developmental research.
+
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.
+
+But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
+
+Researchers are interested in questions concerning individual differences in the social cognition domain [@hughes2015individual].
+Previous studies focused, for example, on the association of stereotypes and theory of mind [@rizzo2018theory], mental state talk and false belief understanding [@hughes2011individual], attachment quality and gaze following [@astor2020social], language and gaze following [@okumura2017individual], emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], and the interplay of physical and social cognition [@herrmann2010structure].
+Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].
+
+This is due to the fact that many developmental psychology studies track change at an (age-) group level. 
+Traditional measures of social cognition are not designed to capture variation between children: 
+they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties. 
+This has profound implications for what these studies can show.
+Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+
+To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.
+
+We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).
 
@@
 
-From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts.
-For example, @sodian2016understanding studied the relation between several social cognition measures.
-Against expectation, they could not find correlations between some theoretically connected constructs (e.g.
-implicit false belief  and moral false belief understanding).
-Interestingly, nearly all measured variables were associated with their verbal IQ test.
-This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed.
-Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.
+[TODO: check Manuels references]
+
+However, we rarely find studies addressing these issues. 
+Methods, that have currently been used, are...
+One of the most commonly applied measures in social cognition research is the Sally-Anne task. [TODO: fill in FB studies]
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would ...
+With four to five years of age, most children pass the task.
+From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task.
+However, no individual differences can be visible, especially when applying only one trial per child.
 
@@
 
-To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small.
+To estimate the effect of inter-individual differences, we need a large sample size since some of the effects that we are looking for might be small.
 Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
@@
 Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.
-
-In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent.
-By acting as a 'front end ability' [@brooks2005development, p.
-535], following an agent's gaze provides insights into their intentions, thoughts, and feelings.
+Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.
+
+In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively [TODO: add references].
+By acting as a 'front end ability' [@brooks2005development, p. 535], following an agent's gaze provides insights into their intentions, thoughts, and feelings. 
 In our definition, gaze cue understanding goes one step further by including the *acting* on the gaze-cued location.
-
-In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on.
-In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.
-
-By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., @brooks2005development).
-It is, however, unclear when and how children start to use these cues to guide their own active behavior.
 
@@
 
-Adults were recruited via *Prolific*.
+Adults were recruited via *Prolific* [@palan2018prolific].
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 # Validity
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment [m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden.
-Daher sehen wir das als indikator für validität, wenn wir das auch finden.]
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment.
+Previous studies found associations between social cognition measures and various environmental factors [@devine2018family; @hughes2004links], including family background and education [@cutting1999theory; bulgarelli2016social], number and age of siblings and family constellation [@zhang2021worse, @cassidy2005theory; @perner1994theory; @peterson2000kindred], interaction with siblings [@dunn1991young], and centre-based childcare [@bulgarelli2016social].
+It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
+Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
 
@@
 ## Discussion
-In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding.
-Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables [m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen].
+We found that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
+Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
+Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.
 

### 2022-05-20 paper/manuscript.tex
minor editing in intro & vali section

@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 
+Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+
 \hypertarget{introduction}{%
@@
 
-Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities.
-Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.
-
-Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.
-
-With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability.
-However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.
-
-If we want to answer questions about the co-development of social-cognitive abilities and the individual's pace of mastering developmental milestones, we need to take variation between children seriously -- both methodologically and theoretically.
-We argue that a systematic individual differences perspective on social-cognitive development is needed.
-
-To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).
+Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the best-studied phenomena in developmental research.
+
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.
+
+But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
+
+Researchers are interested in questions concerning individual differences in the social cognition domain (Hughes \& Devine, 2015).
+Previous studies focused, for example, on the association of stereotypes and theory of mind (Rizzo \& Killen, 2018), mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011), attachment quality and gaze following (Astor et al., 2020), language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017), emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991), and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
+Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd, Donnelly, \& Christiansen, 2018; Mundy et al., 2007 May-Jun; Underwood, 1975).
+
+This is due to the fact that many developmental psychology studies track change at an (age-) group level.
+Traditional measures of social cognition are not designed to capture variation between children:
+they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties.
+This has profound implications for what these studies can show.
+Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+
+To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.
+
+We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).
 
@@
 
-From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts.
-For example, Sodian et al.
-(2016) studied the relation between several social cognition measures.
-Against expectation, they could not find correlations between some theoretically connected constructs (e.g.~implicit false belief and moral false belief understanding).
-Interestingly, nearly all measured variables were associated with their verbal IQ test.
-This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed.
-Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.
+{[}TODO: check Manuels references{]}
+
+However, we rarely find studies addressing these issues.
+Methods, that have currently been used, are\ldots{}
+One of the most commonly applied measures in social cognition research is the Sally-Anne task. {[}TODO: fill in FB studies{]}
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would \ldots{}
+With four to five years of age, most children pass the task.
+From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task.
+However, no individual differences can be visible, especially when applying only one trial per child.
 
@@
 Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.
-
-In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent.
-By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p.
-535), following an agent's gaze provides insights into their intentions, thoughts, and feelings.
+Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.
+
+In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively {[}TODO: add references{]}.
+By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535), following an agent's gaze provides insights into their intentions, thoughts, and feelings.
 In our definition, gaze cue understanding goes one step further by including the \emph{acting} on the gaze-cued location.
-
-In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on.
-In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.
-
-By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., Brooks and Meltzoff (2005)).
-It is, however, unclear when and how children start to use these cues to guide their own active behavior.
 
@@
 
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment {[}m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden.
-Daher sehen wir das als indikator für validität, wenn wir das auch finden.{]}
+Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment.
+Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016).
+It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
+Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the validity of our measure.
 
@@
 First, we calculated a sibling variety score according to Peterson (2000).
-Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements).
+Second, we implemented the modified version of Cassidy et al.
+(2005) (for more details, see Supplements).
 Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
@@
 
-In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding.
-Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables {[}m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen{]}.
+We found that factors of children's social surrounding influenced their gaze cue understanding.
+Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
+Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
+Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
+Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., \ldots{} Gredebäck, G.
+(2020).
+Social and emotional contexts predict the development of gaze following in early infancy.
+\emph{Royal Society Open Science}, \emph{7}(9), 201178.
+\url{https://doi.org/10.1098/rsos.201178}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bulgarelli2016social}{}}%
+Bulgarelli, D., \& Molina, P.
+(2016).
+Social {Cognition} in {Preschoolers}: {Effects} of {Early Experience} and {Individual Differences}.
+\emph{Frontiers in Psychology}, \emph{7}.
+\url{https://doi.org/10.3389/fpsyg.2016.01762}
+
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
@@
 Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cutting1999theory}{}}%
+Cutting, A.
+L., \& Dunn, J.
+(1999).
+Theory of {Mind}, {Emotion Understanding}, {Language}, and {Family Background}: {Individual Differences} and {Interrelations}.
+\emph{Child Development}, \emph{70}(4), 853--865.
+\url{https://doi.org/10.1111/1467-8624.00061}
+
+\leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
+Devine, R.
+T., \& Hughes, C.
+(2018).
+Family {Correlates} of {False Belief Understanding} in {Early Childhood}: {A Meta-Analysis}.
+\emph{Child Development}, \emph{89}(3), 971--987.
+\url{https://doi.org/10.1111/cdev.12682}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunn1991young}{}}%
+Dunn, J., Brown, J., Slomkowski, C., Tesla, C., \& Youngblade, L.
+(1991).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/1786720}{Young children's understanding of other people's feelings and beliefs: Individual differences and their antecedents}.
+\emph{Child Development}, \emph{62}(6), 1352--1366.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-herrmann2010structure}{}}%
+Herrmann, E., Hernández-Lloreda, M.
+V., Call, J., Hare, B., \& Tomasello, M.
+(2010).
+The {Structure} of {Individual Differences} in the {Cognitive Abilities} of {Children} and {Chimpanzees}.
+\emph{Psychological Science}, \emph{21}(1), 102--110.
+\url{https://doi.org/10.1177/0956797609356511}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hughes2015individual}{}}%
+Hughes, C., \& Devine, R.
+T.
+(2015).
+Individual {Differences} in {Theory} of {Mind From Preschool} to {Adolescence}: {Achievements} and {Directions}.
+\emph{Child Development Perspectives}, \emph{9}(3), 149--153.
+\url{https://doi.org/10.1111/cdep.12124}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hughes2011individual}{}}%
+Hughes, C., Ensor, R., \& Marks, A.
+(2011).
+Individual differences in false belief understanding are stable from 3 to 6 years of age and predict children's mental state talk with school friends.
+\emph{Journal of Experimental Child Psychology}, \emph{108}(1), 96--112.
+\url{https://doi.org/10.1016/j.jecp.2010.07.012}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
+Kidd, E., Donnelly, S., \& Christiansen, M.
+H.
+(2018).
+Individual {Differences} in {Language Acquisition} and {Processing}.
+\emph{Trends in Cognitive Sciences}, \emph{22}(2), 154--169.
+\url{https://doi.org/10.1016/j.tics.2017.11.006}
+
 \leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
 McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mundy2007individual}{}}%
+Mundy, P., Block, J., Delgado, C., Pomares, Y., Van Hecke, A.
+V., \& Parlade, M.
+V.
+(2007 May-Jun).
+Individual differences and the development of joint attention in infancy.
+\emph{Child Development}, \emph{78}(3), 938--954.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01042.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-okumura2017individual}{}}%
+Okumura, Y., Kanakogi, Y., Kobayashi, T., \& Itakura, S.
+(2017).
+Individual differences in object-processing explain the relationship between early gaze-following and later language development.
+\emph{Cognition}, \emph{166}, 418--424.
+\url{https://doi.org/10.1016/j.cognition.2017.06.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
+Perner, J., Ruffman, T., \& Leekam, S.
+R.
+(1994).
+Theory of {Mind Is Contagious}: {You Catch It} from {Your Sibs}.
+\emph{Child Development}, \emph{65}(4), 1228--1238.
+\url{https://doi.org/10.2307/1131316}
 
@@
 R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rizzo2018theory}{}}%
+Rizzo, M.
+T., \& Killen, M.
+(2018).
+Theory of mind is related to children's resource allocations in gender stereotypic contexts.
+\emph{Developmental Psychology}, \emph{54}(3), 510.
+\url{https://doi.org/10.1037/dev0000439}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
-Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A.
-(2016).
-Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}.
-\emph{Child Development}, \emph{87}(4), 1221--1232.
-\url{https://doi.org/10.1111/cdev.12533}
+\leavevmode\vadjust pre{\hypertarget{ref-underwood1975individual}{}}%
+Underwood, B. J. (1975). Individual differences as a crucible in theory construction. \emph{American Psychologist}, \emph{30}(2), 128--134. \url{https://doi.org/10.1037/h0076759}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhang2021worse}{}}%
+Zhang, Z., Yu, H., Long, M., \& Li, H.
+(2021).
+Worse {Theory} of {Mind} in {Only-Children Compared} to {Children With Siblings} and {Its Intervention}.
+\emph{Frontiers in Psychology}, \emph{12}, 5073.
+\url{https://doi.org/10.3389/fpsyg.2021.754168}
 

### 2022-05-20 stats/analysis.Rmd
change naming of model comparison tables

@@
   left_join(mExtvaliComparisonWeights) %>%
-  select(model, waic, value, elpd_diff, se_diff) %>%
+  select(model, waic, se_waic, value, elpd_diff, se_diff) %>%
   rename(
@@
     WAIC = waic, 
+    SE_WAIC = se_waic,
     Weight = value, 
-    ELPD = elpd_diff, 
-    SE = se_diff,
+    ELPD_DIFF = elpd_diff, 
+    SE_ELPD_DIFF = se_diff,
   ) %>% 
@@
 ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
- tidybayes::stat_halfeye(alpha = .7, .width = c(.95, .80), scale = 3) +
+ tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 3) +
     labs(x = "Posterior estimate", y = "")+
@@
   theme_minimal()
+
+ggsave("../figures/extvali_results_all.png", width = 10, height = 6, scale = 0.7, bg = "white")
 

### 2022-05-20 stats/supplements_webcamcoding.Rmd
change naming of model comparison tables

@@
   left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
-  select(model, waic, value, elpd_diff, se_diff) %>% 
+  select(model, waic, se_waic, value, elpd_diff, se_diff) %>% 
   rename(

### 2022-05-20 paper/manuscript.Rmd
first draft intro

@@
 
-Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-
 # Introduction 
+<!-- ## What is Social Cognition, and why do we care? -->
 Social cognition – representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior – is among the best-studied phenomena in developmental research.
-
-In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.
-
-But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
-
-Researchers are interested in questions concerning individual differences in the social cognition domain [@hughes2015individual].
-Previous studies focused, for example, on the association of stereotypes and theory of mind [@rizzo2018theory], mental state talk and false belief understanding [@hughes2011individual], attachment quality and gaze following [@astor2020social], language and gaze following [@okumura2017individual], emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], and the interplay of physical and social cognition [@herrmann2010structure].
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development [@gopnik1991young; @wellman2001metaanalysisa; @wellman2004scalinga; @peterson2012mind; @rakoczy2022foundations].
+
+<!-- ## How has it been measured traditionally? -->
+One of the most commonly applied, prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does].
+Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
+A doll called Sally puts her marble into a basket.
+After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
+Participants then get asked where Sally will look for her marble once she returns.
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket.
+Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysisa].
+Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf.
+@mayer2015weird].
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p.
+317).
+Therefore, the focus has been to track change at an (age-) group level – within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+
+<!-- ## Why care about individual differences? -->
+Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret it as error variance, therefore neglecting and trivializing individual differences [@kidd2018individual].
+Consequently, little consensus has been reached on the interrelation or independence of social-cognitive abilities [termed ‘structure of social cognition’ by @happe2017structure].
+
+However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure].
+For example, it could be used to provide evidence for accounts on *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
+Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
+For this endeavor, we need to take individual differences seriously – both theoretically and methodologically.
+
+<!-- ## Existing research tapping into individual differences -->
+Some studies have already examined individual differences in social cognition [@hughes2015individual; @slaughter2015theorya].
+Previous studies focused, for example, on the association of mental state talk and false belief understanding [@hughes2011individual], emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], stereotypes and theory of mind [@rizzo2018theory], prosociality and theory of mind [for a review see @imuta2016theory; @walker2005gender], executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], parenting practices and theory of mind [for a review see @pavarini2013parental], agency and moral cognition [@sodian2016understanding], attachment quality and gaze following [@astor2020social], language and gaze following [@okumura2017individual], and the interplay of physical and social cognition [@herrmann2010structure].
 Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].
 
-This is due to the fact that many developmental psychology studies track change at an (age-) group level. 
-Traditional measures of social cognition are not designed to capture variation between children: 
-they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties. 
+<!-- ## Methodological limitations -->
+Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related [e.g., @sodian2016understanding].
+This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+@hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies.
+The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or show poor test-retest reliability [@mayes1996testretest].
+
+Even studies focusing on individual differences often use behavioral forced-choice paradigms [e.g., carlson2004individual; @walker2005gender].
+Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual].
+This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations].
 This has profound implications for what these studies can show.
@@
 
-To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.
-
-We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).
-
-A recent paper by @hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies.
-The authors could show that this often does not emerge due to high measurement variance but rather low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
-In a similar vein, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a certain cognitive test is suited to draw inferences about individuals.
-
-[TODO: check Manuels references]
-
-However, we rarely find studies addressing these issues. 
-Methods, that have currently been used, are...
-One of the most commonly applied measures in social cognition research is the Sally-Anne task. [TODO: fill in FB studies]
-The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would ...
-With four to five years of age, most children pass the task.
-From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
-With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task.
-However, no individual differences can be visible, especially when applying only one trial per child.
-
+<!-- ## A wish list for new social-cognitive tasks -->
+Therefore, developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].
+
+@schaafsma2015deconstructing compiled a “wish-list” for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way.
+As a nice add-on, tasks should allow for use within an fMRI scanner.
+With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
+
+Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic].
+Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual].
+A proposal was that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities [@schaafsma2015deconstructing].
+
+Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+The task should serve as a proxy for behavior as it appears in the real world.
+Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
+
+<!-- ## Our aims -->
 Our aim is, therefore, to make individual differences measurable in a systematic and reliable way.
-For getting precise person-specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
-One of our main goals is to create a task that induces variation between children.
+We want to create a task that induces variation between children to get precise person-specific estimates.
 To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
-
-To estimate the effect of inter-individual differences, we need a large sample size since some of the effects that we are looking for might be small.
+A standardized, easily accessible test procedure helps us to enable data collection at scale.
 Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
-A standardized, easily accessible test procedure helps us to enable data collection at scale.
-
-Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.
-
-In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively [TODO: add references].
-By acting as a 'front end ability' [@brooks2005development, p. 535], following an agent's gaze provides insights into their intentions, thoughts, and feelings. 
-In our definition, gaze cue understanding goes one step further by including the *acting* on the gaze-cued location.
-
----
-
-- why is social cognition important
-- what methods are currently been used?: wellman
-- what are common issues? 
-- what to aim at. individual differences in developmental psychology
-- what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
-- goal of the current project: standardized, easy to use continuous methods
-- soc cog, gaze cue understanding small def (longer one dev paper)
-
----
-
-Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1–13. https://doi.org/10.1038/s44159-022-00037-z:
-
-"ToM also has specific real-life consequences.
-First, the development of ToM competence goes along with general measures of children’s peer social skills in early and middle childhood.
-(...) Second, ToM specifically predicts communicative competence.
-(...) Third, ToM competence is related to the quality of peer relationships: children with more advanced ToM are rated as more likeable and popular among their peers.
-Fourth, children who are more proficient at ToM tasks tend to act more prosocially, including comforting, sharing or helping other individuals.
-Finally, preschool ToM competence predicts achievement in primary school, a relationship that is possibly mediated by social competence, in that preschool ToM abilities enable subsequent social competence development, which in turn contributes to school achievement." (p.
-2)
-"Evidence for an emerging understanding of perception at 9 months of age comes from various sources.
-For example, children begin to follow the gaze of other agents in systematic and differential ways: they follow an agent’s head turn only when the agent can actually see (has their eyes open rather than closed, or wears a transparent rather than an opaque blindfold)." (p.
-2)
-Developmental determinants: executive function, language ("that" complementations), social (SES, siblings, mind-minded parents)
-Implicit tasks: "A third class of implicit ToM tasks is interaction tasks, in which participants are involved in a communicative or cooperative interaction with another agent.
-This agent forms a mental state (such as a true or false belief regarding the contents of a box) and experimenters measure whether participants spontaneously take the agent’s belief into account in their interaction with the agent (for instance by helping or by interpreting the agent’s communicative acts accordingly)" (p.
-9)
-=> reliable & valid tasks to assess coherent development of social-cognitive functions
+
+In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component of this ability is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a 'front end ability' [@brooks2005development, p.
+535].
+In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* - therefore, using the available social information to guide your behavior as needed in real-life conditions.
 

### 2022-05-20 paper/manuscript.tex
first draft intro

@@
 
-Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
-
 \hypertarget{introduction}{%
@@
 Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the best-studied phenomena in developmental research.
-
-In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.
-
-But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
-
-Researchers are interested in questions concerning individual differences in the social cognition domain (Hughes \& Devine, 2015).
-Previous studies focused, for example, on the association of stereotypes and theory of mind (Rizzo \& Killen, 2018), mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011), attachment quality and gaze following (Astor et al., 2020), language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017), emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991), and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
-Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd, Donnelly, \& Christiansen, 2018; Mundy et al., 2007 May-Jun; Underwood, 1975).
-
-This is due to the fact that many developmental psychology studies track change at an (age-) group level.
-Traditional measures of social cognition are not designed to capture variation between children:
-they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties.
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C.
+Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
+
+One of the most commonly applied, prototypical measures that have been applied in this area is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
+Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
+A doll called Sally puts her marble into a basket.
+After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
+To assess false belief understanding, participants get asked where Sally will look for her marble once she returns.
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
+Many years of research utilizing these verbal change-of-location tasks suggests that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
+Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf.
+Mayer \& Träuble, 2015).
+From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
+Therefore, the focus has been to track change at an (age-) group level -- within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+
+Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret them as error variance, therefore neglecting and trivializing individual differences (Kidd, Donnelly, \& Christiansen, 2018).
+Consequently, little consensus has been reached on the interrelation or independence of social-cognitive abilities (termed `structure of social cognition' by Happé, Cook, \& Bird, 2017).
+However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
+For example, it could be used to disentangle accounts on \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
+Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
+For this endeavor, we need to take individual differences seriously -- both theoretically and methodologically.
+
+Some studies have already examined individual differences in social cognition (Hughes \& Devine, 2015; Slaughter, 2015).
+Previous studies focused, for example, on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011), emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991), stereotypes and theory of mind (Rizzo \& Killen, 2018), prosociality and theory of mind (for a review see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), executive functions and theory of mind {[}Carlson, Moses, and Claxton (2004); @ buttelmann2021relations{]}, parenting practices and theory of mind (for a review see Pavarini, de Hollanda Souza, \& Hawk, 2013), agency and moral cognition (Sodian et al., 2016), attachment quality and gaze following (Astor et al., 2020), language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017), and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
+Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007 May-Jun; Underwood, 1975).
+
+Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related (e.g., Sodian et al., 2016).
+This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+A recent paper by Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
+The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
+A recent review underlines reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+Even studies focusing on individual differences often use behavioral forced-choice paradigms (Carlson et al., 2004; e.g., Walker, 2005) and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
+Few studies that do realize continuous measures often administer (theory of mind) scales and aggregate data across trials.
+This way, the social-cognitive ability in question is still assessed categorically on a trial basis (Bulgarelli \& Molina, 2016; Buttelmann, Kühn, \& Zmyj, 2021; e.g., Rizzo \& Killen, 2018).
 This has profound implications for what these studies can show.
@@
 
-To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.
-
-We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).
-
-A recent paper by Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
-The authors could show that this often does not emerge due to high measurement variance but rather low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
-In a similar vein, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a certain cognitive test is suited to draw inferences about individuals.
-
-{[}TODO: check Manuels references{]}
-
-However, we rarely find studies addressing these issues.
-Methods, that have currently been used, are\ldots{}
-One of the most commonly applied measures in social cognition research is the Sally-Anne task. {[}TODO: fill in FB studies{]}
-The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would \ldots{}
-With four to five years of age, most children pass the task.
-From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
-With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task.
-However, no individual differences can be visible, especially when applying only one trial per child.
+Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
+A recent paper compiled a ``wish-list'' for new social-cognitive paradigms (Schaafsma, Pfaff, Spunt, \& Adolphs, 2015) that advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way.
+As a nice add-on, tasks should allow for use within an fMRI scanner.
+With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
+Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
+Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
+A proposal was that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities (Schaafsma et al., 2015).
+Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+The task should serve as a proxy for behavior as it appears in the real world.
+Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
 
 Our aim is, therefore, to make individual differences measurable in a systematic and reliable way.
-For getting precise person-specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability.
-One of our main goals is to create a task that induces variation between children.
+We want to create a task that induces variation between children to get precise person-specific estimates.
 To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
-
-To estimate the effect of inter-individual differences, we need a large sample size since some of the effects that we are looking for might be small.
+A standardized, easily accessible test procedure helps us to enable data collection at scale.
 Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
-A standardized, easily accessible test procedure helps us to enable data collection at scale.
-
-Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.
-
-In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively {[}TODO: add references{]}.
-By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535), following an agent's gaze provides insights into their intentions, thoughts, and feelings.
-In our definition, gaze cue understanding goes one step further by including the \emph{acting} on the gaze-cued location.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\begin{itemize}
-\tightlist
-\item
-  why is social cognition important
-\item
-  what methods are currently been used?: wellman
-\item
-  what are common issues?
-\item
-  what to aim at. individual differences in developmental psychology
-\item
-  what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
-\item
-  goal of the current project: standardized, easy to use continuous methods
-\item
-  soc cog, gaze cue understanding small def (longer one dev paper)
-\end{itemize}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. Nature Reviews Psychology, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}:
-
-``ToM also has specific real-life consequences.
-First, the development of ToM competence goes along with general measures of children's peer social skills in early and middle childhood.
-(\ldots) Second, ToM specifically predicts communicative competence.
-(\ldots) Third, ToM competence is related to the quality of peer relationships: children with more advanced ToM are rated as more likeable and popular among their peers.
-Fourth, children who are more proficient at ToM tasks tend to act more prosocially, including comforting, sharing or helping other individuals.
-Finally, preschool ToM competence predicts achievement in primary school, a relationship that is possibly mediated by social competence, in that preschool ToM abilities enable subsequent social competence development, which in turn contributes to school achievement.'' (p.~2)
-``Evidence for an emerging understanding of perception at 9 months of age comes from various sources.
-For example, children begin to follow the gaze of other agents in systematic and differential ways: they follow an agent's head turn only when the agent can actually see (has their eyes open rather than closed, or wears a transparent rather than an opaque blindfold).'' (p.~2)
-Developmental determinants: executive function, language (``that'' complementations), social (SES, siblings, mind-minded parents)
-Implicit tasks: ``A third class of implicit ToM tasks is interaction tasks, in which participants are involved in a communicative or cooperative interaction with another agent.
-This agent forms a mental state (such as a true or false belief regarding the contents of a box) and experimenters measure whether participants spontaneously take the agent's belief into account in their interaction with the agent (for instance by helping or by interpreting the agent's communicative acts accordingly)'' (p.~9)
-=\textgreater{} reliable \& valid tasks to assess coherent development of social-cognitive functions
+In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a `front end ability' (Brooks \& Meltzoff, 2005, p.
+535).
+In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} -therefore, using the social information to guide your behavior as needed in real-life conditions.
 
@@
 
-Adults were recruited via \emph{Prolific}.
+Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
@@
 Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment.
-Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016).
+Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018; Hughes \& Leekam, 2004), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016).
 It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the validity of our measure.
+Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
 
@@
 In addition, we calculated three index scores.
-First, we calculated a sibling variety score according to Peterson (2000).
+First, we calculated a sibling variety score according to Candida C.
+Peterson (2000).
 Second, we implemented the modified version of Cassidy et al.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-astor2021gaze}{}}%
+Astor, K., Thiele, M., \& Gredebäck, G.
+(2021).
+Gaze following emergence relies on both perceptual cues and social awareness.
+\emph{Cognitive Development}, \emph{60}, 101121.
+\url{https://doi.org/10.1016/j.cogdev.2021.101121}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baron-cohen1985does}{}}%
+Baron-Cohen, S., Leslie, A. M., \& Frith, U. (1985). Does the autistic child have a "theory of mind" ? \emph{Cognition}, \emph{21}, 37--46. \url{https://doi.org/10.1016/0010-0277(85)90022-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barrett2013early}{}}%
+Barrett, H.
+C., Broesch, T., Scott, R.
+M., He, Z., Baillargeon, R., Wu, D., \ldots{} Laurence, S.
+(2013).
+Early false-belief understanding in traditional non-{Western} societies.
+\emph{Proceedings of the Royal Society B: Biological Sciences}.
+\url{https://doi.org/10.1098/rspb.2012.2654}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
+Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M.
+H.
+(2020).
+Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}.
+\emph{Frontiers in Psychology}, \emph{0}.
+\url{https://doi.org/10.3389/fpsyg.2019.02905}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-buttelmann2021relations}{}}%
+Buttelmann, D., Kühn, K., \& Zmyj, N.
+(2021).
+The {Relations} among {Theory} of {Mind}, {Inhibitory Control}, and {Aggressive Behavior} in 4-{Year-Old Children} \textendash{} {A Multi-Measure Multi-Informant Approach}.
+\emph{Journal of Cognition and Development}, \emph{0}(0), 1--24.
+\url{https://doi.org/10.1080/15248372.2021.1987240}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byers-heinlein2021development}{}}%
+Byers-Heinlein, K., Tsui, R.
+K.-Y., van Renswoude, D., Black, A.
+K., Barr, R., Brown, A., \ldots{} Singh, L.
+(2021).
+The development of gaze following in monolingual and bilingual infants: {A} multi-laboratory study.
+\emph{Infancy}, \emph{26}(1), 4--38.
+\url{https://doi.org/10.1111/infa.12360}
+
+\leavevmode\vadjust pre{\hypertarget{ref-callaghan2005synchrony}{}}%
+Callaghan, T., Rochat, P., Lillard, A., Claux, M.
+L., Odden, H., Itakura, S., \ldots{} Singh, S.
+(2005).
+Synchrony in the onset of mental-state reasoning: {Evidence} from five cultures.
+\emph{Psychological Science}.
+\url{https://doi.org/10.1111/j.0956-7976.2005.01544.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
+Carlson, S.
+M., Moses, L.
+J., \& Claxton, L.
+J.
+(2004).
+Individual differences in executive functioning and theory of mind: {An} investigation of inhibitory control and planning ability.
+\emph{Journal of Experimental Child Psychology}, \emph{87}(4), 299--319.
+\url{https://doi.org/10.1016/j.jecp.2004.01.002}
+
 \leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
 Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106.
+
+\leavevmode\vadjust pre{\hypertarget{ref-coelho2006searching}{}}%
+Coelho, E., George, N., Conty, L., Hugueville, L., \& Tijus, C.
+(2006).
+Searching for asymmetries in the detection of gaze contact versus averted gaze under different head views: A behavioural study.
+\emph{Spatial Vision}, \emph{19}(6), 529--545.
+\url{https://doi.org/10.1163/156856806779194026}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
+Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G.
+(2019).
+The {Developmental Origins} of {Gaze-Following} in {Human Infants}.
+\emph{Infancy}, \emph{24}(3), 433--454.
+\url{https://doi.org/10.1111/infa.12276}
+
 \leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
+Frischen, A., Bayliss, A.
+P., \& Tipper, S.
+P.
+(2007).
+Gaze cueing of attention: {Visual} attention, social cognition, and individual differences.
+\emph{Psychological Bulletin}, \emph{133}(4), 694--724.
+\url{https://doi.org/10.1037/0033-2909.133.4.694}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gopnik1991young}{}}%
+Gopnik, A., \& Slaughter, V. (1991). Young {Children}'s {Understanding} of {Changes} in {Their Mental States}. \emph{Child Development}, \emph{62}(1), 98. \url{https://doi.org/10.2307/1130707}
+
+\leavevmode\vadjust pre{\hypertarget{ref-happe2017structure}{}}%
+Happé, F., Cook, J.
+L., \& Bird, G.
+(2017).
+The {Structure} of {Social Cognition}: {In}(ter)dependence of {Sociocognitive Processes}.
+\emph{Annual Review of Psychology}, \emph{68}(1), 243--267.
+\url{https://doi.org/10.1146/annurev-psych-010416-044046}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hedge2018reliability}{}}%
@@
 \url{https://doi.org/10.3758/s13428-017-0935-1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
+Hernik, M., \& Broesch, T.
+(2019).
+Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}.
+\emph{Developmental Science}, \emph{22}(4), e12779.
+\url{https://doi.org/10.1111/desc.12779}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hughes2004links}{}}%
+Hughes, C., \& Leekam, S.
+(2004).
+What are the {Links Between Theory} of {Mind} and {Social Relations}?
+{Review}, {Reflections} and {New Directions} for {Studies} of {Typical} and {Atypical Development}.
+\emph{Social Development}, \emph{13}(4), 590--619.
+\url{https://doi.org/10.1111/j.1467-9507.2004.00285.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-imuta2016theory}{}}%
+Imuta, K., Henry, J.
+D., Slaughter, V., Selcuk, B., \& Ruffman, T.
+(2016).
+Theory of mind and prosocial behavior in childhood: {A} meta-analytic review.
+\emph{Developmental Psychology}, \emph{52}(8), 1192--1205.
+\url{https://doi.org/10.1037/dev0000140}
+
+\leavevmode\vadjust pre{\hypertarget{ref-itakura1998use}{}}%
+Itakura, S., \& Tanaka, M.
+(1998).
+Use of experimenter-given cues during object-choice tasks by chimpanzees ({Pan} troglodytes), an orangutan ({Pongo} pygmaeus), and human infants ({Homo} sapiens).
+\emph{Journal of Comparative Psychology}, \emph{112}(2), 119--126.
+\url{https://doi.org/10.1037/0735-7036.112.2.119}
+
 \leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lee1998children}{}}%
+Lee, K., Eskritt, M., Symons, L.
+A., \& Muir, D.
+(1998).
+Children's use of triadic eye gaze information for "mind reading".
+\emph{Developmental Psychology}, \emph{34}(3), 525--539.
+\url{https://doi.org/10.1037//0012-1649.34.3.525}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayer2015weird}{}}%
+Mayer, A., \& Träuble, B.
+(2015).
+The weird world of cross-cultural false-belief research: {A} true- and false-belief study among samoan children based on commands.
+\emph{Journal of Cognition and Development}, \emph{16}(4), 650--665.
+\url{https://doi.org/10.1080/15248372.2014.926273}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayes1996testretest}{}}%
+Mayes, L.
+C., Klin, A., Tercyak, K.
+P., Cicchetti, D.
+V., \& Cohen, D.
+J.
+(1996).
+Test-{Retest Reliability} for {False-Belief Tasks}.
+\emph{Journal of Child Psychology and Psychiatry}, \emph{37}(3), 313--319.
+\url{https://doi.org/10.1111/j.1469-7610.1996.tb01408.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
 McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
+Moore, C. (2008). The {Development} of {Gaze Following}. \emph{Child Development Perspectives}, \emph{2}(2), 66--70. \url{https://doi.org/10.1111/j.1750-8606.2008.00052.x}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-palan2018prolific}{}}%
+Palan, S., \& Schitter, C.
+(2018).
+Prolific.ac\textemdash{{A}} subject pool for online experiments.
+\emph{Journal of Behavioral and Experimental Finance}, \emph{17}, 22--27.
+\url{https://doi.org/10.1016/j.jbef.2017.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pavarini2013parental}{}}%
+Pavarini, G., de Hollanda Souza, D., \& Hawk, C.
+K.
+(2013).
+Parental {Practices} and {Theory} of {Mind Development}.
+\emph{Journal of Child and Family Studies}, \emph{22}(6), 844--853.
+\url{https://doi.org/10.1007/s10826-012-9643-8}
+
 \leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
-Peterson, C.
-C.
+Peterson, Candida C.
 (2000).
@@
 \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2012mind}{}}%
+Peterson, Candida C., Wellman, H.
+M., \& Slaughter, V.
+(2012).
+The {Mind Behind} the {Message}: {Advancing Theory-of-Mind Scales} for {Typically Developing Children}, and {Those With Deafness}, {Autism}, or {Asperger Syndrome}: {\textbf{The Mind Behind}}{ \textbf{the} }{\textbf{Message}}.
+\emph{Child Development}, \emph{83}(2), 469--485.
+\url{https://doi.org/10.1111/j.1467-8624.2011.01728.x}
 
@@
 R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
+Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-schaafsma2015deconstructing}{}}%
+Schaafsma, S.
+M., Pfaff, D.
+W., Spunt, R.
+P., \& Adolphs, R.
+(2015).
+Deconstructing and reconstructing theory of mind.
+\emph{Trends in Cognitive Sciences}, \emph{19}(2), 65--72.
+\url{https://doi.org/10.1016/j.tics.2014.11.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
+Shepherd, S. (2010). Following {Gaze}: {Gaze-Following Behavior} as a {Window} into {Social Cognition}. \emph{Frontiers in Integrative Neuroscience}, \emph{4}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-slaughter2015theorya}{}}%
+Slaughter, V. (2015). Theory of {Mind} in {Infants} and {Young Children}: {A Review}. \emph{Australian Psychologist}, \emph{50}(3), 169--172. \url{https://doi.org/10.1111/ap.12080}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
+Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A.
+(2016).
+Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}.
+\emph{Child Development}, \emph{87}(4), 1221--1232.
+\url{https://doi.org/10.1111/cdev.12533}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
+Tomasello, M., Hare, B., Lehmann, H., \& Call, J.
+(2007).
+Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
+\emph{Journal of Human Evolution}, \emph{52}(3), 314--320.
+\url{https://doi.org/10.1016/j.jhevol.2006.10.001}
+
 \leavevmode\vadjust pre{\hypertarget{ref-underwood1975individual}{}}%
 Underwood, B. J. (1975). Individual differences as a crucible in theory construction. \emph{American Psychologist}, \emph{30}(2), 128--134. \url{https://doi.org/10.1037/h0076759}
+
+\leavevmode\vadjust pre{\hypertarget{ref-walker2005gender}{}}%
+Walker, S.
+(2005).
+Gender {Differences} in the {Relationship Between Young Children}'s {Peer-Related Social Competence} and {Individual Differences} in {Theory} of {Mind}.
+\emph{The Journal of Genetic Psychology}, \emph{166}(3), 297--312.
+\url{https://doi.org/10.3200/GNTP.166.3.297-312}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2012theory}{}}%
+Wellman, H.
+M.
+(2012).
+Theory of mind: {Better} methods, clearer findings, more development.
+\emph{European Journal of Developmental Psychology}, \emph{9}(3), 313--330.
+\url{https://doi.org/10.1080/17405629.2012.680297}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysisa}{}}%
+Wellman, H.
+M., Cross, D., \& Watson, J.
+(2001).
+Meta-{Analysis} of {Theory-of-Mind Development}: {The Truth} about {False Belief}.
+\emph{Child Development}, \emph{72}(3), 655--684.
+\url{https://doi.org/10.1111/1467-8624.00304}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scalinga}{}}%
+Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
 
@@
 For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
-First, we followed the approach by Peterson (2000).
+First, we followed the approach by Candida C.
+Peterson (2000).
 Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
@@
 (2005).
-The authors adjusted the original score of Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+The authors adjusted the original score of Candida C.
+Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
 Twins with additional siblings scored depending on the age and number of their siblings.
@@
 The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
-However, teenage siblings might provide opportunities for interesting discussions (Peterson, 2000).
+However, teenage siblings might provide opportunities for interesting discussions (Candida C.
+Peterson, 2000).
 

### 2022-05-20 paper/manuscript.Rmd
add more line breaks for easier review

@@
 Participants then get asked where Sally will look for her marble once she returns. 
-The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket.
+The outcome measures false belief understanding in a dichotomous way: 
+children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket. 
 Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysisa].
-Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf.
-@mayer2015weird].
+Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. 
-As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p.
-317).
-Therefore, the focus has been to track change at an (age-) group level – within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
+Therefore, the focus has been to track change at an (age-) group level – 
+within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
 
@@
 Some studies have already examined individual differences in social cognition [@hughes2015individual; @slaughter2015theorya]. 
-Previous studies focused, for example, on the association of mental state talk and false belief understanding [@hughes2011individual], emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], stereotypes and theory of mind [@rizzo2018theory], prosociality and theory of mind [for a review see @imuta2016theory; @walker2005gender], executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], parenting practices and theory of mind [for a review see @pavarini2013parental], agency and moral cognition [@sodian2016understanding], attachment quality and gaze following [@astor2020social], language and gaze following [@okumura2017individual], and the interplay of physical and social cognition [@herrmann2010structure].
+Previous studies focused, for example, 
+on the association of mental state talk and false belief understanding [@hughes2011individual], 
+emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
+stereotypes and theory of mind [@rizzo2018theory], 
+prosociality and theory of mind [for a review see @imuta2016theory; @walker2005gender], 
+executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], 
+parenting practices and theory of mind [for a review see @pavarini2013parental], 
+agency and moral cognition [@sodian2016understanding], 
+attachment quality and gaze following [@astor2020social], 
+language and gaze following [@okumura2017individual], 
+and the interplay of physical and social cognition [@herrmann2010structure]. 
 Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].
@@
 Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related [e.g., @sodian2016understanding]. 
-This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+This might be because traditional measures of social cognition are not designed to capture variation between children: 
+they often rely on low trial numbers, small sample sizes, and dichotomous measures. 
 @hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies. 
-The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed "reliability paradox").
 Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
@@
 
-@schaafsma2015deconstructing compiled a “wish-list” for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+@schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
 In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way. 
@@
 
-Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+Another goal in creating new tasks should be to focus on the face value: 
+we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. 
 The task should serve as a proxy for behavior as it appears in the real world. 
@@
 
-In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: 
+gaze cue understanding - the ability to locate and use the attentional focus of an agent. 
 The first component of this ability is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
-Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a 'front end ability' [@brooks2005development, p.
-535].
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a 'front end ability' [@brooks2005development, p. 535]. 
 In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* - therefore, using the available social information to guide your behavior as needed in real-life conditions.

### 2022-05-20 paper/manuscript.tex
add more line breaks for easier review

@@
 
-One of the most commonly applied, prototypical measures that have been applied in this area is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
+One of the most commonly applied, prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
@@
 After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
-To assess false belief understanding, participants get asked where Sally will look for her marble once she returns.
-The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
-Many years of research utilizing these verbal change-of-location tasks suggests that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
-Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf.
-Mayer \& Träuble, 2015).
-From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+Participants then get asked where Sally will look for her marble once she returns.
+The outcome measures false belief understanding in a dichotomous way:
+children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
+Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
+Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
-Therefore, the focus has been to track change at an (age-) group level -- within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
-
-Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret them as error variance, therefore neglecting and trivializing individual differences (Kidd, Donnelly, \& Christiansen, 2018).
+Therefore, the focus has been to track change at an (age-) group level --
+within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+
+Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret it as error variance, therefore neglecting and trivializing individual differences (Kidd, Donnelly, \& Christiansen, 2018).
 Consequently, little consensus has been reached on the interrelation or independence of social-cognitive abilities (termed `structure of social cognition' by Happé, Cook, \& Bird, 2017).
+
 However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
-For example, it could be used to disentangle accounts on \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
+For example, it could be used to provide evidence for accounts on \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
 Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
@@
 Some studies have already examined individual differences in social cognition (Hughes \& Devine, 2015; Slaughter, 2015).
-Previous studies focused, for example, on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011), emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991), stereotypes and theory of mind (Rizzo \& Killen, 2018), prosociality and theory of mind (for a review see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), executive functions and theory of mind {[}Carlson, Moses, and Claxton (2004); @ buttelmann2021relations{]}, parenting practices and theory of mind (for a review see Pavarini, de Hollanda Souza, \& Hawk, 2013), agency and moral cognition (Sodian et al., 2016), attachment quality and gaze following (Astor et al., 2020), language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017), and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
-Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007 May-Jun; Underwood, 1975).
+Previous studies focused, for example,
+on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011),
+emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
+stereotypes and theory of mind (Rizzo \& Killen, 2018),
+prosociality and theory of mind (for a review see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
+executive functions and theory of mind (Buttelmann, Kühn, \& Zmyj, 2021; Carlson, Moses, \& Claxton, 2004),
+parenting practices and theory of mind (for a review see Pavarini, de Hollanda Souza, \& Hawk, 2013),
+agency and moral cognition (Sodian et al., 2016),
+attachment quality and gaze following (Astor et al., 2020),
+language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017),
+and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
+Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007; Underwood, 1975).
 
 Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related (e.g., Sodian et al., 2016).
-This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent paper by Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
-The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences.
+This might be because traditional measures of social cognition are not designed to capture variation between children:
+they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
+The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed ``reliability paradox'').
 Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlines reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
-Even studies focusing on individual differences often use behavioral forced-choice paradigms (Carlson et al., 2004; e.g., Walker, 2005) and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
-Few studies that do realize continuous measures often administer (theory of mind) scales and aggregate data across trials.
-This way, the social-cognitive ability in question is still assessed categorically on a trial basis (Bulgarelli \& Molina, 2016; Buttelmann, Kühn, \& Zmyj, 2021; e.g., Rizzo \& Killen, 2018).
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+
+Even studies focusing on individual differences often use behavioral forced-choice paradigms {[}e.g., carlson2004individual; Walker (2005){]}.
+Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
+This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
 This has profound implications for what these studies can show.
@@
 
-Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+Therefore, developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
 To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
-A recent paper compiled a ``wish-list'' for new social-cognitive paradigms (Schaafsma, Pfaff, Spunt, \& Adolphs, 2015) that advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+
+Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
 In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way.
@@
 With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
+
 Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
@@
 A proposal was that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities (Schaafsma et al., 2015).
-Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
+
+Another goal in creating new tasks should be to focus on the face value:
+we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
 The task should serve as a proxy for behavior as it appears in the real world.
@@
 Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
-In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
-Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a `front end ability' (Brooks \& Meltzoff, 2005, p.
-535).
-In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} -therefore, using the social information to guide your behavior as needed in real-life conditions.
+
+In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes:
+gaze cue understanding - the ability to locate and use the attentional focus of an agent.
+The first component of this ability is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535).
+In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} - therefore, using the available social information to guide your behavior as needed in real-life conditions.
 
@@
 V.
-(2007 May-Jun).
+(2007).
 Individual differences and the development of joint attention in infancy.

### 2022-05-23 paper/manuscript.Rmd
incorporate Steven's feedback

@@
 abstract: |
-  In order to explain and predict the behavior of agents, we use social cognition: we represent and reason about other’s perspectives, knowledge, intentions, beliefs and preferences.
-Traditional measures of social cognition (e.g., false belief change-of-location tasks), however, often lack satisfactory psychometric properties: they are not designed to capture variation *between* children and rely on low trial numbers, dichotomous measures, and group averages.
-This has profound implications on what these studies can show.
+  To explain and predict the behavior of agents, we use social cognition: we represent and reason about others' perspectives, knowledge, intentions, beliefs, and preferences.
+However, traditional measures of social cognition (e.g., false belief change-of-location tasks) often lack satisfactory psychometric properties: they are not designed to capture variation *between* children and rely on low trial numbers, dichotomous measures, and group averages.
+This has profound implications for what these studies can show.
 Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-   To approach this issue, we designed a balloon finding task to study social cognition in young children and adults.
+   We designed a balloon-finding task to study social cognition in young children and adults to approach this issue.
 We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding – the ability to locate and use the attentional focus of an agent.
-Our interactive web interface works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
-The implemented spatial layout allows for discrete as well as continuous measures of participants’ click imprecision and is easily adoptable to different study needs.
-  Here we show that our task induces inter-individual differences in a child (N = XXX) and adult (N = XXX) sample.
+Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements.
+  Here we show that our task induces inter-individual differences in a child (N = XXX) and an adult (N = XXX) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
-High internal consistency and test-test reliability estimates underline that the capured variation is systematic.
-Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real life social surrounding.
-Taken together, this work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
+High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
+Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real-life social surroundings.
+This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
 
@@
 <!-- ## What is Social Cognition, and why do we care? -->
-Social cognition – representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior – is among the best-studied phenomena in developmental research.
+Social cognition - representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
 In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development [@gopnik1991young; @wellman2001metaanalysisa; @wellman2004scalinga; @peterson2012mind; @rakoczy2022foundations].
@@
 <!-- ## How has it been measured traditionally? -->
-One of the most commonly applied, prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does]. 
+One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does]. 
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters). 
@@
 As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
-Therefore, the focus has been to track change at an (age-) group level – 
-within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
 
@@
 However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure].
-For example, it could be used to provide evidence for accounts on *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
+For example, those identifiers could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
 Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
@@
 on the association of mental state talk and false belief understanding [@hughes2011individual], 
-emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
+emotion, language, family interaction, and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
 stereotypes and theory of mind [@rizzo2018theory], 
-prosociality and theory of mind [for a review see @imuta2016theory; @walker2005gender], 
+prosociality and theory of mind [for a review, see @imuta2016theory; @walker2005gender], 
 executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], 
-parenting practices and theory of mind [for a review see @pavarini2013parental], 
+parenting practices and theory of mind [for a review, see @pavarini2013parental], 
 agency and moral cognition [@sodian2016understanding], 
@@
 Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or show poor test-retest reliability [@mayes1996testretest].
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest].
 
@@
 <!-- ## A wish list for new social-cognitive tasks -->
-Therefore, developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+Therefore, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
 To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].
 
-@schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+@schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms.
+They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
 In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way. 
-As a nice add-on, tasks should allow for use within an fMRI scanner. 
+Additionally, tasks should allow for use within an fMRI scanner. 
 With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
@@
 Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual]. 
-A proposal was that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities [@schaafsma2015deconstructing].
+@schaafsma2015deconstructing proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
 
@@
 <!-- ## Our aims -->
-Our aim is, therefore, to make individual differences measurable in a systematic and reliable way. 
+Therefore, we aim to make individual differences measurable in a systematic and reliable way. 
 We want to create a task that induces variation between children to get precise person-specific estimates. 
@@
 A standardized, easily accessible test procedure helps us to enable data collection at scale. 
-Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
+Since data collection with families requires much organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
 
@@
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a 'front end ability' [@brooks2005development, p. 535]. 
-In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* - therefore, using the available social information to guide your behavior as needed in real-life conditions.
+In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* - therefore, using the available social information to guide one's behavior as needed in real-life conditions.
 

### 2022-05-23 paper/manuscript.tex
incorporate Steven's feedback

@@
 \abstract{%
-In order to explain and predict the behavior of agents, we use social cognition: we represent and reason about other's perspectives, knowledge, intentions, beliefs and preferences.
-Traditional measures of social cognition (e.g., false belief change-of-location tasks), however, often lack satisfactory psychometric properties: they are not designed to capture variation \emph{between} children and rely on low trial numbers, dichotomous measures, and group averages.
-This has profound implications on what these studies can show.
+To explain and predict the behavior of agents, we use social cognition: we represent and reason about others' perspectives, knowledge, intentions, beliefs, and preferences.
+However, traditional measures of social cognition (e.g., false belief change-of-location tasks) often lack satisfactory psychometric properties: they are not designed to capture variation \emph{between} children and rely on low trial numbers, dichotomous measures, and group averages.
+This has profound implications for what these studies can show.
 Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-To approach this issue, we designed a balloon finding task to study social cognition in young children and adults.
+We designed a balloon-finding task to study social cognition in young children and adults to approach this issue.
 We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding -- the ability to locate and use the attentional focus of an agent.
-Our interactive web interface works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
-The implemented spatial layout allows for discrete as well as continuous measures of participants' click imprecision and is easily adoptable to different study needs.
-Here we show that our task induces inter-individual differences in a child (N = XXX) and adult (N = XXX) sample.
+Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+The implemented spatial layout allows for discrete and continuous measures of participants' click imprecision and is easily adaptable to different study requirements.
+Here we show that our task induces inter-individual differences in a child (N = XXX) and an adult (N = XXX) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
-High internal consistency and test-test reliability estimates underline that the capured variation is systematic.
-Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real life social surrounding.
-Taken together, this work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
+High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
+Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real-life social surroundings.
+This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
 }
@@
 
-Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the best-studied phenomena in developmental research.
+Social cognition - representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
 In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C.
@@
 
-One of the most commonly applied, prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
+One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
@@
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
-Therefore, the focus has been to track change at an (age-) group level --
-within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
+Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
 
@@
 However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
-For example, it could be used to provide evidence for accounts on \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind) or \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
+For example, those identifiers could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
 Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
@@
 on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011),
-emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
+emotion, language, family interaction, and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
 stereotypes and theory of mind (Rizzo \& Killen, 2018),
-prosociality and theory of mind (for a review see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
+prosociality and theory of mind (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
 executive functions and theory of mind (Buttelmann, Kühn, \& Zmyj, 2021; Carlson, Moses, \& Claxton, 2004),
-parenting practices and theory of mind (for a review see Pavarini, de Hollanda Souza, \& Hawk, 2013),
+parenting practices and theory of mind (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013),
 agency and moral cognition (Sodian et al., 2016),
@@
 Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
 
@@
 
-Therefore, developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.
+Therefore, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
 To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
 
-Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms and advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
+Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
+They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
 In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way.
-As a nice add-on, tasks should allow for use within an fMRI scanner.
+Additionally, tasks should allow for use within an fMRI scanner.
 With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
@@
 Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
-A proposal was that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities (Schaafsma et al., 2015).
+Schaafsma et al. (2015) proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
 
@@
 
-Our aim is, therefore, to make individual differences measurable in a systematic and reliable way.
+Therefore, we aim to make individual differences measurable in a systematic and reliable way.
 We want to create a task that induces variation between children to get precise person-specific estimates.
@@
 A standardized, easily accessible test procedure helps us to enable data collection at scale.
-Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
+Since data collection with families requires much organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
 
@@
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535).
-In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} - therefore, using the available social information to guide your behavior as needed in real-life conditions.
+In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} - therefore, using the available social information to guide one's behavior as needed in real-life conditions.
 

### 2022-05-23 paper/manuscript.Rmd
add some more references (ind diff book)

@@
 Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. 
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. 
 As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
@@
 However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure].
-For example, those identifiers could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
-Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
-For this endeavor, we need to take individual differences seriously – both theoretically and methodologically.
+For example, the structure of variability could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
+@stenhaug2021structure have argued for the differentiation between stage models (i.e., synchronization in developmental changes across distinct domains) and modular theories (i.e., particular aspects of development proceed on their own schedule).
+In addition, individual difference studies are useful for identifying antecedent factors as potential developmental causes, consequences of an early or late social-cognitive development, and qualitative differences in the actual social life [@keenan2003individual; @bartsch1996individual].
+Therefore, we argue that studying the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency requires us to take individual differences seriously – both theoretically and methodologically.
 
 <!-- ## Existing research tapping into individual differences -->
-Some studies have already examined individual differences in social cognition [@hughes2015individual; @slaughter2015theorya]. 
-Previous studies focused, for example, 
-on the association of mental state talk and false belief understanding [@hughes2011individual], 
-emotion, language, family interaction, and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
-stereotypes and theory of mind [@rizzo2018theory], 
-prosociality and theory of mind [for a review, see @imuta2016theory; @walker2005gender], 
-executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], 
-parenting practices and theory of mind [for a review, see @pavarini2013parental], 
-agency and moral cognition [@sodian2016understanding], 
-attachment quality and gaze following [@astor2020social], 
-language and gaze following [@okumura2017individual], 
-and the interplay of physical and social cognition [@herrmann2010structure]. 
+Some studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. 
+These individual differences studies usually focus on three different kinds of relationships between social-cognitive abilities and: 
+(1) family influences, (2) other cognitive constructs, and (3) social outcome measures [for an overview, see @repacholi2003introduction].
+
+The first subgroup covers studies on social-cognitive abilities and parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background (education, occupation, sibling interaction, childcare) [@dunn1991young; @cutting1999theory; bulgarelli2016social].
+In the second subgroup, individual differences studies include the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
+The third subgroup encompasses studies on social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], 
+stereotypes and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
+
 Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].
@@
 Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest].
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest] [but cf @hughes2000good].
 
@@
 This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations].
+In addition, individual differences are only identified in the age of onset of the social-cognitive ability and not in performance or competence [@repacholi2003introduction].
 This has profound implications for what these studies can show. 
@@
 
-Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic].
-Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual]. 
+Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic; @keenan2003individual].
+Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual, @repacholi2003introduction]. 
 @schaafsma2015deconstructing proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
@@
 we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. 
-The task should serve as a proxy for behavior as it appears in the real world. 
+The task should serve as a proxy for behavior as it appears in the real world [@repacholi2003introduction; @repacholi2004individual]. 
 Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
@@
 
+- benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
+
 ## Limitations
 ## Future development / extending the task
+- benefits of task battery
 

### 2022-05-23 paper/manuscript.tex
add some more references (ind diff book)

@@
 In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C.
-Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
+Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; \textbf{wellman2001metaanalysisa?}; \textbf{wellman2004scalinga?}).
 
@@
 children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
-Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
+Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see \textbf{wellman2001metaanalysisa?}).
 Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (V. S. \&. B. Repacholi, 2003).
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
@@
 However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
-For example, those identifiers could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
-Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
-For this endeavor, we need to take individual differences seriously -- both theoretically and methodologically.
-
-Some studies have already examined individual differences in social cognition (Hughes \& Devine, 2015; Slaughter, 2015).
-Previous studies focused, for example,
-on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011),
-emotion, language, family interaction, and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
-stereotypes and theory of mind (Rizzo \& Killen, 2018),
-prosociality and theory of mind (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
-executive functions and theory of mind (Buttelmann, Kühn, \& Zmyj, 2021; Carlson, Moses, \& Claxton, 2004),
-parenting practices and theory of mind (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013),
-agency and moral cognition (Sodian et al., 2016),
-attachment quality and gaze following (Astor et al., 2020),
-language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017),
-and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
+For example, the structure of variability could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
+Stenhaug, Ram, and Frank (2021) have argued for the differentiation between stage models (i.e., synchronization in developmental changes across distinct domains) and modular theories (i.e., particular aspects of development proceed on their own schedule).
+In addition, individual difference studies are useful for identifying antecedent factors as potential developmental causes, consequences of an early or late social-cognitive development, and qualitative differences in the actual social life (Bartsch \& Estes, 1996; Keenan, 2003).
+Therefore, we argue that studying the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency requires us to take individual differences seriously -- both theoretically and methodologically.
+
+Some studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
+These individual differences studies usually focus on three different kinds of relationships between social-cognitive abilities and:
+(1) family influences, (2) other cognitive constructs, and (3) social outcome measures (for an overview, see V. S. \&. B. Repacholi, 2003).
+
+The first subgroup covers studies on social-cognitive abilities and parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014), and family background (education, occupation, sibling interaction, childcare) {[}Dunn, Brown, Slomkowski, Tesla, and Youngblade (1991); Cutting and Dunn (1999); bulgarelli2016social{]}.
+In the second subgroup, individual differences studies include the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Stephanie M.
+Carlson \& Moses, 2001; Stephanie M.
+Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007 Mar-Apr; Milligan, Astington, \& Dack, 2007; Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
+The third subgroup encompasses studies on social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
+stereotypes and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).
+
 Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007; Underwood, 1975).
@@
 Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996) (but cf Hughes et al., 2000).
 
@@
 This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
+In addition, individual differences are only identified in the age of onset of the social-cognitive ability and not in performance or competence (V.
+S.
+\&.
+B.
+Repacholi, 2003).
 This has profound implications for what these studies can show.
@@
 
-Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
+Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015; Keenan, 2003).
+Task batteries might be better suited to cover a range of social-cognitive abilities V. S. \&. B. Repacholi (2003).
 Schaafsma et al. (2015) proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
@@
 we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-The task should serve as a proxy for behavior as it appears in the real world.
+The task should serve as a proxy for behavior as it appears in the real world (B. Repacholi \& Slaughter, 2004; V. S. \&. B. Repacholi, 2003).
 Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
@@
 
+\begin{itemize}
+\tightlist
+\item
+  benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
+\end{itemize}
+
 \hypertarget{limitations}{%
@@
 \subsection{Future development / extending the task}\label{future-development-extending-the-task}}
+
+\begin{itemize}
+\tightlist
+\item
+  benefits of task battery
+\end{itemize}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bartsch1996individual}{}}%
+Bartsch, K., \& Estes, D.
+(1996).
+Individual differences in children's developing theory of mind and implications for metacognition.
+\emph{Learning and Individual Differences}, \emph{8}(4), 281--304.
+\url{https://doi.org/10.1016/S1041-6080(96)90020-5}
+
 \leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
@@
 \url{https://doi.org/10.3389/fpsyg.2019.02905}
+
+\leavevmode\vadjust pre{\hypertarget{ref-benson2012individual}{}}%
+Benson, J., Sabbagh, M., Carlson, S., \& Zelazo, P.
+(2012).
+Individual {Differences} in {Executive Functioning Predict Preschoolers}' {Improvement From Theory-of-Mind Training}.
+\emph{Developmental Psychology}, \emph{49}.
+\url{https://doi.org/10.1037/a0031056}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-carlson2001individual}{}}%
+Carlson, Stephanie M., \& Moses, L. J. (2001). Individual {Differences} in {Inhibitory Control} and {Children}'s {Theory} of {Mind}. \emph{Child Development}, \emph{72}(4), 1032--1053.
+
 \leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
-Carlson, S.
-M., Moses, L.
+Carlson, Stephanie M., Moses, L.
 J., \& Claxton, L.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gola2012mental}{}}%
+Gola, A.
+A.
+H.
+(2012).
+Mental verb input for promoting children's theory of mind: {A} training study.
+\emph{Cognitive Development}, \emph{27}(1), 64--76.
+\url{https://doi.org/10.1016/j.cogdev.2011.10.003}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gopnik1991young}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hughes2000good}{}}%
+Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A.
+(2000).
+Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}.
+\emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490.
+\url{https://doi.org/10.1111/1469-7610.00633}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hughes2015individual}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hughes2007executive}{}}%
+Hughes, C., \& Ensor, R.
+(2007).
+Executive function and theory of mind: {Predictive} relations from ages 2 to 4.
+\emph{Developmental Psychology}, \emph{43}(6), 1447--1459.
+\url{https://doi.org/10.1037/0012-1649.43.6.1447}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hughes2011individual}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-keenan2003individual}{}}%
+Keenan, T. (2003). Individual {Differences} in {Theory} of {Mind}: {The Preschool Years} and {Beyond}. In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
@@
 \url{https://doi.org/10.1016/j.tics.2017.11.006}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lecce2014promoting}{}}%
+Lecce, S., Bianco, F., Devine, R.
+T., Hughes, C., \& Banerjee, R.
+(2014).
+Promoting theory of mind during middle childhood: {A} training program.
+\emph{Journal of Experimental Child Psychology}, \emph{126}, 52--67.
+\url{https://doi.org/10.1016/j.jecp.2014.03.002}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
+McEwen, F., Happé, F., Bolton, P., Rijsdijk, F., Ronald, A., Dworzynski, K., \& Plomin, R.
+(2007 Mar-Apr).
+Origins of individual differences in imitation: Links with language, pretend play, and socially insightful behavior in two-year-old twins.
+\emph{Child Development}, \emph{78}(2), 474--492.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01010.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-milligan2007language}{}}%
+Milligan, K., Astington, J.
+W., \& Dack, L.
+A.
+(2007).
+Language and {Theory} of {Mind}: {Meta-Analysis} of the {Relation Between Language Ability} and {False-belief Understanding}.
+\emph{Child Development}, \emph{78}(2), 622--646.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
@@
 Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-repacholi2004individual}{}}%
+Repacholi, B., \& Slaughter, V. (Eds.). (2004). \emph{Individual {Differences} in {Theory} of {Mind}} (Zeroth). {New York}: {Psychology Press}. \url{https://doi.org/10.4324/9780203488508}
+
+\leavevmode\vadjust pre{\hypertarget{ref-repacholi2003introduction}{}}%
+Repacholi, V. S. \&. B. (2003). Introduction {Individual Differences} in {Theory} of {Mind}: {What Are We Investigating}? In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-stenhaug2021structure}{}}%
+Stenhaug, B., Ram, N., \& Frank, M. C. (2021). \emph{The {Structure} of {Developmental Variation} in {Early Childhood}}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/95erq}
+
 \leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
@@
 \url{https://doi.org/10.1080/17405629.2012.680297}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysisa}{}}%
-Wellman, H.
-M., Cross, D., \& Watson, J.
-(2001).
-Meta-{Analysis} of {Theory-of-Mind Development}: {The Truth} about {False Belief}.
-\emph{Child Development}, \emph{72}(3), 655--684.
-\url{https://doi.org/10.1111/1467-8624.00304}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scalinga}{}}%
-Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
 

### 2022-05-23 paper/manuscript.Rmd
incorporate Manuels feedback

--- 2022-05-23 paper/manuscript.Rmd
@@
   - name          : "Manuel Bohn"
-    affiliation   : "1"
-
-  - name          : "Luke Maurits"
     affiliation   : "1"
@@
 # Introduction 
-<!-- ## What is Social Cognition, and why do we care? -->
-Social cognition - representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
-In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development [@gopnik1991young; @wellman2001metaanalysisa; @wellman2004scalinga; @peterson2012mind; @rakoczy2022foundations].
-
-<!-- ## How has it been measured traditionally? -->
-One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does]. 
+Social cognition -- representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development [@gopnik1991young; @wellman2001metaanalysis; @wellman2004scaling; @peterson2012mind; @rakoczy2022foundations].
+Yet, there are always individual differences. 
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions 
+[@happe2017structure; @mundy2007individual; @kidd2018individual; @underwood1975individual; @lecce2014promoting].
+
+Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. 
+These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome [for an overview, see @repacholi2003introduction].
+Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
+Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
+Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
+
+However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding].
+This might be because traditional measures of social cognition are not designed to capture variation between children: 
+they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+A recent review showed that many social cognition measures fail to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they do -- show poor test-retest reliability [@mayes1996testretest].
+
+To give an example: perhaps the most commonly applied prototypical measure for social cognition is the change-of-location false belief task [@baron-cohen1985does; @wimmer1983beliefs]. 
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters). 
@@
 children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket. 
-Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysisa].
+Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysis].
 Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. 
+
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. 
+Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability]. 
 As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
-Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
-
-<!-- ## Why care about individual differences? -->
-Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret it as error variance, therefore neglecting and trivializing individual differences [@kidd2018individual].
-Consequently, little consensus has been reached on the interrelation or independence of social-cognitive abilities [termed ‘structure of social cognition’ by @happe2017structure].
-
-However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure].
-For example, those identifiers could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual].
-Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.
-For this endeavor, we need to take individual differences seriously – both theoretically and methodologically.
-
-<!-- ## Existing research tapping into individual differences -->
-Some studies have already examined individual differences in social cognition [@hughes2015individual; @slaughter2015theorya]. 
-Previous studies focused, for example, 
-on the association of mental state talk and false belief understanding [@hughes2011individual], 
-emotion, language, family interaction, and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
-stereotypes and theory of mind [@rizzo2018theory], 
-prosociality and theory of mind [for a review, see @imuta2016theory; @walker2005gender], 
-executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], 
-parenting practices and theory of mind [for a review, see @pavarini2013parental], 
-agency and moral cognition [@sodian2016understanding], 
-attachment quality and gaze following [@astor2020social], 
-language and gaze following [@okumura2017individual], 
-and the interplay of physical and social cognition [@herrmann2010structure]. 
-Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].
-
-<!-- ## Methodological limitations -->
-Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related [e.g., @sodian2016understanding]. 
-This might be because traditional measures of social cognition are not designed to capture variation between children: 
-they often rely on low trial numbers, small sample sizes, and dichotomous measures. 
-@hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies. 
-The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed "reliability paradox").
-Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest].
-
-Even studies focusing on individual differences often use behavioral forced-choice paradigms [e.g., carlson2004individual; @walker2005gender]. 
-Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual].
-This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations]. 
-This has profound implications for what these studies can show. 
-Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
-
-<!-- ## A wish list for new social-cognitive tasks -->
-Therefore, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
+This has profound implications for what studies on individual differences using this task (or others) can show. 
+Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
+
+Thus, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably. 
 To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].
@@
 @schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms. 
-They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
-In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way. 
-Additionally, tasks should allow for use within an fMRI scanner. 
-With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
-
-Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic].
-Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual]. 
-@schaafsma2015deconstructing proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
-
-Another goal in creating new tasks should be to focus on the face value: 
-we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. 
-The task should serve as a proxy for behavior as it appears in the real world. 
-Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
-
-<!-- ## Our aims -->
-Therefore, we aim to make individual differences measurable in a systematic and reliable way. 
-We want to create a task that induces variation between children to get precise person-specific estimates. 
-To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject. 
-A standardized, easily accessible test procedure helps us to enable data collection at scale. 
-Since data collection with families requires much organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
-
-In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes: 
-gaze cue understanding - the ability to locate and use the attentional focus of an agent. 
-The first component of this ability is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
-Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a 'front end ability' [@brooks2005development, p. 535]. 
-In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* - therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
+New tasks should induce variation across age groups, including older children and adults [@repacholi2003introduction]. 
+Another goal in creating new tasks should be to focus on "face value": 
+measures should probe the underlying social-cognitive ability as straight-forward and directly as possible. 
+The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].
+
+# A new measure of gaze understanding
+
+Our goal was to design a new measure of social cognition that captures individual differences in a systematic and reliable way. 
+We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes: 
+gaze cue understanding -- the ability to locate and use the attentional focus of an agent. 
+The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- 
+and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535]. 
+In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+
+To address the psychometric shortcoming of earlier work, we implemented the following design features: 
+First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages. 
+Second, we designed short trials that facilitate more than a dozen replicates per subject. 
+The result are more precise individual-level estimates. 
+Third, we systematically investigated the psychometric properties of the new task. 
+Finally, to validate the task, we studied how it relates to aspects of children's everyday experience.
+
+Designing this task required a new testing infrastructure. 
+We designed the task as an interactive browser-based web app. 
+This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis. 
+Furthermore, because the task is largely self-contained, it is much more controlled and standardized. 
+Most importantly perhaps, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed). 
+As such, it provides a solid basis to study individual differences in gaze cue understanding across ages at scale. 
+We make the task and its source code openly accessible for other researchers to use and modify.
 
@@
 ## Implementation
-Our balloon finding task is presented as an interactive web app.
-The task is portable across devices and web browsers and does not require any installation.
-An advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
 The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
@@
 
+- benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
+
+From previous intro potentially: 
+- @hedge2018reliability section on reliability paradox
+- Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual].
+This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations]. 
+- Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic].
+Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual].
+
 ## Limitations
 ## Future development / extending the task
+- benefits of task battery
 

### 2022-05-23 paper/manuscript.tex
incorporate Manuels feedback

--- 2022-05-23 paper/manuscript.tex
@@
   pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Luke Maurits1, Steven Kalinke1, \& Daniel M. Haun1},
+  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
   pdflang={en-EN},
@@
 \title{Measuring individual differences in the understanding of gaze cues across the lifespan}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
 \date{}
@@
 
-Social cognition - representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
-In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C.
-Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
-
-One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
+Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
+In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
+Yet, there are always individual differences.
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions
+(Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
+
+Numerous studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
+These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome (for an overview, see Repacholi, 2003).
+Studies on social-cognitive abilities and family influences include the effect of parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce et al., 2014), and family background as parental education, occupation, sibling interaction and childcare (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991).
+Another group of individual differences studies focuses on the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Carlson \& Moses, 2001; Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007; Milligan, Astington, \& Dack, 2007; Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
+Studies on social behavioral outcomes measured the interplay of social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), stereotypes and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).
+
+However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016).
+This might be because traditional measures of social cognition are not designed to capture variation between children:
+they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+A recent review showed that many social cognition measures fail to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they do -- show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+
+To give an example: perhaps the most commonly applied prototypical measure for social cognition is the change-of-location false belief task (Baron-Cohen, Leslie, \& Frith, 1985; Wimmer \& Perner, 1983).
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
@@
 Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
+
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (Repacholi, 2003).
+Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
-Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.
-
-Although humans substantially differ in their behavior, thoughts, and motivations, researchers often regard variability as cumbersome or reinterpret it as error variance, therefore neglecting and trivializing individual differences (Kidd, Donnelly, \& Christiansen, 2018).
-Consequently, little consensus has been reached on the interrelation or independence of social-cognitive abilities (termed `structure of social cognition' by Happé, Cook, \& Bird, 2017).
-
-However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
-For example, those identifiers could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
-Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
-For this endeavor, we need to take individual differences seriously -- both theoretically and methodologically.
-
-Some studies have already examined individual differences in social cognition (Hughes \& Devine, 2015; Slaughter, 2015).
-Previous studies focused, for example,
-on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011),
-emotion, language, family interaction, and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
-stereotypes and theory of mind (Rizzo \& Killen, 2018),
-prosociality and theory of mind (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
-executive functions and theory of mind (Buttelmann, Kühn, \& Zmyj, 2021; Carlson, Moses, \& Claxton, 2004),
-parenting practices and theory of mind (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013),
-agency and moral cognition (Sodian et al., 2016),
-attachment quality and gaze following (Astor et al., 2020),
-language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017),
-and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
-Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007; Underwood, 1975).
-
-Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related (e.g., Sodian et al., 2016).
-This might be because traditional measures of social cognition are not designed to capture variation between children:
-they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
-The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed ``reliability paradox'').
-Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
-A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
-
-Even studies focusing on individual differences often use behavioral forced-choice paradigms {[}e.g., carlson2004individual; Walker (2005){]}.
-Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
-This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
-This has profound implications for what these studies can show.
-Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
-
-Therefore, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
+This has profound implications for what studies on individual differences using this task (or others) can show.
+Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
+
+Thus, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
 To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
@@
 Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
-They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates.
-In valid and reliable tasks, differences in test scores should correspond to differences in the social-cognitive ability and systematically order individuals in the same way.
-Additionally, tasks should allow for use within an fMRI scanner.
-With an easily administrable test procedure, larger sample sizes can be collected to estimate the potentially small effect of inter-individual differences.
-
-Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
-Schaafsma et al. (2015) proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.
-
-Another goal in creating new tasks should be to focus on the face value:
-we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
-The task should serve as a proxy for behavior as it appears in the real world.
-Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.
-
-Therefore, we aim to make individual differences measurable in a systematic and reliable way.
-We want to create a task that induces variation between children to get precise person-specific estimates.
-To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject.
-A standardized, easily accessible test procedure helps us to enable data collection at scale.
-Since data collection with families requires much organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision.
-
-In our first novel task, we concentrate on the fundamental ability that is involved in many social-cognitive reasoning processes:
-gaze cue understanding - the ability to locate and use the attentional focus of an agent.
-The first component of this ability is often termed gaze following - turning one's eyes in the same direction as the gaze of another agent - and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
-Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535).
-In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} - therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
+New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
+Another goal in creating new tasks should be to focus on ``face value'':
+measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
+The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).
+
+\hypertarget{a-new-measure-of-gaze-understanding}{%
+\section{A new measure of gaze understanding}\label{a-new-measure-of-gaze-understanding}}
+
+Our goal was to design a new measure of social cognition that captures individual differences in a systematic and reliable way.
+We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes:
+gaze cue understanding -- the ability to locate and use the attentional focus of an agent.
+The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent --
+and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
+Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
+In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+
+To address the psychometric shortcoming of earlier work, we implemented the following design features:
+First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages.
+Second, we designed short trials that facilitate more than a dozen replicates per subject.
+The result are more precise individual-level estimates.
+Third, we systematically investigated the psychometric properties of the new task.
+Finally, to validate the task, we studied how it relates to aspects of children's everyday experience.
+
+Designing this task required a new testing infrastructure.
+We designed the task as an interactive browser-based web app.
+This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
+Furthermore, because the task is largely self-contained, it is much more controlled and standardized.
+Most importantly perhaps, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
+As such, it provides a solid basis to study individual differences in gaze cue understanding across ages at scale.
+We make the task and its source code openly accessible for other researchers to use and modify.
 
@@
 
-Our balloon finding task is presented as an interactive web app.
-The task is portable across devices and web browsers and does not require any installation.
-An advantage of online testing is that our testing procedure is standardized across participants.
-By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study.
 The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-Pronk et al.
-(2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 In addition, we calculated three index scores.
-First, we calculated a sibling variety score according to Candida C.
-Peterson (2000).
+First, we calculated a sibling variety score according to Peterson (2000).
 Second, we implemented the modified version of Cassidy et al.
@@
 
+\begin{itemize}
+\tightlist
+\item
+  benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
+\end{itemize}
+
+From previous intro potentially:
+- Hedge et al. (2018) section on reliability paradox
+- Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
+This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
+- Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
+Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
+
 \hypertarget{limitations}{%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-benson2012individual}{}}%
+Benson, J., Sabbagh, M., Carlson, S., \& Zelazo, P.
+(2012).
+Individual {Differences} in {Executive Functioning Predict Preschoolers}' {Improvement From Theory-of-Mind Training}.
+\emph{Developmental Psychology}, \emph{49}.
+\url{https://doi.org/10.1037/a0031056}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-carlson2001individual}{}}%
+Carlson, S., \& Moses, L. J. (2001). Individual {Differences} in {Inhibitory Control} and {Children}'s {Theory} of {Mind}. \emph{Child Development}, \emph{72}(4), 1032--1053.
+
 \leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
-Carlson, S.
-M., Moses, L.
+Carlson, S., Moses, L.
 J., \& Claxton, L.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
+McEwen, F., Happé, F., Bolton, P., Rijsdijk, F., Ronald, A., Dworzynski, K., \& Plomin, R.
+(2007).
+Origins of individual differences in imitation: Links with language, pretend play, and socially insightful behavior in two-year-old twins.
+\emph{Child Development}, \emph{78}(2), 474--492.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01010.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-milligan2007language}{}}%
+Milligan, K., Astington, J.
+W., \& Dack, L.
+A.
+(2007).
+Language and {Theory} of {Mind}: {Meta-Analysis} of the {Relation Between Language Ability} and {False-belief Understanding}.
+\emph{Child Development}, \emph{78}(2), 622--646.
+\url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
-Peterson, Candida C.
-(2000).
-Kindred spirits: {Influences} of siblings' perspectives on theory of mind.
-\emph{Cognitive Development}, \emph{15}(4), 435--455.
-\url{https://doi.org/10.1016/S0885-2014(01)00040-5}
+Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
 
 \leavevmode\vadjust pre{\hypertarget{ref-peterson2012mind}{}}%
-Peterson, Candida C., Wellman, H.
+Peterson, Wellman, H.
 M., \& Slaughter, V.
@@
 Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-repacholi2003introduction}{}}%
+Repacholi, V. S. \&. B. (2003). Introduction {Individual Differences} in {Theory} of {Mind}: {What Are We Investigating}? In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysisa}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysis}{}}%
 Wellman, H.
@@
 (2001).
-Meta-{Analysis} of {Theory-of-Mind Development}: {The Truth} about {False Belief}.
-\emph{Child Development}, \emph{72}(3), 655--684.
+Meta-analysis of theory-of-mind development: {The} truth about false belief.
+\emph{Child Development}, \emph{72}, 655--684.
 \url{https://doi.org/10.1111/1467-8624.00304}
 
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scalinga}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
 Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wimmer1983beliefs}{}}%
+Wimmer, H., \& Perner, J.
+(1983).
+Beliefs about beliefs: {Representation} and constraining function of wrong beliefs in young children's understanding of deception.
+\emph{Cognition}.
+\url{https://doi.org/10.1016/0010-0277(83)90004-5}
 
@@
 For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
-First, we followed the approach by Candida C.
-Peterson (2000).
+First, we followed the approach by Peterson (2000).
 Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
@@
 (2005).
-The authors adjusted the original score of Candida C.
-Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
+The authors adjusted the original score of Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
 Twins with additional siblings scored depending on the age and number of their siblings.
@@
 The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
-However, teenage siblings might provide opportunities for interesting discussions (Candida C.
-Peterson, 2000).
+However, teenage siblings might provide opportunities for interesting discussions (Peterson, 2000).
 

### 2022-06-08 paper/manuscript.Rmd
starting discussion section

@@
 title             : "Measuring individual differences in the understanding of gaze cues across the lifespan"
-shorttitle        : "Gaze cue understanding"
+shorttitle        : "gaze understanding"
 
@@
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-   We designed a balloon-finding task to study social cognition in young children and adults to approach this issue.
-We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding – the ability to locate and use the attentional focus of an agent.
+   We designed a gaze understanding task to study social cognition in young children and adults to approach this issue.
+We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding – the ability to locate and use the attentional focus of an agent.
 Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
@@
 High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze cue understanding relates to children's real-life social surroundings.
+Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze understanding relates to children's real-life social surroundings.
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
@@
 they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent review showed that many social cognition measures fail to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they do -- show poor test-retest reliability [@mayes1996testretest].
+A recent review showed that many atudies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].
 
@@
 @schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms. 
-They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
+They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
 New tasks should induce variation across age groups, including older children and adults [@repacholi2003introduction]. 
@@
 
-Our goal was to design a new measure of social cognition that captures individual differences in a systematic and reliable way. 
+Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way. 
 We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes: 
-gaze cue understanding -- the ability to locate and use the attentional focus of an agent. 
+gaze understanding -- the ability to locate and use the attentional focus of an agent. 
 The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- 
@@
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535]. 
-In our definition, gaze cue understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
 
@@
 Most importantly perhaps, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed). 
-As such, it provides a solid basis to study individual differences in gaze cue understanding across ages at scale. 
+As such, it provides a solid basis to study individual differences in gaze understanding across ages at scale. 
 We make the task and its source code openly accessible for other researchers to use and modify.
@@
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(B) Hedge version (continuous) of the balloon finding task.
+(B) Hedge version (continuous) of the gaze understanding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
+(C) Box version (discrete) of the gaze understanding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
 
@@
 # Individual differences
-Our first aim was to assess whether our balloon finding task induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode influences responses.
@@
 
-To estimate the developmental trajectory of gaze cue understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
@@
 
-As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable.
+As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
 We assessed internal consistency (split-half reliability) and test-retest reliability.
@@
 
-We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
+We found that our gaze understanding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
 For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G and H.
@@
 # Validity
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment.
+Our third aim was to assess whether the captured individual variation in gaze understanding relates to factors in children's real live social environment.
 Previous studies found associations between social cognition measures and various environmental factors [@devine2018family; @hughes2004links], including family background and education [@cutting1999theory; bulgarelli2016social], number and age of siblings and family constellation [@zhang2021worse, @cassidy2005theory; @perner1994theory; @peterson2000kindred], interaction with siblings [@dunn1991young], and centre-based childcare [@bulgarelli2016social].
 It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
+Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
 
@@
 ## Analysis
-To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
+To estimate the effects of social surrounding on gaze understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
 The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
+Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the gaze understanding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
 In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
@@
 with the estimates of age being $\beta$ =`r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being $\beta$ =`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version $\beta$ =`r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
-Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
 The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
@@
 
-(ref:figlab4) **External validity of the balloon finding task**. 
+(ref:figlab4) **External validity of the gaze understanding task**. 
 Factors of children's social surroundings and their influence on the probability of responding correctly.
@@
 ## Discussion
-We found that factors of children's social surrounding influenced their gaze cue understanding.
+We found that factors of children's social surrounding influenced their gaze understanding.
 Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
 Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
-Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.
+Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze understanding.
 
 # Discussion
-We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike.
-Our results suggest that the measured variation is systematic during the course of the same and different test days.
-Impressively, gaze cue understanding as measured by our task related to factors in children's everyday life experience.
-
-- benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
-
-From previous intro potentially: 
+We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding. 
+Participants are asked to locate a balloon by using the gaze cues of another agent. 
+The outcome measure depends on the presented study version: 
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
+The cartoon-like presentation makes the task engaging for children and adults alike.
+
+First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person. 
+Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates. 
+Finally, we found that gaze understanding relates to aspects of children's everyday experience.
+The web app (https://ccp-odc.eva.mpg.de/gafo-demo/) and its source code (https://github.com/ccp-eva/gafo-demo) are openly accessible.
+We want to highlight that researchers are welcome to use and modify our task according to their needs.
+
+- summary (so als ob die leute nix gelesen hätten)
+  - continuous
+  - across age, adults nochmal aufgreifen
+  - good reliability
+
+## Comparing our study versions
+Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version. 
+Both study versions exhibit high retest reliability. 
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates [cf. @hughes2000good improved reliability through aggregation]. 
+With respect to psychometric properties, we would recommend the use of the continuous version. 
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
+In addition, researchers could induce different levels of salience for each box.
+Our task could consequently be used to study bias, preferences and diverse desires (e.g.
+matching the box appearance to some feature of the agent).
+
+## Online implementation
+For our task, we designed a new testing infrastructure. 
+The gaze understanding task is presented as an interactive web app. 
+This enables presentation across devices without any prior installation. 
+Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
+Consequently, individual-level estimates are more precise. 
+Stimuli presentation is achieved through the use of SVGs. This has several advantages: 
+the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays. 
+Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
+Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
+
+## Comparing data collection modes
+Participants can be tested in-person with supervision or remotely at home. 
+Test instructions are standardized and, with prior informed consent, the webcam records study participation.
+This allows us to scale up data collection: testing is flexible, fast and requires no further experimenter training. 
+We compared children participating in-person, supervised in kindergartens with children participated remotely at home. 
+Our results suggest a comparable developmental trajectory of gaze understanding in both samples. 
+Children in the remote sample are slightly more precise. 
+This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Appendix XXX). 
+Therefore, we recommend using a tablet for remote data collection. 
+Children can then click for themselves and caregivers have less chance to interfere.
+
+## Validity
+Validity is often assessed by looking at concurrent relations between measures.
+Here we looked at a relation that is often postulated for social cognition tasks, namely that social-cognitive ability is predicted by family level variables.
+We found that children's gaze understanding relates to factors of their social environment: 
+children were more accurate, the more social exposure and the more diverse their surrounding was.
+However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items. 
+We hope that future technological advances will enable continuous measures of children's real life social surroundings [@barr2020screen; @long2020detecting, @rogoff2018importance].
+
+## Future research
+Even though aggregate scores seem to improve reliability estimates [cf. @hughes2000good], they may smooth out noise that could be attributed to individual differences. 
+As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are. 
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity. 
+A potentially promising approach are computational cognitive models. 
+We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and interpretable manner. 
+Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual].
+
+Adding complexity to our gaze understanding task might increase individual differences in an adult sample. 
+Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+By inducing more between-person variance, reliability estimates could further increase.
+
+Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities. 
+We aim at creating a task battery to study individual differences in various aspects of social cognition. 
+As @schaafsma2015deconstructing pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries.
+We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
+
+- conclusion:
+  - big picture
+  - ind diff important for ..., good measures needed
+  - dedicated measures of ind diff instead of simply using well-established. reliability    paradox paper zitieren
+  - task & infrastructure
+  - foundations for more precise measures for cognitive development
+
+---
+We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding. 
+The task is presented as an interactive web app that does not require any prior installation and works across devices. 
+Data collection is enabled at scale, with supervised and remote testing and standardized test instructions.
+Stimuli presentation is achieved through the use of SVGs which has several advantages: 
+the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays. 
+Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
+
+In our task, participants are asked to locate a balloon by using the gaze cues of another agent. 
+Therefore, participants need to follow the agent's gaze and act according to this social cue. 
+The outcome measure depends on the presented study version: 
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
+Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
+The cartoon-like presentation makes the task engaging for children and adults alike.
+
+First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person. 
+Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates. 
+Finally, we found that gaze understanding relates to aspects of children's everyday experience.
+The web app (https://ccp-odc.eva.mpg.de/gafo-demo/) and its source code (https://github.com/ccp-eva/gafo-demo) are openly accessible.
+We want to highlight that researchers are welcome to use and modify our task according to their needs.
+
+- From previous intro potentially: 
   - @hedge2018reliability section on reliability paradox
@@
 Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual].
-
-## Limitations
-## Future development / extending the task
-- benefits of task battery
-
-# Conclusion
 
@@
 #### Scoring of sibling variety scores
-For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature. 
+For assessing the external validity of our gaze understanding task, we calculated two sibling variety scores based on the existing Theory of Mind literature. 
 First, we followed the approach by @peterson2000kindred.
@@
 ### Study 1 - Validation hedge version
-The aim of Study 1 was to validate the hedge version of our balloon finding task.
+The aim of Study 1 was to validate the hedge version of our gaze understanding task.
 The pre-registration can be found here: https://osf.io/r3bhn.
@@
 ### Study 3 - Reliability hedge version
-In study 3 and 4, we assessed the test-retest reliability of our balloon-finding task in an adult sample.
+In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
 The pre-registration can be found here: https://osf.io/nu62m.

### 2022-06-08 paper/manuscript.tex
starting discussion section

@@
 
-\shorttitle{Gaze cue understanding}
+\shorttitle{gaze understanding}
 
@@
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-We designed a balloon-finding task to study social cognition in young children and adults to approach this issue.
-We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding -- the ability to locate and use the attentional focus of an agent.
+We designed a gaze understanding task to study social cognition in young children and adults to approach this issue.
+We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
 Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
@@
 they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent review showed that many social cognition measures fail to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they do -- show poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+A recent review showed that many atudies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
 
@@
 Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
-They advocated for parametric measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
+They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
 New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
@@
 
-Our goal was to design a new measure of social cognition that captures individual differences in a systematic and reliable way.
+Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
 We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes:
-gaze cue understanding -- the ability to locate and use the attentional focus of an agent.
+gaze understanding -- the ability to locate and use the attentional focus of an agent.
 The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent --
@@
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
-In our definition, gaze cue understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+In our definition, gaze understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
 
@@
 Most importantly perhaps, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
-As such, it provides a solid basis to study individual differences in gaze cue understanding across ages at scale.
+As such, it provides a solid basis to study individual differences in gaze understanding across ages at scale.
 We make the task and its source code openly accessible for other researchers to use and modify.
@@
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
+(C) Box version (discrete) of the gaze understanding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
 \end{figure}
@@
 
-Our first aim was to assess whether our balloon finding task induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode influences responses.
@@
 
-To estimate the developmental trajectory of gaze cue understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
@@
 
-Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.32; 95\% CI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CI {[}-0.49; -0.14{]}) were negative and reliably different from zero.
-In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CI {[}0.69; 1.57{]}) were positive and reliably different from zero.
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CI {[}-0.50; -0.14{]}) were negative and reliably different from zero.
+In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode (\(\beta\) = 1.11 (95\% CI {[}0.68; 1.56{]}) were positive and reliably different from zero.
 Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
@@
 Participants were recruited in the same way as in the previous study. The child sample consisted of
-106 children, including
-35 3-year-olds
-(mean = 42.57 months,
-SD = 2.98,
-range = 38
+120 children, including
+41 3-year-olds
+(mean = 42.34 months,
+SD = 3.10,
+range = 37
 - 47,
-17 girls),
-38 4-year-olds
-(mean = 53.77 months,
-SD = 3.16,
+20 girls),
+41 4-year-olds
+(mean = 53.76 months,
+SD = 3.15,
 range = 48
 - 59,
-20 girls),
-and 33 5-year-olds
-(mean = 66.12 months,
-SD = 3.36,
-range = 61
+21 girls),
+and 38 5-year-olds
+(mean = 66.05 months,
+SD = 3.40,
+range = 60
 - 71,
-17 girls).
+19 girls).
 
@@
 
-We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
+We found that our gaze understanding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
 For the internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G and H.
@@
 
-The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.90 (95\% CI {[}0.68;1.00{]}).
-In the box version it was 0.92 (95\% CI {[}0.70;1.00{]}).
+The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.89 (95\% CI {[}0.65;1.00{]}).
+In the box version it was 0.91 (95\% CI {[}0.71;1.00{]}).
 
@@
 
-Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment.
+Our third aim was to assess whether the captured individual variation in gaze understanding relates to factors in children's real live social environment.
 Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018; Hughes \& Leekam, 2004), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016).
 It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
+Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
 
@@
 For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
-137 children, including
-42 3-year-olds
-(mean = 43.04 months,
-SD = 3.25,
+109 children, including
+30 3-year-olds
+(mean = 41.82 months,
+SD = 3.31,
 range = 36
 - 47,
-23 girls),
-46 4-year-olds
-(mean = 54.43 months,
-SD = 2.76,
+19 girls),
+36 4-year-olds
+(mean = 54.32 months,
+SD = 2.95,
 range = 48
 - 59,
-34 girls),
-and 49 5-year-olds
-(mean = 66.25 months,
-SD = 3.47,
+27 girls),
+and 43 5-year-olds
+(mean = 66.43 months,
+SD = 3.48,
 range = 60
 - 71,
-27 girls).
+22 girls).
 
@@
 
-To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
+To estimate the effects of social surrounding on gaze understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
 The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
+Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the gaze understanding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
 In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
@@
 with the estimates of age being \(\beta\) =0.57 (95\% CI {[}0.38; 0.77{]}), data collection mode being \(\beta\) =0.95 (95\% CI {[}0.56; 1.35{]}), and study version \(\beta\) =1.87 (95\% CI {[}0.25; 3.59{]}).
-Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding.
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
 The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
@@
 
-\caption{\textbf{External validity of the balloon finding task}.
+\caption{\textbf{External validity of the gaze understanding task}.
 Factors of children's social surroundings and their influence on the probability of responding correctly.
@@
 
-We found that factors of children's social surrounding influenced their gaze cue understanding.
+We found that factors of children's social surrounding influenced their gaze understanding.
 Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
 Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
-Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.
+Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze understanding.
 
@@
 
-We were able to show that our balloon finding task measures inter-individual variation between children and adults, alike.
-Our results suggest that the measured variation is systematic during the course of the same and different test days.
-Impressively, gaze cue understanding as measured by our task related to factors in children's everyday life experience.
+We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding.
+Participants are asked to locate a balloon by using the gaze cues of another agent.
+The outcome measure depends on the presented study version:
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
+The cartoon-like presentation makes the task engaging for children and adults alike.
+
+First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
+Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
+Finally, we found that gaze understanding relates to aspects of children's everyday experience.
+The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are openly accessible.
+We want to highlight that researchers are welcome to use and modify our task according to their needs.
 
@@
 \item
-  benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
-\end{itemize}
-
-From previous intro potentially:
-- Hedge et al. (2018) section on reliability paradox
-- Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
-This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
-- Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
-
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
-
-\hypertarget{future-development-extending-the-task}{%
-\subsection{Future development / extending the task}\label{future-development-extending-the-task}}
+  summary (so als ob die leute nix gelesen hätten)
 
@@
   \item
-  benefits of task battery
+    continuous
+  \item
+    across age, adults nochmal aufgreifen
+  \item
+    good reliability
   \end{itemize}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\end{itemize}
+
+\hypertarget{comparing-our-study-versions}{%
+\subsection{Comparing our study versions}\label{comparing-our-study-versions}}
+
+Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
+Both study versions exhibit high retest reliability.
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al., 2000 improved reliability through aggregation).
+With respect to psychometric properties, we would recommend the use of the continuous version.
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
+In addition, researchers could induce different levels of salience for each box.
+Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature of the agent).
+
+\hypertarget{online-implementation}{%
+\subsection{Online implementation}\label{online-implementation}}
+
+For our task, we designed a new testing infrastructure.
+The gaze understanding task is presented as an interactive web app.
+This enables presentation across devices without any prior installation.
+Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
+Consequently, individual-level estimates are more precise.
+Stimuli presentation is achieved through the use of SVGs. This has several advantages:
+the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
+Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
+Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
+
+\hypertarget{comparing-data-collection-modes}{%
+\subsection{Comparing data collection modes}\label{comparing-data-collection-modes}}
+
+Participants can be tested in-person with supervision or remotely at home.
+Test instructions are standardized and, with prior informed consent, the webcam records study participation.
+This allows us to scale up data collection: testing is flexible, fast and requires no further experimenter training.
+We compared children participating in-person, supervised in kindergartens with children participated remotely at home.
+Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
+Children in the remote sample are slightly more precise.
+This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Appendix XXX).
+Therefore, we recommend using a tablet for remote data collection.
+Children can then click for themselves and caregivers have less chance to interfere.
+
+\hypertarget{validity-1}{%
+\subsection{Validity}\label{validity-1}}
+
+Validity is often assessed by looking at concurrent relations between measures.
+Here we looked at a relation that is often postulated for social cognition tasks, namely that social-cognitive ability is predicted by family level variables.
+We found that children's gaze understanding relates to factors of their social environment:
+children were more accurate, the more social exposure and the more diverse their surrounding was.
+However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items.
+We hope that future technological advances will enable continuous measures of children's real life social surroundings Rogoff, Dahl, \& Callanan (2018).
+
+\hypertarget{future-research}{%
+\subsection{Future research}\label{future-research}}
+
+Even though aggregate scores seem to improve reliability estimates (cf. Hughes et al., 2000), they may smooth out noise that could be attributed to individual differences.
+As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
+A potentially promising approach are computational cognitive models.
+We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and interpretable manner.
+Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).
+
+Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
+Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+By inducing more between-person variance, reliability estimates could further increase.
+
+Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
+We aim at creating a task battery to study individual differences in various aspects of social cognition.
+As Schaafsma et al.
+(2015) pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries.
+We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
+
+\begin{itemize}
+\tightlist
+\item
+  conclusion:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    big picture
+  \item
+    ind diff important for \ldots, good measures needed
+  \item
+    dedicated measures of ind diff instead of simply using well-established. reliability paradox paper zitieren
+  \item
+    task \& infrastructure
+  \item
+    foundations for more precise measures for cognitive development
+  \end{itemize}
+\end{itemize}
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding.
+The task is presented as an interactive web app that does not require any prior installation and works across devices.
+Data collection is enabled at scale, with supervised and remote testing and standardized test instructions.
+Stimuli presentation is achieved through the use of SVGs which has several advantages:
+the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
+Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
+
+In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
+Therefore, participants need to follow the agent's gaze and act according to this social cue.
+The outcome measure depends on the presented study version:
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
+Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
+The cartoon-like presentation makes the task engaging for children and adults alike.
+
+First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
+Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
+Finally, we found that gaze understanding relates to aspects of children's everyday experience.
+The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are openly accessible.
+We want to highlight that researchers are welcome to use and modify our task according to their needs.
+
+\begin{itemize}
+\tightlist
+\item
+  From previous intro potentially:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Hedge et al. (2018) section on reliability paradox
+  \item
+    Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
+    This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
+  \item
+    Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
+    Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
+  \end{itemize}
+\end{itemize}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-barr2020screen}{}}%
+Barr, R., Kirkorian, H., Radesky, J., Coyne, S., Nichols, D., Blanchfield, O., \ldots{} Fitzpatrick, caroline.
+(2020).
+Beyond {Screen Time}: {A Synergistic Approach} to a {More Comprehensive Assessment} of {Family Media Exposure During Early Childhood}.
+\emph{Frontiers in Psychology}, \emph{11}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2013early}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2022individual}{}}%
+Bohn, M., Tessler, M.
+H., Kordt, C., Hausmann, T., \& Frank, M.
+C.
+(2022).
+\emph{An individual differences perspective on the development of pragmatic abilities in the preschool years}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/s2e3p}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
@@
 \url{https://doi.org/10.1037//0012-1649.34.3.525}
+
+\leavevmode\vadjust pre{\hypertarget{ref-long2020detecting}{}}%
+Long, B., Kachergis, G., Agrawal, K., \& Frank, M.
+C.
+(2020).
+\emph{Detecting social information in a dense dataset of infants' natural visual experience} {[}Preprint{]}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/z7tdg}
 
@@
 \url{https://doi.org/10.1037/dev0000439}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rogoff2018importance}{}}%
+Rogoff, B., Dahl, A., \& Callanan, M. (2018). The importance of understanding children's lived experience. \emph{Developmental Review}, \emph{50}, 5--15. \url{https://doi.org/10.1016/j.dr.2018.05.006}
 
@@
 
-For assessing the external validity of our balloon finding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
+For assessing the external validity of our gaze understanding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
 First, we followed the approach by Peterson (2000).
@@
 
-The aim of Study 1 was to validate the hedge version of our balloon finding task.
+The aim of Study 1 was to validate the hedge version of our gaze understanding task.
 The pre-registration can be found here: \url{https://osf.io/r3bhn}.
@@
 
-In study 3 and 4, we assessed the test-retest reliability of our balloon-finding task in an adult sample.
+In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
 The pre-registration can be found here: \url{https://osf.io/nu62m}.

### 2022-08-09 paper/manuscript.Rmd
save last state before dropping vali section

@@
 It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the predictive validity of our measure.
+Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the validity of our measure.
 
@@
 
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)", fig.show='asis'}
 knitr::include_graphics("../figures/extvali_results.png")
@@
 
-# Discussion
-We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding. 
-Participants are asked to locate a balloon by using the gaze cues of another agent. 
-The outcome measure depends on the presented study version: 
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
-The cartoon-like presentation makes the task engaging for children and adults alike.
-
+# General Discussion
+In this paper, we presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan. 
+This paper contributes to methodological advances in developmental psychology in the following ways. 
 First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person. 
-Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Second, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
 Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates. 
@@
 
-- summary (so als ob die leute nix gelesen hätten)
-  - continuous
-  - across age, adults nochmal aufgreifen
-  - good reliability
-
-## Comparing our study versions
+One of the main contributions of this paper is that our newly presented gaze understanding task induces variation between participants. 
+This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
+Our experimental design enables a continuous outcome measure, which again quantifies individual differences.
+
+In our task, participants are asked to locate a balloon by using the gaze cues of another agent. 
+The outcome measure depends on the presented study version: 
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
 Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version. 
 Both study versions exhibit high retest reliability. 
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates [cf. @hughes2000good improved reliability through aggregation]. 
-With respect to psychometric properties, we would recommend the use of the continuous version. 
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates [cf. @hughes2000good; improved reliability through aggregation]. 
+When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency. 
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
@@
 matching the box appearance to some feature of the agent).
-
-## Online implementation
-For our task, we designed a new testing infrastructure. 
-The gaze understanding task is presented as an interactive web app. 
+In sum, our task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.
+
+In addition to the new task design itself, we designed a new testing infrastructure. 
+Our gaze understanding task is presented as an interactive web app. 
 This enables presentation across devices without any prior installation. 
-Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
-Consequently, individual-level estimates are more precise. 
 Stimuli presentation is achieved through the use of SVGs. This has several advantages: 
@@
 Presented agents and objects can be easily adapted for future task modifications or specific cultural settings. 
-
-## Comparing data collection modes
+The cartoon-like presentation makes the task engaging for children and adults alike.
+
 Participants can be tested in-person with supervision or remotely at home. 
@@
 
-## Validity
+After finding consistent and reliable individual estimates, we aimed at verifying the appropriateness of our new task.
 Validity is often assessed by looking at concurrent relations between measures.
@@
 However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items. 
-We hope that future technological advances will enable continuous measures of children's real life social surroundings [@barr2020screen; @long2020detecting, @rogoff2018importance].
+We hope that future technological advances will enable continuous measures of children's real life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
 
@@
 
-- conclusion:
+# Limitations
+
+# Conclusion
   - big picture

### 2022-08-09 paper/manuscript.tex
save last state before dropping vali section

@@
 
-\hypertarget{discussion-3}{%
-\section{Discussion}\label{discussion-3}}
-
-We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding.
-Participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version:
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
-The cartoon-like presentation makes the task engaging for children and adults alike.
-
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
+
+In this paper, we presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
+This paper contributes to methodological advances in developmental psychology in the following ways.
 First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
-Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
+Second, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
 Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
@@
 
-\begin{itemize}
-\tightlist
-\item
-  summary (so als ob die leute nix gelesen hätten)
-
-  \begin{itemize}
-  \tightlist
-  \item
-    continuous
-  \item
-    across age, adults nochmal aufgreifen
-  \item
-    good reliability
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{comparing-our-study-versions}{%
-\subsection{Comparing our study versions}\label{comparing-our-study-versions}}
-
+One of the main contributions of this paper is that our newly presented gaze understanding task induces variation between participants.
+This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
+Our experimental design enables a continuous outcome measure, which again quantifies individual differences.
+
+In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
+The outcome measure depends on the presented study version:
+in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
 Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
 Both study versions exhibit high retest reliability.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al., 2000 improved reliability through aggregation).
-With respect to psychometric properties, we would recommend the use of the continuous version.
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates {[}cf.
+Hughes et al.
+(2000); improved reliability through aggregation{]}.
+When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
@@
 Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature of the agent).
-
-\hypertarget{online-implementation}{%
-\subsection{Online implementation}\label{online-implementation}}
-
-For our task, we designed a new testing infrastructure.
-The gaze understanding task is presented as an interactive web app.
+In sum, our task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.
+
+In addition to the new task design itself, we designed a new testing infrastructure.
+Our gaze understanding task is presented as an interactive web app.
 This enables presentation across devices without any prior installation.
-Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
-Consequently, individual-level estimates are more precise.
 Stimuli presentation is achieved through the use of SVGs. This has several advantages:
@@
 Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
-
-\hypertarget{comparing-data-collection-modes}{%
-\subsection{Comparing data collection modes}\label{comparing-data-collection-modes}}
+The cartoon-like presentation makes the task engaging for children and adults alike.
 
@@
 
-\hypertarget{validity-1}{%
-\subsection{Validity}\label{validity-1}}
-
+After finding consistent and reliable individual estimates, we aimed at verifying the appropriateness of our new task.
 Validity is often assessed by looking at concurrent relations between measures.
@@
 However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items.
-We hope that future technological advances will enable continuous measures of children's real life social surroundings Rogoff, Dahl, \& Callanan (2018).
+We hope that future technological advances will enable continuous measures of children's real life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  conclusion:
+\hypertarget{limitations}{%
+\section{Limitations}\label{limitations}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
   foundations for more precise measures for cognitive development
-  \end{itemize}
 \end{itemize}

### 2022-08-09 stats/analysis.Rmd
save last state before dropping vali section

@@
 library(ggdist)
+library(parallel) # for mclapply in splithalf reli
 
@@
   ) %>% 
-  select(subjID, age, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)
+  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)
 
@@
 saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")
+
+pp_check(mAgeHedge) + xlim(0, 10)
+```
+
+```{r GLMM_plot_hedge}
+nd_hedge <- mDataAgeHedge %>% 
+  select(-c(clickDistInBalloons, symmetricPosition, targetPosition))
+
+# extract model predictions for mock data
+pred_hedge <- fitted(mAgeHedge, newdata = nd_hedge, re_formula = NA) %>% as_tibble() %>% bind_cols(mDataAgeHedge)
+
+hedge_variation_plot_GLMM <- ggplot() +
+
+  # use model predictions for smoother
+  geom_smooth(
+    data = pred_hedge, 
+    aes(x = ageInMonths/12, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = datacollection, lty = datacollection), 
+    stat = "identity", size = 0.5, alpha = 0.15, col = "darkgrey",
+  ) +
+
+  geom_point(
+    data = variationHedgeInd %>% filter(sample == "kids"), 
+    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
+  ) +
+
+  geom_pointrange(
+    data = variationHedge %>% filter(sample == "kids"), 
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+  ) +
+
+  scale_shape_manual(values = c(16, 18)) + 
+  scale_alpha_discrete(range = c(1, 0.4)) + 
+  scale_linetype_manual(values = c("solid", "dashed")) +
+
+  # adult data
+  geom_jitter(
+    data = variationHedgeInd %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
+  ) +
+
+  geom_pointrange(
+    data = variationHedge %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
+    size = 0.8,
+  ) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
+  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +
+
+  theme(legend.text = element_text(size = 8),
+        legend.key.size = unit(0.4, "cm"), 
+        legend.direction = "vertical", 
+        legend.box = "horizontal",
+        legend.position = c(0.72, 0.85), 
+        legend.background = element_blank(),
+        legend.box.background = element_rect(colour = "black")
+        )
+
+hedge_variation_plot_GLMM
+
+ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
 ```
@@
   ) %>% 
-  select(subjID, age, datacollection, symmetricPosition, targetPosition, correctBox)
+  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, correctBox)
 
@@
 saveRDS(mAgeBox, "../saves/mAgeBox.rds")
+```
+
+```{r GLMM_plot_box}
+nd_box <- mDataAgeBox %>% 
+  select(-c(correctBox, symmetricPosition, targetPosition))
+
+# extract model predictions for mock data
+pred_box <- fitted(mAgeBox, newdata = nd_box, re_formula = NA) %>% as_tibble() %>% bind_cols(mDataAgeBox)
+
+box_variation_plot_GLMM <- ggplot() +
+
+  # use model predictions for smoother
+  geom_smooth(
+    data = pred_box, 
+    aes(x = ageInMonths/12, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = datacollection, lty = datacollection), 
+    stat = "identity", size = 0.5, alpha = 0.15, col = "darkgrey",
+  ) +
+
+  geom_point(
+    data = variationBoxInd %>% filter(sample == "kids"), 
+    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
+  ) +
+
+  geom_pointrange(
+    data = variationBox %>% filter(sample == "kids"), 
+    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
+  ) +
+
+  scale_shape_manual(values = c(16, 18)) + 
+  scale_alpha_discrete(range = c(1, 0.4)) + 
+  scale_linetype_manual(values = c("solid", "dashed")) +
+
+  # adult data
+  geom_jitter(
+    data = variationHedgeInd %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
+  ) +
+
+  geom_pointrange(
+    data = variationBox %>% filter(sample == "adults"), 
+    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
+    size = 0.8,
+  ) +
+
+  labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
+  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
+  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
+  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
+  theme(legend.position="none")
+
+box_variation_plot_GLMM
+
+ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
 ```
@@
 
-```{r splithalfr_hedge_kids}
+```{r splithalfr_luke}
 fn_score_hedge <- function(ds) {
@@
 
-# first-second half split
-splitscores_hedge_firstsecond_kids <- by_split(
+# random split
+splitscores_hedge_random_kids <- by_split(
   hedge_intCon_data %>% filter(sample == "kids"),
@@
   fn_score_hedge,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F
+  replications = 25,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
 )
 
-hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
-hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
-
+hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
+uniq_reps <- unique(splitscores_hedge_random_kids$replication)
+
+parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_random_kids, replication==r), cor))
+}
+
+hedge_random_kids_ci <- mclapply(uniq_reps, parallel_split_ci, mc.cores=48)
+# Darn R
+
+# create dataframe to save data
 splithalf_data <- tibble(
+  studyversion = "hedge",
   sample = "kids",
-                          studyversion = "hedge", 
-                          method = "first-second", 
+  split = "random",
   stratification = "none",
-                          coefficient = hedge_firstsecond_kids, 
-                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
-                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
-                        )
-
-# first-second half stratified by target position
-splitscores_hedge_firstsecondStrat_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F, 
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
-hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "first-second",
-                                        stratification = "target position",
-                                        coefficient = hedge_firstsecondStrat_kids,
-                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split
-splitscores_hedge_oddeven_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F
-)
-
-hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
-hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "odd-even",
-                                        stratification = "none",
-                                        coefficient = hedge_oddeven_kids,
-                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split stratified by target position
-splitscores_hedge_oddevenStrat_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F, 
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
-hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "odd-even",
-                                        stratification = "target position",
-                                        coefficient = hedge_oddevenStrat_kids,
-                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting (random sampling without replacement)
-splitscores_hedge_permutated_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-)
-
-hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
-hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "permutated",
-                                        stratification = "none",
-                                        coefficient = hedge_permutated_kids,
-                                        CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting stratified by target position
-splitscores_hedge_permutatedStrat_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
-hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "permutated",
-                                        stratification = "target position",
-                                        coefficient = hedge_permutatedStrat_kids,
-                                        CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo (sampling with replacement)
-splitscores_hedge_montecarlo_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-)
-
-hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
-hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "Monte Carlo",
-                                        stratification = "none",
-                                        coefficient = hedge_montecarlo_kids,
-                                        CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo stratified by target position
-splitscores_hedge_montecarloStrat_kids <- by_split(
-  hedge_intCon_data %>% filter(sample == "kids"),
-  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
-hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "hedge", 
-                                        method = "Monte Carlo",
-                                        stratification = "target position",
-                                        coefficient = hedge_montecarloStrat_kids,
-                                        CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
-                                      )
+  mean = hedge_random_kids)
+
+splithalf_data$CI_lower = numeric(nrow(splithalf_data))
+splithalf_data$CI_upper = numeric(nrow(splithalf_data))
+for(i in 1:nrow(splithalf_data)) {
+  splithalf_data$CI_lower[i] <- hedge_random_kids_ci[[i]]$lims["0.025","bca"]
+  splithalf_data$CI_upper[i] <- hedge_random_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+print(splithalf_data)
+# write_csv(splithalf_data, "splithalf_data.csv")
+```
+
+```{r splithalfr_hedge_kids}
+# fn_score_hedge <- function(ds) {
+#   return(mean(ds$clickDistInBalloons, na.rm = TRUE))
+# }
+# 
+# hedge_intCon_data <- reli %>% 
+#   filter(studyversion == "hedge" & reliday == "reliday1")
+# 
+# # first-second half split
+# splitscores_hedge_firstsecond_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
+# hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
+# 
+# splithalf_data <- tibble(
+#                           sample = "kids", 
+#                           studyversion = "hedge", 
+#                           method = "first-second", 
+#                           stratification = "none",                                        
+#                           coefficient = hedge_firstsecond_kids, 
+#                           CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
+#                           CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
+#                         )
+# 
+# # first-second half stratified by target position
+# splitscores_hedge_firstsecondStrat_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
+# hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "first-second",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_firstsecondStrat_kids,
+#                                         CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split
+# splitscores_hedge_oddeven_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
+# hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "odd-even",
+#                                         stratification = "none",
+#                                         coefficient = hedge_oddeven_kids,
+#                                         CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split stratified by target position
+# splitscores_hedge_oddevenStrat_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
+# hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "odd-even",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_oddevenStrat_kids,
+#                                         CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting (random sampling without replacement)
+# splitscores_hedge_permutated_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+# )
+# 
+# hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
+# hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "permutated",
+#                                         stratification = "none",
+#                                         coefficient = hedge_permutated_kids,
+#                                         CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting stratified by target position
+# splitscores_hedge_permutatedStrat_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
+# hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "permutated",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_permutatedStrat_kids,
+#                                         CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo (sampling with replacement)
+# splitscores_hedge_montecarlo_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+# )
+# 
+# hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
+# hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "none",
+#                                         coefficient = hedge_montecarlo_kids,
+#                                         CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo stratified by target position
+# splitscores_hedge_montecarloStrat_kids <- by_split(
+#   hedge_intCon_data %>% filter(sample == "kids"),
+#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
+# hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "hedge", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_montecarloStrat_kids,
+#                                         CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
+#                                       )
 ```
@@
 ```{r splithalfr_hedge_adults}
-# first-second half split
-splitscores_hedge_firstsecond_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F
-)
-
-hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
-hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                              sample = "adults", 
-                                              studyversion = "hedge", 
-                                              method = "first-second", 
-                                              stratification = "none",                                        
-                                              coefficient = hedge_firstsecond_adults, 
-                                              CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
-                                              CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
-                                            )
-
-# first-second half stratified by target position
-splitscores_hedge_firstsecondStrat_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F, 
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
-hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "first-second",
-                                        stratification = "target position",
-                                        coefficient = hedge_firstsecondStrat_adults,
-                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split
-splitscores_hedge_oddeven_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F
-)
-
-hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
-hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "odd-even",
-                                        stratification = "none",
-                                        coefficient = hedge_oddeven_adults,
-                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split stratified by target position
-splitscores_hedge_oddevenStrat_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F, 
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
-hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "odd-even",
-                                        stratification = "target position",
-                                        coefficient = hedge_oddevenStrat_adults,
-                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting (random sampling without replacement)
-splitscores_hedge_permutated_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-)
-
-hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
-hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "permutated",
-                                        stratification = "none",
-                                        coefficient = hedge_permutated_adults,
-                                        CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting stratified by target position
-splitscores_hedge_permutatedStrat_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
-hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "permutated",
-                                        stratification = "target position",
-                                        coefficient = hedge_permutatedStrat_adults,
-                                        CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo (sampling with replacement)
-splitscores_hedge_montecarlo_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-)
-
-hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
-hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "Monte Carlo",
-                                        stratification = "none",
-                                        coefficient = hedge_montecarlo_adults,
-                                        CI_lower = hedge_montecarlo_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_montecarlo_adults_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo stratified by target position
-splitscores_hedge_montecarloStrat_adults <- by_split(
-  hedge_intCon_data %>% filter(sample == "adults"),
-  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_hedge,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
-hedge_montecarloStrat_adults_ci <- split_ci(splitscores_hedge_montecarloStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "hedge", 
-                                        method = "Monte Carlo",
-                                        stratification = "target position",
-                                        coefficient = hedge_montecarloStrat_adults,
-                                        CI_lower = hedge_montecarloStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = hedge_montecarloStrat_adults_ci$lims["0.975","bca"]
-                                      )
+# # first-second half split
+# splitscores_hedge_firstsecond_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
+# hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                               sample = "adults", 
+#                                               studyversion = "hedge", 
+#                                               method = "first-second", 
+#                                               stratification = "none",                                        
+#                                               coefficient = hedge_firstsecond_adults, 
+#                                               CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
+#                                               CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
+#                                             )
+# 
+# # first-second half stratified by target position
+# splitscores_hedge_firstsecondStrat_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
+# hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "first-second",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_firstsecondStrat_adults,
+#                                         CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split
+# splitscores_hedge_oddeven_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
+# hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "odd-even",
+#                                         stratification = "none",
+#                                         coefficient = hedge_oddeven_adults,
+#                                         CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split stratified by target position
+# splitscores_hedge_oddevenStrat_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
+# hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "odd-even",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_oddevenStrat_adults,
+#                                         CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting (random sampling without replacement)
+# splitscores_hedge_permutated_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+# )
+# 
+# hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
+# hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "permutated",
+#                                         stratification = "none",
+#                                         coefficient = hedge_permutated_adults,
+#                                         CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting stratified by target position
+# splitscores_hedge_permutatedStrat_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
+# hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "permutated",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_permutatedStrat_adults,
+#                                         CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo (sampling with replacement)
+# splitscores_hedge_montecarlo_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+# )
+# 
+# hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
+# hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "none",
+#                                         coefficient = hedge_montecarlo_adults,
+#                                         CI_lower = hedge_montecarlo_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_montecarlo_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo stratified by target position
+# splitscores_hedge_montecarloStrat_adults <- by_split(
+#   hedge_intCon_data %>% filter(sample == "adults"),
+#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_hedge,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
+# hedge_montecarloStrat_adults_ci <- split_ci(splitscores_hedge_montecarloStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "hedge", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "target position",
+#                                         coefficient = hedge_montecarloStrat_adults,
+#                                         CI_lower = hedge_montecarloStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = hedge_montecarloStrat_adults_ci$lims["0.975","bca"]
+#                                       )
 ```
@@
 ```{r splithalfr_box_kids}
-fn_score_box <- function(ds) {
-  return(mean(ds$correctBox, na.rm = TRUE))
-}
-
-box_intCon_data <- reli %>% 
-  filter(studyversion == "box" & reliday == "reliday1")
-
-# first-second half split
-splitscores_box_firstsecond_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F
-)
-
-box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
-box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                              sample = "kids", 
-                                              studyversion = "box", 
-                                              method = "first-second", 
-                                              stratification = "none",                                        
-                                              coefficient = box_firstsecond_kids, 
-                                              CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
-                                              CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
-                                            )
-
-# first-second half stratified by target position
-splitscores_box_firstsecondStrat_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F, 
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
-box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "first-second",
-                                        stratification = "target position",
-                                        coefficient = box_firstsecondStrat_kids,
-                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split
-splitscores_box_oddeven_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F
-)
-
-box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
-box_oddeven_kids_ci <- split_ci(splitscores_box_oddeven_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "odd-even",
-                                        stratification = "none",
-                                        coefficient = box_oddeven_kids,
-                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split stratified by target position
-splitscores_box_oddevenStrat_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F, 
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
-box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "odd-even",
-                                        stratification = "target position",
-                                        coefficient = box_oddevenStrat_kids,
-                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting (random sampling without replacement)
-splitscores_box_permutated_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-)
-
-box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
-box_permutated_kids_ci <- split_ci(splitscores_box_permutated_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "permutated",
-                                        stratification = "none",
-                                        coefficient = box_permutated_kids,
-                                        CI_lower = box_permutated_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_permutated_kids_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting stratified by target position
-splitscores_box_permutatedStrat_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
-box_permutatedStrat_kids_ci <- split_ci(splitscores_box_permutatedStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "permutated",
-                                        stratification = "target position",
-                                        coefficient = box_permutatedStrat_kids,
-                                        CI_lower = box_permutatedStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_permutatedStrat_kids_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo (sampling with replacement)
-splitscores_box_montecarlo_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-)
-
-box_montecarlo_kids <- split_coefs(splitscores_box_montecarlo_kids, cor)
-box_montecarlo_kids_ci <- split_ci(splitscores_box_montecarlo_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "Monte Carlo",
-                                        stratification = "none",
-                                        coefficient = box_montecarlo_kids,
-                                        CI_lower = box_montecarlo_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_montecarlo_kids_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo stratified by target position
-splitscores_box_montecarloStrat_kids <- by_split(
-  box_intCon_data %>% filter(sample == "kids"),
-  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-)
-
-box_montecarloStrat_kids <- split_coefs(splitscores_box_montecarloStrat_kids, cor)
-box_montecarloStrat_kids_ci <- split_ci(splitscores_box_montecarloStrat_kids, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "kids", 
-                                        studyversion = "box", 
-                                        method = "Monte Carlo",
-                                        stratification = "target position",
-                                        coefficient = box_montecarloStrat_kids,
-                                        CI_lower = box_montecarloStrat_kids_ci$lims["0.025","bca"], 
-                                        CI_upper = box_montecarloStrat_kids_ci$lims["0.975","bca"]
-                                      )
+# fn_score_box <- function(ds) {
+#   return(mean(ds$correctBox, na.rm = TRUE))
+# }
+# 
+# box_intCon_data <- reli %>% 
+#   filter(studyversion == "box" & reliday == "reliday1") 
+# 
+# # first-second half split
+# splitscores_box_firstsecond_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
+# box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                               sample = "kids", 
+#                                               studyversion = "box", 
+#                                               method = "first-second", 
+#                                               stratification = "none",                                        
+#                                               coefficient = box_firstsecond_kids, 
+#                                               CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
+#                                               CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
+#                                             )
+# 
+# # first-second half stratified by target position
+# splitscores_box_firstsecondStrat_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
+# box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "first-second",
+#                                         stratification = "target position",
+#                                         coefficient = box_firstsecondStrat_kids,
+#                                         CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split
+# splitscores_box_oddeven_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
+# box_oddeven_kids_ci <- split_ci(splitscores_box_oddeven_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "odd-even",
+#                                         stratification = "none",
+#                                         coefficient = box_oddeven_kids,
+#                                         CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split stratified by target position
+# splitscores_box_oddevenStrat_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
+# box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "odd-even",
+#                                         stratification = "target position",
+#                                         coefficient = box_oddevenStrat_kids,
+#                                         CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting (random sampling without replacement)
+# splitscores_box_permutated_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+# )
+# 
+# box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
+# box_permutated_kids_ci <- split_ci(splitscores_box_permutated_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "permutated",
+#                                         stratification = "none",
+#                                         coefficient = box_permutated_kids,
+#                                         CI_lower = box_permutated_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_permutated_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting stratified by target position
+# splitscores_box_permutatedStrat_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
+# box_permutatedStrat_kids_ci <- split_ci(splitscores_box_permutatedStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "permutated",
+#                                         stratification = "target position",
+#                                         coefficient = box_permutatedStrat_kids,
+#                                         CI_lower = box_permutatedStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_permutatedStrat_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo (sampling with replacement)
+# splitscores_box_montecarlo_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+# )
+# 
+# box_montecarlo_kids <- split_coefs(splitscores_box_montecarlo_kids, cor)
+# box_montecarlo_kids_ci <- split_ci(splitscores_box_montecarlo_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "none",
+#                                         coefficient = box_montecarlo_kids,
+#                                         CI_lower = box_montecarlo_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_montecarlo_kids_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo stratified by target position
+# splitscores_box_montecarloStrat_kids <- by_split(
+#   box_intCon_data %>% filter(sample == "kids"),
+#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+# )
+# 
+# box_montecarloStrat_kids <- split_coefs(splitscores_box_montecarloStrat_kids, cor)
+# box_montecarloStrat_kids_ci <- split_ci(splitscores_box_montecarloStrat_kids, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "kids", 
+#                                         studyversion = "box", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "target position",
+#                                         coefficient = box_montecarloStrat_kids,
+#                                         CI_lower = box_montecarloStrat_kids_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_montecarloStrat_kids_ci$lims["0.975","bca"]
+#                                       )
 ```
@@
 ```{r splithalfr_box_adults}
-# first-second half split
-splitscores_box_firstsecond_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F
-)
-
-box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
-box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                              sample = "adults", 
-                                              studyversion = "box", 
-                                              method = "first-second", 
-                                              stratification = "none",                                        
-                                              coefficient = box_firstsecond_adults, 
-                                              CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
-                                              CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
-                                            )
-
-# first-second half stratified by target position
-splitscores_box_firstsecondStrat_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("first_second"),
-  ncores = 1,
-  verbose = F, 
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
-box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "first-second",
-                                        stratification = "target position",
-                                        coefficient = box_firstsecondStrat_adults,
-                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split
-splitscores_box_oddeven_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F
-)
-
-box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
-box_oddeven_adults_ci <- split_ci(splitscores_box_oddeven_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "odd-even",
-                                        stratification = "none",
-                                        coefficient = box_oddeven_adults,
-                                        CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
-                                      )
-
-# odd-even split stratified by target position
-splitscores_box_oddevenStrat_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("odd_even"),
-  ncores = 1,
-  verbose = F, 
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
-box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "odd-even",
-                                        stratification = "target position",
-                                        coefficient = box_oddevenStrat_adults,
-                                        CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting (random sampling without replacement)
-splitscores_box_permutated_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-)
-
-box_permutated_adults <- split_coefs(splitscores_box_permutated_adults, cor)
-box_permutated_adults_ci <- split_ci(splitscores_box_permutated_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "permutated",
-                                        stratification = "none",
-                                        coefficient = box_permutated_adults,
-                                        CI_lower = box_permutated_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_permutated_adults_ci$lims["0.975","bca"]
-                                      )
-
-# permutated splitting stratified by target position
-splitscores_box_permutatedStrat_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-box_permutatedStrat_adults <- split_coefs(splitscores_box_permutatedStrat_adults, cor)
-box_permutatedStrat_adults_ci <- split_ci(splitscores_box_permutatedStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "permutated",
-                                        stratification = "target position",
-                                        coefficient = box_permutatedStrat_adults,
-                                        CI_lower = box_permutatedStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_permutatedStrat_adults_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo (sampling with replacement)
-splitscores_box_montecarlo_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-)
-
-box_montecarlo_adults <- split_coefs(splitscores_box_montecarlo_adults, cor)
-box_montecarlo_adults_ci <- split_ci(splitscores_box_montecarlo_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "Monte Carlo",
-                                        stratification = "none",
-                                        coefficient = box_montecarlo_adults,
-                                        CI_lower = box_montecarlo_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_montecarlo_adults_ci$lims["0.975","bca"]
-                                      )
-
-# monte carlo stratified by target position
-splitscores_box_montecarloStrat_adults <- by_split(
-  box_intCon_data %>% filter(sample == "adults"),
-  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-  fn_score_box,
-  method = c("random"),
-  ncores = 1,
-  verbose = F, 
-  replications = 1,
-  replace = TRUE,
-  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-)
-
-box_montecarloStrat_adults <- split_coefs(splitscores_box_montecarloStrat_adults, cor)
-box_montecarloStrat_adults_ci <- split_ci(splitscores_box_montecarloStrat_adults, cor)
-
-splithalf_data <- splithalf_data %>% add_row(
-                                        sample = "adults", 
-                                        studyversion = "box", 
-                                        method = "Monte Carlo",
-                                        stratification = "target position",
-                                        coefficient = box_montecarloStrat_adults,
-                                        CI_lower = box_montecarloStrat_adults_ci$lims["0.025","bca"], 
-                                        CI_upper = box_montecarloStrat_adults_ci$lims["0.975","bca"]
-                                      )
+# # first-second half split
+# splitscores_box_firstsecond_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
+# box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                               sample = "adults", 
+#                                               studyversion = "box", 
+#                                               method = "first-second", 
+#                                               stratification = "none",                                        
+#                                               coefficient = box_firstsecond_adults, 
+#                                               CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
+#                                               CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
+#                                             )
+# 
+# # first-second half stratified by target position
+# splitscores_box_firstsecondStrat_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("first_second"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
+# box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "first-second",
+#                                         stratification = "target position",
+#                                         coefficient = box_firstsecondStrat_adults,
+#                                         CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split
+# splitscores_box_oddeven_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F
+# )
+# 
+# box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
+# box_oddeven_adults_ci <- split_ci(splitscores_box_oddeven_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "odd-even",
+#                                         stratification = "none",
+#                                         coefficient = box_oddeven_adults,
+#                                         CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # odd-even split stratified by target position
+# splitscores_box_oddevenStrat_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("odd_even"),
+#   ncores = 1,
+#   verbose = F, 
+#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
+# box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "odd-even",
+#                                         stratification = "target position",
+#                                         coefficient = box_oddevenStrat_adults,
+#                                         CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting (random sampling without replacement)
+# splitscores_box_permutated_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+# )
+# 
+# box_permutated_adults <- split_coefs(splitscores_box_permutated_adults, cor)
+# box_permutated_adults_ci <- split_ci(splitscores_box_permutated_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "permutated",
+#                                         stratification = "none",
+#                                         coefficient = box_permutated_adults,
+#                                         CI_lower = box_permutated_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_permutated_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # permutated splitting stratified by target position
+# splitscores_box_permutatedStrat_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# box_permutatedStrat_adults <- split_coefs(splitscores_box_permutatedStrat_adults, cor)
+# box_permutatedStrat_adults_ci <- split_ci(splitscores_box_permutatedStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "permutated",
+#                                         stratification = "target position",
+#                                         coefficient = box_permutatedStrat_adults,
+#                                         CI_lower = box_permutatedStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_permutatedStrat_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo (sampling with replacement)
+# splitscores_box_montecarlo_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+# )
+# 
+# box_montecarlo_adults <- split_coefs(splitscores_box_montecarlo_adults, cor)
+# box_montecarlo_adults_ci <- split_ci(splitscores_box_montecarlo_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "none",
+#                                         coefficient = box_montecarlo_adults,
+#                                         CI_lower = box_montecarlo_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_montecarlo_adults_ci$lims["0.975","bca"]
+#                                       )
+# 
+# # monte carlo stratified by target position
+# splitscores_box_montecarloStrat_adults <- by_split(
+#   box_intCon_data %>% filter(sample == "adults"),
+#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+#   fn_score_box,
+#   method = c("random"),
+#   ncores = 1,
+#   verbose = F, 
+#   replications = 1,
+#   replace = TRUE,
+#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+# )
+# 
+# box_montecarloStrat_adults <- split_coefs(splitscores_box_montecarloStrat_adults, cor)
+# box_montecarloStrat_adults_ci <- split_ci(splitscores_box_montecarloStrat_adults, cor)
+# 
+# splithalf_data <- splithalf_data %>% add_row(
+#                                         sample = "adults", 
+#                                         studyversion = "box", 
+#                                         method = "Monte Carlo",
+#                                         stratification = "target position",
+#                                         coefficient = box_montecarloStrat_adults,
+#                                         CI_lower = box_montecarloStrat_adults_ci$lims["0.025","bca"], 
+#                                         CI_upper = box_montecarloStrat_adults_ci$lims["0.975","bca"]
+#                                       )
 ```
@@
 ```{r splithalf_plot}
-splithalf_data %>% 
-  mutate(
-    sample = fct_rev(sample), 
-  ) %>%
-  unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
-  mutate(samplegroup = fct_rev(samplegroup)) %>%
-  unite("methodStrat", c(method, stratification), sep = " - ", remove = FALSE) %>% 
-  mutate(
-    methodStrat = factor(methodStrat, levels = c("first-second - none", "first-second - target position", "odd-even - none", "odd-even - target position", "permutated - none", "permutated - target position", "Monte Carlo - none", "Monte Carlo - target position")) %>% fct_rev(),
-  ) %>%  
-  ggplot(aes(x = methodStrat, y = coefficient, color = sample, group = studyversion)) + 
-    geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
-    geom_point(position = position_dodge(0.1), size = 3) +
-    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-    scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
-    labs(x = "Splitting & stratification method", y = "") +
-    coord_flip() + 
-    facet_wrap(~ samplegroup, nrow = 1) + 
-    theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
-
-ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
+# splithalf_data %>% 
+#   mutate(
+#     sample = fct_rev(sample), 
+#   ) %>%
+#   unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
+#   mutate(samplegroup = fct_rev(samplegroup)) %>%
+#   unite("methodStrat", c(method, stratification), sep = " - ", remove = FALSE) %>% 
+#   mutate(
+#     methodStrat = factor(methodStrat, levels = c("first-second - none", "first-second - target position", "odd-even - none", "odd-even - target position", "permutated - none", "permutated - target position", "Monte Carlo - none", "Monte Carlo - target position")) %>% fct_rev(),
+#   ) %>%  
+#   ggplot(aes(x = methodStrat, y = coefficient, color = sample, group = studyversion)) + 
+#     geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
+#     geom_point(position = position_dodge(0.1), size = 3) +
+#     scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+#     scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
+#     labs(x = "Splitting & stratification method", y = "") +
+#     coord_flip() + 
+#     facet_wrap(~ samplegroup, nrow = 1) + 
+#     theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
+# 
+# ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
 ```
@@
 ```{r splithalf_table}
-knitr::kable(splithalf_data)
+# knitr::kable(splithalf_data)
 ```
@@
 ```{r save_splithalf_data}
-write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
-saveRDS(splithalf_data, file = "../saves/gafo-splithalf.rds")
+# write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
+# saveRDS(splithalf_data, file = "../saves/gafo-splithalf.rds")
 ```
@@
 ```{r retest_hedge_data}
-# take data of first reli day for internal consistency
 hedge_retest <- reli %>% 
@@
 hedge_retest %>% 
+  group_by(sample) %>%
   summarize(
@@
 hedge_retest %>% 
+  group_by(sample) %>%
   filter(mean_reliday1 >= mean(mean_reliday1) + 3*sd(mean_reliday1) | 
@@
          mean_reliday2 <= mean(mean_reliday2) - 3*sd(mean_reliday2))
-
-# exclude 1 outlier
+```
+
+```{r retest_hedge_model}
+# define data
+mDataRetestHedge <- reli %>% 
+  filter(studyversion == "hedge" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, reliday, clickDistInBalloons)
+
+# run model
+mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
+                              data   = mDataRetestHedge, 
+                              family = lognormal(), 
+                              warmup = 1000, 
+                              iter   = 3000, 
+                              chains = 4, 
+                              inits  = "random",
+                              cores  = 4)
+
+write.csv(mRetestHedge, "../saves/mRetestHedge.csv", quote = F, row.names = F)
+saveRDS(mRetestHedge, "../saves/mRetestHedge.rds")
+```
+
+```{r retest_hedge_exclude_outliers}
+# exclude outliers
 hedge_retest <- hedge_retest %>%
@@
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
-  scale_x_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
-  scale_y_continuous(limits = c(0, 4.1), breaks = seq(0, 4, 1)) +
+  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
   labs(x = "Testday 1", y = "Testday 2")
@@
 
-```{r retest_hedge_model}
-# define data
-mDataRetestHedge <- reli %>% 
-  filter(studyversion == "hedge" & sample == "kids") %>% 
-  mutate(
-    # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
-  ) %>% 
-  select(subjID, age, reliday, clickDistInBalloons)
-
-# run model
-mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
-                              data   = mDataRetestHedge, 
-                              family = lognormal(), 
-                              warmup = 1000, 
-                              iter   = 3000, 
-                              chains = 4, 
-                              inits  = "random",
-                              cores  = 4)
-
-write.csv(mRetestHedge, "../saves/mRetestHedge.csv", quote = F, row.names = F)
-saveRDS(mRetestHedge, "../saves/mRetestHedge.rds")
-```
-
 ```{r retest_box_data}
@@
 psych::describeBy(box_retest, box_retest$sample)
+
+####
+# calculate at which values we would start seing data as outliers
+box_retest %>% 
+  group_by(sample) %>%
+  summarize(
+    lower_reliday1 = mean(mean_reliday1, na.rm = T) - 3*sd(mean_reliday1, na.rm = T), 
+    upper_reliday1 = mean(mean_reliday1, na.rm = T) + 3*sd(mean_reliday1, na.rm = T),
+    lower_reliday2 = mean(mean_reliday2, na.rm = T) - 3*sd(mean_reliday2, na.rm = T),
+    upper_reliday2 = mean(mean_reliday2, na.rm = T) + 3*sd(mean_reliday2, na.rm = T),
+  )
+
+# check how many there are
+box_retest %>% 
+  group_by(sample) %>%
+  filter(mean_reliday1 >= mean(mean_reliday1, na.rm = T) + 3*sd(mean_reliday1, na.rm = T) | 
+         mean_reliday1 <= mean(mean_reliday1, na.rm = T) - 3*sd(mean_reliday1, na.rm = T) |
+         mean_reliday2 >= mean(mean_reliday2, na.rm = T) + 3*sd(mean_reliday2, na.rm = T) |
+         mean_reliday2 <= mean(mean_reliday2, na.rm = T) - 3*sd(mean_reliday2, na.rm = T))
+```
+
+```{r retest_box_model}
+# define data
+mDataRetestBox <- reli %>% 
+  filter(studyversion == "box" & sample == "kids") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, reliday, correctBox)
+
+# run model
+mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
+                              data   = mDataRetestBox, 
+                              family = bernoulli(link = "logit"),
+                              warmup = 1000, 
+                              iter   = 3000, 
+                              chains = 4, 
+                              inits  = "random",
+                              cores  = 4)
+
+write.csv(mRetestBox, "../saves/mRetestBox.csv", quote = F, row.names = F)
+saveRDS(mRetestBox, "../saves/mRetestBox.rds")
 ```
@@
 
-ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
+ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
 ```
@@
 
-```{r retest_box_model}
-# define data
-mDataRetestBox <- reli %>% 
-  filter(studyversion == "box" & sample == "kids") %>% 
-  mutate(
-    # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
-  ) %>% 
-  select(subjID, age, reliday, correctBox)
-
-# run model
-mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
-                              data   = mDataRetestBox, 
-                              family = bernoulli(link = "logit"),
-                              warmup = 1000, 
-                              iter   = 3000, 
-                              chains = 4, 
-                              inits  = "random",
-                              cores  = 4)
-
-write.csv(mRetestBox, "../saves/mRetestBox.csv", quote = F, row.names = F)
-saveRDS(mRetestBox, "../saves/mRetestBox.rds")
-```
-
 # Save plots
@@
 
-  ggarrange(hedge_variation_plot,
+  ggarrange(hedge_variation_plot_GLMM,
             NULL,
@@
 
-  ggarrange(box_variation_plot,
+  ggarrange(box_variation_plot_GLMM,
             NULL,
@@
 
-ggsave("../figures/gafo_results.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+ggsave("../figures/gafo_results_GLMM.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+```
+
+```{r}
+ggarrange(hedge_variation_plot,
+          NULL,
+          ggarrange(
+              hedge_intCon_kids, 
+              hedge_retest_kids, 
+              nrow = 1, 
+              ncol = 2, 
+              labels = c("B", "C")
+            ), 
+          nrow = 3, heights = c(0.625, 0.05, 0.325), labels = c("A", "", "")
+)
+
+ggsave("/Users/julia_prein/Downloads/gafo_poster.png", width = 6.5, height = 6, scale = 1.1, bg = "white")
 ```

### 2022-08-09 paper/manuscript.Rmd
update final data set

@@
 High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-Furthermore, we find first evidence for the external validity of our task: the measured performance in gaze understanding relates to children's real-life social surroundings.
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
@@
 Third, we systematically investigated the psychometric properties of the new task.
-Finally, to validate the task, we studied how it relates to aspects of children's everyday experience.
 
@@
 
-# Validity
-Our third aim was to assess whether the captured individual variation in gaze understanding relates to factors in children's real live social environment.
-Previous studies found associations between social cognition measures and various environmental factors [@devine2018family; @hughes2004links], including family background and education [@cutting1999theory; bulgarelli2016social], number and age of siblings and family constellation [@zhang2021worse, @cassidy2005theory; @perner1994theory; @peterson2000kindred], interaction with siblings [@dunn1991young], and centre-based childcare [@bulgarelli2016social].
-It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the validity of our measure.
-
-```{r extvali_sample}
-extvali <- testtrials %>% 
-  filter(ageInYears < 6) %>%
-  mutate(
-        symmetricPosition = case_when(
-                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
-                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
-                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
-                                  targetPosition == "2" | targetPosition == "9" ~ 4,
-                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
-                       ), 
-  ) %>% 
-  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>%
-  group_by(subjID) %>% 
-  # so that all models run with same nr of subjects
-  drop_na()
-
-extvali_sample <- extvali %>%
-  group_by(ageInYears) %>%
-  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
-  summarise(
-    nTotal = n_distinct(subjID), 
-    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
-    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
-    minAgeInMonths = min(ageInMonths, na.rm = T),
-    maxAgeInMonths = max(ageInMonths, na.rm = T),
-    nFemales = ceiling(sum(female/15)),
-  )
-```
-
-## Participants
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of 
-`r sum(extvali_sample$nTotal)` children, including 
-`r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "3"])` months, 
-SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "3"])`, 
-range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "3"])`
-- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "3"])`, 
-`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "3"])` girls),
-`r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "4"])` months, 
-SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "4"])`, 
-range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "4"])`
-- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "4"])`, 
-`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "4"])` girls),
-and `r sum(extvali_sample$nTotal[extvali_sample$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(extvali_sample$meanAgeInMonths[extvali_sample$ageInYears == "5"])` months, 
-SD = `r sum(extvali_sample$sdAgeInMonths[extvali_sample$ageInYears == "5"])`, 
-range = `r sum(extvali_sample$minAgeInMonths[extvali_sample$ageInYears == "5"])`
-- `r sum(extvali_sample$maxAgeInMonths[extvali_sample$ageInYears == "5"])`, 
-`r sum(extvali_sample$nFemales[extvali_sample$ageInYears == "5"])` girls).
-
-## Procedure
-Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire.
-We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-
-## Analysis
-To estimate the effects of social surrounding on gaze understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
-The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the gaze understanding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`).
-In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
-For the target position, we categorized two adjacent bins as one imaginary box.
-To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
-Across the two study versions, we could consequently model the participant's correct response (0/1) using a `Bernoulli` distribution with a logit link function.
-For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
-In addition, we calculated three index scores.
-First, we calculated a sibling variety score according to @peterson2000kindred.
-Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements).
-Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
-We compared the models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2020statistical].
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-
-## Results
-```{r extvali_winningmodel}
-mExtvaliPE <- readRDS(file = "../saves/extvali-mExtvaliPE.rds") 
-```
-
-The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy.
-Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
-The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
-For example, for our winning model, we found a peer exposure estimate of $\beta$ =
-`r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
-with the estimates of age being $\beta$ =`r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being $\beta$ =`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version $\beta$ =`r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]).
-Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
-The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
-
-(ref:figlab4) **External validity of the gaze understanding task**. 
-Factors of children's social surroundings and their influence on the probability of responding correctly.
-Models are ordered according to their WAIC scores, with the uppermost winning the model comparison.
-The graph shows the estimated density curves of a model's predictor coefficient.
-Only models performing better than our null model are included in the graph.
-
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)", fig.show='asis'}
-knitr::include_graphics("../figures/extvali_results.png")
-```
-
-## Discussion
-We found that factors of children's social surrounding influenced their gaze understanding.
-Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
-Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
-Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze understanding.
-
 # General Discussion
@@
 
-After finding consistent and reliable individual estimates, we aimed at verifying the appropriateness of our new task.
+# TODO adjust discussion part validity
 Validity is often assessed by looking at concurrent relations between measures.
@@
 [^fn3]: Attentive readers might notice that we simplified the structure of random effects.
-Compared to our models in the *Individual differences* and *External Validity* sections, this model does not include the random slope for symmetric target position within participants.
+Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
 We decided to do so since we had limited amount of data from few participants.
@@
 # )
-```
-
-### Appendix to external validity section
-#### Scoring of sibling variety scores
-For assessing the external validity of our gaze understanding task, we calculated two sibling variety scores based on the existing Theory of Mind literature. 
-First, we followed the approach by @peterson2000kindred.
-Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
-
-Second, we implemented the sibling variety score by @cassidy2005theory.
-The authors adjusted the original score of @peterson2000kindred in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
-Twins with additional siblings scored depending on the age and number of their siblings.
-
-The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
-However, teenage siblings might provide opportunities for interesting discussions [@peterson2000kindred].
-
-#### WAIC scores and weights of the model comparison
-As can be seen, ELPD difference scores are smaller than their respective standard errors.
-WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}).
-All effects except when a child entered childcare positively influence performance.
-
-```{r extvali_table, results = "asis"}
-extvali_models <- readRDS(file = "../saves/extvali-results.rds") %>% 
-  mutate(across(c(WAIC, SE_WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>% 
-  mutate_if(is.numeric, round, 2)
-
-papaja::apa_table(
-  extvali_models, 
-  caption = "Model comparison for influences of children's social surrounding", 
-  note = "All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants", 
-  escape = T
-)
 ```

### 2022-08-10 stats/analysis.Rmd
adjust splithalfr calculation

@@
 
-```{r variation_hedge_plot}
-hedge_variation_plot <- ggplot() +
-  # child data
-  geom_smooth(
-    data = variationHedgeInd %>% filter(sample == "kids"),  
-    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
-    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
-  ) +
-
-  geom_point(
-    data = variationHedgeInd %>% filter(sample == "kids"), 
-    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
-  ) +
-
-  geom_pointrange(
-    data = variationHedge %>% filter(sample == "kids"), 
-    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
-  ) +
-
-  scale_shape_manual(values = c(16, 18)) + 
-  scale_alpha_discrete(range = c(1, 0.4)) + 
-  scale_linetype_manual(values = c("solid", "dashed")) +
-
-  # adult data
-  geom_jitter(
-    data = variationHedgeInd %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
-  ) +
-
-  geom_pointrange(
-    data = variationHedge %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
-    size = 0.8,
-  ) +
-
-  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
-  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +
-
-  theme(legend.text = element_text(size = 8),
-        legend.key.size = unit(0.4, "cm"), 
-        legend.direction = "vertical", 
-        legend.box = "horizontal",
-        legend.position = c(0.72, 0.85), 
-        legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black")
-        )
-
-hedge_variation_plot
-
-ggsave("../figures/gafo_hedge_variation.png", width = 7, height = 4)
-```
-
 ```{r age_hedge_model}
@@
 
-pp_check(mAgeHedge) + xlim(0, 10)
+# pp_check(mAgeHedge) + xlim(0, 10)
 ```
@@
 hedge_variation_plot_GLMM
-
-ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
+saveRDS(hedge_variation_plot_GLMM, file = "../saves/gafo-hedge-variation-plot-GLMM.rds")
+# ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
 ```
@@
 
-```{r variation_box_plot}
-# with remote sample
-box_variation_plot <- ggplot() +
-  # chance level
-  geom_segment(aes(x = 3.0, y = 0.2, xend = 6.2, yend = 0.2), lty = "dotted") + 
-  geom_segment(aes(x = 6.25, y = 0.125, xend = 6.75, yend = 0.125), lty = "dotted") +
-
-  # child data
-  geom_smooth(
-    data = variationBoxInd %>% filter(sample == "kids"),  
-    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
-    method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey",
-  ) +
-
-  geom_point(
-    data = variationBoxInd %>% filter(sample == "kids"), 
-    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
-  ) +
-
-  geom_pointrange(
-    data = variationBox %>% filter(sample == "kids"), 
-    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
-  ) +
-
-  scale_shape_manual(values = c(16, 18)) + 
-  scale_alpha_discrete(range = c(1, 0.4)) + 
-  scale_linetype_manual(values = c("solid", "dashed")) +
-
-  # adult data
-  geom_jitter(
-    data = variationBoxInd %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
-  ) +
-
-  geom_pointrange(
-    data = variationBox %>% filter(sample == "adults"), 
-    aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper, shape = datacollection), 
-    size = 0.8,
-  ) +
-
-  labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
-  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
-  theme(legend.position="none")
-
-box_variation_plot
-
-ggsave("../figures/gafo_box_variation.png", width = 5, height = 4)
-```
-
 ```{r age_box_model}
@@
 
-ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
+saveRDS(box_variation_plot_GLMM, file = "../saves/gafo-box-variation-plot-GLMM.rds")
+# ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
 ```
@@
 
-## Internal consistency
+## Splithalf Reliability Data
 ```{r intCon_hedge_data}
@@
 
-ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
+saveRDS(hedge_intCon_kids, file = "../saves/gafo-hedge-intCon-kids.rds")
+# ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
 ```
@@
 
-ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
+saveRDS(hedge_intCon_adults, file = "../saves/gafo-hedge-intCon-adults.rds")
+# ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
 ```
@@
 
-ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
+saveRDS(box_intCon_kids, file = "../saves/gafo-box-intCon-kids.rds")
+# ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
 ```
@@
 
-ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
-```
-
-```{r splithalfr_luke}
+saveRDS(box_intCon_adults, file = "../saves/gafo-box-intCon-adults.rds")
+# ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
+```
+
+## Splithalf Reliability - Hedge Kids
+
+```{r splithalfr_hedge_kids_firstsecond}
 fn_score_hedge <- function(ds) {
@@
   fn_score_hedge,
-  replications = 25,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
+hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
+
+splithalf_data <- tibble(
+                          sample = "kids",
+                          studyversion = "hedge",
+                          method = "first-second",
+                          stratification = "none",
+                          coefficient = hedge_firstsecond_kids,
+                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"],
+                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
+                        )
+
+# first-second half stratified by target position
+splitscores_hedge_firstsecondStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
+hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = hedge_firstsecondStrat_kids,
+                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_hedge_kids_oddeven}
+# odd-even split
+splitscores_hedge_oddeven_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
+hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = hedge_oddeven_kids,
+                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split stratified by target position
+splitscores_hedge_oddevenStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F,
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
+hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = hedge_oddevenStrat_kids,
+                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_hedge_kids_permutated}
+# permutated splitting (random sampling without replacement)
+splitscores_hedge_permutated_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
+
+splitscores_hedge_permutated_kids_uniq_reps <- unique(splitscores_hedge_permutated_kids$replication)
+
+splitscores_hedge_permutated_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_permutated_kids, replication==r), cor))
+}
+
+hedge_permutated_kids_ci <- mclapply(splitscores_hedge_permutated_kids_uniq_reps, splitscores_hedge_permutated_kids_parallel_split_ci, mc.cores=48)
+
+hedge_permutated_kids_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "kids",
+  split = "permutated",
+  stratification = "none",
+  mean = hedge_permutated_kids)
+
+hedge_permutated_kids_tbl$CI_lower = numeric(nrow(hedge_permutated_kids_tbl))
+hedge_permutated_kids_tbl$CI_upper = numeric(nrow(hedge_permutated_kids_tbl))
+
+for(i in 1:nrow(hedge_permutated_kids_tbl)) {
+  hedge_permutated_kids_tbl$CI_lower[i] <- hedge_permutated_kids_ci[[i]]$lims["0.025","bca"]
+  hedge_permutated_kids_tbl$CI_upper[i] <- hedge_permutated_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = mean(hedge_permutated_kids_tbl$mean),
+                                        CI_lower = mean(hedge_permutated_kids_tbl$CI_lower),
+                                        CI_upper = mean(hedge_permutated_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_kids_permutated_stratified}
+# permutated splitting stratified by target position
+splitscores_hedge_permutatedStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
+
+splitscores_hedge_permutatedStrat_kids_uniq_reps <- unique(splitscores_hedge_permutatedStrat_kids$replication)
+
+splitscores_hedge_permutatedStrat_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_permutatedStrat_kids, replication==r), cor))
+}
+
+hedge_permutatedStrat_kids_ci <- mclapply(splitscores_hedge_permutatedStrat_kids_uniq_reps, splitscores_hedge_permutatedStrat_kids_parallel_split_ci, mc.cores=48)
+
+hedge_permutatedStrat_kids_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "kids",
+  split = "random",
+  stratification = "target position",
+  mean = hedge_permutatedStrat_kids)
+
+hedge_permutatedStrat_kids_tbl$CI_lower = numeric(nrow(hedge_permutatedStrat_kids_tbl))
+hedge_permutatedStrat_kids_tbl$CI_upper = numeric(nrow(hedge_permutatedStrat_kids_tbl))
+
+for(i in 1:nrow(hedge_permutatedStrat_kids_tbl)) {
+  hedge_permutatedStrat_kids_tbl$CI_lower[i] <- hedge_permutatedStrat_kids_ci[[i]]$lims["0.025","bca"]
+  hedge_permutatedStrat_kids_tbl$CI_upper[i] <- hedge_permutatedStrat_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = mean(hedge_permutatedStrat_kids_tbl$mean),
+                                        CI_lower = mean(hedge_permutatedStrat_kids_tbl$CI_lower),
+                                        CI_upper = mean(hedge_permutatedStrat_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_kids_montecarlo}
+# monte carlo (sampling with replacement)
+splitscores_hedge_montecarlo_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
   method = c("random"),
@@
 
-hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
-uniq_reps <- unique(splitscores_hedge_random_kids$replication)
-
-parallel_split_ci <- function(r) {
-        return(split_ci(filter(splitscores_hedge_random_kids, replication==r), cor))
-}
-
-hedge_random_kids_ci <- mclapply(uniq_reps, parallel_split_ci, mc.cores=48)
-# Darn R
-
-# create dataframe to save data
-splithalf_data <- tibble(
-  studyversion = "hedge",
-  sample = "kids",
+hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
+
+splitscores_hedge_montecarlo_kids_uniq_reps <- unique(splitscores_hedge_montecarlo_kids$replication)
+
+splitscores_hedge_montecarlo_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_montecarlo_kids, replication==r), cor))
+}
+
+hedge_montecarlo_kids_ci <- mclapply(splitscores_hedge_montecarlo_kids_uniq_reps, splitscores_hedge_montecarlo_kids_parallel_split_ci, mc.cores=48)
+
+hedge_montecarlo_kids_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "kids",
+  split = "Monte Carlo",
+  stratification = "none",
+  mean = hedge_montecarlo_kids)
+
+hedge_montecarlo_kids_tbl$CI_lower = numeric(nrow(hedge_montecarlo_kids_tbl))
+hedge_montecarlo_kids_tbl$CI_upper = numeric(nrow(hedge_montecarlo_kids_tbl))
+
+for(i in 1:nrow(hedge_montecarlo_kids_tbl)) {
+  hedge_montecarlo_kids_tbl$CI_lower[i] <- hedge_montecarlo_kids_ci[[i]]$lims["0.025","bca"]
+  hedge_montecarlo_kids_tbl$CI_upper[i] <- hedge_montecarlo_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = mean(hedge_montecarlo_kids_tbl$mean),
+                                        CI_lower = mean(hedge_montecarlo_kids_tbl$CI_lower),
+                                        CI_upper = mean(hedge_montecarlo_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_kids_montecarlo_stratified}
+# monte carlo stratified by target position
+splitscores_hedge_montecarloStrat_kids <- by_split(
+  hedge_intCon_data %>% filter(sample == "kids"),
+  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
+
+splitscores_hedge_montecarloStrat_kids_uniq_reps <- unique(splitscores_hedge_montecarloStrat_kids$replication)
+
+splitscores_hedge_montecarloStrat_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_montecarloStrat_kids, replication==r), cor))
+}
+
+hedge_montecarloStrat_kids_ci <- mclapply(splitscores_hedge_montecarloStrat_kids_uniq_reps, splitscores_hedge_montecarloStrat_kids_parallel_split_ci, mc.cores=48)
+
+hedge_montecarloStrat_kids_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "kids",
+  split = "Monte Carlo",
+  stratification = "target position",
+  mean = hedge_montecarloStrat_kids)
+
+hedge_montecarloStrat_kids_tbl$CI_lower = numeric(nrow(hedge_montecarloStrat_kids_tbl))
+hedge_montecarloStrat_kids_tbl$CI_upper = numeric(nrow(hedge_montecarloStrat_kids_tbl))
+
+for(i in 1:nrow(hedge_montecarloStrat_kids_tbl)) {
+  hedge_montecarloStrat_kids_tbl$CI_lower[i] <- hedge_montecarloStrat_kids_ci[[i]]$lims["0.025","bca"]
+  hedge_montecarloStrat_kids_tbl$CI_upper[i] <- hedge_montecarloStrat_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "hedge",
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = mean(hedge_montecarloStrat_kids_tbl$mean),
+                                        CI_lower = mean(hedge_montecarloStrat_kids_tbl$CI_lower),
+                                        CI_upper = mean(hedge_montecarloStrat_kids_tbl$CI_upper),
+                                      )
+```
+
+####
+## Splithalf Reliability - Hedge Adults
+
+```{r splithalfr_hedge_adults_firstsecond}
+# first-second half split
+splitscores_hedge_firstsecond_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
+hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "first-second",
+                                        stratification = "none",
+                                        coefficient = hedge_firstsecond_adults,
+                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first-second half stratified by target position
+splitscores_hedge_firstsecondStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
+hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = hedge_firstsecondStrat_adults,
+                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_hedge_adults_oddeven}
+# odd-even split
+splitscores_hedge_oddeven_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F
+)
+
+hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
+hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = hedge_oddeven_adults,
+                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split stratified by target position
+splitscores_hedge_oddevenStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F,
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
+hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = hedge_oddevenStrat_adults,
+                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"],
+                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_hedge_adults_permutated}
+# permutated splitting (random sampling without replacement)
+splitscores_hedge_permutated_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
+
+splitscores_hedge_permutated_adults_uniq_reps <- unique(splitscores_hedge_permutated_adults$replication)
+
+splitscores_hedge_permutated_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_permutated_adults, replication==r), cor))
+}
+
+hedge_permutated_adults_ci <- mclapply(splitscores_hedge_permutated_adults_uniq_reps, splitscores_hedge_permutated_adults_parallel_split_ci, mc.cores=48)
+
+hedge_permutated_adults_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "adults",
+  split = "permutated",
+  stratification = "none",
+  mean = hedge_permutated_adults)
+
+hedge_permutated_adults_tbl$CI_lower = numeric(nrow(hedge_permutated_adults_tbl))
+hedge_permutated_adults_tbl$CI_upper = numeric(nrow(hedge_permutated_adults_tbl))
+
+for(i in 1:nrow(hedge_permutated_adults_tbl)) {
+  hedge_permutated_adults_tbl$CI_lower[i] <- hedge_permutated_adults_ci[[i]]$lims["0.025","bca"]
+  hedge_permutated_adults_tbl$CI_upper[i] <- hedge_permutated_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = mean(hedge_permutated_adults_tbl$mean),
+                                        CI_lower = mean(hedge_permutated_adults_tbl$CI_lower),
+                                        CI_upper = mean(hedge_permutated_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_adults_permutated_stratified}
+# permutated splitting stratified by target position
+splitscores_hedge_permutatedStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
+
+splitscores_hedge_permutatedStrat_adults_uniq_reps <- unique(splitscores_hedge_permutatedStrat_adults$replication)
+
+splitscores_hedge_permutatedStrat_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_permutatedStrat_adults, replication==r), cor))
+}
+
+hedge_permutatedStrat_adults_ci <- mclapply(splitscores_hedge_permutatedStrat_adults_uniq_reps, splitscores_hedge_permutatedStrat_adults_parallel_split_ci, mc.cores=48)
+
+hedge_permutatedStrat_adults_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "adults",
   split = "random",
-  stratification = "none",
-  mean = hedge_random_kids)
-
-splithalf_data$CI_lower = numeric(nrow(splithalf_data))
-splithalf_data$CI_upper = numeric(nrow(splithalf_data))
-for(i in 1:nrow(splithalf_data)) {
-  splithalf_data$CI_lower[i] <- hedge_random_kids_ci[[i]]$lims["0.025","bca"]
-  splithalf_data$CI_upper[i] <- hedge_random_kids_ci[[i]]$lims["0.975","bca"]
-}
-
-print(splithalf_data)
-# write_csv(splithalf_data, "splithalf_data.csv")
-```
-
-```{r splithalfr_hedge_kids}
-# fn_score_hedge <- function(ds) {
-#   return(mean(ds$clickDistInBalloons, na.rm = TRUE))
-# }
-# 
-# hedge_intCon_data <- reli %>% 
-#   filter(studyversion == "hedge" & reliday == "reliday1")
-# 
-# # first-second half split
-# splitscores_hedge_firstsecond_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
-# hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
-# 
-# splithalf_data <- tibble(
-#                           sample = "kids", 
-#                           studyversion = "hedge", 
-#                           method = "first-second", 
-#                           stratification = "none",                                        
-#                           coefficient = hedge_firstsecond_kids, 
-#                           CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
-#                           CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
-#                         )
-# 
-# # first-second half stratified by target position
-# splitscores_hedge_firstsecondStrat_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
-# hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "first-second",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_firstsecondStrat_kids,
-#                                         CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split
-# splitscores_hedge_oddeven_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
-# hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "odd-even",
-#                                         stratification = "none",
-#                                         coefficient = hedge_oddeven_kids,
-#                                         CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split stratified by target position
-# splitscores_hedge_oddevenStrat_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
-# hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "odd-even",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_oddevenStrat_kids,
-#                                         CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting (random sampling without replacement)
-# splitscores_hedge_permutated_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-# )
-# 
-# hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
-# hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "permutated",
-#                                         stratification = "none",
-#                                         coefficient = hedge_permutated_kids,
-#                                         CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting stratified by target position
-# splitscores_hedge_permutatedStrat_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
-# hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "permutated",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_permutatedStrat_kids,
-#                                         CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo (sampling with replacement)
-# splitscores_hedge_montecarlo_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-# )
-# 
-# hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
-# hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "none",
-#                                         coefficient = hedge_montecarlo_kids,
-#                                         CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo stratified by target position
-# splitscores_hedge_montecarloStrat_kids <- by_split(
-#   hedge_intCon_data %>% filter(sample == "kids"),
-#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
-# hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "hedge", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_montecarloStrat_kids,
-#                                         CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-```
-
-```{r splithalfr_hedge_adults}
-# # first-second half split
-# splitscores_hedge_firstsecond_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
-# hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                               sample = "adults", 
-#                                               studyversion = "hedge", 
-#                                               method = "first-second", 
-#                                               stratification = "none",                                        
-#                                               coefficient = hedge_firstsecond_adults, 
-#                                               CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
-#                                               CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
-#                                             )
-# 
-# # first-second half stratified by target position
-# splitscores_hedge_firstsecondStrat_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
-# hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "first-second",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_firstsecondStrat_adults,
-#                                         CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split
-# splitscores_hedge_oddeven_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
-# hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "odd-even",
-#                                         stratification = "none",
-#                                         coefficient = hedge_oddeven_adults,
-#                                         CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split stratified by target position
-# splitscores_hedge_oddevenStrat_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
-# hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "odd-even",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_oddevenStrat_adults,
-#                                         CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting (random sampling without replacement)
-# splitscores_hedge_permutated_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-# )
-# 
-# hedge_permutated_adults <- split_coefs(splitscores_hedge_permutated_adults, cor)
-# hedge_permutated_adults_ci <- split_ci(splitscores_hedge_permutated_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "permutated",
-#                                         stratification = "none",
-#                                         coefficient = hedge_permutated_adults,
-#                                         CI_lower = hedge_permutated_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_permutated_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting stratified by target position
-# splitscores_hedge_permutatedStrat_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_permutatedStrat_adults <- split_coefs(splitscores_hedge_permutatedStrat_adults, cor)
-# hedge_permutatedStrat_adults_ci <- split_ci(splitscores_hedge_permutatedStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "permutated",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_permutatedStrat_adults,
-#                                         CI_lower = hedge_permutatedStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_permutatedStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo (sampling with replacement)
-# splitscores_hedge_montecarlo_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-# )
-# 
-# hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
-# hedge_montecarlo_adults_ci <- split_ci(splitscores_hedge_montecarlo_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "none",
-#                                         coefficient = hedge_montecarlo_adults,
-#                                         CI_lower = hedge_montecarlo_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_montecarlo_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo stratified by target position
-# splitscores_hedge_montecarloStrat_adults <- by_split(
-#   hedge_intCon_data %>% filter(sample == "adults"),
-#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_hedge,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
-# hedge_montecarloStrat_adults_ci <- split_ci(splitscores_hedge_montecarloStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "hedge", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "target position",
-#                                         coefficient = hedge_montecarloStrat_adults,
-#                                         CI_lower = hedge_montecarloStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = hedge_montecarloStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-```
-
-```{r splithalfr_box_kids}
-# fn_score_box <- function(ds) {
-#   return(mean(ds$correctBox, na.rm = TRUE))
-# }
-# 
-# box_intCon_data <- reli %>% 
-#   filter(studyversion == "box" & reliday == "reliday1") 
-# 
-# # first-second half split
-# splitscores_box_firstsecond_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
-# box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                               sample = "kids", 
-#                                               studyversion = "box", 
-#                                               method = "first-second", 
-#                                               stratification = "none",                                        
-#                                               coefficient = box_firstsecond_kids, 
-#                                               CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
-#                                               CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
-#                                             )
-# 
-# # first-second half stratified by target position
-# splitscores_box_firstsecondStrat_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
-# box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "first-second",
-#                                         stratification = "target position",
-#                                         coefficient = box_firstsecondStrat_kids,
-#                                         CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split
-# splitscores_box_oddeven_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
-# box_oddeven_kids_ci <- split_ci(splitscores_box_oddeven_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "odd-even",
-#                                         stratification = "none",
-#                                         coefficient = box_oddeven_kids,
-#                                         CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split stratified by target position
-# splitscores_box_oddevenStrat_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
-# box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "odd-even",
-#                                         stratification = "target position",
-#                                         coefficient = box_oddevenStrat_kids,
-#                                         CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting (random sampling without replacement)
-# splitscores_box_permutated_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-# )
-# 
-# box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
-# box_permutated_kids_ci <- split_ci(splitscores_box_permutated_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "permutated",
-#                                         stratification = "none",
-#                                         coefficient = box_permutated_kids,
-#                                         CI_lower = box_permutated_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_permutated_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting stratified by target position
-# splitscores_box_permutatedStrat_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
-# box_permutatedStrat_kids_ci <- split_ci(splitscores_box_permutatedStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "permutated",
-#                                         stratification = "target position",
-#                                         coefficient = box_permutatedStrat_kids,
-#                                         CI_lower = box_permutatedStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_permutatedStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo (sampling with replacement)
-# splitscores_box_montecarlo_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-# )
-# 
-# box_montecarlo_kids <- split_coefs(splitscores_box_montecarlo_kids, cor)
-# box_montecarlo_kids_ci <- split_ci(splitscores_box_montecarlo_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "none",
-#                                         coefficient = box_montecarlo_kids,
-#                                         CI_lower = box_montecarlo_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_montecarlo_kids_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo stratified by target position
-# splitscores_box_montecarloStrat_kids <- by_split(
-#   box_intCon_data %>% filter(sample == "kids"),
-#   box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-#   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
-# )
-# 
-# box_montecarloStrat_kids <- split_coefs(splitscores_box_montecarloStrat_kids, cor)
-# box_montecarloStrat_kids_ci <- split_ci(splitscores_box_montecarloStrat_kids, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "kids", 
-#                                         studyversion = "box", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "target position",
-#                                         coefficient = box_montecarloStrat_kids,
-#                                         CI_lower = box_montecarloStrat_kids_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_montecarloStrat_kids_ci$lims["0.975","bca"]
-#                                       )
-```
-
-```{r splithalfr_box_adults}
-# # first-second half split
-# splitscores_box_firstsecond_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
-# box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                               sample = "adults", 
-#                                               studyversion = "box", 
-#                                               method = "first-second", 
-#                                               stratification = "none",                                        
-#                                               coefficient = box_firstsecond_adults, 
-#                                               CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
-#                                               CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
-#                                             )
-# 
-# # first-second half stratified by target position
-# splitscores_box_firstsecondStrat_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("first_second"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
-# box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "first-second",
-#                                         stratification = "target position",
-#                                         coefficient = box_firstsecondStrat_adults,
-#                                         CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split
-# splitscores_box_oddeven_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F
-# )
-# 
-# box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
-# box_oddeven_adults_ci <- split_ci(splitscores_box_oddeven_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "odd-even",
-#                                         stratification = "none",
-#                                         coefficient = box_oddeven_adults,
-#                                         CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # odd-even split stratified by target position
-# splitscores_box_oddevenStrat_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("odd_even"),
-#   ncores = 1,
-#   verbose = F, 
-#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
-# box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "odd-even",
-#                                         stratification = "target position",
-#                                         coefficient = box_oddevenStrat_adults,
-#                                         CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting (random sampling without replacement)
-# splitscores_box_permutated_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-# )
-# 
-# box_permutated_adults <- split_coefs(splitscores_box_permutated_adults, cor)
-# box_permutated_adults_ci <- split_ci(splitscores_box_permutated_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "permutated",
-#                                         stratification = "none",
-#                                         coefficient = box_permutated_adults,
-#                                         CI_lower = box_permutated_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_permutated_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # permutated splitting stratified by target position
-# splitscores_box_permutatedStrat_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# box_permutatedStrat_adults <- split_coefs(splitscores_box_permutatedStrat_adults, cor)
-# box_permutatedStrat_adults_ci <- split_ci(splitscores_box_permutatedStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "permutated",
-#                                         stratification = "target position",
-#                                         coefficient = box_permutatedStrat_adults,
-#                                         CI_lower = box_permutatedStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_permutatedStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo (sampling with replacement)
-# splitscores_box_montecarlo_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-# )
-# 
-# box_montecarlo_adults <- split_coefs(splitscores_box_montecarlo_adults, cor)
-# box_montecarlo_adults_ci <- split_ci(splitscores_box_montecarlo_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "none",
-#                                         coefficient = box_montecarlo_adults,
-#                                         CI_lower = box_montecarlo_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_montecarlo_adults_ci$lims["0.975","bca"]
-#                                       )
-# 
-# # monte carlo stratified by target position
-# splitscores_box_montecarloStrat_adults <- by_split(
-#   box_intCon_data %>% filter(sample == "adults"),
-#   box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
-#   fn_score_box,
-#   method = c("random"),
-#   ncores = 1,
-#   verbose = F, 
-#   replications = 1,
-#   replace = TRUE,
-#   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
-# )
-# 
-# box_montecarloStrat_adults <- split_coefs(splitscores_box_montecarloStrat_adults, cor)
-# box_montecarloStrat_adults_ci <- split_ci(splitscores_box_montecarloStrat_adults, cor)
-# 
-# splithalf_data <- splithalf_data %>% add_row(
-#                                         sample = "adults", 
-#                                         studyversion = "box", 
-#                                         method = "Monte Carlo",
-#                                         stratification = "target position",
-#                                         coefficient = box_montecarloStrat_adults,
-#                                         CI_lower = box_montecarloStrat_adults_ci$lims["0.025","bca"], 
-#                                         CI_upper = box_montecarloStrat_adults_ci$lims["0.975","bca"]
-#                                       )
-```
-
+  stratification = "target position",
+  mean = hedge_permutatedStrat_adults)
+
+hedge_permutatedStrat_adults_tbl$CI_lower = numeric(nrow(hedge_permutatedStrat_adults_tbl))
+hedge_permutatedStrat_adults_tbl$CI_upper = numeric(nrow(hedge_permutatedStrat_adults_tbl))
+
+for(i in 1:nrow(hedge_permutatedStrat_adults_tbl)) {
+  hedge_permutatedStrat_adults_tbl$CI_lower[i] <- hedge_permutatedStrat_adults_ci[[i]]$lims["0.025","bca"]
+  hedge_permutatedStrat_adults_tbl$CI_upper[i] <- hedge_permutatedStrat_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = mean(hedge_permutatedStrat_adults_tbl$mean),
+                                        CI_lower = mean(hedge_permutatedStrat_adults_tbl$CI_lower),
+                                        CI_upper = mean(hedge_permutatedStrat_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_adults_montecarlo}
+# monte carlo (sampling with replacement)
+splitscores_hedge_montecarlo_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+hedge_montecarlo_adults <- split_coefs(splitscores_hedge_montecarlo_adults, cor)
+
+splitscores_hedge_montecarlo_adults_uniq_reps <- unique(splitscores_hedge_montecarlo_adults$replication)
+
+splitscores_hedge_montecarlo_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_montecarlo_adults, replication==r), cor))
+}
+
+hedge_montecarlo_adults_ci <- mclapply(splitscores_hedge_montecarlo_adults_uniq_reps, splitscores_hedge_montecarlo_adults_parallel_split_ci, mc.cores=48)
+
+hedge_montecarlo_adults_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "adults",
+  split = "Monte Carlo",
+  stratification = "none",
+  mean = hedge_montecarlo_adults)
+
+hedge_montecarlo_adults_tbl$CI_lower = numeric(nrow(hedge_montecarlo_adults_tbl))
+hedge_montecarlo_adults_tbl$CI_upper = numeric(nrow(hedge_montecarlo_adults_tbl))
+
+for(i in 1:nrow(hedge_montecarlo_adults_tbl)) {
+  hedge_montecarlo_adults_tbl$CI_lower[i] <- hedge_montecarlo_adults_ci[[i]]$lims["0.025","bca"]
+  hedge_montecarlo_adults_tbl$CI_upper[i] <- hedge_montecarlo_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = mean(hedge_montecarlo_adults_tbl$mean),
+                                        CI_lower = mean(hedge_montecarlo_adults_tbl$CI_lower),
+                                        CI_upper = mean(hedge_montecarlo_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_hedge_adults_montecarlo_stratified}
+# monte carlo stratified by target position
+splitscores_hedge_montecarloStrat_adults <- by_split(
+  hedge_intCon_data %>% filter(sample == "adults"),
+  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_hedge,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+hedge_montecarloStrat_adults <- split_coefs(splitscores_hedge_montecarloStrat_adults, cor)
+
+splitscores_hedge_montecarloStrat_adults_uniq_reps <- unique(splitscores_hedge_montecarloStrat_adults$replication)
+
+splitscores_hedge_montecarloStrat_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_hedge_montecarloStrat_adults, replication==r), cor))
+}
+
+hedge_montecarloStrat_adults_ci <- mclapply(splitscores_hedge_montecarloStrat_adults_uniq_reps, splitscores_hedge_montecarloStrat_adults_parallel_split_ci, mc.cores=48)
+
+hedge_montecarloStrat_adults_tbl <- tibble(
+  studyversion = "hedge",
+  sample = "adults",
+  split = "Monte Carlo",
+  stratification = "target position",
+  mean = hedge_montecarloStrat_adults)
+
+hedge_montecarloStrat_adults_tbl$CI_lower = numeric(nrow(hedge_montecarloStrat_adults_tbl))
+hedge_montecarloStrat_adults_tbl$CI_upper = numeric(nrow(hedge_montecarloStrat_adults_tbl))
+
+for(i in 1:nrow(hedge_montecarloStrat_adults_tbl)) {
+  hedge_montecarloStrat_adults_tbl$CI_lower[i] <- hedge_montecarloStrat_adults_ci[[i]]$lims["0.025","bca"]
+  hedge_montecarloStrat_adults_tbl$CI_upper[i] <- hedge_montecarloStrat_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "hedge",
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = mean(hedge_montecarloStrat_adults_tbl$mean),
+                                        CI_lower = mean(hedge_montecarloStrat_adults_tbl$CI_lower),
+                                        CI_upper = mean(hedge_montecarloStrat_adults_tbl$CI_upper),
+                                      )
+```
+
+## Splithalf Reliability - Box Kids
+
+```{r splithalfr_box_kids_firstsecond}
+fn_score_box <- function(ds) {
+  return(mean(ds$correctBox, na.rm = TRUE))
+}
+
+box_intCon_data <- reli %>%
+  filter(studyversion == "box" & reliday == "reliday1")
+
+# first-second half split
+splitscores_box_firstsecond_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
+box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "first-second",
+                                        stratification = "none",
+                                        coefficient = box_firstsecond_kids,
+                                        CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"],
+                                        CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
+                                      )
+
+# first-second half stratified by target position
+splitscores_box_firstsecondStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
+box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = box_firstsecondStrat_kids,
+                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"],
+                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_kids_oddeven}
+# odd-even split
+splitscores_box_oddeven_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F
+)
+
+box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
+box_oddeven_kids_ci <- split_ci(splitscores_box_oddeven_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = box_oddeven_kids,
+                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"],
+                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split stratified by target position
+splitscores_box_oddevenStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F,
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
+box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = box_oddevenStrat_kids,
+                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"],
+                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_kids_permutated}
+# permutated splitting (random sampling without replacement)
+splitscores_box_permutated_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+box_permutated_kids <- split_coefs(splitscores_box_permutated_kids, cor)
+
+splitscores_box_permutated_kids_uniq_reps <- unique(splitscores_box_permutated_kids$replication)
+
+splitscores_box_permutated_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_permutated_kids, replication==r), cor))
+}
+
+box_permutated_kids_ci <- mclapply(splitscores_box_permutated_kids_uniq_reps, splitscores_box_permutated_kids_parallel_split_ci, mc.cores=48)
+
+box_permutated_kids_tbl <- tibble(
+  studyversion = "box",
+  sample = "kids",
+  split = "permutated",
+  stratification = "none",
+  mean = box_permutated_kids)
+
+box_permutated_kids_tbl$CI_lower = numeric(nrow(box_permutated_kids_tbl))
+box_permutated_kids_tbl$CI_upper = numeric(nrow(box_permutated_kids_tbl))
+
+for(i in 1:nrow(box_permutated_kids_tbl)) {
+  box_permutated_kids_tbl$CI_lower[i] <- box_permutated_kids_ci[[i]]$lims["0.025","bca"]
+  box_permutated_kids_tbl$CI_upper[i] <- box_permutated_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = mean(box_permutated_kids_tbl$mean),
+                                        CI_lower = mean(box_permutated_kids_tbl$CI_lower),
+                                        CI_upper = mean(box_permutated_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_kids_permutated_stratified}
+# permutated splitting stratified by target position
+splitscores_box_permutatedStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_permutatedStrat_kids <- split_coefs(splitscores_box_permutatedStrat_kids, cor)
+
+splitscores_box_permutatedStrat_kids_uniq_reps <- unique(splitscores_box_permutatedStrat_kids$replication)
+
+splitscores_box_permutatedStrat_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_permutatedStrat_kids, replication==r), cor))
+}
+
+box_permutatedStrat_kids_ci <- mclapply(splitscores_box_permutatedStrat_kids_uniq_reps, splitscores_box_permutatedStrat_kids_parallel_split_ci, mc.cores=48)
+
+box_permutatedStrat_kids_tbl <- tibble(
+  studyversion = "box",
+  sample = "kids",
+  split = "random",
+  stratification = "target position",
+  mean = box_permutatedStrat_kids)
+
+box_permutatedStrat_kids_tbl$CI_lower = numeric(nrow(box_permutatedStrat_kids_tbl))
+box_permutatedStrat_kids_tbl$CI_upper = numeric(nrow(box_permutatedStrat_kids_tbl))
+
+for(i in 1:nrow(box_permutatedStrat_kids_tbl)) {
+  box_permutatedStrat_kids_tbl$CI_lower[i] <- box_permutatedStrat_kids_ci[[i]]$lims["0.025","bca"]
+  box_permutatedStrat_kids_tbl$CI_upper[i] <- box_permutatedStrat_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = mean(box_permutatedStrat_kids_tbl$mean),
+                                        CI_lower = mean(box_permutatedStrat_kids_tbl$CI_lower),
+                                        CI_upper = mean(box_permutatedStrat_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_kids_montecarlo}
+# monte carlo (sampling with replacement)
+splitscores_box_montecarlo_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+box_montecarlo_kids <- split_coefs(splitscores_box_montecarlo_kids, cor)
+
+splitscores_box_montecarlo_kids_uniq_reps <- unique(splitscores_box_montecarlo_kids$replication)
+
+splitscores_box_montecarlo_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_montecarlo_kids, replication==r), cor))
+}
+
+box_montecarlo_kids_ci <- mclapply(splitscores_box_montecarlo_kids_uniq_reps, splitscores_box_montecarlo_kids_parallel_split_ci, mc.cores=48)
+
+box_montecarlo_kids_tbl <- tibble(
+  studyversion = "box",
+  sample = "kids",
+  split = "Monte Carlo",
+  stratification = "none",
+  mean = box_montecarlo_kids)
+
+box_montecarlo_kids_tbl$CI_lower = numeric(nrow(box_montecarlo_kids_tbl))
+box_montecarlo_kids_tbl$CI_upper = numeric(nrow(box_montecarlo_kids_tbl))
+
+for(i in 1:nrow(box_montecarlo_kids_tbl)) {
+  box_montecarlo_kids_tbl$CI_lower[i] <- box_montecarlo_kids_ci[[i]]$lims["0.025","bca"]
+  box_montecarlo_kids_tbl$CI_upper[i] <- box_montecarlo_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = mean(box_montecarlo_kids_tbl$mean),
+                                        CI_lower = mean(box_montecarlo_kids_tbl$CI_lower),
+                                        CI_upper = mean(box_montecarlo_kids_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_kids_montecarlo_stratified}
+# monte carlo stratified by target position
+splitscores_box_montecarloStrat_kids <- by_split(
+  box_intCon_data %>% filter(sample == "kids"),
+  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
+)
+
+box_montecarloStrat_kids <- split_coefs(splitscores_box_montecarloStrat_kids, cor)
+
+splitscores_box_montecarloStrat_kids_uniq_reps <- unique(splitscores_box_montecarloStrat_kids$replication)
+
+splitscores_box_montecarloStrat_kids_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_montecarloStrat_kids, replication==r), cor))
+}
+
+box_montecarloStrat_kids_ci <- mclapply(splitscores_box_montecarloStrat_kids_uniq_reps, splitscores_box_montecarloStrat_kids_parallel_split_ci, mc.cores=48)
+
+box_montecarloStrat_kids_tbl <- tibble(
+  studyversion = "box",
+  sample = "kids",
+  split = "Monte Carlo",
+  stratification = "target position",
+  mean = box_montecarloStrat_kids)
+
+box_montecarloStrat_kids_tbl$CI_lower = numeric(nrow(box_montecarloStrat_kids_tbl))
+box_montecarloStrat_kids_tbl$CI_upper = numeric(nrow(box_montecarloStrat_kids_tbl))
+
+for(i in 1:nrow(box_montecarloStrat_kids_tbl)) {
+  box_montecarloStrat_kids_tbl$CI_lower[i] <- box_montecarloStrat_kids_ci[[i]]$lims["0.025","bca"]
+  box_montecarloStrat_kids_tbl$CI_upper[i] <- box_montecarloStrat_kids_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "kids",
+                                        studyversion = "box",
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = mean(box_montecarloStrat_kids_tbl$mean),
+                                        CI_lower = mean(box_montecarloStrat_kids_tbl$CI_lower),
+                                        CI_upper = mean(box_montecarloStrat_kids_tbl$CI_upper),
+                                      )
+```
+
+## Splithalf Reliability - Box Adults
+
+```{r splithalfr_box_adults_firstsecond}
+# first-second half split
+splitscores_box_firstsecond_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F
+)
+
+box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
+box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "first-second",
+                                        stratification = "none",
+                                        coefficient = box_firstsecond_adults,
+                                        CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"],
+                                        CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
+                                      )
+
+# first-second half stratified by target position
+splitscores_box_firstsecondStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("first_second"),
+  ncores = 1,
+  verbose = F,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
+box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "first-second",
+                                        stratification = "target position",
+                                        coefficient = box_firstsecondStrat_adults,
+                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"],
+                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_adults_oddeven}
+# odd-even split
+splitscores_box_oddeven_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F
+)
+
+box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
+box_oddeven_adults_ci <- split_ci(splitscores_box_oddeven_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "odd-even",
+                                        stratification = "none",
+                                        coefficient = box_oddeven_adults,
+                                        CI_lower = box_oddeven_adults_ci$lims["0.025","bca"],
+                                        CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
+                                      )
+
+# odd-even split stratified by target position
+splitscores_box_oddevenStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  method = c("odd_even"),
+  ncores = 1,
+  verbose = F,
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
+box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "odd-even",
+                                        stratification = "target position",
+                                        coefficient = box_oddevenStrat_adults,
+                                        CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"],
+                                        CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
+                                      )
+```
+
+```{r splithalfr_box_adults_permutated}
+# permutated splitting (random sampling without replacement)
+splitscores_box_permutated_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+box_permutated_adults <- split_coefs(splitscores_box_permutated_adults, cor)
+
+splitscores_box_permutated_adults_uniq_reps <- unique(splitscores_box_permutated_adults$replication)
+
+splitscores_box_permutated_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_permutated_adults, replication==r), cor))
+}
+
+box_permutated_adults_ci <- mclapply(splitscores_box_permutated_adults_uniq_reps, splitscores_box_permutated_adults_parallel_split_ci, mc.cores=48)
+
+box_permutated_adults_tbl <- tibble(
+  studyversion = "box",
+  sample = "adults",
+  split = "permutated",
+  stratification = "none",
+  mean = box_permutated_adults)
+
+box_permutated_adults_tbl$CI_lower = numeric(nrow(box_permutated_adults_tbl))
+box_permutated_adults_tbl$CI_upper = numeric(nrow(box_permutated_adults_tbl))
+
+for(i in 1:nrow(box_permutated_adults_tbl)) {
+  box_permutated_adults_tbl$CI_lower[i] <- box_permutated_adults_ci[[i]]$lims["0.025","bca"]
+  box_permutated_adults_tbl$CI_upper[i] <- box_permutated_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "permutated",
+                                        stratification = "none",
+                                        coefficient = mean(box_permutated_adults_tbl$mean),
+                                        CI_lower = mean(box_permutated_adults_tbl$CI_lower),
+                                        CI_upper = mean(box_permutated_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_adults_permutated_stratified}
+# permutated splitting stratified by target position
+splitscores_box_permutatedStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_permutatedStrat_adults <- split_coefs(splitscores_box_permutatedStrat_adults, cor)
+
+splitscores_box_permutatedStrat_adults_uniq_reps <- unique(splitscores_box_permutatedStrat_adults$replication)
+
+splitscores_box_permutatedStrat_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_permutatedStrat_adults, replication==r), cor))
+}
+
+box_permutatedStrat_adults_ci <- mclapply(splitscores_box_permutatedStrat_adults_uniq_reps, splitscores_box_permutatedStrat_adults_parallel_split_ci, mc.cores=48)
+
+box_permutatedStrat_adults_tbl <- tibble(
+  studyversion = "box",
+  sample = "adults",
+  split = "random",
+  stratification = "target position",
+  mean = box_permutatedStrat_adults)
+
+box_permutatedStrat_adults_tbl$CI_lower = numeric(nrow(box_permutatedStrat_adults_tbl))
+box_permutatedStrat_adults_tbl$CI_upper = numeric(nrow(box_permutatedStrat_adults_tbl))
+
+for(i in 1:nrow(box_permutatedStrat_adults_tbl)) {
+  box_permutatedStrat_adults_tbl$CI_lower[i] <- box_permutatedStrat_adults_ci[[i]]$lims["0.025","bca"]
+  box_permutatedStrat_adults_tbl$CI_upper[i] <- box_permutatedStrat_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "permutated",
+                                        stratification = "target position",
+                                        coefficient = mean(box_permutatedStrat_adults_tbl$mean),
+                                        CI_lower = mean(box_permutatedStrat_adults_tbl$CI_lower),
+                                        CI_upper = mean(box_permutatedStrat_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_adults_montecarlo}
+# monte carlo (sampling with replacement)
+splitscores_box_montecarlo_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+)
+
+box_montecarlo_adults <- split_coefs(splitscores_box_montecarlo_adults, cor)
+
+splitscores_box_montecarlo_adults_uniq_reps <- unique(splitscores_box_montecarlo_adults$replication)
+
+splitscores_box_montecarlo_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_montecarlo_adults, replication==r), cor))
+}
+
+box_montecarlo_adults_ci <- mclapply(splitscores_box_montecarlo_adults_uniq_reps, splitscores_box_montecarlo_adults_parallel_split_ci, mc.cores=48)
+
+box_montecarlo_adults_tbl <- tibble(
+  studyversion = "box",
+  sample = "adults",
+  split = "Monte Carlo",
+  stratification = "none",
+  mean = box_montecarlo_adults)
+
+box_montecarlo_adults_tbl$CI_lower = numeric(nrow(box_montecarlo_adults_tbl))
+box_montecarlo_adults_tbl$CI_upper = numeric(nrow(box_montecarlo_adults_tbl))
+
+for(i in 1:nrow(box_montecarlo_adults_tbl)) {
+  box_montecarlo_adults_tbl$CI_lower[i] <- box_montecarlo_adults_ci[[i]]$lims["0.025","bca"]
+  box_montecarlo_adults_tbl$CI_upper[i] <- box_montecarlo_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "Monte Carlo",
+                                        stratification = "none",
+                                        coefficient = mean(box_montecarlo_adults_tbl$mean),
+                                        CI_lower = mean(box_montecarlo_adults_tbl$CI_lower),
+                                        CI_upper = mean(box_montecarlo_adults_tbl$CI_upper),
+                                      )
+```
+
+```{r splithalfr_box_adults_montecarlo_stratified}
+# monte carlo stratified by target position
+splitscores_box_montecarloStrat_adults <- by_split(
+  box_intCon_data %>% filter(sample == "adults"),
+  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
+  fn_score_box,
+  replications = 5000,
+  method = c("random"),
+  replace = TRUE,
+  split_p = 1,
+  ncores = 7, # setting ncores equally to something less than detectCores()
+  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
+)
+
+box_montecarloStrat_adults <- split_coefs(splitscores_box_montecarloStrat_adults, cor)
+
+splitscores_box_montecarloStrat_adults_uniq_reps <- unique(splitscores_box_montecarloStrat_adults$replication)
+
+splitscores_box_montecarloStrat_adults_parallel_split_ci <- function(r) {
+        return(split_ci(filter(splitscores_box_montecarloStrat_adults, replication==r), cor))
+}
+
+box_montecarloStrat_adults_ci <- mclapply(splitscores_box_montecarloStrat_adults_uniq_reps, splitscores_box_montecarloStrat_adults_parallel_split_ci, mc.cores=48)
+
+box_montecarloStrat_adults_tbl <- tibble(
+  studyversion = "box",
+  sample = "adults",
+  split = "Monte Carlo",
+  stratification = "target position",
+  mean = box_montecarloStrat_adults)
+
+box_montecarloStrat_adults_tbl$CI_lower = numeric(nrow(box_montecarloStrat_adults_tbl))
+box_montecarloStrat_adults_tbl$CI_upper = numeric(nrow(box_montecarloStrat_adults_tbl))
+
+for(i in 1:nrow(box_montecarloStrat_adults_tbl)) {
+  box_montecarloStrat_adults_tbl$CI_lower[i] <- box_montecarloStrat_adults_ci[[i]]$lims["0.025","bca"]
+  box_montecarloStrat_adults_tbl$CI_upper[i] <- box_montecarloStrat_adults_ci[[i]]$lims["0.975","bca"]
+}
+
+splithalf_data <- splithalf_data %>% add_row(
+                                        sample = "adults",
+                                        studyversion = "box",
+                                        method = "Monte Carlo",
+                                        stratification = "target position",
+                                        coefficient = mean(box_montecarloStrat_adults_tbl$mean),
+                                        CI_lower = mean(box_montecarloStrat_adults_tbl$CI_lower),
+                                        CI_upper = mean(box_montecarloStrat_adults_tbl$CI_upper),
+                                      )
+```
+
+## Splithalf Reliability Table & Plot
 ```{r splithalf_plot}
-# splithalf_data %>% 
-#   mutate(
-#     sample = fct_rev(sample), 
-#   ) %>%
-#   unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
-#   mutate(samplegroup = fct_rev(samplegroup)) %>%
-#   unite("methodStrat", c(method, stratification), sep = " - ", remove = FALSE) %>% 
-#   mutate(
-#     methodStrat = factor(methodStrat, levels = c("first-second - none", "first-second - target position", "odd-even - none", "odd-even - target position", "permutated - none", "permutated - target position", "Monte Carlo - none", "Monte Carlo - target position")) %>% fct_rev(),
-#   ) %>%  
-#   ggplot(aes(x = methodStrat, y = coefficient, color = sample, group = studyversion)) + 
-#     geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
-#     geom_point(position = position_dodge(0.1), size = 3) +
-#     scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
-#     scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
-#     labs(x = "Splitting & stratification method", y = "") +
-#     coord_flip() + 
-#     facet_wrap(~ samplegroup, nrow = 1) + 
-#     theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
-# 
+splithalf_plot <- splithalf_data %>%
+  mutate(
+    sample = fct_rev(sample),
+  ) %>%
+  unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>%
+  mutate(samplegroup = fct_rev(samplegroup)) %>%
+  unite("methodStrat", c(method, stratification), sep = " - ", remove = FALSE) %>%
+  mutate(
+    methodStrat = factor(methodStrat, levels = c("first-second - none", "first-second - target position", "odd-even - none", "odd-even - target position", "permutated - none", "permutated - target position", "Monte Carlo - none", "Monte Carlo - target position")) %>% fct_rev(),
+  ) %>%
+  ggplot(aes(x = methodStrat, y = coefficient, color = sample, group = studyversion)) +
+    geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
+    geom_point(position = position_dodge(0.1), size = 3) +
+    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
+    scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
+    labs(x = "Splitting & stratification method", y = "") +
+    coord_flip() +
+    facet_wrap(~ samplegroup, nrow = 1) +
+    theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))
+
+splithalf_plot
+saveRDS(splithalf_plot, file = "../saves/gafo-splithalf-plot.rds")
 # ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
@@
 ```{r splithalf_table}
-# knitr::kable(splithalf_data)
+knitr::kable(splithalf_data)
 ```
@@
 ```{r save_splithalf_data}
-# write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
-# saveRDS(splithalf_data, file = "../saves/gafo-splithalf.rds")
+write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
+saveRDS(splithalf_data, file = "../saves/gafo-splithalf-table.rds")
 ```

### 2022-08-10 stats/analysis.Rmd
delete ext vali section

@@
                     inits  = "random",
-                    cores  = 4)
+                    cores  = 100)
 
@@
   method = c("random"),
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
 )
@@
   method = c("random"),
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
@@
   split_p = 1,
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
 )
@@
   split_p = 1,
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
@@
   method = c("random"),
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
@@
   split_p = 1,
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
@@
   method = c("random"),
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
@@
   split_p = 1,
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
@@
   method = c("random"),
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
@@
   split_p = 1,
-  ncores = 7, # setting ncores equally to something less than detectCores()
+  ncores = 100, # setting ncores equally to something less than detectCores()
   stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
@@
 saveRDS(splithalf_data, file = "../saves/gafo-splithalf-table.rds")
-```
-
-## Test-retest reliability
+
+# clean up
+rm(list = ls(pattern = "^splitscores"))
+```
+
+## Test-retest Reliability - Hedge
 
@@
                               inits  = "random",
-                              cores  = 4)
+                              cores  = 100)
 
@@
 
-ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
+saveRDS(hedge_retest_kids, file = "../saves/gafo-hedge-retest-kids.rds")
+# ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
 ```
@@
 
-ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
-```
+saveRDS(hedge_retest_adults, file = "../saves/gafo-hedge-retest-adults.rds")
+# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+```
+
+## Test-retest Reliability - Box
 
 ```{r retest_box_data}
-# take data of first reli day for internal consistency
 box_retest <- reli %>% 
@@
 
-# check how many there are
+# check how many there are => there are none!
 box_retest %>% 
@@
 
-ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
+saveRDS(box_retest_kids, file = "../saves/gafo-box-retest-kids.rds")
+# ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
 ```
@@
 
-ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+saveRDS(box_retest_adults, file = "../saves/gafo-box-retest-adults.rds")
+# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
 ```
@@
 ```{r arrange_plots}
-ggarrange(
+gafo_arrangedplot <- ggarrange(
 
@@
 
-ggsave("../figures/gafo_results_GLMM.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
-```
-
-```{r}
-ggarrange(hedge_variation_plot,
-          NULL,
-          ggarrange(
-              hedge_intCon_kids, 
-              hedge_retest_kids, 
-              nrow = 1, 
-              ncol = 2, 
-              labels = c("B", "C")
-            ), 
-          nrow = 3, heights = c(0.625, 0.05, 0.325), labels = c("A", "", "")
-)
-
-ggsave("/Users/julia_prein/Downloads/gafo_poster.png", width = 6.5, height = 6, scale = 1.1, bg = "white")
-```
-
-# EXTERNAL VALIDITY
-
-```{r extvali_prepareData}
-mDataExtvali <- testtrials %>% 
-  filter(ageInYears < 6) %>% 
-  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, symmetricPosition) %>%
-  group_by(subjID) %>% 
-  # so that all models run with same nr of subjects
-  drop_na() %>% 
-  ungroup() %>% 
-  mutate(
-    # centered around minimum
-    hhSibs = siblingsNr, 
-    sibsChildAged = siblingsChildAged,
-
-    # centered around mean
-    trial = scale(trialNr, center = TRUE, scale = FALSE)[,1],
-    ccAge = scale(childcareAge, center = TRUE, scale = FALSE)[,1],
-    ccHours = scale(childcareHours, center = TRUE, scale = FALSE)[,1],
-    hhTotal = scale(householdTotal, center = TRUE, scale = FALSE)[,1],
-
-    # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
-    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE)[,1],
-    pe = scale(peerExposure, center = TRUE, scale = TRUE)[,1], 
-  ) %>% 
-  select(datacollection, studyversion, subjID, trial, age, targetPosition, symmetricPosition, correctBox, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>%
-  mutate_if(is.character, as.factor)
-
-n_distinct(mDataExtvali$subjID)
-```
-
-```{r extvali_nullmodel}
-mExtvalinull <- brm(correctBox ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                    data = mDataExtvali,
-                    family = bernoulli(link = "logit"),
-                    warmup = 1000, 
-                    iter   = 3000, 
-                    chains = 4, 
-                    inits  = "random",
-                    cores  = 4)
-```
-
-```{r extvali_fullmodels}
-mExtvaliccAge <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ ccAge + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"),
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvaliccHours <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ ccHours + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvalihhTotal <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ hhTotal + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvalihhSibs <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ hhSibs + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvalisibsChildAged <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ sibsChildAged + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvalisiblingsVarietyScoreP <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ siblingsVarietyScoreP + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvalisiblingsVarietyScoreW <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ siblingsVarietyScoreW + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-
-mExtvaliPE <- update(mExtvalinull,
-                      newdata = mDataExtvali,
-                      formula = correctBox ~ pe + age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition),
-                      family = bernoulli(link = "logit"), 
-                      warmup = 1000, 
-                      iter   = 3000, 
-                      chains = 4, 
-                      inits  = "random",
-                      cores  = 4)
-```
-
-```{r extvali_modelcomparisons}
-mExtvalinull <- add_criterion(mExtvalinull, "waic")
-mExtvaliccAge <- add_criterion(mExtvaliccAge, "waic")
-mExtvaliccHours <- add_criterion(mExtvaliccHours, "waic")
-mExtvalihhTotal <- add_criterion(mExtvalihhTotal, "waic")
-mExtvalihhSibs <- add_criterion(mExtvalihhSibs, "waic")
-mExtvalisibsChildAged <- add_criterion(mExtvalisibsChildAged, "waic")
-mExtvalisiblingsVarietyScoreP <- add_criterion(mExtvalisiblingsVarietyScoreP, "waic")
-mExtvalisiblingsVarietyScoreW <- add_criterion(mExtvalisiblingsVarietyScoreW, "waic")
-mExtvaliPE <- add_criterion(mExtvaliPE, "waic")
-
-mExtvaliComparison <- as_tibble(loo_compare(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")
-
-mExtvaliComparison
-
-mExtvaliComparisonWeights <- as_tibble(model_weights(mExtvalinull, mExtvaliccAge, mExtvaliccHours, mExtvalihhTotal, mExtvalihhSibs, mExtvalisibsChildAged, mExtvalisiblingsVarietyScoreP, mExtvalisiblingsVarietyScoreW, mExtvaliPE, criterion = "waic"), rownames = "model")
-
-mExtvaliComparisonWeights %>% arrange(-value)
-
-extvaliModelorder <- mExtvaliComparisonWeights %>% arrange(value) %>%  pull(model)
-```
-
-```{r extvali_savemodels}
-write.csv(mExtvalinull, "../saves/extvali-mExtvalinull.csv", quote = F, row.names = F)
-saveRDS(mExtvalinull, "../saves/extvali-mExtvalinull.rds")
-
-write.csv(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.csv", quote = F, row.names = F)
-saveRDS(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.rds")
-
-write.csv(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.csv", quote = F, row.names = F)
-saveRDS(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.rds")
-
-write.csv(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.csv", quote = F, row.names = F)
-saveRDS(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.rds")
-
-write.csv(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.csv", quote = F, row.names = F)
-saveRDS(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.rds")
-
-write.csv(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.csv", quote = F, row.names = F)
-saveRDS(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.rds")
-
-write.csv(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.csv", quote = F, row.names = F)
-saveRDS(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.rds")
-
-write.csv(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.csv", quote = F, row.names = F)
-saveRDS(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.rds")
-
-write.csv(mExtvaliPE, "../saves/extvali-mExtvaliPE.csv", quote = F, row.names = F)
-saveRDS(mExtvaliPE, "../saves/extvali-mExtvaliPE.rds")
-```
-
-```{r extvali_save}
-extvali_results <- mExtvaliComparison %>%
-  left_join(mExtvaliComparisonWeights) %>%
-  select(model, waic, se_waic, value, elpd_diff, se_diff) %>%
-  rename(
-    Predictor = model, 
-    WAIC = waic, 
-    SE_WAIC = se_waic,
-    Weight = value, 
-    ELPD_DIFF = elpd_diff, 
-    SE_ELPD_DIFF = se_diff,
-  ) %>% 
-  mutate(
-    Predictor = recode(Predictor, 
-                   "mExtvaliPE" = "Peer exposure index", 
-                   "mExtvalisiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
-                   "mExtvalihhSibs" = "# Children in household aged 0-18", 
-                   "mExtvaliccHours" = "Average hours spent in childcare per day",
-                   "mExtvalinull" = "Null model", 
-                   "mExtvalihhTotal" = "# Household members",
-                   "mExtvaliccAge" = "Age of childcare entry", 
-                   "mExtvalisiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
-                   "mExtvalisibsChildAged" = "# Children in household aged 1-12",
-                   )
-  )
-
-write.csv(extvali_results, "../saves/extvali-results.csv", quote = F, row.names = F)
-saveRDS(extvali_results, "../saves/extvali-results.rds")
-```
-
-```{r extvali_posteriordraws}
-extvali_draws <- bind_rows(
-  mExtvaliccAge %>% gather_draws(b_ccAge),
-  mExtvaliccHours %>% gather_draws(b_ccHours), 
-  mExtvalihhTotal %>% gather_draws(b_hhTotal), 
-  mExtvalihhSibs %>% gather_draws(b_hhSibs), 
-  mExtvalisibsChildAged %>% gather_draws(b_sibsChildAged), 
-  mExtvalisiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
-  mExtvalisiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
-  mExtvaliPE %>% gather_draws(b_pe)
-  ) %>% 
-  mutate(
-    Predictor = factor(.variable, 
-                       levels = c("b_hhSibs", 
-                                  "b_siblingsVarietyScoreP", 
-                                  "b_sibsChildAged", 
-                                  "b_hhTotal", 
-                                  "b_ccHours", 
-                                  "b_ccAge", 
-                                  "b_siblingsVarietyScoreW", 
-                                  "b_pe"), 
-                       labels = c("# Children in household aged 0-18", 
-                                  "Sibling variety score (Peterson, 2000)", 
-                                  "# Children in household aged 1-12", 
-                                  "# Household members", 
-                                  "Average hours spent in childcare per day", 
-                                  "Age of childcare entry", 
-                                  "Sibling variety score (Cassidy et al., 2005)", 
-                                  "Peer exposure index")
-                       )  
-  )
-
-write.csv(extvali_draws, "../saves/extvali-draws.csv", quote = F, row.names = F)
-saveRDS(extvali_draws, "../saves/extvali-draws.rds")
-```
-
-```{r extvali_plot}
-ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
- tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 3) +
-    labs(x = "Posterior estimate", y = "")+
-  guides(fill = "none")+
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  scale_fill_manual(values = c("grey","#85AD00")) +
-  xlim(-0.2, 0.6) +
-  theme_minimal()
-
-ggsave("../figures/extvali_results_all.png", width = 10, height = 6, scale = 0.7, bg = "white")
-
-extvali_draws %>% 
-  filter(
-          Predictor == "Peer exposure index" ||
-          Predictor == "Sibling variety score (Cassidy et al., 2005)" ||
-          Predictor == "Number of children in household aged 0-18" ||
-          Predictor == "Average hours spent in childcare per day", 
-         ) %>% 
-  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
- tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
-    labs(x = "Posterior estimate", y = "") +
-  guides(fill = "none")+
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  scale_fill_manual(values = c("grey","#85AD00")) +
-  scale_x_continuous(limits = c(-0.6, 1), breaks = seq(-0.5, 1, 0.25)) + 
-  theme_minimal()
-
-ggsave("../figures/extvali_results.png", width = 10, height = 6, scale = 0.7, bg = "white")
-```
+gafo_arrangedplot
+saveRDS(gafo_arrangedplot, file = "../saves/gafo-arrangedplot.rds")
+# ggsave("../figures/gafo_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+```

### 2022-08-10 paper/manuscript.Rmd
complete run through script on stats server

@@
 library("papaja")
+library(ggplot2)
+theme_set(theme_classic())
 # r_refs("r-references.bib")
@@
 ```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+hedge_variation_plot_GLMM <- readRDS(file = "../saves/gafo-hedge-variation-plot-GLMM.rds")
+box_variation_plot_GLMM <- readRDS(file = "../saves/gafo-box-variation-plot-GLMM.rds")
+box_variation_plot_GLMM
+
 knitr::include_graphics(c("../figures/gafo_results.png"))

### 2022-08-10 paper/manuscript.Rmd
add final figures

--- 2022-08-09 paper/manuscript.Rmd
@@
 library("papaja")
-# r_refs("r-references.bib")
+library("ggplot2")
+library("ggpubr")
+theme_set(theme_classic())
 ```
@@
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
+Participants consisted of `r sum(vali_adults$nTotal)` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 ```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics(c("../figures/gafo_results.png"))
+knitr::include_graphics(c("../figures/gafo_arrangedplot.png"))
 ```
@@
 ```{r splithalf}
-splithalf <- readRDS(file = "../saves/gafo-splithalf.rds")
+splithalf <- readRDS(file = "../saves/gafo-splithalf-table.rds")
 ```
@@
 ### Webcam coding
-(ref:figlab5) **Model comparison for exploratory webcam coding of parental interference**. 
+(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**. 
 Factors of parental interference and their influence on the probability of responding correctly.
@@
 
-```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
 knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")

### 2022-08-10 paper/manuscript.tex
add final figures

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
-  pdflang={en-EN},
-  pdfkeywords={social cognition, individual differences, gaze cues, psychometrics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{longtable,booktabs,array}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
+  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
+  pdflang={en-EN},
+  pdfkeywords={social cognition, individual differences, gaze cues, psychometrics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of 50 and 50 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
+Participants consisted of 100 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/gafo_results}
+{\centering \includegraphics[width=1\linewidth]{../figures/gafo_arrangedplot}
 
@@
 Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CI {[}-0.50; -0.14{]}) were negative and reliably different from zero.
-In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.88{]}) and the estimate of data collection mode (\(\beta\) = 1.11 (95\% CI {[}0.68; 1.56{]}) were positive and reliably different from zero.
+In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.87{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CI {[}0.68; 1.56{]}) were positive and reliably different from zero.
 Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
@@
 Figure \ref{fig:fig3} compares splithalf reliability coefficients by splitting and stratification method (Pronk et al., 2021).
-In the hedge version, the splithalf reliability coefficients ranged from 0.57 to 0.84. In the box version, splithalf reliability coefficients ranged from 0.49 to 0.76.
+In the hedge version, the splithalf reliability coefficients ranged from 0.65 to 0.93. In the box version, splithalf reliability coefficients ranged from 0.48 to 0.86.
 Similarly to the results of Pronk et al.
@@
 
-The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.89 (95\% CI {[}0.65;1.00{]}).
-In the box version it was 0.91 (95\% CI {[}0.71;1.00{]}).
+The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.90 (95\% CI {[}0.67;1.00{]}).
+In the box version it was 0.91 (95\% CI {[}0.69;1.00{]}).
 
@@
 This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
-
-\hypertarget{validity}{%
-\section{Validity}\label{validity}}
-
-Our third aim was to assess whether the captured individual variation in gaze understanding relates to factors in children's real live social environment.
-Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018; Hughes \& Leekam, 2004), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016).
-It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind.
-Therefore, if we find a link between gaze understanding and family factors, we regard this as an indicator for the validity of our measure.
-
-\hypertarget{participants-2}{%
-\subsection{Participants}\label{participants-2}}
-
-For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
-109 children, including
-30 3-year-olds
-(mean = 41.82 months,
-SD = 3.31,
-range = 36
-- 47,
-19 girls),
-36 4-year-olds
-(mean = 54.32 months,
-SD = 2.95,
-range = 48
-- 59,
-27 girls),
-and 43 5-year-olds
-(mean = 66.43 months,
-SD = 3.48,
-range = 60
-- 71,
-22 girls).
-
-\hypertarget{procedure-2}{%
-\subsection{Procedure}\label{procedure-2}}
-
-Families of our kindergarten and online child sample were asked to fill out a brief demographic questionnaire.
-We asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-
-\hypertarget{analysis-2}{%
-\subsection{Analysis}\label{analysis-2}}
-
-To estimate the effects of social surrounding on gaze understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version).
-The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants.
-Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the gaze understanding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
-In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
-For the target position, we categorized two adjacent bins as one imaginary box.
-To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
-Across the two study versions, we could consequently model the participant's correct response (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
-For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
-In addition, we calculated three index scores.
-First, we calculated a sibling variety score according to Peterson (2000).
-Second, we implemented the modified version of Cassidy et al.
-(2005) (for more details, see Supplements).
-Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
-We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-
-\hypertarget{results-2}{%
-\subsection{Results}\label{results-2}}
-
-The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy.
-Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
-The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
-For example, for our winning model, we found a peer exposure estimate of \(\beta\) =
-0.17 (95\% CI {[}-0.03; 0.36{]}),
-with the estimates of age being \(\beta\) =0.57 (95\% CI {[}0.38; 0.77{]}), data collection mode being \(\beta\) =0.95 (95\% CI {[}0.56; 1.35{]}), and study version \(\beta\) =1.87 (95\% CI {[}0.25; 3.59{]}).
-Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
-The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/extvali_results}
-
-}
-
-\caption{\textbf{External validity of the gaze understanding task}.
-Factors of children's social surroundings and their influence on the probability of responding correctly.
-Models are ordered according to their WAIC scores, with the uppermost winning the model comparison.
-The graph shows the estimated density curves of a model's predictor coefficient.
-Only models performing better than our null model are included in the graph.}\label{fig:fig4}
-\end{figure}
-
-\hypertarget{discussion-2}{%
-\subsection{Discussion}\label{discussion-2}}
-
-We found that factors of children's social surrounding influenced their gaze understanding.
-Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables.
-Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding).
-Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze understanding.
 
@@
 
-After finding consistent and reliable individual estimates, we aimed at verifying the appropriateness of our new task.
+\hypertarget{todo-adjust-discussion-part-validity}{%
+\section{TODO adjust discussion part validity}\label{todo-adjust-discussion-part-validity}}
+
 Validity is often assessed by looking at concurrent relations between measures.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
-Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106.
-
 \leavevmode\vadjust pre{\hypertarget{ref-coelho2006searching}{}}%
@@
 \url{https://doi.org/10.1111/infa.12276}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
-Devine, R.
-T., \& Hughes, C.
-(2018).
-Family {Correlates} of {False Belief Understanding} in {Early Childhood}: {A Meta-Analysis}.
-\emph{Child Development}, \emph{89}(3), 971--987.
-\url{https://doi.org/10.1111/cdev.12682}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
-McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
@@
 \url{https://doi.org/10.1007/s10826-012-9643-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
-Perner, J., Ruffman, T., \& Leekam, S.
-R.
-(1994).
-Theory of {Mind Is Contagious}: {You Catch It} from {Your Sibs}.
-\emph{Child Development}, \emph{65}(4), 1228--1238.
-\url{https://doi.org/10.2307/1131316}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
-Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhang2021worse}{}}%
-Zhang, Z., Yu, H., Long, M., \& Li, H.
-(2021).
-Worse {Theory} of {Mind} in {Only-Children Compared} to {Children With Siblings} and {Its Intervention}.
-\emph{Frontiers in Psychology}, \emph{12}, 5073.
-\url{https://doi.org/10.3389/fpsyg.2021.754168}
-
 \end{CSLReferences}
@@
 (A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level.}\label{fig:fig5}
+(B) Analysis on a subject level.}\label{fig:fig4}
 \end{figure}
@@
 Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.\footnote{Attentive readers might notice that we simplified the structure of random effects.
-Compared to our models in the \emph{Individual differences} and \emph{External Validity} sections, this model does not include the random slope for symmetric target position within participants.
+Compared to our models in the \emph{Individual differences} section, this model does not include the random slope for symmetric target position within participants.
 We decided to do so since we had limited amount of data from few participants.}
@@
 
-\hypertarget{appendix-to-external-validity-section}{%
-\subsubsection{Appendix to external validity section}\label{appendix-to-external-validity-section}}
-
-\hypertarget{scoring-of-sibling-variety-scores}{%
-\paragraph{Scoring of sibling variety scores}\label{scoring-of-sibling-variety-scores}}
-
-For assessing the external validity of our gaze understanding task, we calculated two sibling variety scores based on the existing Theory of Mind literature.
-First, we followed the approach by Peterson (2000).
-Here, only-children as well as firstborns with siblings under one year scored 0 points; lastborns with siblings above 12 years scored 0.5 points; children with twins, firstborns with siblings over one year, and lastborns with at least one sibling under 13 years scored 1 point, middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
-
-Second, we implemented the sibling variety score by Cassidy et al.
-(2005).
-The authors adjusted the original score of Peterson (2000) in the following way: only-children scored 0 points; children with a sibling under one year or above 12 years, and twins with no other sibling scored 0.5 points; children with a sibling above one year or under 13 years scored 1 point; middleborns with at least one older and younger sibling aged one to 12 years scored 2 points.
-Twins with additional siblings scored depending on the age and number of their siblings.
-
-The reasoning was that children between one and 13 years of age would engage in sibling play, while the youngest and most mature siblings would be less likely to participate in such.
-However, teenage siblings might provide opportunities for interesting discussions (Peterson, 2000).
-
-\hypertarget{waic-scores-and-weights-of-the-model-comparison}{%
-\paragraph{WAIC scores and weights of the model comparison}\label{waic-scores-and-weights-of-the-model-comparison}}
-
-As can be seen, ELPD difference scores are smaller than their respective standard errors.
-WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}).
-All effects except when a child entered childcare positively influence performance.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:extvali_table}Model comparison for influences of children's social surrounding}
-
-\begin{tabular}{llllll}
-\toprule
-Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{SE\_WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD\_DIFF} & \multicolumn{1}{c}{SE\_ELPD\_DIFF}\\
-\midrule
-Average hours spent in childcare per day & 2,540.39 & 52.23 & 0.54 & 0.00 & 0.00\\
-Peer exposure index & 2,541.00 & 52.22 & 0.28 & -0.30 & 0.92\\
-\# Children in household aged 0-18 & 2,541.65 & 52.30 & 0.02 & -0.63 & 1.09\\
-Sibling variety score (Cassidy et al., 2005) & 2,541.76 & 52.33 & 0.01 & -0.68 & 1.05\\
-Sibling variety score (Peterson, 2000) & 2,541.80 & 52.38 & 0.02 & -0.71 & 1.10\\
-Age of childcare entry & 2,542.19 & 52.38 & 0.12 & -0.90 & 1.32\\
-\# Children in household aged 1-12 & 2,542.26 & 52.34 & 0.00 & -0.94 & 0.92\\
-Null model & 2,542.58 & 52.26 & 0.00 & -1.09 & 0.79\\
-\# Household members & 2,543.46 & 52.36 & 0.00 & -1.54 & 0.97\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \hypertarget{adult-sample}{%
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
-\toprule
+\toprule()
 \endhead
@@
 \textbf{sound for target click} & - & - & positive-feedback.mp3 \\
-\bottomrule
+\bottomrule()
 \end{longtable}

### 2022-08-10 stats/analysis.Rmd
add final figures

@@
 saveRDS(splithalf_plot, file = "../saves/gafo-splithalf-plot.rds")
+
 # ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)

### 2022-08-15 paper/manuscript.Rmd
correct data exclusion for retest hedge

@@
 library("ggpubr")
+library("tidyverse")
+library("brms")
 theme_set(theme_classic())
@@
 ```{r load_data}
-library(tidyverse)
-library(brms)
 testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
@@
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
@@
 Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
-Small points show the mean performance for each subject.
+Small points show the mean performance for each subject averaged across trials.
 Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection.
@@
 
-[^fn2]: In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
-The performance of the mentioned child was 3 standard deviations above the mean on both test days.
-Including the child yielded a *Pearson* correlation coefficient of *r* = 0.87.
+```{r hedge_retest_correlationcoefficients}
+hedge_retest_correlationcoefficients <- readRDS(file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
+```
+
+[^fn2]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
+The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
+Including the two children yielded a *Pearson* correlation coefficient of *r* = `r hedge_retest_correlationcoefficients$pearson_retest[hedge_retest_correlationcoefficients$sample == "kids" & hedge_retest_correlationcoefficients$analysis == "outlier included"]`.
+Including the two adults yielded a *Pearson* correlation coefficient of *r* = `r hedge_retest_correlationcoefficients$pearson_retest[hedge_retest_correlationcoefficients$sample == "adults" & hedge_retest_correlationcoefficients$analysis == "outlier included"]`.
 
@@
 (A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level.
+(B) Analysis on a subject level (i.e., average across trials per subject).
 
@@
 ```{r webcam_table, results = "asis"}
-# webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-#   mutate(across(c(WAIC, SE_WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>% 
-#   mutate_if(is.numeric, round, 2)
-#     
-# papaja::apa_table(
-#   webcam_models, 
-#   caption = "Model comparison for exploratory webcam coding of parental interference", 
-#   note = "All models included random intercepts for participant and target position.", 
-#   escape = T
-# )
+webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
+  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
+  mutate_if(is.numeric, round, 2)
+
+papaja::apa_table(
+  webcam_models,
+  caption = "Model comparison for exploratory webcam coding of parental interference",
+  note = "All models included random intercepts for participant and target position.",
+  escape = T
+)
 ```

### 2022-08-15 paper/manuscript.tex
correct data exclusion for retest hedge

@@
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
 The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
@@
 Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
-Small points show the mean performance for each subject.
+Small points show the mean performance for each subject averaged across trials.
 Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection.
@@
 
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 5-year-old child from the test-retest analysis.
-The performance of the mentioned child was 3 standard deviations above the mean on both test days.
-Including the child yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.87.}
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
+The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
+Including the two children yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.89.
+Including the two adults yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.73.}
 
@@
 (A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level.}\label{fig:fig4}
+(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig4}
 \end{figure}
@@
 Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
+
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
+\midrule
+By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
+By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
+By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
+By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
+By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
+By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
+By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
+By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
+By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
+By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
+By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
+By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2022-08-15 stats/analysis.Rmd
correct data exclusion for retest hedge

@@
 # exclude outliers
-hedge_retest <- hedge_retest %>%
-  filter(mean_reliday1 < mean(mean_reliday1) + 3*sd(mean_reliday1), mean_reliday1 > mean(mean_reliday1) - 3*sd(mean_reliday1),
-         mean_reliday2 < mean(mean_reliday2) + 3*sd(mean_reliday2), mean_reliday2 > mean(mean_reliday2) - 3*sd(mean_reliday2))
+hedge_retest_all <- hedge_retest
+
+hedge_retest <- hedge_retest_all %>%
+  group_by(sample) %>%
+  filter(mean_reliday1 <= mean(mean_reliday1) + 3*sd(mean_reliday1),
+         mean_reliday1 >= mean(mean_reliday1) - 3*sd(mean_reliday1),
+         mean_reliday2 <= mean(mean_reliday2) + 3*sd(mean_reliday2), 
+         mean_reliday2 >= mean(mean_reliday2) - 3*sd(mean_reliday2))
+
+# see how subject exclusion influences the retest correlation
+hedge_retest_correlationcoefficients <- rbind(
+  (hedge_retest %>%
+  group_by(sample) %>%
+  summarise(
+    n = n_distinct(subjID),
+    pearson_retest = cor(mean_reliday1, mean_reliday2, method = "pearson") %>% round(2), 
+    analysis = "outlier excluded",
+  )), 
+  (hedge_retest_all %>%
+  group_by(sample) %>%
+  summarise(
+    n = n_distinct(subjID),
+    pearson_retest = cor(mean_reliday1, mean_reliday2, method = "pearson") %>% round(2), 
+    analysis = "outlier included",
+  )))
+
+hedge_retest_correlationcoefficients
+
+saveRDS(hedge_retest_correlationcoefficients, file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
 ```

### 2022-08-17 paper/manuscript.Rmd
first complete draft of discussion

@@
 shorttitle        : "gaze understanding"
+author:
 
-author: 
   - name          : "Julia Prein"
@@
     affiliation   : "1"
-
   - name          : "Steven Kalinke"
@@
     affiliation   : "1"
-
 affiliation:
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+authornote: |
+abstract: |
 
-authornote: |
-
-abstract: |
   To explain and predict the behavior of agents, we use social cognition: we represent and reason about others' perspectives, knowledge, intentions, beliefs, and preferences.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-
-keywords          : "social cognition, individual differences, gaze cues, psychometrics"
+keywords          : "social cognition, individual differences, gaze cues, cognitive development"
 wordcount         : "X"
-
 bibliography      : ["../../references.bib"]
-
 floatsintext      : yes
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
-
 header-includes:
@@
   - \captionsetup[figure]{font={stretch=1}}
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 # Introduction
-Social cognition -- representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
+Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
 In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development [@gopnik1991young; @wellman2001metaanalysis; @wellman2004scaling; @peterson2012mind; @rakoczy2022foundations].
 Yet, there are always individual differences.
-Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions 
-[@happe2017structure; @mundy2007individual; @kidd2018individual; @underwood1975individual; @lecce2014promoting].
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions [@happe2017structure; @mundy2007individual; @kidd2018individual; @underwood1975individual; @lecce2014promoting].
 
@@
 However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding].
-This might be because traditional measures of social cognition are not designed to capture variation between children: 
-they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent review showed that many atudies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].
+This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].
 
@@
 Participants then get asked where Sally will look for her marble once she returns.
-The outcome measures false belief understanding in a dichotomous way: 
-children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket. 
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
 Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysis].
-Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
+Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf.
+@mayer2015weird].
 
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
-Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability]. 
-As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
+Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences [cf.
+"reliability paradox", @hedge2018reliability].
+As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
 This has profound implications for what studies on individual differences using this task (or others) can show.
@@
 New tasks should induce variation across age groups, including older children and adults [@repacholi2003introduction].
-Another goal in creating new tasks should be to focus on "face value": 
-measures should probe the underlying social-cognitive ability as straight-forward and directly as possible. 
+Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
+Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical and demographic contexts [@molleman2019unleashing].
 The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].
@@
 # A new measure of gaze understanding
-
 Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
-We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes: 
-gaze understanding -- the ability to locate and use the attentional focus of an agent. 
-The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- 
-and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
+We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
+The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
@@
 
-To address the psychometric shortcoming of earlier work, we implemented the following design features: 
-First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages. 
+To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages.
 Second, we designed short trials that facilitate more than a dozen replicates per subject.
@@
 # Task design
-
 ## Implementation
-The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
+The code is open-source (<https://github.com/ccp-eva/gafo-demo>) and a live demo version can be found under: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
 
@@
 The target then falls to the ground.
-At all times, the agent’s gaze tracks the movement of the target.
+At all times, the agent's gaze tracks the movement of the target.
 That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
@@
 Participants are then asked to locate the target: they respond by touching or clicking on the screen.
-Visual access to the target’s true location is manipulated by a hedge.
+Visual access to the target's true location is manipulated by a hedge.
 Participants either have full, partial, or no visual access to the true target location.
-When partial or no information about the target location is accessible, participants are expected to use the agent’s gaze as a cue.
+When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.
 
@@
 For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback so that learning effects are reduced and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 In test trials, participants have no visual access to the target flight or the end location.
-Participants are expected to use the agent’s gaze as a cue to locate the target.
+Participants are expected to use the agent's gaze as a cue to locate the target.
 The first trial of each type comprises a voice-over description of the presented events.
@@
 In the hedge version, participants have to indicate their estimated target location directly on a hedge.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant’s click.
+Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
 In the box version, the target lands in a box and participants are asked to click on the box that hides the target.
@@
 (A) Infrastructure for online testing.
-(i) Subjects aged 3 – 99+ can participate.
+(i) Subjects aged 3 -- 99+ can participate.
 Data collection can take place anywhere: online, in kindergartens or research labs.
@@
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.
+(C) Box version (discrete) of the gaze understanding task.
+Number of boxes (min.
+1; max.
+8) as potential hiding locations can be set according to the researcher's need.
 
@@
 Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
-Furthermore, we were interested in how the data collection mode influences responses.
+Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.
 
-Methods, sample size and analysis were pre-registered: https://osf.io/snju6 (child sample) and https://osf.io/r3bhn (adult sample).
+Methods, sample size and analysis were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
 Participants were equally distributed across the two study versions.
@@
   filter(ageInYears == 18) %>% 
+  ungroup() %>% 
   mutate(
@@
 ```
+
 ## Participants
 We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
-In-person testing with children took place in kindergartens in Leipzig, Germany. The in-person child sample consisted of 
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
-and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).
+In-person testing with children took place in kindergartens in Leipzig, Germany.
+The in-person child sample consisted of `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).
 
-For our remote child sample, we recruited families via an internal database.
-The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
-`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
-and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
-SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
-range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
-- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
-`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
+For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in studies on child development and who indicated interest in online studies.
+Families received an email with a short study description and a personalized link, and received a reminder two weeks later if they had not already participated in the study.
+
+The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
 Children in our sample grow up in an industrialized, urban Central-European context.
@@
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of `r sum(vali_adults$nTotal)` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
+Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 (A) Developmental trajectory in continuous hedge version.
-Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click.
+Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
 The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
@@
 (J) Test-retest reliability in box adult sample.
-Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
+For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode.
+For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
 Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
@@
 For example, some three-year-olds were more precise in their responses than some five-year-olds.
-Even though variation is smaller, we even find inter-individual differences in the adult sample.
+Even though variation is smaller, we could even find inter-individual differences in the adult sample.
 
@@
 It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^fn1]
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^1]
 
-[^fn1]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+[^1]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
     We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
@@
 ## Discussion
-Our task induced inter-individual variation in both adults and children.
+Our task induced inter-individual variation in both children and adults.
 We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
@@
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
-This illustrates the flexibility of the task.
+This illustrates the flexibility of the task design.
 
 # Internal consistency and retest reliability
-
 As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
-We assessed internal consistency (split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: https://osf.io/xqm73 for child sample, and https://osf.io/nu62m adult sample).
+We assessed internal consistency (as splithalf reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: <https://osf.io/xqm73> for the child sample, and <https://osf.io/nu62m> for the adult sample).
 Participants were equally distributed across the two study versions.
 The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between July 2021 and April 2022.
+Data was collected between July 2021 and June 2022.
 
@@
   ) %>% 
+  group_by(subjID) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
   summarise(
@@
     nFemales = sum(female),
-  ) %>% 
-  mutate(
-    nFemales = ifelse(studyversion == "hedge", nFemales/60, nFemales/64), # test trials * 2
-    nFemales = ceiling(nFemales)
   )
 ```
+
 ## Participants
-Participants were recruited in the same way as in the previous study. The child sample consisted of 
-`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
-`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
-(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
-SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
-range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
-- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
-`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
-`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
-(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
-SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
-range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
-- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
-`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
-and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
-(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
-SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
-range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
-- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
-`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).
+Participants were recruited in the same way as in the previous study.
+The child sample consisted of `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` - `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, `r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls), `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` - `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, `r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls), and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` - `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, `r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).
 
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-@pronk2021methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+@pronk2021methods recently compared various methods for computing splithalf reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics].
-We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
-The model computes a correlation between the participant specific estimates for each test day.
+The model computes a correlation between the participant-specific estimates for each test day.
 This can be interpreted as the test-retest reliability.
@@
 Error bars show the 95% confidence intervals of the coefficient estimates, calculated with the function `by_split` from the `splithalfr` package [@pronk2021methods].
+
 ```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
@@
 ```
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^fn2]
 
@@
 
-[^fn2]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
+For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^2]
+
+[^2]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
     The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
@@
 The age-corrected, GLMM based retest reliabilities for children yielded similar results.
-In hedge version it was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
-In the box version it was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the hedge version, the correlation between testdays was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the box version, the correlation between testdays was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
 
@@
 # General Discussion
-In this paper, we presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan. 
+We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
 This paper contributes to methodological advances in developmental psychology in the following ways.
-First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person. 
-Second, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates. 
-Finally, we found that gaze understanding relates to aspects of children's everyday experience.
-The web app (https://ccp-odc.eva.mpg.de/gafo-demo/) and its source code (https://github.com/ccp-eva/gafo-demo) are openly accessible.
+First, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+Individuals behaved consistently different from one another.
+Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
+Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
+In sum, our gaze understanding task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.The web app (<https://ccp-odc.eva.mpg.de/gafo-demo/>) and its source code (<https://github.com/ccp-eva/gafo-demo>) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
 
-One of the main contributions of this paper is that our newly presented gaze understanding task induces variation between participants. 
+One of the main contributions of the gaze understanding task is that it induces variation between participants.
 This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
-Our experimental design enables a continuous outcome measure, which again quantifies individual differences.
 
 In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version: 
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
+The outcome measure depends on the presented study version: in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
+
+Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) towards an ability on a continuum [@hughes2015individual; @beaudoin2020systematic].
+Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
+Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building [@hedge2018reliability].
+
 Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
-Both study versions exhibit high retest reliability. 
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates [cf. @hughes2000good; improved reliability through aggregation]. 
+Both study versions exhibit high retest reliability, also when controlling for age.
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
 When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
-However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
-In addition, researchers could induce different levels of salience for each box.
-Our task could consequently be used to study bias, preferences and diverse desires (e.g.
-matching the box appearance to some feature of the agent).
-In sum, our task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
+Our task could consequently be used to study bias, preferences and diverse desires (e.g. matching the box appearance to some feature/behavioral characteristic of the agent).
+
+Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
+Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+Another task extension could realize differential feedback dependent on the participant's accuracy.
+By inducing more between-person variance, reliability estimates could further increase.
+
+As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
+A potentially promising approach are computational cognitive models.
+We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
+Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual]
 
@@
 This enables presentation across devices without any prior installation.
-Stimuli presentation is achieved through the use of SVGs. This has several advantages: 
-the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays. 
+Stimuli presentation is achieved through the use of SVGs.
+This has several advantages: the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
+The cartoon-like presentation makes the task engaging for children and adults alike.
 Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
 Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
-The cartoon-like presentation makes the task engaging for children and adults alike.
 
-Participants can be tested in-person with supervision or remotely at home. 
+The web-based implementation allows for different data collection modes: participants can be tested in-person with supervision or remotely at home.
 Test instructions are standardized and, with prior informed consent, the webcam records study participation.
@@
 Children in the remote sample are slightly more precise.
-This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Appendix XXX). 
+This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
 Therefore, we recommend using a tablet for remote data collection.
-Children can then click for themselves and caregivers have less chance to interfere.
+Children can click for themselves and caregivers have less chance to interfere.
 
-# TODO adjust discussion part validity
+The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.
+
+After having proven satisfactory psychometric properties, the next step will be to ensure the validity of our task.
 Validity is often assessed by looking at concurrent relations between measures.
-Here we looked at a relation that is often postulated for social cognition tasks, namely that social-cognitive ability is predicted by family level variables.
-We found that children's gaze understanding relates to factors of their social environment: 
-children were more accurate, the more social exposure and the more diverse their surrounding was.
-However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items. 
-We hope that future technological advances will enable continuous measures of children's real life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
-
-## Future research
-Even though aggregate scores seem to improve reliability estimates [cf. @hughes2000good], they may smooth out noise that could be attributed to individual differences. 
-As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are. 
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity. 
-A potentially promising approach are computational cognitive models. 
-We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and interpretable manner. 
-Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual].
-
-Adding complexity to our gaze understanding task might increase individual differences in an adult sample. 
-Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
-By inducing more between-person variance, reliability estimates could further increase.
+Studies on gaze following traditionally present children with a simultaneous, congruent movement of eyes and head orientation.
+In our study, however, children only observe a subtle eye movement.
+Therefore, our results are not directly comparable to traditional gaze following studies.
+Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
+For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
+In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
+In addition, a subset of our remote child sample completed a receptive vocabulary task [@bohnorev].
+We will report the association between these family-level factors and children's language on their gaze understanding abilities in a separate paper (in preparation).
+In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
 
 Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-We aim at creating a task battery to study individual differences in various aspects of social cognition. 
-As @schaafsma2015deconstructing pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries.
+As has been pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries [@hughes2011individual; @schaafsma2015deconstructing].
 We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
 
-# Limitations
-
 # Conclusion
-  - big picture
-  - ind diff important for ..., good measures needed
-  - dedicated measures of ind diff instead of simply using well-established. reliability    paradox paper zitieren
-  - task & infrastructure
-  - foundations for more precise measures for cognitive development
-
----
-We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding. 
-The task is presented as an interactive web app that does not require any prior installation and works across devices. 
-Data collection is enabled at scale, with supervised and remote testing and standardized test instructions.
-Stimuli presentation is achieved through the use of SVGs which has several advantages: 
-the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays. 
-Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
-
-In our task, participants are asked to locate a balloon by using the gaze cues of another agent. 
-Therefore, participants need to follow the agent's gaze and act according to this social cue. 
-The outcome measure depends on the presented study version: 
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure. 
-Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
-The cartoon-like presentation makes the task engaging for children and adults alike.
-
-First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person. 
-Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
-Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates. 
-Finally, we found that gaze understanding relates to aspects of children's everyday experience.
-The web app (https://ccp-odc.eva.mpg.de/gafo-demo/) and its source code (https://github.com/ccp-eva/gafo-demo) are openly accessible.
-We want to highlight that researchers are welcome to use and modify our task according to their needs.
-
-- From previous intro potentially: 
-  - @hedge2018reliability section on reliability paradox
-  - Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual].
-This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations]. 
-  - Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic].
-Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual].
+We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
+The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in-person.
+Ultimately, this work shows a promising way forward towards more precise measures of cognitive development.
+The dataset and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
+A demo version of the task is available at the following website: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
+The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: <https://github.com/ccp-eva/gafo-demo>.
+These resources allow interested researchers to use, extend and adapt the task.
 
@@
 ## Open practices statement
-The web application (https://ccp-odc.eva.mpg.de/gafo-demo/) described here is open source (https://github.com/ccp-eva/gafo-demo).
-The datasets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (https://github.com/jprein/gazecues-methods).
-All experiments were preregistered (https://osf.io/zjhsc/).
+The web application (<https://ccp-odc.eva.mpg.de/gafo-demo/>) described here is open source (<https://github.com/ccp-eva/gafo-demo>).
+The datasets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (<https://github.com/jprein/gazecues-methods>).
+All experiments were preregistered (<https://osf.io/zjhsc/>).
 
@@
 This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children and parents who participated in the study.
+We thank all the children, caregivers and adults who participated in the study. We thank Jana Jurkat for her help with data collection.
 
@@
 
-## Ethics approval
-
 ## Consent to participate
@@
 
-## Consent for publication
-
-## Open access
-
 ## Authors' contributions
-optional: please review the submission guidelines from the journal whether statements are mandatory
+The authors made the following contributions.
+Julia Prein: Conceptualization, Software, Formal Analysis, Writing - Original Draft Preparation, Writing - Review & Editing; Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing; Steven Kalinke: Software, Writing - Review & Editing; Daniel Haun: Conceptualization, Writing - Review & Editing.
 
@@
 # References
-
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
+```{=tex}
 \endgroup
-
+```
 \newpage
@@
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^fn3]
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^3]
 
-[^fn3]: Attentive readers might notice that we simplified the structure of random effects.
+[^3]: Attentive readers might notice that we simplified the structure of random effects.
     Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
@@
 *Prolific*'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
-The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US$6.50 or €6.00) per hour.
+The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
 We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
@@
 The aim of Study 1 was to validate the hedge version of our gaze understanding task.
-The pre-registration can be found here: https://osf.io/r3bhn.
+The pre-registration can be found here: <https://osf.io/r3bhn>.
 We recruited participants online by advertising the study on *Prolific*.
@@
 In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
-The pre-registration can be found here: https://osf.io/nu62m.
+The pre-registration can be found here: <https://osf.io/nu62m>.
 We tested the same participants twice with a delay of two weeks.
@@
 |                              |                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                       |                       |
-| --- | --- | --- | --- |
+|------------------|------------------|------------------|------------------|
 | **Timeline**                 | **German**                                                                                                                                                                                                                                       | **English**                                                                                                                                                                                                                                           | **Filename**          |
@@
 | Hello!
-Great that you’re here.
-We’ll now play a balloon game.
+Great that you're here.
+We'll now play a balloon game.
 Can you see the animals in the picture over there?
 We want to play together with the animals using the balloon.
-We’ll now talk you through exactly what will happen.
+We'll now talk you through exactly what will happen.
 | welcome.mp3           |
@@
 | touch-1.mp3           |
-|     | Wo ist der Ballon? Drück auf den Ballon! | Where is the balloon? Click on the balloon! | prompt-touch-long.mp3 |
+|                              | Wo ist der Ballon?
+Drück auf den Ballon!
+| Where is the balloon?
+Click on the balloon!
+| prompt-touch-long.mp3 |
 | **fam - HEDGE**              | Klasse, das war super!
@@
 | Perfect, that was great!
-Now, we’ll continue playing.
+Now, we'll continue playing.
 Can you see the animal and the balloon again?
@@
 | fam-hedge-1.mp3       |
-|     | Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. | Where is the balloon? On the hedge, click where the balloon is. | prompt-hedge-long.mp3 |
+|                              | Wo ist der Ballon?
+Drücke auf die Hecke - wo der Ballon ist.
+| Where is the balloon?
+On the hedge, click where the balloon is.
+| prompt-hedge-long.mp3 |
 | **fam - BOX**                | Klasse, das war super!
@@
 | fam-box-1.mp3         |
-|     | Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. | Where is the balloon? Click on the box with the balloon. | prompt-box-long.mp3 |
+|                              | Wo ist der Ballon?
+Drücke auf die Kiste mit dem Ballon.
+| Where is the balloon?
+Click on the box with the balloon.
+| prompt-box-long.mp3   |
 | **test - HEDGE**             | Klasse , das hast du toll gemacht!
@@
 | Nice, good job!
-Now, we’ll continue playing.
+Now, we'll continue playing.
 There is the balloon, the animal and the hedge.
@@
 | The balloon is behind the hedge now.
-You can’t see it - but the animal can!
+You can't see it - but the animal can!
 The balloon falls to the ground and you have to find it.
@@
 | test-hedge-2.mp3      |
-|     | Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. | Now, the hedge is shrinking. On the hedge, click where the balloon is. | test-hedge-3.mp3 |
+|                              | Dann schrumpft die Hecke.
+Drücke auf die Hecke - wo der Ballon ist.
+| Now, the hedge is shrinking.
+On the hedge, click where the balloon is.
+| test-hedge-3.mp3      |
 | **test - BOX**               | Klasse , das hast du toll gemacht!
@@
 | Nice, good job!
-Now, we’ll continue playing.
+Now, we'll continue playing.
 There is the balloon and the animal.
@@
 | The balloon is behind the hedge now.
-You can’t see it - but the animal can!
+You can't see it - but the animal can!
 The balloon falls into a box and you have to find it.
@@
 | test-box-2.mp3        |
-|     | Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. | Now, the hedge is shrinking. Click on the box with the balloon. | test-box-3.mp3 |
+|                              | Dann schrumpft die Hecke.
+Drücke auf die Kiste mit dem Ballon.
+| Now, the hedge is shrinking.
+Click on the box with the balloon.
+| test-box-3.mp3        |
 | **goodbye**                  | Geschafft!
@@
 See you soon and goodbye from the pig, monkey and sheep                                                                                                                        | goodbye.mp3           |
-| **general prompt** | Wo ist der Ballon? | Where is the balloon? | prompt-general.mp3 |
-| **touch - no response** | Drück auf den Ballon! | Click on the balloon! | prompt-touch.mp3 |
-| **hedge - no response** | Drücke auf die Hecke - wo der Ballon ist! | On the hedge, click where the balloon is! | prompt-hedge.mp3 |
-| **box - no response** | Drücke auf die Kiste mit dem Ballon! | Click on the box with the balloon! | prompt-box.mp3 |
+| **general prompt**           | Wo ist der Ballon?
+| Where is the balloon?
+| prompt-general.mp3    |
+| **touch - no response**      | Drück auf den Ballon!
+| Click on the balloon!
+| prompt-touch.mp3      |
+| **hedge - no response**      | Drücke auf die Hecke - wo der Ballon ist!
+| On the hedge, click where the balloon is!
+| prompt-hedge.mp3      |
+| **box - no response**        | Drücke auf die Kiste mit dem Ballon!
+| Click on the box with the balloon!
+| prompt-box.mp3        |
 | **landing sound of balloon** | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | balloon-lands.mp3     |

### 2022-08-17 paper/manuscript.tex
first complete draft of discussion

@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, psychometrics\newline\indent Word count: X}
+\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: X}
 \usepackage{lineno}
@@
   pdflang={en-EN},
-  pdfkeywords={social cognition, individual differences, gaze cues, psychometrics},
+  pdfkeywords={social cognition, individual differences, gaze cues, cognitive development},
   hidelinks,
@@
 Yet, there are always individual differences.
-Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions
-(Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions (Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
 
@@
 However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016).
-This might be because traditional measures of social cognition are not designed to capture variation between children:
-they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent review showed that many atudies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
+This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
 
@@
 Participants then get asked where Sally will look for her marble once she returns.
-The outcome measures false belief understanding in a dichotomous way:
-children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
+The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
 Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
-Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
+Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf.
+Mayer \& Träuble, 2015).
 
@@
 New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
-Another goal in creating new tasks should be to focus on ``face value'':
-measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
+Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
+Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
 The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).
@@
 Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
-We focused on one of the fundamental abilities implicated in many social-cognitive reasoning processes:
-gaze understanding -- the ability to locate and use the attentional focus of an agent.
-The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent --
-and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
+We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
+The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
@@
 
-To address the psychometric shortcoming of earlier work, we implemented the following design features:
-First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages.
+To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages.
 Second, we designed short trials that facilitate more than a dozen replicates per subject.
@@
 To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
-Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.~The landing of the target is accompanied by a tapping sound.
+Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.
+The landing of the target is accompanied by a tapping sound.
 Once the target landed, the instructor's voice asks ``Where is the balloon?''.
 For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback so that learning effects are reduced and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
+(C) Box version (discrete) of the gaze understanding task.
+Number of boxes (min.
+1; max.
+8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
 \end{figure}
@@
 Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
-Furthermore, we were interested in how the data collection mode influences responses.
+Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.
 
@@
 We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
-In-person testing with children took place in kindergartens in Leipzig, Germany. The in-person child sample consisted of
-120 children, including
-40 3-year-olds
-(mean = 41.45 months,
-SD = 3.85,
-range = 36
-- 47,
-22 girls),
-40 4-year-olds
-(mean = 54.60 months,
-SD = 3.10,
-range = 48
-- 59,
-19 girls),
-and 40 5-year-olds
-(mean = 66.95 months,
-SD = 3.39,
-range = 60
-- 71,
-22 girls).
-
-For our remote child sample, we recruited families via an internal database. The remote child sample included 147 children, including
-45 3-year-olds
-(mean = 42.62 months,
-SD = 3.35,
-range = 36
-- 47,
-14 girls),
-47 4-year-olds
-(mean = 52.64 months,
-SD = 3.40,
-range = 48
-- 59,
-25 girls),
-and 55 5-year-olds
-(mean = 65.11 months,
-SD = 3.77,
-range = 60
-- 71,
-27 girls).
+In-person testing with children took place in kindergartens in Leipzig, Germany.
+The in-person child sample consisted of 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.60 months, SD = 3.10, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).
+
+For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in studies on child development and who indicated interest in online studies.
+Families received an email with a short study description and a personalized link, and received a reminder two weeks later if they had not already participated in the study.
+
+The remote child sample included 147 children, including 45 3-year-olds (mean = 42.62 months, SD = 3.35, range = 36 - 47, 14 girls), 47 4-year-olds (mean = 52.64 months, SD = 3.40, range = 48 - 59, 25 girls), and 55 5-year-olds (mean = 65.11 months, SD = 3.77, range = 60 - 71, 27 girls).
 Children in our sample grow up in an industrialized, urban Central-European context.
@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
-Participants consisted of 100 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
+Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
 For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
@@
 (J) Test-retest reliability in box adult sample.
-Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
+For (A) and (F), regression lines show the predicted developmental trajectories (with 95\% CrI) based on GLMMs, with the line type indicating the data collection mode.
+For (B-E) and (G-J), regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
 Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
@@
 
-Our task induced inter-individual variation in both adults and children.
+Our task induced inter-individual variation in both children and adults.
 We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
@@
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
-This illustrates the flexibility of the task.
+This illustrates the flexibility of the task design.
 
@@
 As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
-We assessed internal consistency (split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for child sample, and \url{https://osf.io/nu62m} adult sample).
+We assessed internal consistency (as splithalf reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for the child sample, and \url{https://osf.io/nu62m} for the adult sample).
 Participants were equally distributed across the two study versions.
 The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between July 2021 and April 2022.
+Data was collected between July 2021 and June 2022.
 
@@
 
-Participants were recruited in the same way as in the previous study. The child sample consisted of
-120 children, including
-41 3-year-olds
-(mean = 42.34 months,
-SD = 3.10,
-range = 37
-- 47,
-20 girls),
-41 4-year-olds
-(mean = 53.76 months,
-SD = 3.15,
-range = 48
-- 59,
-21 girls),
-and 38 5-year-olds
-(mean = 66.05 months,
-SD = 3.40,
-range = 60
-- 71,
-19 girls).
-
-The adult sample consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).
+Participants were recruited in the same way as in the previous study.
+The child sample consisted of 120 children, including 41 3-year-olds (mean = 42.34 months, SD = 3.10, range = 37 - 47, 20 girls), 41 4-year-olds (mean = 53.76 months, SD = 3.15, range = 48 - 59, 21 girls), and 38 5-year-olds (mean = 66.05 months, SD = 3.40, range = 60 - 71, 19 girls).
+
+The adult sample consisted of 136 English-speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females).
 
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing splithalf reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
@@
 Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
-We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
-The model computes a correlation between the participant specific estimates for each test day.
+The model computes a correlation between the participant-specific estimates for each test day.
 This can be interpreted as the test-retest reliability.
@@
 Figure \ref{fig:fig3} compares splithalf reliability coefficients by splitting and stratification method (Pronk et al., 2021).
-In the hedge version, the splithalf reliability coefficients ranged from 0.65 to 0.93. In the box version, splithalf reliability coefficients ranged from 0.48 to 0.86.
-Similarly to the results of Pronk et al.
-(2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+In the hedge version, the splithalf reliability coefficients ranged from 0.65 to 0.93.
+In the box version, splithalf reliability coefficients ranged from 0.48 to 0.86.
+Similarly to the results of Pronk et al. (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
 In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
@@
 
-The age-corrected, GLMM based retest reliabilities for children yielded similar results. In hedge version it was 0.90 (95\% CI {[}0.67;1.00{]}).
-In the box version it was 0.91 (95\% CI {[}0.69;1.00{]}).
+The age-corrected, GLMM based retest reliabilities for children yielded similar results.
+In the hedge version, the correlation between testdays was 0.90 (95\% CI {[}0.67;1.00{]}).
+In the box version, the correlation between testdays was 0.91 (95\% CI {[}0.69;1.00{]}).
 
@@
 
-In this paper, we presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
+We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
 This paper contributes to methodological advances in developmental psychology in the following ways.
-First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
-Second, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Finally, we found that gaze understanding relates to aspects of children's everyday experience.
-The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are openly accessible.
+First, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+Individuals behaved consistently different from one another.
+Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
+Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
+In sum, our gaze understanding task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
 
-One of the main contributions of this paper is that our newly presented gaze understanding task induces variation between participants.
+One of the main contributions of the gaze understanding task is that it induces variation between participants.
 This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
-Our experimental design enables a continuous outcome measure, which again quantifies individual differences.
 
 In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version:
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
+The outcome measure depends on the presented study version: in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
+
+Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) towards an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
+Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
+Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building (Hedge et al., 2018).
+
 Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
-Both study versions exhibit high retest reliability.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates {[}cf.
-Hughes et al.
-(2000); improved reliability through aggregation{]}.
+Both study versions exhibit high retest reliability, also when controlling for age.
+Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al. (2000); improved reliability through aggregation).
 When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
-However, the categorical box version demonstrates design features that might be preferable in some research contexts: the discrete outcome might facilitate clicking for children.
-In addition, researchers could induce different levels of salience for each box.
-Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature of the agent).
-In sum, our task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
+Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature/behavioral characteristic of the agent).
+
+Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
+Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+Another task extension could realize differential feedback dependent on the participant's accuracy.
+By inducing more between-person variance, reliability estimates could further increase.
+
+As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
+A potentially promising approach are computational cognitive models.
+We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
+Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022)
 
@@
 This enables presentation across devices without any prior installation.
-Stimuli presentation is achieved through the use of SVGs. This has several advantages:
-the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
+Stimuli presentation is achieved through the use of SVGs.
+This has several advantages: the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
+The cartoon-like presentation makes the task engaging for children and adults alike.
 Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
 Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
-The cartoon-like presentation makes the task engaging for children and adults alike.
-
-Participants can be tested in-person with supervision or remotely at home.
+
+The web-based implementation allows for different data collection modes: participants can be tested in-person with supervision or remotely at home.
 Test instructions are standardized and, with prior informed consent, the webcam records study participation.
@@
 Children in the remote sample are slightly more precise.
-This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Appendix XXX).
+This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
 Therefore, we recommend using a tablet for remote data collection.
-Children can then click for themselves and caregivers have less chance to interfere.
-
-\hypertarget{todo-adjust-discussion-part-validity}{%
-\section{TODO adjust discussion part validity}\label{todo-adjust-discussion-part-validity}}
-
+Children can click for themselves and caregivers have less chance to interfere.
+
+The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.
+
+After having proven satisfactory psychometric properties, the next step will be to ensure the validity of our task.
 Validity is often assessed by looking at concurrent relations between measures.
-Here we looked at a relation that is often postulated for social cognition tasks, namely that social-cognitive ability is predicted by family level variables.
-We found that children's gaze understanding relates to factors of their social environment:
-children were more accurate, the more social exposure and the more diverse their surrounding was.
-However, compared to our fine-grained, parametric measure of gaze understanding, family variables were only captured on the surface level by employing single questionnaire items.
-We hope that future technological advances will enable continuous measures of children's real life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).
-
-\hypertarget{future-research}{%
-\subsection{Future research}\label{future-research}}
-
-Even though aggregate scores seem to improve reliability estimates (cf. Hughes et al., 2000), they may smooth out noise that could be attributed to individual differences.
-As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
-A potentially promising approach are computational cognitive models.
-We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and interpretable manner.
-Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).
-
-Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
-Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
-By inducing more between-person variance, reliability estimates could further increase.
+Studies on gaze following traditionally present children with a simultaneous, congruent movement of eyes and head orientation.
+In our study, however, children only observe a subtle eye movement.
+Therefore, our results are not directly comparable to traditional gaze following studies.
+Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
+For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
+In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
+In addition, a subset of our remote child sample completed a receptive vocabulary task (Bohn, Prein, Delikaya, Haun, \& Gagarina, n.d.).
+We will report the association between these family-level factors and children's language on their gaze understanding abilities in a separate paper (in preparation).
+In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).
 
 Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-We aim at creating a task battery to study individual differences in various aspects of social cognition.
-As Schaafsma et al.
-(2015) pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries.
+As has been pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
 We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
-
-\hypertarget{limitations}{%
-\section{Limitations}\label{limitations}}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  big picture
-\item
-  ind diff important for \ldots, good measures needed
-\item
-  dedicated measures of ind diff instead of simply using well-established. reliability paradox paper zitieren
-\item
-  task \& infrastructure
-\item
-  foundations for more precise measures for cognitive development
-\end{itemize}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-We presented a new experimental paradigm to study individual differences in a fundamental social-cognitive ability -- gaze understanding.
-The task is presented as an interactive web app that does not require any prior installation and works across devices.
-Data collection is enabled at scale, with supervised and remote testing and standardized test instructions.
-Stimuli presentation is achieved through the use of SVGs which has several advantages:
-the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
-Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
-
-In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-Therefore, participants need to follow the agent's gaze and act according to this social cue.
-The outcome measure depends on the presented study version:
-in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
-Short trials facilitate a substantial number of trials -- here, we employed 15 test trials within 5-10 minutes testing time.
-The cartoon-like presentation makes the task engaging for children and adults alike.
-
-First, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
-Second, we could show that we captured fine grained individual differences in gaze understanding at different ages -- especially in the continuous hedge version.
-Third, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Finally, we found that gaze understanding relates to aspects of children's everyday experience.
-The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are openly accessible.
-We want to highlight that researchers are welcome to use and modify our task according to their needs.
-
-\begin{itemize}
-\tightlist
-\item
-  From previous intro potentially:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Hedge et al. (2018) section on reliability paradox
-  \item
-    Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
-    This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
-  \item
-    Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-    Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
-  \end{itemize}
-\end{itemize}
+We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
+The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in-person.
+Ultimately, this work shows a promising way forward towards more precise measures of cognitive development.
+The dataset and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
+A demo version of the task is available at the following website: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: \url{https://github.com/ccp-eva/gafo-demo}.
+These resources allow interested researchers to use, extend and adapt the task.
 
@@
 
-\hypertarget{ethics-approval}{%
-\subsection{Ethics approval}\label{ethics-approval}}
-
 \hypertarget{consent-to-participate}{%
@@
 
-\hypertarget{consent-for-publication}{%
-\subsection{Consent for publication}\label{consent-for-publication}}
-
-\hypertarget{open-access}{%
-\subsection{Open access}\label{open-access}}
-
 \hypertarget{authors-contributions}{%
@@
 
-optional: please review the submission guidelines from the journal whether statements are mandatory
+The authors made the following contributions.
+Julia Prein: Conceptualization, Software, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Steven Kalinke: Software, Writing - Review \& Editing; Daniel Haun: Conceptualization, Writing - Review \& Editing.
 
@@
 \url{https://doi.org/10.1037/a0031056}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohnorev}{}}%
+Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (n.d.). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
 
@@
 \url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-molleman2019unleashing}{}}%
+Molleman, L., Kurvers, R.
+H.
+J.
+M., \& van den Bos, W.
+(2019).
+Unleashing the {BEAST}: A brief measure of human social information use.
+\emph{Evolution and Human Behavior}, \emph{40}(5), 492--499.
+\url{https://doi.org/10.1016/j.evolhumbehav.2019.06.005}
 

### 2022-08-18 paper/manuscript.Rmd
create separate document for supplements

@@
 # Introduction
+
 Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
@@
 Yet, there are always individual differences.
-Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions [@happe2017structure; @mundy2007individual; @kidd2018individual; @underwood1975individual; @lecce2014promoting].
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and designing interventions [@happe2017structure; @mundy2007individual; @kidd2018individual; @underwood1975individual; @lecce2014promoting].
 
@@
 
-However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding].
+However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding].
 This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
@@
 
-To give an example: perhaps the most commonly applied prototypical measure for social cognition is the change-of-location false belief task [@baron-cohen1985does; @wimmer1983beliefs].
+To give an example: the most commonly applied prototypical measure for social cognition is the change-of-location false belief task [@baron-cohen1985does; @wimmer1983beliefs].
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
@@
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
-Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences [cf.
+Thus, this task seems well suited to track group-level developmental trends, yet it fails to capture individual differences [cf.
 "reliability paradox", @hedge2018reliability].
@@
 Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
-Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical and demographic contexts [@molleman2019unleashing].
+Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts [@molleman2019unleashing].
 The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].
@@
 # A new measure of gaze understanding
+
 Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
@@
 
-To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine grained individual differences at different ages.
+To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine-grained individual differences at different ages.
 Second, we designed short trials that facilitate more than a dozen replicates per subject.
-The result are more precise individual-level estimates.
+The result is more precise individual-level estimates.
 Third, we systematically investigated the psychometric properties of the new task.
@@
 Furthermore, because the task is largely self-contained, it is much more controlled and standardized.
-Most importantly perhaps, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
+Most importantly, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
 As such, it provides a solid basis to study individual differences in gaze understanding across ages at scale.
@@
 # Task design
+
 ## Implementation
-The code is open-source (<https://github.com/ccp-eva/gafo-demo>) and a live demo version can be found under: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
+
+The code is open-source (<https://github.com/ccp-eva/gafo-demo>), and a live demo version can be found under: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
 
@@
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant.
+This way, the composition scales according to the user's viewport without loss of quality while keeping the aspect ratio and relative object positions constant.
 Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
 These files can either be sent to a server or downloaded to the local device.
@@
 ## Stimuli
+
 Our newly implemented task features an online game where children or adults are asked to search for a balloon.
@@
 The target then falls to the ground.
-At all times, the agent's gaze tracks the movement of the target.
-That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target.
+At all times, the agent's gaze tracks the movement of the target: the pupils and iris move so that their center aligns with the center of the target.
 While the distance of the target's flight depends on the final location, the target moves at a constant speed.
@@
 Once the target landed, the instructor's voice asks "Where is the balloon?".
-For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback so that learning effects are reduced and trials stay comparable across the sample.
+For confirming the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 ## Trials
+
 Trials differ in the amount of visual access that participants have to the final target position.
@@
 ## Study versions
-We designed two study versions which differ in the final hiding place of the target and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
+
+We designed two study versions that differ in the target's final hiding place and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
@@
 Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the box version, the target lands in a box and participants are asked to click on the box that hides the target.
-Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
+In the box version, the target lands in a box, and participants are asked to click on the box that hides the target.
+Researchers can choose how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
 Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
@@
 (i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens or research labs.
+Data collection can take place anywhere: online, in kindergartens, or research labs.
 (ii) The task is presented as a website that works across devices.
@@
 ## Randomization
+
 All agents and target colors appear equally often and are not repeated in more than two consecutive trials.
@@
 # Individual differences
+
 Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
@@
 
-Methods, sample size and analysis were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
+Methods, sample size, and analysis were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
 Participants were equally distributed across the two study versions.
@@
 ## Participants
+
 We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
@@
 
-For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in studies on child development and who indicated interest in online studies.
-Families received an email with a short study description and a personalized link, and received a reminder two weeks later if they had not already participated in the study.
+For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
+Families received an email with a short study description and a personalized link and received a reminder two weeks later if they had not already participated in the study.
 
@@
 Adults were recruited via *Prolific* [@palan2018prolific].
-*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
+*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
 Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
-For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
 
 ## Procedure
+
 Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten.
 An experimenter guided the child through the study.
-Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
+At the beginning of the online study, families were invited to enter our "virtual institute".
+We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
 Then, caregivers were informed about data security and were asked for their informed consent.
@@
 We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Study participation was video recorded whenever possible in order to ensure that children themselves generated the answers.
 Depending on the participant's device, the website automatically presented the hedge or box version of the study.
 For families that used a tablet with touchscreen, the hedge version was shown.
-Here, children could directly click on the touchscreen themselves to indicate where the target is.
+Here, children could directly click on the touchscreen to indicate where the target is.
 For families that used a computer without touchscreen, the website presented the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+We assumed that younger children in our sample would not be acquainted with using a computer mouse.
 Therefore, we asked children to point to the screen, while caregivers were asked to act as the "digital finger" of their children and click on the indicated box.
@@
 ## Analysis
-All test trials without voice over description were included in our analyses.
+
+All test trials without voice-over description were included in our analyses.
 We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
@@
 Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
+We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
 
@@
 ## Results
+
 (ref:figlab2) **Measuring inter-individual variation**.
@@
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
 (B) Internal consistency (odd-even split) in hedge child sample.
@@
 (F) Developmental trajectory in discrete box version.
-Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
+Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
 Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
@@
 
-We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
+We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
+In the hedge version, children's click imprecision decreased with age, while in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
 Most participants in the box version performed above chance level.
@@
 We found evidence that responses of children participating remotely were slightly more precise.
-This difference was mainly driven by the younger participants and especially prominent in the box version of the task.
+This difference was mainly driven by the younger participants and was especially prominent in the box version of the task.
 It is conceivable that caregivers were especially prone to influence the behavior of younger children.
@@
 In the box version, the estimate of age ($\beta$ =`r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode ($\beta$ = `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]) were positive and reliably different from zero.
-Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
+Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.
 
 ## Discussion
+
 Our task induced inter-individual variation in both children and adults.
-We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
+We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
 The five-year-olds reached a proficiency level close to the adults' level.
 For neither study version nor age group did we find any floor or ceiling effects.
-The presentation as a tablet game kept children interest and motivated throughout the 15 test trials.
+The presentation as a tablet game kept children interested and motivated throughout the 15 test trials.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 # Internal consistency and retest reliability
-As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
-We assessed internal consistency (as splithalf reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: <https://osf.io/xqm73> for the child sample, and <https://osf.io/nu62m> for the adult sample).
+
+As a next step, we aimed to investigate whether the variation that we captured with our gaze understanding task is reliable.
+We assessed internal consistency (as split-half reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: <https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
 Participants were equally distributed across the two study versions.
@@
 ## Participants
+
 Participants were recruited in the same way as in the previous study.
@@
 ## Procedure
+
 We applied the same procedure as in the first study, with the following differences.
 Participants completed the study twice, with a delay of 14 ± 3 days.
-The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
+The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
 The child sample received 15 test trials.
 In the hedge version, each bin occurred once, making up ten of the test trials.
-For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc).
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc.).
 In the box version, we ensured that each of the five boxes occurred exactly three times.
@@
 Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
-Adults in the box version received 32 test trials with each of the eight boxes occurring exactly four times.
+Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
 
 ## Analysis
+
 We assessed reliability in two ways.
-First, we focused on the internal consistency by calculating splithalf reliability coefficients.
+First, we focused on internal consistency by calculating split-half reliability coefficients.
 For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using *Pearson* coefficients.
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-@pronk2021methods recently compared various methods for computing splithalf reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+@pronk2021methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
-First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
 Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2021methods].
@@
 We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
-Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics].
-We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
+Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics].
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
@@
 The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
-A high correlation between our participant specific model estimates would speak for a high association between test days.
+This rules out the possibility that a high correlation between test days arises from domain-general cognitive development instead of study-specific inter-individual differences.
+A high correlation between our participant-specific model estimates would indicate a high association between test days.
 
 ## Results
+
 ```{r splithalf}
@@
 
-We found that our gaze understanding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
-For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G and H.
-Figure \@ref(fig:fig3) compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
-In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
-In the box version, splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
-Similarly to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
-In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
-As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
+We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was high for most samples.
+For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.
+Figure \@ref(fig:fig3) compares split-half reliability coefficients by splitting and stratification method [@pronk2021methods].
+In the hedge version, the split-half reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
+In the box version, split-half reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
+Similar to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+In most cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
+As expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
 
 (ref:figlab3) **Internal Consistency**.
-Reliability coefficients per splitting method, stratification level, study version and age group.
+Reliability coefficients per splitting method, stratification level, study version, and age group.
 Error bars show the 95% confidence intervals of the coefficient estimates, calculated with the function `by_split` from the `splithalfr` package [@pronk2021methods].
@@
 
-The age-corrected, GLMM based retest reliabilities for children yielded similar results.
+The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
 In the hedge version, the correlation between testdays was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
@@
 ## Discussion
+
 Our results indicated that the measured variation was systematic.
-As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
+As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
 For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
@@
 # General Discussion
+
 We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
 This paper contributes to methodological advances in developmental psychology in the following ways.
-First, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+First, we could capture fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
 Individuals behaved consistently different from one another.
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
-In sum, our gaze understanding task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.The web app (<https://ccp-odc.eva.mpg.de/gafo-demo/>) and its source code (<https://github.com/ccp-eva/gafo-demo>) are freely accessible.
+Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
+In sum, our gaze understanding task provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
+The web app (<https://ccp-odc.eva.mpg.de/gafo-demo/>) and its source code (<https://github.com/ccp-eva/gafo-demo>) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
@@
 
-Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) towards an ability on a continuum [@hughes2015individual; @beaudoin2020systematic].
+Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum [@hughes2015individual; @beaudoin2020systematic].
 Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
@@
 
-Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
+Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
 Both study versions exhibit high retest reliability, also when controlling for age.
 Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
-When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
+When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
-Our task could consequently be used to study bias, preferences and diverse desires (e.g. matching the box appearance to some feature/behavioral characteristic of the agent).
+Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).
 
 Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
-Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+Researchers could consider adjusting the task difficulty, for example, by changing the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
 Another task extension could realize differential feedback dependent on the participant's accuracy.
@@
 
-As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
+As we could see in the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
 Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
-A potentially promising approach are computational cognitive models.
+Computational cognitive models are a promising approach forward.
 We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
 Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual]
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual].
 
@@
 
-The web-based implementation allows for different data collection modes: participants can be tested in-person with supervision or remotely at home.
-Test instructions are standardized and, with prior informed consent, the webcam records study participation.
-This allows us to scale up data collection: testing is flexible, fast and requires no further experimenter training.
-We compared children participating in-person, supervised in kindergartens with children participated remotely at home.
+The web-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
+Test instructions are standardized and with prior informed consent the webcam records study participation.
+This allows us to scale up data collection: testing is flexible, fast, and requires no further experimenter training.
+We compared children participating in-person, supervised in kindergartens with children who participated remotely at home.
 Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
@@
 Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-As has been pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries [@hughes2011individual; @schaafsma2015deconstructing].
+As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries [@hughes2011individual; @schaafsma2015deconstructing].
 We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
@@
 # Conclusion
+
 We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
 The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
-The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in-person.
-Ultimately, this work shows a promising way forward towards more precise measures of cognitive development.
-The dataset and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
+The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
+Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
+The data set and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
 A demo version of the task is available at the following website: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
@@
 
+\newpage
+
 # Declarations
+
 ## Open practices statement
+
 The web application (<https://ccp-odc.eva.mpg.de/gafo-demo/>) described here is open source (<https://github.com/ccp-eva/gafo-demo>).
-The datasets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (<https://github.com/jprein/gazecues-methods>).
+The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (<https://github.com/jprein/gazecues-methods>).
 All experiments were preregistered (<https://osf.io/zjhsc/>).
@@
 ## Funding
+
 This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers and adults who participated in the study. We thank Jana Jurkat for her help with data collection.
+We thank all the children, caregivers and adults who participated in the study.
+We thank Jana Jurkat for her help with data collection.
 
 ## Conflicts of interest
+
 The authors declare that they have no conflict of interest.
@@
 ## Consent to participate
+
 Informed consent was obtained from all individual participants included in the study or their legal guardians.
@@
 ## Authors' contributions
+
 The authors made the following contributions.
@@
 # References
+
 ```{=tex}
@@
 ```
-\newpage
-
-# Supplements
-## Child sample
-### Webcam coding
-(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**.
-Factors of parental interference and their influence on the probability of responding correctly.
-The graph shows the estimated density curves of a model's predictor coefficient.
-Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison.
-(A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level (i.e., average across trials per subject).
-
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
-```
-
-Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
-This difference was especially prominent in younger participants in the box version of the task.
-It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
-In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
-We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-A trial was defined as the time between two eye blinking sounds.
-We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
-In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
-We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^3]
-
-[^3]: Attentive readers might notice that we simplified the structure of random effects.
-    Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
-    We decided to do so since we had limited amount of data from few participants.
-
-We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
-Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
-Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
-We compared models using WAIC (widely applicable information criterion) scores and weights.
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
-In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
-
-```{r webcam_table, results = "asis"}
-webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
-  mutate_if(is.numeric, round, 2)
-
-papaja::apa_table(
-  webcam_models,
-  caption = "Model comparison for exploratory webcam coding of parental interference",
-  note = "All models included random intercepts for participant and target position.",
-  escape = T
-)
-```
-
-## Adult sample
-### Recruitment
-We recruited participants using the online participant recruitment service *Prolific* from the University of Oxford.
-*Prolific*'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
-The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
-We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
-*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
-Therefore, study data was saved only on our internal servers, while *Prolific* provided demographic information of the participants.
-Participants' *Prolific* ID was forwarded to our study website using URL parameters.
-This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion: we redirected participants from our study website back to the *Prolific* website using URL parameters.
-We used *Prolific*'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
-
-### Study 1 - Validation hedge version
-The aim of Study 1 was to validate the hedge version of our gaze understanding task.
-The pre-registration can be found here: <https://osf.io/r3bhn>.
-We recruited participants online by advertising the study on *Prolific*.
-
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in May 2021.
-Participants were compensated with £1.25 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-In average, participants took 05:56min to complete the study.
-Participants were required to complete the study on a tablet or desktop.
-Participation on mobile devices was disabled since the display would be too small and would harm click precision.
-It was indicated that the study required audio sound.
-
-We stored *Prolific*'s internal demographic information, while not asking for additional personal information.
-
-### Study 2 - Validation box version
-As in study 1, we recruited participants on *Prolific*, and employed the same methodology.
-However, this time we focussed on validating the box version of the task in an adult sample.
-Participants were presented with eight boxes in which the target could land.
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in June 2021.
-Participants were compensated with £1.00 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-In average, participants took 04:43min to complete the study.
-
-### Study 3 - Reliability hedge version
-In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
-The pre-registration can be found here: <https://osf.io/nu62m>.
-We tested the same participants twice with a delay of two weeks.
-The testing conditions were as specified in Study 1 and 2.
-However, the target locations as well as the succession of animals and target colors was randomized once.
-Each participant then received the same fixed randomized order of target location, animal, and target color.
-Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.
-
-In addition to the beforementioned prescreening settings, we used a whitelist.
-*Prolific* has a so-called *custom allowlist prescreening filter* where one can enter the *Prolific* IDs of participants who completed a previous study.
-Only these subjects are then invited to participate in a study.
-This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.
-
-In a first round, 60 participants took part on the first testday.
-Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-The maximum time is calculated by *Prolific*, based on the estimated average completion time.
-For this study, the maximum time amounted to 41 minutes.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-In average, participants took 07:11min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-In average, participants took 06:36min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-In average, participants took 06:51min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-In average, participants took 06:26min to complete the second part of the study.
-
-### Study 4 - Reliability box version
-As in study 3, we recruited participants on *Prolific*, and employed the same methodology.
-However, this time participants were presented with the box version of the task.
-Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
-As in study 2, we employed eight boxes in which the target could land.
-
-In a first round, 60 participants took part on the first testday.
-Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-In average, participants took 07:33min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-In average, participants took 07:50min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-In average, participants took 07:37min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
-Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-In average, participants took 06:30min to complete the second part of the study.
-
-# Instructions and voice over descriptions
-This is the content of our audio recordings that were played as instructions and during voice over trials.
-
-|                              |                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                       |                       |
-|------------------|------------------|------------------|------------------|
-| **Timeline**                 | **German**                                                                                                                                                                                                                                       | **English**                                                                                                                                                                                                                                           | **Filename**          |
-| **welcome**                  | Hallo!
-Schön, dass du da bist.
-Wir spielen jetzt das Ballon-Spiel!
-Siehst du die Tiere auf dem Bild da?
-Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen.
-Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
-| Hello!
-Great that you're here.
-We'll now play a balloon game.
-Can you see the animals in the picture over there?
-We want to play together with the animals using the balloon.
-We'll now talk you through exactly what will happen.
-| welcome.mp3           |
-| **touch**                    | Schau mal, da steht ein Tier im Fenster.
-Und siehst du den Ballon da?
-Der Ballon fällt immer runter und landet auf dem Boden.
-Und du musst ihn dann finden.
-Das Tier hilft Dir und schaut immer den Ballon an.
-| Look, an animal is standing in the window.
-And can you see the balloon over there?
-The balloon always falls down and lands on the ground.
-And you have to find it!
-The animal helps you and always looks at the balloon.
-| touch-1.mp3           |
-|                              | Wo ist der Ballon?
-Drück auf den Ballon!
-| Where is the balloon?
-Click on the balloon!
-| prompt-touch-long.mp3 |
-| **fam - HEDGE**              | Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er hinter eine Hecke.
-Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-| Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon will fall down again.
-This time, it will fall behind a hedge.
-And you have to find it!
-The animal helps you and looks at the balloon.
-| fam-hedge-1.mp3       |
-|                              | Wo ist der Ballon?
-Drücke auf die Hecke - wo der Ballon ist.
-| Where is the balloon?
-On the hedge, click where the balloon is.
-| prompt-hedge-long.mp3 |
-| **fam - BOX**                | Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er in eine Kiste.
-<br>Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-| Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon falls down again.
-This time, it falls into a box.
-And you have to find it!
-The animal helps you and looks at the balloon.
-| fam-box-1.mp3         |
-|                              | Wo ist der Ballon?
-Drücke auf die Kiste mit dem Ballon.
-| Where is the balloon?
-Click on the box with the balloon.
-| prompt-box-long.mp3   |
-| **test - HEDGE**             | Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Hecke.
-Die Hecke wächst jetzt hoch.
-| Nice, good job!
-Now, we'll continue playing.
-There is the balloon, the animal and the hedge.
-The hedge is growing a bit now.
-| test-hedge-1.mp3      |
-|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-| The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls to the ground and you have to find it.
-Remember - the animal always looks at the balloon!
-| test-hedge-2.mp3      |
-|                              | Dann schrumpft die Hecke.
-Drücke auf die Hecke - wo der Ballon ist.
-| Now, the hedge is shrinking.
-On the hedge, click where the balloon is.
-| test-hedge-3.mp3      |
-| **test - BOX**               | Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Kisten.
-Jetzt wächst eine Hecke hoch.
-| Nice, good job!
-Now, we'll continue playing.
-There is the balloon and the animal.
-Now, a hedge is growing.
-| test-box-1.mp3        |
-|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-| The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls into a box and you have to find it.
-Remember - the animal always looks at the balloon!
-| test-box-2.mp3        |
-|                              | Dann schrumpft die Hecke.
-Drücke auf die Kiste mit dem Ballon.
-| Now, the hedge is shrinking.
-Click on the box with the balloon.
-| test-box-3.mp3        |
-| **goodbye**                  | Geschafft!
-Die Tiere sind schon ganz glücklich vom Spielen!
-Vielen Dank für deine Hilfe!
-Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf                                                                                       | The animals are super happy after playing.
-Thanks a lot for your help!
-See you soon and goodbye from the pig, monkey and sheep                                                                                                                        | goodbye.mp3           |
-| **general prompt**           | Wo ist der Ballon?
-| Where is the balloon?
-| prompt-general.mp3    |
-| **touch - no response**      | Drück auf den Ballon!
-| Click on the balloon!
-| prompt-touch.mp3      |
-| **hedge - no response**      | Drücke auf die Hecke - wo der Ballon ist!
-| On the hedge, click where the balloon is!
-| prompt-hedge.mp3      |
-| **box - no response**        | Drücke auf die Kiste mit dem Ballon!
-| Click on the box with the balloon!
-| prompt-box.mp3        |
-| **landing sound of balloon** | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | balloon-lands.mp3     |
-| **sound of blinking eyes**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | blink.mp3             |
-| **sound for target click**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | positive-feedback.mp3 |

### 2022-08-18 paper/manuscript.tex
create separate document for supplements

@@
 \usepackage{xcolor}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 Yet, there are always individual differences.
-Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and for designing interventions (Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
+Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and designing interventions (Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
 
@@
 
-However, frequently, developmental psychologists are surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016).
+However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Sodian et al., 2016).
 This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
@@
 
-To give an example: perhaps the most commonly applied prototypical measure for social cognition is the change-of-location false belief task (Baron-Cohen, Leslie, \& Frith, 1985; Wimmer \& Perner, 1983).
+To give an example: the most commonly applied prototypical measure for social cognition is the change-of-location false belief task (Baron-Cohen, Leslie, \& Frith, 1985; Wimmer \& Perner, 1983).
 Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
@@
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (Repacholi, 2003).
-Thus, this sort of task seems to be well suited to track group-level developmental trends, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
+Thus, this task seems well suited to track group-level developmental trends, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
@@
 Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
-Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
+Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
 The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).
@@
 
-The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}), and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
 
@@
 Once the target landed, the instructor's voice asks ``Where is the balloon?''.
-For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback so that learning effects are reduced and trials stay comparable across the sample.
+For confirming the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 
-We designed two study versions which differ in the final hiding place of the target and, consequently, on the outcome measure: a \emph{hedge version} (continuous) and a \emph{box version} (discrete).
+We designed two study versions that differ in the target's final hiding place and, consequently, on the outcome measure: a \emph{hedge version} (continuous) and a \emph{box version} (discrete).
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
@@
 
-Methods, sample size and analysis were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
+Methods, sample size, and analysis were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
 Participants were equally distributed across the two study versions.
@@
 Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
-\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool.
+\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
 Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
-For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
 
@@
 An experimenter guided the child through the study.
-Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted.
-In the beginning of the online study, families were invited to enter our ``virtual institute'' and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure.
+Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
+At the beginning of the online study, families were invited to enter our ``virtual institute''.
+We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
 Then, caregivers were informed about data security and were asked for their informed consent.
@@
 We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
+Study participation was video recorded whenever possible in order to ensure that children themselves generated the answers.
 Depending on the participant's device, the website automatically presented the hedge or box version of the study.
 For families that used a tablet with touchscreen, the hedge version was shown.
-Here, children could directly click on the touchscreen themselves to indicate where the target is.
+Here, children could directly click on the touchscreen to indicate where the target is.
 For families that used a computer without touchscreen, the website presented the box version of the task.
-We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse.
+We assumed that younger children in our sample would not be acquainted with using a computer mouse.
 Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.
@@
 
-All test trials without voice over description were included in our analyses.
+All test trials without voice-over description were included in our analyses.
 We ran all analyses in R version 4.2.0 (2022-04-22) (R Core Team, 2022).
@@
 Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.
+We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
 
@@
 (F) Developmental trajectory in discrete box version.
-Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target.
+Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
 Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
@@
 
-We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
+We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
+In the hedge version, children's click imprecision decreased with age, while in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
 Most participants in the box version performed above chance level.
@@
 In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.87{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CI {[}0.68; 1.56{]}) were positive and reliably different from zero.
-Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.
+Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.
 
@@
 Our task induced inter-individual variation in both children and adults.
-We see substantial developmental gains: with increasing age, participants got more and more precise in locating the target.
+We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
 The five-year-olds reached a proficiency level close to the adults' level.
 For neither study version nor age group did we find any floor or ceiling effects.
-The presentation as a tablet game kept children interest and motivated throughout the 15 test trials.
+The presentation as a tablet game kept children interested and motivated throughout the 15 test trials.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 
-As a next step, we aimed at investigating whether the variation that we captured with our gaze understanding task is reliable.
-We assessed internal consistency (as splithalf reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for the child sample, and \url{https://osf.io/nu62m} for the adult sample).
+As a next step, we aimed to investigate whether the variation that we captured with our gaze understanding task is reliable.
+We assessed internal consistency (as split-half reliability) and test-retest reliability.
+Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
 Participants were equally distributed across the two study versions.
@@
 Participants completed the study twice, with a delay of 14 ± 3 days.
-The target locations as well as the succession of agents and target colors was randomized once and then held constant across participants.
+The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
 The child sample received 15 test trials.
 In the hedge version, each bin occurred once, making up ten of the test trials.
-For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 \& 2, bin 3 \& 4, etc).
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 \& 2, bin 3 \& 4, etc.).
 In the box version, we ensured that each of the five boxes occurred exactly three times.
@@
 Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
-Adults in the box version received 32 test trials with each of the eight boxes occurring exactly four times.
+Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
 
@@
 We assessed reliability in two ways.
-First, we focused on the internal consistency by calculating splithalf reliability coefficients.
+First, we focused on internal consistency by calculating split-half reliability coefficients.
 For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using \emph{Pearson} coefficients.
@@
 Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing splithalf reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
-First-second and odd-even splits belong to single sample methods, since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
+First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
 Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).
@@
 We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
-Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
-We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
+Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
@@
 The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
-This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences.
-A high correlation between our participant specific model estimates would speak for a high association between test days.
+This rules out the possibility that a high correlation between test days arises from domain-general cognitive development instead of study-specific inter-individual differences.
+A high correlation between our participant-specific model estimates would indicate a high association between test days.
 
@@
 
-We found that our gaze understanding task induced systematic variation: splithalf and test-retest reliability was high for most samples.
-For the internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G and H.
-Figure \ref{fig:fig3} compares splithalf reliability coefficients by splitting and stratification method (Pronk et al., 2021).
-In the hedge version, the splithalf reliability coefficients ranged from 0.65 to 0.93.
-In the box version, splithalf reliability coefficients ranged from 0.48 to 0.86.
-Similarly to the results of Pronk et al. (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
-In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
-As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
+We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was high for most samples.
+For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.
+Figure \ref{fig:fig3} compares split-half reliability coefficients by splitting and stratification method (Pronk et al., 2021).
+In the hedge version, the split-half reliability coefficients ranged from 0.65 to 0.93.
+In the box version, split-half reliability coefficients ranged from 0.48 to 0.86.
+Similar to the results of Pronk et al. (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+In most cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
+As expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
 
@@
 \caption{\textbf{Internal Consistency}.
-Reliability coefficients per splitting method, stratification level, study version and age group.
+Reliability coefficients per splitting method, stratification level, study version, and age group.
 Error bars show the 95\% confidence intervals of the coefficient estimates, calculated with the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).}\label{fig:fig3}
@@
 
-The age-corrected, GLMM based retest reliabilities for children yielded similar results.
+The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
 In the hedge version, the correlation between testdays was 0.90 (95\% CI {[}0.67;1.00{]}).
@@
 Our results indicated that the measured variation was systematic.
-As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
+As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
 For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
@@
 This paper contributes to methodological advances in developmental psychology in the following ways.
-First, we could captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+First, we could capture fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
 Individuals behaved consistently different from one another.
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in-person.
-In sum, our gaze understanding task provides a step towards more robust and reliable research methods, especially with regards to individual differences research.The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are freely accessible.
+Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
+In sum, our gaze understanding task provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
+The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
@@
 
-Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) towards an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
+Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
 Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
@@
 
-Our continuous hedge version yields higher internal consistency estimates compared to the categorical box version.
+Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
 Both study versions exhibit high retest reliability, also when controlling for age.
 Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al. (2000); improved reliability through aggregation).
-When testing time is limited, we would recommend the use of the continuous study version for higher internal consistency.
+When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
-Our task could consequently be used to study bias, preferences and diverse desires (e.g.~matching the box appearance to some feature/behavioral characteristic of the agent).
+Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).
 
 Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
-Researchers could consider to adjust the task difficulty, for example, by adjusting the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
+Researchers could consider adjusting the task difficulty, for example, by changing the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
 Another task extension could realize differential feedback dependent on the participant's accuracy.
@@
 
-As we could see in the splithalf reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
+As we could see in the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
 Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
-A potentially promising approach are computational cognitive models.
+Computational cognitive models are a promising approach forward.
 We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
 Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022)
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).
 
@@
 Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-As has been pointed out, social cognition is encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
+As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
 We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
@@
 The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
-The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in-person.
-Ultimately, this work shows a promising way forward towards more precise measures of cognitive development.
-The dataset and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
+The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
+Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
+The data set and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
 A demo version of the task is available at the following website: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
@@
 
+\newpage
+
 \hypertarget{declarations}{%
@@
 The web application (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) described here is open source (\url{https://github.com/ccp-eva/gafo-demo}).
-The datasets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
+The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
 All experiments were preregistered (\url{https://osf.io/zjhsc/}).
@@
 This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers and adults who participated in the study. We thank Jana Jurkat for her help with data collection.
+We thank all the children, caregivers and adults who participated in the study.
+We thank Jana Jurkat for her help with data collection.
 
@@
 
-\newpage
-
-\hypertarget{supplements}{%
-\section{Supplements}\label{supplements}}
-
-\hypertarget{child-sample}{%
-\subsection{Child sample}\label{child-sample}}
-
-\hypertarget{webcam-coding}{%
-\subsubsection{Webcam coding}\label{webcam-coding}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_webcamcoding_draws}
-
-}
-
-\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
-Factors of parental interference and their influence on the probability of responding correctly.
-The graph shows the estimated density curves of a model's predictor coefficient.
-Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison.
-(A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig4}
-\end{figure}
-
-Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
-This difference was especially prominent in younger participants in the box version of the task.
-It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
-In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
-We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-A trial was defined as the time between two eye blinking sounds.
-We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
-In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
-We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.\footnote{Attentive readers might notice that we simplified the structure of random effects.
-  Compared to our models in the \emph{Individual differences} section, this model does not include the random slope for symmetric target position within participants.
-  We decided to do so since we had limited amount of data from few participants.}
-
-We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
-Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
-Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
-We compared models using WAIC (widely applicable information criterion) scores and weights.
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
-In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
-Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
-
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
-\midrule
-By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
-By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
-By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
-By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
-By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
-By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
-By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
-By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
-By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
-By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
-By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
-By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{adult-sample}{%
-\subsection{Adult sample}\label{adult-sample}}
-
-\hypertarget{recruitment}{%
-\subsubsection{Recruitment}\label{recruitment}}
-
-We recruited participants using the online participant recruitment service \emph{Prolific} from the University of Oxford.
-\emph{Prolific}'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
-The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
-We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
-\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
-Therefore, study data was saved only on our internal servers, while \emph{Prolific} provided demographic information of the participants.
-Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
-This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion: we redirected participants from our study website back to the \emph{Prolific} website using URL parameters.
-We used \emph{Prolific}'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
-
-\hypertarget{study-1---validation-hedge-version}{%
-\subsubsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}
-
-The aim of Study 1 was to validate the hedge version of our gaze understanding task.
-The pre-registration can be found here: \url{https://osf.io/r3bhn}.
-We recruited participants online by advertising the study on \emph{Prolific}.
-
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in May 2021.
-Participants were compensated with £1.25 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-In average, participants took 05:56min to complete the study.
-Participants were required to complete the study on a tablet or desktop.
-Participation on mobile devices was disabled since the display would be too small and would harm click precision.
-It was indicated that the study required audio sound.
-
-We stored \emph{Prolific}'s internal demographic information, while not asking for additional personal information.
-
-\hypertarget{study-2---validation-box-version}{%
-\subsubsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}
-
-As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
-However, this time we focussed on validating the box version of the task in an adult sample.
-Participants were presented with eight boxes in which the target could land.
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in June 2021.
-Participants were compensated with £1.00 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-In average, participants took 04:43min to complete the study.
-
-\hypertarget{study-3---reliability-hedge-version}{%
-\subsubsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}
-
-In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
-The pre-registration can be found here: \url{https://osf.io/nu62m}.
-We tested the same participants twice with a delay of two weeks.
-The testing conditions were as specified in Study 1 and 2.
-However, the target locations as well as the succession of animals and target colors was randomized once.
-Each participant then received the same fixed randomized order of target location, animal, and target color.
-Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.
-
-In addition to the beforementioned prescreening settings, we used a whitelist.
-\emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
-Only these subjects are then invited to participate in a study.
-This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.
-
-In a first round, 60 participants took part on the first testday.
-Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-The maximum time is calculated by \emph{Prolific}, based on the estimated average completion time.
-For this study, the maximum time amounted to 41 minutes.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-In average, participants took 07:11min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-In average, participants took 06:36min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-In average, participants took 06:51min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-In average, participants took 06:26min to complete the second part of the study.
-
-\hypertarget{study-4---reliability-box-version}{%
-\subsubsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}
-
-As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
-However, this time participants were presented with the box version of the task.
-Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
-As in study 2, we employed eight boxes in which the target could land.
-
-In a first round, 60 participants took part on the first testday.
-Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-In average, participants took 07:33min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-In average, participants took 07:50min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-In average, participants took 07:37min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
-Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-In average, participants took 06:30min to complete the second part of the study.
-
-\hypertarget{instructions-and-voice-over-descriptions}{%
-\section{Instructions and voice over descriptions}\label{instructions-and-voice-over-descriptions}}
-
-This is the content of our audio recordings that were played as instructions and during voice over trials.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
-\toprule()
-\endhead
-\textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
-\textbf{welcome} & Hallo!
-Schön, dass du da bist.
-Wir spielen jetzt das Ballon-Spiel!
-Siehst du die Tiere auf dem Bild da?
-Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen.
-Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
-& Hello!
-Great that you're here.
-We'll now play a balloon game.
-Can you see the animals in the picture over there?
-We want to play together with the animals using the balloon.
-We'll now talk you through exactly what will happen.
-& welcome.mp3 \\
-\textbf{touch} & Schau mal, da steht ein Tier im Fenster.
-Und siehst du den Ballon da?
-Der Ballon fällt immer runter und landet auf dem Boden.
-Und du musst ihn dann finden.
-Das Tier hilft Dir und schaut immer den Ballon an.
-& Look, an animal is standing in the window.
-And can you see the balloon over there?
-The balloon always falls down and lands on the ground.
-And you have to find it!
-The animal helps you and always looks at the balloon.
-& touch-1.mp3 \\
-& Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
-\textbf{fam - HEDGE} & Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er hinter eine Hecke.
-Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-& Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon will fall down again.
-This time, it will fall behind a hedge.
-And you have to find it!
-The animal helps you and looks at the balloon.
-& fam-hedge-1.mp3 \\
-& Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
-\textbf{fam - BOX} & Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er in eine Kiste.
-Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-& Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon falls down again.
-This time, it falls into a box.
-And you have to find it!
-The animal helps you and looks at the balloon.
-& fam-box-1.mp3 \\
-& Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
-\textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Hecke.
-Die Hecke wächst jetzt hoch.
-& Nice, good job!
-Now, we'll continue playing.
-There is the balloon, the animal and the hedge.
-The hedge is growing a bit now.
-& test-hedge-1.mp3 \\
-& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-& The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls to the ground and you have to find it.
-Remember - the animal always looks at the balloon!
-& test-hedge-2.mp3 \\
-& Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
-\textbf{test - BOX} & Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Kisten.
-Jetzt wächst eine Hecke hoch.
-& Nice, good job!
-Now, we'll continue playing.
-There is the balloon and the animal.
-Now, a hedge is growing.
-& test-box-1.mp3 \\
-& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-& The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls into a box and you have to find it.
-Remember - the animal always looks at the balloon!
-& test-box-2.mp3 \\
-& Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
-\textbf{goodbye} & Geschafft!
-Die Tiere sind schon ganz glücklich vom Spielen!
-Vielen Dank für deine Hilfe!
-Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf & The animals are super happy after playing.
-Thanks a lot for your help!
-See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
-\textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
-\textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
-\textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
-\textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
-\textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
-\textbf{sound of blinking eyes} & - & - & blink.mp3 \\
-\textbf{sound for target click} & - & - & positive-feedback.mp3 \\
-\bottomrule()
-\end{longtable}
-
 \end{document}

### 2022-08-18 supplements/supplements.Rmd
create separate document for supplements

---
title             : |
                    <center> Supplements for the manuscript </center>
                    <center> "Measuring individual differences in the understanding of gaze cues across the lifespan" </center>
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Steven Kalinke"
    affiliation   : "1"

  - name          : "Daniel M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Child sample
## Webcam coding
(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**. Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level (i.e., average across trials per subject).

```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
```

```{r sample}
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
This difference was especially prominent in younger participants in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(testtrials$subjID[testtrials$datacollection == "remote - unsupervised" & testtrials$ageInYears == 3 & testtrials$studyversion == "box" & testtrials$webcam == TRUE & testtrials$studytype == "vali"])`).
We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
A trial was defined as the time between two eye blinking sounds.
We transcribed all utterances by parents and children and counted the words uttered by each.
We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
We conducted a model comparison to estimate the effects of parental interference.
Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^3]

[^3]: Attentive readers might notice that we simplified the structure of random effects.
    Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
    We decided to do so since we had limited amount of data from few participants.

We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
We compared models using WAIC (widely applicable information criterion) scores and weights.
As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
In all cases, however, ELPD difference scores were smaller than their standard errors.
Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.

```{r webcam_table, results = "asis"}
webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

papaja::apa_table(
  webcam_models,
  caption = "Model comparison for exploratory webcam coding of parental interference",
  note = "All models included random intercepts for participant and target position.",
  escape = T
)
```

\newpage

# Adult sample
## Recruitment
We recruited participants using the online participant recruitment service *Prolific* from the University of Oxford.
*Prolific*'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
Therefore, study data was saved only on our internal servers, while *Prolific* provided demographic information of the participants.
Participants' *Prolific* ID was forwarded to our study website using URL parameters.
This way, we could match participant demographic data to our study data.
The same technique was used to confirm study completion: we redirected participants from our study website back to the *Prolific* website using URL parameters.
We used *Prolific*'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.

## Study 1 - Validation hedge version
The aim of Study 1 was to validate the hedge version of our gaze understanding task.
The pre-registration can be found here: <https://osf.io/r3bhn>.
We recruited participants online by advertising the study on *Prolific*.

50 adults participated in the study.
One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in May 2021.
Participants were compensated with £1.25 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
On average, participants took 05:56min to complete the study.
Participants were required to complete the study on a tablet or desktop.
Participation on mobile devices was disabled since the display would be too small and would harm click precision.
It was indicated that the study required audio sound.

We stored *Prolific*'s internal demographic information, while not asking for additional personal information.

## Study 2 - Validation box version
As in study 1, we recruited participants on *Prolific*, and employed the same methodology.
However, this time we focussed on validating the box version of the task in an adult sample.
Participants were presented with eight boxes in which the target could land.
50 adults participated in the study.
One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in June 2021.
Participants were compensated with £1.00 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
On average, participants took 04:43min to complete the study.

## Study 3 - Reliability hedge version
In stuyy 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
The pre-registration can be found here: <https://osf.io/nu62m>.
We tested the same participants twice with a delay of two weeks.
The testing conditions were as specified in Study 1 and 2.
However, the target locations as well as the succession of animals and target colors was randomized once.
Each participant then received the same fixed randomized order of target location, animal, and target color.
Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.

In addition to the beforementioned prescreening settings, we used a whitelist.
*Prolific* has a so-called *custom allowlist prescreening filter* where one can enter the *Prolific* IDs of participants who completed a previous study.
Only these subjects are then invited to participate in a study.
This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.

In a first round, 60 participants took part on the first testday.
Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
The maximum time is calculated by *Prolific*, based on the estimated average completion time.
For this study, the maximum time amounted to 41 minutes.
For the first testday, participants were compensated with £1.25.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
On average, participants took 07:11min to complete the first part.

Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Participants were compensated with £1.50 for completing the second part of the study.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
On average, participants took 06:36min to complete the second part of the study.

Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
On average, participants took 06:51min to complete the first part.

Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
On average, participants took 06:26min to complete the second part of the study.

## Study 4 - Reliability box version
As in study 3, we recruited participants on *Prolific*, and employed the same methodology.
However, this time participants were presented with the box version of the task.
Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
As in study 2, we employed eight boxes in which the target could land.

In a first round, 60 participants took part on the first testday.
Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
For the first testday, participants were compensated with £1.25.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
On average, participants took 07:33min to complete the first part.

Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
Participants were compensated with £1.50 for completing the second part of the study.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
On average, participants took 07:50min to complete the second part of the study.

Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
On average, participants took 07:37min to complete the first part.

Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
On average, participants took 06:30min to complete the second part of the study.

\newpage

# Instructions and voice-over descriptions
This is the content of our audio recordings that were played as instructions and during voice-over trials.

|                              |                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                       |                       |
|------------------|------------------|------------------|------------------|
| **Timeline**                 | **German**                                                                                                                                                                                                                                       | **English**                                                                                                                                                                                                                                           | **Filename**          |
| **welcome**                  | Hallo! Schön, dass du da bist. Wir spielen jetzt das Ballon-Spiel! Siehst du die Tiere auf dem Bild da? Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen. Was genau passiert, erklären wir dir jetzt ganz in Ruhe.            | Hello! Great that you're here. We'll now play a balloon game. Can you see the animals in the picture over there? We want to play together with the animals using the balloon. We'll now talk you through exactly what will happen.                    | welcome.mp3           |
| **touch**                    | Schau mal, da steht ein Tier im Fenster. Und siehst du den Ballon da? Der Ballon fällt immer runter und landet auf dem Boden. Und du musst ihn dann finden. Das Tier hilft Dir und schaut immer den Ballon an.                                   | Look, an animal is standing in the window. And can you see the balloon over there? The balloon always falls down and lands on the ground. And you have to find it! The animal helps you and always looks at the balloon.                              | touch-1.mp3           |
|                              | Wo ist der Ballon? Drück auf den Ballon!                                                                                                                                                                                                         | Where is the balloon? Click on the balloon!                                                                                                                                                                                                           | prompt-touch-long.mp3 |
| **fam - HEDGE**              | Klasse, das war super! Jetzt spielen wir weiter. Siehst du wieder das Tier und den Ballon da? Der Ballon fällt wieder runter. Diesmal fällt er hinter eine Hecke. Du musst ihn wieder finden. Das Tier hilft dir und schaut immer den Ballon an. | Perfect, that was great! Now, we'll continue playing. Can you see the animal and the balloon again? The balloon will fall down again. This time, it will fall behind a hedge. And you have to find it! The animal helps you and looks at the balloon. | fam-hedge-1.mp3       |
|                              | Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist.                                                                                                                                                                                     | Where is the balloon? On the hedge, click where the balloon is.                                                                                                                                                                                       | prompt-hedge-long.mp3 |
| **fam - BOX**                | Klasse, das war super! Jetzt spielen wir weiter. Siehst du wieder das Tier und den Ballon da? Der Ballon fällt wieder runter. Diesmal fällt er in eine Kiste. <br>Du musst ihn wieder finden. Das Tier hilft dir und schaut immer den Ballon an. | Perfect, that was great! Now, we'll continue playing. Can you see the animal and the balloon again? The balloon falls down again. This time, it falls into a box. And you have to find it! The animal helps you and looks at the balloon.             | fam-box-1.mp3         |
|                              | Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon.                                                                                                                                                                                          | Where is the balloon? Click on the box with the balloon.                                                                                                                                                                                              | prompt-box-long.mp3   |
| **test - HEDGE**             | Klasse , das hast du toll gemacht! Nun spielen wir weiter. Da sind wieder der Ballon, das Tier und die Hecke. Die Hecke wächst jetzt hoch.                                                                                                       | Nice, good job! Now, we'll continue playing. There is the balloon, the animal and the hedge. The hedge is growing a bit now.                                                                                                                          | test-hedge-1.mp3      |
|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber! Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden. Denk dran - das Tier schaut immer den Ballon an.                                            | The balloon is behind the hedge now. You can't see it - but the animal can! The balloon falls to the ground and you have to find it. Remember - the animal always looks at the balloon!                                                               | test-hedge-2.mp3      |
|                              | Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist.                                                                                                                                                                              | Now, the hedge is shrinking. On the hedge, click where the balloon is.                                                                                                                                                                                | test-hedge-3.mp3      |
| **test - BOX**               | Klasse , das hast du toll gemacht! Nun spielen wir weiter. Da sind wieder der Ballon, das Tier und die Kisten. Jetzt wächst eine Hecke hoch.                                                                                                     | Nice, good job! Now, we'll continue playing. There is the balloon and the animal. Now, a hedge is growing.                                                                                                                                            | test-box-1.mp3        |
|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber! Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden. Denk dran - das Tier schaut immer den Ballon an.                                            | The balloon is behind the hedge now. You can't see it - but the animal can! The balloon falls into a box and you have to find it. Remember - the animal always looks at the balloon!                                                                  | test-box-2.mp3        |
|                              | Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon.                                                                                                                                                                                   | Now, the hedge is shrinking. Click on the box with the balloon.                                                                                                                                                                                       | test-box-3.mp3        |
| **goodbye**                  | Geschafft! Die Tiere sind schon ganz glücklich vom Spielen! Vielen Dank für deine Hilfe! Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf                                                                                       | The animals are super happy after playing. Thanks a lot for your help! See you soon and goodbye from the pig, monkey and sheep                                                                                                                        | goodbye.mp3           |
| **general prompt**           | Wo ist der Ballon?                                                                                                                                                                                                                               | Where is the balloon?                                                                                                                                                                                                                                 | prompt-general.mp3    |
| **touch - no response**      | Drück auf den Ballon!                                                                                                                                                                                                                            | Click on the balloon!                                                                                                                                                                                                                                 | prompt-touch.mp3      |
| **hedge - no response**      | Drücke auf die Hecke - wo der Ballon ist!                                                                                                                                                                                                        | On the hedge, click where the balloon is!                                                                                                                                                                                                             | prompt-hedge.mp3      |
| **box - no response**        | Drücke auf die Kiste mit dem Ballon!                                                                                                                                                                                                             | Click on the box with the balloon!                                                                                                                                                                                                                    | prompt-box.mp3        |
| **landing sound of balloon** | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | balloon-lands.mp3     |
| **sound of blinking eyes**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | blink.mp3             |
| **sound for target click**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | positive-feedback.mp3 |

### 2022-08-18 supplements/supplements.tex
create separate document for supplements

--- 2022-08-18 supplements/supplements.Rmd
@@
----
-title             : |
-                    <center> Supplements for the manuscript </center>
-                    <center> "Measuring individual differences in the understanding of gaze cues across the lifespan" </center>
-shorttitle        : "Supplements"
-author:
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man,floatsintext]{apa6}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-  - name          : "Julia Prein"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
-    email         : "julia_prein@eva.mpg.de"
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-  - name          : "Manuel Bohn"
-    affiliation   : "1"
-  - name          : "Steven Kalinke"
-    affiliation   : "1"
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
-  - name          : "Daniel M. Haun"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes:
-  - \usepackage{setspace}
-  - \captionsetup[figure]{font={stretch=1}}
-editor_options: 
-  markdown: 
-    wrap: sentence
----
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 
-```{r setup, include = FALSE}
-library("papaja")
-library("tidyverse")
-theme_set(theme_classic())
-```
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
 
-# Child sample
-## Webcam coding
-(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**.
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\usepackage{setspace}
+\captionsetup[figure]{font={stretch=1}}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
+  pdflang={en-EN},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Supplements for the manuscript
+
+``Measuring individual differences in the understanding of gaze cues across the lifespan''}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
+\date{}
+
+\shorttitle{Supplements}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
+E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}
+
+\begin{document}
+\maketitle
+
+\hypertarget{child-sample}{%
+\section{Child sample}\label{child-sample}}
+
+\hypertarget{webcam-coding}{%
+\subsection{Webcam coding}\label{webcam-coding}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/supplements_webcamcoding_draws}
+
+}
+
+\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
 Factors of parental interference and their influence on the probability of responding correctly.
@@
 (A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level (i.e., average across trials per subject).
-
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
-```
-
-```{r sample}
-testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-    studyversion = factor(studyversion, levels = c("hedge", "box")), 
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "adults")), 
-    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
-  )
-```
+(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig4}
+\end{figure}
 
@@
 In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(testtrials$subjID[testtrials$datacollection == "remote - unsupervised" & testtrials$ageInYears == 3 & testtrials$studyversion == "box" & testtrials$webcam == TRUE & testtrials$studytype == "vali"])`).
+Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive & negative feedback, motivational statements, and incomprehensible utterances.
+We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
 In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^3]
-
-[^3]: Attentive readers might notice that we simplified the structure of random effects.
-    Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
-    We decided to do so since we had limited amount of data from few participants.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.\footnote{Attentive readers might notice that we simplified the structure of random effects.
+  Compared to our models in the \emph{Individual differences} section, this model does not include the random slope for symmetric target position within participants.
+  We decided to do so since we had limited amount of data from few participants.}
 
@@
 In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
+Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
 Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
 
-```{r webcam_table, results = "asis"}
-webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
-  mutate_if(is.numeric, round, 2)
+\begin{table}[tbp]
 
-papaja::apa_table(
-  webcam_models,
-  caption = "Model comparison for exploratory webcam coding of parental interference",
-  note = "All models included random intercepts for participant and target position.",
-  escape = T
-)
-```
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
+
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
+\midrule
+By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
+By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
+By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
+By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
+By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
+By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
+By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
+By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
+By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
+By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
+By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
+By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 
-# Adult sample
-## Recruitment
-We recruited participants using the online participant recruitment service *Prolific* from the University of Oxford.
-*Prolific*'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
+\hypertarget{adult-sample}{%
+\section{Adult sample}\label{adult-sample}}
+
+\hypertarget{recruitment}{%
+\subsection{Recruitment}\label{recruitment}}
+
+We recruited participants using the online participant recruitment service \emph{Prolific} from the University of Oxford.
+\emph{Prolific}'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
 The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
 We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
-*Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
-Therefore, study data was saved only on our internal servers, while *Prolific* provided demographic information of the participants.
-Participants' *Prolific* ID was forwarded to our study website using URL parameters.
+\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
+Therefore, study data was saved only on our internal servers, while \emph{Prolific} provided demographic information of the participants.
+Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
 This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion: we redirected participants from our study website back to the *Prolific* website using URL parameters.
-We used *Prolific*'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
+The same technique was used to confirm study completion: we redirected participants from our study website back to the \emph{Prolific} website using URL parameters.
+We used \emph{Prolific}'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
 
-## Study 1 - Validation hedge version
+\hypertarget{study-1---validation-hedge-version}{%
+\subsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}
+
 The aim of Study 1 was to validate the hedge version of our gaze understanding task.
-The pre-registration can be found here: <https://osf.io/r3bhn>.
-We recruited participants online by advertising the study on *Prolific*.
+The pre-registration can be found here: \url{https://osf.io/r3bhn}.
+We recruited participants online by advertising the study on \emph{Prolific}.
 
@@
 
-We stored *Prolific*'s internal demographic information, while not asking for additional personal information.
+We stored \emph{Prolific}'s internal demographic information, while not asking for additional personal information.
 
-## Study 2 - Validation box version
-As in study 1, we recruited participants on *Prolific*, and employed the same methodology.
+\hypertarget{study-2---validation-box-version}{%
+\subsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}
+
+As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
 However, this time we focussed on validating the box version of the task in an adult sample.
@@
 
-## Study 3 - Reliability hedge version
+\hypertarget{study-3---reliability-hedge-version}{%
+\subsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}
+
 In stuyy 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
-The pre-registration can be found here: <https://osf.io/nu62m>.
+The pre-registration can be found here: \url{https://osf.io/nu62m}.
 We tested the same participants twice with a delay of two weeks.
@@
 In addition to the beforementioned prescreening settings, we used a whitelist.
-*Prolific* has a so-called *custom allowlist prescreening filter* where one can enter the *Prolific* IDs of participants who completed a previous study.
+\emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
 Only these subjects are then invited to participate in a study.
@@
 One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-The maximum time is calculated by *Prolific*, based on the estimated average completion time.
+The maximum time is calculated by \emph{Prolific}, based on the estimated average completion time.
 For this study, the maximum time amounted to 41 minutes.
@@
 
-## Study 4 - Reliability box version
-As in study 3, we recruited participants on *Prolific*, and employed the same methodology.
+\hypertarget{study-4---reliability-box-version}{%
+\subsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}
+
+As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
 However, this time participants were presented with the box version of the task.
@@
 
-# Instructions and voice-over descriptions
+\hypertarget{instructions-and-voice-over-descriptions}{%
+\section{Instructions and voice-over descriptions}\label{instructions-and-voice-over-descriptions}}
+
 This is the content of our audio recordings that were played as instructions and during voice-over trials.
 
-|                              |                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                       |                       |
-|------------------|------------------|------------------|------------------|
-| **Timeline**                 | **German**                                                                                                                                                                                                                                       | **English**                                                                                                                                                                                                                                           | **Filename**          |
-| **welcome**                  | Hallo!
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
+\toprule()
+\endhead
+\textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
+\textbf{welcome} & Hallo!
 Schön, dass du da bist.
@@
 Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
-| Hello!
+& Hello!
 Great that you're here.
@@
 We'll now talk you through exactly what will happen.
-| welcome.mp3           |
-| **touch**                    | Schau mal, da steht ein Tier im Fenster.
+& welcome.mp3 \\
+\textbf{touch} & Schau mal, da steht ein Tier im Fenster.
 Und siehst du den Ballon da?
@@
 Das Tier hilft Dir und schaut immer den Ballon an.
-| Look, an animal is standing in the window.
+& Look, an animal is standing in the window.
 And can you see the balloon over there?
@@
 The animal helps you and always looks at the balloon.
-| touch-1.mp3           |
-|                              | Wo ist der Ballon?
-Drück auf den Ballon!
-| Where is the balloon?
-Click on the balloon!
-| prompt-touch-long.mp3 |
-| **fam - HEDGE**              | Klasse, das war super!
+& touch-1.mp3 \\
+& Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
+\textbf{fam - HEDGE} & Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 Das Tier hilft dir und schaut immer den Ballon an.
-| Perfect, that was great!
+& Perfect, that was great!
 Now, we'll continue playing.
@@
 The animal helps you and looks at the balloon.
-| fam-hedge-1.mp3       |
-|                              | Wo ist der Ballon?
-Drücke auf die Hecke - wo der Ballon ist.
-| Where is the balloon?
-On the hedge, click where the balloon is.
-| prompt-hedge-long.mp3 |
-| **fam - BOX**                | Klasse, das war super!
+& fam-hedge-1.mp3 \\
+& Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
+\textbf{fam - BOX} & Klasse, das war super!
 Jetzt spielen wir weiter.
@@
 Diesmal fällt er in eine Kiste.
-<br>Du musst ihn wieder finden.
+Du musst ihn wieder finden.
 Das Tier hilft dir und schaut immer den Ballon an.
-| Perfect, that was great!
+& Perfect, that was great!
 Now, we'll continue playing.
@@
 The animal helps you and looks at the balloon.
-| fam-box-1.mp3         |
-|                              | Wo ist der Ballon?
-Drücke auf die Kiste mit dem Ballon.
-| Where is the balloon?
-Click on the box with the balloon.
-| prompt-box-long.mp3   |
-| **test - HEDGE**             | Klasse , das hast du toll gemacht!
+& fam-box-1.mp3 \\
+& Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
+\textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 Die Hecke wächst jetzt hoch.
-| Nice, good job!
+& Nice, good job!
 Now, we'll continue playing.
@@
 The hedge is growing a bit now.
-| test-hedge-1.mp3      |
-|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
+& test-hedge-1.mp3 \\
+& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
 Denk dran - das Tier schaut immer den Ballon an.
-| The balloon is behind the hedge now.
+& The balloon is behind the hedge now.
 You can't see it - but the animal can!
@@
 Remember - the animal always looks at the balloon!
-| test-hedge-2.mp3      |
-|                              | Dann schrumpft die Hecke.
-Drücke auf die Hecke - wo der Ballon ist.
-| Now, the hedge is shrinking.
-On the hedge, click where the balloon is.
-| test-hedge-3.mp3      |
-| **test - BOX**               | Klasse , das hast du toll gemacht!
+& test-hedge-2.mp3 \\
+& Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
+\textbf{test - BOX} & Klasse , das hast du toll gemacht!
 Nun spielen wir weiter.
@@
 Jetzt wächst eine Hecke hoch.
-| Nice, good job!
+& Nice, good job!
 Now, we'll continue playing.
@@
 Now, a hedge is growing.
-| test-box-1.mp3        |
-|                              | Der Ballon ist nun hinter der Hecke. Du kannst das nicht sehen - das Tier aber!
+& test-box-1.mp3 \\
+& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
 Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
 Denk dran - das Tier schaut immer den Ballon an.
-| The balloon is behind the hedge now.
+& The balloon is behind the hedge now.
 You can't see it - but the animal can!
@@
 Remember - the animal always looks at the balloon!
-| test-box-2.mp3        |
-|                              | Dann schrumpft die Hecke.
-Drücke auf die Kiste mit dem Ballon.
-| Now, the hedge is shrinking.
-Click on the box with the balloon.
-| test-box-3.mp3        |
-| **goodbye**                  | Geschafft!
+& test-box-2.mp3 \\
+& Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
+\textbf{goodbye} & Geschafft!
 Die Tiere sind schon ganz glücklich vom Spielen!
 Vielen Dank für deine Hilfe!
-Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf                                                                                       | The animals are super happy after playing.
+Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf & The animals are super happy after playing.
 Thanks a lot for your help!
-See you soon and goodbye from the pig, monkey and sheep                                                                                                                        | goodbye.mp3           |
-| **general prompt**           | Wo ist der Ballon?
-| Where is the balloon?
-| prompt-general.mp3    |
-| **touch - no response**      | Drück auf den Ballon!
-| Click on the balloon!
-| prompt-touch.mp3      |
-| **hedge - no response**      | Drücke auf die Hecke - wo der Ballon ist!
-| On the hedge, click where the balloon is!
-| prompt-hedge.mp3      |
-| **box - no response**        | Drücke auf die Kiste mit dem Ballon!
-| Click on the box with the balloon!
-| prompt-box.mp3        |
-| **landing sound of balloon** | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | balloon-lands.mp3     |
-| **sound of blinking eyes**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | blink.mp3             |
-| **sound for target click**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | positive-feedback.mp3 |
+See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
+\textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
+\textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
+\textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
+\textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
+\textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
+\textbf{sound of blinking eyes} & - & - & blink.mp3 \\
+\textbf{sound for target click} & - & - & positive-feedback.mp3 \\
+\bottomrule()
+\end{longtable}
+
+\end{document}

### 2022-08-18 paper/manuscript.Rmd
small proof-reading edits

@@
 abstract: |
-
-  To explain and predict the behavior of agents, we use social cognition: we represent and reason about others' perspectives, knowledge, intentions, beliefs, and preferences.
-However, traditional measures of social cognition (e.g., false belief change-of-location tasks) often lack satisfactory psychometric properties: they are not designed to capture variation *between* children and rely on low trial numbers, dichotomous measures, and group averages.
-This has profound implications for what these studies can show.
-Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+  To navigate the social world and interact with other agents, we use social cognition.
+Traditional measures of social cognition often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals.
+This is problematic because developmental theories emphasize the role of social interaction on the development of social cognition which varies substantially across individuals.
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-   We designed a gaze understanding task to study social cognition in young children and adults to approach this issue.
+   Here, we present a new task to study individual differences in social cognition in children and adults.
 We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding – the ability to locate and use the attentional focus of an agent.
-Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+Our interactive browser-based task works across devices and enables in-person and remote testing.
 The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements.
-  Here we show that our task induces inter-individual differences in a child (N = XXX) and an adult (N = XXX) sample.
+   Our task induces inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
+  All materials and code are freely accessible to interested researchers. The task can be found here: https://ccp-odc.eva.mpg.de/gafo-demo/.
+
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
@@
 These files can either be sent to a server or downloaded to the local device.
+Personalized links can be created by passing on URL parameters.
 
@@
 
-Our newly implemented task features an online game where children or adults are asked to search for a balloon.
+Our newly implemented task asks children and adults to search for a balloon.
 The events proceed as follows (see Figure \@ref(fig:fig1)B and C).
@@
 The first trial of each type comprises a voice-over description of the presented events.
-The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script).
+The audio descriptions explicitly state that the agent is always looking at the target (see Supplements for audio script).
 After the four training trials, participants receive 15 test trials.
@@
 For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
-Families received an email with a short study description and a personalized link and received a reminder two weeks later if they had not already participated in the study.
+Families received an email with a short study description and a personalized link.
+If they had not participated in the study within two weeks, they received a reminder via email.
+Response rate to invitations after the reminder was \~50%.
 
@@
 Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
 
@@
 An experimenter guided the child through the study.
+
 Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
@@
 For neither study version nor age group did we find any floor or ceiling effects.
-The presentation as a tablet game kept children interested and motivated throughout the 15 test trials.
+The presentation as a web-app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 We assessed internal consistency (as split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: <https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
+Data collection and analysis were pre-registered (<https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
 Participants were equally distributed across the two study versions.
@@
 For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc.).
-In the box version, we ensured that each of the five boxes occurred exactly three times.
-For the remaining training trials, we repeated a fixed order of four random bins/boxes.
+In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
 Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
 Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
+For the four training trials, we repeated a fixed order of random bins/boxes.
 
@@
 For this, we used the data of the first test day.
-Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+
 @pronk2021methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
-To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+To compare our traditional approach of a simple odd-even split, we additionally calculated split-half reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
 First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
@@
 
-Second, we assessed the test-retest reliability.
+Second, we assessed test-retest reliability.
 We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
-Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics].
+Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach [@rouder2019psychometrics].
 We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
@@
 
-We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was high for most samples.
+We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.
+
 Figure \@ref(fig:fig3) compares split-half reliability coefficients by splitting and stratification method [@pronk2021methods].
@@
 
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^2]
+For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^2]
 
@@
 The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
-In the hedge version, the correlation between testdays was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
-In the box version, the correlation between testdays was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the hedge version, the correlation between test days was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the box version, the correlation between test days was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
 
@@
 As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
-For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
+For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
 This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
@@
 In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version: in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
-
+The outcome measure depends on the presented study version: the box version employs a categorical measure (i.e., proportion of correct choices), while the hedge version uses a continuous outcome (i.e., imprecision as distance between target and click).
 Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum [@hughes2015individual; @beaudoin2020systematic].
@@
 Both study versions exhibit high retest reliability, also when controlling for age.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
+Therefore, when a sufficient amount of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
 When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
-However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
 Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).
@@
 The cartoon-like presentation makes the task engaging for children and adults alike.
-Most importantly, we can dynamically modify the stimulus details (e.g., positions) on a trial-by-trial basis.
+Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
 Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
@@
 Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
-Children in the remote sample are slightly more precise.
-This effect is most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
+Children in the remote sample were slightly more precise.
+This effect was most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
 Therefore, we recommend using a tablet for remote data collection.
 Children can click for themselves and caregivers have less chance to interfere.
-
 The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.
 
-After having proven satisfactory psychometric properties, the next step will be to ensure the validity of our task.
+After having probed our new testing infrastructure and psychometric properties, the next step will be to ensure the validity of our gaze understanding task.
 Validity is often assessed by looking at concurrent relations between measures.
@@
 In addition, a subset of our remote child sample completed a receptive vocabulary task [@bohnorev].
-We will report the association between these family-level factors and children's language on their gaze understanding abilities in a separate paper (in preparation).
+We will report the association between these family-level factors and children's language skills on their gaze understanding abilities in a separate paper (in preparation).
 In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
@@
 As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries [@hughes2011individual; @schaafsma2015deconstructing].
-We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
+We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding to get a complete picture of children's social cognition.
 
@@
 
-We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
-The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+We have presented a new experimental paradigm to study gaze understanding across the lifespan.
+Our gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
 The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
 Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
-The data set and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
+The data sets and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
 A demo version of the task is available at the following website: <https://ccp-odc.eva.mpg.de/gafo-demo/>.

### 2022-08-18 paper/manuscript.tex
small proof-reading edits

@@
 \abstract{%
-To explain and predict the behavior of agents, we use social cognition: we represent and reason about others' perspectives, knowledge, intentions, beliefs, and preferences.
-However, traditional measures of social cognition (e.g., false belief change-of-location tasks) often lack satisfactory psychometric properties: they are not designed to capture variation \emph{between} children and rely on low trial numbers, dichotomous measures, and group averages.
-This has profound implications for what these studies can show.
-Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.
+To navigate the social world and interact with other agents, we use social cognition.
+Traditional measures of social cognition often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
+This is problematic because developmental theories emphasize the role of social interaction on the development of social cognition which varies substantially across individuals and contexts.
 To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-We designed a gaze understanding task to study social cognition in young children and adults to approach this issue.
+Here, we present a new task to study individual differences in social cognition in children and adults.
 We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
-Our interactive task works across devices and enables supervised and unsupervised, as well as in-person and remote testing.
+Our interactive browser-based task works across devices and enables in-person and remote testing.
 The implemented spatial layout allows for discrete and continuous measures of participants' click imprecision and is easily adaptable to different study requirements.
-Here we show that our task induces inter-individual differences in a child (N = XXX) and an adult (N = XXX) sample.
+Our task induces inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
+All materials and code are freely accessible to interested researchers. The task can be found here: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
 }
@@
 
-Our newly implemented task features an online game where children or adults are asked to search for a balloon.
+Our newly implemented task asks children and adults to search for a balloon.
 The events proceed as follows (see Figure \ref{fig:fig1}B and C).
@@
 For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
-Families received an email with a short study description and a personalized link and received a reminder two weeks later if they had not already participated in the study.
+Families received an email with a short study description and a personalized link.
+If they had not participated in the study within two weeks, they received a reminder via email.
+Response rate to invitations after the reminder was \textasciitilde50\%.
 
@@
 Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
 
@@
 We assessed internal consistency (as split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (can be found here: \url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
+Data collection and analysis were pre-registered (\url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
 Participants were equally distributed across the two study versions.
@@
 For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 \& 2, bin 3 \& 4, etc.).
-In the box version, we ensured that each of the five boxes occurred exactly three times.
-For the remaining training trials, we repeated a fixed order of four random bins/boxes.
+In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
 Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
 Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
+For the four training trials, we repeated a fixed order of random bins/boxes.
 
@@
 For this, we used the data of the first test day.
-Performance was defined according to study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+
 Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
-To compare our traditional approach of a simple odd-even split, we additionally calculated reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
+To compare our traditional approach of a simple odd-even split, we additionally calculated split-half reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
 First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
@@
 
-Second, we assessed the test-retest reliability.
+Second, we assessed test-retest reliability.
 We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
-Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM based approach (Rouder \& Haaf, 2019).
+Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach (Rouder \& Haaf, 2019).
 We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
@@
 
-We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was high for most samples.
+We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.
+
 Figure \ref{fig:fig3} compares split-half reliability coefficients by splitting and stratification method (Pronk et al., 2021).
@@
 
-For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
+For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
   The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
@@
 The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
-In the hedge version, the correlation between testdays was 0.90 (95\% CI {[}0.67;1.00{]}).
-In the box version, the correlation between testdays was 0.91 (95\% CI {[}0.69;1.00{]}).
+In the hedge version, the correlation between test days was 0.90 (95\% CI {[}0.67;1.00{]}).
+In the box version, the correlation between test days was 0.91 (95\% CI {[}0.69;1.00{]}).
 
@@
 As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
-For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age.
+For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
 This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
@@
 In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version: in the hedge version, we implemented a continuous measure, while the box version employs a categorical measure.
-
+The outcome measure depends on the presented study version: the box version employs a categorical measure (i.e., proportion of correct choices), while the hedge version uses a continuous outcome (i.e., imprecision as distance between target and click).
 Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
@@
 Both study versions exhibit high retest reliability, also when controlling for age.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can yield reliable individual estimates (cf. Hughes et al. (2000); improved reliability through aggregation).
+Therefore, when a sufficient amount of trials is presented, the box version of the task can also yield reliable individual estimates (cf.
+Hughes et al.
+(2000); improved reliability through aggregation).
 When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
-However, the categorical box version demonstrates design features that might be preferable in some research contexts: researchers could induce different levels of salience for each box.
+However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
 Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).
@@
 In addition, a subset of our remote child sample completed a receptive vocabulary task (Bohn, Prein, Delikaya, Haun, \& Gagarina, n.d.).
-We will report the association between these family-level factors and children's language on their gaze understanding abilities in a separate paper (in preparation).
+We will report the association between these family-level factors and children's language skills on their gaze understanding abilities in a separate paper (in preparation).
 In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).
@@
 As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
-We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding.
+We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding to get a complete picture of children's social cognition.
 
@@
 
-We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
-The gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+We have presented a new experimental paradigm to study gaze understanding across the lifespan.
+Our gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
 The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
 Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
-The data set and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
+The data sets and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
 A demo version of the task is available at the following website: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.

### 2022-08-24 paper/manuscript.Rmd
comments discussion Manuel

@@
 ---
-title             : "Measuring individual differences in the understanding of gaze cues across the lifespan"
+title             : "Measuring individual differences in the understanding of gaze cues across the lifespan [Julia: ich würde mehr info in den titel packen - sowas wie reliable, open-source, web-based task to measure individual differences in gaze cue understanding in children (vll sogar age range) and adults.
+Ich denke bei do nem methods paper ist es wichtig das man weiß was phase ist basierend auf dem Titel.
+Vll willst DU auch ein Acronym?
+:)]"
 shorttitle        : "gaze understanding"
@@
 abstract: |
-  To navigate the social world and interact with other agents, we use social cognition.
-Traditional measures of social cognition often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals.
-This is problematic because developmental theories emphasize the role of social interaction on the development of social cognition which varies substantially across individuals.
-To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
+  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals [Julia: hab die zwei Sätze raus gelöscht weil nicht unbedingt relevant für methods paper].
 Here, we present a new task to study individual differences in social cognition in children and adults.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-  All materials and code are freely accessible to interested researchers. The task can be found here: https://ccp-odc.eva.mpg.de/gafo-demo/.
+  All materials and code are freely accessible to interested researchers. A version of the task is accessible online: https://ccp-odc.eva.mpg.de/gafo-demo/.
 
@@
 Designing this task required a new testing infrastructure.
-We designed the task as an interactive browser-based web app.
+We designed the task as an interactive browser-based web app [Julia: hier noch folgendes paper zitieren: http://dx.doi.org/https://doi.org/10.1080/15248372.2015.1061528; falls du den ansatz noch mehr "legitimieren" willst, kannst du auch noch eins oder zwei meiner tablet paper zitieren, zB: https://onlinelibrary.wiley.com/doi/10.1111/desc.13049  oder https://www.nature.com/articles/s41562-021-01145-1.
+Zeigt einfach dass das schon "erfolgreich" eingesetzt wird.].
 This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
@@
 ## Results
+
+[Julia: Kannst du in Figure 2 panel F noch chance linie mit rein machen?]
 
@@
 Another task extension could realize differential feedback dependent on the participant's accuracy.
-By inducing more between-person variance, reliability estimates could further increase.
+By inducing more between-person variance, reliability estimates could further increase [Julia: hier vll nochmal sagen, dass die momentanen properties abers chon gut sind].
 
 As we could see in the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity [Julia: Hier noch das zitieren: https://psyarxiv.com/xr7y3/].
 Computational cognitive models are a promising approach forward.
@@
 With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual].
+
+[Julia: Hier oder weiter oben eingebaut könntest du nochmal die wishlist aufgreifen und sagen in wie fern der task die Forderungen darin abdeckt - muss nicht sein, aber wäre denke ich nett weil das so ein coole Rechfertigung ist.]
 
@@
 Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
-Presented agents and objects can be easily adapted for future task modifications or specific cultural settings.
+Presented agents, voice-over instructions and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
 
@@
 Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
-For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
-In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
-In addition, a subset of our remote child sample completed a receptive vocabulary task [@bohnorev].
-We will report the association between these family-level factors and children's language skills on their gaze understanding abilities in a separate paper (in preparation).
-In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
+For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities [Julia: hier noch eine ziation jeweils, also einmal family einmal language].
+[Julia: Hab das alles raus genommen - macht meiner meinung nach wenig sinn das an zu teasern und dann zu sagen das kommt in nem anderen paper.
+ich als reviewer oder editor würde sagen: pack das hie rein.
+Daher eher sagen: future research should probe these realtions (family level und language)].
 
@@
 These resources allow interested researchers to use, extend and adapt the task.
+[Julia: Du könntest überlegen hier oder weiter oben noch einen screenshot von der demo version als figure zu nehmen.
+Das macht die usability nochmal konkreter.]
 

### 2022-08-25 paper/manuscript.Rmd
incorporate Manuels feedback;TANGO acronym

--- 2022-08-18 paper/manuscript.Rmd
@@
 ---
-title             : "Measuring individual differences in the understanding of gaze cues across the lifespan"
-shorttitle        : "gaze understanding"
+title             : "TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults"
+shorttitle        : "assessing individual differences in gaze understanding"
 author:
@@
     affiliation   : "1"
+  - name          : "Daniel B. M. Haun"
+    affiliation   : "1"
 
-  - name          : "Daniel M. Haun"
-    affiliation   : "1"
 affiliation:
@@
 abstract: |
-  To navigate the social world and interact with other agents, we use social cognition.
-Traditional measures of social cognition often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals.
-This is problematic because developmental theories emphasize the role of social interaction on the development of social cognition which varies substantially across individuals.
-To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-   Here, we present a new task to study individual differences in social cognition in children and adults.
-We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding – the ability to locate and use the attentional focus of an agent.
+  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
+  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief(approx.
+5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
    Our interactive browser-based task works across devices and enables in-person and remote testing.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-  All materials and code are freely accessible to interested researchers. The task can be found here: https://ccp-odc.eva.mpg.de/gafo-demo/.
+  All materials and code are freely accessible to interested researchers. A version of the task is accessible online: https://ccp-odc.eva.mpg.de/tango-demo/.
 
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "X"
+wordcount         : "6705"
 bibliography      : ["../../references.bib"]
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 header-includes:
@@
 ```{r load_data}
-testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
   # determine order of factors
@@
 
-@schaafsma2015deconstructing compiled a "wish-list" for new social-cognitive paradigms.
+@schaafsma2015deconstructing compiled a "wish list" for new social-cognitive paradigms.
 They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
@@
 We designed the task as an interactive browser-based web app. 
+Previous research has successfully used online study implementations that compare well to in-person data collection [@frank2016using; @bohn2021children; @bohn2021how].
 This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
@@
 
-The code is open-source (<https://github.com/ccp-eva/gafo-demo>), and a live demo version can be found under: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
+The code is open-source (<https://github.com/ccp-eva/tango-demo>), and a live demo version can be found under: <https://ccp-odc.eva.mpg.de/tango-demo/>.
 
@@
 (iii) The scripts for the website and the recorded data are stored on secure local servers.
-(B) Hedge version (continuous) of the gaze understanding task.
+(B) Hedge version (continuous) of the TANGO.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task.
+(C) Box version (discrete) of the TANGO.
 Number of boxes (min.
@@
 ```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/gafo_procedure.jpg")
+knitr::include_graphics("../figures/tango_procedure.png")
 ```
@@
 
-Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether the TANGO induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.
@@
 ```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics(c("../figures/gafo_arrangedplot.png"))
+knitr::include_graphics(c("../figures/tango_arrangedplot.png"))
 ```
@@
 
-As a next step, we aimed to investigate whether the variation that we captured with our gaze understanding task is reliable.
+As a next step, we aimed to investigate whether the variation that we captured with the TANGO is reliable.
 We assessed internal consistency (as split-half reliability) and test-retest reliability.
@@
 ```{r splithalf}
-splithalf <- readRDS(file = "../saves/gafo-splithalf-table.rds")
+splithalf <- readRDS(file = "../saves/tango-splithalf-table.rds")
 ```
 
-We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was medium to high.
+We found that the TANGO induced systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.
@@
 ```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/gafo_splithalf.png")
+knitr::include_graphics("../figures/tango_splithalf.png")
 ```
@@
 ```{r hedge_retest_correlationcoefficients}
-hedge_retest_correlationcoefficients <- readRDS(file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
+hedge_retest_correlationcoefficients <- readRDS(file = "../saves/tango-hedge-retest-correlationcoefficients.rds")
 ```
@@
 Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
-In sum, our gaze understanding task provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
-The web app (<https://ccp-odc.eva.mpg.de/gafo-demo/>) and its source code (<https://github.com/ccp-eva/gafo-demo>) are freely accessible.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
+The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
 
-One of the main contributions of the gaze understanding task is that it induces variation between participants.
+One of the main contributions of the TANGO is that it induces variation between participants.
 This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
@@
 
-Adding complexity to our gaze understanding task might increase individual differences in an adult sample.
+Adding complexity to the TANGO might increase individual differences in an adult sample.
 Researchers could consider adjusting the task difficulty, for example, by changing the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
 Another task extension could realize differential feedback dependent on the participant's accuracy.
-By inducing more between-person variance, reliability estimates could further increase.
+By inducing more between-person variance, reliability estimates could further increase and could get even more precise than they already are.
 
@@
 Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity. 
-Computational cognitive models are a promising approach forward.
+Theoretically informed, computational cognitive models are a promising approach forward [@haines2020theoretically].
 We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
@@
 
+The TANGO fulfills several demands that were proposed by @schaafsma2015deconstructing's wish list: it measures proficiency on a range, avoids floor and ceiling effects, induces variation across age ranges, shows satisfactory reliability estimates, and a high face value.
+
 In addition to the new task design itself, we designed a new testing infrastructure.
-Our gaze understanding task is presented as an interactive web app.
+The TANGO is presented as an interactive web app.
 This enables presentation across devices without any prior installation.
@@
 
-After having probed our new testing infrastructure and psychometric properties, the next step will be to ensure the validity of our gaze understanding task.
+After having probed our new testing infrastructure and psychometric properties, the next step will be to ensure the validity of the TANGO.
 Validity is often assessed by looking at concurrent relations between measures.
@@
 Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
-For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
-In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
-In addition, a subset of our remote child sample completed a receptive vocabulary task [@bohnorev].
-We will report the association between these family-level factors and children's language skills on their gaze understanding abilities in a separate paper (in preparation).
-In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings [@barr2020screen; @long2020detecting; @rogoff2018importance].
+For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities [e.g., @bulgarelli2016social].
+Future research should probe these relations.
 
@@
 We have presented a new experimental paradigm to study gaze understanding across the lifespan.
-Our gaze understanding task captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
 The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
@@
 The data sets and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
-A demo version of the task is available at the following website: <https://ccp-odc.eva.mpg.de/gafo-demo/>.
-The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: <https://github.com/ccp-eva/gafo-demo>.
+A demo version of the task is available at the following website (see Figure \@ref(fig:fig4)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
+The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
 These resources allow interested researchers to use, extend and adapt the task.
+
+(ref:figlab4) **TANGO demo website.** We want to highlight that researchers are welcome to use and modify our task according to their needs.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/tango_demo_screenshot.png")
+```
 
@@
 
-The web application (<https://ccp-odc.eva.mpg.de/gafo-demo/>) described here is open source (<https://github.com/ccp-eva/gafo-demo>).
+The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
 The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (<https://github.com/jprein/gazecues-methods>).

### 2022-08-25 paper/manuscript.tex
incorporate Manuels feedback;TANGO acronym

@@
 \hypersetup{
-  pdftitle={Measuring individual differences in the understanding of gaze cues across the lifespan},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
+  pdftitle={TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults},
+  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
@@
 
-\title{Measuring individual differences in the understanding of gaze cues across the lifespan}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
+\title{TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
 \date{}
 
-\shorttitle{gaze understanding}
+\shorttitle{assessing individual differences in gaze understanding}
 
@@
 \abstract{%
-To navigate the social world and interact with other agents, we use social cognition.
-Traditional measures of social cognition often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
-This is problematic because developmental theories emphasize the role of social interaction on the development of social cognition which varies substantially across individuals and contexts.
-To fully understand how social-cognitive abilities emerge and relate to each other, we need new tools that can reliably measure individual differences.
-Here, we present a new task to study individual differences in social cognition in children and adults.
-We concentrate on an essential ability that is involved in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
+``Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
+Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief(approx.
+5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
 Our interactive browser-based task works across devices and enables in-person and remote testing.
@@
 This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-All materials and code are freely accessible to interested researchers. The task can be found here: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+All materials and code are freely accessible to interested researchers. A version of the task is accessible online: \url{https://ccp-odc.eva.mpg.de/tango-demo/}.''
 }
@@
 
-Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish-list'' for new social-cognitive paradigms.
+Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish list'' for new social-cognitive paradigms.
 They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
@@
 We designed the task as an interactive browser-based web app.
+Previous research has successfully used online study implementations that compare well to in-person data collection (Bohn, Le, Peloquin, Köymen, \& Frank, 2021; Bohn, Tessler, Merrick, \& Frank, 2021; Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016).
 This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
@@
 
-The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}), and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
+The code is open-source (\url{https://github.com/ccp-eva/tango-demo}), and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/gafo_procedure}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_procedure}
 
@@
 
-Our first aim was to assess whether our gaze understanding task induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether the TANGO induces inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/gafo_arrangedplot}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_arrangedplot}
 
@@
 
-We found that our gaze understanding task induced systematic variation: split-half and test-retest reliability was medium to high.
+We found that the TANGO induced systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/gafo_splithalf}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_splithalf}
 
@@
 Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
-In sum, our gaze understanding task provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
-The web app (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) and its source code (\url{https://github.com/ccp-eva/gafo-demo}) are freely accessible.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
+The web app (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) and its source code (\url{https://github.com/ccp-eva/tango-demo}) are freely accessible.
 We want to highlight that researchers are welcome to use and modify our task according to their needs.
 
-One of the main contributions of the gaze understanding task is that it induces variation between participants.
+One of the main contributions of the TANGO is that it induces variation between participants.
 This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
@@
 Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
-Computational cognitive models are a promising approach forward.
+Theoretically informed, computational cognitive models are a promising approach forward (Haines et al., 2020).
 We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
@@
 
+The TANGO fulfills several demands that were proposed by Schaafsma et al.
+(2015)'s wish list: it measures proficiency on a range, avoids floor and ceiling effects, induces variation across age ranges, shows satisfactory reliability estimates, and a high face value.
+
 In addition to the new task design itself, we designed a new testing infrastructure.
-Our gaze understanding task is presented as an interactive web app.
+The TANGO is presented as an interactive web app.
 This enables presentation across devices without any prior installation.
@@
 Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
-For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities.
-In our sample, caregivers were asked to fill out a short questionnaire on children's daily surroundings (e.g., sibling composition; information on childcare).
-In addition, a subset of our remote child sample completed a receptive vocabulary task (Bohn, Prein, Delikaya, Haun, \& Gagarina, n.d.).
-We will report the association between these family-level factors and children's language skills on their gaze understanding abilities in a separate paper (in preparation).
-In order to match our fine-grained, parametric measure of gaze understanding, however, we hope that future technological advances will enable the continuous measures of children's real-life social surroundings (Barr et al., 2020; Long, Kachergis, Agrawal, \& Frank, 2020; Rogoff, Dahl, \& Callanan, 2018).
+For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities (e.g., Bulgarelli \& Molina, 2016).
+Future research should probe these relations.
 
@@
 The data sets and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
-A demo version of the task is available at the following website: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.
-The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: \url{https://github.com/ccp-eva/gafo-demo}.
+A demo version of the task is available at the following website (see Figure \ref{fig:fig4}): \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
+The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: \url{https://github.com/ccp-eva/tango-demo}.
 These resources allow interested researchers to use, extend and adapt the task.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_demo_screenshot}
+
+}
+
+\caption{\textbf{TANGO demo website.} We want to highlight that researchers are welcome to use and modify our task according to their needs.}\label{fig:fig4}
+\end{figure}
 
@@
 
-The web application (\url{https://ccp-odc.eva.mpg.de/gafo-demo/}) described here is open source (\url{https://github.com/ccp-eva/gafo-demo}).
+The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
 The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barr2020screen}{}}%
-Barr, R., Kirkorian, H., Radesky, J., Coyne, S., Nichols, D., Blanchfield, O., \ldots{} Fitzpatrick, caroline.
-(2020).
-Beyond {Screen Time}: {A Synergistic Approach} to a {More Comprehensive Assessment} of {Family Media Exposure During Early Childhood}.
-\emph{Frontiers in Psychology}, \emph{11}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-barrett2013early}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bohnorev}{}}%
-Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (n.d.). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2021children}{}}%
+Bohn, M., Le, K.
+N., Peloquin, B., Köymen, B., \& Frank, M.
+C.
+(2021).
+Children's interpretation of ambiguous pronouns based on prior discourse.
+\emph{Developmental Science}, \emph{24}(3), e13049.
+\url{https://doi.org/10.1111/desc.13049}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2021how}{}}%
+Bohn, M., Tessler, M.
+H., Merrick, M., \& Frank, M.
+C.
+(2021).
+How young children integrate information sources to infer the meaning of words.
+\emph{Nature Human Behaviour}, \emph{5}(8), 1046--1054.
+\url{https://doi.org/10.1038/s41562-021-01145-1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frank2016using}{}}%
+Frank, M.
+C., Sugarman, E., Horowitz, A.
+C., Lewis, M.
+L., \& Yurovsky, D.
+(2016).
+Using {Tablets} to {Collect Data From Young Children}.
+\emph{Journal of Cognition and Development}, \emph{17}(1), 1--17.
+\url{https://doi.org/10.1080/15248372.2015.1061528}
+
 \leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-haines2020theoretically}{}}%
+Haines, N., Kvam, P.
+D., Irving, L.
+H., Smith, C., Beauchaine, T.
+P., Pitt, M.
+A., \ldots{} Turner, B.
+M.
+(2020).
+\emph{Theoretically {Informed Generative Models Can Advance} the {Psychological} and {Brain Sciences}: {Lessons} from the {Reliability Paradox}}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/xr7y3}
+
 \leavevmode\vadjust pre{\hypertarget{ref-happe2017structure}{}}%
@@
 \url{https://doi.org/10.1037//0012-1649.34.3.525}
-
-\leavevmode\vadjust pre{\hypertarget{ref-long2020detecting}{}}%
-Long, B., Kachergis, G., Agrawal, K., \& Frank, M.
-C.
-(2020).
-\emph{Detecting social information in a dense dataset of infants' natural visual experience} {[}Preprint{]}.
-{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/z7tdg}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rogoff2018importance}{}}%
-Rogoff, B., Dahl, A., \& Callanan, M. (2018). The importance of understanding children's lived experience. \emph{Developmental Review}, \emph{50}, 5--15. \url{https://doi.org/10.1016/j.dr.2018.05.006}
-
 \leavevmode\vadjust pre{\hypertarget{ref-rouder2019psychometrics}{}}%

### 2022-08-25 stats/analysis.Rmd
incorporate Manuels feedback;TANGO acronym

@@
 hedge_variation_plot_GLMM
-saveRDS(hedge_variation_plot_GLMM, file = "../saves/gafo-hedge-variation-plot-GLMM.rds")
-# ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
+saveRDS(hedge_variation_plot_GLMM, file = "../saves/tango-hedge-variation-plot-GLMM.rds")
+# ggsave("../figures/tango_hedge_variation_GLMM.png", width = 7, height = 4)
 ```
@@
 ```{r GLMM_plot_box}
+# mAgeBox <- readRDS("../saves/mAgeBox.rds")
+
 nd_box <- mDataAgeBox %>% 
@@
 box_variation_plot_GLMM <- ggplot() +
+
+  # chance level
+  geom_segment(aes(x = 3.0, y = 0.2, xend = 6.2, yend = 0.2), lty = "dotted") + 
+  geom_segment(aes(x = 6.25, y = 0.125, xend = 6.75, yend = 0.125), lty = "dotted") +
 
@@
   geom_jitter(
-    data = variationHedgeInd %>% filter(sample == "adults"), 
+    data = variationBoxInd %>% filter(sample == "adults"), 
     aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
@@
 
-saveRDS(box_variation_plot_GLMM, file = "../saves/gafo-box-variation-plot-GLMM.rds")
-# ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
+saveRDS(box_variation_plot_GLMM, file = "../saves/tango-box-variation-plot-GLMM.rds")
+# ggsave("../figures/tango_box_variation_GLMM.png", width = 7, height = 4)
 ```
@@
 
-saveRDS(hedge_intCon_kids, file = "../saves/gafo-hedge-intCon-kids.rds")
-# ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
+saveRDS(hedge_intCon_kids, file = "../saves/tango-hedge-intCon-kids.rds")
+# ggsave("../figures/tango_hedge_intCon_kids.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(hedge_intCon_adults, file = "../saves/gafo-hedge-intCon-adults.rds")
-# ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
+saveRDS(hedge_intCon_adults, file = "../saves/tango-hedge-intCon-adults.rds")
+# ggsave("../figures/tango_hedge_intCon_adults.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(box_intCon_kids, file = "../saves/gafo-box-intCon-kids.rds")
-# ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
+saveRDS(box_intCon_kids, file = "../saves/tango-box-intCon-kids.rds")
+# ggsave("../figures/tango_box_intCon_kids.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(box_intCon_adults, file = "../saves/gafo-box-intCon-adults.rds")
-# ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
+saveRDS(box_intCon_adults, file = "../saves/tango-box-intCon-adults.rds")
+# ggsave("../figures/tango_box_intCon_adults.png", width = 6, height = 4)
 ```
@@
 splithalf_plot
-saveRDS(splithalf_plot, file = "../saves/gafo-splithalf-plot.rds")
-
-# ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
+saveRDS(splithalf_plot, file = "../saves/tango-splithalf-plot.rds")
+
+# ggsave("../figures/tango_splithalf.png", width = 8, height = 2.5, scale = 1.2)
 ```
@@
 ```{r save_splithalf_data}
-write.csv(splithalf_data, "../saves/gafo-splithalf.csv", quote = F, row.names = F)
-saveRDS(splithalf_data, file = "../saves/gafo-splithalf-table.rds")
+write.csv(splithalf_data, "../saves/tango-splithalf.csv", quote = F, row.names = F)
+saveRDS(splithalf_data, file = "../saves/tango-splithalf-table.rds")
 
@@
 
-saveRDS(hedge_retest_correlationcoefficients, file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
+saveRDS(hedge_retest_correlationcoefficients, file = "../saves/tango-hedge-retest-correlationcoefficients.rds")
 ```
@@
 
-saveRDS(hedge_retest_kids, file = "../saves/gafo-hedge-retest-kids.rds")
-# ggsave("../figures/gafo_hedge_retest_kids.png", width = 6, height = 4)
+saveRDS(hedge_retest_kids, file = "../saves/tango-hedge-retest-kids.rds")
+# ggsave("../figures/tango_hedge_retest_kids.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(hedge_retest_adults, file = "../saves/gafo-hedge-retest-adults.rds")
-# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+saveRDS(hedge_retest_adults, file = "../saves/tango-hedge-retest-adults.rds")
+# ggsave("../figures/tango_hedge_retest_adults.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(box_retest_kids, file = "../saves/gafo-box-retest-kids.rds")
-# ggsave("../figures/gafo_box_retest_kids.png", width = 6, height = 4)
+saveRDS(box_retest_kids, file = "../saves/tango-box-retest-kids.rds")
+# ggsave("../figures/tango_box_retest_kids.png", width = 6, height = 4)
 ```
@@
 
-saveRDS(box_retest_adults, file = "../saves/gafo-box-retest-adults.rds")
-# ggsave("../figures/gafo_hedge_retest_adults.png", width = 6, height = 4)
+saveRDS(box_retest_adults, file = "../saves/tango-box-retest-adults.rds")
+# ggsave("../figures/tango_hedge_retest_adults.png", width = 6, height = 4)
 ```
@@
 ```{r arrange_plots}
-gafo_arrangedplot <- ggarrange(
+# hedge_variation_plot_GLMM <- readRDS(file = "../saves/tango-hedge-variation-plot-GLMM.rds")
+# hedge_intCon_kids <- readRDS(file = "../saves/tango-hedge-intCon-kids.rds")
+# hedge_intCon_adults <- readRDS(file = "../saves/tango-hedge-intCon-adults.rds")
+# hedge_retest_kids <- readRDS(file = "../saves/tango-hedge-retest-kids.rds")
+# hedge_retest_adults <- readRDS(file = "../saves/tango-hedge-retest-adults.rds")
+# box_variation_plot_GLMM <- readRDS(file = "../saves/tango-box-variation-plot-GLMM.rds")
+# box_intCon_kids <- readRDS(file = "../saves/tango-box-intCon-kids.rds")
+# box_intCon_adults <- readRDS(file = "../saves/tango-box-intCon-adults.rds")
+# box_retest_kids <- readRDS(file = "../saves/tango-box-retest-kids.rds")
+# box_retest_adults <- readRDS(file = "../saves/tango-box-retest-adults.rds")
+
+tango_arrangedplot <- ggarrange(
 
@@
 
-gafo_arrangedplot
-saveRDS(gafo_arrangedplot, file = "../saves/gafo-arrangedplot.rds")
-# ggsave("../figures/gafo_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
-```
+tango_arrangedplot
+saveRDS(tango_arrangedplot, file = "../saves/tango-arrangedplot.rds")
+# ggsave("../figures/tango_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+```

### 2022-09-02 paper/manuscript.Rmd
incorporate Daniel's feedback; pre-registration deviations; participant exclusions

@@
 ---
-title             : "TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults"
+title             : "TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults"
 shorttitle        : "assessing individual differences in gaze understanding"
@@
   Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
-  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief(approx.
+  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
 5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
@@
 The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements.
-   Our task induces inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
+   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
 High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-  All materials and code are freely accessible to interested researchers. A version of the task is accessible online: https://ccp-odc.eva.mpg.de/tango-demo/.
+This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
 
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "6705"
+wordcount         : "6859"
 bibliography      : ["../../references.bib"]
@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 header-includes:
@@
 Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
-Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
+Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
 
@@
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
-Thus, this task seems well suited to track group-level developmental trends, yet it fails to capture individual differences [cf.
+Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf.
 "reliability paradox", @hedge2018reliability].
@@
 
-Thus, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
-To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].
+Thus, developmental psychology faces a dilemma: many research questions rely on measuring individuals' development, yet, there is a lack of tasks to measure these individual differences reliably.
+To capture the emergence of social-cognitive abilities and their relation to social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].
 
@@
 They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
-New tasks should induce variation across age groups, including older children and adults [@repacholi2003introduction].
+New tasks should capture variation across age groups, including older children and adults [@repacholi2003introduction].
 Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
@@
 
-The web app was programmed in `JavaScript`, `HTML5`, `CSS` and `PHP`.
+The web app was programmed in `JavaScript`, `HTML5`, `CSS,` and `PHP`.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
-This is needed for precisely calculating exact pupil and target locations and sizes.
+This is needed for precisely calculating the exact pupil and target locations and sizes.
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
@@
 The landing of the target is accompanied by a tapping sound.
-Once the target landed, the instructor's voice asks "Where is the balloon?".
-For confirming the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
+Once the target landed, the instructor's voice asked "Where is the balloon?".
+To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback, so that learning effects are reduced, and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 (i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens, or research labs.
+Data collection can take place anywhere: online, in kindergartens, or in research labs.
 (ii) The task is presented as a website that works across devices.
@@
 
-Our first aim was to assess whether the TANGO induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.
 
-Methods, sample size, and analysis were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
+The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations.
+The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.
+
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.
+2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+
 Participants were equally distributed across the two study versions.
-The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between May and October 2021.
+Data were collected between May and October 2021.
 
@@
 
+We pre-registered the replacement for participants that finished fewer than four test trials.
+This was not the case for any participant.
+One child stopped participation after 16 trials (i.e., 3 test trials missing) but was included in the sample due to the pre-registered replacement rule.
+Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).
+
 For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
@@
 If they had not participated in the study within two weeks, they received a reminder via email.
-Response rate to invitations after the reminder was \~50%.
+The response rate to invitations after the reminder was \~50%.
 
 The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
+Of these, three families participated twice.
+In these cases, we only kept the data sets from the first participation.
+
+Four additional participants were recruited but not included in the study because they were already part of the in-person kindergarten sample (n=3), or because of unknown age (n = 1).
+
 Children in our sample grow up in an industrialized, urban Central-European context.
@@
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
+`r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females) were included.
 For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
@@
 They were asked to enable the sound and seat their child centrally in front of their device.
-Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
+Before the study started, families were instructed on how to set up their webcam and enable the recording permissions.
 We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that children themselves generated the answers.
+Study participation was video recorded whenever possible in order to ensure that the children themselves generated the answers.
 Depending on the participant's device, the website automatically presented the hedge or box version of the study.
-For families that used a tablet with touchscreen, the hedge version was shown.
+For families that used a tablet with a touchscreen, the hedge version was shown.
 Here, children could directly click on the touchscreen to indicate where the target is.
-For families that used a computer without touchscreen, the website presented the box version of the task.
+For families that used a computer without a touchscreen, the website presented the box version of the task.
 We assumed that younger children in our sample would not be acquainted with using a computer mouse.
@@
 
-All test trials without voice-over description were included in our analyses.
+All test trials without voice-over descriptions were included in our analyses.
 We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
@@
 (ref:figlab2) **Measuring inter-individual variation**.
-(A) Developmental trajectory in continuous hedge version.
+(A) Developmental trajectory in the continuous hedge version.
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
@@
 (E) Test-retest reliability in hedge adult sample.
-(F) Developmental trajectory in discrete box version.
+(F) Developmental trajectory in the discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
-Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
+The dotted black line shows the level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
 (G) Internal consistency (odd-even split) in box child sample.
@@
 Small points show the mean performance for each subject averaged across trials.
-Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection.
-Color of data points denotes age group.
+The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection.
+the color of data points denotes age group.
 
@@
 We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
+In the hedge version, children's click imprecision decreased with age, while in the box version, the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
 Most participants in the box version performed above chance level.
@@
 
-Our task induced inter-individual variation in both children and adults.
+Our task measured inter-individual variation in both children and adults.
 We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
@@
 We assessed internal consistency (as split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (<https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
+Task procedure, data collection, and sample sizes were pre-registered (<https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
 Participants were equally distributed across the two study versions.
-The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
 Data was collected between July 2021 and June 2022.
+
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.
+2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
 
@@
 
-The adult sample consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).
+Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1).
+Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
+
+The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).
 
@@
 In the hedge version, each bin occurred once, making up ten of the test trials.
-For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc.).
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bins 1 & 2, bins 3 & 4, etc.).
 In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
-Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
+Adults in the hedge version received 30 test trials, each of the ten bins occurring exactly three times.
 Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
@@
 First, we focused on internal consistency by calculating split-half reliability coefficients.
-For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using *Pearson* coefficients.
+For each subject, trials were split into odd and even trials.
+Performance was aggregated and then correlated using *Pearson* coefficients.
 For this, we used the data of the first test day.
@@
 Second, we assessed test-retest reliability.
-We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
+We calculated performance scores (depending on the study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients.
 Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach [@rouder2019psychometrics].
-We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`).
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in `R: performance ~ age + (0 + reliday | subjID)`).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
@@
 
-We found that the TANGO induced systematic variation: split-half and test-retest reliability was medium to high.
+We found that the TANGO measured systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.
@@
 
+For both study versions, reliability estimates based on the GLMM approach were higher than the *Pearson* correlations.
+The GLMM-based estimates are less noisy due to the fact that the model uses all available information (e.g., participant age) and does not rely on data aggregation across trials.
+
 ## Discussion
@@
 For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
-This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
+This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.
 
@@
 
-We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
-This paper contributes to methodological advances in developmental psychology in the following ways.
-First, we could capture fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Individuals behaved consistently different from one another.
+We have presented a new experimental paradigm to study gaze understanding across the lifespan.
+This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+Individuals behaved consistently differently from one another.
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
-In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
-The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible.
-We want to highlight that researchers are welcome to use and modify our task according to their needs.
+Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to developmental research.
+The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible for use and modification.
 
-One of the main contributions of the TANGO is that it induces variation between participants.
-This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
-
-In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version: the box version employs a categorical measure (i.e., proportion of correct choices), while the hedge version uses a continuous outcome (i.e., imprecision as distance between target and click).
 Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum [@hughes2015individual; @beaudoin2020systematic].
-Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
+Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change, revealing relations between different aspects of cognition and children's real-life social surroundings, and for meaningful comparisons across human cultures and across animal species.
 Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building [@hedge2018reliability].
@@
 Both study versions exhibit high retest reliability, also when controlling for age.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
-When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
+Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
+When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
@@
 
-Adding complexity to the TANGO might increase individual differences in an adult sample.
-Researchers could consider adjusting the task difficulty, for example, by changing the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
-Another task extension could realize differential feedback dependent on the participant's accuracy.
-By inducing more between-person variance, reliability estimates could further increase and could get even more precise than they already are.
-
-As we could see in the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity. 
+In the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher the reliability estimates are.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the complexity of the experimental design.
 Theoretically informed, computational cognitive models are a promising approach forward [@haines2020theoretically].
-We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
+Computational models take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
 Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
@@
 
-The TANGO fulfills several demands that were proposed by @schaafsma2015deconstructing's wish list: it measures proficiency on a range, avoids floor and ceiling effects, induces variation across age ranges, shows satisfactory reliability estimates, and a high face value.
+The TANGO fulfills several demands that were proposed by @schaafsma2015deconstructing's wish list: it measures proficiency on a continuum, avoids floor and ceiling effects, measures variation across age ranges, shows satisfactory reliability estimates, and has a high face value.
 
@@
 Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
-Presented agents, voice-over instructions and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
+Presented agents, voice-over instructions, and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
 
-The web-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
-Test instructions are standardized and with prior informed consent the webcam records study participation.
+The browser-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
+Test instructions are standardized, and with prior informed consent, the webcam records study participation.
 This allows us to scale up data collection: testing is flexible, fast, and requires no further experimenter training.
-We compared children participating in-person, supervised in kindergartens with children who participated remotely at home.
+We compared children participating in-person and supervised in kindergartens with children who participated remotely at home.
 Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
@@
 Therefore, we recommend using a tablet for remote data collection.
-Children can click for themselves and caregivers have less chance to interfere.
+Children can click for themselves, and caregivers have less chance to interfere.
 The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.
@@
 
-Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries [@hughes2011individual; @schaafsma2015deconstructing].
-We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding to get a complete picture of children's social cognition.
-
 # Conclusion
@@
 The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
-The web-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
+The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
 Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
@@
 The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository, (<https://github.com/jprein/gazecues-methods>).
-All experiments were preregistered (<https://osf.io/zjhsc/>).
+The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository (<https://github.com/jprein/gazecues-methods>).
+All experiments were pre-registered (<https://osf.io/zjhsc/>).
 
@@
 This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers and adults who participated in the study.
+We thank all the children, caregivers, and adults who participated in the study.
 We thank Jana Jurkat for her help with data collection.

### 2022-09-02 paper/manuscript.tex
incorporate Daniel's feedback; pre-registration deviations; participant exclusions

@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: X}
+\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: 6859}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults},
+  pdftitle={TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults},
   pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
@@
 
-\title{TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}
+\title{TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}
 \author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
@@
 \abstract{%
-``Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
-Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief(approx.
+Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
+Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
 5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
@@
 The implemented spatial layout allows for discrete and continuous measures of participants' click imprecision and is easily adaptable to different study requirements.
-Our task induces inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
+Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
 High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
-All materials and code are freely accessible to interested researchers. A version of the task is accessible online: \url{https://ccp-odc.eva.mpg.de/tango-demo/}.''
+This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
 }
@@
 Another group of individual differences studies focuses on the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Carlson \& Moses, 2001; Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007; Milligan, Astington, \& Dack, 2007; Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
-Studies on social behavioral outcomes measured the interplay of social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), stereotypes and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).
+Studies on social behavioral outcomes measured the interplay of social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), stereotypes, and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).
 
@@
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (Repacholi, 2003).
-Thus, this task seems well suited to track group-level developmental trends, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
+Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
 As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
@@
 
-Thus, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
-To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
+Thus, developmental psychology faces a dilemma: many research questions rely on measuring individuals' development, yet, there is a lack of tasks to measure these individual differences reliably.
+To capture the emergence of social-cognitive abilities and their relation to social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
 
@@
 They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
-New tasks should induce variation across age groups, including older children and adults (Repacholi, 2003).
+New tasks should capture variation across age groups, including older children and adults (Repacholi, 2003).
 Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
@@
 
-The web app was programmed in \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS} and \texttt{PHP}.
+The web app was programmed in \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS,} and \texttt{PHP}.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 The landing of the target is accompanied by a tapping sound.
-Once the target landed, the instructor's voice asks ``Where is the balloon?''.
-For confirming the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
+Once the target landed, the instructor's voice asked ``Where is the balloon?''.
+To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
+Participants do not receive differential feedback, so that learning effects are reduced, and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 
-Our first aim was to assess whether the TANGO induces inter-individual variation in a child and adult sample.
+Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
 Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.
 
-Methods, sample size, and analysis were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
+Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
+The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations.
+The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.
+
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+
 Participants were equally distributed across the two study versions.
-The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between May and October 2021.
+Data were collected between May and October 2021.
 
@@
 If they had not participated in the study within two weeks, they received a reminder via email.
-Response rate to invitations after the reminder was \textasciitilde50\%.
+The response rate to invitations after the reminder was \textasciitilde50\%.
 
 The remote child sample included 147 children, including 45 3-year-olds (mean = 42.62 months, SD = 3.35, range = 36 - 47, 14 girls), 47 4-year-olds (mean = 52.64 months, SD = 3.40, range = 48 - 59, 25 girls), and 55 5-year-olds (mean = 65.11 months, SD = 3.77, range = 60 - 71, 27 girls).
+Of these, three families participated twice.
+In these cases, we only kept the data sets from the first participation.
+
+Four additional participants were recruited but not included in the study because they were already part of the in-person kindergarten sample (n=3), or because of unknown age (n = 1).
+
 Children in our sample grow up in an industrialized, urban Central-European context.
@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of 100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females).
+100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females) were included.
 For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
@@
 
-All test trials without voice-over description were included in our analyses.
+All test trials without voice-over descriptions were included in our analyses.
 We ran all analyses in R version 4.2.0 (2022-04-22) (R Core Team, 2022).
@@
 \caption{\textbf{Measuring inter-individual variation}.
-(A) Developmental trajectory in continuous hedge version.
+(A) Developmental trajectory in the continuous hedge version.
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
@@
 (E) Test-retest reliability in hedge adult sample.
-(F) Developmental trajectory in discrete box version.
+(F) Developmental trajectory in the discrete box version.
 Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
-Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
+The dotted black line shows the level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
 (G) Internal consistency (odd-even split) in box child sample.
@@
 Small points show the mean performance for each subject averaged across trials.
-Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection.
-Color of data points denotes age group.}\label{fig:fig2}
+The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection.
+the color of data points denotes age group.}\label{fig:fig2}
 \end{figure}
@@
 We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while in the box version the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
+In the hedge version, children's click imprecision decreased with age, while in the box version, the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
 Most participants in the box version performed above chance level.
@@
 We assessed internal consistency (as split-half reliability) and test-retest reliability.
-Data collection and analysis were pre-registered (\url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
+Task procedure, data collection, and sample sizes were pre-registered (\url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
 Participants were equally distributed across the two study versions.
-The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
 Data was collected between July 2021 and June 2022.
+
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
 
@@
 
-The adult sample consisted of 136 English-speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females).
+Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned \emph{Individual Differences} sample (n = 3), or children did not understand the task instructions (n = 1).
+Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
+
+The adult sample included 136 English speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females; see Supplements for further details).
 
@@
 In the hedge version, each bin occurred once, making up ten of the test trials.
-For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 \& 2, bin 3 \& 4, etc.).
+For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bins 1 \& 2, bins 3 \& 4, etc.).
 In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
-Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
+Adults in the hedge version received 30 test trials, each of the ten bins occurring exactly three times.
 Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
@@
 First, we focused on internal consistency by calculating split-half reliability coefficients.
-For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using \emph{Pearson} coefficients.
+For each subject, trials were split into odd and even trials.
+Performance was aggregated and then correlated using \emph{Pearson} coefficients.
 For this, we used the data of the first test day.
@@
 Second, we assessed test-retest reliability.
-We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
+We calculated performance scores (depending on the study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
 Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach (Rouder \& Haaf, 2019).
-We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ (0\ +\ reliday\ \textbar{}\ subjID)}).
+We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ (0\ +\ reliday\ \textbar{}\ subjID)}).
 For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
@@
 
-We found that the TANGO induced systematic variation: split-half and test-retest reliability was medium to high.
+We found that the TANGO measured systematic variation: split-half and test-retest reliability was medium to high.
 For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.
@@
 
+For both study versions, reliability estimates based on the GLMM approach were higher than the \emph{Pearson} correlations.
+The GLMM-based estimates are less noisy due to the fact that the model uses all available information (e.g., participant age) and does not rely on data aggregation across trials.
+
 \hypertarget{discussion-1}{%
@@
 For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
-This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.
+This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.
 
@@
 
-We have presented a new experimental paradigm to study individual differences in gaze understanding across the lifespan.
-This paper contributes to methodological advances in developmental psychology in the following ways.
-First, we could capture fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Individuals behaved consistently different from one another.
+We have presented a new experimental paradigm to study gaze understanding across the lifespan.
+This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
+Individuals behaved consistently differently from one another.
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Third, our new web-based testing infrastructure proved useful for standardized, portable data collection at scale, both remotely as well as in person.
-In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to individual differences research.
-The web app (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) and its source code (\url{https://github.com/ccp-eva/tango-demo}) are freely accessible.
-We want to highlight that researchers are welcome to use and modify our task according to their needs.
-
-One of the main contributions of the TANGO is that it induces variation between participants.
-This is primarily achieved through the implementation of short trials, resulting in over a dozen replicates per subject (15 test trials within 5-10 minutes testing time).
-
-In our task, participants are asked to locate a balloon by using the gaze cues of another agent.
-The outcome measure depends on the presented study version: the box version employs a categorical measure (i.e., proportion of correct choices), while the hedge version uses a continuous outcome (i.e., imprecision as distance between target and click).
+Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to developmental research.
+The web app (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) and its source code (\url{https://github.com/ccp-eva/tango-demo}) are freely accessible for use and modification.
+
 Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change and revealing relations between different aspects of cognition and children's real-life social surroundings.
+Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change, revealing relations between different aspects of cognition and children's real-life social surroundings, and for meaningful comparisons across human cultures and across animal species.
 Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building (Hedge et al., 2018).
@@
 Both study versions exhibit high retest reliability, also when controlling for age.
-Therefore, when a sufficient amount of trials is presented, the box version of the task can also yield reliable individual estimates (cf.
+Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf.
 Hughes et al.
 (2000); improved reliability through aggregation).
-When testing time is limited (and number of trials might be low), we recommend using the continuous study version for higher internal consistency.
+When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
 However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
@@
 
-Adding complexity to the TANGO might increase individual differences in an adult sample.
-Researchers could consider adjusting the task difficulty, for example, by changing the target speed or implementing a saccade version (i.e., where the agent only briefly looks at the target position and then back to the center).
-Another task extension could realize differential feedback dependent on the participant's accuracy.
-By inducing more between-person variance, reliability estimates could further increase and could get even more precise than they already are.
-
-As we could see in the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher our reliability estimates are.
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the experimental design in its complexity.
+In the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher the reliability estimates are.
+Therefore, we argue that future research should aim at implementing statistical analyses that mirror the complexity of the experimental design.
 Theoretically informed, computational cognitive models are a promising approach forward (Haines et al., 2020).
-We could take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
+Computational models take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
 Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
@@
 The TANGO fulfills several demands that were proposed by Schaafsma et al.
-(2015)'s wish list: it measures proficiency on a range, avoids floor and ceiling effects, induces variation across age ranges, shows satisfactory reliability estimates, and a high face value.
+(2015)'s wish list: it measures proficiency on a continuum, avoids floor and ceiling effects, measures variation across age ranges, shows satisfactory reliability estimates, and has a high face value.
 
@@
 Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
-Presented agents, voice-over instructions and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
-
-The web-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
-Test instructions are standardized and with prior informed consent the webcam records study participation.
+Presented agents, voice-over instructions, and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
+
+The browser-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
+Test instructions are standardized, and with prior informed consent, the webcam records study participation.
 This allows us to scale up data collection: testing is flexible, fast, and requires no further experimenter training.
-We compared children participating in-person, supervised in kindergartens with children who participated remotely at home.
+We compared children participating in-person and supervised in kindergartens with children who participated remotely at home.
 Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
@@
 
-Our future goal is to utilize the presented testing infrastructure for further studies on social-cognitive abilities.
-As has been pointed out, social cognition encompasses a whole range of abilities which could be best assessed by task batteries (Hughes et al., 2011; Schaafsma et al., 2015).
-We want to move from the most fundamental social-cognitive abilities to more complex processes like knowledge-ignorance or false belief understanding to get a complete picture of children's social cognition.
-
 \hypertarget{conclusion}{%
@@
 The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
-The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository, (\url{https://github.com/jprein/gazecues-methods}).
-All experiments were preregistered (\url{https://osf.io/zjhsc/}).
+The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository (\url{https://github.com/jprein/gazecues-methods}).
+All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
 

### 2022-09-02 supplements/supplements.Rmd
incorporate Daniel's feedback; pre-registration deviations; participant exclusions

@@
                     <center> Supplements for the manuscript </center>
-                    <center> "Measuring individual differences in the understanding of gaze cues across the lifespan" </center>
+                    <center> "TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults" </center>
 shorttitle        : "Supplements"
@@
 
-  - name          : "Daniel M. Haun"
+  - name          : "Daniel B. M. Haun"
     affiliation   : "1"

### 2022-09-07 paper/manuscript.Rmd
incorporate Luke's and Steven's feedback

@@
   Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
-5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
+5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
    Our interactive browser-based task works across devices and enables in-person and remote testing.
@@
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
-High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
+High internal consistency and test–retest reliability estimates underline that the captured variation is systematic.
+This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
 
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "6859"
+wordcount         : "6856"
 bibliography      : ["../../references.bib"]
@@
 Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya].
-These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome [for an overview, see @repacholi2003introduction].
+These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
 Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
@@
 Designing this task required a new testing infrastructure.
-We designed the task as an interactive browser-based web app.
+We designed the task as an interactive web application.
 Previous research has successfully used online study implementations that compare well to in-person data collection [@frank2016using; @bohn2021children; @bohn2021how].
@@
 
-The web app was programmed in `JavaScript`, `HTML5`, `CSS,` and `PHP`.
+The web app was developed using `JavaScript`, `HTML5`, `CSS,` and `PHP`.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
+The web app generates two file types: (1) a text file (.json) containing metadata, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
 These files can either be sent to a server or downloaded to the local device.
@@
 Trials differ in the amount of visual access that participants have to the final target position.
-Before the test trials start, participants complete four training trials during which they familiarize themselves with clicking the screen.
+Before the test trials start, participants complete four training trials during which they familiarize themselves with touching the screen.
 In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
@@
 (A) Infrastructure for online testing.
-(i) Subjects aged 3 -- 99+ can participate.
+(i) Subjects aged 3 to 99+ can participate.
 Data collection can take place anywhere: online, in kindergartens, or in research labs.
 (ii) The task is presented as a website that works across devices.
-(iii) The scripts for the website and the recorded data are stored on secure local servers.
+(iii) The scripts for the website and the recorded data are stored on secure in-house servers.
 (B) Hedge version (continuous) of the TANGO.
@@
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
+For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
 For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
@@
 
-Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were negative and reliably different from zero.
-In the box version, the estimate of age ($\beta$ =`r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode ($\beta$ = `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]) were positive and reliably different from zero.
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CrI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CrI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were negative and reliably different from zero.
+In the box version, the estimate of age ($\beta$ =`r fixef(mAgeBox)["age", "Estimate"]` (95% CrI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode ($\beta$ = `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CrI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]) were positive and reliably different from zero.
 Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.
@@
 For neither study version nor age group did we find any floor or ceiling effects.
-The presentation as a web-app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
+The presentation as a web app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
 Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
@@
 The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
-In the hedge version, the correlation between test days was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
-In the box version, the correlation between test days was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the hedge version, the correlation between test days was `r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CrI [`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestHedge)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
+In the box version, the correlation between test days was `r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Estimate"]` (95% CrI [`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q2.5"]`;`r posterior_summary(mRetestBox)["cor_subjID__relidayreliday1__relidayreliday2", "Q97.5"]`]).
 
@@
 A demo version of the task is available at the following website (see Figure \@ref(fig:fig4)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
-The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
+The code base and respective assets can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
 These resources allow interested researchers to use, extend and adapt the task.

### 2022-09-07 paper/manuscript.tex
incorporate Luke's and Steven's feedback

@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: 6859}
+\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: 6856}
 \usepackage{lineno}
@@
 Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
-5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
+5--10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
 Our interactive browser-based task works across devices and enables in-person and remote testing.
@@
 Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
-High internal consistency and test-retest reliability estimates underline that the captured variation is systematic.
-This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
+High internal consistency and test--retest reliability estimates underline that the captured variation is systematic.
+This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
 }
@@
 Numerous studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
-These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome (for an overview, see Repacholi, 2003).
+These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes (for an overview, see Repacholi, 2003).
 Studies on social-cognitive abilities and family influences include the effect of parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce et al., 2014), and family background as parental education, occupation, sibling interaction and childcare (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991).
@@
 Designing this task required a new testing infrastructure.
-We designed the task as an interactive browser-based web app.
+We designed the task as an interactive web application.
 Previous research has successfully used online study implementations that compare well to in-person data collection (Bohn, Le, Peloquin, Köymen, \& Frank, 2021; Bohn, Tessler, Merrick, \& Frank, 2021; Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016).
@@
 
-The web app was programmed in \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS,} and \texttt{PHP}.
+The web app was developed using \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS,} and \texttt{PHP}.
 For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
@@
 All test trials without voice-over descriptions were included in our analyses.
-We ran all analyses in R version 4.2.0 (2022-04-22) (R Core Team, 2022).
+We ran all analyses in R version 4.2.1 (2022-06-23) (R Core Team, 2022).
 Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
@@
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
+For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
 For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
@@
 
-Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CI {[}-0.50; -0.14{]}) were negative and reliably different from zero.
-In the box version, the estimate of age (\(\beta\) =0.63 (95\% CI {[}0.40; 0.87{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CI {[}0.68; 1.56{]}) were positive and reliably different from zero.
+Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CrI {[}-0.41; -0.24{]}) and data collection mode -0.32 (95\% CrI {[}-0.50; -0.14{]}) were negative and reliably different from zero.
+In the box version, the estimate of age (\(\beta\) =0.63 (95\% CrI {[}0.40; 0.87{]}) and the estimate of data collection mode (\(\beta\) = 1.12 (95\% CrI {[}0.68; 1.56{]}) were positive and reliably different from zero.
 Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.
@@
 The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
-In the hedge version, the correlation between test days was 0.90 (95\% CI {[}0.67;1.00{]}).
-In the box version, the correlation between test days was 0.91 (95\% CI {[}0.69;1.00{]}).
+In the hedge version, the correlation between test days was 0.90 (95\% CrI {[}0.67;1.00{]}).
+In the box version, the correlation between test days was 0.91 (95\% CrI {[}0.69;1.00{]}).
 
@@
 A demo version of the task is available at the following website (see Figure \ref{fig:fig4}): \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
-The implementation architecture (JavaScript and HTML code) and the materials can be accessed in the following repository: \url{https://github.com/ccp-eva/tango-demo}.
+The code base and respective assets can be accessed in the following repository: \url{https://github.com/ccp-eva/tango-demo}.
 These resources allow interested researchers to use, extend and adapt the task.

### 2022-09-08 supplements/supplements.Rmd
update supplements titel

@@
 ```{r sample}
-testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
   # determine order of factors

### 2022-09-08 supplements/supplements.tex
update supplements titel

@@
 \hypersetup{
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel M. Haun1},
+  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
@@
 
-``Measuring individual differences in the understanding of gaze cues across the lifespan''}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel M. Haun\textsuperscript{1}}
+``TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults''}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
 \date{}

### 2023-03-10 paper/manuscript.Rmd
prepare repo for revision

@@
 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
+Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
    Our interactive browser-based task works across devices and enables in-person and remote testing.
@@
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "6856"
+wordcount         : "8548"
 bibliography      : ["../../references.bib"]
@@
 draft             : no
-documentclass     : "apa6"
+documentclass     : "apa7"
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 header-includes:
@@
 Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya].
-These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
+The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities [e.g., @wellman2004scaling], and which factors drive the development of social cognition [e.g., @gola2012mental; @devine2018family].
+For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development [@okumura2017individual].
+In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
 Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
@@
 
-However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding].
+However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @poulin-dubois2023discontinuity; @sodian2023reply; @sodian2016understanding].
 This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
@@
 Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysis].
-Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf.
-@mayer2015weird].
+Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
 
 However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
-Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf.
-"reliability paradox", @hedge2018reliability].
+Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
 As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
@@
 Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
+For example, @sodian2016understanding neither found a correlation between two moral Theory of Mind False Belief and Intention tasks at 60 months, nor a relationship between these two factors and implicit False Belief understanding at 18 months.
+
+The "Sandbox task" is one of the few tasks that attempt to overcome these methodological challenges [@begeer2012continuous; @bernstein2011theory; @coburn2015new; @mahy2017testing; @sommerville2013measuring].
+This continuous FB task measures the degree to which the estimate of another's belief is biased by one's own knowledge.
+Recent work questions the interpretation of this measure [@samuel2018egocentric; @samuel2018unreliability]: it is unclear whether a smaller egocentric bias can be directly translated into a better mental state reasoning ability.
+Another evaluation criterion should, therefore, be whether a task captures meaningful variability in performance; that is, differences in test scores should correspond to differences in the social-cognitive ability in question.
 
@@
 The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
+In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+
 Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
-In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
+Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
+As such, the eyes have been regarded as a "window into the mind" [@shepherd2010following].
+Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions [@tomasello2007reliance; @bohn2018common].
+In addition, gaze and language development seem to be related [@brooks2005development].
+Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication [@macdonald2013eye; @hernik2019infant].
+While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
+One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
+However, many cognitive abilities continue to develop beyond early childhood [e.g., @gathercole2004structure for working memory; @raviv2018developmental for visual statistical learning].
+Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
+Consequently, we aimed to assess the differentiation of the ability to understand gaze.
+Our goal was not to establish the youngest age at which children understand gaze cues.
+Rather, we wanted to examine how that ability changes with age.
+To accurately measure developmental change, we were interested in capturing individual variability.
 
@@
 To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback, so that learning effects are reduced, and trials stay comparable across the sample.
+Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
 If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
@@
 
-We designed two study versions that differ in the target's final hiding place and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
+We designed two study versions that differ in the target's final hiding place and, consequently, in the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
 Both versions use the same first training trial and then differ in the consecutive training and test trials.
@@
 The agent's eyes track the movement of the target.
+Three exemplary target locations are shown to depict how indicative the agent's gaze cues are in determining the target's location.
+The transparent target is only shown for an illustrative purpose (not visible during the test).
 (C) Box version (discrete) of the TANGO.
@@
 Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
-The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations.
+The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
 The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.
@@
 
-```{r vali_sample}
-vali <- testtrials %>% 
+```{r inddiff_sample}
+inddiff <- testtrials %>% 
   filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
 
-vali_kids <- vali %>%
+inddiff_kids <- inddiff %>%
   filter(ageInYears < 6) %>% 
@@
 
-vali_adults <- vali %>%
+inddiff_adults <- inddiff %>%
   filter(ageInYears == 18) %>% 
@@
 In-person testing with children took place in kindergartens in Leipzig, Germany.
-The in-person child sample consisted of `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).
+The in-person child sample consisted of `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised"])` children, including `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` girls), `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` girls), and `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` girls).
 
@@
 This was not the case for any participant.
-One child stopped participation after 16 trials (i.e., 3 test trials missing) but was included in the sample due to the pre-registered replacement rule.
+One child stopped participation after 12 test trials but was included in the sample due to the pre-registered replacement rule.
 Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).
@@
 
-The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
+The remote child sample included `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised"])` children, including `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` girls), `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` girls), and `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` girls).
 Of these, three families participated twice.
@@
 
-Children in our sample grow up in an industrialized, urban Central-European context.
+Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
+They often live in nuclear two-generational families with few household members.
 Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+The median individual monthly net income in the year 2021 was \~ 1,600€ for the city of Leipzig.
 
 Adults were recruited via *Prolific* [@palan2018prolific].
-*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-`r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females) were included.
+*Prolific* is an online participant recruitment service with a predominantly European and US-American subject pool.
+`r inddiff_adults$nTotal` English-speakers with an average age of `r inddiff_adults$meanAge` years (SD = `r inddiff_adults$sdAge`, range = `r inddiff_adults$minAge` - `r inddiff_adults$maxAge`, `r inddiff_adults$nFemales` females) were included.
+Participants live in a variety of different countries: the UK, Italy, Spain, Poland, Netherlands, Canada, Australia, Ireland, South Africa, Norway, Portugal, France, Austria, Finland, Greece, Germany, the U.S., Mexico, Chile, Iceland, New Zealand, Czech Republic, Hungary, Latvia, and Switzerland.
+In this sample, most participants resided in the United Kingdom (n = 47), South Africa (n = 8), and Portugal (n = 6).
+Additional, detailed information can be found in the data set online.
 For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
@@
 All participants received 15 test trials.
-In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.
+In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes, while adults were presented with eight boxes as possible target locations.
 
@@
 To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
-Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
+The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`).[^1]
+
+[^1]: In the pre-registration (<https://osf.io/snju6>), we specified the following model structure: "All models will include a fixed effect of target centrality and age, a random intercept for ID and a random slope for trial number by ID.
+For both study versions, we will compare the above specified null models with a model including data source (live vs.
+online) as a fixed effect." Or, in R model formula: `R: performance ~ target_centrality + age + (1 | ID) + (1 + trial | ID)`.
+    In this paper, we added symmetricPosition (synonymous to target_centrality) as a random slope because we expected that this item effect could vary between participants.
+    To be better able to interpret trial number effects, we decided to include it as a fixed effect.
+    Data collection mode (formerly named "data source") proved as a meaningful predictor and was accordingly added to the model.
+
+Here, `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
 We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
@@
 The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection.
-the color of data points denotes age group.
+The color of data points denotes age group.
 
@@
 ```
+
+Children showed nearly perfect precision in the first training trial.
+As visual access to the target location decreased in the subsequent training trials, imprecision levels increased (see Supplements).
+Within test trials, children's imprecision levels did not vary as a function of trial number.
+We take this as evidence that (A) children were comfortable touching the screen, (B) children understood the task instructions insofar as they aimed at locating the target, and (C) our experimental design successfully manipulated task difficulty.
 
@@
 It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^1]
+In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^2]
 
-[^1]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-    We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(vali$subjID[vali$datacollection == "remote - unsupervised" & vali$ageInYears == 3 & vali$studyversion == "box" & vali$webcam == TRUE])`).
+[^2]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
+    We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(inddiff$subjID[inddiff$datacollection == "remote - unsupervised" & inddiff$ageInYears == 3 & inddiff$studyversion == "box" & inddiff$webcam == TRUE])`).
     We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 
+There was no effect of trial number (hedge version: $\beta$ = `r fixef(mAgeHedge)["trialNr", "Estimate"]`; 95% CrI [`r fixef(mAgeHedge)["trialNr", "Q2.5"]`; `r fixef(mAgeHedge)["trialNr", "Q97.5"]`]; box version: $\beta$ = `r fixef(mAgeBox)["trialNr", "Estimate"]`; 95% CrI [`r fixef(mAgeBox)["trialNr", "Q2.5"]`; `r fixef(mAgeBox)["trialNr", "Q97.5"]`).
+However, trials differed in difficulty depending on where the target landed (hedge version: $\beta$ = `r fixef(mAgeHedge)["symmetricPosition", "Estimate"]`; 95% CrI [`r fixef(mAgeHedge)["symmetricPosition", "Q2.5"]`; `r fixef(mAgeHedge)["symmetricPosition", "Q97.5"]`]; box version: $\beta$ = `r fixef(mAgeBox)["symmetricPosition", "Estimate"]`; 95% CrI [`r fixef(mAgeBox)["symmetricPosition", "Q2.5"]`; `r fixef(mAgeBox)["symmetricPosition", "Q97.5"]`).
+When the target landed closer to the center of the screen, participants were more accurate in locating it.
+
 ## Discussion
 
-Our task measured inter-individual variation in both children and adults.
-We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
+Our task measured inter-individual differences in both children and adults; that is, we found substantial variation in individuals across age groups.
+For example, some three-year-olds showed greater precision levels than some five-year-olds.
+This holds across both study versions.
+However, due to the continuous study design, the hedge version was able to capture more fine-grained differences in individual performance.
+We see substantial developmental gains: with increasing age, participants became on average more and more precise in locating the target.
 The five-year-olds reached a proficiency level close to the adults' level.
@@
 
-# Internal consistency and retest reliability
+# Internal consistency and test-retest reliability
 
@@
 
-Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1).
+Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1; manifested in too early clicking in the training trials while the instructions were still playing, and no clicking by themselves in the test trials).
 Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
@@
 The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).
+Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).
 
@@
 For the four training trials, we repeated a fixed order of random bins/boxes.
+For the adult sample, we decided to increase the number of trials in order to get more accurate reliability estimates.
+Trial numbers were multipliers of the possible target locations and therefore differed between hedge and box versions.
+For the child sample, we stuck to the same number of trials to not risk higher attrition rates.
 
@@
 We assessed reliability in two ways.
-First, we focused on internal consistency by calculating split-half reliability coefficients.
+First, we focused on internal consistency by calculating split-half reliability coefficients.[^3]
 For each subject, trials were split into odd and even trials.
@@
 Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
+
+[^3]: The assessment of internal consistency was not pre-registered and was included as an additional measure of reliability.
 
@@
 Similar to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
-In most cases, stratifying by target position lead to similar or even higher estimates compared to no stratification.
+In most cases, stratifying by target position led to similar or even higher estimates compared to no stratification.
 As expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
@@
 
-For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^2]
+For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^4]
+See Supplements for reliability estimates by age group.
 
-[^2]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
+[^4]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
     The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
@@
 
+# Validity
+
+```{r vali_sample}
+vali_sample <- readRDS("../saves/vali_sample.rds")
+```
+
+After having probed our new testing infrastructure and the psychometric properties of the TANGO task, we aimed at establishing its validity. 
+One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related. 
+Social cognition is often described as developing in response to social interaction [@devine2018family; @hughes2004links]. 
+It is assumed that opportunities to play, communicate and argue with peers help children to understand the human mind.
+Therefore, many studies link social cognition to opportunities for social interaction captured in demographic variables such as parent-child interaction quality and quantity, mental state talk, and center-based childcare [@bulgarelli2016social; @pavarini2013parental; @dunn1991young].
+In particular, family constellation, the number and age of siblings, and their interaction have been linked to social cognition [@zhang2021worse; @cassidy2005theory; @perner1994theory; @peterson2000kindred; @dunn1991young].
+
+To assess such external validity for the TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day.
+`r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
+We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers.
+Only the `predictor age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements).
+Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding.
+Albeit the effects were weak, they are consistent with the literature.
+
+In addition, children's sensitivity to gaze has been linked to language acquisition [@brooks2005development; @okumura2017individual; @delbianco2019developmental].
+Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
+For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [@bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO task.
+We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)B and C).
+Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic of measures of social cognition.
+
+(ref:figlab4) **Validity of the TANGO task.** (A) Influence of age of childcare entry on gaze understanding.
+The older the children were when entering childcare, the less likely they are to respond correctly.
+(B) Influence of social-environmental factors on gaze understanding.
+Adding each predictors respectively to the null model did not improve model fit.
+(C) Influence of gaze understanding on receptive vocabulary.
+(D) Influence of gaze understanding on receptive vocabulary by age.
+The regression line with 95% CI shows a smooth conditional mean based on a linear model, with a *Pearson*’s correlation coefficient *r*.
+Dots show the mean performance for each subject averaged across trials.
+The color of dots denotes age group.
+For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model.
+Black dots represent means, thicker black lines 80% CI and thinner black lines 95% CI.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/tango_vali_arrangedplot.png")
+```
+
 # General Discussion
@@
 This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Individuals behaved consistently differently from one another.
+Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
 Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
-In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to developmental research.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
 The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible for use and modification.
@@
 
-After having probed our new testing infrastructure and psychometric properties, the next step will be to ensure the validity of the TANGO.
-Validity is often assessed by looking at concurrent relations between measures.
-Studies on gaze following traditionally present children with a simultaneous, congruent movement of eyes and head orientation.
-In our study, however, children only observe a subtle eye movement.
-Therefore, our results are not directly comparable to traditional gaze following studies.
-Another promising way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
-For example, it has been postulated that social-cognitive abilities are predicted by family-level variables and children's language abilities [e.g., @bulgarelli2016social].
-Future research should probe these relations.
+With respect to validity, we found that performance in the TANGO task was related to relevant external variables and cognitive measures.
+Family-level variables, capturing a child’s opportunity for social interaction, systematically influenced gaze understanding.
+Even though the effects were small and confidence intervals were wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real-life variables.
+In addition, we assessed the influence of gaze understanding on receptive vocabulary. 
+We found a substantial relationship between the two variables, even when correcting for age. 
+Taken together, this speaks to the validity of our TANGO task.
+
+# Limitations
+
+First, we want to address the scope and interpretation of the TANGO task.
+We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
+This speaks to the face validity of the TANGO task and its focus on an inherently social stimulus.
+However, we do not want to claim that the TANGO task does not also recruit other, domain general processes.
+For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
+From that perspective, gaze understanding could be seen as a particular case of vector-following that is learned and used in social interactions.
+Future research could assess how much variation of the gaze understanding task is shared with a physical vector-following task.
+In addition, computational cognitive models might prove helpful in defining children's behavior on a process-level and disentangling parameters that influence task performance (e.g., spatial acuity).
+
+Second, the influence of testing modality requires further attention.
+Remote data collection loosens the standardization of the experimental procedure, as we cannot prevent caregivers from interfering.
+Steering the child's behavior becomes less possible when touchscreens are used, and the child can click on the screen directly.
+This is why we recommend using tablets for remote data collection.
+However, it should be noted that families' access to technological devices varies, both across socio-environmental as well as cultural settings.
+
+Finally, we utilized subtle gaze cues in order to increase difficulty and capture individual differences.
+However, in real-life settings, children could be more accustomed to a combination of head and eye orientation changes, and subtle gaze differences might be less common.
 
@@
 The data sets and the analysis code are freely available in the associated online repository (<https://github.com/ccp-eva/gazecues-methods>).
-A demo version of the task is available at the following website (see Figure \@ref(fig:fig4)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
+A demo version of the task is available at the following website (see Figure \@ref(fig:fig5)): <https://ccp-odc.eva.mpg.de/tango-demo/>.
 The code base and respective assets can be accessed in the following repository: <https://github.com/ccp-eva/tango-demo>.
@@
 
-(ref:figlab4) **TANGO demo website.** We want to highlight that researchers are welcome to use and modify our task according to their needs.
+(ref:figlab5) **TANGO demo website.** We want to highlight that researchers are welcome to use and modify our task according to their needs.
+The number of training and test trials and the number of boxes can be adjusted within the JavaScript code, while agents and targets can be exchanged within the HTML code.
 
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
 knitr::include_graphics("../figures/tango_demo_screenshot.png")

### 2023-03-10 stats/analysis.Rmd
prepare repo for revision

@@
     # the smaller the value, the more central the position
-    symmetricPosition = case_when(
-                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
-                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
-                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
-                                  targetPosition == "2" | targetPosition == "9" ~ 4,
-                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
+    symmetricPosition = ifelse(studyversion == "box", 
+                               # for box version
+                               case_when(
+                                  targetPosition == "box3" ~ 0, 
+                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
+                                  targetPosition == "box1" | targetPosition == "box5" ~ 2), 
+                               # for hedge version
+                               targetCentralityX
                        ),
@@
 ```{r vali_data}
-vali <- testtrials %>% 
+inddiff <- testtrials %>% 
   filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18)) %>% 
@@
 ```{r variation_hedge_preparateData}
-variationHedgeInd <- vali %>% 
+variationHedgeInd <- inddiff %>% 
   filter(studyversion == "hedge") %>% 
@@
 ```{r age_hedge_model}
-mDataAgeHedge <- vali %>% 
+mDataAgeHedge <- inddiff %>% 
   filter(studyversion == "hedge" & sample == "kids") %>% 
@@
     # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+    age = scale(ageInMonths), 
+    symmetricPosition = scale(symmetricPosition),
+    trialNr = trialNr - min(trialNr), 
   ) %>% 
-  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)
-
-mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
+  select(subjID, age, ageInMonths, datacollection, symmetricPosition, trialNr, clickDistInBalloons)
+
+mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID),
                     data = mDataAgeHedge,
@@
                     inits  = "random",
-                    cores  = 100)
+                    cores  = 4)
 
@@
 nd_hedge <- mDataAgeHedge %>% 
-  select(-c(clickDistInBalloons, symmetricPosition, targetPosition))
-
-# extract model predictions for mock data
-pred_hedge <- fitted(mAgeHedge, newdata = nd_hedge, re_formula = NA) %>% as_tibble() %>% bind_cols(mDataAgeHedge)
+  select(-c(clickDistInBalloons, trialNr)) %>% 
+  mutate(trialNr = 0, symmetricPosition = 0)
+
+pred_hedge <- fitted(mAgeHedge, newdata = nd_hedge, re_formula = NA) %>% as_tibble() %>% bind_cols(nd_hedge)
 
@@
   labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
   scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) + 
@@
 ```{r variation_box_prepareData}
-variationBoxInd <- vali %>% 
+variationBoxInd <- inddiff %>% 
   filter(studyversion == "box") %>% 
@@
 # define data
-mDataAgeBox <- vali %>% 
+mDataAgeBox <- inddiff %>% 
   filter(studyversion == "box" & sample == "kids") %>% 
@@
     # scaled (centered around mean, SD = 1, i.e., z-transformed)
-    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
+    age = scale(ageInMonths),
+    symmetricPosition = scale(symmetricPosition),
+    trialNr = trialNr - min(trialNr),
   ) %>% 
-  select(subjID, age, ageInMonths, datacollection, symmetricPosition, targetPosition, correctBox)
-
-mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
+  select(subjID, age, ageInMonths, datacollection, symmetricPosition, trialNr, correctBox)
+
+mAgeBox <- brm(correctBox ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID),
                     data = mDataAgeBox,
@@
 # mAgeBox <- readRDS("../saves/mAgeBox.rds")
-
 nd_box <- mDataAgeBox %>% 
-  select(-c(correctBox, symmetricPosition, targetPosition))
+  select(-c(correctBox, trialNr)) %>% 
+  mutate(trialNr = 0, symmetricPosition = 0)
 
@@
   labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
   scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
@@
   geom_point(aes(col = ageInYears), size = 0.7) + 
-  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), guide = "none") +
   geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
@@
   mutate(
-    sample = fct_rev(sample),
+    sample = factor(sample, levels = c("kids", "adults"), labels = c("children", "adults")),
   ) %>%
@@
 
-# ggsave("../figures/tango_splithalf.png", width = 8, height = 2.5, scale = 1.2)
+ggsave("../figures/tango_splithalf.png", width = 8, height = 2.5, scale = 1.2)
 ```
@@
 
-            # hedge: space between vari and reli
+            # hedge: space between inddiff and reli
             nrow = 1, widths = c(1, 0.06, 1),
@@
 
-            # box: space between vari and reli
+            # box: space between inddiff and reli
             nrow = 1, widths = c(1, 0.06, 1),
@@
 saveRDS(tango_arrangedplot, file = "../saves/tango-arrangedplot.rds")
-# ggsave("../figures/tango_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
-```
+ggsave("../figures/tango_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+```

### 2023-03-10 stats/supplements_triallevel.Rmd
prepare repo for revision

---
title: "TANGO training"
author: "Julia Prein"
date: "02/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggthemes)
library(ggrain)

options(scipen = 999)
theme_set(theme_classic())
```

```{r load_data}
alltrials <- readRDS(file = "../data/tango-alltrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    trialType = factor(trialType, levels = c("touch", "fam", "test"), labels = c("training 1", "training 2 & 3", "test")), 
    studytype = factor(studytype, levels = c("vali", "reli"), labels = c("individual variation sample", "reliability sample")),

    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = case_when(
                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
                                  targetPosition == "2" | targetPosition == "9" ~ 4,
                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
                       ),

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
  )
```

```{r trainingtrials}
alltrials %>% 
  filter(ageInYears < 6) %>% 
  ggplot(., aes(x = trialType, y = clickDistInBalloons, fill = trialType)) +
  geom_rain(cov = "clickDistInBalloons", 
            point.args.pos = rlang::list2(size = 0.5, position = position_jitter(width = 0.05, height = 0)),
            boxplot.args.pos = list(
              width = 0.1, position = position_nudge(x = 0.13)),
            violin.args.pos = list(
              side = "r",
              width = 1, position = position_nudge(x = 0.2))) +
  guides(fill = 'none', color = 'none') +
  scale_colour_gradient(high = "#220220", low = "#D3D3D3") + 
  scale_fill_manual(values=c("#c6d325", "#00b1ea", "#29485d")) + 
  facet_grid(studytype ~ studyversion) + 
  scale_x_discrete(expand = c(0, 0)) +
  labs(x = "Trial type", y = "Imprecision in target width")

ggsave("../figures/tango_supplements_trainingtrials.png", width = 9, height = 6, scale = 1.2, bg = "white")
```

```{r across_trials}
alltrials %>% 
  filter(trialType == "test" & ageInYears < 6) %>%
  ggplot(mapping = aes(x = trialNr, y = clickDistInBalloons)) +
  geom_point(aes(color = subjID, group = subjID), alpha = 0.2) +
  geom_line(aes(color = subjID, group = subjID), alpha = 0.2) +
  geom_smooth(method = "lm", linetype = "dashed", size = 1.5, color = "black", se = FALSE) +
  scale_x_continuous(breaks = seq(1, 19, 1)) + 
  scale_y_continuous(limits = c(0, 12), breaks = seq(0, 12, 2)) + 
  xlab("Trial Number") + 
  ylab("Imprecision in target widths") +
  theme_classic() +
  theme(legend.position = "none") + 
  facet_grid(studytype ~ studyversion)

ggsave("../figures/tango_supplements_acrosstrials.png", width = 8, height = 6, scale = 1, bg = "white")
```

### 2023-03-10 stats/supplements_validity.Rmd
prepare repo for revision

---
title: "TANGO Validity"
author: "Julia Prein"
date: "2023-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(ggpubr)
library(ggthemes)
library(brms) # modeling
library(tidyverse) # data handling etc.
library(tidybayes) # gather_draws

options(scipen = 999)
theme_set(theme_classic())
```

```{r load_data}
testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli")),

    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = ifelse(studyversion == "box", 
                               # for box version
                               case_when(
                                  targetPosition == "box3" ~ 0, 
                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
                                  targetPosition == "box1" | targetPosition == "box5" ~ 2), 
                               # for hedge version
                               targetCentralityX
                       ),

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
  )
```

```{r orev_data}
orev_data <- read.table("../data/tango-orev-data.csv", encoding="UTF-8", header = TRUE, sep = ",", quote = "\"", dec = ".") %>% 
  mutate_if(is.character, as.factor)
```

# SOCIAL ENVIRONMENTAL INFLUENCES

```{r socenv_prepareData}
mDataSocenv <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW) %>% 
  group_by(subjID) %>% 
  # so that all models run with same nr of subjects
  drop_na() %>%
  ungroup() %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    hhSibs = scale(siblingsNr, center = TRUE, scale = TRUE),
    sibsChildAged = scale(siblingsChildAged, center = TRUE, scale = TRUE),
    ccAge = scale(childcareAge, center = TRUE, scale = TRUE),
    ccHours = scale(childcareHours, center = TRUE, scale = TRUE),
    hhTotal = scale(householdTotal, center = TRUE, scale = TRUE),
    age = scale(ageInMonths, center = TRUE, scale = TRUE), 
    peerExposure = scale(childcareHours, center = TRUE, scale = TRUE) + scale(siblingsNr, center = TRUE, scale = TRUE),
    pe = scale(peerExposure, center = TRUE, scale = TRUE), 
  ) %>% 
  group_by(datacollection, studyversion, subjID, age, ageInMonths, ageInYears, ccAge, ccHours, hhTotal, hhSibs, sibsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, pe) %>% 
  summarise(
    cor_tango = sum(correctBox),
    n_tango = n()
  ) %>% 
  mutate_if(is.character, as.factor)
```

```{r socenv_sample}
testtrials %>%
  filter(ageInYears < 6) %>% 
  distinct(subjID, .keep_all = T) %>%
  pivot_longer(cols = c(childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW), names_to = "score", values_to = "value") %>%
  group_by(score) %>%
  summarise(na = sum(is.na(value)))

n_distinct(mDataSocenv$subjID)

socenv_sample <- mDataSocenv %>% 
  group_by(ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAge = sd(ageInMonths, na.rm = T) %>% round(2),
    minAge = min(ageInMonths, na.rm = T),
    maxAge = max(ageInMonths, na.rm = T),
  ) %>% 
  mutate(sample = "socenv")

socenv_sample
```

```{r socenv_nullmodel}
mSEnull <- brm(cor_tango | trials(n_tango) ~ age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))
```

```{r socenv_fullmodels}
mSEccAge <- brm(cor_tango | trials(n_tango) ~ ccAge + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEccHours <- brm(cor_tango | trials(n_tango) ~ ccHours + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEhhTotal <- brm(cor_tango | trials(n_tango) ~ hhTotal + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEhhSibs <- brm(cor_tango | trials(n_tango) ~ hhSibs + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEsibsChildAged <- brm(cor_tango | trials(n_tango) ~ sibsChildAged + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEsiblingsVarietyScoreP <- brm(cor_tango | trials(n_tango) ~ siblingsVarietyScoreP + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEsiblingsVarietyScoreW <- brm(cor_tango | trials(n_tango) ~ siblingsVarietyScoreW + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mSEPE <- brm(cor_tango | trials(n_tango) ~ pe + age + datacollection + studyversion,
                data = mDataSocenv,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))
```

```{r socenv_modelcomparisons}
mSEComparison <- loo_compare(mSEnull, mSEccAge, mSEccHours, mSEhhTotal, mSEhhSibs, mSEsibsChildAged, mSEsiblingsVarietyScoreP, mSEsiblingsVarietyScoreW, mSEPE, criterion = "waic")%>% 
  as_tibble(rownames = "model") %>%
  left_join(as_tibble(model_weights(mSEnull, mSEccAge, mSEccHours, mSEhhTotal, mSEhhSibs, mSEsibsChildAged, mSEsiblingsVarietyScoreP, mSEsiblingsVarietyScoreW, mSEPE, weights = "waic"), rownames = "model")) %>% 
  rename(modelweight = value)

mSEComparison

socenvModelorder <- mSEComparison %>% arrange(modelweight) %>% pull(model)
```

```{r socenv_savemodels}
write.csv(mSEnull, "../saves/mSEnull.csv", quote = F, row.names = F)
saveRDS(mSEnull, "../saves/mSEnull.rds")
write.csv(mSEccAge, "../saves/mSEccAge.csv", quote = F, row.names = F)
saveRDS(mSEccAge, "../saves/mSEccAge.rds")
write.csv(mSEccHours, "../saves/mSEccHours.csv", quote = F, row.names = F)
saveRDS(mSEccHours, "../saves/mSEccHours.rds")
write.csv(mSEhhTotal, "../saves/mSEhhTotal.csv", quote = F, row.names = F)
saveRDS(mSEhhTotal, "../saves/mSEhhTotal.rds")
write.csv(mSEhhSibs, "../saves/mSEhhSibs.csv", quote = F, row.names = F)
saveRDS(mSEhhSibs, "../saves/mSEhhSibs.rds")
write.csv(mSEsibsChildAged, "../saves/mSEsibsChildAged.csv", quote = F, row.names = F)
saveRDS(mSEsibsChildAged, "../saves/mSEsibsChildAged.rds")
write.csv(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.csv", quote = F, row.names = F)
saveRDS(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.rds")
write.csv(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.csv", quote = F, row.names = F)
saveRDS(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.rds")
write.csv(mSEPE, "../saves/mSEPE.csv", quote = F, row.names = F)
saveRDS(mSEPE, "../saves/mSEPE.rds")
```

```{r socenv_save}
socenv_results <- mSEComparison %>%
  select(model, waic, se_waic, modelweight, elpd_diff, se_diff) %>%
  rename(
    Predictor = model, 
    WAIC = waic, 
    SE_WAIC = se_waic,
    Weight = modelweight, 
    ELPD_DIFF = elpd_diff, 
    SE_ELPD_DIFF = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mSEPE" = "Peer exposure index", 
                   "mSEsiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
                   "mSEhhSibs" = "# Children in household aged 0-18", 
                   "mSEccHours" = "Average hours spent in childcare per day",
                   "mSEnull" = "Null model", 
                   "mSEhhTotal" = "# Household members",
                   "mSEccAge" = "Age of childcare entry", 
                   "mSEsiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
                   "mSEsibsChildAged" = "# Children in household aged 1-12",
                   )
  )
write.csv(socenv_results, "../saves/socenv_results.csv", quote = F, row.names = F)
saveRDS(socenv_results, "../saves/socenv_results.rds")
```

```{r socenv_posteriordraws}
socenv_draws <- bind_rows(
  mSEccAge %>% gather_draws(b_ccAge),
  mSEccHours %>% gather_draws(b_ccHours), 
  mSEhhTotal %>% gather_draws(b_hhTotal), 
  mSEhhSibs %>% gather_draws(b_hhSibs), 
  mSEsibsChildAged %>% gather_draws(b_sibsChildAged), 
  mSEsiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
  mSEsiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
  mSEPE %>% gather_draws(b_pe)
  ) %>% 
  mutate(
    predictor = factor(.variable, 
                       levels = c("b_hhSibs", 
                                  "b_siblingsVarietyScoreP", 
                                  "b_sibsChildAged", 
                                  "b_hhTotal", 
                                  "b_ccHours", 
                                  "b_ccAge", 
                                  "b_siblingsVarietyScoreW", 
                                  "b_pe"), 
                       labels = c("# Children in household aged 0-18", 
                                  "Sibling variety score (Peterson, 2000)", 
                                  "# Children in household aged 1-12", 
                                  "# Household members", 
                                  "Average hours spent in childcare per day", 
                                  "Age of childcare entry", 
                                  "Sibling variety score (Cassidy et al., 2005)", 
                                  "Peer exposure index")
                       )  
  ) %>% 
  rename(estimate = .value)

write.csv(socenv_draws, "../saves/socenv_draws.csv", quote = F, row.names = F)
saveRDS(socenv_draws, "../saves/socenv_draws.rds")
```

```{r socenv_plot_winning}
socenv_plot_winning <- socenv_draws %>% 
  filter(predictor == "Age of childcare entry") %>% 
  ggplot(., aes(y = predictor, x = estimate)) +
  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 0.8, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, ylim = c(1.5, 1.5)) +
  theme_classic()

socenv_plot_winning

saveRDS(socenv_plot_winning, file = "../saves/socenv_plot_winning.rds")
# ggsave("../figures/socenv_plot_winning.png", width = 10, height = 6, scale = 1, bg = "white")
```

```{r socenv_plot_allother}
socenv_plot_allother <- socenv_draws %>% 
  filter(predictor != "Age of childcare entry") %>% 
  ggplot(., aes(y = predictor, x = estimate)) +
  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_size = 0.5, slab_fill = "#EBECEC", slab_alpha = 0.9) +
  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, ylim = c(1.5, 7.5)) +
  theme_classic()

socenv_plot_allother

saveRDS(socenv_plot_allother, file = "../saves/socenv_plot_allother.rds")
# ggsave("../figures/socenv_plot_allother.png", width = 10, height = 6, scale = 1, bg = "white")
```

# RECEPTIVE VOCABULARY

```{r orev_sample}
orev_sample <- orev_data %>% 
  group_by(ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age_orev*12, na.rm = T) %>% round(2),
    sdAge = sd(age_orev*12, na.rm = T) %>% round(2),
    minAge = min(age_orev*12, na.rm = T) %>% round(),
    maxAge = max(age_orev*12, na.rm = T) %>% round(),
  ) %>% 
  mutate(sample = "orev")

time_diff <- orev_data %>% 
  summarise(
    meanTimeDiff = mean(time_diff, na.rm = T) %>% round(2),
    sdTimeDiff = sd(time_diff, na.rm = T) %>% round(2),
    minTimeDiff = min(time_diff, na.rm = T) %>% round(2),
    maxTimeDiff = max(time_diff, na.rm = T) %>% round(2),
  ) %>% 
  mutate(sample = "orev_tango")

vali_sample <- bind_rows(socenv_sample, orev_sample, time_diff)

vali_sample
saveRDS(vali_sample, file = "../saves/vali_sample.rds")
```

```{r orev_prepareData}
mDataOrev <- orev_data %>% 
  mutate(
    age_centered = scale(age_orev, scale = T, center = T), 
    mean_tango_centered = scale(mean_tango, scale = T, center = T),
  )

n_distinct(mDataOrev$subjID)
```

```{r orev_models}
mOrevNull <- brm(cor_orev | trials(n_orev) ~ 1,
                 data = mDataOrev,
                 family = binomial, 
                 warmup = 1000, 
                 iter   = 3000, 
                 chains = 4, 
                 inits  = "random",
                 cores  = 4
     ) %>%
  add_criterion(c("loo","waic"))

mOrevAge <- brm(cor_orev | trials(n_orev) ~ age_centered,
                data = mDataOrev,
                family = binomial, 
                warmup = 1000, 
                iter   = 3000, 
                chains = 4, 
                inits  = "random",
                cores  = 4
            ) %>% 
  add_criterion(c("loo","waic"))

mOrevFull <- brm(cor_orev | trials(n_orev) ~ age_centered + mean_tango_centered,
                 data = mDataOrev,
                 family = binomial, 
                 warmup = 1000, 
                 iter   = 3000, 
                 chains = 4, 
                 inits  = "random",
                 cores  = 4
              ) %>%
  add_criterion(c("loo","waic"))
```

```{r orev_modelcomparison}
mOrevComparison <- loo_compare(mOrevNull, mOrevAge, mOrevFull, criterion = "waic") %>% as_tibble(rownames = "model") %>%
  left_join(as_tibble(model_weights(mOrevNull, mOrevAge, mOrevFull, weights = "waic"), rownames = "model")) %>% 
  rename(modelweight = value)

mOrevComparison
```

```{r orev_save}
orev_results <- mOrevComparison %>%
  select(model, waic, se_waic, modelweight, elpd_diff, se_diff) %>%
  rename(
    Predictor = model, 
    WAIC = waic, 
    SE_WAIC = se_waic,
    Weight = modelweight, 
    ELPD_DIFF = elpd_diff, 
    SE_ELPD_DIFF = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mOrevFull" = "Age (scaled), TANGO score (scaled)", 
                   "mOrevAge" = "Age (scaled)", 
                   "mOrevNull" = "Null model", 
                   )
  )

write.csv(orev_results, "../saves/orev_results.csv", quote = F, row.names = F)
saveRDS(orev_results, "../saves/orev_results.rds")
```

```{r orev_posteriordraws}
orev_draws <- bind_rows(
  mOrevAge %>% gather_draws(b_age_centered) %>% mutate(model = "age model"), 
  mOrevFull %>% gather_draws(b_age_centered, b_mean_tango_centered) %>% mutate(model = "full model"), 
  ) %>% 
  mutate(
    .variable = factor(.variable, levels = c("b_age_centered", "b_mean_tango_centered"), labels = c("Age (scaled)", "TANGO score (scaled)")), 
  ) %>% 
  rename(estimate = .value, predictor = .variable)

write.csv(orev_draws, "../saves/orev_draws.csv", quote = F, row.names = F)
saveRDS(orev_draws, "../saves/orev_draws.rds")
```

```{r orev_modelplot}
orev_modelplot <- orev_draws %>% 
  ggplot(., aes(x = estimate, y = predictor)) +
 tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
    labs(x = "Posterior estimate when predicting oREV score", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  coord_cartesian(expand = TRUE, xlim = c(-0.1, 0.6), ylim = c(1.5, 2.5)) +
  theme_classic()

orev_modelplot

saveRDS(orev_modelplot, file = "../saves/orev_modelplot.rds")
# ggsave("../figures/tango_orev_model.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

```{r orev_plot}
orev_plot <- ggplot(mDataOrev, aes(x = mean_orev, y = mean_tango)) +

  geom_point(aes(col = as.factor(ageInYears)), shape = 18, size = 2) +
  geom_smooth(method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0.9, label.y = 0.975, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +

  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "6-year-olds", "7-year-olds")) +

  labs(x = "oREV score", y = "TANGO score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +

  theme(legend.title = element_text(size = 9), 
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.4, "cm"), 
        legend.direction = "vertical", 
        legend.box = "horizontal",
        legend.position = c(0.175, 0.25), 
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black")
        )

orev_plot

saveRDS(orev_plot, file = "../saves/orev_plot.rds")
# ggsave("../figures/tango_orev_plot.png", width = 7, height = 4)
```

# ARRANGE PLOT

```{r arrange_plots}
vali_arrangedplot <- ggarrange(
  ggarrange(
    socenv_plot_winning,
    socenv_plot_allother,
    ncol = 2,
    labels = c("A", "B")
  ),

  ggarrange(
    orev_modelplot, 
    orev_plot,
    ncol = 2,
    labels = c("C", "D")
  ), 
  nrow = 2
  )

vali_arrangedplot

saveRDS(vali_arrangedplot, file = "../saves/vali-arrangedplot.rds")
ggsave("../figures/tango_vali_arrangedplot.png", width = 8.5, height = 6, scale = 1.5, bg = "white")
```

### 2023-03-10 stats/supplements_webcamcoding.Rmd
prepare repo for revision

--- 2022-04-29 stats/supplements_webcamcoding.Rmd
@@
 ```{r load_data}
-webcam_data <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
+webcam_data <- readRDS(file = "../data/tango-testtrials.rds") %>% 
   filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & webcam == TRUE & ageInYears == 3) %>% 
@@
   mutate(
+    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
+    # the smaller the value, the more central the position
+    symmetricPosition = case_when(
+                                  targetPosition == "box3" ~ 0, 
+                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
+                                  targetPosition == "box1" | targetPosition == "box5" ~ 2),
     targetPosition = factor(targetPosition, levels = c("box1", "box2", "box3", "box4", "box5")), 
@@
   )
-```
-
-### VISUAL EXPLORATION
-
-```{r webcam_exploring}
-### nrRepeatedTestquestion
-webcam_data %>% 
-  group_by(subjID) %>% 
-  mutate(repeatedTestquestion = mean(nrRepeatedTestquestion, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = repeatedTestquestion, y = proportionCorrectBox)) + 
-  geom_point(col = "#006c66", size = 0.7) + 
-  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))
-
-### nrHintsEyes
-webcam_data %>% 
-  group_by(subjID) %>% 
-  mutate(hintsEyes = mean(nrHintsEyes, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = hintsEyes, y = proportionCorrectBox)) + 
-  geom_point(col = "#006c66", size = 0.7) + 
-  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))
-
-### nrVerificationChoice
-webcam_data %>% 
-  group_by(subjID) %>% 
-  mutate(verificationChoice = mean(nrVerificationChoice, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = verificationChoice, y = proportionCorrectBox)) + 
-  geom_point(col = "#006c66", size = 0.7) + 
-  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))
-
-### nrParentSpeech
-webcam_data %>% 
-  group_by(subjID) %>% 
-  mutate(parentSpeech = mean(nrParentSpeech, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = parentSpeech, y = proportionCorrectBox)) + 
-  geom_point(col = "#006c66", size = 0.7) + 
-  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(r.accuracy = 0.01, p.accuracy = 0.01) + 
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2))
 ```
@@
 
-    # centered around minimum
-    age = ageInMonths - min(ageInMonths),
-
-    # centered around mean
-    trial = scale(trialNr, center = TRUE, scale = FALSE), 
-    repeatedTestquestion = scale(nrRepeatedTestquestion, center = TRUE, scale = FALSE),
-    verificationChoice = scale(nrVerificationChoice, center = TRUE, scale = FALSE),
-    hintsEyes = scale(nrHintsEyes, center = TRUE, scale = FALSE),
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(ageInMonths, scale = TRUE, center = TRUE), 
+    trial = scale(trialNr, center = TRUE, scale = TRUE), 
+    repeatedTestquestion = scale(nrRepeatedTestquestion, center = TRUE, scale = TRUE),
+    verificationChoice = scale(nrVerificationChoice, center = TRUE, scale = TRUE),
+    hintsEyes = scale(nrHintsEyes, center = TRUE, scale = TRUE),
     nrParentSpeech = replace_na(nrParentSpeech, 0), 
-    parentSpeech = scale(nrParentSpeech, center = TRUE, scale = FALSE),
-
-    # calculating index
+    parentSpeech = scale(nrParentSpeech, center = TRUE, scale = TRUE),
     parentalInterference = -(repeatedTestquestion) + -(verificationChoice) + hintsEyes, 
-
-    # scaled (centered around mean, SD = 1, i.e., z-transformed)
     pi = scale(parentalInterference, scale = TRUE, center = TRUE), 
   ) %>% 
-  select(trial, subjID, correct, targetPosition, age, parentalInterference, pi, repeatedTestquestion, verificationChoice, hintsEyes, parentSpeech)
-
+  select(trial, subjID, correct, symmetricPosition, targetPosition, age, parentalInterference, pi, repeatedTestquestion, verificationChoice, hintsEyes, parentSpeech)
 ```
@@
 # originally: 
-# brm(correct ~ age + (symmetricPosition | subjID) + (1 | targetPosition)
-# age + person effect + trial effect
+# brm(correct ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)
 # simplified the model, since not a lot of data / info to estimate all the parameters.
-# therefore, remove trial & targetposition
 
-mPerTrialNull <- brm(correct ~ age + (1 | subjID) + (1 | targetPosition), 
+mPerTrialNull <- brm(correct ~ age + symmetricPosition + (1 + symmetricPosition | subjID), 
                               data   = mData, 
@@
                               inits  = "random",
-                              cores  = 4)
+                              cores  = 4) %>%
+  add_criterion(c("loo","waic"))
 
@@
                       newdata = mData,
-                      formula = correct ~ age + pi + (1 | subjID) + (1 | targetPosition), 
+                      formula = correct ~ pi + age + symmetricPosition + (1 + symmetricPosition | subjID),
                       family = bernoulli(link = "logit"),
@@
                       inits  = "random",
-                      cores  = 4)
+                      cores  = 4) %>%
+  add_criterion(c("loo","waic"))
 
@@
                       newdata = mData,
-                      formula = correct ~ age + repeatedTestquestion + (1 | subjID) + (1 | targetPosition), 
+                      formula = correct ~ repeatedTestquestion + age + symmetricPosition + (1 + symmetricPosition | subjID),
                       family = bernoulli(link = "logit"),
@@
                       newdata = mData,
-                      formula = correct ~ age + verificationChoice + (1 | subjID) + (1 | targetPosition), 
+                      formula = correct ~ verificationChoice + age + symmetricPosition + (1 + symmetricPosition | subjID),
                       family = bernoulli(link = "logit"),
@@
                       newdata = mData,
-                      formula = correct ~ age + hintsEyes + (1 | subjID) + (1 | targetPosition), 
+                      formula = correct ~ hintsEyes + age + symmetricPosition + (1 + symmetricPosition | subjID),
                       family = bernoulli(link = "logit"),
@@
                       newdata = mData,
-                      formula = correct ~ age + parentSpeech + (1 | subjID) + (1 | targetPosition), 
+                      formula = correct ~ parentSpeech + age + symmetricPosition + (1 + symmetricPosition | subjID),
                       family = bernoulli(link = "logit"),
@@
                       inits  = "random",
-                      cores  = 4)
+                      cores  = 4) %>%
+  add_criterion(c("loo","waic"))
 ```
@@
 ```{r webcam_perTrial_comparisons}
-mPerTrialNull <- add_criterion(mPerTrialNull, "waic")
-mPerTrialPI <- add_criterion(mPerTrialPI, "waic")
-mPerTrialRepeatedTestquestion <- add_criterion(mPerTrialRepeatedTestquestion, "waic")
-mPerTrialVerificationChoice <- add_criterion(mPerTrialVerificationChoice, "waic")
-mPerTrialHintsEyes <- add_criterion(mPerTrialHintsEyes, "waic")
-mPerTrialParentSpeech <- add_criterion(mPerTrialParentSpeech, "waic")
+mPerTrialComparison <- loo_compare(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic") %>% as_tibble(rownames = "model") %>%
+  left_join(as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, weights = "waic"), rownames = "model")) %>%
+  rename(modelweight = value)
 
-mPerTrialComparison <- loo_compare(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic")
-
-mPerTrialComparison <- as_tibble(mPerTrialComparison, rownames = "model")
-
-mPerTrialComparisonWeights <- as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic"), rownames = "model")
+mPerTrialComparison
 ```
@@
   mutate(
-    Predictor = factor(.variable, 
+    predictor = factor(.variable, 
                        levels = c("b_verificationChoice", 
@@
                 )  
-  )
+  ) %>% 
+  rename(estimate = .value)
 
@@
 perTrial_plot <- perTrial_draws %>% 
-  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
- tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
+  ggplot(., aes(x = estimate, y = predictor)) +
+  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
   labs(x = "Posterior estimate", y = "") +
-  guides(fill = "none")+
+  guides(fill = "none") +
   geom_vline(xintercept = 0, linetype = "dashed") +
-  scale_fill_manual(values = c("grey","#85AD00")) +
-  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 0.5)) +
-  theme_minimal()
+  coord_cartesian(expand = TRUE, ylim = c(1.5, 5.5)) +
+  theme_classic()
 
@@
 
-ggsave("../figures/supplements_webcamcoding_perTrial.png", width = 10, height = 6, scale = 0.7, bg = "white")
+saveRDS(perTrial_plot, file = "../saves/tango_supplements_webcamcoding_perTrial_plot.rds")
+# ggsave("../figures/tango_supplements_webcamcoding_perTrial.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```
@@
 ```{r webcam_perSubject_comparisons}
-mPerSubjectNull <- add_criterion(mPerSubjectNull, "waic")
-mPerSubjectPI <- add_criterion(mPerSubjectPI, "waic")
-mPerSubjectRepeatedTestquestion <- add_criterion(mPerSubjectRepeatedTestquestion, "waic")
-mPerSubjectVerificationChoice <- add_criterion(mPerSubjectVerificationChoice, "waic")
-mPerSubjectHintsEyes <- add_criterion(mPerSubjectHintsEyes, "waic")
-mPerSubjectParentSpeech <- add_criterion(mPerSubjectParentSpeech, "waic")
+mPerSubjectComparison <- loo_compare(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic") %>% as_tibble(rownames = "model") %>%
+  left_join(as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, weights = "waic"), rownames = "model")) %>%
+  rename(modelweight = value)
 
-mPerSubjectComparison <- loo_compare(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic")
-
-mPerSubjectComparison <- as_tibble(mPerSubjectComparison, rownames = "model")
-
-mPerSubjectComparisonWeights <- as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic"), rownames = "model")
+mPerSubjectComparison
 ```
@@
                 )
-  )
+  ) %>% 
+  rename(estimate = .value)
 
@@
 perSubject_plot <- perSubject_draws %>% 
-  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
- tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 1.75) +
+  ggplot(., aes(x = estimate, y = predictor)) +
+  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
   labs(x = "Posterior estimate", y = "") +
-  guides(fill = "none")+
+  guides(fill = "none") +
   geom_vline(xintercept = 0, linetype = "dashed") +
-  scale_fill_manual(values = c("grey","#85AD00")) +
-  scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.25)) +
-  theme_minimal()
+  coord_cartesian(expand = TRUE, ylim = c(1.5, 5.5)) +
+  theme_classic()
 
@@
 
-ggsave("../figures/supplements_webcamcoding_perSubject_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
+saveRDS(perSubject_plot, file = "../saves/tango_supplements_webcamcoding_perSubject_plot.rds")
+# ggsave("../figures/tango_supplements_webcamcoding_perSubject.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```
@@
 ```{r combined_plot}
-ggarrange(perTrial_draws %>% 
-            ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
-            tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
-            labs(x = "Posterior estimate", y = "") +
-            guides(fill = "none")+
-            geom_vline(xintercept = 0, linetype = "dashed") +
-            scale_fill_manual(values = c("grey","#85AD00")) +
-            scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 1)) +
-            theme_minimal() + 
-            theme(panel.grid.minor.x = element_blank()),
-
-          ggarrange(
-            perSubject_draws %>% 
-              ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
-              tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 2) +
-              labs(x = "", y = "") +
-              guides(y = "none", fill = "none") +
-              geom_vline(xintercept = 0, linetype = "dashed") +
-              scale_fill_manual(values = c("grey","#85AD00")) +
-              scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.5)) +
-              theme_minimal(), 
-            NULL, 
-            nrow = 2, heights = c(1, 0.0001)
-          ),
-
-          nrow = 1, widths = c(1, 0.75),
+ggarrange(perTrial_plot,
+          perSubject_plot,
+          nrow = 1,
           labels = c("A", "B")
@@
 
-ggsave("../figures/supplements_webcamcoding_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
+ggsave("../figures/tango_supplements_webcamcoding.png", width = 10, height = 5, scale = 1, bg = "white")
 ```
@@
 overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
-  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
-  select(model, waic, value, elpd_diff, se_diff) %>% 
+  select(model, waic, se_waic, modelweight, elpd_diff, se_diff) %>% 
   rename(
@@
     WAIC = waic, 
-    Weight = value, 
-    ELPD = elpd_diff, 
-    SE = se_diff,
+    SE_WAIC = se_waic,
+    Weight = modelweight, 
+    ELPD_DIFF = elpd_diff, 
+    SE_ELPD_DIFF = se_diff,
   ) %>% 

### 2023-03-10 supplements/supplements.Rmd
prepare repo for revision

@@
 ---
-title             : |
-                    <center> Supplements for the manuscript </center>
-                    <center> "TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults" </center>
+title             : "Supplements for the manuscript  'TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'"
 shorttitle        : "Supplements"
@@
     affiliation   : "1"
-
   - name          : "Daniel B. M. Haun"
@@
 floatsintext      : yes
+bibliography      : ["../../references.bib"]
 figurelist        : no
@@
 library("tidyverse")
+library("ggpubr")
+library("kableExtra")
 theme_set(theme_classic())
@@
 
-# Child sample
-## Webcam coding
-(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**.
+# Effects of trial type and trial number
+
+Children showed nearly perfect precision in the first training trial.
+As visual access to the target location decreased in the succeeding training trials, imprecision levels increased.
+Within test trials, children’s imprecision levels did not vary as a function of trial number.
+
+(ref:figlab1) **Imprecision by trial type, split by study version and sample**.
+The x axis represents the trial type.
+The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
+Small dots show the imprecision for each subject in each trial.
+Boxplots (boxes represent first to third quartiles of data; vertical lines indicate the median; horizontal black lines display the range) and a half violin plot show the data distribution.
+
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/tango_supplements_trainingtrials.png")
+```
+
+(ref:figlab2) **Imprecision across test trials, split by study version and sample**.
+The x axis represents trial number.
+The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
+The black dashed regression lines show smooth conditional means based on linear models.
+Small colored dots show the imprecision for each subject in each trial.
+Colored lines connect the trials of each individual.
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/tango_supplements_acrosstrials.png")
+```
+
+\newpage
+
+# Webcam coding of the child sample
+
+(ref:figlab3) **Model comparison for exploratory webcam coding of parental interference**.
 Factors of parental interference and their influence on the probability of responding correctly.
@@
 
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/supplements_webcamcoding_draws.png")
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/tango_supplements_webcamcoding.png")
 ```
@@
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + (1 | subjID) + (1 | targetPosition)`.[^3]
-
-[^3]: Attentive readers might notice that we simplified the structure of random effects.
-    Compared to our models in the *Individual differences* section, this model does not include the random slope for symmetric target position within participants.
-    We decided to do so since we had limited amount of data from few participants.
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in `R: correct ~ age + symmetricPosition + (1 + symmetricPosition | subjID)`.
 
@@
 In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
+Similarly, 95% CI of the model estimates included zero and were rather wide.
 Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
 
-```{r webcam_table, results = "asis"}
+```{r webcam_table}
 webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
-  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
+  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
   mutate_if(is.numeric, round, 2)
 
-papaja::apa_table(
-  webcam_models,
-  caption = "Model comparison for exploratory webcam coding of parental interference",
-  note = "All models included random intercepts for participant and target position.",
-  escape = T
+knitr::kable(webcam_models, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+```{r reli_agegroup, include=FALSE}
+hedge_intCon_agegroup <- readRDS("../saves/tango-hedge-intCon-kids.rds") + 
+  geom_point(aes(col = ageInYears), size = 1) + 
+  facet_wrap(~ ageInYears)
+
+hedge_retest_agegroup <- readRDS("../saves/tango-hedge-retest-kids.rds") + 
+  geom_point(aes(col = ageInYears), size = 1) + 
+  facet_wrap(~ ageInYears)
+
+box_intCon_agegroup <- readRDS("../saves/tango-box-intCon-kids.rds") + 
+  geom_point(aes(col = ageInYears), size = 1) + 
+  facet_wrap(~ ageInYears)
+
+box_retest_agegroup <- readRDS("../saves/tango-box-retest-kids.rds") + 
+  geom_point(aes(col = ageInYears), size = 1) + 
+  facet_wrap(~ ageInYears)
+
+ggarrange(hedge_intCon_agegroup, 
+          hedge_retest_agegroup,
+          box_intCon_agegroup, 
+          box_retest_agegroup, 
+          ncol = 2,
+          nrow = 2, 
+          labels = c("A", "B", "C", "D")
 )
+
+ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 9, height = 6)
 ```
@@
 
-# Adult sample
+# Reliability by age group
+
+(ref:figlab4) **Reliability split by age group**.
+(A) Internal consistency (odd-even split) in hedge child sample by age group.
+(B) Test-retest reliability in hedge child sample by age group.
+(C) Internal consistency (odd-even split) in box child sample by age group.
+(D) Test-retest reliability in box child sample by age group.
+For the hedge version, performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+For the box version, performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
+Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
+Dots show the performance for each subject.
+The color of data points denotes age group.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/tango_supplements_reli_byagegroup.png")
+```
+
+\newpage
+
+# Validity
+
+## Social-environmental factors
+
+```{r vali_sample}
+vali_sample <- readRDS("../saves/vali_sample.rds")
+```
+
+### Participants
+We included all children where families filled out a short demographic questionnaire.
+This subsample consisted of `r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` children, including `r vali_sample$nTotal[vali_sample$sample == "socenv" & vali_sample$ageInYears == "3"]` 3-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "3"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "3"]`, range = `r vali_sample$minAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "3"]` - `r vali_sample$maxAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "3"]`),
+`r vali_sample$nTotal[vali_sample$sample == "socenv" & vali_sample$ageInYears == "4"]` 4-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "4"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "4"]`, range = `r vali_sample$minAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "4"]` - `r vali_sample$maxAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "4"]`), and
+`r vali_sample$nTotal[vali_sample$sample == "socenv" & vali_sample$ageInYears == "5"]` 5-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "5"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "5"]`, range = `r vali_sample$minAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "5"]` - `r vali_sample$maxAge[vali_sample$sample == "socenv" & vali_sample$ageInYears == "5"]`).
+
+### Analysis
+To estimate social environmental influences on gaze understanding, we fitted GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (scaled), data collection mode (reference category: remote unsupervised) and study version (reference category: box version): `cor_tango | trials(n_tango) ~ age + datacollection + studyversion`).
+In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+For the target position, we categorized two adjacent bins as one imaginary box.
+To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
+Across the two study versions, we could consequently model the number of participant's correct responses using a `Binomial` distribution.
+For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
+In addition, we calculated three index scores.
+First, we calculated a sibling variety score according to @peterson2000kindred.
+Second, we implemented the modified version of @cassidy2005theory.
+Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare.
+We compared the models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2020statistical].
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+
+### Results 
+```{r socenv_results, results = "asis"}
+socenv_results <- readRDS("../saves/socenv_results.rds") %>% 
+  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
+  mutate_if(is.numeric, round, 2)
+
+knitr::kable(socenv_results, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
+The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero.
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
+
+## Receptive vocabulary
+
+### Participants
+
+Our sample consisted of `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, including `r vali_sample$nTotal[vali_sample$sample == "orev" & vali_sample$ageInYears == "3"]` 3-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "3"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "3"]`, range = `r vali_sample$minAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "3"]` - `r vali_sample$maxAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "3"]`,
+`r vali_sample$nTotal[vali_sample$sample == "orev" & vali_sample$ageInYears == "4"]` 4-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "4"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "4"]`, range = `r vali_sample$minAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "4"]` - `r vali_sample$maxAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "4"]`),
+`r vali_sample$nTotal[vali_sample$sample == "orev" & vali_sample$ageInYears == "5"]` 5-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "5"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "5"]`, range = `r vali_sample$minAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "5"]` - `r vali_sample$maxAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "5"]`),
+`r vali_sample$nTotal[vali_sample$sample == "orev" & vali_sample$ageInYears == "6"]` 6-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "6"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "6"]`, range = `r vali_sample$minAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "6"]` - `r vali_sample$maxAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "6"]`), and `r vali_sample$nTotal[vali_sample$sample == "orev" & vali_sample$ageInYears == "7"]` 7-year-olds (mean = `r vali_sample$meanAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "7"]` months, SD = `r vali_sample$sdAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "7"]`, range = `r vali_sample$minAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "7"]` - `r vali_sample$maxAge[vali_sample$sample == "orev" & vali_sample$ageInYears == "7"]`).
+
+### Materials
+
+We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children [@bohn2022orev].
+Similarly to the TANGO, the task was presented as an interactive web application (see Figure \@ref(fig:fig5); live demo https://ccp-odc.eva.mpg.de/orev-demo/; source code https://github.com/ccp-eva/orev-demo).
+
+Each trial presented four pictures: one target word alongside three distractors (1 phonological, 1 semantic, 1 unrelated distractor).
+A verbal prompt asked children to select one of the pictures (prompt: "Zeige mir [target word]"; engl.: "Show me [target word]").
+The positioning of the target word and the three distractor types was counterbalanced across the four display positions (upper/lower and left/right corners).
+Children responded by clicking on one of the four pictures.
+The outcome measure consisted of the proportion of correct responses.
+
+(ref:figlab5) Setup of the oREV. On each trial, participants heard a word and were asked to select the corresponding picture. Verbal prompts could be replayed by pressing the loudspeaker button.
+
+```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
+knitr::include_graphics("../figures/orev_procedure.png")
+```
+
+### Procedure
+
+Families received a personalized study link and completed the study at any location or time they wanted.
+Caregivers were asked to only provide technical support but no further help.
+Webcam recordings were done whenever consented and technically possible.
+We analyzed data of 20 trials per child.
+Children received the trials in two different orders.
+Performance across the two study orders did not differ.
+Hence, we decided to combine the data.
+
+### Analysis
+To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: `cor_clt | trials(n_clt) ~ age_centered + mean_gaze_centered`).
+We modelled the number of participant's correct responses using a `Binomial` distribution.
+
+### Results
+
+```{r orev_results, results = "asis"}
+orev_results <- readRDS("../saves/socenv_results.rds") %>% 
+  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
+  mutate_if(is.numeric, round, 2)
+
+knitr::kable(orev_results, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+\newpage
+
+# Additional information for the adult sample
+
+```{r adult_sample_country, include=FALSE}
+levels(testtrials$`Current Country of Residence`)
+```
+
+```{r adult_sample_countryn, echo=FALSE}
+adult_sample_countryn <- testtrials %>% 
+  group_by(subjID) %>% 
+  slice(1) %>% 
+  group_by(`Current Country of Residence`, studytype) %>%
+  summarise(n = n()) %>%
+  arrange(studytype, -n) %>% 
+  filter(!is.na(`Current Country of Residence`) & !is.na(studytype))
+
+kable(adult_sample_countryn, "latex", booktabs = TRUE, longtable = TRUE) %>%
+  kable_styling(latex_options = c("hold_position", "repeat_header"))
+```
+
 ## Recruitment
@@
 ## Study 3 - Reliability hedge version
-In stuyy 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
+In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
 The pre-registration can be found here: <https://osf.io/nu62m>.
@@
 
-In addition to the beforementioned prescreening settings, we used a whitelist.
+In addition to the aforementioned prescreening settings, we used a whitelist.
 *Prolific* has a so-called *custom allowlist prescreening filter* where one can enter the *Prolific* IDs of participants who completed a previous study.
@@
 | **sound for target click**   | \-                                                                                                                                                                                                                                               | \-                                                                                                                                                                                                                                                    | positive-feedback.mp3 |
+
+\newpage
+
+# References
+
+```{=tex}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
+```{=tex}
+\endgroup
+```

### 2023-03-10 supplements/supplements.tex
prepare repo for revision

@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \ifLuaTeX
@@
 \hypersetup{
+  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
   pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
@@
 
-\title{Supplements for the manuscript
-
-``TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults''}
+\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
 \author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
@@
 
-\hypertarget{child-sample}{%
-\section{Child sample}\label{child-sample}}
+\hypertarget{effects-of-trial-type-and-trial-number}{%
+\section{Effects of trial type and trial number}\label{effects-of-trial-type-and-trial-number}}
 
-\hypertarget{webcam-coding}{%
-\subsection{Webcam coding}\label{webcam-coding}}
+Children showed nearly perfect precision in the first training trial.
+As visual access to the target location decreased in the succeeding training trials, imprecision levels increased.
+Within test trials, children's imprecision levels did not vary as a function of trial number.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_webcamcoding_draws}
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_trainingtrials}
+
+}
+
+\caption{\textbf{Imprecision by trial type, split by study version and sample}.
+The x axis represents the trial type.
+The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
+Small dots show the imprecision for each subject in each trial.
+Boxplots (boxes represent first to third quartiles of data; vertical lines indicate the median; horizontal black lines display the range) and a half violin plot show the data distribution.}\label{fig:fig1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_acrosstrials}
+
+}
+
+\caption{\textbf{Imprecision across test trials, split by study version and sample}.
+The x axis represents trial number.
+The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
+The black dashed regression lines show smooth conditional means based on linear models.
+Small colored dots show the imprecision for each subject in each trial.
+Colored lines connect the trials of each individual.}\label{fig:fig2}
+\end{figure}
+
+\newpage
+
+\hypertarget{webcam-coding-of-the-child-sample}{%
+\section{Webcam coding of the child sample}\label{webcam-coding-of-the-child-sample}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_webcamcoding}
 
@@
 (A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig4}
+(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig3}
 \end{figure}
@@
 We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ (1\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}.\footnote{Attentive readers might notice that we simplified the structure of random effects.
-  Compared to our models in the \emph{Individual differences} section, this model does not include the random slope for symmetric target position within participants.
-  We decided to do so since we had limited amount of data from few participants.}
+Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.
 
@@
 In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}).
+Similarly, 95\% CI of the model estimates included zero and were rather wide.
 Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}
-
-\begin{tabular}{lllll}
+\begin{table}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrrr}
 \toprule
-Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
+Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
 \midrule
-By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
-By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
-By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
-By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
-By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
-By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
-By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
-By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
-By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
-By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
-By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
-By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
+By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
+By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
+By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
+By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
+By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
+\addlinespace
+By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
+By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
+By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
+By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
+By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
+\addlinespace
+By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
+By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
 \bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
+\end{tabular}}
 \end{table}
@@
 
-\hypertarget{adult-sample}{%
-\section{Adult sample}\label{adult-sample}}
+\hypertarget{reliability-by-age-group}{%
+\section{Reliability by age group}\label{reliability-by-age-group}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_reli_byagegroup}
+
+}
+
+\caption{\textbf{Reliability split by age group}.
+(A) Internal consistency (odd-even split) in hedge child sample by age group.
+(B) Test-retest reliability in hedge child sample by age group.
+(C) Internal consistency (odd-even split) in box child sample by age group.
+(D) Test-retest reliability in box child sample by age group.
+For the hedge version, performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+For the box version, performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
+Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
+Dots show the performance for each subject.
+The color of data points denotes age group.}\label{fig:fig4}
+\end{figure}
+
+\newpage
+
+\hypertarget{validity}{%
+\section{Validity}\label{validity}}
+
+\hypertarget{social-environmental-factors}{%
+\subsection{Social-environmental factors}\label{social-environmental-factors}}
+
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
+
+We included all children where families filled out a short demographic questionnaire.
+This subsample consisted of 109 children, including 30 3-year-olds (mean = 41.80 months, SD = 3.44, range = 36 - 47),
+36 4-year-olds (mean = 54.19 months, SD = 3.08, range = 48 - 59), and
+43 5-year-olds (mean = 66.28 months, SD = 3.62, range = 60 - 71).
+
+\hypertarget{analysis}{%
+\subsubsection{Analysis}\label{analysis}}
+
+To estimate social environmental influences on gaze understanding, we fitted GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (scaled), data collection mode (reference category: remote unsupervised) and study version (reference category: box version): \texttt{cor\_tango\ \textbar{}\ trials(n\_tango)\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion}).
+In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+For the target position, we categorized two adjacent bins as one imaginary box.
+To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
+Across the two study versions, we could consequently model the number of participant's correct responses using a \texttt{Binomial} distribution.
+For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
+In addition, we calculated three index scores.
+First, we calculated a sibling variety score according to Peterson (2000).
+Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005).
+Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare.
+We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
+As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
+WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
+
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
+
+\begin{table}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrrr}
+\toprule
+Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
+\midrule
+Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
+Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
+Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
+\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
+Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
+\addlinespace
+Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
+\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
+\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
+Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
+The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
+Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
+The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
+The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
+
+\hypertarget{receptive-vocabulary}{%
+\subsection{Receptive vocabulary}\label{receptive-vocabulary}}
+
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
+
+Our sample consisted of 117 children, including 11 3-year-olds (mean = 45.05 months, SD = 1.58, range = 43 - 47,
+26 4-year-olds (mean = 53.17 months, SD = 3.01, range = 48 - 57),
+32 5-year-olds (mean = 65.80 months, SD = 3.23, range = 61 - 71),\\
+36 6-year-olds (mean = 78.36 months, SD = 3.26, range = 72 - 84), and 12 7-year-olds (mean = 88.11 months, SD = 1.96, range = 84 - 91).
+
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
+
+We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022).
+Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).
+
+Each trial presented four pictures: one target word alongside three distractors (1 phonological, 1 semantic, 1 unrelated distractor).
+A verbal prompt asked children to select one of the pictures (prompt: ``Zeige mir {[}target word{]}''; engl.: ``Show me {[}target word{]}'').
+The positioning of the target word and the three distractor types was counterbalanced across the four display positions (upper/lower and left/right corners).
+Children responded by clicking on one of the four pictures.
+The outcome measure consisted of the proportion of correct responses.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/orev_procedure}
+
+}
+
+\caption{Setup of the oREV.
+On each trial, participants heard a word and were asked to select the corresponding picture.
+Verbal prompts could be replayed by pressing the loudspeaker button.}\label{fig:fig5}
+\end{figure}
+
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
+
+Families received a personalized study link and completed the study at any location or time they wanted.
+Caregivers were asked to only provide technical support but no further help.
+Webcam recordings were done whenever consented and technically possible.
+We analyzed data of 20 trials per child.
+Children received the trials in two different orders.
+Performance across the two study orders did not differ.
+Hence, we decided to combine the data.
+
+\hypertarget{analysis-1}{%
+\subsubsection{Analysis}\label{analysis-1}}
+
+To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: \texttt{cor\_clt\ \textbar{}\ trials(n\_clt)\ \textasciitilde{}\ age\_centered\ +\ mean\_gaze\_centered}).
+We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.
+
+\hypertarget{results-1}{%
+\subsubsection{Results}\label{results-1}}
+
+\begin{table}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrrr}
+\toprule
+Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
+\midrule
+Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
+Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
+Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
+\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
+Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
+\addlinespace
+Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
+\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
+\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
+Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\newpage
+
+\hypertarget{additional-information-for-the-adult-sample}{%
+\section{Additional information for the adult sample}\label{additional-information-for-the-adult-sample}}
+
+\begin{longtable}{llr}
+\toprule
+Current Country of Residence & studytype & n\\
+\midrule
+\endfirsthead
+\multicolumn{3}{@{}l}{\textit{(continued)}}\\
+\toprule
+Current Country of Residence & studytype & n\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+United Kingdom & vali & 47\\
+South Africa & vali & 8\\
+Portugal & vali & 6\\
+Poland & vali & 5\\
+Ireland & vali & 5\\
+\addlinespace
+Italy & vali & 4\\
+Spain & vali & 4\\
+Netherlands & vali & 4\\
+Canada & vali & 2\\
+Australia & vali & 2\\
+\addlinespace
+France & vali & 2\\
+Austria & vali & 2\\
+Norway & vali & 1\\
+DATA EXPIRED & vali & 1\\
+Finland & vali & 1\\
+\addlinespace
+Greece & vali & 1\\
+Germany & vali & 1\\
+United States & vali & 1\\
+Mexico & vali & 1\\
+South Africa & reli & 48\\
+\addlinespace
+United Kingdom & reli & 19\\
+United States & reli & 14\\
+Portugal & reli & 10\\
+Italy & reli & 7\\
+Canada & reli & 6\\
+\addlinespace
+Spain & reli & 5\\
+Ireland & reli & 5\\
+Poland & reli & 4\\
+Greece & reli & 4\\
+Netherlands & reli & 3\\
+\addlinespace
+CONSENT REVOKED & reli & 3\\
+Germany & reli & 3\\
+Australia & reli & 2\\
+France & reli & 2\\
+Czech Republic & reli & 2\\
+\addlinespace
+Hungary & reli & 2\\
+Chile & reli & 1\\
+Iceland & reli & 1\\
+New Zealand & reli & 1\\*
+\end{longtable}
 
@@
 
-In stuyy 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
+In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
 The pre-registration can be found here: \url{https://osf.io/nu62m}.
@@
 
-In addition to the beforementioned prescreening settings, we used a whitelist.
+In addition to the aforementioned prescreening settings, we used a whitelist.
 \emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
@@
 
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
+Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
+Cassidy, K.
+W., Fineberg, D.
+S., Brown, K., \& Perkins, A.
+(2005).
+Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}.
+\emph{Child Development}, \emph{76}(1), 97--106.
+Retrieved from \url{https://www.jstor.org/stable/3696711}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
+McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
+Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
+
+\end{CSLReferences}
+
+\endgroup
+
 \end{document}

### 2023-03-20 paper/manuscript.Rmd
prepare manuscript revision

@@
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "8548"
+wordcount         : "8590"
 bibliography      : ["../../references.bib"]
@@
 We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers.
-Only the `predictor age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements).
+Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements).
 Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding.
+Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see Supplements for distribution characteristics of the predictors).
 Albeit the effects were weak, they are consistent with the literature.

### 2023-03-20 stats/supplements_validity.Rmd
prepare manuscript revision

@@
   group_by(subjID) %>% 
+  mutate(siblingsChildAged = replace(siblingsChildAged, siblingsChildAged == -4, 0)) %>% 
   # so that all models run with same nr of subjects
   drop_na() %>%
-  ungroup() %>% 
+  ungroup()
+
+socenv_predictordistributions <- mDataSocenv %>% 
+  group_by(subjID) %>% 
+  slice(1) %>% 
+  select(childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW) %>% 
+  rename(
+    "Age of childcare entry in months" = childcareAge, 
+    "# Children in household aged 0-18" = siblingsNr, 
+    "Sibling variety score (Peterson, 2000)" = siblingsVarietyScoreP, 
+    "# Children in household aged 1-12" = siblingsChildAged,
+    "# Household members" = householdTotal,
+    "Average hours spent in childcare per day" = childcareHours, 
+    "Sibling variety score (Cassidy et al., 2005)" = siblingsVarietyScoreW,
+  ) %>% 
+  psych::describe() %>% 
+  select(-c(vars, median, trimmed, mad, range))
+
+socenv_predictordistributions
+saveRDS(socenv_predictordistributions, file = "../saves/socenv_predictordistributions.rds")
+
+mDataSocenv <- mDataSocenv %>% 
   mutate(

### 2023-03-20 supplements/supplements.Rmd
prepare manuscript revision

@@
 knitr::kable(webcam_models, format = "latex", booktabs = TRUE) %>% 
-  kable_styling(latex_options = "scale_down")
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
 ```
@@
 knitr::kable(socenv_results, format = "latex", booktabs = TRUE) %>% 
-  kable_styling(latex_options = "scale_down")
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
 ```
@@
 The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
+Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).
+
+```{r socenv_predictordistributions, results = "asis"}
+socenv_predictordistributions <- readRDS("../saves/socenv_predictordistributions.rds") %>%
+  mutate_if(is.numeric, round, 2) %>% 
+  ungroup()
+
+socenv_predictordistributions <- socenv_predictordistributions[-1,] # get rid of subjid
+
+knitr::kable(socenv_predictordistributions, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
 
@@
 ```{r orev_results, results = "asis"}
-orev_results <- readRDS("../saves/socenv_results.rds") %>% 
+orev_results <- readRDS("../saves/orev_results.rds") %>% 
   mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
@@
 knitr::kable(orev_results, format = "latex", booktabs = TRUE) %>% 
-  kable_styling(latex_options = "scale_down")
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
 ```
@@
 kable(adult_sample_countryn, "latex", booktabs = TRUE, longtable = TRUE) %>%
-  kable_styling(latex_options = c("hold_position", "repeat_header"))
+  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
 ```

### 2023-03-20 paper/manuscript.Rmd
correct link to github

@@
 The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository (<https://github.com/jprein/gazecues-methods>).
+The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository (<https://github.com/ccp-eva/gazecues-methods>).
 All experiments were pre-registered (<https://osf.io/zjhsc/>).

### 2023-05-12 paper/manuscript.Rmd
incorporate reviews round 2

@@
 High internal consistency and test–retest reliability estimates underline that the captured variation is systematic.
+Associations with social-environmental factors and language skills speak toward the validity of the task.
 This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
@@
 Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
-Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
+Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
 
 However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @poulin-dubois2023discontinuity; @sodian2023reply; @sodian2016understanding].
-This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
+This might be because traditional measures of social cognition are not designed to capture variation *between* children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
 A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].
@@
 
-Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
+Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic, reliable, and valid way.
 We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
@@
 Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication [@macdonald2013eye; @hernik2019infant].
+
 While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
@@
 Consequently, we aimed to assess the differentiation of the ability to understand gaze.
-Our goal was not to establish the youngest age at which children understand gaze cues.
+Our goal was *not* to establish the youngest age at which children understand gaze cues.
 Rather, we wanted to examine how that ability changes with age.
@@
 Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
-Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.
+Furthermore, we were interested in whether and how the data collection mode (in-person vs.
+remote) influences responses.
+Since we expected a greater difference in responses between the two data collection modes for children, the analysis of data collection mode was restricted to a child sample.
 
@@
 The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
-The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.
+The additional analyses mentioned in the pre-registrations (e.g., computational model) address separate research questions (e.g., how can we explain the concept and process of gaze understanding?) and will be reported elsewhere.
+In this paper, we focus on the methodological and psychometric aspects of our task.
 
@@
 
+Please note that we did not collect participant-specific demographics. 
+In the following, we aim to provide context and generalizations based on the broader community and the larger pool of potential participants. 
 Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
@@
 For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
-We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
+We inspected the posterior distribution (mean and 95% Credible Interval (CrI)) for the age and data collection estimates.
 
@@
 For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode.
-For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
 Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
 Small points show the mean performance for each subject averaged across trials.
+For adult data in (A) and (F), we added minimal horizontal and vertical noise to avoid overplotting.
 The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection.
 The color of data points denotes age group.
+For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
 
@@
 Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
+Similar to our first study, we did not collect participant-specific demographics. For a community-based description of our participant pool, see Participant section of the first study.
 
+As in our first study, adults were recruited via *Prolific* [@palan2018prolific].
 The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).
 Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).
+See Supplements and the available online data set for more detailed information.
 
@@
 For each subject, trials were split into odd and even trials.
-Performance was aggregated and then correlated using *Pearson* coefficients.
+Performance was aggregated and then correlated using *Pearson* correlation coefficients.
 For this, we used the data of the first test day.
@@
 
-After having probed our new testing infrastructure and the psychometric properties of the TANGO task, we aimed at establishing its validity. 
+After having probed our new testing infrastructure and the psychometric properties of the TANGO, we aimed at establishing its validity. 
 One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related. 
@@
 
-To assess such external validity for the TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day.
+To assess such external validity for the TANGO, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in daycare, and if yes, (5) since when and (6) for how long on an average day.
 `r sum(vali_sample$nTotal[vali_sample$sample == "socenv"])` families filled out the questionnaire and were included in the analysis.
@@
 Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
-For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [@bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO task.
-We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)B and C).
+For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [oREV; @bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO.
+In the oREV task, children are shown four pictures (target word, distractor with similar age-of-acquisition rating, phonological distractor, and semantic distractor; see Supplements for further detail) and hear a verbal prompt asking them to select one of the pictures.
+The oREV score then represents the proportion of correctly identified target pictures.
+We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)C and D).
 Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic of measures of social cognition.
 
-(ref:figlab4) **Validity of the TANGO task.** (A) Influence of age of childcare entry on gaze understanding.
+(ref:figlab4) **Validity of the TANGO.** (A) Influence of age of childcare entry on gaze understanding.
 The older the children were when entering childcare, the less likely they are to respond correctly.
@@
 (C) Influence of gaze understanding on receptive vocabulary.
+The oREV score represents a proportion of correctly identified target words in the receptive vocabulary test.
+Similarly, the TANGO score refers to proportion of correctly located targets (see Supplements for further detail).
 (D) Influence of gaze understanding on receptive vocabulary by age.
-The regression line with 95% CI shows a smooth conditional mean based on a linear model, with a *Pearson*’s correlation coefficient *r*.
-Dots show the mean performance for each subject averaged across trials.
+The regression line with 95% CI shows a smooth conditional mean based on a generalized linear model, with *Pearson*’s correlation coefficient *r*.
+Dots show the mean performance for each subject averaged across trials with minimal horizontal and vertical noise added to avoid overplotting.
 The color of dots denotes age group.
 For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model.
-Black dots represent means, thicker black lines 80% CI and thinner black lines 95% CI.
+Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
 
@@
 Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
-Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
+Second, our task showed satisfactory psychometric properties with respect to internal consistency and test-retest reliability estimates.
 Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
@@
 Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
-Both study versions exhibit high retest reliability, also when controlling for age.
+Both study versions exhibit high test-retest reliability, also when controlling for age.
 Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf. @hughes2000good; improved reliability through aggregation).
@@
 
-With respect to validity, we found that performance in the TANGO task was related to relevant external variables and cognitive measures.
+With respect to validity, we found that performance in the TANGO was related to relevant external variables and cognitive measures.
 Family-level variables, capturing a child’s opportunity for social interaction, systematically influenced gaze understanding.
@@
 We found a substantial relationship between the two variables, even when correcting for age. 
-Taken together, this speaks to the validity of our TANGO task.
+Taken together, this speaks to the validity of the TANGO.
 
@@
 
-First, we want to address the scope and interpretation of the TANGO task.
+First, we want to address the scope and interpretation of the TANGO.
 We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
-This speaks to the face validity of the TANGO task and its focus on an inherently social stimulus.
-However, we do not want to claim that the TANGO task does not also recruit other, domain general processes.
+This speaks to the face validity of the TANGO and its focus on an inherently social stimulus.
+However, we do not want to claim that the TANGO does not also recruit other, domain-general processes.
 For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
@@
 
+Third, the children in our sample live in an industrialized, urban Central-European context.
+It is unclear how our results would generalize to different socio-cultural contexts.
+A limiting factor of our study is that we did not collect demographical information on a participant-level.
+Therefore, we could only provide a broader demographic description on a community-level.
+This is important to keep in mind when gauging the generalizability of our new measure.
+
 Finally, we utilized subtle gaze cues in order to increase difficulty and capture individual differences.
@@
 We have presented a new experimental paradigm to study gaze understanding across the lifespan.
-The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
+The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and test-retest reliability.
 The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
+Associations with social-environmental factors and language skills speak toward the validity of the task.
 Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.

### 2023-05-12 stats/analysis.Rmd
incorporate reviews round 2

@@
 ```
+
+```{r supplements_reli_byagegroup}
+ggarrange(
+  hedge_intCon_kids + facet_grid(~ ageInYears), 
+  hedge_retest_kids + facet_grid(~ ageInYears),
+  box_intCon_kids + facet_grid(~ ageInYears) + scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)), 
+  box_retest_kids + facet_grid(~ ageInYears) + scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)), 
+  nrow = 2, 
+  ncol = 2, 
+  labels = c("A", "B", "C", "D")
+)
+
+ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 8, height = 6)
+```

### 2023-05-12 stats/supplements_validity.Rmd
incorporate reviews round 2

@@
 library(tidybayes) # gather_draws
+library(ggtext) # for printing italics
 
@@
 ```{r orev_plot}
-orev_plot <- ggplot(mDataOrev, aes(x = mean_orev, y = mean_tango)) +
+orev_data %>%
+  group_by(ageInYears) %>%
+  summarize(cor=cor(mean_tango, mean_orev) %>% round(2))
 
-  geom_point(aes(col = as.factor(ageInYears)), shape = 18, size = 2) +
-  geom_smooth(method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey") +
-  stat_cor(method = "pearson", label.x = 0.9, label.y = 0.975, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+orev_plot <- ggplot(orev_data, aes( x = mean_tango, y = mean_orev)) +
 
-  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "6-year-olds", "7-year-olds")) +
+  geom_jitter(aes(col = as.factor(ageInYears)), shape = 18, size = 2, width = 0.05, height = 0.05) +
+  geom_smooth(method = "glm", size = 1, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0.9, label.y = 0.98, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
 
-  labs(x = "oREV score", y = "TANGO score", col = "Age in years") + 
-  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) + 
-  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds (*r* = 0.26)", "4-year-olds (*r* = 0.22)", "5-year-olds (*r* = 0.29)", "6-year-olds (*r* = 0.11)", "7-year-olds (*r* = 0.40)")) +
+
+  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
+  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) + 
+  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
 
   theme(legend.title = element_text(size = 9), 
-        legend.text = element_text(size = 9),
         legend.key.size = unit(0.4, "cm"), 
@@
         legend.box = "horizontal",
-        legend.position = c(0.175, 0.25), 
+        legend.position = c(0.2, 0.18), 
         legend.background = element_blank(),
-        legend.box.background = element_rect(colour = "black")
+        legend.box.background = element_rect(colour = "black"), 
+        legend.text = element_markdown()
         )
@@
 ```
+
+```{r orev_by_agegroup}
+orev_agegroup <- ggplot(orev_data, aes( x = mean_tango, y = mean_orev)) +
+
+  geom_jitter(aes(col = as.factor(ageInYears)), shape = 18, size = 2, width = 0.05, height = 0.05) +
+  geom_smooth(method = "glm", size = 1, alpha = 0.15, col = "darkgrey") +
+  stat_cor(method = "pearson", label.x = 0.05, label.y = 1.1, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
+
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds (*r* = 0.26)", "4-year-olds (*r* = 0.22)", "5-year-olds (*r* = 0.29)", "6-year-olds (*r* = 0.11)", "7-year-olds (*r* = 0.40)")) +
+
+  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
+  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.5)) + 
+  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
+  facet_grid(~ ageInYears) + 
+  theme(legend.position = "none")
+d
+orev_agegroup
+
+saveRDS(orev_agegroup, file = "../saves/tango_orev_byagegroup.rds")
+ggsave("../figures/tango_supplements_orev_byagegroup.png", width = 7, height = 4)
+```

### 2023-05-12 supplements/supplements.Rmd
incorporate reviews round 2

@@
 
-```{r reli_agegroup, include=FALSE}
-hedge_intCon_agegroup <- readRDS("../saves/tango-hedge-intCon-kids.rds") + 
-  geom_point(aes(col = ageInYears), size = 1) + 
-  facet_wrap(~ ageInYears)
-
-hedge_retest_agegroup <- readRDS("../saves/tango-hedge-retest-kids.rds") + 
-  geom_point(aes(col = ageInYears), size = 1) + 
-  facet_wrap(~ ageInYears)
-
-box_intCon_agegroup <- readRDS("../saves/tango-box-intCon-kids.rds") + 
-  geom_point(aes(col = ageInYears), size = 1) + 
-  facet_wrap(~ ageInYears)
-
-box_retest_agegroup <- readRDS("../saves/tango-box-retest-kids.rds") + 
-  geom_point(aes(col = ageInYears), size = 1) + 
-  facet_wrap(~ ageInYears)
-
-ggarrange(hedge_intCon_agegroup, 
-          hedge_retest_agegroup,
-          box_intCon_agegroup, 
-          box_retest_agegroup, 
-          ncol = 2,
-          nrow = 2, 
-          labels = c("A", "B", "C", "D")
-)
-
-ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 9, height = 6)
-```
-
 \newpage
@@
 We modelled the number of participant's correct responses using a `Binomial` distribution.
+In order to combine data of our two TANGO study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+After this transformation, we calculated a "TANGO score" as the proportion of correctly located targets.
+See Analysis section of Social-environmental factors for further detail.
 
@@
   kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
+
+(ref:figlab6) **Effect of gaze understanding on receptive vocabulary by age group**.
+Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
+Diamonds show the performance for each subject.
+The color of data points denotes age group.
+
+```{r fig6, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab6)"}
+knitr::include_graphics("../figures/tango_supplements_orev_byagegroup.png")
 ```

### 2023-05-16 paper/manuscript.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 
-  - name          : "Julia Prein"
+  - name          : "Julia Christin Prein"
     affiliation   : "1"
@@
     email         : "julia_prein@eva.mpg.de"
+    role          :
+      - Conceptualization
+      - Software
+      - Formal Analysis
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing
 
   - name          : "Manuel Bohn"
-    affiliation   : "1"
+    affiliation   : "1,2"
+    role          :
+      - Conceptualization
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing    
   - name          : "Steven Kalinke"
     affiliation   : "1"
+    role          : 
+      - Software
+      - Writing - Review & Editing
   - name          : "Daniel B. M. Haun"
     affiliation   : "1"
+    role          :
+      - Conceptualization
+      - Writing - Review & Editing
 
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+  - id            : "2"
+    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"    
 authornote: |
@@
 High internal consistency and test–retest reliability estimates underline that the captured variation is systematic.
-Associations with social-environmental factors and language skills speak toward the validity of the task.
+Associations with social-environmental factors and language skills speak to the validity of the task.
 This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
@@
 keywords          : "social cognition, individual differences, gaze cues, cognitive development"
-wordcount         : "8590"
+wordcount         : "8897"
 bibliography      : ["../../references.bib"]
@@
 The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
-The additional analyses mentioned in the pre-registrations (e.g., computational model) address separate research questions (e.g., how can we explain the concept and process of gaze understanding?) and will be reported elsewhere.
+The additional analyses mentioned in the pre-registrations (e.g., computational model) address separate research questions (e.g., process-level account of gaze understanding) and will be reported elsewhere.
 In this paper, we focus on the methodological and psychometric aspects of our task.
@@
     nTotal = n_distinct(subjID), 
-    meanAge = mean(age, na.rm = T) %>% round(2),
-    sdAge = sd(age, na.rm = T) %>% round(2),
-    minAge = min(age, na.rm = T),
-    maxAge = max(age, na.rm = T),
+    meanAge = mean(ageAdults, na.rm = T) %>% round(2),
+    sdAge = sd(ageAdults, na.rm = T) %>% round(2),
+    minAge = min(ageAdults, na.rm = T),
+    maxAge = max(ageAdults, na.rm = T),
     nFemales = ceiling(sum(female/15)),
@@
     maxAgeInMonths = max(ageInMonths, na.rm = T),
-    nFemales = ceiling(sum(female/30)), # 15 test trials * 2
+    nFemales = ceiling(sum(female/30)),
   )
@@
     nTotal = n_distinct(subjID), 
-    meanAge = mean(age, na.rm = T) %>% round(2),
-    sdAge = sd(age, na.rm = T) %>% round(2),
-    minAge = min(age, na.rm = T),
-    maxAge = max(age, na.rm = T),
+    meanAge = mean(ageAdults, na.rm = T) %>% round(2),
+    sdAge = sd(ageAdults, na.rm = T) %>% round(2),
+    minAge = min(ageAdults, na.rm = T),
+    maxAge = max(ageAdults, na.rm = T),
     nFemales = sum(female),
@@
 We used parents' responses to construct different scores suggested in the literature [@peterson2000kindred; @cassidy2005theory], capturing aspects of children’s opportunities for social interaction with adults and peers.
-Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements).
-Figure \@ref(fig:fig4)B shows that all other predictor scores were positively linked to gaze understanding.
+Only the predictor `age of childcare entry` improved the model fit compared to the null model (see Figure Figure \@ref(fig:fig4)A; for model comparisons, see Supplements): the older the children were when entering childcare, the less likely they were to correctly use the available gaze cue.
+Figure \@ref(fig:fig4)A shows that all other predictor scores were positively linked to gaze understanding.
 Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see Supplements for distribution characteristics of the predictors).
@@
 Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
-For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data on a receptive vocabulary test [oREV; @bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO.
-In the oREV task, children are shown four pictures (target word, distractor with similar age-of-acquisition rating, phonological distractor, and semantic distractor; see Supplements for further detail) and hear a verbal prompt asking them to select one of the pictures.
-The oREV score then represents the proportion of correctly identified target pictures.
-We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)C and D).
+For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data with a receptive vocabulary test [oREV, @bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO.
+In the oREV task, children are shown four pictures (see Supplements for further detail) and hear a verbal prompt asking them to select one of the pictures.
+The oREV score is the proportion of correctly selected pictures.
+We found a substantial relationship between gaze understanding six months prior and receptive vocabulary, even when correcting for age (see Figure \@ref(fig:fig4)B and C).
 Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic of measures of social cognition.
 
-(ref:figlab4) **Validity of the TANGO.** (A) Influence of age of childcare entry on gaze understanding.
-The older the children were when entering childcare, the less likely they are to respond correctly.
-(B) Influence of social-environmental factors on gaze understanding.
-Adding each predictors respectively to the null model did not improve model fit.
-(C) Influence of gaze understanding on receptive vocabulary.
-The oREV score represents a proportion of correctly identified target words in the receptive vocabulary test.
+(ref:figlab4) **Validity of the TANGO.** (A) Influence of social-environmental factors on gaze understanding.
+(B) Influence of gaze understanding on receptive vocabulary.
+For (A) and (B), the graphs show the posterior distributions for the respective predictor of each model.
+Filled green distributions show that adding the respective predictor improved the model fit compared to the null model.
+Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
+The oREV score is the proportion of correctly selected pictures in the receptive vocabulary task.
 Similarly, the TANGO score refers to proportion of correctly located targets (see Supplements for further detail).
-(D) Influence of gaze understanding on receptive vocabulary by age.
+(C) Influence of gaze understanding on receptive vocabulary by age.
 The regression line with 95% CI shows a smooth conditional mean based on a generalized linear model, with *Pearson*’s correlation coefficient *r*.
@@
 The color of dots denotes age group.
-For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model.
-Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
 
 ```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/tango_vali_arrangedplot.png")
+knitr::include_graphics("../figures/tango_vali_plot.pdf")
 ```
@@
 Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2022individual].
+With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes [@bohn2023individual].
 
@@
 It is unclear how our results would generalize to different socio-cultural contexts.
-A limiting factor of our study is that we did not collect demographical information on a participant-level.
-Therefore, we could only provide a broader demographic description on a community-level.
+A related limitation is that we did not collect demographical information on a participant-level and, instead, had to rely on a community-level description of the sample.
 This is important to keep in mind when gauging the generalizability of our new measure.
@@
 The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
-Associations with social-environmental factors and language skills speak toward the validity of the task.
+Associations with social-environmental factors and language skills illustrate the validity of the task.
 Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.

### 2023-05-16 stats/analysis.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 ```{r load_data}
-testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-    studyversion = factor(studyversion, levels = c("hedge", "box")), 
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "adults")), 
-    studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
-
-    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
-    # the smaller the value, the more central the position
-    symmetricPosition = ifelse(studyversion == "box", 
-                               # for box version
-                               case_when(
-                                  targetPosition == "box3" ~ 0, 
-                                  targetPosition == "box2" | targetPosition == "box4" ~ 1,
-                                  targetPosition == "box1" | targetPosition == "box5" ~ 2), 
-                               # for hedge version
-                               targetCentralityX
-                       ),
-
-    # distance between target and click in balloon widths (balloon width is 160 SVG units)
-    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
-  )
+testtrials <- readRDS(file = "../data/tango-testtrials.rds")
 ```
@@
 hedge_variation_plot_GLMM
-saveRDS(hedge_variation_plot_GLMM, file = "../saves/tango-hedge-variation-plot-GLMM.rds")
+saveRDS(hedge_variation_plot_GLMM, file = "../saves/tango_hedge_variation_plot_GLMM.rds")
 # ggsave("../figures/tango_hedge_variation_GLMM.png", width = 7, height = 4)
@@
 ```{r GLMM_plot_box}
-# mAgeBox <- readRDS("../saves/mAgeBox.rds")
 nd_box <- mDataAgeBox %>% 
@@
 
-saveRDS(box_variation_plot_GLMM, file = "../saves/tango-box-variation-plot-GLMM.rds")
+saveRDS(box_variation_plot_GLMM, file = "../saves/tango_box_variation_plot_GLMM.rds")
 # ggsave("../figures/tango_box_variation_GLMM.png", width = 7, height = 4)
@@
 
-saveRDS(hedge_intCon_kids, file = "../saves/tango-hedge-intCon-kids.rds")
+saveRDS(hedge_intCon_kids, file = "../saves/tango_hedge_intCon_kids.rds")
 # ggsave("../figures/tango_hedge_intCon_kids.png", width = 6, height = 4)
@@
 
-saveRDS(hedge_intCon_adults, file = "../saves/tango-hedge-intCon-adults.rds")
+saveRDS(hedge_intCon_adults, file = "../saves/tango_hedge_intCon_adults.rds")
 # ggsave("../figures/tango_hedge_intCon_adults.png", width = 6, height = 4)
@@
 
-saveRDS(box_intCon_kids, file = "../saves/tango-box-intCon-kids.rds")
+saveRDS(box_intCon_kids, file = "../saves/tango_box_intCon_kids.rds")
 # ggsave("../figures/tango_box_intCon_kids.png", width = 6, height = 4)
@@
 
-saveRDS(box_intCon_adults, file = "../saves/tango-box-intCon-adults.rds")
+saveRDS(box_intCon_adults, file = "../saves/tango_box_intCon_adults.rds")
 # ggsave("../figures/tango_box_intCon_adults.png", width = 6, height = 4)
@@
 splithalf_plot
-saveRDS(splithalf_plot, file = "../saves/tango-splithalf-plot.rds")
+saveRDS(splithalf_plot, file = "../saves/tango_splithalf_plot.rds")
 
 ggsave("../figures/tango_splithalf.png", width = 8, height = 2.5, scale = 1.2)
+ggsave("../figures/tango_splithalf.pdf", width = 8, height = 2.5, scale = 1.2)
 ```
@@
 ```{r save_splithalf_data}
-write.csv(splithalf_data, "../saves/tango-splithalf.csv", quote = F, row.names = F)
-saveRDS(splithalf_data, file = "../saves/tango-splithalf-table.rds")
+write.csv(splithalf_data, "../saves/tango_splithalf_table.csv", quote = F, row.names = F)
+saveRDS(splithalf_data, file = "../saves/tango_splithalf_table.rds")
 
@@
 
-saveRDS(hedge_retest_correlationcoefficients, file = "../saves/tango-hedge-retest-correlationcoefficients.rds")
+saveRDS(hedge_retest_correlationcoefficients, file = "../saves/tango_hedge_retest_correlationcoefficients.rds")
+write.csv(hedge_retest_correlationcoefficients, "../saves/tango_hedge_retest_correlationcoefficients.csv", quote = F, row.names = F)
 ```
@@
 
-saveRDS(hedge_retest_kids, file = "../saves/tango-hedge-retest-kids.rds")
+saveRDS(hedge_retest_kids, file = "../saves/tango_hedge_retest_kids.rds")
 # ggsave("../figures/tango_hedge_retest_kids.png", width = 6, height = 4)
@@
 
-saveRDS(hedge_retest_adults, file = "../saves/tango-hedge-retest-adults.rds")
+saveRDS(hedge_retest_adults, file = "../saves/tango_hedge_retest_adults.rds")
 # ggsave("../figures/tango_hedge_retest_adults.png", width = 6, height = 4)
@@
 
-saveRDS(box_retest_kids, file = "../saves/tango-box-retest-kids.rds")
+saveRDS(box_retest_kids, file = "../saves/tango_box_retest_kids.rds")
 # ggsave("../figures/tango_box_retest_kids.png", width = 6, height = 4)
@@
 
-saveRDS(box_retest_adults, file = "../saves/tango-box-retest-adults.rds")
+saveRDS(box_retest_adults, file = "../saves/tango_box_retest_adults.rds")
 # ggsave("../figures/tango_hedge_retest_adults.png", width = 6, height = 4)
@@
 ```{r arrange_plots}
-# hedge_variation_plot_GLMM <- readRDS(file = "../saves/tango-hedge-variation-plot-GLMM.rds")
-# hedge_intCon_kids <- readRDS(file = "../saves/tango-hedge-intCon-kids.rds")
-# hedge_intCon_adults <- readRDS(file = "../saves/tango-hedge-intCon-adults.rds")
-# hedge_retest_kids <- readRDS(file = "../saves/tango-hedge-retest-kids.rds")
-# hedge_retest_adults <- readRDS(file = "../saves/tango-hedge-retest-adults.rds")
-# box_variation_plot_GLMM <- readRDS(file = "../saves/tango-box-variation-plot-GLMM.rds")
-# box_intCon_kids <- readRDS(file = "../saves/tango-box-intCon-kids.rds")
-# box_intCon_adults <- readRDS(file = "../saves/tango-box-intCon-adults.rds")
-# box_retest_kids <- readRDS(file = "../saves/tango-box-retest-kids.rds")
-# box_retest_adults <- readRDS(file = "../saves/tango-box-retest-adults.rds")
-
 tango_arrangedplot <- ggarrange(
@@
 tango_arrangedplot
-saveRDS(tango_arrangedplot, file = "../saves/tango-arrangedplot.rds")
+saveRDS(tango_arrangedplot, file = "../saves/tango_arrangedplot.rds")
 ggsave("../figures/tango_arrangedplot.png", width = 6.5, height = 5, scale = 1.6, bg = "white")
+ggsave("../figures/tango_arrangedplot.pdf", width = 6.5, height = 5, scale = 1.6, bg = "white")
 ```
@@
 ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 8, height = 6)
-```
+ggsave("../figures/tango_supplements_reli_byagegroup.pdf", width = 8, height = 6)
+```

### 2023-05-16 stats/supplements_triallevel.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 ```{r load_data}
-alltrials <- readRDS(file = "../data/tango-alltrials.rds") %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-    studyversion = factor(studyversion, levels = c("hedge", "box")), 
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "adults")), 
-    trialType = factor(trialType, levels = c("touch", "fam", "test"), labels = c("training 1", "training 2 & 3", "test")), 
-    studytype = factor(studytype, levels = c("vali", "reli"), labels = c("individual variation sample", "reliability sample")),
-
-    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
-    # the smaller the value, the more central the position
-    symmetricPosition = case_when(
-                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
-                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
-                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
-                                  targetPosition == "2" | targetPosition == "9" ~ 4,
-                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
-                       ),
-
-    # distance between target and click in balloon widths (balloon width is 160 SVG units)
-    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
-  )
+alltrials <- readRDS(file = "../data/tango-alltrials.rds")
 ```
@@
 ggsave("../figures/tango_supplements_trainingtrials.png", width = 9, height = 6, scale = 1.2, bg = "white")
+ggsave("../figures/tango_supplements_trainingtrials.pdf", width = 9, height = 6, scale = 1.2, bg = "white")
 ```
@@
 ggsave("../figures/tango_supplements_acrosstrials.png", width = 8, height = 6, scale = 1, bg = "white")
+ggsave("../figures/tango_supplements_acrosstrials.pdf", width = 8, height = 6, scale = 1, bg = "white")
 ```

### 2023-05-16 stats/supplements_validity.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 saveRDS(socenv_predictordistributions, file = "../saves/socenv_predictordistributions.rds")
+write.csv(socenv_predictordistributions, "../saves/socenv_predictordistributions.csv", quote = F, row.names = F)
 
@@
 ```{r socenv_savemodels}
-write.csv(mSEnull, "../saves/mSEnull.csv", quote = F, row.names = F)
 saveRDS(mSEnull, "../saves/mSEnull.rds")
-write.csv(mSEccAge, "../saves/mSEccAge.csv", quote = F, row.names = F)
 saveRDS(mSEccAge, "../saves/mSEccAge.rds")
-write.csv(mSEccHours, "../saves/mSEccHours.csv", quote = F, row.names = F)
 saveRDS(mSEccHours, "../saves/mSEccHours.rds")
-write.csv(mSEhhTotal, "../saves/mSEhhTotal.csv", quote = F, row.names = F)
 saveRDS(mSEhhTotal, "../saves/mSEhhTotal.rds")
-write.csv(mSEhhSibs, "../saves/mSEhhSibs.csv", quote = F, row.names = F)
 saveRDS(mSEhhSibs, "../saves/mSEhhSibs.rds")
-write.csv(mSEsibsChildAged, "../saves/mSEsibsChildAged.csv", quote = F, row.names = F)
 saveRDS(mSEsibsChildAged, "../saves/mSEsibsChildAged.rds")
-write.csv(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.csv", quote = F, row.names = F)
 saveRDS(mSEsiblingsVarietyScoreP, "../saves/mSEsiblingsVarietyScoreP.rds")
-write.csv(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.csv", quote = F, row.names = F)
 saveRDS(mSEsiblingsVarietyScoreW, "../saves/mSEsiblingsVarietyScoreW.rds")
-write.csv(mSEPE, "../saves/mSEPE.csv", quote = F, row.names = F)
 saveRDS(mSEPE, "../saves/mSEPE.rds")
@@
     predictor = factor(.variable, 
-                       levels = c("b_hhSibs", 
+                       levels = c(
+                                  "b_ccAge", 
+                                  "b_hhSibs", 
+                                  "b_pe",
+                                  "b_sibsChildAged", 
+                                  "b_siblingsVarietyScoreW", 
                                   "b_siblingsVarietyScoreP", 
-                                  "b_sibsChildAged", 
                                   "b_hhTotal", 
-                                  "b_ccHours", 
-                                  "b_ccAge", 
-                                  "b_siblingsVarietyScoreW", 
-                                  "b_pe"), 
-                       labels = c("# Children in household aged 0-18", 
+                                  "b_ccHours"
+                                  ), 
+                       labels = c(
+                                  "Age of childcare entry", 
+                                  "# Children in household aged 0-18", 
+                                  "Peer exposure index",
+                                  "# Children in household aged 1-12", 
+                                  "Sibling variety score (Cassidy et al., 2005)", 
                                   "Sibling variety score (Peterson, 2000)", 
-                                  "# Children in household aged 1-12", 
                                   "# Household members", 
-                                  "Average hours spent in childcare per day", 
-                                  "Age of childcare entry", 
-                                  "Sibling variety score (Cassidy et al., 2005)", 
-                                  "Peer exposure index")
+                                  "Average hours spent in childcare per day" 
+                                  )
                        )  
@@
 
-```{r socenv_plot_winning}
-socenv_plot_winning <- socenv_draws %>% 
-  filter(predictor == "Age of childcare entry") %>% 
-  ggplot(., aes(y = predictor, x = estimate)) +
-  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 0.8, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
+```{r socenv_plot}
+socenv_plot <- socenv_draws %>% 
+  mutate(
+    winning_model = ifelse(predictor == "Age of childcare entry", TRUE, FALSE)
+  ) %>% 
+  ggplot(., aes(x = estimate, y = reorder(predictor, desc(predictor)), fill = winning_model)) +
+  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 0.8, slab_color = "#006c66", slab_size = 0.5, slab_alpha = 0.4) +
+  scale_fill_manual(values = c("#EBECEC", "#006c66")) +
   labs(x = "Posterior estimate when predicting TANGO score", y = "") +
@@
   geom_vline(xintercept = 0, linetype = "dashed") +
-  coord_cartesian(expand = TRUE, ylim = c(1.5, 1.5)) +
+  coord_cartesian(expand = TRUE, ylim = c(1.5, 8.5)) +
   theme_classic()
 
-socenv_plot_winning
+socenv_plot
 
-saveRDS(socenv_plot_winning, file = "../saves/socenv_plot_winning.rds")
-# ggsave("../figures/socenv_plot_winning.png", width = 10, height = 6, scale = 1, bg = "white")
-```
-
-```{r socenv_plot_allother}
-socenv_plot_allother <- socenv_draws %>% 
-  filter(predictor != "Age of childcare entry") %>% 
-  ggplot(., aes(y = predictor, x = estimate)) +
-  tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_size = 0.5, slab_fill = "#EBECEC", slab_alpha = 0.9) +
-  labs(x = "Posterior estimate when predicting TANGO score", y = "") +
-  guides(fill = "none")+
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  coord_cartesian(expand = TRUE, ylim = c(1.5, 7.5)) +
-  theme_classic()
-
-socenv_plot_allother
-
-saveRDS(socenv_plot_allother, file = "../saves/socenv_plot_allother.rds")
-# ggsave("../figures/socenv_plot_allother.png", width = 10, height = 6, scale = 1, bg = "white")
+saveRDS(socenv_plot, file = "../saves/socenv_plot.rds")
+# ggsave("../figures/socenv_plot.png", width = 10, height = 6, scale = 1, bg = "white")
 ```
@@
 saveRDS(vali_sample, file = "../saves/vali_sample.rds")
+write.csv(vali_sample, "../saves/vali_sample.csv", quote = F, row.names = F)
 ```
@@
   ggplot(., aes(x = estimate, y = predictor)) +
- tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#EBECEC", slab_alpha = 0.9) +
+ tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#006c66", slab_alpha = 0.4) +
     labs(x = "Posterior estimate when predicting oREV score", y = "") +
@@
   scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) + 
-  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
+  scale_y_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) +
 
@@
         legend.box = "horizontal",
-        legend.position = c(0.2, 0.18), 
+        legend.position = c(0.8, 0.18), 
         legend.background = element_blank(),
@@
 
-```{r arrange_plots}
-vali_arrangedplot <- ggarrange(
+```{r vali_plot}
 ggarrange(
-    socenv_plot_winning,
-    socenv_plot_allother,
-    ncol = 2,
-    labels = c("A", "B")
-  ),
-
-  ggarrange(
+  socenv_plot,
   orev_modelplot, 
   orev_plot,
-    ncol = 2,
-    labels = c("C", "D")
-  ), 
-  nrow = 2
+  ncol = 3, 
+  widths = c(1.2, 1, 1),
+  labels = c("A", "B", "C")
 )
 
-vali_arrangedplot
-
-saveRDS(vali_arrangedplot, file = "../saves/vali-arrangedplot.rds")
-ggsave("../figures/tango_vali_arrangedplot.png", width = 8.5, height = 6, scale = 1.5, bg = "white")
+ggsave("../figures/tango_vali_plot.png", width = 8, height = 2, scale = 2, bg = "white")
+ggsave("../figures/tango_vali_plot.pdf", width = 8, height = 2, scale = 2, bg = "white")
 ```
@@
   theme(legend.position = "none")
-d
+
 orev_agegroup
@@
 ggsave("../figures/tango_supplements_orev_byagegroup.png", width = 7, height = 4)
+ggsave("../figures/tango_supplements_orev_byagegroup.pdf", width = 7, height = 4)
 ```

### 2023-05-16 stats/supplements_webcamcoding.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 webcam_data <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-  filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & webcam == TRUE & ageInYears == 3) %>% 
+  filter(studytype == "vali" & datacollection == "remote - unsupervised" & studyversion == "box" & !is.na(nrRepeatedTestquestion) & ageInYears == 3) %>% 
   group_by(subjID) %>% 
@@
 
-write.csv(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.csv", quote = F, row.names = F)
-saveRDS(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.rds")
+write.csv(perTrial_draws, "../saves/supplements_webcamcoding_perTrialdraws.csv", quote = F, row.names = F)
+saveRDS(perTrial_draws, "../saves/supplements_webcamcoding_perTrialdraws.rds")
 ```
@@
 
-write.csv(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.csv", quote = F, row.names = F)
-saveRDS(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.rds")
+write.csv(perSubject_draws, "../saves/supplements_webcamcoding_perSubjectdraws.csv", quote = F, row.names = F)
+saveRDS(perSubject_draws, "../saves/supplements_webcamcoding_perSubjectdraws.rds")
 ```
@@
 ggsave("../figures/tango_supplements_webcamcoding.png", width = 10, height = 5, scale = 1, bg = "white")
+ggsave("../figures/tango_supplements_webcamcoding.pdf", width = 10, height = 5, scale = 1, bg = "white")
 ```
@@
 
-write.csv(overall_results, "../saves/supplements-webcamcoding-results.csv", quote = F, row.names = F)
-saveRDS(overall_results, "../saves/supplements-webcamcoding-results.rds")
+write.csv(overall_results, "../saves/supplements_webcamcoding_results.csv", quote = F, row.names = F)
+saveRDS(overall_results, "../saves/supplements_webcamcoding_results.rds")
 ```

### 2023-05-16 supplements/supplements.Rmd
clean up data file and naming conventions. incorporate manuels feedback

@@
 ---
-title             : "Supplements for the manuscript  'TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'"
+title             : "Supplemental Material for the manuscript  'TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'"
 shorttitle        : "Supplements"
@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
     address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
@@
   - name          : "Manuel Bohn"
-    affiliation   : "1"
+    affiliation   : "1,2"
   - name          : "Steven Kalinke"
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+  - id            : "2"
+    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany" 
 floatsintext      : yes
@@
 ```{r sample}
-testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-    studyversion = factor(studyversion, levels = c("hedge", "box")), 
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "adults")), 
-    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
-  )
+testtrials <- readRDS(file = "../data/tango-testtrials.rds")
 ```
@@
 ```{r webcam_table}
-webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
+webcam_models <- readRDS(file = "../saves/supplements_webcamcoding_results.rds") %>%
   mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
@@
 ```{r adult_sample_country, include=FALSE}
-levels(testtrials$`Current Country of Residence`)
+levels(testtrials$currentResidence)
 ```
@@
   slice(1) %>% 
-  group_by(`Current Country of Residence`, studytype) %>%
+  group_by(currentResidence, studytype) %>%
   summarise(n = n()) %>%
   arrange(studytype, -n) %>% 
-  filter(!is.na(`Current Country of Residence`) & !is.na(studytype))
+  filter(!is.na(currentResidence) & !is.na(studytype))
 

### 2023-05-31 paper/manuscript.Rmd
make ready for resubmission

@@
 ```{r splithalf}
-splithalf <- readRDS(file = "../saves/tango-splithalf-table.rds")
+splithalf <- readRDS(file = "../saves/tango_splithalf_table.rds")
 ```
@@
 ```{r hedge_retest_correlationcoefficients}
-hedge_retest_correlationcoefficients <- readRDS(file = "../saves/tango-hedge-retest-correlationcoefficients.rds")
+hedge_retest_correlationcoefficients <- readRDS(file = "../saves/tango_hedge_retest_correlationcoefficients.rds")
 ```

### 2023-06-22 paper/manuscript.Rmd
minor proof-reading edits

@@
   Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
-  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
+  Here we present the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
@@
 For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development [@okumura2017individual].
-In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
+In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @slaughter2003introduction].
 Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
-Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
+Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2022relations; @hughes2007executive; @benson2013individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
 Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].
@@
 
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
+However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@slaughter2003introduction].
 Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
@@
 They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
-New tasks should capture variation across age groups, including older children and adults [@repacholi2003introduction].
+New tasks should capture variation across age groups, including older children and adults [@slaughter2003introduction].
 Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
 Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts [@molleman2019unleashing].
-The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].
+The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@slaughter2003introduction].
 
-# A new measure of gaze understanding
+## A new measure of gaze understanding
 
@@
 In this sample, most participants resided in the United Kingdom (n = 47), South Africa (n = 8), and Portugal (n = 6).
-Additional, detailed information can be found in the data set online.
+Additional detailed information can be found in the data set online.
 For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
@@
 To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`).[^1]
+The model included random intercepts for each participant and symmetric target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`).[^1]
 
@@
 [^2]: In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-    We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(inddiff$subjID[inddiff$datacollection == "remote - unsupervised" & inddiff$ageInYears == 3 & inddiff$studyversion == "box" & inddiff$webcam == TRUE])`).
+    We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = `r n_distinct(inddiff$subjID[inddiff$datacollection == "remote - unsupervised" & inddiff$ageInYears == 3 & inddiff$studyversion == "box" & !is.na(inddiff$nrRepeatedTestquestion)])`).
     We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 
-@pronk2021methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
+@pronk2022methods recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
 To compare our traditional approach of a simple odd-even split, we additionally calculated split-half reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
 First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2021methods].
+Analyses were run using the function `by_split` from the `splithalfr` package [@pronk2022methods].
 
@@
 
-Figure \@ref(fig:fig3) compares split-half reliability coefficients by splitting and stratification method [@pronk2021methods].
+Figure \@ref(fig:fig3) compares split-half reliability coefficients by splitting and stratification method [@pronk2022methods].
 In the hedge version, the split-half reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`.
 In the box version, split-half reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`.
-Similar to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
+Similar to the results of @pronk2022methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
 In most cases, stratifying by target position led to similar or even higher estimates compared to no stratification.
@@
 Reliability coefficients per splitting method, stratification level, study version, and age group.
-Error bars show the 95% confidence intervals of the coefficient estimates, calculated with the function `by_split` from the `splithalfr` package [@pronk2021methods].
+Error bars show the 95% confidence intervals of the coefficient estimates, calculated with the function `by_split` from the `splithalfr` package [@pronk2022methods].
 
@@
 For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
-This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.
+This corroborates what we already saw in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.
 
@@
 Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word [@tomasello2003constructing].
-For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data with a receptive vocabulary test [oREV, @bohn2022orev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO.
+For `r sum(vali_sample$nTotal[vali_sample$sample == "orev"])` children, we also collected data with a receptive vocabulary test [oREV, @bohninpressorev] approximately six months (mean = `r vali_sample$meanTimeDiff[vali_sample$sample == "orev_tango"]` years, sd = `r vali_sample$sdTimeDiff[vali_sample$sample == "orev_tango"]`, range = `r vali_sample$minTimeDiff[vali_sample$sample == "orev_tango"]` - `r vali_sample$maxTimeDiff[vali_sample$sample == "orev_tango"]`) after their participation in the TANGO.
 In the oREV task, children are shown four pictures (see Supplements for further detail) and hear a verbal prompt asking them to select one of the pictures.
@@
 For (A) and (B), the graphs show the posterior distributions for the respective predictor of each model.
-Filled green distributions show that adding the respective predictor improved the model fit compared to the null model.
+Filled green density curves show that adding the respective predictor improved the model fit compared to the null model.
 Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
@@
 This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
+Individuals behaved consistently differently from one another (i.e., we found substantial variation between individuals across age groups).
 Second, our task showed satisfactory psychometric properties with respect to internal consistency and test-retest reliability estimates.
 Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
-In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
+In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring developmental change in a fundamental social-cognitive ability.
 The web app (<https://ccp-odc.eva.mpg.de/tango-demo/>) and its source code (<https://github.com/ccp-eva/tango-demo>) are freely accessible for use and modification.
@@
 
-# Limitations
+## Limitations
 
@@
 
-# Conclusion
+## Conclusion
 

### 2023-06-22 supplements/supplements.tex
minor proof-reading edits

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
+  pdftitle={Supplemental Material for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
+  pdfauthor={Julia Prein1, Manuel Bohn1,2, Steven Kalinke1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
@@
 
-\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
+\title{Supplemental Material for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1,2}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
 \date{}
@@
 
-\authornote{
-
-Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
-E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany}
 
@@
 In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
+Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 0).
 We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
@@
 
-\begin{table}
+\begin{table}[H]
 \centering
@@
 \midrule
-By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
-By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
-By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
-By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
-By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
+By trial - Null model & 256.42 & 15.10 & 0.31 & 0.00 & 0.00\\
+By trial - \# Verification choice & 256.57 & 15.46 & 0.29 & -0.07 & 1.08\\
+By trial - Parental interference index & 258.08 & 15.38 & 0.14 & -0.83 & 0.76\\
+By trial - \# Repeated testquestion & 258.83 & 15.25 & 0.09 & -1.20 & 0.61\\
+By trial - \# Hints eyes & 258.88 & 15.30 & 0.09 & -1.23 & 0.50\\
 \addlinespace
-By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
-By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
-By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
-By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
-By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
+By trial - \# Words uttered by caregiver & 259.15 & 15.39 & 0.08 & -1.37 & 0.36\\
+By subject - \# Repeated testquestion & 83.45 & 10.20 & 0.82 & 0.00 & 0.00\\
+By subject - Parental interference index & 88.17 & 12.15 & 0.08 & -2.36 & 3.55\\
+By subject - Null model & 89.36 & 11.28 & 0.04 & -2.96 & 3.59\\
+By subject - \# Verification choice & 89.94 & 12.01 & 0.03 & -3.25 & 4.44\\
 \addlinespace
-By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
-By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
+By subject - \# Words uttered by caregiver & 90.50 & 10.62 & 0.02 & -3.52 & 4.19\\
+By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.78 & 3.71\\
 \bottomrule
@@
 \midrule
-Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
-Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
-Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
-\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
-Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
+Age of childcare entry & 571.54 & 28.09 & 0.72 & 0.00 & 0.00\\
+Null model & 575.80 & 30.43 & 0.09 & -2.13 & 4.51\\
+\# Children in household aged 0-18 & 577.29 & 29.61 & 0.04 & -2.88 & 4.70\\
+Peer exposure index & 577.90 & 30.20 & 0.03 & -3.18 & 4.65\\
+\# Children in household aged 1-12 & 578.02 & 29.93 & 0.03 & -3.24 & 4.69\\
 \addlinespace
-Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
-\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
-\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
-Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
+Sibling variety score (Cassidy et al., 2005) & 578.15 & 29.85 & 0.03 & -3.31 & 4.66\\
+Sibling variety score (Peterson, 2000) & 578.21 & 29.84 & 0.03 & -3.34 & 4.64\\
+\# Household members & 578.30 & 30.32 & 0.02 & -3.38 & 4.48\\
+Average hours spent in childcare per day & 579.04 & 30.66 & 0.02 & -3.75 & 4.56\\
 \bottomrule
@@
 The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
+Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).
+
+\begin{table}[H]
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lrrrrrrrr}
+\toprule
+  & n & mean & sd & min & max & skew & kurtosis & se\\
+\midrule
+Age of childcare entry in months & 109 & 14.96 & 5.54 & 1.0 & 40 & 1.72 & 5.65 & 0.53\\
+Average hours spent in childcare per day & 109 & 7.50 & 0.92 & 3.5 & 9 & -0.67 & 1.92 & 0.09\\
+\# Household members & 109 & 3.72 & 0.92 & 2.0 & 7 & 0.30 & 0.49 & 0.09\\
+\# Children in household aged 0-18 & 109 & 0.83 & 0.79 & 0.0 & 4 & 0.87 & 1.09 & 0.08\\
+\# Children in household aged 1-12 & 109 & 0.69 & 0.74 & 0.0 & 4 & 1.23 & 2.67 & 0.07\\
+\addlinespace
+Sibling variety score (Peterson, 2000) & 109 & 0.60 & 0.56 & 0.0 & 2 & 0.23 & -0.87 & 0.05\\
+Sibling variety score (Cassidy et al., 2005) & 109 & 0.63 & 0.54 & 0.0 & 2 & 0.18 & -0.70 & 0.05\\
+\bottomrule
+\end{tabular}}
+\end{table}
 
@@
 
-We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022).
+We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn et al., 2022).
 Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).
@@
 We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.
+In order to combine data of our two TANGO study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
+After this transformation, we calculated a ``TANGO score'' as the proportion of correctly located targets.
+See Analysis section of Social-environmental factors for further detail.
 
@@
 \midrule
-Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
-Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
-Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
-\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
-Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
-\addlinespace
-Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
-\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
-\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
-Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
+Age (scaled), TANGO score (scaled) & 570.16 & 26.38 & 0.98 & 0.00 & 0.00\\
+Age (scaled) & 577.66 & 27.16 & 0.02 & -3.75 & 4.16\\
+Null model & 635.72 & 28.70 & 0.00 & -32.78 & 10.62\\
 \bottomrule
@@
 \end{table}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_orev_byagegroup}
+
+}
+
+\caption{\textbf{Effect of gaze understanding on receptive vocabulary by age group}.
+Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
+Diamonds show the performance for each subject.
+The color of data points denotes age group.}\label{fig:fig6}
+\end{figure}
 
@@
 \toprule
-Current Country of Residence & studytype & n\\
+currentResidence & studytype & n\\
 \midrule
@@
 Mexico & vali & 1\\
+South Africa & vali2 & 20\\
+\addlinespace
+Portugal & vali2 & 11\\
+United Kingdom & vali2 & 5\\
+France & vali2 & 3\\
+Italy & vali2 & 2\\
+Spain & vali2 & 2\\
+\addlinespace
+Poland & vali2 & 2\\
+DATA EXPIRED & vali2 & 1\\
+Finland & vali2 & 1\\
+Czech Republic & vali2 & 1\\
+Latvia & vali2 & 1\\
+\addlinespace
+Switzerland & vali2 & 1\\
 South Africa & reli & 48\\
-\addlinespace
 United Kingdom & reli & 19\\
@@
 Portugal & reli & 10\\
+\addlinespace
 Italy & reli & 7\\
 Canada & reli & 6\\
-\addlinespace
 Spain & reli & 5\\
@@
 Poland & reli & 4\\
+\addlinespace
 Greece & reli & 4\\
 Netherlands & reli & 3\\
-\addlinespace
 CONSENT REVOKED & reli & 3\\
@@
 Australia & reli & 2\\
+\addlinespace
 France & reli & 2\\
 Czech Republic & reli & 2\\
-\addlinespace
 Hungary & reli & 2\\
@@
 Iceland & reli & 1\\
+\addlinespace
 New Zealand & reli & 1\\*
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
-\toprule()
+\toprule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 \textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
@@
 \textbf{sound for target click} & - & - & positive-feedback.mp3 \\
-\bottomrule()
 \end{longtable}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
-Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
+Bohn, M., Prein, J.
+C., Koch, T., Bee, R.
+M., Delikaya, B., Haun, D.
+B.
+M., \& Gagarina, N.
+(2022).
+\emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children} {[}Preprint{]}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/4z86w}
 
